### 2021-07-30 appendix/appendix.Rmd
adding main files

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^freire]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^roman]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

\appendix

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Required packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "devtools", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick",
          'stargazer', 'pander', 'broom')

# Install if not already installed
install <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
                     repos = "http://cran.us.r-project.org")
}
lapply(pkgs, install)
devtools::install_github("isubirana/compareGroups")
devtools::install_github("MathiasHarrer/dmetar")

# Load packages
lapply(pkgs, require, character.only = T)
library("compareGroups"); library(dmetar)

# Broom the multi-level model
broom_mod <- function(mod, subgroup = FALSE) {
  aux <- data.frame(predict(mod))
  if (subgroup) {
    teeff = aux$pred
    seteeff = aux$se
    labeff = c("Subgroup Effect")
    loeff = c(aux$ci.lb)
    upeff = c(aux$ci.ub)
  } else {
    teeff = c(aux$pred, NA)
    seteeff = c(aux$se, NA)
    labeff = c("Overall Effect",
               "Prediction Interval")
    loeff = c(aux$ci.lb, aux$cr.lb)
    upeff = c(aux$ci.ub, aux$cr.ub)
  }
  mod2 <- tibble(
    TE = as.numeric(mod$yi),
    seTE = sqrt(mod$vi),
    studlab = mod$slab,
    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
    group = 'A') %>%
    bind_rows(.,
              aux = tibble(
                TE = teeff,
                seTE = seteeff,
                studlab = labeff,
                lower = loeff,
                upper = upeff,
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  return(mod2)
}

# Estimation of the 
estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
  if (is.null(hetvar)) {
    stop('Hetvar should be different than null.')
  }
  levshetvar <- unique(hetvar)
  fullmod <- rma.mv(yi = yi, V = v, random = random,
                    data = dat, slab = slab, method = 'REML',
                    test = 't', tdist = T)
  res <- tibble()
  for (i in levshetvar) {
    partmod <- rma.mv(yi = yi, V = v, 
                      random = random,
                      data = dat, slab = slab, 
                      method = 'REML',
                      test = 't', tdist = T, 
                      subset = hetvar == i)
    partmod <- broom_mod(partmod, subgroup = T)
    partmod$byvar = i
    partmod <- bind_rows(
      tibble(TE = NA, seTE = NA,
             studlab = toupper(i), lower = NA,
             upper = NA, group = "B", byvar = i),
      partmod
    )
    res <- bind_rows(res, partmod)
  }
  aux <- data.frame(predict(fullmod))
  res <- bind_rows(res,
                   tibble(
                     byvar = NA,
                     TE = c(aux$pred, NA),
                     seTE = c(aux$se, NA),
                     studlab = c("Overall Effect", "Prediction Interval"),
                     lower = c(aux$ci.lb, aux$cr.lb),
                     upper = c(aux$ci.ub, aux$cr.ub),
                     group = "B"))
  res <- data.frame(res)
  res$byvar <- toupper(res$byvar)
  return(res)
}

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  if(class(mod)[1] == "rma.mv") {
    mod2 <- broom_mod(mod)
  } else {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  }
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod2 <- estim_het(dat = dat, 
                    yi = coef, 
                    v = v, 
                    random = ~ 1 | id_level1/id_level2, 
                    slab = slab, 
                    hetvar = hetvar)
  mod2 <- data.frame(mod2)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Load datasets
load("../dataset/dataCoefs.RData")
```

\newpage

# A Brief Introduction to the Law of _1/n_ and the Reverse Law of _1/n_

In this section, we present the intuition behind the _law of 1/n_, as well as the alternative _reverse law of 1/n_ proposed by @primo2008distributive.

In their seminal paper, @weingast1981political argue that a high number of legislators will increase public spending beyond the optimal economic benchmark. They suggest that politicians have an incentive to over-provide concentrated benefits to their constituencies, spreading the costs across all constituencies through generalised taxation. The corollary of their model is that larger legislatures generate more public spending.

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{The concavity assumption implies that $b'>0$ and $b''<0$. A similarly convex assumption would mean that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hiring a local company for the project). The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hiring a company from another state). Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

Projects are economically efficient when the marginal costs are equal to the marginal benefits of the project size. This leads to the economic optimal project size, $x^E$. The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$. However, the projects that are actually implemented have a different structure. First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represents the number of constituencies. Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms. Therefore, the costs and benefits of implementing a project with size $x$ have the following structure:

\[
N(x) = b(x) + c_1(x) - \frac{1}{n}[c_1(x) + c_2(x)] - c_3(x)
\]

Differentiating $N(x)$ with respect to $x$ gives us the first order condition for an optimal project implementation.

\[
b'(x) + c_1'(x) - \dfrac{1}{n}[c_1'(x) + c_2'(x)] - c_3'(x) = 0
\]

Totally differentiating $x$ with respect to $n$ gives us the following:

\[
b''(x)\dfrac{dx}{dn} + c_1''(x)\dfrac{dx}{dn} - \dfrac{1}{n}[c_1''(x) + c_2''(x)]\dfrac{dx}{dn} + \dfrac{1}{n^2}[c_1'(x) + c_2'(x)] - c_3''(x)\dfrac{dx}{dn} = 0
\]

And rearranging the terms, we find the following expression for $\dfrac{dx}{dn}$:

\[
\dfrac{dx}{dn} = -\dfrac{n^{-2}[c_1'(x) + c_2'(x)]}{b''(x) + c_1''(x)-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x)}
\]

Note that the numerator is always positive, as the marginal investment costs inside and outside the district increase according to the project size. The _law of 1/n_ holds when the denominator is negative. $b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$. Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.

As the above condition suggests, the _law of 1/n_ holds only in specific situations. @primo2008distributive advance that theory by considering other situations where the _law_ may not hold, and they also argue that there are cases in which a _reverse law of 1/n_ holds, that is, larger legislatures may lead to lower public expenditures.

Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit of $b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the degree of congestion of the public good, that is, how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district pay both local and federal government taxes. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Therefore, the citizens receive the following net benefit of a project with size $x$:

\[
\pi = x^\alpha m^{\beta-1} - \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta
\]

Maximising this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects, we find the following optimal project size:

\[
x^* = \left[\left(\dfrac{\alpha}{\theta}\right)^{\dfrac{1}{\theta-\alpha}}\right]\left[\left(nm\right)^{\dfrac{\beta+\theta-1}{\theta - \alpha}}\right]\left[\left( \dfrac{n^{2-\beta-\theta}}{n-ns+s}\right)^{\dfrac{1}{\theta-\alpha}}\right]
\]

And in the graph below, we show simulations for $n$ varying from 10 to 20, holding constant $\beta = 0.35$, $\theta \in \{0.65, 0.75\}$, $s = 0.5$, $m = 100$, and $\alpha = 0.7$.

```{r, echo=FALSE, cache=TRUE, fig.align='center'}
xstar <- function(x, beta, theta, alpha = 0.7, s = 0.5, m = 10) {
  n = x
  a = (alpha/theta)^(1/(theta-alpha))
  b = (n*m)^((beta+theta-1)/(theta-alpha))
  c = ((n^(2-beta-theta))/(n-n*s+s))^(1/(theta-alpha))
  return (a*b*c)
}

curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
```

Thus, we see that both the _law of 1/n_ and its reverse formulation are equally plausible. Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen2007law], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].

# Search Criteria

The first step in our systematic review consisted in gathering a study sample. We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature. This search produced a database with many entries that were unrelated to our subject of investigation. To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is the fundamental contribution to the field. Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in the `R` script available in this repository. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles.

We complemented this process by doing a term search on Google Scholar after having finished the entire eligibility procedure in the first sample. We formulated the search string based on the terms and expressions that appeared most frequently in the articles included in our meta-analysis. The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending. The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`. We scraped Google Scholar on March 5^th^, 2021. Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously. We then performed the exact same eligibility procedures, further explained below. This resulted in 3,041 additional records. Combining the two search strategies, we assessed a total of 5,705 records.

# Article Selection

The selection process was conducted by two authors in three phases. In the first phase, we excluded all titles that were clearly unrelated to our topic of interest. This was only a preliminary step, as we were not able to eliminate a large number of entries. Then, we read all abstracts. We kept all publications whose main topics were either government expenditure or legislative structures. Abstracts that indicated that the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were included. This allowed us to significantly reduce our sample.

In the second phase, we assessed full texts. To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure. If the publication had all three, we kept it in our sample. Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.

The third phase consisted of filling out tables for each of the remaining 47
articles to systematically evaluate their eligibility. Since authors use
different measures for government spending and the number of lower/upper house
members, we extracted all coefficients that provided this information. In this
phase, we also collected information on whether the paper had been published,
and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
we excluded two studies from the first sample, as they did not have the
dependent/independent variables we collected for our meta-analysis. We then
included the 2 papers we found in the second search, as both conformed to our
criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
articles.

## Exclusion Analysis

We selected the final pool of articles based on two criteria, namely the independent and the dependent variables employed in the paper. The categories follow below:

1.  Independent variables:

-   *N*: Number Legislators in the Lower Chamber
-   *logN*: Log Number Legislators in the Lower Chamber
-   *K*: Number Legislators in the Upper Chamber

2.  Dependent variables:

-   *ExpPC*: Expenditure Per Capita
-   *logExpPC*: Log Expenditure Per Capita
-   *PCTGDP*: Expenditure as Percentage of GDP

If a paper did not use a combination of these variables, we excluded it from the meta-analysis.

## Flow Chart

The diagram below shows each step of our article selection process. We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) statement to conduct our study\footnote{More information about the PRISMA statement is available at \url{http://www.prisma-statement.org}.}. The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.

\bigskip

```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}

  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Identification}};

  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening}};

  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};

  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};

  \node (id) [phase, right of = ID, xshift = 1cm] {Records identified through webscraping  \\ \textbf{(n = 2664)}};

  \node (1st) [exc, right of = id, xshift = 3cm] {Records in languages other than English, book chapters, doctoral theses, and duplicates excluded \\ \textbf{(n = 1220)}};

  \node (screen) [phase, below of = id] {Records screened \\ \textbf{(n = 1445)}};

  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading title and abstract \\ \textbf{(n = 1069)}};

  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 376)}};

  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 329)}};

  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 47)}};

  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 19)}};

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 28)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

 \end{tikzpicture}
```

\bigskip

```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}
  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 11)}};
\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 2)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
```

# Meta-Analysis Dataset

Our meta-analytic data are comprised of two datasets. The first dataset has the main coefficients reported in the selected studies. These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.

In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended dataset. Here we present the results of all tests performed in both reduced and full samples.

# Descriptive Statistics

Here we show the descriptive statistics for our sample. We focus on the following paper characteristics: study year; paper publication; the electoral system mentioned in the publication; and the distribution of the dependent and independent variables of interest.

## Study Year

The average year of publication in our sample is `r round(mean(dat$year), 2)` with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.

```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE, size="footnotesize", echo = FALSE}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

## Frequency of Published Papers

Studies were included in our sample regardless of their publication status. From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were not published.

```{r, fig.width=4, fig.height=2.5, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

## Electoral System

Our sample differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies. In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

```{r, fig.width=6, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

## Dependent Variables

The dependent variables included in the paper are:

-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Expenditure Per Capita papers
-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Log of Expenditure Per Capita papers

```{r, fig.width=6, fig.height=2.3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Expenditure Per Capita",
                                     "Expenditure as Percentage GDP",
                                     "Log Expenditure Per Capita"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  coord_flip() +
  theme_bw()
```

## Independent Variables

Most papers in our sample analyse the number of legislators in the lower chamber (`r as.numeric(table(dat$indepvar2)[3])`). The second most frequent independent variable is the number of legislators in the upper chamber (`r as.numeric(table(dat$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower chamber as an independent variable (`r as.numeric(table(dat$indepvar2)[2])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.

```{r, fig.width=6, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, 
                            labels = c("Upper Chamber Size",
                                       "Log of Lower Chamber Size",
                                       "Lower Chamber Size"
                                                  ))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  coord_flip() +
  theme_bw()
```

## Histogram of the Coefficients and the Standard Errors

The coefficients in the papers vary considerably. We plot a histogram of the coefficients for all measurements included in the meta-analytic dataset. Most coefficients and standard deviations are close to zero.

Coefficients:

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients", y = '') +
  theme_bw()
```

\newpage

Standard errors:

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors", y = '') +
  theme_bw()
```

## Sign Coefficients

One simple statistic that we can compute to assess the validity of the *law of 1/n* is the frequency of positive and negative estimates in the study sample. Below we plot the frequency for all the papers included in the meta-analytic dataset.

```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE, echo = FALSE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

# Descriptive Statistics of Moderators

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study: lower chamber size ($n$), natural logarithm of lower chamber size (log[$n$]), or upper chamber size ($k$). The additional moderators are: the publication year; whether the paper was published in an academic journal; the estimation method used in the paper; the insitution design in terms of the division of legislative power; and the electoral system.

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, year, published, method,
              instdesign, elecsys2) %>%
  mutate(indepvar2 = recode(indepvar2,
                            `N` = "Lower Chamber Size",
                            `K` = "Upper Chamber Size",
                            `logN` = "Log of Lower Chamber Size"),
         elecsys2 = recode(elecsys2,
                           `Non-Maj` = "Non-Majoritarian",
                           `Maj` = "Majoritarian")) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

# Binomial Tests for Coefficient Signs

The *law of 1/n* posits that we should expect a positive influence of legislature size on public expenditures. A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations. In statistical terms, consider a random variable representing the coefficient sign for the papers. As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the chance of a positive sign. The *law of 1/n* can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory. The null statistical hypothesis for such a test is that:

- $H_0$: the proportion of positive and negative signs are statistically equal ($p=0.5$).

As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) may be true. In this case, the alternative hypothesis is $p \neq 0.5$. To perform this test, we run binomial exact tests in `R`, using the function `binom.test(.)`.

This test has two advantages. First, it is robust to the design of the paper. This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not. The binomial test ignores the design discrepancies and focuses on the overall reported effect. Second, this test has the advantages of requiring few assumptions and being easy to interpret. The disadvantage is that the test is not as informative as the meta-regressions, as we shall see in the next sections.

For the number of legislators in the lower chamber ($N$), the results follow below.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
```

Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. Thus, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

For the log of the number of legislators in the lower chamber ($\log(N)$), the results are as follows:

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
```

Out of `r sum(table(aux$scoef))` studies, `r as.numeric(table(aux$scoef)[2])` have a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. So we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

Finally, for the number of legislators in the upper chamber ($K$), the results are:

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
```

Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign. The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`. Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$. This is the only test that presents evidence of an association between the legislature size and expenditure.

We also tested the possibility that the signs change heterogeneously, based on whether the paper studied unicameral versus non-unicameral legislative bodies. This analysis does not take into consideration the size of the upper house, as it would indicate that the cases in the paper had trivially a non-unicameral legislature. The results for this analysis follow below, and show that there is no significant change in the sign of the relationship between public spending and legislature size, when controlling by the institution design.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- list()
aux[[1]] <- filter(dat, indepvar2 == "N", instdesign2 == 'Unicameral')
aux[[2]] <- filter(dat, indepvar2 == "N", instdesign2 != 'Unicameral')
aux[[3]] <- filter(dat, indepvar2 == "logN", instdesign2 == 'Unicameral')
aux[[4]] <- filter(dat, indepvar2 == "logN", instdesign2 != 'Unicameral')
aux[[1]] <- binom.test(table(aux[[1]]$scoef)[2],
                       sum(table(aux[[1]]$scoef)), p = 0.5)
aux[[2]] <- binom.test(table(aux[[2]]$scoef)[2],
                       sum(table(aux[[2]]$scoef)), p = 0.5)
aux[[3]] <- binom.test(table(aux[[3]]$scoef)[2],
                       sum(table(aux[[3]]$scoef)), p = 0.5)
aux[[4]] <- binom.test(table(aux[[4]]$scoef)[2],
                       sum(table(aux[[4]]$scoef)), p = 0.5)
aux2 <- tidy(aux[[1]])[,-c(2,4,5,6)][,c(3,4,1,2)]
aux2 <- bind_rows(aux2, tidy(aux[[2]])[,-c(2,4,5,6)][,c(3,4,1,2)])
aux2 <- bind_rows(aux2, tidy(aux[[3]])[,-c(2,4,5,6)][,c(3,4,1,2)])
aux2 <- bind_rows(aux2, tidy(aux[[4]])[,-c(2,4,5,6)][,c(3,4,1,2)])
aux2 <- aux2 %>%
  mutate(`Indep. Variable` = c('Lower House Size', 'Lower House Size', 'Log of Lower House Size', 'Log of Lower House Size'),
         `Legislative Inst.` = c('Unicameral', 'Non-unicameral', 'Unicameral', 'Non-unicameral')) %>%
  relocate(`Indep. Variable`, `Legislative Inst.`, .before = method)
aux2$method <- NULL
aux2$alternative <- NULL
pander(aux2)
```

# Meta-Analysis

## Estimation Method

In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models. The fixed effects model assumes that there exists a single true effect and all estimates are an attempt to uncover this effect. The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.

In this paper, we employ a random effects model. The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

1.  **Study sample**: Counties, Municipalities, States, Provinces, Countries.
2.  **Electoral systems**: Majoritarian, PR, Mixed.
3.  **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
4.  **Institution design**: Unicameral, Bicameral, or the Mixed of both Unicameral and Bicameral.

These sources of heterogeneity have two implications. First, they make our estimates notably disperse. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased. Thus, we opt for the random effects model.

Assume that each study has an effect of $T_i$. In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:

$$
T_i \ = \ \theta_i + \varepsilon_i
$$

And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:

$$
T_i \ = \ \mu + \xi_i + \varepsilon_i
$$

And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.

Another crucial assumption in meta-analysis is that the coefficients should be independent [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction]. This assumption states that for our findings to be consistent, the coefficients must come from different sources of variation. However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model with similar variables. While our restricted dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients. This is because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients. To correct for the violation of the study independence assumption, we use a multilevel random effects model [@cheung2014modeling]. We add two extra levels to the regular random effects model, one that indicates the publication ID and another that indicates the data used in the original article. These levels are assumed to remove dependence structures in the data, therefore improving the estimates of our coefficient of interest, which is the effect of legislature size on public spending.

There are two levels in the main models. First, we build a common index for papers that share the same data specifications. The papers with common indexing are:

| Publication ID                              | Source of Dependence                                                     |
|---------------------------------------------|--------------------------------------------------------------------------|
| 3, 42, 132, 165, 439, 441, 467, 505         | US States Data                                                           |
| 408, 208, A258                              | US Municipalities Data                                                   |
| 849, 578                                    | US Municipalities Data and Same Author in Two Different Studies          |

All the remaining papers received a unique index. As the number of papers with these dependencies is not very high, and many characteristics within papers vary (e. g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs. In regard to the full dataset, the results change considerably, because authors fit several models within the same paper. In any case, we use multilevel random effects for all the estimated models in this paper.

To study the possibility of publication bias, we add a funnel plot and an @egger1997bias test for distribution asymmetry for every model. Funnel plots display the possibility of having a file-drawer effect, meaning that null results are under-represented in our sample. In this type of plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome. If they are asymmetric, it provides evidence for a file-drawer effect.

We use the `R` packages `meta` and `dmetar` in all estimates [@harrer2019doing]. We employ the *Restricted Maximum Likelihood Estimator* to assess the variance of the true effect size ($\tau^2$), which in our formulation represents the variance of $\xi_i$. The literature regards this estimator as the most precise when analysing continuous measures, such as the ones we have in our data [@veroniki2016methods].

We combine the three independent variables (Lower Chamber Size, Log of Lower Chamber Size, and Upper Chamber Size) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP). This formed a $3 \times 3$ table, yet not all combinations are available in the data. The results are shown below.

## Lower Chamber Size and Expenditure Per Capita

The results for the meta-analysis that compares lower chamber size and expenditure per capita are available below.

```{r, cache=TRUE, echo = FALSE, size="footnotesize"}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

mod
```

The forest plot:

```{r, fig.width=8, fig.height=4.5, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r,include=F, warning=F, cache=TRUE, echo = FALSE}
f1 <- build_forest(mod, NULL, lsize = 15, ttl = '1.1 - Lower Chamber Size\nand Expenditure Per Capita')
```

And to assess the possibility of publication bias, we add the funnel plot below:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

### Electoral System Subgroup Analysis

The *law of 1/n* was introduced to describe majoritarian systems, but the theory has also been applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary indicator for electoral system. The results may be seen below.

We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita. Both coefficients are not statistically significant, and they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Electoral System", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

### Institution Design Subgroup Analysis

The *law of 1/n* was conceived to explain the expected effect of chamber size on public expenditure. However, papers such as @chen2007law demonstrated that the relationship is mediated by the size of the upper chamber. Their finding suggests that the institutional design of the legislature influences the empirical predictions in the sample we study. To test this possibility, we estimated a subgroup analysis using a binary indicator for institutional design. The results may be seen below.

We find little evidence that either unicameral or non-unicameral legislative institutions produce systematically positive effects on expenditure per capita. However, the coefficients tend to be weakly positive for unicameral studies, suggesting that there might be a relationship, that is masked by the low statistical power.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Institution Design", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$instdesign2)
```

## Log of Lower Chamber Size and Expenditure Per Capita

There are no studies that have per capita expenditure as the dependent variable and log of lower chamber size as the independent variable.

## Upper House Size and Expenditure Per Capita

Now we look into the upper chamber size. In this model, we investigate the effect of upper house size on expenditure per capita.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

```{r, fig.width=7, fig.height=3, fig.cap="Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, echo = FALSE}
build_forest(mod, NULL)
```

We see no evidence of publication bias:

```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r, include=FALSE, warning=FALSE, echo = FALSE}
f2 <- build_forest(mod, NULL, 15, ttl = '1.6 - Upper Chamber Size\nand Expenditure Per Capita')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Lower Chamber Size and Log of Expenditure Per Capita

This model estimates the log of expenditure per capita as the dependent variable, and lower chamber size as the independent variable.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

mod
```

The forest plot is as follows:

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Log of Expenditure Per Capita",warning=FALSE, echo = FALSE, cache=TRUE}
build_forest(mod, NULL)
```

The funnel plot shows no evidence of publication bias.

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
f3 <- build_forest(mod, NULL, 15, ttl = '1.2 - Lower Chamber Size\nand Log Expenditure Per Capita')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Log of Lower Chamber Size and Log of Expenditure Per Capita

In this specification, we study the log of per capita expenditure as a function of the log of lower chamber size.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

The forest plot is available below:

```{r, fig.width=6, fig.height=4, fig.cap="Effect of Log Lower Chamber Size on Log Expenditure Per Capita", echo = FALSE, warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

The funnel plot:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
f4  <- build_forest(mod, NULL, 15, ttl = '1.4 - Log Lower Chamber Size\nand Log Expenditure Per Capita')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Upper Chamber Size and Log of Expenditure Per Capita

No studies correlate the log of per capita expenditure with the size of the upper chamber (K).

## Lower Chamber Size and Expenditure as Percentage of GDP

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the independent variable.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

Below, you may find the forest plot:

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, echo = FALSE, cache=TRUE}
build_forest(mod, NULL)
```

The funnel plot to test for publication bias:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r, include=F, warning=F, echo = FALSE, cache=TRUE}
f5 <- build_forest(mod, NULL, 15, ttl = '1.3 - Lower Chamber Size\nand Expenditure as Percentage of GDP')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Log Lower Chamber Size and Expenditure as Percentage of GDP

This model investigates the percentage of GDP as public expenditure as the dependent variable and the log lower chamber size as the independent variable.

```{r, echo = FALSE, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

mod
```

```{r, echo = FALSE, fig.width=8, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

The funnel plot is available below:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
f6 <- build_forest(mod, NULL, 15, ttl = '1.5 - Log Lower Chamber Size\nand Expenditure as Percentage of GDP')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Upper Chamber Size and Expenditure as Percentage of GDP

This model looks into the effect of upper chamber size on the public expenditure share of the GDP.

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

```{r, fig.width=8, fig.height=4, fig.cap="Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

As in our previous estimations, we find no evidence of file-drawer effect.

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
f7 <- build_forest(mod, NULL, 15, ttl = '1.7 - Upper Chamber Size\nand Expenditure as Percentage of GDP')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Lower Chamber Size and Expenditure per Capita (Instrumental Variables Only)

Here we estimate a meta-analysis of the papers which use instrumental variables. The results may be seen below.

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

And the forest plot:

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

No evidence of publication bias, as shown in the following funnel plot:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

f8 <- build_forest_het(aux, aux$coef, 
                       aux$VAR, slab = aux$authoryear,
                       capt = NULL, lsize = 15, 
                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(subgrouping by the estimation technique)', 
                       hetvar = aux$method)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

### Regression Method Subgroup Analysis

Over time, the literature evolved to use causally identified techniques to determine the effect of legislature size on the expenditure per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$method)
```

Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers displaying negative effects. The random effects model for the subgroup is 0.22, which is negative but non-significant. Improving the estimation technique, for the case of IVs, still renders a null effect of legislature size on per capita government expenditure.

## Lower Chamber Size and Log of Expenditure per Capita (Regression Discontinuity Design Only)

In this subsection, we run a meta-analysis with papers that include regression discontinuity designs.

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- logExpPC x N (RDD only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

Forest plot:

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

f9 <- build_forest(mod, capt = NULL, 
                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(subgrouping by RDD)')
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. The reason is because in that paper, the author uses Log of Expenditure Per Capita x Log of Legislature Size.

```{r, warning=F, cache=TRUE, echo = FALSE, results='hide'}
## Plot 1
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
## Plot 2
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```

# Meta-Analysis (All Coefficients)

## Lower Chamber Size and Expenditure Per Capita

Here we estimate the relationship between expenditure per capita as a dependent variable, and the lower chamber as the independent variable.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

The forest plot:

```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And to assess the possibility of publication bias, we add the funnel plot below:

```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

### Electoral System Subgroup Analysis

The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems. In the theoretical section below, we explain why the argument has potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.

We see that majoritarian systems do not have a clear positive effect on budgetary spending. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Electoral System", warning=FALSE, cache=T, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

### Institution Design Subgroup Analysis

The *law of 1/n* was conceived to explain the expected effect of chamber size on public expenditure. However, papers such as @chen2007law demonstrated that the relationship is mediated by the size of the upper chamber. Their finding suggests that the institutional design of the legislature influences the empirical predictions in the sample we study. To test this possibility, we estimated a subgroup analysis using a binary indicator for institutional design. The results may be seen below.

We find little evidence that either unicameral or non-unicameral legislative institutions produce systematically positive effects on expenditure per capita. However, the coefficients tend to be weakly positive for unicameral studies, suggesting that there might be a relationship, that is masked by the low statistical power.

```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Institution Design", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$instdesign2)
```

## Log of Lower Chamber Size and Expenditure Per Capita

There are no studies that have per capita expenditure as the dependent variable and log of lower chamber size as the independent variable.

## Upper Chamber Size and Expenditure Per Capita

Now we investigate the effect of the upper chamber size on expenditure per capita.

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

The forest plot:

```{r, fig.width=9, fig.height=10, fig.cap="Effect of Upper Chamber Size on the Per Capita Government Expenditure",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

The funnel plot suggests no publication bias.

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Lower Chamber Size and Log of Expenditure Per Capita

This model estimates the log of per capita expenditure as the dependent variable, and the number of lower chamber legislators as the independent variable.

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- logExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

The forest plot is shown below:

```{r, fig.width=8, fig.height=5, fig.cap="Effect of Lower Chamber Size on Log Expenditure Per Capita",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Log of Lower Chamber Size and Log of Expenditure Per Capita

In this specification, we study the log of per capita expenditure as a function of the log of lower chamber size.

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- logExpPC x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

The forest plot:

```{r, fig.width=8, fig.height=7, fig.cap="Effect of Log of Lower Chamber Size on Log of Expenditure Per Capita",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And the funnel plot:

```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of Log of Lower Chamber Size on Log of Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Upper Chamber Size and Log of Expenditure Per Capita

No studies related the log of per capita expenditure with the size of upper chamber.

## Lower Chamber Size and Expenditure as Percentage of GDP

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower chamber as the independent variable.

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

Here is the forest plot:

```{r, fig.width=8, fig.height=7, fig.cap="Effect of Lower Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And here is the funnel plot to assess the possibility of publication bias:

```{r, fig.width=4, fig.height=3.75, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Log of Lower Chamber Size and Expenditure as Percentage of GDP

This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the natural logarithm of lower chamber size as the independent variable.

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- PCTGDP x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

The forest plot:

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And the funnel plot:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Upper Chamber Size and Expenditure as Percentage of GDP

This model looks into the effect of upper chamber size on the expenditure as a percentage of the GDP.

```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
# Pooling effects analysis -- PCTGDP x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

And the forest plot:

```{r, fig.width=8, fig.height=4, fig.cap="Effect of Upper Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And to assess the possibility of publication bias, we add funnel plot below:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Lower Chamber Size and Expenditure per Capita (Instrumental Variables Only)

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

And the forest plot:

```{r, fig.width=8, fig.height=4, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And to assess the possibility of publication bias, we add funnel plot below:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

## Lower Chamber Size and Log of Expenditure Per Capita (Regression Discontinuity Designs Only)

```{r, size="footnotesize", cache=TRUE, echo = FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

And the forest plot:

```{r, fig.width=8, fig.height=4, fig.cap="Effect of Lower Chamber Size on Log Expenditure Per Capita (RDD Only)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And to assess the possibility of publication bias, we add funnel plot below:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

Highlights:

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

# Meta-Regressions

In the meta-regressions, we study the effects of a group of moderators on the reported government spending data. We select the following moderators:

1. The independent variable (variable `indepvar2`):
  - `K`: Upper Chamber Size
  - `N`: Lower Chamber Size
  - `logN`: Log of Lower Chamber Size

2. Year that the paper was published (for working papers, the year it was posted online; variable `year`)

3. A dummy indicating whether the paper was published or not (variable `published`).

4. A dummy for non-majoritarian electoral systems (variable `elecsys2`).

5. A institution design variable, with:
 - `Bicameral`: a legislative system comprised of two chambers (e.g. US Federal Senate and House).
 - `Unicameral`: a system with only a lower chamber (e.g. US Municipalities).
 - `Mixed`: more than one system in the same sample (cross-country regressions).

6. The estimation method used in the papers (variable `method`):
  - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
  - `PANEL`: Time-Series Cross-Section models, with estimated fixed effects.
  - `IV`: Instrumental Variables models.
  - `RDD`: Regression Discontinuity Designs.

The results follows below, for the three combinations of dependent variables: Expenditure Per Capita, Log of Expenditure Per Capita, and Expenditure as Percentage of GDP.

## Meta-Regressions for Expenditure Per Capita

Here we study the expenditure per capita as the main outcome, aggregating all types of independent variables.

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              sparse = TRUE,
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

summary(mod)
```

For the meta-regressions of Expenditure Per Capita, we find no significant moderator. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

summary(mod)
```

With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:

1.  Compared with upper chamber size, models with lower chamber size tend to detect significantly smaller effects.

2.  Year has now a positive effect on coefficient sizes.

3.  All other moderators were insignificant.

## Meta-Regressions for Log of Expenditure Per Capita

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)

summary(mod)
```

The only significant result points that published papers tend to report a smaller coefficient than unpublished papers.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

summary(mod)
```

With all coefficients, results of the effect sizes on the log of expenditure per capita regressions indicate that in regard to the estimation method, papers that use panel data or regression discontinuity designs have smaller effects than articles that employ simple OLS regressions. All other results are insignificant.

## Meta-Regressions for Expenditure as a Percentage of GDP

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

summary(mod)
```

In the meta-regressions of Expenditure as a Percentage of GDP, we found that:

1. Recent papers find smaller effect sizes than older studies.

2. Papers whose samples included unicameral legislatures report slightly higher coefficients.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

With all coefficients, the results of the effect sizes on the Expenditure as a Percentage of GDP regressions are the following:

1. Papers from more recent years find smaller effect sizes than older studies.

2. Studies using non-majoritarian systems find more positive effects between variables.

3. Papers whose samples included unicameral legislatures report significantly higher coefficients.

# Meta-Regressions (All Coefficients)

In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling for:

1. The type of the dependent variable in the study (expenditure per capita, log expenditure per capita, and expenditure as percentage of GDP).

2. The type of the independent variable in the study (lower chamber size, upper chamber size, or log of lower chamber size).

3. The electoral system (Majoritarian versus Non-Majoritarian).

4. The year when the study was published.

5. Whether the study is a working paper or published work.

6. The institutional design: whether the legislature in the analysis is unicameral, bicameral, or mixed.

7. The estimation method used in the paper (OLS, PANEL, IV, or RDD).

The results follow below, and show null effects for all variables except for Unicameral institutional designs.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = dat$authoryear)

summary(mod)
```

In the restricted model, with only the main coefficients in the selected papers, Unicameralism has a positive, significant effect. Also, papers using Regression Discontinuity Design tend to have a negative effect, significant at the 10% level. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = fulldat$authoryear)
summary(mod)
```
In the full model, we can see that:

1. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.

2. Evidence from unicameral systems presents significantly larger effect sizes.

3. All other moderators are insignificant.

### 2021-07-30 article/article.Rmd
adding main files

---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/legislature-size-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending. The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Clean up
rm(list = ls())

## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

# Install if not already installed
installIfNot <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
					 repos = "http://cran.us.r-project.org")
}
lapply(pkgs, installIfNot)

# Load packages
lapply(pkgs, require, character.only = T)
devtools::install_github("isubirana/compareGroups")
library("compareGroups")

# Load datasets
load("../dataset/dataCoefs.RData")

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)

  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

\newpage

# Introduction
\label{sec:intro}

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Early
studies that empirically tested the "law of $1/n$", as the theory is currently
known, indeed found a positive correlation between the number of legislature
seats and different measures of government spending, although these first
results were mainly based on US state legislatures and the effect was often
limited to one house [e.g., @baqir2002districting; @gilligan1995deviations;
@gilligan2001fiscal].

Later research, however, has questioned the validity of the "law of $1/n$".
@primo2008distributive affirm that, due to spatial spillovers, a collection of
small districts can supply public goods more efficiently than the central
government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. Similarly, @primo2006stop and @chen2007law find that
lower and upper chambers may have mixed effects on government spending, while
@petterssonlidbom2012size argues that the impact of larger chamber sizes is
negative when using data from Finland and Sweden.

Since many empirical tests of the "law of $1/n$" have produced conflicting
results, scholars have expanded this research agenda and closely investigated
how institutional factors condition the original formulation of the theory. For
instance, authors such as @crowley2019law and @pecorino2018supermajority
accurately point out that collective action problems have been overlooked in
the literature, and recent findings indicate that bicameralism
[@maldonado2013legislatures], intergovernmental competition
[@crowley2015local], redistricting [@lee2018court], and party ideology
[@bjedov2014impact] strongly influence the relationship between seats and
spending. Moreover, the literature has increasingly applied causal inference
designs to estimate the effect of the "law of $1/n$", and in contrast to
previous studies using panel data, regression discontinuity designs generally
indicate that more legislators decrease public expenditures
[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
respect, scholars have long been aware of the theoretical and empirical
limitations of the "law of $1/n$", and the proliferation of new studies reflect
a conscious attempt to assess the robustness of the theory [@crowley2019law].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to evaluate the impact of legislature size over
government spending across several dimensions. Our study sample mirrors the
diversity of the literature. Out of the `r dim(dat)[1]` coefficients
included in our main analysis, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given the volume and the disparity of
the studies, we employ meta-analysis to summarise the results. Meta-analysis
provides a rigorous approach to combine heterogeneous outcomes into a single
estimation, and it allows scholars to gain valuable insights from the
aggregated data [@cooper2019handbook; @hedges1985statistical]. Meta-analysis
can also identify potential sources of study variability, enabling researchers
to assess threats to external validity and direct future efforts into more
promising areas of academic inquiry [@doucouliagos2008democracy]. Research
synthesis methods have been successfully applied in medicine and psychology
since the 1970s [@glass2015meta], and our work contributes to the burgeoning
literature that uses meta-analytic methods to understand challenging questions
in political science [@costa2017responsive; @doucouliagos2008democracy;
@green2013field; @lau2007effects; @schwarz2020supporting].

We run binomial tests and meta-regressions to further evaluate the relationship
between legislature size and government expenditures. We use binomial tests
to assess whether the proportions of positive and negative coefficients in our
sample are statistically different from each other. In the meta-regressions, we
measure the effect of five moderators that capture different sources of
heterogeneity in the literature. As our sample includes both published and
unpublished articles, we also construct a series of funnel plots to test for
publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

Aggregate results indicate that legislature size has no significant impact on
public spending. All of our main meta-analysis estimates show that the overall
effect is not statistically different from zero, thus confirming the
conflicting findings reported by the literature. However, when we look only at
articles that employ regression discontinuity designs, we see that all three
papers included in our sample suggest that a higher number of legislators leads
to lower public spending [@debenedetto2018effect; @hohmann2017effect;
@lewis2019legislature]. In this regard, it is possible that methodological
choices partially explain the divergent results observed in the literature, as
studies that use causal inference methods consistently point to the same
direction. One limitation of this finding is that these studies only test the
impact of lower house size on the natural logarithm of expenditure per capita,
thus it remains unclear whether the results hold with other variables.

The meta-regressions provide additional evidence that our study sample is
highly heterogeneous and that effect sizes differ substantially according to
study specifications. When using our extended sample of `r dim(fulldat)[1]`
coefficients, we find that unicameralism is associated with higher public
spending, as predicted by the "law of $1/n$". Since most unicameral
legislatures are located in local governments (municipalities or districts),
this result supports the theory strictly in its first formulation. Moreover,
our meta-regressions indicate that larger upper chambers spend more in terms of
per capita expenditure than lower chambers, a result that also appears in the
binomial tests. Non-majoritarian voting systems decrease government spending as
a percentage of GDP, but they do not have a relevant impact on the other
measures of public expenditure, following the idea that the $1/n$ effect grows
weaker as the empirical cases distance from the original definition of the law.
Finally, meta-regression results confirm that regression discontinuity models
reduce public spending estimates.

In summary, our results are in line with previous findings that lend partial
support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
An assessment of the effects of collective action costs in these analyses is
crucial to determine the full mechanism operating behind these results.
Overall, our analysis does not provide robust support for the theory as
originally conceived.

# Data and Methods

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that were published in English and
cited \citet{weingast1981political}, as it is the foundational work in the
literature on the "law of $1/n$". To ensure that our sample was comparable, we
only selected papers that used quantitative methods to analyse
data\footnote{Since meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our selected variables. Please refer to Section C in the Supplementary Material
for a detailed description of the selection procedure. We also included two
PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
flow diagrammes \citep{liberati2009prisma} showing the number of resulting
papers after each review step.}. After this stage, we identified six
measurements that the literature often employs to quantify government
expenditure and legislature size. For government expenditure, our study sample
uses (i) public expenditure as a share of GDP; (ii) public expenditure per
capita; and (iii) the natural logarithm of public expenditure per capita as its
main variables of interest. In regards to legislature size, the variables are
(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
upper house size\footnote{There are a few important nuances concerning coding
of these variables. Unicameralism, for example, is captured both by lower
chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
the literature estimates how institutional designs affect this relationship,
ours and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any article that used the natural
logarithm of upper chamber size in their models.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. This search
added two new results to our sample [@coate2011government;
@debenedetto2018effect], but neither of them included variables beyond the six
measures we had previously identified. In the third search round, we looked
into the personal webpages of every author whom we had already included in our
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript that we had missed in the two former
queries. All papers we found in the last search had already been included in
our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March 2021.
Table \ref{tab:papers} contains the full list of articles we analyse in this
paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
a percentage of GDP.}
\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
design.}
\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference
designs such as instrumental variables and regression discontinuity models to
test the relationship between house size and public spending.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original definition of the "law of $1/n$"
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`). 
These six variables formed a $3 \times 3$ table, yet not all combinations were
available in the data. We found no studies that correlate public expenditure
per capita with either upper chamber size or the natural logarithm of lower
house size. Thus, our meta-analysis contains seven of the nine possible
variable combinations.

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
added only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

\vspace{.5cm}

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
aux$`Independent Variables` <- recode(aux$`Independent Variables`,
                                      `N` = "Lower Chamber Size",
                                      `K` = "Upper Chamber Size",
                                      `logN` = "Log of Lower Chamber Size")
aux$`Electoral system` <- recode(aux$`Electoral system`,
                                 `Non-Maj` = "Non-Majoritarian",
                                 `Maj` = "Majoritarian")
aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive statistics of moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets in their models,
and almost all papers fit more than one regression with similar variables, what
suggests that the assumption above does not hold. We use two procedures to tackle this
problem. First, we created two sets of study coefficients to reduce the impact
of multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
articles analysed two dependent or independent variables of
interest\footnote{The papers that used more than one dependent or independent
variable of interest are \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are very similar when we use the extended
set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency and improving
the accuracy of the results. More information about the multilevel models can
be found in Section H of the Supplementary Material.

We use Hedges' $g$ to calculate effect sizes in our meta-analysis
[@hedges1981distribution]. While there are other methods to standardise
coefficients in meta-analytic studies, Hedges' $g$ corrects for upward bias in
small sample sizes and is considered more robust than measures such as Cohen's
$d$ [@lakens2013calculating]. We estimate the Standardised Mean Difference
(SMD), which represents the effect size in each study relative to the
variability observed in that study, by extracting the coefficients and the
standard errors from all articles included in our sample and converting them to
Hedges' $g$. In cases where authors did not report the standard errors for
their estimates, we computed them using the t-statistic presented in the
original tables.

# Results

The "law of $1/n$" states that more legislators increase government
expenditure. In this paper, we employ three methods to test the empirical
validity of that relationship. First, we run binomial z-tests to assess the
frequency of positive and negative coefficients in our sample. Then, we fit 9
multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
Lastly, we run two sets of meta-regressions to measure the effects of a group
of moderators on the effect sizes of our study sample. To recapitulate, our
independent variables of interest are lower chamber size, the natural logarithm
of lower chamber size, and upper chamber size. The dependent variables are
public expenditure per capita, the natural logarithm of public expenditure per
capita, and government expenditure as a percentage of GDP. Since the outcomes
have different scales, we treat them separately in our models.

```{r, cache=TRUE, echo = FALSE}
aux <- filter(dat, indepvar2 == "N")
binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux <- filter(dat, indepvar2=='K')
binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux <- filter(dat, indepvar2 == "logN")
binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
```

## Binomial Z-Tests
\label{sub:binomial}

The binomial z-test evaluates whether the majority of the coefficients of our
independent variables are positive or negative[^binomial]. If increasing the
number of legislators leads to higher public expending, we should expect most
coefficients to be positive. Conversely, if the "reverse law of $1/n" is true,
our results should indicate that $p < 0.5$, that is, the proportion of positive
coefficients is lower than 0.5. The null hypothesis here states that the sign
of the coefficient is equally likely to be positive or negative.

[^binomial]: Since coefficients are either positive or negative, each of them
can be considered a Bernoulli trial. Thus, the aggregate results for all papers
follow a Binomial distribution where parameters $n$ equals the number of papers
and $p$ is the chance of a positive coefficient. The "law of $1/n$" can be
reformulated as the chance of $p > 0.5$, which facilitates the testing of the
theory.

We start with lower house size. Our results indicate that there is no
correlation between the number of legislators in the lower house and public
expenditure (successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`], $p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for the natural logarithm of lower
chamber size also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house, which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

## Meta-Analysis
\label{sub:Meta-Analysis}

```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
mod <- list()
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod[[1]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[2]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod[[3]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod[[4]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[5]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod[[6]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod[[7]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Full model - Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[8]] <- metagen(coef, SE, data = aux,
          studlab = paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm = "SMD")

# Full data - Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[9]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
```

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in the
article pool. Our sample does not contain any papers that analyse the
relationships between the log lower chamber size and public expenditure per
capita, or between upper chamber size and the logarithm of public expenditure
per capita. We calculated the effect sizes by drawing the coefficients and
standard errors from the articles and computing Hedges' $g$, which is a widely
used measure of standardised difference between means. When standard errors
were not directly available in the texts, we used t-statistics to retrieve
them.

Figure \ref{fig:plots} shows the forest plots for our restricted sample, which
includes the `r dim(dat)[1]` main coefficients of the `r length(unique(dat$id))`
selected papers.\footnote{Please refer to Sections H and I in the Supplementary
Material for full results regarding both samples.} On the left side of the
plots are the names of the study authors and paper publication year. For
unpublished studies, we included the first year the paper was available online.
The bars in the middle show the reported effect sizes and the vertical lines
indicate their average, weighted by standard errors. The length of the lines
represent the precision of the estimates. The red line at the bottom of the
figures displays the overall effects plus their respective confidence
intervals.

\begin{landscape}
\begin{figure}[!ht]
\centering
\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
\vspace{0.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{figure}
\end{landscape}

The uppermost row shows the results for lower chamber size in our restricted
sample. In the first model, which correlates lower house and expenditure per
capita, we find a standardised mean difference (SMD) of 0.022 and a standard
error of 0.131 (studies = `r mod[[1]]$k`, 95\% CI = [-0.256; 0.299], $p$-value
= 0.87), so we cannot rule that the effect is different from zero. Indeed, the
effect of lower chamber size on the other two dependent variables is also null
in statistical terms. When we compare lower chamber size with log expenditure
per capita, the overall effect size is -0.031 and the standard error is 0.049
(studies = `r mod[[3]]$k`, 95\% CI = [-0.188; 0.127], $p$-value = 0.58), and
the impact of larger lower houses on government spending as a percentage of GDP
is also negligible (studies = `r mod[[5]]$k`, SMD = - 0.006, 95\% CI =
[-0.0334; 0.021], $p$-value = 0.563). The results are virtually identical when
we estimate the meta-analyses using our extended sample, and the all three
coefficients are again statistically indistinguishable from zero.

Next, we present the meta-analyses using the logarithm of lower house size as
an independent variable. The relationship between this variable and the log of
per capita expenditure is positive, but the coefficient is not significant
(studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI = [-0.225; 0.381],
$p$-value = 0.515. The effect of log lower house size on expenditure as a
percentage of the GDP is very similar, although the SMD is negative (studies =
`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = 
`r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`;
`r round(mod[[6]]$upper.random,3)`], $p$-value = 
`r round(mod[[6]]$pval.random,3)`). Results in the full sample are also null, and
the coefficients for each dependent variable have the same sign as the
restricted sample -- positive and negative, respectively.

The third set of models uses upper house size as the main independent variable.
We find a positive correlation between this variable and expenditure per capita
(studies = `r mod[[2]]$k`, SMD = 3.658, SE = 4.299, 95\% CI = [-6.255; 13.572],
$p$-value = 0.419), and a negative relationship with government spending as a
percentage of GDP (studies = `r mod[[7]]$k`, SMD = 
`r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI =
[`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`],
$p$-value = `r round(mod[[7]]$pval.random,3)`), yet neither coefficient is
statistically significant. Results are the same in our extended sample.

Taken together, these results yield conservative interpretations. Besides all
average effect sizes not reaching conventional levels of statistical
significance, the studies are also notably heterogeneous. The $I^2$ statistic
quantifies the degree of heterogeneity among studies. @higgins2019cochrane
consider any $I^2$ value above 75\% to indicate high heterogeneity, and the
lowest $I^2$ we find in the restricted sample is `r round(mod[[2]]$I2*100,
2)`\% (for the subset of upper chamber size and per capita expenditure).
Additionally, all prediction intervals encompass zero. Therefore, we cannot
reject the null hypothesis that the effect size is zero in any variable
combination.

In a nutshell, we do not find evidence in favour of the "law of $1/n$".
One reason for this may be the identification strategy authors use in their
models. On the one hand, OLS and panel data models require too many controls to
make units comparable, and they are vulnerable to omitted variable bias or
post-treatment bias [@cinelli2020making; @pearl2015conditioning]. On the other
hand, estimation methods such as instrumental variables (IV) and regression
discontinuity designs (RDD) have become popular because of their high internal
validity [@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated
effects for two sets of models that employ causal estimation techniques. They
measure the impact of lower house size on expenditure per capita (left) and on
the natural logarithm of expenditure per capita (right).

\vspace{.5cm}

\begin{figure}[htb]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

Papers that employ instrumental variables and panel/fixed-effects models show
somewhat symmetrical distributions. Out of the five papers listed under IV, two
are positive, two are negative, and one is null. In the plot for panel data,
although more studies accumulate negative coefficients, the positive shifts are
more pronounced, so the overall effect is also null. In contrast, all papers
that use regression discontinuity designs show negative and statistically
significant results. Since only three papers in our sample use RDDs, we are
cautious about predicting an overall negative relationship, but they do
indicate that better identification strategies yield a zero-to-negative impact
of legislature size on expenditure, in support of the "reverse law of $1/n$".

## Meta-Regressions
\label{sub:regressions}

In this section, we run a series of meta-regressions with six moderators to
account for the heterogeneity across the selected papers. The first variable
indicates whether the study uses lower chamber size, log lower chamber size, or
upper chamber size as a main explanatory variable. We include separate effect
sizes for upper and lower chamber sizes when papers analysed both. The second
variable shows the study publication year, which we included to capture
temporal variation in the study coefficients. We also add a dummy variable to
assess whether published articles report effect sizes that are higher or lower
than those from working papers. The fourth variable measures whether studies
focusing on non-majoritarian electoral systems report coefficients that are
smaller or larger than those from majoritarian countries. The fifth covariate
is a categorical variable indicating the statistical procedure used in the
original models (panel data, instrumental variables, OLS, or regression
discontinuity design). In our last variable, we separate coefficients produced
from samples of unicameral or bicameral systems, and code papers that analyse
multiple polities with different institutional designs as "mixed".

Table {tab:regressions} presents the meta-regression results for our restricted
and extended samples. Each column represents one of the three measures of
public spending we discuss in this paper, and the last one uses all
coefficients. To reduce the risk of false positives in our analyses, we use
permutation tests to calculate significance levels for the meta-regressions
\citep{higgins2004controlling}. To interpret these results, the sign of
coefficients matters the most. These meta-regression coefficients can be viewed
as representing "the effect of the moderator on the $1/n$ effect". This means
positive coefficients predict a strengthening of the $1/n$ effect, and negative
ones predict it will get weaker under that moderator category, when compared to
its reference category. Since we aggregate different types of independent
variables under the same models, the size of the effects does not accurately
translate the scale of variations.

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
res <- list()

# Aux fctns
strep <- function (x) {
  if(!is.na(x)) {
    return(ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*',''))))
  } else {
    return('')
  }
}

extract_coefs <- function(mod, modnam) {
  dfr <- data.frame(
     nams2 = row.names(mod[["beta"]]),
     est = mod[["beta"]],
     se = mod[["se"]],
     pval = mod[["pval"]],
     model = modnam
  )
  aux <- data.frame(nams = c("Intercept",
             "Indepvar: logN",
             "Indepvar: N",
             "Year",
             "Published",
             "Elecsys: Non-Majoritarian",
             "Method: Panel",
             "Method: IV",
             "Method: RDD",
             "Legislature: Mixed",
             "Legislature: Unicameral"), 
             nams2 = c("intrcpt", 
                       "indepvar2logN", 
                       "indepvar2N", 
                       "year", 
                       "publishedYes", 
                       "elecsys2Non-Maj", 
                       "methodPANEL", 
                       "methodIV", 
                       "methodRDD",
                       "instdesignMixed",
                       "instdesignUnicameral"))
  dfr <- left_join(aux, dfr) %>%
    mutate_if(is.numeric, list(~round(., digits = 4)))
  dfr$nams2 <- NULL
  return(dfr)
}

gcf <- function(mod, pos) {
  x <- mod$est[pos]
  y <- mod$pval[pos]
  if(!is.na(x)) {
    return(paste0(format(round(x, digits = 3), nsmall = 3), strep(y)))
  } else {
    return('')
  }
}
gcf2 <- function(mod, pos) {
  x <- mod$se[pos]
  if(!is.na(x)) {
    return(paste0('(', format(round(x, digits = 3), nsmall = 3), ')'))
  } else {
    return('')
  }
}

# Expenditure per capita - Restricted
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              sparse = TRUE,
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

res[[1]] <- extract_coefs(mod, "ExpPC")

# Expenditure per capita - Extended
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")

# Log of Expenditure per capita - Restricted
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)

res[[3]] <- extract_coefs(mod, "logExpPC")

# Log of Expenditure per capita - Extended
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")

## Expenditure as percentage GDP -- Restricted
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

res[[5]] <- extract_coefs(mod, "PCTGDP")

## Expenditure as percentage GDP -- Extended
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

res[[6]] <- extract_coefs(mod, "PCTGDP - All coefs")

mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = dat$authoryear)

res[[7]] <- extract_coefs(mod, "Full Model")

mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = fulldat$authoryear)

res[[8]] <- extract_coefs(mod, "Full Model - All coefs")
```

\vspace{0.5cm}

```{=latex}
\begin{table}[htpb]
\caption{Meta Regression Results\label{tabregressions}}
\scriptsize
\centering
\begin{tabular}{lcccccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{All Coefficients} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
& Restricted & Extended & Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Log of Lower Chamber Size & 
`r gcf(res[[1]], 2)` & `r gcf(res[[2]], 2)` & 
`r gcf(res[[3]], 2)` & `r gcf(res[[4]], 2)` & 
`r gcf(res[[5]], 2)` & `r gcf(res[[6]], 2)` &
`r gcf(res[[7]], 2)` & `r gcf(res[[8]], 2)` \\
 & `r gcf2(res[[1]], 2)` & `r gcf2(res[[2]], 2)` & 
`r gcf2(res[[3]], 2)` & `r gcf2(res[[4]], 2)` & 
`r gcf2(res[[5]], 2)` & `r gcf2(res[[6]], 2)` & 
`r gcf2(res[[7]], 2)` & `r gcf2(res[[8]], 2)` \\
%
Lower Chamber Size &
`r gcf(res[[1]], 3)` & `r gcf(res[[2]], 3)` & 
`r gcf(res[[3]], 3)` & `r gcf(res[[4]], 3)` & 
`r gcf(res[[5]], 3)` & `r gcf(res[[6]], 3)` &
`r gcf(res[[7]], 3)` & `r gcf(res[[8]], 3)` \\
 & `r gcf2(res[[1]], 3)` & `r gcf2(res[[2]], 3)` & 
`r gcf2(res[[3]], 3)` & `r gcf2(res[[4]], 3)` & 
`r gcf2(res[[5]], 3)` & `r gcf2(res[[6]], 3)` & 
`r gcf2(res[[7]], 3)` & `r gcf2(res[[8]], 3)` \\
%
Year & 
`r gcf(res[[1]], 4)` & `r gcf(res[[2]], 4)` & 
`r gcf(res[[3]], 4)` & `r gcf(res[[4]], 4)` & 
`r gcf(res[[5]], 4)` & `r gcf(res[[6]], 4)` &
`r gcf(res[[7]], 4)` & `r gcf(res[[8]], 4)` \\
& `r gcf2(res[[1]], 4)` & `r gcf2(res[[2]], 4)` & 
`r gcf2(res[[3]], 4)` & `r gcf2(res[[4]], 4)` & 
`r gcf2(res[[5]], 4)` & `r gcf2(res[[6]], 4)` & 
`r gcf2(res[[7]], 4)` & `r gcf2(res[[8]], 4)` \\
%
Non-Majoritarian & 
`r gcf(res[[1]], 5)` & `r gcf(res[[2]], 5)` & 
`r gcf(res[[3]], 5)` & `r gcf(res[[4]], 5)` & 
`r gcf(res[[5]], 5)` & `r gcf(res[[6]], 5)` &
`r gcf(res[[7]], 5)` & `r gcf(res[[8]], 5)` \\
& `r gcf2(res[[1]], 5)` & `r gcf2(res[[2]], 5)` & 
`r gcf2(res[[3]], 5)` & `r gcf2(res[[4]], 5)` & 
`r gcf2(res[[5]], 5)` & `r gcf2(res[[6]], 5)` & 
`r gcf2(res[[7]], 5)` & `r gcf2(res[[8]], 5)` \\
%
Published: Yes & 
`r gcf(res[[1]], 6)` & `r gcf(res[[2]], 6)` & 
`r gcf(res[[3]], 6)` & `r gcf(res[[4]], 6)` & 
`r gcf(res[[5]], 6)` & `r gcf(res[[6]], 6)` &
`r gcf(res[[7]], 6)` & `r gcf(res[[8]], 6)` \\
& `r gcf2(res[[1]], 6)` & `r gcf2(res[[2]], 6)` & 
`r gcf2(res[[3]], 6)` & `r gcf2(res[[4]], 6)` & 
`r gcf2(res[[5]], 6)` & `r gcf2(res[[6]], 6)` & 
`r gcf2(res[[7]], 6)` & `r gcf2(res[[8]], 6)` \\
%
Method: Panel & 
`r gcf(res[[1]], 7)` & `r gcf(res[[2]], 7)` & 
`r gcf(res[[3]], 7)` & `r gcf(res[[4]], 7)` & 
`r gcf(res[[5]], 7)` & `r gcf(res[[6]], 7)` &
`r gcf(res[[7]], 7)` & `r gcf(res[[8]], 7)` \\
& `r gcf2(res[[1]], 7)` & `r gcf2(res[[2]], 7)` & 
`r gcf2(res[[3]], 7)` & `r gcf2(res[[4]], 7)` & 
`r gcf2(res[[5]], 7)` & `r gcf2(res[[6]], 7)` & 
`r gcf2(res[[7]], 7)` & `r gcf2(res[[8]], 7)` \\
%
Method: IV & 
`r gcf(res[[1]], 8)` & `r gcf(res[[2]], 8)` & 
`r gcf(res[[3]], 8)` & `r gcf(res[[4]], 8)` & 
`r gcf(res[[5]], 8)` & `r gcf(res[[6]], 8)` &
`r gcf(res[[7]], 8)` & `r gcf(res[[8]], 8)` \\
& `r gcf2(res[[1]], 8)` & `r gcf2(res[[2]], 8)` & 
`r gcf2(res[[3]], 8)` & `r gcf2(res[[4]], 8)` & 
`r gcf2(res[[5]], 8)` & `r gcf2(res[[6]], 8)` & 
`r gcf2(res[[7]], 8)` & `r gcf2(res[[8]], 8)` \\
%
Method: RDD &
`r gcf(res[[1]], 9)` & `r gcf(res[[2]], 9)` & 
`r gcf(res[[3]], 9)` & `r gcf(res[[4]], 9)` & 
`r gcf(res[[5]], 9)` & `r gcf(res[[6]], 9)` &
`r gcf(res[[7]], 9)` & `r gcf(res[[8]], 9)` \\
& `r gcf2(res[[1]], 9)` & `r gcf2(res[[2]], 9)` & 
`r gcf2(res[[3]], 9)` & `r gcf2(res[[4]], 9)` & 
`r gcf2(res[[5]], 9)` & `r gcf2(res[[6]], 9)` & 
`r gcf2(res[[7]], 9)` & `r gcf2(res[[8]], 9)` \\
% 
Inst. Design: Mixed & 
`r gcf(res[[1]], 10)` & `r gcf(res[[2]], 10)` & 
`r gcf(res[[3]], 10)` & `r gcf(res[[4]], 10)` & 
`r gcf(res[[5]], 10)` & `r gcf(res[[6]], 10)` &
`r gcf(res[[7]], 10)` & `r gcf(res[[8]], 10)` \\
& `r gcf2(res[[1]], 10)` & `r gcf2(res[[2]], 10)` & 
`r gcf2(res[[3]], 10)` & `r gcf2(res[[4]], 10)` & 
`r gcf2(res[[5]], 10)` & `r gcf2(res[[6]], 10)` & 
`r gcf2(res[[7]], 10)` & `r gcf2(res[[8]], 10)` \\
% 
Inst. Design: Unicameral & 
`r gcf(res[[1]], 11)` & `r gcf(res[[2]], 11)` & 
`r gcf(res[[3]], 11)` & `r gcf(res[[4]], 11)` & 
`r gcf(res[[5]], 11)` & `r gcf(res[[6]], 11)` &
`r gcf(res[[7]], 11)` & `r gcf(res[[8]], 11)` \\
& `r gcf2(res[[1]], 11)` & `r gcf2(res[[2]], 11)` & 
`r gcf2(res[[3]], 11)` & `r gcf2(res[[4]], 11)` & 
`r gcf2(res[[5]], 11)` & `r gcf2(res[[6]], 11)` & 
`r gcf2(res[[7]], 11)` & `r gcf2(res[[8]], 11)` \\
% 
Intercept & 
`r gcf(res[[1]], 1)` & `r gcf(res[[2]], 1)` & 
`r gcf(res[[3]], 1)` & `r gcf(res[[4]], 1)` & 
`r gcf(res[[5]], 1)` & `r gcf(res[[6]], 1)` &
`r gcf(res[[7]], 1)` & `r gcf(res[[8]], 1)` \\
& `r gcf2(res[[1]], 1)` & `r gcf2(res[[2]], 1)` & 
`r gcf2(res[[3]], 1)` & `r gcf2(res[[4]], 1)` & 
`r gcf2(res[[5]], 1)` & `r gcf2(res[[6]], 1)` & 
`r gcf2(res[[7]], 1)` & `r gcf2(res[[8]], 1)` \\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable: Upper House Size; Published $= No$; Non-Majoritarian; Method $= OLS$, Inst. Design $= Bicameral$. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$. Blank cells mean that there is no sufficient data to estimate the paramater.}}
\end{minipage}
\end{table}
```

\vspace{0.5cm}

The first two models show the results for public expenditure per capita. No
variable reaches conventional levels of statistical significance in the
restricted sample. In the extended sample, we find that models that use lower
chamber size as an independent variable have lower effects when compared to
upper chamber size. This suggests that an additional member in the lower house
has a smaller impact on public spending than a member in the upper house.
Moreover, the results for the extended sample point out that recent studies
find larger effects than older ones.

The third and fourth columns use the natural logarithm of expenditure per
capita as the dependent variable. Among the coefficients in the restricted
sample, those in published studies are significantly smaller than those in
working papers. Another two moderators are negatively associated with the
outcome in our larger study pool. They both refer to estimation methods.
Studies that employ panel/fixed effects or regression discontinuity designs
(RDDs) have lower coefficients for log expenditure per capita if we take OLS as
the reference category.

Three variables are statistically significant in the third set of
meta-regressions, which include public expenditure as a percentage of GDP as
the dependent variable. Both in our restricted and in our extended samples,
recent studies have smaller coefficients than older papers, which stands in
contrast with our previous models. Moreover, institutional design also affects
outcomes. Papers that use mixed samples of bicameral and unicameral systems
report significantly lower coefficients than those that analyse bicameral
legislatures exclusively. Non-majoritarian electoral systems are also
associated with lower levels of public spending, which may be justified since
the "law of $1/n$" was conceived for majoritarian voting. These latter results,
however, do not replicate in the first set of estimations.

The last two columns report meta-regressions that aggregate all selected
studies. In the restricted sample of coefficients, unicameralism has a
pro-$1/n$ effect. This strongly supports the theory's original formulation, as
most unicameral occurrences are local governments, for which the "law" was
originally conceived. This result holds for the extended sample as well. When
we regress all `r dim(fulldat)[1]` coefficients, the effects of estimation
methods become stronger once again. Panel/fixed-effects models and regression
discontinuity designs both decrease the $1/n$ effect at the .1\% significance
level. Instrumental variable models follow along these lines. Additionally,
non-majoritarian voting constituencies appear once again as settings where the
law of $1/n$ becomes weaker.

The evidence seems to be sensitive to the methodological design. Our results
suggest that the same study samples may produce different outcomes depending on
the response variables scholars decide to analyse. The broadest aggregation
level presented the most insightful results in dialogue with the literature.
The additional legislator in non-majoritarian legislatures does not increase
expenditure as much as she would if the system were majoritarian. We are also
more likely to witness legislative expenditure growing along with the amount of
representatives in unicameral legislatures rather than in bicameral systems.
This indicates that while the law of $1/n$ is not generalisable, its predicted
effects are stronger when the institutional features of a polity come closer to
its original theoretical framework.

# Discussion
\label{sec:discussion}

In this letter, we assess the empirical validity of the "law of $1/n$". Based
on a sample of `r length(unique(dat$id))` publications on the topic, our
meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. If such
effect exists, it is likely driven by an increase in $k$, the size of the upper
legislature, as suggested by several studies in the literature
[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
better evidence for the "reverse law of $1/n$", which posits that larger
legislatures lead to lower government spending. This is mainly because studies
using regression discontinuity designs, a method that has robust internal
validity, consistently indicate a negative relationship between lower house size
and the logarithm of expenditure per capita [@hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size].

The meta-regressions show that study characteristics have a considerable
influence on reported results. Electoral system affects the relationship
between legislature size and public expenditure, but the results are not
replicable in all estimations. Publication year generates conflicting findings
in our models. Nevertheless, the meta-regressions confirm that RDDs produce
negative effects more frequently than OLS regressions.

Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
plausible reason may be that there are few incentives for the pure accumulation
of knowledge in the social sciences, at least when compared to the benefits
scholars may accrue when they challenge or add features to existing theories
[@geddes2003paradigms]. This leads to a reduced number of replication studies in
the field, although we have seen some positive changes in this respect, such as
EGAP's _Metaketa Initiative_.\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.} For instance, in our sample, papers added supermajority rules
[@lee2015supermajority; @lee2016supermajority], redistricting
[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
bicameralism [@ricciuti2004legislature], and the interplay between upper and
lower houses [@chen2007law] to the main theory, but a comprehensive
procedural replication of the findings using different samples is yet to be
written. The addition of new features has the benefit of enriching the original
theory with useful details, although it has the disadvantage of not providing a
conclusive test to the "law of $1/n$".

Our analyses suggest three areas for further research. First, our study
sample did not include articles that evaluate the association between the
log($n$) and public expenditure per capita or between $k$ and log expenditure
per capita. New work on that area might clarify some of the inconsistencies we
find here. Second, despite the inclusion of several moderators in our models,
aggregate results still show considerable heterogeneity. Domestic factors such
as party dynamics or gerrymandering [@lee2015supermajority;
@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
regard. Finally, we highlight the need for more causal inference studies in the
literature. Whenever possible, authors should leverage natural and
quasi-experiments to assess whether the current results hold when tested with
such research designs. These suggestions may help scholars and policy-makers to
reach an optimal balance between sound fiscal policy and the demands for
increased political representation.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
erler2007termlimits, fiorino2007legislature, hohmann2017effect,
kessler2014communication, lewis2019legislature, lledo2003electoral,
mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
matsusaka2005endogeneity, ricciuti2004legislatures}

### 2021-08-04 appendix/appendix.Rmd
changes article and appendix - adding model 1

@@
 title: |
-       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
+       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
 author:
-- "Huzeyfe Alptekin[^alptekin]"
-- "Danilo Freire[^freire]"
-- "Umberto Mignozzetti[^mignozzetti]"
-- "Catarina Roman[^roman]"
+  - Umberto Mignozzetti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
 date: \today
@@
 
-[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.
-
-[^freire]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
-
-[^roman]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
+
+[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
 
 \appendix
+\addtocounter{section}{2}
 
@@
 ## Starting
-set.seed(732578) # From random.org
+XXXX
 
 # Required packages
-pkgs <- c("tidyverse", "meta", "metafor",
-          "readxl", "devtools", "data.table",
-          "knitr", "gridGraphics", "gridExtra",
-          "ggpubr", "kableExtra", "magick",
-          'stargazer', 'pander', 'broom')
-
-# Install if not already installed
-install <- function(x) {
-  if (x %in% rownames(installed.packages()) == FALSE)
-    install.packages(x, dependencies = T,
-                     repos = "http://cran.us.r-project.org")
+XXXX
+
+# Load datasets
+XXXX
+```
+
+\newpage
+
+\subsection{A Model of Legislature Size and Service Provision}
+
+Consider an strategic interaction comprised of a mayor ($M$), and $N \geq 3$ of city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
+The mayor is head of the local Executive, and has the prerogative of proposing a vector of policies, that is voted by the city councilors.
+The policy proposal, if accepted, is implemented.
+
+Every city councilor has a party affiliation, and the party label may or may not match the mayor's affiliation.
+If the politician shares the same party as the mayor, we say that it belongs to the government coalition ($G \subset \{1, 2, \cdots, N \}$).
+Otherwise, we assume that the politician belongs to the opposition $O \not\subset G$.
+The party affiliation is important because it provides a political benefit or cost for the councilor.
+If the mayor implements the policy, then a councilor aligned with the mayor receives a policy benefit $p > 0$.
+If the politician belongs to the opposition, then the mayoral policies impose her a cost of $-p$.
+For simplicity, we assume that these costs are symmetric.
+
+However, if the mayor's policy proposal lose majoritarian support from the council, then we assume that a reversal policy takes place, where the resources diminish by a factor of $\delta \in (0,1)$, and a random councilor is recognized to make a proposal.\footnote{In a model similar to [Baron Ferejohn / Cliff XXXX].} The councilor proposes the new policy vector, and the council votes.
+If the policy is rejected, then another councilor is recognized to make the offer, and this goes on until one offer is finally accepted by the majority of the legislators.
+For simplicity, we assume that the councilor's offers generate no political benefits or costs, so that if a councilor proposes the policy vector, then $p=0$.
+This may sound restrictive, but we will show that councilors propose zero public goods in equilibrium, as they have only to please their particularistic constituencies to get reelected.
+
+To convince the councilors, the politician making the proposal has three vectors of policies at her disposal.
+First, the proposer may give targeted goods for the councilor $i$ that she is trying to earn support, $t_i \geq 0$.
+These targeted goods improve the reelection rates of the councilor.
+Second, the proposer may also give private goods $x_i \geq 0$ to a councilor $i$.
+Private goods do not affect the reelection rates of the politicians, but provide instant benefits for the receiver.
+Finally, the proposer can provide public goods $g \geq 0$.
+Public goods help the mayor to get reelected, and also affect the policy benefits received by the politicians, depending on the party affiliation.
+
+For the mayor, the expected utility function is a sum of the utility from rents and benefits from reelection.
+Both the utilities from rents ($u(r)$) and the probability of getting reelected $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
+The probability of getting reelected is also multiplied by the benefit from holding office $B_M > 0$.
+This term captures the tangible and intangible gains that the mayor perceives from being reelected into the position.
+The utility is multiplied by an indicator $\mathbb{I}$ that captures whether the mayor's proposal was accepted by the city council.\footnote{The indicator function is defined as
+\[
+I(condition) \ = \ \twopdo{1}{\text{Condition is satisfied.}}{0}.
+\]
+} The expected utility for the mayor is:
+
+\[
+\mathbb{E}U(r, g, \bf{x}, \bf{t}) \ = \ \mathbb{I}(\text{Approval})(u(r) + B_M\pi(g))
+\]
+
+And the mayor chooses the optimal policy subject to a budget constraint.
+The municipality has $R$ resources, and we assume that the municipality cannot run debts.
+This budget balance constraint requires the policy vector $(r, g, \bf{x}, \bf{t})$ to satisfy the following rule:
+
+\[
+r + g + \sum_{i=1}^{N}t_i + \sum_{i=1}^{N} x_i \ \leq \ \delta^kR
+\]
+
+And the mayor's proposal happens when $k=0$.
+This makes mayoral budget inequality to satisfy: $r + g + \sum_{i=1}^{N}t_i + \sum_{i=1}^{N} x_i \ \leq \ R$.
+Otherwise, in the reversal proposals, the resources diminish by a $\delta^k$ rate, with $k$ being the number of unsuccessful offers by the councilors.
+
+We can decompose the councilor's utility function into three major components.
+First, the political gains or losses (depending on the councilor's party affiliation); second, the rents $x_i$ offered by the policy proposer to the councilor; and finally, the transfers for the constituents $t_i$, offered by the policy proposer to the councilor.
+As the constituent transfer $t_i$ affects chance of winning the election $\pi_C(t_i)$, we multiply this chance by the benefits accrued from remaining in office, $B > 0$.
+Again, as in the mayor's case, the utility is only realized when the city council accepts the policy proposed, so that we multiply the approval indicator $\mathbb{I}(.)$.
+The councilor's expected utility is equal to:
+
+\[
+\mathbb{E}U(r, g, \bf{x}, \bf{t}) \ = \  \mathbb{I}(\text{Approval})((-1)^{\mathbb{I}(i \in O)}p + x_i + B\pi_C(t_i))
+\]
+
+For simplicity, we assume that the councilor's probability of reelection satisfy a simple cutoff rule:
+
+\[
+\pi_C(t_i) \ = \ \twopdo{1}{t_i \geq \underline{t}}{0}
+\]
+
+This assumption simplifies the calculations, and it is reasonable as many models have the voter's decision as a cutoff strategy [@XXXX].
+We also assume, for convenience, that $B > \underline{t}$.
+Otherwise, the councilor would prefer to pocket the targeted goods, and not being reelected.
+
+The timeline of the game is as follows:
+
+1. The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
+2. The mayor proposes a policy vector $(r, g, \bf{x}, \bf{t})_M$.
+3. The city council votes the proposal.
+  - If the council accepts, then the policy is implemented, and the game ends. 
+  - Otherwise, the reversal policy is implemented.
+4.
+(Reversal Policy) At the beginning of each iteration of the reversal policy, one councilor is randomly recognized to be the proposer.
+She proposes a vector $(\bf{x}, \bf{t})$, with $r =  g = 0$.
+If the proposal is accepted, it is implemented.
+If the proposal is rejected, a new round of reversal start, but with the municipal resources reduced by a factor $\delta$.
+
+We solve the game for a Sub-game Perfect Nash Equilibrium using backward induction.
+Although the game tree may extend infinitely, a Stationary Sub-game Perfect Equilibrium can be reached with no delay in the policy implementation, and the mayoral proposal being successful.
+
+\begin{definition}
+The solution for the game consists in a pair of XXXX.
+\end{definition}
+
+Solving by backward induction, suppose that there were $k$ prior rejections, and the municipal resources shrank by $\delta^{k}R$.
+As at this stage the politicians are similar with regard to political affiliation, we can drop the party label.\footnote{In the extensions, we solve the game assuming that the distribution remained partisan even for the councilors.
+The results are similar, with the only difference that when partisanship is relevant for councilors, the expected provision of public goods is higher than zero.} A given councilor is recognized as the proposer with $1/N$ probability.
+The recognized councilor has to convince at least one-half of the council members to agree with her policy proposal.
+Therefore, a legislator $i$, that receives an offer from a proposer ($x_i, t_i$), at round $k$, will accept the offer if it is at least as good as waiting for the next round.
+
+\[
+x_i + B\pi_C(t_i) \ \geq \ \dfrac{1}{N}\left[\delta^{k+1}R - \dfrac{N}{2}(x_{-i} + t_{-i}) + B\pi_C(t_i)\right] + \dfrac{1}{2}(x_i + B\pi_C(t_i))
+\]
+
+At the $k$-th stage, the players are equivalent.
+Therefore, the offer $x_i, t_i$, and the offer for the other players, ($x_{-i} + t_{-i}$), are the same.
+Moreover, as $B > \underline{t}$, $t^* = t_i = t_{-i} = \underline{t}$, and the offer that would make legislator $i$ accept without further delay is:
+
+\[
+x + B \ \geq \ \dfrac{1}{N}\left(\delta^{k+1}R - \dfrac{N}{2}(x + \underline{t}) + B\right) + \dfrac{1}{2}(x + B)
+\]
+
+And after some algebra, the optimal private goods offer has to satisfy:
+
+\[
+x \geq \dfrac{1}{N}\left( \delta^{k+1}R + B \right) - \dfrac{1}{2}(B + \underline{t}) \equiv \underline{x}(k)
+\]
+
+For all $k \in \{1, 2, \cdots, \infty\}$.
+
+\begin{lemma}
+Suppose that the council rejected the mayor's offer.
+Then, at the $k$-th stage of the game, the proposer will offer $t^* = \underline{t}$ and $x^* = \underline{x}(k)$ for half of the members, keeping for her $t_i = \max\{0, \underline{t}\}$, and
+
+\[
+x_i \ = \ R\delta^k\left( 1 - \dfrac{\delta}{2} \right) + \dfrac{N}{4}(B-\underline{t}) + \dfrac{B}{2}
+\]
+
+Subject to the budget constraint:
+
+\[
+\dfrac{N}{2}\left(\underline{t}+\underline{x}(k)\right) + x_i  \ \leq \ \delta^kR
+\]
+
+The sequence of strategies derived here are an equilibrium for all $k \in \{1, 2, \cdots, \infty\}$.
+
+\end{lemma}
+
+\begin{proof}
+The proof is direct, after collecting the terms from the previous discussion.
+
+Note that after some iterations, the budget may shrink enough so that $t^* = \underline{t}$ is unfeasible.
+This means that there exists a $k^*$ such that, when $k > k^*$, $t^* = 0$, and the councilors divide the remaining budget as rents.
+This case is trivial to solve, making $\underline{x}(k) = \dfrac{1}{N}\left(\delta^{k+1}R\right)$ and $x_i = \delta^kR\left(1 - \dfrac{\delta}{2}\right)$.
+\end{proof}
+
+We now have the entire strategy profile for the city councilors, provided that they reject the initial mayor's proposal.
+Proceeding by backward induction, we need to find the mayor's proposal that will win the support of the majority of the council.
+As the mayor is the proposer, policy concerns come into play, and the offer for a government aligned councilor will be different from the offer for an opposition councilor.
+For a government aligned councilor, assuming that the councilor is the pivotal players, the accepted offer has to be better than rejecting the proposal and waiting for the next round:
+
+\[
+p + x_i + B\pi_C(t_i) \ \geq \ \dfrac{1}{N}\left(\right) + \dfrac{1}{2}(x_i + B\pi_C(t_i))
+\]
+
+.
+
+\newpage
+
+\subsection{Variable Sources and Descriptive Statistics\label{appsources}}
+
+We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
+
+\begin{sidewaystable}[!htbp] \centering 
+  \caption{Data Sources} 
+  \label{varsources}
+  \scalebox{0.75}{
+\begin{tabular}{@{\extracolsep{5pt}}llll} 
+\\[-1.8ex]\hline\hline \\[-1.8ex] 
+Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
+\hline \\[-1.8ex] 
+& & & \\
+DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
+& & & \\
+IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
+& & & \\
+INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
+& & & \\
+InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
+& & & \\
+IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
+& & & \\
+MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
+& & & \\
+TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
+& & & \\
+\hline\hline \\[-1.8ex] 
+\end{tabular} 
 }
-lapply(pkgs, install)
-devtools::install_github("isubirana/compareGroups")
-devtools::install_github("MathiasHarrer/dmetar")
-
-# Load packages
-lapply(pkgs, require, character.only = T)
-library("compareGroups"); library(dmetar)
-
-# Broom the multi-level model
-broom_mod <- function(mod, subgroup = FALSE) {
-  aux <- data.frame(predict(mod))
-  if (subgroup) {
-    teeff = aux$pred
-    seteeff = aux$se
-    labeff = c("Subgroup Effect")
-    loeff = c(aux$ci.lb)
-    upeff = c(aux$ci.ub)
-  } else {
-    teeff = c(aux$pred, NA)
-    seteeff = c(aux$se, NA)
-    labeff = c("Overall Effect",
-               "Prediction Interval")
-    loeff = c(aux$ci.lb, aux$cr.lb)
-    upeff = c(aux$ci.ub, aux$cr.ub)
+\end{sidewaystable}
+
+Now let us define each variable.
+
+\textbf{Outcomes Aggregated at the Municipal Level:}
+
+\begin{itemize}
+    \item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
+    \item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
+    \item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
+    \item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
+    \item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
+    \item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+    \item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+    \item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
+    \item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
+    \item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
+    \item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
+    \item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
+IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
+The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
+    \item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality.
+IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying.
+The estimators are cleaned to avoid the influence of schools and classrooms specific effects.
+(source: INEP, years: 2005, 2007).
+    \item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
+    \item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
+    \item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality.
+Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
+    \item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
+    \item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
+    \item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council.
+We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures).
+    \item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
+    \item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
+\end{itemize}
+
+\textbf{Legislation Dataset:}
+
+We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:
+
+\begin{itemize}
+    \item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
+    \item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
+    \item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
+    \item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
+    \item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
+\end{itemize}
+
+\textbf{Online 2016 Former City Councilors Survey:}
+
+We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:
+
+\begin{itemize}
+    \item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
+    \item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
+\end{itemize}
+
+In this Appendix, we present other questions we asked in the survey.
+They are meant to improve the knowledge we have about the city councilors perceptions about their representation.
+We have not added these to the main paper because they were more complimentary and not of general interest.
+The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.
+
+\input{tabs/edited/sumstatOut2016e.tex}
+
+\newpage
+
+\subsection{Threshold Manipulation, Sorting, and Pre-treatment Consistency}
+
+The validity of our causal claim relies on three assumptions.
+First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds.
+Second, that we are consistently comparing municipalities in the same cutoffs.
+Lastly, that we have no pre-treatment differences in our sample.
+
+For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
+For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
+
+We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
+We use local polynomial orders from one to four.
+As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
+Therefore, there is no manipulation according to \citet{calonico2019regression}.
+
+We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/McCrary.pdf}}
+      \caption{\citet{McCrary2008} manipulation test}
+      \bigskip
+      \label{manipulationplot}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}.
+For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21.
+When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor.
+However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors.
+This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
+That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.
+
+To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
+Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
+The reason for the first variable is the multiple threshold assignments.
+We add GDP per capita because wealthier cities tend to be more productive and have better public services.
+The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
+The year and the northeast dummies serve to improve efficiency.
+Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.
+See the following section for further tests and simulations.
+
+For the last assumption, we should have no changes in pre-treatment covariates.
+These pre-treatment covariates are variables measured before the primary outcomes.
+As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
+
+Table \ref{validitycheck} displays the results of the validity checks.
+At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs.
+At the bottom, we estimate the pre-treatment covariate balance.
+
+\begin{table}[htb!] \centering 
+  \caption{Research Design Validity Check} 
+  \label{validitycheck} 
+    \scalebox{0.9}{
+  \begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+ & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
+   & \multicolumn{1}{c}{\small{(1)}} & 
+ \multicolumn{1}{c}{\small{(2)}} & 
+ \multicolumn{1}{c}{\small{(3)}} & 
+ \multicolumn{1}{c}{\small{(4)}} \\
+
+ & \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} & 
+ \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
+  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+\\[-1.8ex] 
+ LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
+  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
+\hdashline \\[-1.8ex]   
+ N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
+Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
+BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
+BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
+\midrule 
+ & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(5)}} & 
+ \multicolumn{1}{c}{\small{(6)}} & 
+ \multicolumn{1}{c}{\small{(7)}} & 
+ \multicolumn{1}{c}{\small{(8)}} \\
+  & \multicolumn{1}{c}{\small{Number of}} & 
+ \multicolumn{1}{c}{\small{Population}} & 
+ \multicolumn{1}{c}{\small{GDP}} & 
+ \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2000}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} &
+   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
+  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
+  \hdashline \\[-1.8ex]
+ N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
+Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
+Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
+BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
+BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
+RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
+After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
+Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
+These tests reinforce the validity of our research designs.
+
+\pagebreak
+
+\subsection{Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision\label{appidentif}}
+
+The identification strategy requires exogenous changes in the city council size thresholds.
+Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
+
+\begin{table}[htp!]
+\centering
+\caption{City council size from the 1988 Constitution}
+\scalebox{0.75}{
+\begin{tabular}{rccrrr}
+  \hline\hline
+ & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\ 
+ & & & & & \multicolumn{1}{c}{(2001-2004)} \\
+  \hline
+  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\ 
+  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\ 
+  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\ 
+   \hline\hline
+\end{tabular}
 }
-  mod2 <- tibble(
-    TE = as.numeric(mod$yi),
-    seTE = sqrt(mod$vi),
-    studlab = mod$slab,
-    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
-    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
-    group = 'A') %>%
-    bind_rows(.,
-              aux = tibble(
-                TE = teeff,
-                seTE = seteeff,
-                studlab = labeff,
-                lower = loeff,
-                upper = upeff,
-                group = "B")) %>%
-    group_by(studlab) %>%
-    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-    ungroup()
-  return(mod2)
+\label{tabcitycouncilsize1988}
+\end{table}
+
+These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors.
+The two losing councilors started a judicial contestation that made it to the Supreme Court.
+The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55.
+Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004).
+According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
+
+\begin{table}[htp!]
+\centering
+\caption{City council size thresholds according to TSE resolution 21,702/2004}
+\scalebox{0.75}{
+\begin{tabular}{rcrrr}
+  \hline\hline
+ &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
+ & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
+  \hline
+  1 &  9 & 0 & 47,619 & 5,029 \\ 
+  2 &  10 & 47,620 & 95,238 & 317 \\ 
+  3 &  11 & 95,239 & 142,857 & 89 \\ 
+  4 &  12 & 142,858 & 190,476 & 43 \\ 
+  5 &  13 & 190,477 & 238,095 & 30 \\ 
+  6 &  14 & 238,096 & 285,714 & 21 \\ 
+  7 &  15 & 285,715 & 333,333 & 13 \\ 
+  8 &  16 & 333,334 & 380,952 & 13 \\ 
+  9 &  17 & 380,953 & 428,571 & 6 \\ 
+  10  & 18 & 428,572 & 476,190 & 6 \\ 
+  11  & 19 & 476,191 & 523,809 & 4 \\ 
+  12  & 20 & 523,810 & 571,428 & 5 \\ 
+  13  & 21 & 571,429 & 1,000,000 & 13 \\ 
+  14  & 33 & 1,000,001 & 1,121,952 & 1 \\ 
+  15  & 34 & 1,121,953 & 1,243,903 & 2 \\ 
+  16  & 35 & 1,243,904 & 1,365,854 & 1 \\ 
+  17  & 36 & 1,365,855 & 1,487,805 & 2 \\ 
+  18  & 37 & 1,487,806 & 1,609,756 & 1 \\ 
+  19  & 38 & 1,609,757 & 1,731,707 & 1 \\ 
+  20  & 39 & 1,731,708 & 1,853,658 & 0 \\ 
+  21  & 40 & 1,853,659 & 1,975,609 & 0 \\ 
+  22  & 41 & 1,975,610 & 4,999,999 & 4 \\ 
+  23  & 42 & 5,000,000 & 5,119,047 & 0 \\ 
+  24  & 43 & 5,119,048 & 5,238,094 & 0 \\ 
+  25  & 44 & 5,238,095 & 5,357,141 & 0 \\ 
+  26  & 45 & 5,357,142 & 5,476,188 & 0 \\ 
+  27  & 46 & 5,476,189 & 5,595,235 & 0 \\ 
+  28  & 47 & 5,595,236 & 5,714,282 & 0 \\ 
+  29  & 48 & 5,714,283 & 5,833,329 & 0 \\ 
+  30  & 49 & 5,833,330 & 5,952,376 & 0 \\ 
+  31  & 50 & 5,952,377 & 6,071,423 & 1 \\ 
+  32  & 51 & 6,071,424 & 6,190,470 & 0 \\ 
+  33  & 52 & 6,190,471 & 6,309,517 & 0 \\ 
+  34  & 53 & 6,309,518 & 6,428,564 & 0 \\ 
+  35  & 54 & 6,428,565 & 6,547,611 & 1 \\ 
+  36  & 55 & 6,547,612 & $\infty$  & 0 \\ 
+   \hline\hline
+\end{tabular}
 }
-
-# Estimation of the 
-estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
-  if (is.null(hetvar)) {
-    stop('Hetvar should be different than null.')
+\label{tabcitycouncilsize2004all}
+\end{table}
+
+As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants.
+Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.
+
+\begin{table}[htp!]
+\centering
+\caption{City council thresholds used in the paper}
+\scalebox{0.85}{
+\renewcommand*{\arraystretch}{1.2}
+\begin{tabular}{rcrrr}
+  \hline \hline
+ & \multicolumn{1}{c}{Legislature} & \multicolumn{1}{c}{Min.} & \multicolumn{1}{c}{Max.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
+ & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{(2003 pop.)} \\
+  \hline
+  1 & 9 & 0 & 47,619 & 5,029 \\ 
+  2 & 10 & 47,620 & 95,238 & 317 \\ 
+  3 & 11 & 95,239 & 142,857 & 89 \\ 
+  4 & 12 & 142,858 & 190,476 & 43 \\ 
+  5 & 13 & 190,477 & 238,095 & 30 \\ 
+  6 & 14 & 238,096 & 285,714 & 21 \\ 
+  7 & 15 & 285,715 & 333,333 & 13 \\ 
+  8 & 16 & 333,334 & 380,952 & 13 \\ 
+  9 & 17 & 380,953 & 428,571 & 6 \\ 
+  10 & 18 & 428,572 & 476,190 & 6 \\ 
+  11 & 19 & 476,191 & 523,809 & 4 \\ 
+  12 & 20 & 523,810 & 571,428 & 5 \\ 
+  13 & 21 & 571,429 & 1,000,000 & 13 \\ 
+   \hline \hline
+\end{tabular}
 }
-  levshetvar <- unique(hetvar)
-  fullmod <- rma.mv(yi = yi, V = v, random = random,
-                    data = dat, slab = slab, method = 'REML',
-                    test = 't', tdist = T)
-  res <- tibble()
-  for (i in levshetvar) {
-    partmod <- rma.mv(yi = yi, V = v, 
-                      random = random,
-                      data = dat, slab = slab, 
-                      method = 'REML',
-                      test = 't', tdist = T, 
-                      subset = hetvar == i)
-    partmod <- broom_mod(partmod, subgroup = T)
-    partmod$byvar = i
-    partmod <- bind_rows(
-      tibble(TE = NA, seTE = NA,
-             studlab = toupper(i), lower = NA,
-             upper = NA, group = "B", byvar = i),
-      partmod
-    )
-    res <- bind_rows(res, partmod)
-  }
-  aux <- data.frame(predict(fullmod))
-  res <- bind_rows(res,
-                   tibble(
-                     byvar = NA,
-                     TE = c(aux$pred, NA),
-                     seTE = c(aux$se, NA),
-                     studlab = c("Overall Effect", "Prediction Interval"),
-                     lower = c(aux$ci.lb, aux$cr.lb),
-                     upper = c(aux$ci.ub, aux$cr.ub),
-                     group = "B"))
-  res <- data.frame(res)
-  res$byvar <- toupper(res$byvar)
-  return(res)
-}
-
-# Build plot function for forest plots
-build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
-  if(class(mod)[1] == "rma.mv") {
-    mod2 <- broom_mod(mod)
-  } else {
-  # Build dataset for plot
-  mod2 <- tibble(
-    TE = mod$TE,
-    seTE = mod$seTE,
-    studlab = mod$studlab,
-    lower = mod$lower,
-    upper = mod$upper,
-    group = "A") %>%
-    bind_rows(.,
-              aux = tibble(
-                TE = c(mod$TE.random, NA),
-                seTE = c(mod$seTE.random, NA),
-                studlab = c("Overall Effect",
-                            "Prediction Interval"),
-                lower = c(mod$lower.random,
-                          mod$lower.predict),
-                upper = c(mod$upper.random,
-                          mod$upper.predict),
-                group = "B")) %>%
-    group_by(studlab) %>%
-    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-    ungroup()
-  }
-  # Graph limits
-  limg <- max(abs(c(mod2$lower, mod2$upper)))
-  # Build plot
-  p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab2, TE),
-               x = TE, xmin = lower, xmax = upper)) +
-    geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group),
-                   height = 0.1) +
-    scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
-    scale_y_discrete(
-      labels = function(x)
-        str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept = 0,
-               color = "#000000", linetype = "dashed") +
-    labs(x = "",
-         y = "") +
-    facet_grid(group~., scales = "free", space = "free") +
-    labs(caption = capt,
-         title = ttl) +
-    theme_minimal() %+replace%
-    theme(strip.text.y = element_blank(),
-          legend.position = "none",
-          axis.text.y = element_text(size = .8 * lsize,
-                                     hjust = 1),
-          axis.text.x = element_text(size = .6 * lsize,
-                                     hjust = 1.1),
-          plot.caption = element_text(size = lsize),
-          plot.title.position = "plot",
-          plot.title = element_text(hjust = 0.5,
-                                    face = "bold",
-                                    margin = margin(0, 0, 10, 0)),
-          panel.grid.major = element_blank())
-  return(p)
-}
-
-# Build forest plot for heterogeneous analysis
-build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
-  mod2 <- estim_het(dat = dat, 
-                    yi = coef, 
-                    v = v, 
-                    random = ~ 1 | id_level1/id_level2, 
-                    slab = slab, 
-                    hetvar = hetvar)
-  mod2 <- data.frame(mod2)
-  mod2$byvar <- toupper(mod2$byvar)
-  TEaux <- mod2$TE
-  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
-  # Graph limits
-  limg <- max(abs(c(mod2$lower, mod2$upper)))
-  # Build plot
-  p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab, TEaux),
-               x = TE, xmin = lower, xmax = upper)) +
-    geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group),
-                   height = 0.1) +
-    scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
-    scale_y_discrete(
-      labels = function(x)
-        str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept = 0,
-               color = "#000000", linetype = "dashed") +
-    labs(x = "",
-         y = "") +
-    facet_grid(byvar~., scales = "free", space = "free") +
-    labs(caption = capt,
-         title = ttl) +
-    theme_minimal() %+replace%
-    theme(strip.text.y = element_blank(),
-          legend.position = "none",
-          axis.text.y = element_text(size = .8 * lsize,
-                                     hjust = 1),
-          axis.text.x = element_text(size = .6 * lsize,
-                                     hjust = 1.1),
-          plot.caption = element_text(size = lsize),
-          plot.title.position = "plot",
-          plot.title = element_text(hjust = 0.5,
-                                    face = "bold",
-                                    margin = margin(0, 0, 10, 0)),
-          panel.grid.major = element_blank())
-  return(p)
-}
-
-# Load datasets
-load("../dataset/dataCoefs.RData")
-```
+\label{tabcitycouncilsize2004short}
+\end{table}
+
+The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
+In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections.
+Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).
+
+To provide an overview of the data dispersion, Figure \ref{sample_plot} plots the municipalities by their proximity from the cutoffs.
+In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
+The darker the color, the closer to the population thresholds.
+In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation.
+Figure \ref{sample_plot} also shows that our municipalities are reasonably distributed around the whole country.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=7in,angle=0]{figs/sampplot2019.pdf}}
+      \caption{Municipalities by their Selection Status}
+      \bigskip
+      \label{sample_plot}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+Moreover, we could question whether the discontinuities studied here are sharp or fuzzy.
+In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced.
+For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities.
+However, this problem was absent in our RDD, as the problem identified by Cavalvanti was based on the use of thresholds approved in 2009.
+In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).
 
@@
 
-# A Brief Introduction to the Law of _1/n_ and the Reverse Law of _1/n_
-
-In this section, we present the intuition behind the _law of 1/n_, as well as the alternative _reverse law of 1/n_ proposed by @primo2008distributive.
-
-In their seminal paper, @weingast1981political argue that a high number of legislators will increase public spending beyond the optimal economic benchmark.
-They suggest that politicians have an incentive to over-provide concentrated benefits to their constituencies, spreading the costs across all constituencies through generalised taxation.
-The corollary of their model is that larger legislatures generate more public spending.
-
-In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{The concavity assumption implies that $b'>0$ and $b''<0$.
-A similarly convex assumption would mean that $c'>0$ and $c''>0$.
-We assume that the derivatives are well defined throughout the analysis.
-Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e.
-g., hiring a local company for the project).
-The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e.
-g., hiring a company from another state).
-Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e.
-g., how much prices shift because local economic factors are being used to provide the project).
-The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$.
-The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.
-
-Projects are economically efficient when the marginal costs are equal to the marginal benefits of the project size.
-This leads to the economic optimal project size, $x^E$.
-The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$.
-However, the projects that are actually implemented have a different structure.
-First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represents the number of constituencies.
-Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms.
-Therefore, the costs and benefits of implementing a project with size $x$ have the following structure:
+\subsection{Identification Strategy in Multiple Thresholds Regression Discontinuity Design\label{ISMT}}
+
+Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes.
+Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
+The outcome variable is assumed to be $Y$.
+In the pooled model, the Local Average Treatment Effect is:
 
 \[
-N(x) = b(x) + c_1(x) - \frac{1}{n}[c_1(x) + c_2(x)] - c_3(x)
+LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
 \]
 
-Differentiating $N(x)$ with respect to $x$ gives us the first order condition for an optimal project implementation.
+Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff.
+The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
+To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
+For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
+As the population varies smoothly around each cutoff, it makes it a perfect control to add.
+The new estimator is:
 
 \[
-b'(x) + c_1'(x) - \dfrac{1}{n}[c_1'(x) + c_2'(x)] - c_3'(x) = 0
+LATE_{controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C, Z_i \right]
 \]
 
-Totally differentiating $x$ with respect to $n$ gives us the following:
-
-\[
-b''(x)\dfrac{dx}{dn} + c_1''(x)\dfrac{dx}{dn} - \dfrac{1}{n}[c_1''(x) + c_2''(x)]\dfrac{dx}{dn} + \dfrac{1}{n^2}[c_1'(x) + c_2'(x)] - c_3''(x)\dfrac{dx}{dn} = 0
-\]
-
-And rearranging the terms, we find the following expression for $\dfrac{dx}{dn}$:
-
-\[
-\dfrac{dx}{dn} = -\dfrac{n^{-2}[c_1'(x) + c_2'(x)]}{b''(x) + c_1''(x)-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x)}
-\]
-
-Note that the numerator is always positive, as the marginal investment costs inside and outside the district increase according to the project size.
-The _law of 1/n_ holds when the denominator is negative.
-$b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$.
-Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.
-
-As the above condition suggests, the _law of 1/n_ holds only in specific situations.
-@primo2008distributive advance that theory by considering other situations where the _law_ may not hold, and they also argue that there are cases in which a _reverse law of 1/n_ holds, that is, larger legislatures may lead to lower public expenditures.
-
-Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country.
-Consider a local public good that generates a per capita benefit of $b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the degree of congestion of the public good, that is, how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion).
-In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district pay both local and federal government taxes.
-The degree that taxes are shared is denoted by $s$.
-Moreover, there is a deadweight loss of the taxes $\theta \geq 1$.
-The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$.
-Therefore, the citizens receive the following net benefit of a project with size $x$:
-
-\[
-\pi = x^\alpha m^{\beta-1} - \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta
-\]
-
-Maximising this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects, we find the following optimal project size:
-
-\[
-x^* = \left[\left(\dfrac{\alpha}{\theta}\right)^{\dfrac{1}{\theta-\alpha}}\right]\left[\left(nm\right)^{\dfrac{\beta+\theta-1}{\theta - \alpha}}\right]\left[\left( \dfrac{n^{2-\beta-\theta}}{n-ns+s}\right)^{\dfrac{1}{\theta-\alpha}}\right]
-\]
-
-And in the graph below, we show simulations for $n$ varying from 10 to 20, holding constant $\beta = 0.35$, $\theta \in \{0.65, 0.75\}$, $s = 0.5$, $m = 100$, and $\alpha = 0.7$.
-
-```{r, echo=FALSE, cache=TRUE, fig.align='center'}
-xstar <- function(x, beta, theta, alpha = 0.7, s = 0.5, m = 10) {
-  n = x
-  a = (alpha/theta)^(1/(theta-alpha))
-  b = (n*m)^((beta+theta-1)/(theta-alpha))
-  c = ((n^(2-beta-theta))/(n-n*s+s))^(1/(theta-alpha))
-  return (a*b*c)
-}
-
-curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
-      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
-curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
-      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
-```
-
-Thus, we see that both the _law of 1/n_ and its reverse formulation are equally plausible.
-Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen2007law], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].
-
-# Search Criteria
-
-The first step in our systematic review consisted in gathering a study sample.
-We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature.
-This search produced a database with many entries that were unrelated to our subject of investigation.
-To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is the fundamental contribution to the field.
-Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
-
-We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736).
-The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated.
-Our code is available in the `R` script available in this repository.
-We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses.
-We set no restriction to unpublished articles.
-
-We complemented this process by doing a term search on Google Scholar after having finished the entire eligibility procedure in the first sample.
-We formulated the search string based on the terms and expressions that appeared most frequently in the articles included in our meta-analysis.
-The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending.
-The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`.
-We scraped Google Scholar on March 5^th^, 2021.
-Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously.
-We then performed the exact same eligibility procedures, further explained below.
-This resulted in 3,041 additional records.
-Combining the two search strategies, we assessed a total of 5,705 records.
-
-# Article Selection
-
-The selection process was conducted by two authors in three phases.
-In the first phase, we excluded all titles that were clearly unrelated to our topic of interest.
-This was only a preliminary step, as we were not able to eliminate a large number of entries.
-Then, we read all abstracts.
-We kept all publications whose main topics were either government expenditure or legislative structures.
-Abstracts that indicated that the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were included.
-This allowed us to significantly reduce our sample.
-
-In the second phase, we assessed full texts.
-To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure.
-If the publication had all three, we kept it in our sample.
-Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.
-
-The third phase consisted of filling out tables for each of the remaining 47
-articles to systematically evaluate their eligibility. Since authors use
-different measures for government spending and the number of lower/upper house
-members, we extracted all coefficients that provided this information. In this
-phase, we also collected information on whether the paper had been published,
-and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
-we excluded two studies from the first sample, as they did not have the
-dependent/independent variables we collected for our meta-analysis. We then
-included the 2 papers we found in the second search, as both conformed to our
-criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
-articles.
-
-## Exclusion Analysis
-
-We selected the final pool of articles based on two criteria, namely the independent and the dependent variables employed in the paper. The categories follow below:
-
-1.  Independent variables:
-
--   *N*: Number Legislators in the Lower Chamber
--   *logN*: Log Number Legislators in the Lower Chamber
--   *K*: Number Legislators in the Upper Chamber
-
-2.  Dependent variables:
-
--   *ExpPC*: Expenditure Per Capita
--   *logExpPC*: Log Expenditure Per Capita
--   *PCTGDP*: Expenditure as Percentage of GDP
-
-If a paper did not use a combination of these variables, we excluded it from the meta-analysis.
-
-## Flow Chart
-
-The diagram below shows each step of our article selection process.
-We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) statement to conduct our study\footnote{More information about the PRISMA statement is available at \url{http://www.prisma-statement.org}.}.
-The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.
-
-\bigskip
-
-```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
-\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
-  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
-  \footnotesize
-  \linespread{1.0}
-
-  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Identification}};
-
-  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening}};
-
-  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
-
-  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
-
-  \node (id) [phase, right of = ID, xshift = 1cm] {Records identified through webscraping  \\ \textbf{(n = 2664)}};
-
-  \node (1st) [exc, right of = id, xshift = 3cm] {Records in languages other than English, book chapters, doctoral theses, and duplicates excluded \\ \textbf{(n = 1220)}};
-
-  \node (screen) [phase, below of = id] {Records screened \\ \textbf{(n = 1445)}};
-
-  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading title and abstract \\ \textbf{(n = 1069)}};
-
-  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 376)}};
-
-  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 329)}};
-
-  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 47)}};
-
-  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 19)}};
-
-\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 28)}};
-  \draw [arrow] (id) -- (1st);
-  \draw [arrow] (id) -- (screen);
-  \draw [arrow] (screen) -- (2nd);
-  \draw [arrow] (screen) -- (elig);
-  \draw [arrow] (elig) -- (3rd);
-  \draw [arrow] (elig) -- (inc_1);
-  \draw [arrow] (inc_1) -- (4th);
-  \draw [arrow] (inc_1) -- (inc_2);
-
- \end{tikzpicture}
-```
-
-\bigskip
-
-```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
-\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
-  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
-  \footnotesize
-  \linespread{1.0}
-  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
-  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
-  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
-  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
-  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
-  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
-  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
-  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
-  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
-  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
-  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
-  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 11)}};
-\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 2)}};
-  \draw [arrow] (id) -- (1st);
-  \draw [arrow] (id) -- (screen);
-  \draw [arrow] (screen) -- (2nd);
-  \draw [arrow] (screen) -- (elig);
-  \draw [arrow] (elig) -- (3rd);
-  \draw [arrow] (elig) -- (inc_1);
-  \draw [arrow] (inc_1) -- (4th);
-  \draw [arrow] (inc_1) -- (inc_2);
- \end{tikzpicture}
-```
-
-# Meta-Analysis Dataset
-
-Our meta-analytic data are comprised of two datasets.
-The first dataset has the main coefficients reported in the selected studies.
-These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them.
-If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
-This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest.
-Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.
-
-In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended dataset.
-Here we present the results of all tests performed in both reduced and full samples.
-
-# Descriptive Statistics
-
-Here we show the descriptive statistics for our sample.
-We focus on the following paper characteristics: study year; paper publication; the electoral system mentioned in the publication; and the distribution of the dependent and independent variables of interest.
-
-## Study Year
-
-The average year of publication in our sample is `r round(mean(dat$year), 2)` with standard deviation of `r round(sd(dat$year), 2)`.
-The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`.
-Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.
-
-```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE, size="footnotesize", echo = FALSE}
-dat %>%
-  select(id, year) %>%
-  unique() %>%
-  ggplot(aes(x = as.factor(year))) +
-    geom_bar(color = "black") +
-  labs(x = "",
-       y = "") +
-  theme_bw()
-```
-
-## Frequency of Published Papers
-
-Studies were included in our sample regardless of their publication status.
-From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were not published.
-
-```{r, fig.width=4, fig.height=2.5, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
-dat %>%
-  select(id, published) %>%
-  unique() %>%
-  ggplot(aes(x = as.factor(published))) +
-    geom_bar(color = "black") +
-  labs(x = "",
-       y = "") +
-  theme_bw()
-```
-
-## Electoral System
-
-Our sample differs considerably in regards to research design.
-One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies.
-In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, votes are geographically concentrated.
-The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}
-
-```{r, fig.width=6, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
-dat %>%
-  select(id, elecsys2) %>%
-  unique() %>%
-  ggplot(aes(x=as.factor(elecsys2))) +
-    geom_bar(color = "black") +
-  labs(x = "",
-       y = "") +
-  theme_bw()
-```
-
-## Dependent Variables
-
-The dependent variables included in the paper are:
-
--   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Expenditure Per Capita papers
--   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
--   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Log of Expenditure Per Capita papers
-
-```{r, fig.width=6, fig.height=2.3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
-dat %>%
-  select(id, depvar2) %>%
-  unique() %>%
-  mutate(depvar2 = factor(depvar2,
-                          labels = c("Expenditure Per Capita",
-                                     "Expenditure as Percentage GDP",
-                                     "Log Expenditure Per Capita"))) %>%
-  ggplot(aes(x = depvar2)) +
-    geom_bar(color = "black") +
-  labs(x = "",
-       y = "") +
-  coord_flip() +
-  theme_bw()
-```
-
-## Independent Variables
-
-Most papers in our sample analyse the number of legislators in the lower chamber (`r as.numeric(table(dat$indepvar2)[3])`).
-The second most frequent independent variable is the number of legislators in the upper chamber (`r as.numeric(table(dat$indepvar2)[1])`).
-Finally, the minority of papers use the natural log of the number of legislators in the lower chamber as an independent variable (`r as.numeric(table(dat$indepvar2)[2])`).
-As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.
-
-```{r, fig.width=6, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
-dat %>%
-  select(id, indepvar2) %>%
-  unique() %>%
-  mutate(indepvar2 = factor(indepvar2, 
-                            labels = c("Upper Chamber Size",
-                                       "Log of Lower Chamber Size",
-                                       "Lower Chamber Size"
-                                                  ))) %>%
-  ggplot(aes(x = indepvar2)) +
-    geom_bar(color = "black") +
-  labs(x = "",
-       y = "") +
-  coord_flip() +
-  theme_bw()
-```
-
-## Histogram of the Coefficients and the Standard Errors
-
-The coefficients in the papers vary considerably.
-We plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
-Most coefficients and standard deviations are close to zero.
-
-Coefficients:
-
-```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
-dat %>%
-  ggplot(aes(x = coef)) +
-  geom_histogram(bins = 15, color = "black") +
-  labs(x = "Coefficients", y = '') +
-  theme_bw()
-```
+We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
+All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}.
+To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff.
+To compute the optimal bandwidth, we use the \citet{CCT2014} method.
+To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
+We also use cluster-robust standard errors at the municipal level.
+
+However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable?
+To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.
+
+Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
+We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes.
+The first three outcomes are sharp changes.
+In the first, we add variation from one to 10, with one step for each change.
+In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
+The estimated change should be equal to zero.
+In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
+This is intended to simulate a diminishing effect from one cutoff to the other.
+The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
+We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{0.9\linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/simdistrRDD.pdf}}
+      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
+      \bigskip
+      \label{simRDdd}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+A consistent estimator should fit one in the first and fourth data distribution.
+In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
+In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$.
+The first three models should present a more efficient estimation than the last three models.
+We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1\linewidth}
+      \centerline{\includegraphics[width=4.5in,angle=0]{figs/estimsRDD.pdf}}
+      \caption{Estimations for the Different Data Generating Processes}
+      \bigskip
+      \label{estimDGP}
+    \end{minipage}
+  \end{center}
+\end{figure}
 
@@
 
-Standard errors:
-
-```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
-dat %>%
-  ggplot(aes(x = SE)) +
-  geom_histogram(bins = 10, color = "black") +
-  labs(x = "Standard Errors", y = '') +
-  theme_bw()
-```
-
-## Sign Coefficients
-
-One simple statistic that we can compute to assess the validity of the *law of 1/n* is the frequency of positive and negative estimates in the study sample.
-Below we plot the frequency for all the papers included in the meta-analytic dataset.
-
-```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE, echo = FALSE}
-dat %>%
-  ggplot(aes(x=as.factor(scoef))) +
-  geom_bar(color = "black") +
-  labs(x = "",
-       y = "") +
-  theme_bw()
-```
-
-# Descriptive Statistics of Moderators
-
-We chose a set of moderators that frequently appear in the literature and may help us interpret our results.
-We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study: lower chamber size ($n$), natural logarithm of lower chamber size (log[$n$]), or upper chamber size ($k$).
-The additional moderators are: the publication year; whether the paper was published in an academic journal; the estimation method used in the paper; the insitution design in terms of the division of legislative power; and the electoral system.
-
-```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
-fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
-aux <- select(fulldat, usemeta2, indepvar2, year, published, method,
-              instdesign, elecsys2) %>%
-  mutate(indepvar2 = recode(indepvar2,
-                            `N` = "Lower Chamber Size",
-                            `K` = "Upper Chamber Size",
-                            `logN` = "Log of Lower Chamber Size"),
-         elecsys2 = recode(elecsys2,
-                           `Non-Maj` = "Non-Majoritarian",
-                           `Maj` = "Majoritarian")) %>%
-  rename(`Independent Variables` = indepvar2,
-         `Year`                  = year,
-         `Published work`        = published,
-         `Estimation method`     = method,
-         `Institutional Design`  = instdesign,
-         `Electoral system`      = elecsys2)
-export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-                        show.p.overall = F, show.all = T),
-          caption = "Descriptive Statistics of Moderators",
-          format  = "latex")
-```
-
-# Binomial Tests for Coefficient Signs
-
-The *law of 1/n* posits that we should expect a positive influence of legislature size on public expenditures.
-A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations.
-In statistical terms, consider a random variable representing the coefficient sign for the papers.
-As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the chance of a positive sign.
-The *law of 1/n* can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
-The null statistical hypothesis for such a test is that:
-
-- $H_0$: the proportion of positive and negative signs are statistically equal ($p=0.5$).
-
-As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) may be true.
-In this case, the alternative hypothesis is $p \neq 0.5$.
-To perform this test, we run binomial exact tests in `R`, using the function `binom.test(.)`.
-
-This test has two advantages.
-First, it is robust to the design of the paper.
-This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not.
-The binomial test ignores the design discrepancies and focuses on the overall reported effect.
-Second, this test has the advantages of requiring few assumptions and being easy to interpret.
-The disadvantage is that the test is not as informative as the meta-regressions, as we shall see in the next sections.
-
-For the number of legislators in the lower chamber ($N$), the results follow below.
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-aux <- filter(dat, indepvar2 == "N")
-aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
-```
-
-Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign.
-The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
-Thus, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-
-For the log of the number of legislators in the lower chamber ($\log(N)$), the results are as follows:
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-aux <- filter(dat, indepvar2 == "logN")
-aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
-```
-
-Out of `r sum(table(aux$scoef))` studies, `r as.numeric(table(aux$scoef)[2])` have a positive sign.
-The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
-So we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-
-Finally, for the number of legislators in the upper chamber ($K$), the results are:
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-aux <- filter(dat, indepvar2=='K')
-aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
-pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
-```
-
-Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign.
-The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`.
-Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-This is the only test that presents evidence of an association between the legislature size and expenditure.
-
-We also tested the possibility that the signs change heterogeneously, based on whether the paper studied unicameral versus non-unicameral legislative bodies.
-This analysis does not take into consideration the size of the upper house, as it would indicate that the cases in the paper had trivially a non-unicameral legislature.
-The results for this analysis follow below, and show that there is no significant change in the sign of the relationship between public spending and legislature size, when controlling by the institution design.
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-aux <- list()
-aux[[1]] <- filter(dat, indepvar2 == "N", instdesign2 == 'Unicameral')
-aux[[2]] <- filter(dat, indepvar2 == "N", instdesign2 != 'Unicameral')
-aux[[3]] <- filter(dat, indepvar2 == "logN", instdesign2 == 'Unicameral')
-aux[[4]] <- filter(dat, indepvar2 == "logN", instdesign2 != 'Unicameral')
-aux[[1]] <- binom.test(table(aux[[1]]$scoef)[2],
-                       sum(table(aux[[1]]$scoef)), p = 0.5)
-aux[[2]] <- binom.test(table(aux[[2]]$scoef)[2],
-                       sum(table(aux[[2]]$scoef)), p = 0.5)
-aux[[3]] <- binom.test(table(aux[[3]]$scoef)[2],
-                       sum(table(aux[[3]]$scoef)), p = 0.5)
-aux[[4]] <- binom.test(table(aux[[4]]$scoef)[2],
-                       sum(table(aux[[4]]$scoef)), p = 0.5)
-aux2 <- tidy(aux[[1]])[,-c(2,4,5,6)][,c(3,4,1,2)]
-aux2 <- bind_rows(aux2, tidy(aux[[2]])[,-c(2,4,5,6)][,c(3,4,1,2)])
-aux2 <- bind_rows(aux2, tidy(aux[[3]])[,-c(2,4,5,6)][,c(3,4,1,2)])
-aux2 <- bind_rows(aux2, tidy(aux[[4]])[,-c(2,4,5,6)][,c(3,4,1,2)])
-aux2 <- aux2 %>%
-  mutate(`Indep. Variable` = c('Lower House Size', 'Lower House Size', 'Log of Lower House Size', 'Log of Lower House Size'),
-         `Legislative Inst.` = c('Unicameral', 'Non-unicameral', 'Unicameral', 'Non-unicameral')) %>%
-  relocate(`Indep. Variable`, `Legislative Inst.`, .before = method)
-aux2$method <- NULL
-aux2$alternative <- NULL
-pander(aux2)
-```
-
-# Meta-Analysis
-
-## Estimation Method
-
-In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models.
-The fixed effects model assumes that there exists a single true effect and all estimates are an attempt to uncover this effect.
-The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.
-
-In this paper, we employ a random effects model.
-The empirical papers testing the *law of 1/n* are very diverse.
-We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
-
-1.  **Study sample**: Counties, Municipalities, States, Provinces, Countries.
-2.  **Electoral systems**: Majoritarian, PR, Mixed.
-3.  **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
-4.  **Institution design**: Unicameral, Bicameral, or the Mixed of both Unicameral and Bicameral.
-
-These sources of heterogeneity have two implications.
-First, they make our estimates notably disperse.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
-Thus, we opt for the random effects model.
-
-Assume that each study has an effect of $T_i$.
-In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
-
-$$
-T_i \ = \ \theta_i + \varepsilon_i
-$$
-
-And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
-
-$$
-T_i \ = \ \mu + \xi_i + \varepsilon_i
-$$
-
-And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
-
-Another crucial assumption in meta-analysis is that the coefficients should be independent [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction].
-This assumption states that for our findings to be consistent, the coefficients must come from different sources of variation.
-However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model with similar variables.
-While our restricted dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
-This is because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients.
-To correct for the violation of the study independence assumption, we use a multilevel random effects model [@cheung2014modeling].
-We add two extra levels to the regular random effects model, one that indicates the publication ID and another that indicates the data used in the original article.
-These levels are assumed to remove dependence structures in the data, therefore improving the estimates of our coefficient of interest, which is the effect of legislature size on public spending.
-
-There are two levels in the main models. First, we build a common index for papers that share the same data specifications. The papers with common indexing are:
-
-| Publication ID                              | Source of Dependence                                                     |
-|---------------------------------------------|--------------------------------------------------------------------------|
-| 3, 42, 132, 165, 439, 441, 467, 505         | US States Data                                                           |
-| 408, 208, A258                              | US Municipalities Data                                                   |
-| 849, 578                                    | US Municipalities Data and Same Author in Two Different Studies          |
-
-All the remaining papers received a unique index.
-As the number of papers with these dependencies is not very high, and many characteristics within papers vary (e.
-g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs.
-In regard to the full dataset, the results change considerably, because authors fit several models within the same paper.
-In any case, we use multilevel random effects for all the estimated models in this paper.
-
-To study the possibility of publication bias, we add a funnel plot and an @egger1997bias test for distribution asymmetry for every model.
-Funnel plots display the possibility of having a file-drawer effect, meaning that null results are under-represented in our sample.
-In this type of plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome.
-If they are asymmetric, it provides evidence for a file-drawer effect.
-
-We use the `R` packages `meta` and `dmetar` in all estimates [@harrer2019doing].
-We employ the *Restricted Maximum Likelihood Estimator* to assess the variance of the true effect size ($\tau^2$), which in our formulation represents the variance of $\xi_i$.
-The literature regards this estimator as the most precise when analysing continuous measures, such as the ones we have in our data [@veroniki2016methods].
-
-We combine the three independent variables (Lower Chamber Size, Log of Lower Chamber Size, and Upper Chamber Size) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
-This formed a $3 \times 3$ table, yet not all combinations are available in the data.
-The results are shown below.
-
-## Lower Chamber Size and Expenditure Per Capita
-
-The results for the meta-analysis that compares lower chamber size and expenditure per capita are available below.
-
-```{r, cache=TRUE, echo = FALSE, size="footnotesize"}
-# Pooling effects analysis -- ExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-mod
-```
-
-The forest plot:
-
-```{r, fig.width=8, fig.height=4.5, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F, warning=F, cache=TRUE, echo = FALSE}
-f1 <- build_forest(mod, NULL, lsize = 15, ttl = '1.1 - Lower Chamber Size\nand Expenditure Per Capita')
-```
-
-And to assess the possibility of publication bias, we add the funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-### Electoral System Subgroup Analysis
-
-The *law of 1/n* was introduced to describe majoritarian systems, but the theory has also been applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a binary indicator for electoral system.
-The results may be seen below.
-
-We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita.
-Both coefficients are not statistically significant, and they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
-
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Electoral System", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
-                 capt = NULL, hetvar = aux$elecsys2)
-```
-
-### Institution Design Subgroup Analysis
-
-The *law of 1/n* was conceived to explain the expected effect of chamber size on public expenditure.
-However, papers such as @chen2007law demonstrated that the relationship is mediated by the size of the upper chamber.
-Their finding suggests that the institutional design of the legislature influences the empirical predictions in the sample we study.
-To test this possibility, we estimated a subgroup analysis using a binary indicator for institutional design.
-The results may be seen below.
-
-We find little evidence that either unicameral or non-unicameral legislative institutions produce systematically positive effects on expenditure per capita.
-However, the coefficients tend to be weakly positive for unicameral studies, suggesting that there might be a relationship, that is masked by the low statistical power.
-
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Institution Design", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
-                 capt = NULL, hetvar = aux$instdesign2)
-```
-
-## Log of Lower Chamber Size and Expenditure Per Capita
-
-There are no studies that have per capita expenditure as the dependent variable and log of lower chamber size as the independent variable.
-
-## Upper House Size and Expenditure Per Capita
-
-Now we look into the upper chamber size. In this model, we investigate the effect of upper house size on expenditure per capita.
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-# Pooling effects analysis -- ExpPC x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-```{r, fig.width=7, fig.height=3, fig.cap="Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-We see no evidence of publication bias:
-
-```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r, include=FALSE, warning=FALSE, echo = FALSE}
-f2 <- build_forest(mod, NULL, 15, ttl = '1.6 - Upper Chamber Size\nand Expenditure Per Capita')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Lower Chamber Size and Log of Expenditure Per Capita
-
-This model estimates the log of expenditure per capita as the dependent variable, and lower chamber size as the independent variable.
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-# Pooling effects analysis -- logExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-mod
-```
-
-The forest plot is as follows:
-
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Log of Expenditure Per Capita",warning=FALSE, echo = FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-The funnel plot shows no evidence of publication bias.
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
-f3 <- build_forest(mod, NULL, 15, ttl = '1.2 - Lower Chamber Size\nand Log Expenditure Per Capita')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Log of Lower Chamber Size and Log of Expenditure Per Capita
-
-In this specification, we study the log of per capita expenditure as a function of the log of lower chamber size.
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-# Pooling effects analysis -- logExpPC x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-The forest plot is available below:
-
-```{r, fig.width=6, fig.height=4, fig.cap="Effect of Log Lower Chamber Size on Log Expenditure Per Capita", echo = FALSE, warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-The funnel plot:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
-f4  <- build_forest(mod, NULL, 15, ttl = '1.4 - Log Lower Chamber Size\nand Log Expenditure Per Capita')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Upper Chamber Size and Log of Expenditure Per Capita
-
-No studies correlate the log of per capita expenditure with the size of the upper chamber (K).
-
-## Lower Chamber Size and Expenditure as Percentage of GDP
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the independent variable.
-
-```{r, size="footnotesize", echo = FALSE, cache=TRUE}
-# Pooling effects analysis -- PCTGDP x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-Below, you may find the forest plot:
-
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, echo = FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-The funnel plot to test for publication bias:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r, include=F, warning=F, echo = FALSE, cache=TRUE}
-f5 <- build_forest(mod, NULL, 15, ttl = '1.3 - Lower Chamber Size\nand Expenditure as Percentage of GDP')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Log Lower Chamber Size and Expenditure as Percentage of GDP
-
-This model investigates the percentage of GDP as public expenditure as the dependent variable and the log lower chamber size as the independent variable.
-
-```{r, echo = FALSE, size="footnotesize", cache=TRUE}
-# Pooling effects analysis -- PCTGDP x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-mod
-```
-
-```{r, echo = FALSE, fig.width=8, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-The funnel plot is available below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
-f6 <- build_forest(mod, NULL, 15, ttl = '1.5 - Log Lower Chamber Size\nand Expenditure as Percentage of GDP')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Upper Chamber Size and Expenditure as Percentage of GDP
-
-This model looks into the effect of upper chamber size on the public expenditure share of the GDP.
-
-```{r, size="footnotesize", cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- PCTGDP x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-As in our previous estimations, we find no evidence of file-drawer effect.
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
-f7 <- build_forest(mod, NULL, 15, ttl = '1.7 - Upper Chamber Size\nand Expenditure as Percentage of GDP')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Lower Chamber Size and Expenditure per Capita (Instrumental Variables Only)
-
-Here we estimate a meta-analysis of the papers which use instrumental variables. The results may be seen below.
-
-```{r, size="footnotesize", cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- ExpPC x N (IV only)
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC',
-         method %in% c('IV'))
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-And the forest plot:
-
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-No evidence of publication bias, as shown in the following funnel plot:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-f8 <- build_forest_het(aux, aux$coef, 
-                       aux$VAR, slab = aux$authoryear,
-                       capt = NULL, lsize = 15, 
-                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(subgrouping by the estimation technique)', 
-                       hetvar = aux$method)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-### Regression Method Subgroup Analysis
-
-Over time, the literature evolved to use causally identified techniques to determine the effect of legislature size on the expenditure per capita.
-To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
-
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Methods", warning=FALSE, cache=TRUE, echo = FALSE}
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
-                 capt = NULL, hetvar = aux$method)
-```
-
-Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers displaying negative effects.
-The random effects model for the subgroup is 0.22, which is negative but non-significant.
-Improving the estimation technique, for the case of IVs, still renders a null effect of legislature size on per capita government expenditure.
-
-## Lower Chamber Size and Log of Expenditure per Capita (Regression Discontinuity Design Only)
-
-In this subsection, we run a meta-analysis with papers that include regression discontinuity designs.
-
-```{r, size="footnotesize", cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- logExpPC x N (RDD only)
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC',
-         method == 'RDD')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-Forest plot:
-
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC',
-         method == 'RDD')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-f9 <- build_forest(mod, capt = NULL, 
-                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(subgrouping by RDD)')
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. The reason is because in that paper, the author uses Log of Expenditure Per Capita x Log of Legislature Size.
-
-```{r, warning=F, cache=TRUE, echo = FALSE, results='hide'}
-## Plot 1
-pdf('../graphs/graph1.pdf', width = 16, height = 11)
-ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
-dev.off()
-## Plot 2
-pdf('../graphs/graph2.pdf', width = 12, height = 6)
-ggarrange(f8, f9, align = 'hv')
-dev.off()
-```
-
-# Meta-Analysis (All Coefficients)
-
-## Lower Chamber Size and Expenditure Per Capita
-
-Here we estimate the relationship between expenditure per capita as a dependent variable, and the lower chamber as the independent variable.
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-# Pooling effects analysis -- ExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-The forest plot:
-
-```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And to assess the possibility of publication bias, we add the funnel plot below:
-
-```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-### Electoral System Subgroup Analysis
-
-The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems.
-In the theoretical section below, we explain why the argument has potential issues when applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.
-
-We see that majoritarian systems do not have a clear positive effect on budgetary spending.
-The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
-
-```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Electoral System", warning=FALSE, cache=T, echo = FALSE}
-build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
-                 capt = NULL, hetvar = aux$elecsys2)
-```
-
-### Institution Design Subgroup Analysis
-
-The *law of 1/n* was conceived to explain the expected effect of chamber size on public expenditure.
-However, papers such as @chen2007law demonstrated that the relationship is mediated by the size of the upper chamber.
-Their finding suggests that the institutional design of the legislature influences the empirical predictions in the sample we study.
-To test this possibility, we estimated a subgroup analysis using a binary indicator for institutional design.
-The results may be seen below.
-
-We find little evidence that either unicameral or non-unicameral legislative institutions produce systematically positive effects on expenditure per capita.
-However, the coefficients tend to be weakly positive for unicameral studies, suggesting that there might be a relationship, that is masked by the low statistical power.
-
-```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Institution Design", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
-                 capt = NULL, hetvar = aux$instdesign2)
-```
-
-## Log of Lower Chamber Size and Expenditure Per Capita
-
-There are no studies that have per capita expenditure as the dependent variable and log of lower chamber size as the independent variable.
-
-## Upper Chamber Size and Expenditure Per Capita
-
-Now we investigate the effect of the upper chamber size on expenditure per capita.
-
-```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- ExpPC x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-The forest plot:
-
-```{r, fig.width=9, fig.height=10, fig.cap="Effect of Upper Chamber Size on the Per Capita Government Expenditure",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-The funnel plot suggests no publication bias.
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Lower Chamber Size and Log of Expenditure Per Capita
-
-This model estimates the log of per capita expenditure as the dependent variable, and the number of lower chamber legislators as the independent variable.
-
-```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- logExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-The forest plot is shown below:
-
-```{r, fig.width=8, fig.height=5, fig.cap="Effect of Lower Chamber Size on Log Expenditure Per Capita",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Log of Lower Chamber Size and Log of Expenditure Per Capita
-
-In this specification, we study the log of per capita expenditure as a function of the log of lower chamber size.
-
-```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- logExpPC x logN
-aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-The forest plot:
-
-```{r, fig.width=8, fig.height=7, fig.cap="Effect of Log of Lower Chamber Size on Log of Expenditure Per Capita",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And the funnel plot:
-
-```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of Log of Lower Chamber Size on Log of Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Upper Chamber Size and Log of Expenditure Per Capita
-
-No studies related the log of per capita expenditure with the size of upper chamber.
-
-## Lower Chamber Size and Expenditure as Percentage of GDP
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower chamber as the independent variable.
-
-```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- PCTGDP x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-Here is the forest plot:
-
-```{r, fig.width=8, fig.height=7, fig.cap="Effect of Lower Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And here is the funnel plot to assess the possibility of publication bias:
-
-```{r, fig.width=4, fig.height=3.75, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Log of Lower Chamber Size and Expenditure as Percentage of GDP
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the natural logarithm of lower chamber size as the independent variable.
-
-```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- PCTGDP x logN
-aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-The forest plot:
-
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And the funnel plot:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Upper Chamber Size and Expenditure as Percentage of GDP
-
-This model looks into the effect of upper chamber size on the expenditure as a percentage of the GDP.
-
-```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- PCTGDP x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-And the forest plot:
-
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of Upper Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Lower Chamber Size and Expenditure per Capita (Instrumental Variables Only)
-
-```{r, size="footnotesize", cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- ExpPC x N (IV only)
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC',
-         method %in% c('IV'))
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-And the forest plot:
-
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-## Lower Chamber Size and Log of Expenditure Per Capita (Regression Discontinuity Designs Only)
-
-```{r, size="footnotesize", cache=TRUE, echo = FALSE}
-# Pooling effects analysis -- ExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC',
-         method == 'RDD')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-mod
-```
-
-And the forest plot:
-
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of Lower Chamber Size on Log Expenditure Per Capita (RDD Only)",warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest(mod, NULL)
-```
-
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod)
-```
-
-Highlights:
-
-1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
-3.
-The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
-Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-
-# Meta-Regressions
-
-In the meta-regressions, we study the effects of a group of moderators on the reported government spending data. We select the following moderators:
-
-1. The independent variable (variable `indepvar2`):
-  - `K`: Upper Chamber Size
-  - `N`: Lower Chamber Size
-  - `logN`: Log of Lower Chamber Size
-
-2. Year that the paper was published (for working papers, the year it was posted online; variable `year`)
-
-3. A dummy indicating whether the paper was published or not (variable `published`).
-
-4. A dummy for non-majoritarian electoral systems (variable `elecsys2`).
-
-5. A institution design variable, with:
- - `Bicameral`: a legislative system comprised of two chambers (e.g. US Federal Senate and House).
- - `Unicameral`: a system with only a lower chamber (e.g. US Municipalities).
- - `Mixed`: more than one system in the same sample (cross-country regressions).
-
-6. The estimation method used in the papers (variable `method`):
-  - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
-  - `PANEL`: Time-Series Cross-Section models, with estimated fixed effects.
-  - `IV`: Instrumental Variables models.
-  - `RDD`: Regression Discontinuity Designs.
-
-The results follows below, for the three combinations of dependent variables: Expenditure Per Capita, Log of Expenditure Per Capita, and Expenditure as Percentage of GDP.
-
-## Meta-Regressions for Expenditure Per Capita
-
-Here we study the expenditure per capita as the main outcome, aggregating all types of independent variables.
-
-```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              sparse = TRUE,
-              tdist = TRUE,
-              subset = dat$depvar2=='ExpPC',
-              slab = dat$authoryear)
-
-summary(mod)
-```
-
-For the meta-regressions of Expenditure Per Capita, we find no significant moderator. We also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = fulldat$depvar2=='ExpPC',
-              slab = fulldat$authoryear)
-
-summary(mod)
-```
-
-With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:
-
-1.  Compared with upper chamber size, models with lower chamber size tend to detect significantly smaller effects.
-
-2.  Year has now a positive effect on coefficient sizes.
-
-3.  All other moderators were insignificant.
-
-## Meta-Regressions for Log of Expenditure Per Capita
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = dat$depvar2=='logExpPC',
-              slab = dat$authoryear)
-
-summary(mod)
-```
-
-The only significant result points that published papers tend to report a smaller coefficient than unpublished papers.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = fulldat$depvar2=='logExpPC',
-              slab = fulldat$authoryear)
-
-summary(mod)
-```
-
-With all coefficients, results of the effect sizes on the log of expenditure per capita regressions indicate that in regard to the estimation method, papers that use panel data or regression discontinuity designs have smaller effects than articles that employ simple OLS regressions.
-All other results are insignificant.
-
-## Meta-Regressions for Expenditure as a Percentage of GDP
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = dat$depvar2=='PCTGDP',
-              slab = dat$authoryear)
-
-summary(mod)
-```
-
-In the meta-regressions of Expenditure as a Percentage of GDP, we found that:
-
-1. Recent papers find smaller effect sizes than older studies.
-
-2. Papers whose samples included unicameral legislatures report slightly higher coefficients.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-summary(mod)
-```
-
-With all coefficients, the results of the effect sizes on the Expenditure as a Percentage of GDP regressions are the following:
-
-1. Papers from more recent years find smaller effect sizes than older studies.
-
-2. Studies using non-majoritarian systems find more positive effects between variables.
-
-3. Papers whose samples included unicameral legislatures report significantly higher coefficients.
-
-# Meta-Regressions (All Coefficients)
-
-In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling for:
-
-1. The type of the dependent variable in the study (expenditure per capita, log expenditure per capita, and expenditure as percentage of GDP).
-
-2. The type of the independent variable in the study (lower chamber size, upper chamber size, or log of lower chamber size).
-
-3. The electoral system (Majoritarian versus Non-Majoritarian).
-
-4. The year when the study was published.
-
-5. Whether the study is a working paper or published work.
-
-6. The institutional design: whether the legislature in the analysis is unicameral, bicameral, or mixed.
-
-7. The estimation method used in the paper (OLS, PANEL, IV, or RDD).
-
-The results follow below, and show null effects for all variables except for Unicameral institutional designs.
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              slab = dat$authoryear)
-
-summary(mod)
-```
-
-In the restricted model, with only the main coefficients in the selected papers, Unicameralism has a positive, significant effect.
-Also, papers using Regression Discontinuity Design tend to have a negative effect, significant at the 10% level.
-We also run the meta-regressions adding all coefficients in the papers.
-The results follow below:
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              slab = fulldat$authoryear)
-summary(mod)
-```
-In the full model, we can see that:
-
-1. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
-
-2. Evidence from unicameral systems presents significantly larger effect sizes.
-
-3. All other moderators are insignificant.
+\subsection{Placebo Regressions for the Aggregated Mechanism Outcomes\label{placmechmain}}
+
+Here we present the placebo regressions for the mechanism-aggregated outcomes.
+In Panel A of the main paper, we run the regression on alternative explanations.
+As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases.
+For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank.
+In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage.
+As expected, the placebo regressions were not statistically significant.
+
+\input{tabs/edited/appmechreg1Oct2016e.tex}
+
+\newpage
+
+\subsection{Sensitivity Analysis for Bandwidth Selection\label{sensffapp}}
+
+We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1\linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/bwsens2019.pdf}}
+      \caption{Bandwidth Sensitivity -- Main Models}
+      \bigskip
+      \label{graphbw}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placbwsens2019.pdf}}
+      \caption{Placebo Regressions -- Bandwidth Sensitivity}
+      \bigskip
+      \label{placgraphbw}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to Different States in the Analysis\label{sensstate}}
+
+The literature considers that some states are more prone to inefficiencies than the rest of the country.
+Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves.
+As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size.
+We run the analysis dropping one state at a time, to investigate this statewide heterogeneity.
+The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
+
+To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks.
+The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states.
+In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo.
+Otherwise, note that all the other variables remain unchanged, except for gender.
+Gender changes because there were laws during this period mandating a minimum amount of female candidates.
+It is expected that one variable changes as a response to randomness.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/dropstatesens12019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
+      \bigskip
+      \label{graphsensstatedrop1}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/dropstatesens22019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
+      \bigskip
+      \label{graphsensstatedrop2}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placdropstatesens12019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop1}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/placdropstatesens22019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop2}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to the Functional Form Analysis\label{sensfuncform}}
+
+In the paper, we run all the regressions using local linear polynomials.
+\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
+
+However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms.
+With two exceptions, the results are mostly consistent.
+First, quadratic and cubic polynomials make the significance go away in some models.
+Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions.
+Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/ffsens2019.pdf}}
+      \caption{Sensitivity Analysis for the Functional Form}
+      \bigskip
+      \label{graphsensff}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/placffsens2019.pdf}}
+      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
+      \bigskip
+      \label{placgraphsensff}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to Covariates\label{senstcovapp}}
+
+The control variables play an essential role in our model.
+As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
+
+However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis.
+To study the sensitivity to controls, we run the same regressions for all possible control combinations.
+Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
+The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}
+
+\begin{landscape}
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=6in,angle=0]{figs/senscov2019.pdf}}
+      \caption{Sensitivity Analysis for the Control Variable's Choices}
+      \bigskip
+      \label{graphsenscontrol}
+    \end{minipage}
+  \end{center}
+\end{figure}
+\end{landscape}
+
+For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.
+
+In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant.
+Otherwise, our model is not significant when most combinations are also insignificant.
+Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.
+
+We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
+The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placsens1cov2019.pdf}}
+      \caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
+      \bigskip
+      \label{placsenscov1}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placsens2cov2019.pdf}}
+      \caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
+      \bigskip
+      \label{placsenscov2}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}
+
+To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
+This strategy is similar to adding one cutoff at a time.
+The results are stable and do not change our main conclusions.
+Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring.
+Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/rdaddcuts12019.pdf}}
+      \caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
+      \bigskip
+      \label{senscut1}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/rdaddcuts22019.pdf}}
+      \caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
+      \bigskip
+      \label{senscut2}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{0.8 \linewidth}
+      \centerline{\includegraphics[width=5.5in,angle=0]{figs/placrdaddcuts12019.pdf}}
+      \caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
+      \bigskip
+      \label{placsenscut1}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{0.8 \linewidth}
+      \centerline{\includegraphics[width=5.5in,angle=0]{figs/placrdaddcuts22019.pdf}}
+      \caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
+      \bigskip
+      \label{placsenscut2}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Further analysis on the role of mayors, mayoral parties, and parties in the city council.}
+
+In this section, we analyze the role of political composition of city council and mayoral parties on outcomes.
+We also analyzed the revenues and transfers from the Federal government to municipalities.
+
+\subsubsection{Mayoral parties}
+
+Mayors in Brazil have considerably more discretionary power to implement policies when compared with city councilors.
+Therefore, our outcomes could be byproduct of the mayor in power.
+To avoid this possibility, we run the regressions using the mayoral parties as an outcome.
+The results below show no differences in likelihood of electing a mayor from PT, PSDB, PMDB, and PFL when we add an extra councilor.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:47
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Mayors from Major Parties} 
+  \label{appmayparty} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Mayor from PT}} & \multicolumn{1}{c}{\textbf{Mayor from PSDB}} & \multicolumn{1}{c}{\textbf{Mayor from PMDB}} & \multicolumn{1}{c}{\textbf{Mayor from PFL (DEM)}} \\ 
+\hline \\[-1.8ex] 
+ LATE & -0.01 & 0.11 & 0.0004 & 0.01 \\ 
+  & (0.09) & (0.12) & (0.10) & (0.06) \\ 
+ N Left & 5069 & 5069 & 5069 & 5069 \\ 
+N Right & 335 & 335 & 335 & 335 \\ 
+Eff N Left & 257 & 162 & 226 & 105 \\ 
+Eff N Right & 166 & 124 & 154 & 103 \\ 
+BW Loc Poly & 10.52 & 7.585 & 9.637 & 5.605 \\ 
+BW Bias & 16.103 & 11.409 & 15.41 & 9.632 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular}}
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:47
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Mayors from Major Parties -- Placebo} 
+  \label{placappmayparty} 
+  \resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Mayor from PT}} & \multicolumn{1}{c}{\textbf{Mayor from PSDB}} & \multicolumn{1}{c}{\textbf{Mayor from PMDB}} & \multicolumn{1}{c}{\textbf{Mayor from PFL (DEM)}} \\ 
+\hline \\[-1.8ex] 
+ LATE & 0.05 & 0.02 & 0.03 & -0.11$^{*}$ \\ 
+  & (0.05) & (0.06) & (0.07) & (0.06) \\ 
+ N Left & 4526 & 4526 & 4526 & 4526 \\ 
+N Right & 878 & 878 & 878 & 878 \\ 
+Eff N Left & 486 & 823 & 609 & 544 \\ 
+Eff N Right & 319 & 453 & 372 & 335 \\ 
+BW Loc Poly & 5.568 & 8.407 & 6.551 & 6.027 \\ 
+BW Bias & 9.222 & 13.908 & 10.539 & 11.459 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular}}
+\end{table}
+
+\subsubsection{Mayoral characteristics}
+
+We also run the same regressions on mayoral characteristics.
+We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
+The results also show no variation on council size and mayoral characteristics.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:50
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Mayoral Characteristics} 
+  \label{appmaychar} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
+College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
+\hline \\[-1.8ex] 
+ LATE & 0.07 & -0.06 & -0.09 & 0.06 \\ 
+  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
+ N Left & 5069 & 5069 & 5184 & 5183 \\ 
+N Right & 335 & 335 & 343 & 343 \\ 
+Eff N Left & 299 & 226 & 192 & 231 \\ 
+Eff N Right & 184 & 154 & 141 & 159 \\ 
+BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\ 
+BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular} }
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:51
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Mayoral characteristics -- Placebo} 
+  \label{placappmaychar} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
+College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
+\hline \\[-1.8ex] 
+ LATE & 0.03 & 0.04 & 0.08 & -0.07 \\ 
+  & (0.05) & (0.08) & (0.07) & (0.08) \\ 
+ N Left & 4526 & 4526 & 4621 & 4620 \\ 
+N Right & 878 & 878 & 906 & 906 \\ 
+Eff N Left & 567 & 707 & 683 & 759 \\ 
+Eff N Right & 342 & 406 & 397 & 427 \\ 
+BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\ 
+BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular} }
+\end{table}
+
+\subsubsection{Transfers and revenue}
+
+To investigate whether transfers are driving our results, we run the regressions on federal transfers and revenue raised within the municipalities.
+There is only a small effect on education transfer.
+The other indicators remain insignificant.
+Note that the placebo is significant, but this does not invalidate the placebo tests.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:18:41
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Transfers and Revenue} 
+  \label{apptrev} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
+\hline \\[-1.8ex] 
+ LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\ 
+  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
+ N Left & 15555 & 15555 & 15460 & 14668 \\ 
+N Right & 1029 & 1029 & 1028 & 998 \\ 
+Eff N Left & 804 & 258 & 349 & 626 \\ 
+Eff N Right & 516 & 273 & 333 & 442 \\ 
+BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\ 
+BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular} }
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:18:42
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Transfers and Revenue -- Placebo} 
+  \label{plactrev} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
+\hline \\[-1.8ex] 
+ LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\ 
+  & (0.03) & (0.03) & (0.06) & (0.03) \\ 
+ N Left & 13865 & 13865 & 13776 & 13103 \\ 
+N Right & 2719 & 2719 & 2712 & 2563 \\ 
+Eff N Left & 807 & 636 & 1928 & 848 \\ 
+Eff N Right & 619 & 544 & 1163 & 611 \\ 
+BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\ 
+BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular} }
+\end{table}
+
+\subsubsection{City councilors party composition}
+
+As the result could be driven by party composition of the mayor, we run the regression on city council party composition. There is no effect of party composition and city council size.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:54
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Councilors from Major Parties} 
+  \label{appcouncilparty} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
+\hline \\[-1.8ex] 
+ LATE & -0.01 & -0.05 & -0.01 & -0.01 \\ 
+  & (0.02) & (0.05) & (0.03) & (0.02) \\ 
+ N Left & 5179 & 5179 & 5179 & 5179 \\ 
+N Right & 343 & 343 & 343 & 343 \\ 
+Eff N Left & 375 & 152 & 267 & 231 \\ 
+Eff N Right & 212 & 121 & 172 & 159 \\ 
+BW Loc Poly & 13.99 & 6.8 & 10.58 & 9.63 \\ 
+BW Bias & 22.64 & 11.373 & 16.803 & 15.647 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular} }
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:55
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Councilors from Major Parties -- Placebo} 
+  \label{placappcouncilparty} 
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
+\hline \\[-1.8ex] 
+ LATE & 0.02 & 0.01 & 0.02 & 0.003 \\ 
+  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
+ N Left & 4617 & 4617 & 4617 & 4617 \\ 
+N Right & 905 & 905 & 905 & 905 \\ 
+Eff N Left & 434 & 939 & 621 & 845 \\ 
+Eff N Right & 303 & 495 & 378 & 461 \\ 
+BW Loc Poly & 5.012 & 9.003 & 6.505 & 8.333 \\ 
+BW Bias & 8.078 & 13.701 & 11.172 & 13.303 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+\end{tabular} }
+\end{table}
+
+\newpage
+
+\subsection{Legislation Dataset\label{legdfr}}
+
+In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds.
+There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.
+
+To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases.
+First, we train and test the accuracy of the SVM classifier on 80\% of the dataset.
+Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
+We choose SVM as it gives the highest prediction rate.
+We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
+
+We hand-coded using five characteristics:
+
+\begin{enumerate}
+    \item \textbf{Local Public Goods}: Whether the bills provided a local public good or service.
+Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
+To lay on this category, the service should have been targeted for a fraction of the population.
+    \item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law).
+    \item \textbf{Oversight}: Legislation requesting information on the status of service provision.
+    \item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
+    \item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
+\end{enumerate}
+
+We run the SVM on the hand-coded data.
+Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded.
+In all models, we set cost equals 10 to avoid overfitting.
+
+\begin{table}
+\centering
+\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
+\label{accurClassif}
+\begin{tabular}{lc} 
+\hline
+\textbf{Variable}            & \textbf{Accuracy}  \\ 
+\hline
+Local Public Goods           & 93.8               \\
+Public Goods and Legislation & 94.2               \\
+Oversight                    & 94.9               \\
+Others                       & 93.5               \\
+Education and Health Care    & 92.5               \\
+\hline
+\end{tabular}
+\end{table}
+
+After we classify all the bills, the frequency in each category was added to the main paper.
+We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
+As expected, the results changed little from when we considered the absolute values.
+
+\newpage
+
+\subsection{City Councilors Survey\label{appsurv}}
+
+From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period.
+We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.
+
+We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
+In December 1st we closed the pool, having 174 responses.
+Figure \ref{geodistrsurv} displays a distribution of responses.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/distrrespsurvey2019.pdf}}
+      \caption{Geographical Distribution of Survey Responses}
+      \bigskip
+      \label{geodistrsurv}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative.
+We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions.
+We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
+In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
+
+\begin{table}[htp!]
+\centering
+\caption{Proportions for each bin used in the weighting process}
+\label{tabweight}
+\begin{tabular}{lccc}
+\hline
+& Sample & Population & Weighted \\
+& Proportions & Proportions. & Proportions \\
+\hline
+\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
+\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
+\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
+\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
+\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
+\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
+\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
+\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
+\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
+\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
+\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
+\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
+\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
+\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
+\end{tabular}
+\end{table}
+
+Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.
+
+The questions of interest for this research, asked in the survey were:
+
+\begin{enumerate}
+    \item No Brasil é comum que o prefeito tenha de negociar para ter maioria na Câmara de Vereadores.
+Com que frequência, o(a) Sr(a) acha que o prefeito usa os seguintes dispositivos para conseguir apoio?
+    \item Quais dessas atividades o(a) Sr(a) acredita serem mais comuns no trabalho da maioria dos vereadores?
+    \item Quais dessas atividades o(a) Sr(a) acredita que ajudam mais um vereador durante a eleição?
+\end{enumerate}
+
+A free translation to English would be:
+
+\begin{enumerate}
+    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
+    \item Which of those activities do city councilors perform the most in their representation practices?
+    \item Which of the following activities do you believe helps city councilors the most in elections?
+\end{enumerate}
+
+The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
+Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6.5in,angle=0]{figs/commonJobsCouncilorsJan2019.pdf}}
+      \caption{City Councilor's Common Activities}
+      \bigskip
+      \label{commonservice}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+The last question measures the willingness of mayors to give services to city councilors.
+This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors.
+Figure \ref{mayorneg} shows the results for the mayoral activities.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6.5in,angle=0]{figs/strategySupportMayorsJan2019.pdf}}
+      \caption{Mayor negotiated services in exchange of support}
+      \bigskip
+      \label{mayorneg}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield.
+The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.
+
+Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors.
+Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.

### 2021-08-04 article/article.Rmd
changes article and appendix - adding model 1

@@
 title:  |
-        | The Effect of Legislature Size on Public Spending:
-        | A Meta-Analysis
+        | Legislature Size and Welfare:
+        | Evidence from Brazil
 author: 
-  - Huzeyfe Alptekin[^huzeyfe]
+  - Gabriel Cepaluni[^gabriel]
   - Danilo Freire[^danilo]
   - Umberto Mignozzetti[^umberto]
-  - Catarina Roman[^catarina]
 date: \today
-thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback.
-We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
-Replication materials are available at <https://github.com/danilofreire/legislature-size-meta-analysis>.
-We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
-abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures.
-Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration.
-However, recent studies have questioned the validity of the theory.
-In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending.
-Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets.
-Yet the aggregate results show significant heterogeneity.
-While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending.
-The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
+thanks: "We thank Cedric Antunes, Victor Araujo, Eric Arias, Taylor Boas, Natalia Bueno, Andrea Freitas, Saad Gulzar, James Mahon, Lucas Novaes, Nelson Ruiz, Catarina Roman, David Skarbek, and Denis Stukal for their valuable comments.
+We also thank the participants of seminars and conferences at CEPESP, CUNY, INSPER, IPSA, LACEA, LASA, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.
+We gratefully acknowledge the financial support of the São Paulo Research Foundation (FAPESP), grant number 2017/07290-5.
+All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
+abstract: "What is the effect of legislature size on social welfare?
+While the literature suggests that increasing the number of legislators broadens political representation and raises government expenditures, its implications for public service provision remain understudied.
+In this paper, we exploit exogenous changes in city-council size in Brazil and show that adding a legislator increases education and healthcare indicators.
+XXXX Education quality and preventive health care remain unaffected, but primary school enrolment and infant mortality significantly improve.
+To investigate the mechanism, we surveyed former councillors and analysed 346,553 bills proposed between 2005 and 2008.
+This analysis shows that politicians prefer to provide private and targeted goods instead of public goods.
+This paper has implications for the design of legislative institutions."
 abstractspacing: double
-keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
-jelcodes: H21; H23; H50; H61
+keywords: Legislature size; Legislative politics; Public goods provision; Regression discontinuity design; Brazil
+jelcodes: HXXXX
 fontsize: 11pt
@@
 ```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
-# Clean up
-rm(list = ls())
-
-## Starting
-set.seed(732578) # From random.org
-
-# Needed packages
-pkgs <- c("tidyverse", "meta", "metafor",
-          "readxl", "data.table",
-          "knitr", "gridGraphics", "gridExtra",
-          "ggpubr", "kableExtra", "magick")
-
-# Install if not already installed
-installIfNot <- function(x) {
-  if (x %in% rownames(installed.packages()) == FALSE)
-    install.packages(x, dependencies = T,
-					 repos = "http://cran.us.r-project.org")
-}
-lapply(pkgs, installIfNot)
-
-# Load packages
-lapply(pkgs, require, character.only = T)
-devtools::install_github("isubirana/compareGroups")
-library("compareGroups")
-
-# Load datasets
-load("../dataset/dataCoefs.RData")
-
-# Build plot function for forest plots
-build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
-  # Build dataset for plot
-  mod2 <- tibble(
-    TE = mod$TE,
-    seTE = mod$seTE,
-    studlab = mod$studlab,
-    lower = mod$lower,
-    upper = mod$upper,
-    group = "A") %>%
-    bind_rows(.,
-              aux = tibble(
-                TE = c(mod$TE.random, NA),
-                seTE = c(mod$seTE.random, NA),
-                studlab = c("Overall Effect",
-                            "Prediction Interval"),
-                lower = c(mod$lower.random,
-                          mod$lower.predict),
-                upper = c(mod$upper.random,
-                          mod$upper.predict),
-                group = "B")) %>%
-    group_by(studlab) %>%
-    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-    ungroup()
-
-  # Graph limits
-  limg <- max(abs(c(mod2$lower, mod2$upper)))
-
-  # Build plot
-  p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab2, TE),
-               x = TE, xmin = lower, xmax = upper)) +
-    geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group),
-                   height = 0.1) +
-    scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
-    scale_y_discrete(
-      labels = function(x)
-        str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept = 0,
-               color = "#000000", linetype = "dashed") +
-    labs(x = "",
-         y = "") +
-    facet_grid(group~., scales = "free", space = "free") +
-    labs(caption = capt,
-         title = ttl) +
-    theme_minimal() %+replace%
-    theme(strip.text.y = element_blank(),
-          legend.position = "none",
-          axis.text.y = element_text(size = .8 * lsize,
-                                     hjust = 1),
-          axis.text.x = element_text(size = .6 * lsize,
-                                     hjust = 1.1),
-          plot.caption = element_text(size = lsize),
-          plot.title.position = "plot",
-          plot.title = element_text(hjust = 0.5,
-                                    face = "bold",
-                                    margin = margin(0, 0, 10, 0)),
-          panel.grid.major = element_blank())
-  return(p)
-}
-
-# Build forest plot for heterogeneous analysis
-# Build plot function for forest plots
-build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
-  mod <- update(mod, byvar = hetvar, print.byvar = F)
-
-  # Build dataset for plot
-  mod2 <- tibble(
-    byvar = mod$byvar,
-    TE = mod$TE,
-    seTE = mod$seTE,
-    studlab = mod$studlab,
-    lower = mod$lower,
-    upper = mod$upper,
-    group = "A") %>%
-    arrange(byvar)
-  auxmod <- tibble()
-  for (i in rev(mod$bylevs)){
-    auxmod <- rbind(auxmod, tibble(byvar = i,
-                    TE = NA,
-                    seTE = NA,
-                    studlab = toupper(i),
-                    lower = NA,
-                    upper = NA,
-                    group = "B"))
-    auxmod <- rbind(auxmod, 
-                    filter(mod2, byvar==i) %>% 
-                      arrange(desc(TE)))
-    auxmod <- rbind(auxmod, tibble(
-      byvar = i,
-      TE = mod$TE.random.w[which(mod$bylevs==i)],
-      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
-      studlab = 'Subgroup Effect',
-      lower = mod$lower.random.w[which(mod$bylevs==i)],
-      upper = mod$upper.random.w[which(mod$bylevs==i)],
-      group = "B"))
-  }
-  auxmod <- rbind(auxmod, tibble(
-    byvar = NA,
-    TE = c(mod$TE.random, NA),
-    seTE = c(mod$seTE.random, NA),
-    studlab = c("Overall Effect", "Prediction Interval"),
-    lower = c(mod$lower.random, mod$lower.predict),
-    upper = c(mod$upper.random, mod$upper.predict),
-    group = "B"))
-  mod2 <- data.frame(auxmod)
-  mod2$byvar <- toupper(mod2$byvar)
-  TEaux <- mod2$TE
-  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
-
-  # Graph limits
-  limg <- max(abs(c(mod2$lower, mod2$upper)))
-
-  # Build plot
-  p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab, TEaux),
-               x = TE, xmin = lower, xmax = upper)) +
-    geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group),
-                   height = 0.1) +
-    scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
-    scale_y_discrete(
-      labels = function(x)
-        str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept = 0,
-               color = "#000000", linetype = "dashed") +
-    labs(x = "",
-         y = "") +
-    facet_grid(byvar~., scales = "free", space = "free") +
-    labs(caption = capt,
-         title = ttl) +
-    theme_minimal() %+replace%
-    theme(strip.text.y = element_blank(),
-          legend.position = "none",
-          axis.text.y = element_text(size = .8 * lsize,
-                                     hjust = 1),
-          axis.text.x = element_text(size = .6 * lsize,
-                                     hjust = 1.1),
-          plot.caption = element_text(size = lsize),
-          plot.title.position = "plot",
-          plot.title = element_text(hjust = 0.5,
-                                    face = "bold",
-                                    margin = margin(0, 0, 10, 0)),
-          panel.grid.major = element_blank())
-  return(p)
-}
+# XXXX
 ```
 
-[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
 
@@
 
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
-[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
 
@@
 
-Over the past decades, a large literature has examined the relationship between
-legislature size and public expenditure. @weingast1981political provided the
-general framework to analyse distributive politics. The authors argue that the
-larger the number of legislative districts ($n$), the smaller the share of tax
-burden each one will bear ($1/n$), thus legislators have an incentive to
-overspend in their districts and transfer the costs to the entire polity. Early
-studies that empirically tested the "law of $1/n$", as the theory is currently
-known, indeed found a positive correlation between the number of legislature
-seats and different measures of government spending, although these first
-results were mainly based on US state legislatures and the effect was often
-limited to one house [e.g., @baqir2002districting; @gilligan1995deviations;
-@gilligan2001fiscal].
+Legislative institutions are crucial for welfare and service provision in democratic countries.
+Historically, the division of power and the birth of a representative government placed the legislatures at the center of popular consent \citep{north1989constitutions}.
+In modern democracies, most countries have assemblies at all levels of government.
+These institutions affect the information and quality of legislation \citep{krehbiel2010information}, check and veto the other political powers \citep{tsebelis2002veto}, and influence policymaking \citep{weingast1988industrial, north1989constitutions, auriol2012optimal}.
+Moreover, they also determine taxation, government expenditure \citep{Weingastetal1981, PrimoSnyder2008, stasavage2011states}, and oversee service provision \citep{mccubbins1984congressional, poulsen2018political}.
 
-Later research, however, has questioned the validity of the "law of $1/n$".
-@primo2008distributive affirm that, due to spatial spillovers, a collection of
-small districts can supply public goods more efficiently than the central
-government. The authors conclude that a "reverse law of $1/n$" may hold,
-wherein a higher number of legislators in small constituencies decrease the
-overall public spending. Similarly, @primo2006stop and @chen2007law find that
-lower and upper chambers may have mixed effects on government spending, while
-@petterssonlidbom2012size argues that the impact of larger chamber sizes is
-negative when using data from Finland and Sweden.
+Regardless of differences in electoral rules, social composition, and procedures, all legislatures share one feature: more than one representative composes them.
+Legislature size relates to collective action problems \citep{crain1979cost, rogers2002free}, government spending \citep{Weingastetal1981, PrimoSnyder2008}, and representation \citep{allenrepresentation}, but how these components affect welfare remain understudied.
+On the one hand, enlarged legislatures increase government spending and lawmaking, and this may improve some services \citep{Weingastetal1981, }.
+On the other hand, adding a legislator can increase the number of veto players and broaden the collective action problems, hindering service provision.
+Therefore, larger legislatures have an ambiguous effect on welfare, and XXXX.
 
-Since many empirical tests of the "law of $1/n$" have produced conflicting
-results, scholars have expanded this research agenda and closely investigated
-how institutional factors condition the original formulation of the theory. For
-instance, authors such as @crowley2019law and @pecorino2018supermajority
-accurately point out that collective action problems have been overlooked in
-the literature, and recent findings indicate that bicameralism
-[@maldonado2013legislatures], intergovernmental competition
-[@crowley2015local], redistricting [@lee2018court], and party ideology
-[@bjedov2014impact] strongly influence the relationship between seats and
-spending. Moreover, the literature has increasingly applied causal inference
-designs to estimate the effect of the "law of $1/n$", and in contrast to
-previous studies using panel data, regression discontinuity designs generally
-indicate that more legislators decrease public expenditures
-[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
-respect, scholars have long been aware of the theoretical and empirical
-limitations of the "law of $1/n$", and the proliferation of new studies reflect
-a conscious attempt to assess the robustness of the theory [@crowley2019law].
+In this paper, we propose a theory of legislature size and welfare that takes into account two crucial components: the XXXX and the partisan affiliation of the legislators.
 
-In this letter, we conduct the first meta-analysis that tests the generality of
-the "law of $1/n$". We select `r length(unique(dat$id))` articles that
-use quantitative methods to evaluate the impact of legislature size over
-government spending across several dimensions. Our study sample mirrors the
-diversity of the literature. Out of the `r dim(dat)[1]` coefficients
-included in our main analysis, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
-them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
-are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
-are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant. Given the volume and the disparity of
-the studies, we employ meta-analysis to summarise the results. Meta-analysis
-provides a rigorous approach to combine heterogeneous outcomes into a single
-estimation, and it allows scholars to gain valuable insights from the
-aggregated data [@cooper2019handbook; @hedges1985statistical]. Meta-analysis
-can also identify potential sources of study variability, enabling researchers
-to assess threats to external validity and direct future efforts into more
-promising areas of academic inquiry [@doucouliagos2008democracy]. Research
-synthesis methods have been successfully applied in medicine and psychology
-since the 1970s [@glass2015meta], and our work contributes to the burgeoning
-literature that uses meta-analytic methods to understand challenging questions
-in political science [@costa2017responsive; @doucouliagos2008democracy;
-@green2013field; @lau2007effects; @schwarz2020supporting].
+XXXX Umberto: Parei aqui.
 
-We run binomial tests and meta-regressions to further evaluate the relationship
-between legislature size and government expenditures. We use binomial tests
-to assess whether the proportions of positive and negative coefficients in our
-sample are statistically different from each other. In the meta-regressions, we
-measure the effect of five moderators that capture different sources of
-heterogeneity in the literature. As our sample includes both published and
-unpublished articles, we also construct a series of funnel plots to test for
-publication bias in existing research on the "law of $1/n$"
-[@easterbrook1991publication; @gerber2001testing].
+This paper fills this gap by studying the effects of legislature size on service provision.
+Assuming that politicians want to further their careers, we argue that two variables determine service provision: the perceived importance of the service by voters and the politician's capacity to claim credit for its provision.
+Politicians perform a simple cost-benefit analysis: if providing a service results in high electoral yield, and it is easy to claim credit for, politicians will produce this service abundantly.
+When a service is hard to claim credit for, politicians only invest their time if it is highly preferred by voters.
+Finally, when services are both hard to claim credit for and of low importance to voters, they are placed at the bottom of the politicians' priorities.
 
-Aggregate results indicate that legislature size has no significant impact on
-public spending. All of our main meta-analysis estimates show that the overall
-effect is not statistically different from zero, thus confirming the
-conflicting findings reported by the literature. However, when we look only at
-articles that employ regression discontinuity designs, we see that all three
-papers included in our sample suggest that a higher number of legislators leads
-to lower public spending [@debenedetto2018effect; @hohmann2017effect;
-@lewis2019legislature]. In this regard, it is possible that methodological
-choices partially explain the divergent results observed in the literature, as
-studies that use causal inference methods consistently point to the same
-direction. One limitation of this finding is that these studies only test the
-impact of lower house size on the natural logarithm of expenditure per capita,
-thus it remains unclear whether the results hold with other variables.
+To test this theory, we exploit an exogenous variation in Brazilian city council sizes.
+In 2004, the judiciary reinterpreted the constitution, unexpectedly changing the number of city councilors in Brazilian municipalities.
+Before the decision, towns could freely choose their legislature size, but in March 2004, the Superior Electoral Court created population thresholds, adding one councilor for each set of 47,619 inhabitants.
+Around the cutoffs, this decision represents an exogenous change in city council size, allowing us to investigate the welfare effects of increasing the legislatures in Brazil.
 
-The meta-regressions provide additional evidence that our study sample is
-highly heterogeneous and that effect sizes differ substantially according to
-study specifications. When using our extended sample of `r dim(fulldat)[1]`
-coefficients, we find that unicameralism is associated with higher public
-spending, as predicted by the "law of $1/n$". Since most unicameral
-legislatures are located in local governments (municipalities or districts),
-this result supports the theory strictly in its first formulation. Moreover,
-our meta-regressions indicate that larger upper chambers spend more in terms of
-per capita expenditure than lower chambers, a result that also appears in the
-binomial tests. Non-majoritarian voting systems decrease government spending as
-a percentage of GDP, but they do not have a relevant impact on the other
-measures of public expenditure, following the idea that the $1/n$ effect grows
-weaker as the empirical cases distance from the original definition of the law.
-Finally, meta-regression results confirm that regression discontinuity models
-reduce public spending estimates.
+Studying the 2005 to 2008 Brazilian mayoral term, when the ruling was in effect, we find improvements in health care and education.
+Increasing the council size by one legislator lowers infant mortality by 1.99 per one thousand infants born and increases elementary school enrollment by 2.58 children in kindergarten classrooms.
+However, the additional legislator had no influence on preventive health care and education quality.
+[] Voters place a high electoral premium on hospital care and mediating school enrollment is relatively easy to claim credit for.
+In line with our theoretical model, these services should improve with legislative size.
+On the other hand, preventive health care is harder to claim credit for, and school quality improvements are expensive and pay off only in the long-run.
+Thus, these services remain unchanged with larger legislatures.
 
-In summary, our results are in line with previous findings that lend partial
-support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
-An assessment of the effects of collective action costs in these analyses is
-crucial to determine the full mechanism operating behind these results.
-Overall, our analysis does not provide robust support for the theory as
-originally conceived.
+Finally, we present three sets of evidence that the results are consistent with the micro-level representation practices of city councilors.
+First, we show that the new councilor has access to government resources and uses public office appointments to mediate service provision.
+They have a 91\% chance of belonging to the mayoral coalition, and they appoint an average of 105 extra bureaucrats for many positions at the mayor's office, having loyal workers inside the municipal bureaucracy.
+Second, we analyzed 346,553 bills approved by city councilors in municipalities close to the council size thresholds.
+In line with our theory, we find that councilors prefer to provide targeted goods (72.9\% of all bills), as they satisfy the populations' needs and are easier to credit claim.
+Finally, we ran an online survey among the councilors during the period, showing that most councilors believe that voters prefer targeted services (68.8\%) to lawmaking (24.6\%) and oversight (30\%).\footnote{Councilors were able to select multiple categories, so the sum can be over 100\%.} We also refute three alternative explanations: increased representation of women and non-white legislators, change in electoral competitiveness, and a larger average of approved legislation by each councilor.
 
-# Data and Methods
+# Legislature Size, Legislative Support, and Welfare
+\label{sec:theory}
 
-We compiled our study sample in three search rounds. In the first round, we
-gathered data from three large academic databases (Scopus, Microsoft Academic,
-and Google Scholar) and looked for studies that were published in English and
-cited \citet{weingast1981political}, as it is the foundational work in the
-literature on the "law of $1/n$". To ensure that our sample was comparable, we
-only selected papers that used quantitative methods to analyse
-data\footnote{Since meta-analysis requires a single estimate per observation,
-we excluded articles that use interaction terms or quadratic specifications of
-our selected variables. Please refer to Section C in the Supplementary Material
-for a detailed description of the selection procedure. We also included two
-PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
-flow diagrammes \citep{liberati2009prisma} showing the number of resulting
-papers after each review step.}. After this stage, we identified six
-measurements that the literature often employs to quantify government
-expenditure and legislature size. For government expenditure, our study sample
-uses (i) public expenditure as a share of GDP; (ii) public expenditure per
-capita; and (iii) the natural logarithm of public expenditure per capita as its
-main variables of interest. In regards to legislature size, the variables are
-(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
-upper house size\footnote{There are a few important nuances concerning coding
-of these variables. Unicameralism, for example, is captured both by lower
-chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
-the literature estimates how institutional designs affect this relationship,
-ours and many other articles use both lower and upper chamber sizes as main
-explanatory variables. We did not find any article that used the natural
-logarithm of upper chamber size in their models.}.
+What is the effect of larger legislatures on public service provision?
+The most striking feature of a legislature is the fact that decisions are undertaken collectively.
+Legislators have to propose changes in the status-quo, agree upon what they want to decide, evaluate proposals put forward by mayors, discuss and improve the proposals, and decide which changes they will carry on.
 
-In the second round, we did not require articles to cite @weingast1981political
-and used a keyword-based query on Google Scholar to broaden the scope of the
-first search. The search string contained terms strongly associated with the
-literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
-"lower chamber size" OR "council size" OR "parliament size" OR "legislature
-size" OR "number of legislators" OR "legislative size") AND ("spending" OR
-"expenditure" OR "government size")`. We again restricted the search to
-articles written in English which employed quantitative methods. This search
-added two new results to our sample [@coate2011government;
-@debenedetto2018effect], but neither of them included variables beyond the six
-measures we had previously identified. In the third search round, we looked
-into the personal webpages of every author whom we had already included in our
-sample. The purpose of this manual search was to assess whether there was any
-working paper or unpublished manuscript that we had missed in the two former
-queries. All papers we found in the last search had already been included in
-our sample. Combined, the three searches produced a dataset of 
-`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March 2021.
-Table \ref{tab:papers} contains the full list of articles we analyse in this
-paper.
+In this sense, legislature size is critical in determining the efficiency of the decision-making process.
+Upon adding a new city councilor, the most simple change is the increased production capability.
+Legislative production, analogous to what happens in firms, may increase when adding an extra legislator \citep{crain1979cost, crain1982team, rogers2002free}.
+For instance, suppose that working full time, politicians can approve five bills a month.
+Ten politicians can together approve 50 bills, while 11 can pass 55.
+This increases the number of measures adopted, and if laws enact services to constituencies, then we shall witness an increase in service provision.\footnote{An alternative explanation relates to the Condorcet Jury Theorem.
+In these models, there is a binary choice, with one of them being ex-ante the best.
+If legislators access the best choice with a probability higher than 0.5, more legislators will increase the change of selecting the best choice \citep{myerson1998extended}.
+However, this logic assumes that politicians choose among exogenously provided proposals, which makes sense in the case of a jury, but is somewhat uncommon for legislatures.
+\citet{auriol2012optimal} compute the optimal size of chambers considering that this is the solution to the interplay between specialization costs and citizens' preferences.}
 
-\footnotesize
-\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
-\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
+However, increasing the size of legislatures also carries considerable costs.
+Larger legislatures can raise the transaction costs \citep{weingast1988industrial}, increase collective action problems \citep{crain1979cost}, and make  forming majorities more costly \citep{crain1982team}.
+These negative features, together with the fact that legislators may free-ride on each others' proposals, may decrease legislative productivity.
+For instance, if decisions need a majority or qualified majority to be approved, more legislators create a perverse incentive, increasing the difficulty of approval.
+Moreover, legislators are pressured to provide targeted services for their constituencies at the expense of the entire polity \citep{Weingastetal1981, PrimoSnyder2008}, and this can raise inefficiencies in expenditure allocation.
+Additionally, transaction costs within legislatures may increase the difficulty of passing bills \citep{weingast1988industrial, baron1989bargaining}.
+Therefore, it is unclear whether and how larger legislatures impact lawmaking and service provision.
+
+In our view, to understand the effects of larger legislatures, we need to consider the political motivations behind the legislator's work.
+While an extra politician may increase the productivity frontier of a legislature, the types of services that will be favored remain unclear.
+To understand the political motivations, we need a theory that accounts for the cost-benefit calculations performed by politicians.
+
+When deciding which service to prioritize, politicians look into two dimensions of the service provision.
+First, the competition with other legislators motivates politicians to provide services that they believe voters want, regardless of whether these policies improve long-term welfare.
+For instance, suppose that there are three services, organized hypothetically based on beliefs about which of these three voters are more likely to reward:\footnote{Note that there is a difference between \textit{what voters want} and what \textit{politicians believe voters want}.
+Although politicians and brokers mostly access voter's beliefs accurately \citep{FinanSchechter2012, Stokesetal2013}, the crucial signal that a politician gets is vote shares, which are aggregated.
+It is hard to disentangle which service generated the highest electoral yield for the politician.
+Therefore, the politician's beliefs play an essential role in the services that they prioritize.} improving a local health clinic (most preferred), building a playground (second most preferred), or increasing the quality of education (least preferable).
+Politicians seeking recognition will mostly want to improve the health care system, which they believe will most benefit their electoral yields.
+After getting this done, they will shift efforts toward the playground construction and finally to education quality.
+Therefore, increasing legislature size will disproportionately increase the provision of services that the politicians believe voters prefer and will reward the most in the polls.
+
+Second, to get reelected, besides providing the services that voters prefer, politicians have to take credit for facilitating provision \citep{fiorina1987personal, gulzar2017politicians, nielsen2017politicians, silva2017clarity}.
+Typically, the services that are easiest in terms of credit claiming are either providing local public goods, such as improving a neighborhood health clinic, or purely clientelistic and personalistic services \citep{Weingastetal1981, kuschnir2000cotidiano, Stokes2005, nichter2011electoral, Stokesetal2013, luna2014segmented, vieira2015clientelismo, bertholini2018pork}.
+This explains why clientelism and pork-barrel are persistent in democratic polities.
+Table \ref{tabcli} summarizes the incentives.
+
+\begin{table}[htp!]
+\centering
+\caption{Effects of Legislature Size on Service Provision}
+\label{tabcli}
+\scalebox{1}{%
+\begin{tabular}{@{}lcc@{}}
 \toprule
-\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
-\tabularnewline
+& \textbf{Hard for Credit Claim} & \textbf{Easy for Credit Claim} \\ 
 \midrule
-\endhead
-```{r papers, echo = FALSE, results = 'asis', cache = T}
-build_nams <- function(x) {
-  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
-  if(length(x_) == 1) return(x_)
-  else {
-    aux <- x_[1]
-      for (i in 2:length(x_))
-        if (i == length(x_)){
-          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
-        } else {
-          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
+\multirow{3}{*}{\textbf{Low ranked by voters}} & No changes & None or mild \\
+& or deterioration & improvements \\
+& (Preventive Health)  & (Honors bills) \\[0.5em]
+\multirow{3}{*}{\textbf{High ranked by Voters}} & Mild to low & Mild to strong \\ 
+& improvement & improvement \\
+& (Infant Mortality)  & (School Enrollment) \\
+\bottomrule
+\end{tabular}
 }
-  }
-  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
-                   sep = ''))
-}
-aux <- dat %>%
-  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
-  unique() %>%
-  arrange(year, depvar2)
-aux2 <- aux %>%
-  mutate(depvar2 = 'aux') %>%
-  unique()
-for(i in 1:dim(aux)[1]) {
-  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
-    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
-  } else {
-    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
-      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
-      aux$depvar2[i], sep = ', ')
-  }
-}
-aux <- aux2
-for (i in 1:dim(aux)[1]) {
-  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
-      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
-      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
-      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
-}
-```
-\bottomrule
-\label{tab:papers}
-\begin{minipage}{\textwidth}
-\renewcommand{\footnoterule}{}
-\vspace{-0.5cm}
-\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
-Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
-JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
-APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
-UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
-Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
-Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
-Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
-\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
-international standard.} 
-\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
-logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
-a percentage of GDP.}
-\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
-variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
-design.}
-\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
-representation).} 
-\end{minipage} 
-\end{longtable}
-\normalsize
+\end{table}
 
-Our study sample reflects the development of the literature. Although the "law
-of $1/n$" was first formulated in 1981, the empirical assessment of the theory
-only started a few years later, as dates of publishing range from `r min(dat$year)`
-to `r max(dat$year)`.
-Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
-papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
-Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`).
-Eight articles use cross-national data and analyse from 2 to 110
-countries. Early studies used OLS and panel data methods to estimate the
-results, while studies from 2012 onward have also applied causal inference
-designs such as instrumental variables and regression discontinuity models to
-test the relationship between house size and public spending.
+These two dimensions provide a simple yet powerful guide of the politicians' incentives.
+When voter places a high premium on the provision of a given service, and it is easy to claim credit for the provision, politicians will concentrate their efforts in providing it.
+The more politicians, the higher the provision of the service.
+Consider, for instance, constituency service, such as getting a child enrolled at a public school.
+The voters highly rank service such as this, and the politicians can break the school access directly, getting all the credit for the provision.
+Therefore, these services tend to increase, up to the point of being over provided.
 
-Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
-public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
-analyse the impact of legislature size on public expenditures as a percentage of
-GDP. This indicates that the area has refined the original definition of the "law of $1/n$"
-and tested the impact of larger legislatures on different measures of government
-spending. Our independent variables are lower chamber size 
-(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
-logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
-These six variables formed a $3 \times 3$ table, yet not all combinations were
-available in the data. We found no studies that correlate public expenditure
-per capita with either upper chamber size or the natural logarithm of lower
-house size. Thus, our meta-analysis contains seven of the nine possible
-variable combinations.
+When a service is hard to credit claim, to be provided, it has to be highly ranked by the voters.
+Consider services that decrease infant mortality.
+Although policies in this direction might be harder to be directly associated with one given politician, every politician wants to be known as the ones that diminished infant mortality.
+The death of a child has devastating effects over a polity, and no politician wants to be associated with it.
+On the other hand, every parent would be extremely thankful for the politicians that improved health care and saved their child.
+Moreover, politicians might facilitate access to medication and hospitals, which in turn is easier for credit claiming.
+Therefore, these services will have anywhere from modest to substantial improvements.
 
-We also coded five moderators that may help us understand the heterogeneity in
-the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study. The
-additional moderators are: 1) publication year; 2) paper publication in an
-academic journal; 3) estimation method; 4) institutional design; 5) electoral
-system. Since the literature on the "law of $1/n$" is notably diverse, we
-added only moderators that either refer to important theoretical questions,
-such as the effect of the electoral system on public spending, or to essential
-characteristics of the publications themselves. Although more moderators exist
-in the literature (e.g., data aggregation level), they do not appear as often
-as necessary for their inclusion in the meta-regressions. Table
-\ref{tab:descriptive} shows the descriptive statistics of the moderator
-variables.
+Suppose now that service is secure to credit claim for, but gives low electoral yield.
+In this case, although the provision can be unquestionably traced back to the legislator, voters care little about the provision.
+For instance, honors and appraisal legislation are very common in Brazilian municipalities.
+However, they are perceived by politicians as low electoral yield, but the legislator that proposed the homage usually gets associated with it.
+These types of legislation increase with legislature size, but their effect on welfare is negligible.
+
+Finally, services that are difficult to credit-claim, or that politicians believe that voters care very little about, are expected to receive little invested effort from politicians.
+For instance, consider preventive health care.
+Preventive care refers to health measures, such as prenatal care or vaccination, undertaken to lower the chances or the severity of a disease(s) in the future.
+However, it is a compounded chance: the voter has to consume the service, but its effectiveness depends on voters getting sick.
+Nowadays, we are witnessing how hard it is to vaccinate children, despite all the scientific evidence demonstrating its effectiveness.
+Moreover, rational voters may fail to punish politicians for low investments in preventive public policies, such as natural disasters or climate change mitigation \citep{gailmard2019preventing}.
+Hence, voters might also not punish politicians for low investments in preventive health care because they might only observe whether a politician properly invested in preventive public policies in cases of emergency.
+Therefore, we shall expect little to no improvement in these types of services with larger legislatures.
+
+In sum, these considerations suggest that instead of looking for overall positive or negative effects, the effects of legislature size should manifest diversely, conditional on the type of service studied.
+The most significant changes should be expected in services that voters want and that are easier to claim credit for.
+Services with only one of these characteristics will be intermediate in terms of their priority and efforts exerted by politicians in their provision and will improve with less intensity.
+Services hard to credit claim and low ranked by voters will tend to be unaffected or under-provided by lawmakers.
+
+# Background on the Brazilian Case
+\label{sec:background}
+
+In 2004, Brazil comprised 5,560 municipalities.
+According to the Brazilian Constitution, each city must provide healthcare, primary education, transportation, and infrastructure to its citizens.
+Municipalities have the authority to enact local laws and collect taxes on housing and services.
+However, their room for fiscal manipulation is limited.
+On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%.
+This reduces the ability of municipal legislators to effectively influence local spending, what makes improvements in local services dependent only on the efforts of city-level politicians.
+XXXX
+
+With regards to their political organisation, municipalities have one mayor and one city council.
+Citizens choose their representatives by direct vote in the same election.
+Mayors are in charge of organising the provision of public services, as well as proposing laws and amendments to the tax code.
+Proposals submitted by the mayor are subject to the approval of the city council.
+Councillors, in turn, have two primary duties.
+First, they should discuss and vote legislation put forward by the mayors or by their peers.
+Second, they oversee the public budget and sanction mayors who do not comply with fiscal legislation.
+Councillors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrolment, and even paying their voters' utility bills \citep{nichter2011electoral, AlmeidaFelix2012}.
+
+Until 2004, there was no specific regulation on the size of city councils.
+The 1988 Brazilian Constitution set only broad guidelines about the number of council seats in each municipality, which allowed cities to determine how many legislators they should have in their local chambers.
+This led to severe imbalances in the proportion of representatives per citizen across the country.
+For instance, the Nova Russas municipality had 30,009 inhabitants and 21 councillors, which accounts for one legislator per 1,429 citizens.
+In contrast, the city of Sorocaba had only 15 councillors for 528,735 inhabitants, that is, one legislator per 35,249 citizens.
+In 2003, this malapportionment problem gained national visibility when Mira Estrela, a small municipality with only 2,651 residents, reduced its city council from 11 to 9 seats because of fiscal considerations.
+The change motivated a legal dispute that reached the Brazilian Supreme Court.
+The Court favoured the city's decision and ruled that the size of every local council should correspond to precise population thresholds.
+
+Following the ruling of the Supreme Court, in March 2004 the Brazilian Electoral Court established a series of population cutoffs for all municipal legislatures.
+The Court specified that, following the Brazilian Constitution, cities with up to one million residents should have between 9 and 21 legislators.
+The number of seats was allocated as follows.
+Each city starts with 9 councillors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members.
+This threshold implies that cities with a population between 571,428 and one million should all the same number of legislators, that is, 21 of them.
+Conversely, cities between one and four million inhabitants should have at least 33 councillors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.
+
+This decision makes Brazil the ideal testing ground for our theory.
+Although an endogenous decision motivated the Electoral Court ruling, the population cutoffs created sharp discontinuities in the distribution of local council seats.
+That is, cities close to the cutoffs had very similar characteristics, but those which were just above the threshold gained a new legislator.
+Moreover, cities could not self-select into any group, as their population estimates were calculated using the 2003 projections by the Brazilian Census Bureau (IBGE).
+This change in council size also happened only seven months before the election, making it impossible for candidates to adjust their service provision strategies for the 2004 election.
+Therefore, the ruling allows us to study the effect of larger legislatures on public service provision during the 2005-2008 term while holding all else constant.
+
+\section{Empirical Strategy}
+\label{sec:empstrat}
+
+\subsection{Methodology}
+\label{sub:methods}
+
+We employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Superior Electoral Court resolution as treatment indicators.
+Figure \ref{fig:runningvarplot} displays the distribution of municipalities within each city council size.
+These population thresholds remained in effect until 2009, when Congress amended the Brazilian Constitution.
+This study covers the period between 2005 and 2008, which constitutes the full mayoral and city-council term following the 2004 Brazilian elections.
 
@@
 
-\footnotesize
-```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
-fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
-aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
-              year, published, instdesign) %>%
-  rename(`Independent Variables` = indepvar2,
-         `Year`                  = year,
-         `Published work`        = published,
-         `Estimation method`     = method,
-         `Institutional Design`  = instdesign,
-         `Electoral system`      = elecsys2)
-aux$`Independent Variables` <- recode(aux$`Independent Variables`,
-                                      `N` = "Lower Chamber Size",
-                                      `K` = "Upper Chamber Size",
-                                      `logN` = "Log of Lower Chamber Size")
-aux$`Electoral system` <- recode(aux$`Electoral system`,
-                                 `Non-Maj` = "Non-Majoritarian",
-                                 `Maj` = "Majoritarian")
-aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/distrseats2019.pdf}}
+      \caption{Distribution of Municipalities by Population and City Council Size XXXX CHANGE HERE}
+      \bigskip
+      \label{fig:runningvarplot}
+    \end{minipage}
+  \end{center}
+\end{figure}
 
-export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-                        show.p.overall = F, show.all = T),
-          caption = "Descriptive statistics of moderators",
-          format  = "latex")
-```
-\normalsize
+Our identification strategy relies on three assumptions.
+First, we assume that no municipality self-selected into each side of the discontinuity.
+Second, as we run a sharp RDD, we also assume that council size increases precisely as the law mandates.
+Third, our design assumes that the pre-treatment variables, collected before the 2003 Supreme Court decision, were not affected by the 2004 ruling on council size.
+In the online appendix, we test these assumptions by building an estimator that balances the local average treatment effects (LATE).
+Our estimate is an extension of RDD and uses covariates to balance the multiple cutoff differences.
+Additionally, we propose a placebo test in which we run the same models with fake cutoffs around the original thresholds.
+Our balance and placebo tests indicate that the assumptions underlying the analyses are indeed met.
 
-A key methodological issue we had to address concerns the potential violation
-of an important assumption in a meta-analysis, that of effect size independence
-[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
-sample, authors frequently use similar datasets in their models,
-and almost all papers fit more than one regression with similar variables, what
-suggests that the assumption above does not hold. We use two procedures to tackle this
-problem. First, we created two sets of study coefficients to reduce the impact
-of multicollinearity in our estimations. The first group includes only the most
-rigorous models from each paper, that is, those estimated with the largest $n$,
-most control variables, and fixed effects if the authors added them. If the
-article employed a regression discontinuity design, we chose the coefficient
-from the optimal bandwidth or from the intermediate one. This sample
-encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
-articles analysed two dependent or independent variables of
-interest\footnote{The papers that used more than one dependent or independent
-variable of interest are \citet{baqir1999districts, bjedov2014impact,
-bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
-gilligan2001fiscal, lee2016supermajority, lee2018court,
-maldonado2013legislatures, primo2006stop, ricciuti2003trading,
-ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
-`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
-papers. Here we focus on the results for our restricted sample as we consider
-them more robust, but the findings are very similar when we use the extended
-set.
+% Subsection: Variables
+\subsection{Variables and Data Sources}
+\label{sub:sources}
 
-Our second procedure consists of employing multilevel random effect models
-[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
-extra levels to the regular meta-analysis, one including a unique publication
-ID for each paper, and another indicating the data source used in the original
-study. By adding these two levels, we account for within- and between-study
-variation, thus removing these sources of effect size dependency and improving
-the accuracy of the results. More information about the multilevel models can
-be found in Section H of the Supplementary Material.
+We use four groups of city-level variables in our models.
+The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution.
+We add them to the models to improve the balance between treated and non-treated units.
+The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality.
+The data come from the Superior Electoral Court (Tribunal Superior Eleitoral--TSE) and the 2000 Brazilian census.
 
-We use Hedges' $g$ to calculate effect sizes in our meta-analysis
-[@hedges1981distribution]. While there are other methods to standardise
-coefficients in meta-analytic studies, Hedges' $g$ corrects for upward bias in
-small sample sizes and is considered more robust than measures such as Cohen's
-$d$ [@lakens2013calculating]. We estimate the Standardised Mean Difference
-(SMD), which represents the effect size in each study relative to the
-variability observed in that study, by extracting the coefficients and the
-standard errors from all articles included in our sample and converting them to
-Hedges' $g$. In cases where authors did not report the standard errors for
-their estimates, we computed them using the t-statistic presented in the
-original tables.
+We employ a second set of variables to quantify social welfare.
+They are our outcomes of interest.
+Our main focus here is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
+We measure access to education with the average enrolment in primary (K--4) and secondary (5--8) public schools.
+We assess education quality with the Education Development Index (\'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
+The index is a weighted average of student scores in Portuguese and Mathematics (0--10) multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
+To test the effect of the 2004 ruling on healthcare, we mapped the coverage of the Family Health Programme, a local-level primary care policy, and the proportion of pregnant women who attended more than six pre-natal consultations.
+We also gather data on post-neonatal mortality\footnote{Post-neonatal mortality rate is the probability of dying between 28 days and one year of life, expressed per 1,000 live births.} to assess healthcare quality.
+The source of all variables is the Brazilian Ministry of Health Data Centre (DataSUS).
+
+Next, we look into municipal data, city councillors' characteristics, approved legislation, and an online survey with 174 former city councillors that served during the 2005--2008 term to test our proposed micro-level mechanisms\footnote{We also analysed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
+The authors asked councillors about their daily work.
+The interviews reinforced the idea that councillors see private goods provision as more electorally profitable than formal lawmaking or executive policy oversight.}.
+The municipal data contains: 1) the number of councillors belonging to the pre-electoral mayoral coalition; 2) the councillor's gender and race; 3) the number of mayor-appointed, councillor-appointed, and career civil servants.
+All variables come from the Superior Electoral Court and the Brazilian Institute for Geography and Statistics.
+
+Lastly, we also collect 346,553 bills from cities whose populations lie within 10 thousand inhabitants from the 2004 population thresholds.
+We selected 64 out of 202 municipalities whose voting records were available online.
+We evaluate information regarding proposal types, discriminating between local and municipal public goods, oversight, and other legislative activity.
+While local public goods consist of services targeting personal, group, or neighbourhood levels, municipal public goods comprise laws and policies covering the entire municipality.
+Examples of the first are investing in a given public health clinic, requesting school bureaucracy to accommodate an extra child, and renovating sewage and fixing potholes on a given street\footnote{Our theory does not differentiate between clientelism and service provision, as it is hard to disentangle legislator's intentions.
+On the one hand, a voter may request a particular service, such as fixing a pothole.
+Attending this request can be interpreted as a clientelistic practice, despite their non-excludable benefits to the adjoining neighborhood.
+On the other hand, upon request, facilitating hospital admission is a very particularized service, thus likely to fall under clientelistic logic.
+Saying this is vote-buying can be imprecise, as service provision might simply be a way of signaling responsiveness to the electorate's demands and efficacy.
+\citet{kuschnir2000cotidiano}'s qualitative work shows the Silveira Family in Rio de Janeiro aided the community they represented regardless of political preference.
+As a result, when one of the family members ran in an election, he had the highest vote share ever seen in Rio de Janeiro.}.
+As for the latter, examples are to ameliorate education by capacitating public teachers, and to raise public health care standards through city-wide vaccination campaigns.
+Oversight bills are accountability and transparency mechanisms meant to keep public services undertaken by the bureaucracy in check.
+Other legislation comprises bills that do not fit in the previous categories.
+Examples are changes in street names, motions to honour citizens or groups, and legislative and internal city council procedures.
+
+Together, this evidence provides a clear picture of representation patterns in Brazil, from municipal welfare consequences to their micro-level mechanisms.
+Summary statistics follow in the online supplemental materials.
 
@@
 
-The "law of $1/n$" states that more legislators increase government
-expenditure. In this paper, we employ three methods to test the empirical
-validity of that relationship. First, we run binomial z-tests to assess the
-frequency of positive and negative coefficients in our sample. Then, we fit 9
-multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
-`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
-Lastly, we run two sets of meta-regressions to measure the effects of a group
-of moderators on the effect sizes of our study sample. To recapitulate, our
-independent variables of interest are lower chamber size, the natural logarithm
-of lower chamber size, and upper chamber size. The dependent variables are
-public expenditure per capita, the natural logarithm of public expenditure per
-capita, and government expenditure as a percentage of GDP. Since the outcomes
-have different scales, we treat them separately in our models.
+% Session: Results
+\section{Results}
+\label{sec:outcomes}
 
-```{r, cache=TRUE, echo = FALSE}
-aux <- filter(dat, indepvar2 == "N")
-binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-aux <- filter(dat, indepvar2=='K')
-binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
-aux <- filter(dat, indepvar2 == "logN")
-binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-```
+\subsection{The Effect of Legislature Size on Service Provision}
+\label{sub:effects}
 
-## Binomial Z-Tests
-\label{sub:binomial}
+We study the impact of legislatures on two services: education and health care. We collect eight indicators: four in education, and four in health care.
 
-The binomial z-test evaluates whether the majority of the coefficients of our
-independent variables are positive or negative[^binomial]. If increasing the
-number of legislators leads to higher public expending, we should expect most
-coefficients to be positive. Conversely, if the "reverse law of $1/n" is true,
-our results should indicate that $p < 0.5$, that is, the proportion of positive
-coefficients is lower than 0.5. The null hypothesis here states that the sign
-of the coefficient is equally likely to be positive or negative.
+\begin{sidewaystable}[!htbp] \centering 
+  \caption{Public Service Outcomes} 
+  \label{tab:outcomes} 
+\scalebox{0.9}{
+\begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c }
+\toprule
+& \multicolumn{4}{c}{\textbf{Education Outcomes}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes}}  \\ \cline{2-5} \cline{6-9}
+  & \multicolumn{1}{c}{\small{(1)}} & 
+ \multicolumn{1}{c}{\small{(2)}} & 
+ \multicolumn{1}{c}{\small{(3)}} & 
+ \multicolumn{1}{c}{\small{(4)}} & 
+ \multicolumn{1}{c}{\small{(5)}} & 
+ \multicolumn{1}{c}{\small{(6)}} & 
+ \multicolumn{1}{c}{\small{(7)}} & 
+ \multicolumn{1}{c}{\small{(8)}} \\
+ & \multicolumn{1}{c}{\small{Average}} & 
+ \multicolumn{1}{c}{\small{Average}} & 
+ \multicolumn{1}{c}{\small{Elem. School}} & 
+ \multicolumn{1}{c}{\small{Middle School}} &
+\multicolumn{1}{c}{\small{Infant}} & 
+ \multicolumn{1}{c}{\small{Post-Natal}} & 
+ \multicolumn{1}{c}{\small{Cov. Family}} & 
+ \multicolumn{1}{c}{\small{Pr. Born w. 6+}} \\ 
+ & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
+ \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
+ \multicolumn{1}{c}{\small{Quality Index}} & 
+ \multicolumn{1}{c}{\small{Quality Index}} &
+ \multicolumn{1}{c}{\small{Mortality}} & 
+ \multicolumn{1}{c}{\small{Mort. Rate}} & 
+ \multicolumn{1}{c}{\small{Health Program}} & 
+ \multicolumn{1}{c}{\small{Pre-Natal Consult.}}\\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
+ LATE & 2.58$^{***}$ & -0.01 & -0.04 & -0.11 & -1.99$^{**}$ & -0.90$^{*}$ & -1.67 & -4.23 \\ 
+    & (0.81) & (1.07) & (0.13) & (0.11) & (0.78) & (0.48) & (2.09) & (4.01) \\
+  \hdashline \\[-1.8ex] 
+ N Left & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{7306} & \multicolumn{1}{c}{8597} & \multicolumn{1}{c}{5037} &
+ \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{19280} & \multicolumn{1}{c}{15548} \\ 
+ N Right & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{581} & \multicolumn{1}{c}{670} & \multicolumn{1}{c}{529} & \multicolumn{1}{c}{1030} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{1297} & \multicolumn{1}{c}{1030} \\
+ Eff N Left & \multicolumn{1}{c}{196} & \multicolumn{1}{c}{475} & \multicolumn{1}{c}{387} & \multicolumn{1}{c}{279} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{314} & \multicolumn{1}{c}{281} & \multicolumn{1}{c}{615} \\
+ Eff N Right & \multicolumn{1}{c}{202} & \multicolumn{1}{c}{312} & \multicolumn{1}{c}{283} & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{390} & \multicolumn{1}{c}{242} & \multicolumn{1}{c}{301} & \multicolumn{1}{c}{438} \\
+ BW Loc Poly & 5.132 & 11.208 & 8.724 & 7.824 
+ 7.720 & 7.183 & 4.185 & 8.891 \\ 
+ BW Bias & 10.615 & 16.694 & 15.186 & 13.714 
+ 12.289 & 10.726 & 8.310 & 15.007 \\ 
+\midrule 
+ & \multicolumn{4}{c}{\textbf{Education Outcomes -- Placebo Cutoffs}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes -- Placebo Cutoffs}}\\ \cline{2-5} \cline{6-9}
+  & \multicolumn{1}{c}{\small{(9)}} & 
+ \multicolumn{1}{c}{\small{(10)}} & 
+ \multicolumn{1}{c}{\small{(11)}} & 
+ \multicolumn{1}{c}{\small{(12)}} & 
+ \multicolumn{1}{c}{\small{(13)}} & 
+ \multicolumn{1}{c}{\small{(14)}} & 
+ \multicolumn{1}{c}{\small{(15)}} & 
+ \multicolumn{1}{c}{\small{(16)}} \\
+ & \multicolumn{1}{c}{\small{Average}} & 
+ \multicolumn{1}{c}{\small{Average}} & 
+ \multicolumn{1}{c}{\small{Elem. School}} & 
+ \multicolumn{1}{c}{\small{Middle School}}&
+ \multicolumn{1}{c}{\small{Infant}} & 
+ \multicolumn{1}{c}{\small{Post-Natal}} & 
+ \multicolumn{1}{c}{\small{Cov. Family}} & 
+ \multicolumn{1}{c}{\small{Pr. Born w. 6+}}\\ 
+ & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
+ \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
+ \multicolumn{1}{c}{\small{Quality Index}} & 
+ \multicolumn{1}{c}{\small{Quality Index}} &
+ \multicolumn{1}{c}{\small{Mortality}} & 
+ \multicolumn{1}{c}{\small{Mort. Rate}} & 
+ \multicolumn{1}{c}{\small{Health Program}} & 
+ \multicolumn{1}{c}{\small{Pre-Natal Consult.}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
+  LATE & 0.45 & 0.97 & -0.10 & -0.12
+  & -1.14 & -0.25 & 1.85 & -2.22 \\ 
+  & (0.61) & (0.98) & (0.11) & (0.09)
+  & (1.05) & (0.65) & (1.25) & (2.92) \\ 
+  \hdashline \\[-1.8ex]   
+ N Left & \multicolumn{1}{c}{9040} & \multicolumn{1}{c}{6350} & \multicolumn{1}{c}{7529} & \multicolumn{1}{c}{4243} & \multicolumn{1}{c}{10614} & \multicolumn{1}{c}{4449} & \multicolumn{1}{c}{17198} & \multicolumn{1}{c}{13861} \\
+ N Right & \multicolumn{1}{c}{1802} & \multicolumn{1}{c}{1537} & \multicolumn{1}{c}{1738} & \multicolumn{1}{c}{1323} & \multicolumn{1}{c}{2715} & \multicolumn{1}{c}{1664} & \multicolumn{1}{c}{3379} & \multicolumn{1}{c}{2717} \\
+ Eff N Left & \multicolumn{1}{c}{1186} & \multicolumn{1}{c}{1138} & \multicolumn{1}{c}{1202} & \multicolumn{1}{c}{931} & \multicolumn{1}{c}{1213} & \multicolumn{1}{c}{775} & \multicolumn{1}{c}{2575} & \multicolumn{1}{c}{1575} \\
+ Eff N Right & \multicolumn{1}{c}{724} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{734} & \multicolumn{1}{c}{580} & \multicolumn{1}{c}{890} & \multicolumn{1}{c}{557} & \multicolumn{1}{c}{1483} & \multicolumn{1}{c}{1004} \\
+ BW Loc Poly & 6.325 & 6.975 & 6.686 & 7.198 
+ & 4.840 & 5.360 & 6.999 & 5.796 \\ 
+ BW Bias & 9.860 & 12.598 & 10.029 & 11.004 
+ & 7.268 & 7.943 & 11.213 & 9.559 \\ 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
+RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, are in parentheses.
+The control variables are: population, GDP per capita, number of seats in 2000, year, and a dummy for the northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{sidewaystable}
 
-[^binomial]: Since coefficients are either positive or negative, each of them
-can be considered a Bernoulli trial. Thus, the aggregate results for all papers
-follow a Binomial distribution where parameters $n$ equals the number of papers
-and $p$ is the chance of a positive coefficient. The "law of $1/n$" can be
-reformulated as the chance of $p > 0.5$, which facilitates the testing of the
-theory.
+XXXX Rewrite all this!
 
-We start with lower house size. Our results indicate that there is no
-correlation between the number of legislators in the lower house and public
-expenditure (successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`], $p$-value = `r round(as.numeric(binN$p.value), 3)`).
-Note that the "law of $1/n$" suggests that there is a positive
-association between both. The binomial test for the natural logarithm of lower
-chamber size also shows a
-non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
-positive result for the number of legislators in the upper house, which is
-in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binK$p.value), 3)`).
+Each of the outcomes is further divided into two groups.
+In the first group, we include services that are easier to provide or credit claim, or both.
+These services are preferred by the electorate and have an intensive advertising effect for the councillor.
+In this category, we have school enrollment and infant mortality.
+In the second group are services either considered less critical by voters or harder to credit claim.
+They are harder to translate into votes or to target and advertise.
+In our models, we use preventive health care and quality of education to illustrate.
+According to our theory, we expect that increasing legislature size has a positive effect on desirable services that are easy to target.
 
-## Meta-Analysis
-\label{sub:Meta-Analysis}
+Table \ref{tab:outcomes} presents the results for education and health care outcomes.
+The data shows that, with the addition of a city councillor, enrollment in elementary schools increased by 2.58 children on average per school.
+This represents a change of around 0.20 standard deviations.
+From 5th to 8th grades, council size has no effect on school enrollment.
+Due to high dropout rates at this stage, spots for extra students remain vacant.
+Results are insignificant for quality indicators.\footnote{As education quality improves in the medium to long term, we look into the 2015 education quality index in the Online Supplemental Materials.
+Effects are null, pointing to no delayed benefits.} As expected, the placebo regressions are also insignificant.
 
-```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
-mod <- list()
-# Pooling effects analysis -- ExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
+Although Brazil achieved universal elementary school enrolment, enrolling a child in public school is particularly difficult in the early years.
+At the same time, taking care of small children is a considerable burden for poor households.
+Citizens thus reach out to councillors who can pressure school's bureaucracy to accommodate an extra child.
+Such an effort has virtually no cost to the politician, and grants her direct recognition, benefiting her electorally.
 
-mod[[1]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
+Consequences for infant mortality rates are also substantial.
+1.99 deaths per 1,000 children born are prevented with every extra legislator.
+This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
+Moreover, post-neonatal mortality decreases by 0.90 casualties per 1,000 births, which improves health care by 0.14 standard deviations.
+As expected, placebo regressions were statistically insignificant.
+However, the Family Health Program coverage and the proportion of children born with more than six prenatal consultations seems to decrease.
+This apparent inconsistency with the other indicators will be discussed further in the text.
 
-# Pooling effects analysis -- ExpPC x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
+% Sub-Section: Mechanisms
+\subsection{Applying the Mechanism and Testing Hypotheses}
+\label{sub:mechanism}
 
-mod[[2]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-# Pooling effects analysis -- logExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
+We test our hypotheses in Table \ref{tab:mechanism-reg} dividing the municipal outcome data in two panels.
+In Panel A, we counter alternative explanations for our mechanism.
+In Panel B, we present evidence that corroborates our arguments.
+\begin{table}[!htbp] \centering 
+  \caption{Mechanism Regressions -- Aggregated Municipal Level Outcomes} 
+  \label{tab:mechanism-reg} 
+\scalebox{0.9}{
+\begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+& \multicolumn{4}{c}{\textbf{Panel A: Representation, Competition, and Legislation Approval}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(1)}} 
+ & \multicolumn{1}{c}{\small{(2)}} 
+ & \multicolumn{1}{c}{\small{(3)}} 
+ & \multicolumn{1}{c}{\small{(4)}} \\
+ & \multicolumn{1}{c}{\small{Num. Female}} & 
+ \multicolumn{1}{c}{\small{Num. Non-white}} &
+  \multicolumn{1}{c}{\small{Candidates}} & 
+  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
+   & \multicolumn{1}{c}{\small{councillors}} & 
+ \multicolumn{1}{c}{\small{councillors}} &
+  \multicolumn{1}{c}{\small{Per Seat}} & 
+  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.22 & 0.60 & -0.19 & -0.02 \\ 
+  & (0.38) & (0.85) & (1.11) & (0.08) \\ 
+  \hdashline \\[-1.8ex] 
+ N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{270} \\ 
+Eff N Left & \multicolumn{1}{c}{194} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
+Eff N Right & \multicolumn{1}{c}{144} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{142} \\ 
+BW Loc Poly & 8.564 & 2.954 & 8.126 & 11.080 \\ 
+BW Bias & 13.569 & 4.917 & 12.049 & 16.921 \\[1.0ex] 
+\midrule 
+& \multicolumn{4}{c}{\textbf{Panel B: Access to Resources and Patronage}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(5)}} 
+ & \multicolumn{1}{c}{\small{(6)}} 
+ & \multicolumn{1}{c}{\small{(7)}} 
+ & \multicolumn{1}{c}{\small{(8)}} \\
+ & \multicolumn{1}{c}{\small{Mayoral}} & 
+ \multicolumn{1}{c}{\small{Num. Politically}} & 
+ \multicolumn{1}{c}{\small{Num. Career}} & 
+ \multicolumn{1}{c}{\small{Num. councillor}} \\
+ & \multicolumn{1}{c}{\small{Coalition Size}} & 
+ \multicolumn{1}{c}{\small{Appointed Empl.}} & 
+ \multicolumn{1}{c}{\small{Bureaucrats}} & 
+ \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.91$^{*}$ & 105.09$^{*}$ & 71.57 & 2.09 \\ 
+  & (0.50) & (62.12) & (218.12) & (4.37) \\ 
+    \hdashline \\[-1.8ex] 
+ N Left & \multicolumn{1}{c}{5168} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1028} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
+Eff N Left & \multicolumn{1}{c}{240} & \multicolumn{1}{c}{351} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
+Eff N Right & \multicolumn{1}{c}{161} & \multicolumn{1}{c}{334} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
+BW Loc Poly & 9.906 & 6.019 & 7.695 & 5.134 \\ 
+BW Bias & 15.846 & 10.170 & 11.780 & 8.902 \\ 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
+RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
 
-mod[[3]] <- metagen(
-  coef, SE, data=aux,
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction = TRUE,
-  sm="SMD"
-  )
+Panel A (Table \ref{mechreg1}) tests perspectives proposed by the literature.
+One of them is that better representation of under-served groups could broaden health care and education provision \citep{pande2003can, chattopadhyay2004women, chin2011redistributive, duflo2012women}.
+However, columns (1) and (2) show that neither gender nor representation of non-white legislators significantly improves public service provision for minorities.
+Alternatively, enhanced competition is also thought to improve responsiveness, alleviating the principal-agent problem between voters and politicians.
+Yet, we show that competition (3) or bills approval (4) remain unchanged when we increase council size.
 
-# Pooling effects analysis -- logExpPC x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
+Panel B (Table \ref{mechreg1}) illustrates our mechanism.
+Column (5) shows that there is a 91\% chance of the extra legislator belonging to the mayoral coalition.
+This suggests that these additions will likely enhance welfare effects due to increased governability\footnote{It is possible that the new coalition councillor facilitates mayor's lawmaking process.
+Indeed, we might actually be estimating the effects of mayors on policy-making.
+Their relationship with the central government is fundamental for service provision \citep{bueno2018bypassing}.
+In the Online Supplemental Materials, we investigate whether mayoral and council party composition vary across cities, and find that it remains unchanged around the thresholds.}.
+Column (6) demonstrates that adding one councillor increases the number of appointed employees by 105 with a standard deviation of over 0.30.
+This attests councillors' strong ties with the administration and facilitates service provision.
 
-mod[[4]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
+Additionally, we consider the number of career employees\footnote{Career bureaucrats have to undergo rigorous selection that prevents them from being fired for political reasons.} and find that improvements in state capacity and welfare are not consequences of bureaucratic agency.
+Column (7) points that the number of career bureaucrats does not significantly explain access to resources.
+Finally, adding a legislator has a null effect on the average number of appointed cabinet employees (column (8)).
 
-# Pooling effects analysis -- PCTGDP x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
+\subsection{Disaggregating Data on Approved Legislation and City councillor Survey}
+\label{sub:survey}
 
-mod[[5]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
+To evidence our mechanism's operation in city councillors' ordinary legislative activities, we examine two datasets: one composed by the approved bills, and the other by answers to the online survey.
+Figure \ref{LEGAPPR} showcases the results of the analysis of approved legislation.
 
-# Pooling effects analysis -- PCTGDP x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod[[6]] <- metagen(
-  coef, SE, data=aux,
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction=TRUE,
-  sm="SMD"
-  )
-
-# Pooling effects analysis -- PCTGDP x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod[[7]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-# Full model - Pooling effects analysis -- PCTGDP x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod[[8]] <- metagen(coef, SE, data = aux,
-          studlab = paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm = "SMD")
-
-# Full data - Pooling effects analysis -- ExpPC x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod[[9]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-```
-
-We then proceed to the meta-analysis. We matched the house size variables with
-our measures of government spending and created a theoretical $3 \times 3$
-matrix. Out of the 9 possible variable combinations, we found only 7 in the
-article pool. Our sample does not contain any papers that analyse the
-relationships between the log lower chamber size and public expenditure per
-capita, or between upper chamber size and the logarithm of public expenditure
-per capita. We calculated the effect sizes by drawing the coefficients and
-standard errors from the articles and computing Hedges' $g$, which is a widely
-used measure of standardised difference between means. When standard errors
-were not directly available in the texts, we used t-statistics to retrieve
-them.
-
-Figure \ref{fig:plots} shows the forest plots for our restricted sample, which
-includes the `r dim(dat)[1]` main coefficients of the `r length(unique(dat$id))`
-selected papers.\footnote{Please refer to Sections H and I in the Supplementary
-Material for full results regarding both samples.} On the left side of the
-plots are the names of the study authors and paper publication year. For
-unpublished studies, we included the first year the paper was available online.
-The bars in the middle show the reported effect sizes and the vertical lines
-indicate their average, weighted by standard errors. The length of the lines
-represent the precision of the estimates. The red line at the bottom of the
-figures displays the overall effects plus their respective confidence
-intervals.
-
-\begin{landscape}
-\begin{figure}[!ht]
-\centering
-\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
-\vspace{0.3cm}
-\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
-\label{fig:plots}
-\end{figure}
-\end{landscape}
-
-The uppermost row shows the results for lower chamber size in our restricted
-sample. In the first model, which correlates lower house and expenditure per
-capita, we find a standardised mean difference (SMD) of 0.022 and a standard
-error of 0.131 (studies = `r mod[[1]]$k`, 95\% CI = [-0.256; 0.299], $p$-value
-= 0.87), so we cannot rule that the effect is different from zero. Indeed, the
-effect of lower chamber size on the other two dependent variables is also null
-in statistical terms. When we compare lower chamber size with log expenditure
-per capita, the overall effect size is -0.031 and the standard error is 0.049
-(studies = `r mod[[3]]$k`, 95\% CI = [-0.188; 0.127], $p$-value = 0.58), and
-the impact of larger lower houses on government spending as a percentage of GDP
-is also negligible (studies = `r mod[[5]]$k`, SMD = - 0.006, 95\% CI =
-[-0.0334; 0.021], $p$-value = 0.563). The results are virtually identical when
-we estimate the meta-analyses using our extended sample, and the all three
-coefficients are again statistically indistinguishable from zero.
-
-Next, we present the meta-analyses using the logarithm of lower house size as
-an independent variable. The relationship between this variable and the log of
-per capita expenditure is positive, but the coefficient is not significant
-(studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI = [-0.225; 0.381],
-$p$-value = 0.515. The effect of log lower house size on expenditure as a
-percentage of the GDP is very similar, although the SMD is negative (studies =
-`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = 
-`r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`;
-`r round(mod[[6]]$upper.random,3)`], $p$-value = 
-`r round(mod[[6]]$pval.random,3)`). Results in the full sample are also null, and
-the coefficients for each dependent variable have the same sign as the
-restricted sample -- positive and negative, respectively.
-
-The third set of models uses upper house size as the main independent variable.
-We find a positive correlation between this variable and expenditure per capita
-(studies = `r mod[[2]]$k`, SMD = 3.658, SE = 4.299, 95\% CI = [-6.255; 13.572],
-$p$-value = 0.419), and a negative relationship with government spending as a
-percentage of GDP (studies = `r mod[[7]]$k`, SMD = 
-`r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI =
-[`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`],
-$p$-value = `r round(mod[[7]]$pval.random,3)`), yet neither coefficient is
-statistically significant. Results are the same in our extended sample.
-
-Taken together, these results yield conservative interpretations. Besides all
-average effect sizes not reaching conventional levels of statistical
-significance, the studies are also notably heterogeneous. The $I^2$ statistic
-quantifies the degree of heterogeneity among studies. @higgins2019cochrane
-consider any $I^2$ value above 75\% to indicate high heterogeneity, and the
-lowest $I^2$ we find in the restricted sample is `r round(mod[[2]]$I2*100,
-2)`\% (for the subset of upper chamber size and per capita expenditure).
-Additionally, all prediction intervals encompass zero. Therefore, we cannot
-reject the null hypothesis that the effect size is zero in any variable
-combination.
-
-In a nutshell, we do not find evidence in favour of the "law of $1/n$".
-One reason for this may be the identification strategy authors use in their
-models. On the one hand, OLS and panel data models require too many controls to
-make units comparable, and they are vulnerable to omitted variable bias or
-post-treatment bias [@cinelli2020making; @pearl2015conditioning]. On the other
-hand, estimation methods such as instrumental variables (IV) and regression
-discontinuity designs (RDD) have become popular because of their high internal
-validity [@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated
-effects for two sets of models that employ causal estimation techniques. They
-measure the impact of lower house size on expenditure per capita (left) and on
-the natural logarithm of expenditure per capita (right).
-
-\vspace{.5cm}
-
-\begin{figure}[htb]
+\begin{figure}[htb!]
   \begin{center}
-\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
-\vspace{.3cm}
-\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
-\label{fig:plots2}
+  \caption{Legislation Approved in Municipalities Closer to the City Council Thresholds}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/laws2019.pdf}}
+      \bigskip
+      \label{LEGAPPR}
+    \end{minipage}
   \end{center}
@@
 
-Papers that employ instrumental variables and panel/fixed-effects models show
-somewhat symmetrical distributions. Out of the five papers listed under IV, two
-are positive, two are negative, and one is null. In the plot for panel data,
-although more studies accumulate negative coefficients, the positive shifts are
-more pronounced, so the overall effect is also null. In contrast, all papers
-that use regression discontinuity designs show negative and statistically
-significant results. Since only three papers in our sample use RDDs, we are
-cautious about predicting an overall negative relationship, but they do
-indicate that better identification strategies yield a zero-to-negative impact
-of legislature size on expenditure, in support of the "reverse law of $1/n$".
+As previously argued, lawmakers decide on service provision based on the feasibility of credit-claiming.
+The top-two preferred legislation categories share this feature.
+In addition,\textit{local public goods} carries high electoral yield, which explains it ranking above \textit{others}.
+Graph 2A (Figure \ref{LEGAPPR}) presents the frequency of approved proposals.
+The overwhelming majority belongs to \textit{local public goods} (72.9\%), followed by \textit{others} (17.4\%).\footnote{Note that the sum is below 100\%.
+This is due to the SVM algorithm classifying around 3.5\% of laws as belonging to none of the categories above.
+For more information, see \citet{collingwood2013rtexttools}.} Graph 2B (Figure \ref{LEGAPPR}) depicts the average number of bills per legislator and, evidently, reflects the same pattern: \textit{local public goods} also amount to the highest, at 290.7 (S.E.
+56.95), and \textit{others} follows with 77.6 (S.E.
+15.50).
+Measuring the production of each representative builds on the idea that adding legislators – who provide more services – generates greater welfare.
 
-## Meta-Regressions
-\label{sub:regressions}
+Health care and education services, which compose 11.1\% of total approved bills (44.3 per legislator), are mainly addressed through \textit{local public goods}.
+According to Graph 2C (Figure \ref{LEGAPPR}), they represent 80.6\% of proposals in these sectors, followed by \textit{municipal public goods} (7.8\%).
+Productivity follows the same pattern (Graph 2D, Figure \ref{LEGAPPR}).
+Legislators propose 36.4 (in absolute terms) of the first, and 4.2 of the latter.
+Therefore, not only in general, but also specifically for education and health care, \textit{local public goods} are the preferred choice of councillors in Brazilian municipal chambers.
 
-In this section, we run a series of meta-regressions with six moderators to
-account for the heterogeneity across the selected papers. The first variable
-indicates whether the study uses lower chamber size, log lower chamber size, or
-upper chamber size as a main explanatory variable. We include separate effect
-sizes for upper and lower chamber sizes when papers analysed both. The second
-variable shows the study publication year, which we included to capture
-temporal variation in the study coefficients. We also add a dummy variable to
-assess whether published articles report effect sizes that are higher or lower
-than those from working papers. The fourth variable measures whether studies
-focusing on non-majoritarian electoral systems report coefficients that are
-smaller or larger than those from majoritarian countries. The fifth covariate
-is a categorical variable indicating the statistical procedure used in the
-original models (panel data, instrumental variables, OLS, or regression
-discontinuity design). In our last variable, we separate coefficients produced
-from samples of unicameral or bicameral systems, and code papers that analyse
-multiple polities with different institutional designs as "mixed".
+In our online survey with former city councillors, we asked about their legislative activity, the amount of votes it yielded, and how they negotiated with the mayor.
+While most results are in the Online Supplemental Materials, Figure \ref{survelec} displays the services councillors believe to generate the highest electoral results.
 
-Table {tab:regressions} presents the meta-regression results for our restricted
-and extended samples. Each column represents one of the three measures of
-public spending we discuss in this paper, and the last one uses all
-coefficients. To reduce the risk of false positives in our analyses, we use
-permutation tests to calculate significance levels for the meta-regressions
-\citep{higgins2004controlling}. To interpret these results, the sign of
-coefficients matters the most. These meta-regression coefficients can be viewed
-as representing "the effect of the moderator on the $1/n$ effect". This means
-positive coefficients predict a strengthening of the $1/n$ effect, and negative
-ones predict it will get weaker under that moderator category, when compared to
-its reference category. Since we aggregate different types of independent
-variables under the same models, the size of the effects does not accurately
-translate the scale of variations.
+\begin{figure}[htb!]
+  \begin{center}
+  \caption{Electoral Attractiveness of Councilor's Activities and Practices}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/elecYieldJobsCouncilorsJan2019.pdf}}
+      \bigskip
+      \label{survelec}
+    \end{minipage}
+  \end{center}
+\end{figure}
 
-```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
-res <- list()
+The service that best secures votes, according to 84.3\% of the interviewed, is access to hospital facilities; to 56.0\%, it is school admission; and to 71.0\%, it is access to medication.
+82.6\% of respondents confirm that local public goods are electorally beneficial, and 50.2\% indicated that, namely, fixing potholes on public roads resulting in some or many votes.
+Second in their evaluation is public school quality oversight (34.7\%), followed by  reported public construction oversight (25.3\%).
+These last two services, despite being preferred by voters and easy to credit-claim, require more investment.
+Coordination costs related to mayor negotiation and bureaucratic mediation also force them to recur to less demanding options, for instance, honors legislation.
+This is likely the reason why more approved bills fall under the \textit{others} label than under \textit{oversight}.
 
-# Aux fctns
-strep <- function (x) {
-  if(!is.na(x)) {
-    return(ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*',''))))
-  } else {
-    return('')
-  }
-}
+\section{Discussion}
 
-extract_coefs <- function(mod, modnam) {
-  dfr <- data.frame(
-     nams2 = row.names(mod[["beta"]]),
-     est = mod[["beta"]],
-     se = mod[["se"]],
-     pval = mod[["pval"]],
-     model = modnam
-  )
-  aux <- data.frame(nams = c("Intercept",
-             "Indepvar: logN",
-             "Indepvar: N",
-             "Year",
-             "Published",
-             "Elecsys: Non-Majoritarian",
-             "Method: Panel",
-             "Method: IV",
-             "Method: RDD",
-             "Legislature: Mixed",
-             "Legislature: Unicameral"), 
-             nams2 = c("intrcpt", 
-                       "indepvar2logN", 
-                       "indepvar2N", 
-                       "year", 
-                       "publishedYes", 
-                       "elecsys2Non-Maj", 
-                       "methodPANEL", 
-                       "methodIV", 
-                       "methodRDD",
-                       "instdesignMixed",
-                       "instdesignUnicameral"))
-  dfr <- left_join(aux, dfr) %>%
-    mutate_if(is.numeric, list(~round(., digits = 4)))
-  dfr$nams2 <- NULL
-  return(dfr)
-}
+%CLIENTELISM
 
-gcf <- function(mod, pos) {
-  x <- mod$est[pos]
-  y <- mod$pval[pos]
-  if(!is.na(x)) {
-    return(paste0(format(round(x, digits = 3), nsmall = 3), strep(y)))
-  } else {
-    return('')
-  }
-}
-gcf2 <- function(mod, pos) {
-  x <- mod$se[pos]
-  if(!is.na(x)) {
-    return(paste0('(', format(round(x, digits = 3), nsmall = 3), ')'))
-  } else {
-    return('')
-  }
-}
+Although city councillors should have governing advantages for being the closest representatives to citizens, the literature often presents them as inefficient and clientelistic \citep{Castroetal2009, AlmeidaFelix2012, leal2012coronelismo}.
+This proximity to the community results in better informed decision-making and accountability.
+However, it also creates perverse incentives to corruption, patronage and overprovision of electorally beneficial services.
+Poor management could be driven by private interests, or by limitations restraining governability.
+It is unrealistic to think that all politicians have free rein to approve and implement policies at their will.
+Bureaucracy and strong executives balance the assembly, who, in turn, develops strategies to enforce its will.
 
-# Expenditure per capita - Restricted
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              sparse = TRUE,
-              tdist = TRUE,
-              subset = dat$depvar2=='ExpPC',
-              slab = dat$authoryear)
+A councillor can only provide services which she can control or influence.
+In a Brazilian municipality, mayors directly control budget and staff allocation.
+Consequently, councillors must side with the mayor to participate in policy-making.
+Efforts towards establishing alliances start in the pre-electoral coalition period.
+If a candidate is part of the mayoral coalition, she credibly signals being able to deliver her platform promises.
+As the Electoral Justice allocates seats according to vote shares (D'Hondt method), pre-electoral coalitions have advantages since extremely popular candidates' votes thrust smaller candidates into office.
+Pre-electoral coalitions become crucial for mayors' governability after the election.
 
-res[[1]] <- extract_coefs(mod, "ExpPC")
+Bureaucrats also mediate most of the access to resources, and may filter councillor's demands, either for or against them.
+To influence service provision, city councillors sometimes recur to patronage, which is a strategy mobilized to ensure collaborative administrations.
+It is characterized by the employment of bureaucrats attached to an incumbent's personal figure.
+These politically-appointed employees have incentives to support the councillor's interests unconditionally \citep{Robinson2013}.
+Loyalty of the administration – through patronage or not – thus appears as fundamental in the political game.
 
-# Expenditure per capita - Extended
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = fulldat$depvar2=='ExpPC',
-              slab = fulldat$authoryear)
+Another limitation to representative agency is based on perception, as politicians imperfectly observe voters' preferences.
+The online survey provides us with clues on how councillor's beliefs could translate into their policy choices.
+\textit{Local public goods} is the preferred type of legislation across sources.
+We assembled five specific welfare-improving policies into the \textit{local public goods} category (Figure \ref{survelec}), namely \textit{hospital admission aid} (84.3\% answered it gives some to many votes), \textit{other local public goods} (82.6\%), \textit{access to medication} (71.0\%), \textit{school admission aid} (56.0\%), and \textit{street repairs} (50.2\%).
+They all pushed down remaining categories.
+\textit{School quality oversight} places second at overwhelming distance (34.7\%).
+In the approved legislation dataset (Graph 2A, Figure \ref{LEGAPPR}), \textit{local public goods} is equally favoured (72.9\%), followed by \textit{others} legislation (17.4\%), which we know to represent mostly honors bills.
 
-res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")
+If councillors aim for reelection, why do approved legislation frequencies not reflect answers to the survey?
+Comparison points to an inconsistency that circles back to the aforementioned limitations.
+Since negative exposure of executive and bureaucratic underachievement tensions political coalitions, and is less attractive to voters than policy-making.
+Logically, councillors will dedicate more to \textit{local public goods} than to \textit{oversight}.
+This does not attest their lack of competence, efficiency or honesty, but rather evidences the hardship of coordinating efforts and collectively making decisions under diverging goals and interests.
 
-# Log of Expenditure per capita - Restricted
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = dat$depvar2=='logExpPC',
-              slab = dat$authoryear)
+# Conclusion
+\label{sec:conclusion}
 
-res[[3]] <- extract_coefs(mod, "logExpPC")
+In this paper, we argue that political motivation determines the services that gain traction with larger legislatures.
+Councillors, guided by reelection, invest in policies they believe voters want and for which credit-claiming is feasible.
+Consequently, many essential welfare services are underprovided, giving place to locally-targeted policies.
+For instance, our theory explains why patterns of poor education persist in developing countries.
+In 2000, among the 32 countries that participated in the OECD's \textit{Programme for International Student Assessment} (PISA), Brazil ranked last.
+Between 2006 and 2015, there were virtually no improvements in scores.
+Counterintuitively, school enrolment was close to 99\% since 2010.
+Although desired by voters, ameliorating education quality is difficult to trace back to specific politicians.
+In this logic, they have incentives to target education through tangible yet low-reaching measures, such as raising the amount of children attending schools.
 
-# Log of Expenditure per capita - Extended
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = fulldat$depvar2=='logExpPC',
-              slab = fulldat$authoryear)
+We run a RDD to capture the effect of adding representatives to a municipal council.
+We focus on the effects of exogenously imposing thresholds to chamber sizes.
+We compare cities with similar populations, but located on different sides of the cutoff.
+We also collect data on the approved legislation during the 2005-2008 term, and perform an online survey with former representatives.
+Empirically, larger municipal chambers prevents death in infancy and stimulate educational enrollment.
+These changes do not, however, coincide with improvements in education and health care quality.
+We find that councillors prefer investing in local public goods, and they access resources via attachment to mayors and through bureaucratic mediation.
 
-res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")
-
-## Expenditure as percentage GDP -- Restricted
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              subset = dat$depvar2=='PCTGDP',
-              slab = dat$authoryear)
-
-res[[5]] <- extract_coefs(mod, "PCTGDP")
-
-## Expenditure as percentage GDP -- Extended
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-
-res[[6]] <- extract_coefs(mod, "PCTGDP - All coefs")
-
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              slab = dat$authoryear)
-
-res[[7]] <- extract_coefs(mod, "Full Model")
-
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              slab = fulldat$authoryear)
-
-res[[8]] <- extract_coefs(mod, "Full Model - All coefs")
-```
-
-\vspace{0.5cm}
-
-```{=latex}
-\begin{table}[htpb]
-\caption{Meta Regression Results\label{tabregressions}}
-\scriptsize
-\centering
-\begin{tabular}{lcccccccc}
-\toprule
-\midrule
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{All Coefficients} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
-& Restricted & Extended & Restricted & Extended & Restricted & Extended & Restricted & Extended \\
-\midrule
-Log of Lower Chamber Size & 
-`r gcf(res[[1]], 2)` & `r gcf(res[[2]], 2)` & 
-`r gcf(res[[3]], 2)` & `r gcf(res[[4]], 2)` & 
-`r gcf(res[[5]], 2)` & `r gcf(res[[6]], 2)` &
-`r gcf(res[[7]], 2)` & `r gcf(res[[8]], 2)` \\
- & `r gcf2(res[[1]], 2)` & `r gcf2(res[[2]], 2)` & 
-`r gcf2(res[[3]], 2)` & `r gcf2(res[[4]], 2)` & 
-`r gcf2(res[[5]], 2)` & `r gcf2(res[[6]], 2)` & 
-`r gcf2(res[[7]], 2)` & `r gcf2(res[[8]], 2)` \\
-%
-Lower Chamber Size &
-`r gcf(res[[1]], 3)` & `r gcf(res[[2]], 3)` & 
-`r gcf(res[[3]], 3)` & `r gcf(res[[4]], 3)` & 
-`r gcf(res[[5]], 3)` & `r gcf(res[[6]], 3)` &
-`r gcf(res[[7]], 3)` & `r gcf(res[[8]], 3)` \\
- & `r gcf2(res[[1]], 3)` & `r gcf2(res[[2]], 3)` & 
-`r gcf2(res[[3]], 3)` & `r gcf2(res[[4]], 3)` & 
-`r gcf2(res[[5]], 3)` & `r gcf2(res[[6]], 3)` & 
-`r gcf2(res[[7]], 3)` & `r gcf2(res[[8]], 3)` \\
-%
-Year & 
-`r gcf(res[[1]], 4)` & `r gcf(res[[2]], 4)` & 
-`r gcf(res[[3]], 4)` & `r gcf(res[[4]], 4)` & 
-`r gcf(res[[5]], 4)` & `r gcf(res[[6]], 4)` &
-`r gcf(res[[7]], 4)` & `r gcf(res[[8]], 4)` \\
-& `r gcf2(res[[1]], 4)` & `r gcf2(res[[2]], 4)` & 
-`r gcf2(res[[3]], 4)` & `r gcf2(res[[4]], 4)` & 
-`r gcf2(res[[5]], 4)` & `r gcf2(res[[6]], 4)` & 
-`r gcf2(res[[7]], 4)` & `r gcf2(res[[8]], 4)` \\
-%
-Non-Majoritarian & 
-`r gcf(res[[1]], 5)` & `r gcf(res[[2]], 5)` & 
-`r gcf(res[[3]], 5)` & `r gcf(res[[4]], 5)` & 
-`r gcf(res[[5]], 5)` & `r gcf(res[[6]], 5)` &
-`r gcf(res[[7]], 5)` & `r gcf(res[[8]], 5)` \\
-& `r gcf2(res[[1]], 5)` & `r gcf2(res[[2]], 5)` & 
-`r gcf2(res[[3]], 5)` & `r gcf2(res[[4]], 5)` & 
-`r gcf2(res[[5]], 5)` & `r gcf2(res[[6]], 5)` & 
-`r gcf2(res[[7]], 5)` & `r gcf2(res[[8]], 5)` \\
-%
-Published: Yes & 
-`r gcf(res[[1]], 6)` & `r gcf(res[[2]], 6)` & 
-`r gcf(res[[3]], 6)` & `r gcf(res[[4]], 6)` & 
-`r gcf(res[[5]], 6)` & `r gcf(res[[6]], 6)` &
-`r gcf(res[[7]], 6)` & `r gcf(res[[8]], 6)` \\
-& `r gcf2(res[[1]], 6)` & `r gcf2(res[[2]], 6)` & 
-`r gcf2(res[[3]], 6)` & `r gcf2(res[[4]], 6)` & 
-`r gcf2(res[[5]], 6)` & `r gcf2(res[[6]], 6)` & 
-`r gcf2(res[[7]], 6)` & `r gcf2(res[[8]], 6)` \\
-%
-Method: Panel & 
-`r gcf(res[[1]], 7)` & `r gcf(res[[2]], 7)` & 
-`r gcf(res[[3]], 7)` & `r gcf(res[[4]], 7)` & 
-`r gcf(res[[5]], 7)` & `r gcf(res[[6]], 7)` &
-`r gcf(res[[7]], 7)` & `r gcf(res[[8]], 7)` \\
-& `r gcf2(res[[1]], 7)` & `r gcf2(res[[2]], 7)` & 
-`r gcf2(res[[3]], 7)` & `r gcf2(res[[4]], 7)` & 
-`r gcf2(res[[5]], 7)` & `r gcf2(res[[6]], 7)` & 
-`r gcf2(res[[7]], 7)` & `r gcf2(res[[8]], 7)` \\
-%
-Method: IV & 
-`r gcf(res[[1]], 8)` & `r gcf(res[[2]], 8)` & 
-`r gcf(res[[3]], 8)` & `r gcf(res[[4]], 8)` & 
-`r gcf(res[[5]], 8)` & `r gcf(res[[6]], 8)` &
-`r gcf(res[[7]], 8)` & `r gcf(res[[8]], 8)` \\
-& `r gcf2(res[[1]], 8)` & `r gcf2(res[[2]], 8)` & 
-`r gcf2(res[[3]], 8)` & `r gcf2(res[[4]], 8)` & 
-`r gcf2(res[[5]], 8)` & `r gcf2(res[[6]], 8)` & 
-`r gcf2(res[[7]], 8)` & `r gcf2(res[[8]], 8)` \\
-%
-Method: RDD &
-`r gcf(res[[1]], 9)` & `r gcf(res[[2]], 9)` & 
-`r gcf(res[[3]], 9)` & `r gcf(res[[4]], 9)` & 
-`r gcf(res[[5]], 9)` & `r gcf(res[[6]], 9)` &
-`r gcf(res[[7]], 9)` & `r gcf(res[[8]], 9)` \\
-& `r gcf2(res[[1]], 9)` & `r gcf2(res[[2]], 9)` & 
-`r gcf2(res[[3]], 9)` & `r gcf2(res[[4]], 9)` & 
-`r gcf2(res[[5]], 9)` & `r gcf2(res[[6]], 9)` & 
-`r gcf2(res[[7]], 9)` & `r gcf2(res[[8]], 9)` \\
-% 
-Inst. Design: Mixed & 
-`r gcf(res[[1]], 10)` & `r gcf(res[[2]], 10)` & 
-`r gcf(res[[3]], 10)` & `r gcf(res[[4]], 10)` & 
-`r gcf(res[[5]], 10)` & `r gcf(res[[6]], 10)` &
-`r gcf(res[[7]], 10)` & `r gcf(res[[8]], 10)` \\
-& `r gcf2(res[[1]], 10)` & `r gcf2(res[[2]], 10)` & 
-`r gcf2(res[[3]], 10)` & `r gcf2(res[[4]], 10)` & 
-`r gcf2(res[[5]], 10)` & `r gcf2(res[[6]], 10)` & 
-`r gcf2(res[[7]], 10)` & `r gcf2(res[[8]], 10)` \\
-% 
-Inst. Design: Unicameral & 
-`r gcf(res[[1]], 11)` & `r gcf(res[[2]], 11)` & 
-`r gcf(res[[3]], 11)` & `r gcf(res[[4]], 11)` & 
-`r gcf(res[[5]], 11)` & `r gcf(res[[6]], 11)` &
-`r gcf(res[[7]], 11)` & `r gcf(res[[8]], 11)` \\
-& `r gcf2(res[[1]], 11)` & `r gcf2(res[[2]], 11)` & 
-`r gcf2(res[[3]], 11)` & `r gcf2(res[[4]], 11)` & 
-`r gcf2(res[[5]], 11)` & `r gcf2(res[[6]], 11)` & 
-`r gcf2(res[[7]], 11)` & `r gcf2(res[[8]], 11)` \\
-% 
-Intercept & 
-`r gcf(res[[1]], 1)` & `r gcf(res[[2]], 1)` & 
-`r gcf(res[[3]], 1)` & `r gcf(res[[4]], 1)` & 
-`r gcf(res[[5]], 1)` & `r gcf(res[[6]], 1)` &
-`r gcf(res[[7]], 1)` & `r gcf(res[[8]], 1)` \\
-& `r gcf2(res[[1]], 1)` & `r gcf2(res[[2]], 1)` & 
-`r gcf2(res[[3]], 1)` & `r gcf2(res[[4]], 1)` & 
-`r gcf2(res[[5]], 1)` & `r gcf2(res[[6]], 1)` & 
-`r gcf2(res[[7]], 1)` & `r gcf2(res[[8]], 1)` \\
-\bottomrule
-\end{tabular}
-\begin{minipage}{\textwidth}
-\renewcommand{\footnoterule}{}
-\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively.
-We report the results from the permutation tests.
-Reference categories: Independent Variable: Upper House Size; Published $= No$; Non-Majoritarian; Method $= OLS$, Inst.
-Design $= Bicameral$.
-Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.
-Blank cells mean that there is no sufficient data to estimate the paramater.}}
-\end{minipage}
-\end{table}
-```
-
-\vspace{0.5cm}
-
-The first two models show the results for public expenditure per capita. No
-variable reaches conventional levels of statistical significance in the
-restricted sample. In the extended sample, we find that models that use lower
-chamber size as an independent variable have lower effects when compared to
-upper chamber size. This suggests that an additional member in the lower house
-has a smaller impact on public spending than a member in the upper house.
-Moreover, the results for the extended sample point out that recent studies
-find larger effects than older ones.
-
-The third and fourth columns use the natural logarithm of expenditure per
-capita as the dependent variable. Among the coefficients in the restricted
-sample, those in published studies are significantly smaller than those in
-working papers. Another two moderators are negatively associated with the
-outcome in our larger study pool. They both refer to estimation methods.
-Studies that employ panel/fixed effects or regression discontinuity designs
-(RDDs) have lower coefficients for log expenditure per capita if we take OLS as
-the reference category.
-
-Three variables are statistically significant in the third set of
-meta-regressions, which include public expenditure as a percentage of GDP as
-the dependent variable. Both in our restricted and in our extended samples,
-recent studies have smaller coefficients than older papers, which stands in
-contrast with our previous models. Moreover, institutional design also affects
-outcomes. Papers that use mixed samples of bicameral and unicameral systems
-report significantly lower coefficients than those that analyse bicameral
-legislatures exclusively. Non-majoritarian electoral systems are also
-associated with lower levels of public spending, which may be justified since
-the "law of $1/n$" was conceived for majoritarian voting. These latter results,
-however, do not replicate in the first set of estimations.
-
-The last two columns report meta-regressions that aggregate all selected
-studies. In the restricted sample of coefficients, unicameralism has a
-pro-$1/n$ effect. This strongly supports the theory's original formulation, as
-most unicameral occurrences are local governments, for which the "law" was
-originally conceived. This result holds for the extended sample as well. When
-we regress all `r dim(fulldat)[1]` coefficients, the effects of estimation
-methods become stronger once again. Panel/fixed-effects models and regression
-discontinuity designs both decrease the $1/n$ effect at the .1\% significance
-level. Instrumental variable models follow along these lines. Additionally,
-non-majoritarian voting constituencies appear once again as settings where the
-law of $1/n$ becomes weaker.
-
-The evidence seems to be sensitive to the methodological design. Our results
-suggest that the same study samples may produce different outcomes depending on
-the response variables scholars decide to analyse. The broadest aggregation
-level presented the most insightful results in dialogue with the literature.
-The additional legislator in non-majoritarian legislatures does not increase
-expenditure as much as she would if the system were majoritarian. We are also
-more likely to witness legislative expenditure growing along with the amount of
-representatives in unicameral legislatures rather than in bicameral systems.
-This indicates that while the law of $1/n$ is not generalisable, its predicted
-effects are stronger when the institutional features of a polity come closer to
-its original theoretical framework.
-
-# Discussion
-\label{sec:discussion}
-
-In this letter, we assess the empirical validity of the "law of $1/n$". Based
-on a sample of `r length(unique(dat$id))` publications on the topic, our
-meta-analyses show that there is no strong evidence that an increase in the
-number of legislators has a significant effect on public expenditures. If such
-effect exists, it is likely driven by an increase in $k$, the size of the upper
-legislature, as suggested by several studies in the literature
-[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
-@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
-better evidence for the "reverse law of $1/n$", which posits that larger
-legislatures lead to lower government spending. This is mainly because studies
-using regression discontinuity designs, a method that has robust internal
-validity, consistently indicate a negative relationship between lower house size
-and the logarithm of expenditure per capita [@hohmann2017effect;
-@lewis2019legislature; @petterssonlidbom2012size].
-
-The meta-regressions show that study characteristics have a considerable
-influence on reported results. Electoral system affects the relationship
-between legislature size and public expenditure, but the results are not
-replicable in all estimations. Publication year generates conflicting findings
-in our models. Nevertheless, the meta-regressions confirm that RDDs produce
-negative effects more frequently than OLS regressions.
-
-Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
-plausible reason may be that there are few incentives for the pure accumulation
-of knowledge in the social sciences, at least when compared to the benefits
-scholars may accrue when they challenge or add features to existing theories
-[@geddes2003paradigms]. This leads to a reduced number of replication studies in
-the field, although we have seen some positive changes in this respect, such as
-EGAP's _Metaketa Initiative_.\footnote{See
-\url{https://egap.org/our-work/the-metaketa-initiative} for further
-information.} For instance, in our sample, papers added supermajority rules
-[@lee2015supermajority; @lee2016supermajority], redistricting
-[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
-coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
-bicameralism [@ricciuti2004legislature], and the interplay between upper and
-lower houses [@chen2007law] to the main theory, but a comprehensive
-procedural replication of the findings using different samples is yet to be
-written. The addition of new features has the benefit of enriching the original
-theory with useful details, although it has the disadvantage of not providing a
-conclusive test to the "law of $1/n$".
-
-Our analyses suggest three areas for further research. First, our study
-sample did not include articles that evaluate the association between the
-log($n$) and public expenditure per capita or between $k$ and log expenditure
-per capita. New work on that area might clarify some of the inconsistencies we
-find here. Second, despite the inclusion of several moderators in our models,
-aggregate results still show considerable heterogeneity. Domestic factors such
-as party dynamics or gerrymandering [@lee2015supermajority;
-@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
-regard. Finally, we highlight the need for more causal inference studies in the
-literature. Whenever possible, authors should leverage natural and
-quasi-experiments to assess whether the current results hold when tested with
-such research designs. These suggestions may help scholars and policy-makers to
-reach an optimal balance between sound fiscal policy and the demands for
-increased political representation.
+Our study has implications for policy-making and for the literature on distributive politics.
+First, we provide tools to predict welfare effects of changing the number of seats in municipal councils.
+We also contribute to comprehend the strategies politicians may use to adapt to these modifications.
+For example, an extra legislator will hardly add diversity to council activities, since there is a 91\% probability she will integrate the mayoral coalition.
+As for academia, we offer a simple theory to understand the underprovision of essential public goods as education and health care.
+We add complexity to the common belief that politicians in developing countries are purely clientelistic, inefficient or dishonest.
+We conclude that the political architecture of the assembly floor creates perverse incentives.
 
@@
 \setlength{\parskip}{5pt}
-
-\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
-erler2007termlimits, fiorino2007legislature, hohmann2017effect,
-kessler2014communication, lewis2019legislature, lledo2003electoral,
-mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
-stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
-matsusaka2005endogeneity, ricciuti2004legislatures}

### 2021-08-05 appendix/appendix.Rmd
change appendix
adding parts solution mayors offer councilor

@@
 
-We now have the entire strategy profile for the city councilors, provided that they reject the initial mayor's proposal.
-Proceeding by backward induction, we need to find the mayor's proposal that will win the support of the majority of the council.
-As the mayor is the proposer, policy concerns come into play, and the offer for a government aligned councilor will be different from the offer for an opposition councilor.
-For a government aligned councilor, assuming that the councilor is the pivotal players, the accepted offer has to be better than rejecting the proposal and waiting for the next round:
-
-\[
-p + x_i + B\pi_C(t_i) \ \geq \ \dfrac{1}{N}\left(\right) + \dfrac{1}{2}(x_i + B\pi_C(t_i))
-\]
+We now have the entire strategy profile for the city councilors, provided that they reject the mayor's proposal.
+Proceeding by backward induction, we solve for the mayor's proposal that wins the support of the majority of the council.
+In the mayor's proposal policy concerns come into play and the offer for a government an aligned councilor is different than the offer for an opposition councilor.
+For a government aligned councilor, assuming that the councilor is the pivotal players, the accepted offer $(\underline{x}_m^g, \underline{t}_m^g)$ has to be better than rejecting the proposal and waiting for the next round:
+
+\[
+p + x_m^g + B\pi_C(t_m^g) \ \geq \ \dfrac{1}{N}\left( \delta R -\dfrac{N}{2}(\underline{x}(1) + \underline{t}) + B\pi_C(t_i))  \right) + \left(1 - \dfrac{1}{N}\right)\left(\dfrac{1}{2}\right)(\underline{x}(1) + B\pi_C(t_i))
+\]
+
+Note that $\underline{x}(1)$ is the offer of private goods if the councilor rejects the mayors offer, so that $k = 1$.
+As the benefit of retention $B$ is higher than the cost of providing the targeted goods $\underline{t}$, the optimal provision of targeted goods satisfy the threshold for reelection: $t^* = t_m^g = t_i = \underline{t}$.
+Rewriting the equations with this info leads to:
+
+\[
+p + x_m^g + B \ \geq \ \dfrac{1}{N}\left( \delta R -\dfrac{N}{2}(\underline{x}(1) + \underline{t}) + B)  \right) + \left(1 - \dfrac{1}{N}\right)\left(\dfrac{1}{2}\right)(\underline{x}(1) + B)
+\]
+
+Solving for $x_m^g$ leads us to:
+
+\[
+x_m^g \ \geq \ -p +\dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \equiv \underline{x}_m^g
+\]
+
+For the opposition politician, the offer is equal to:
+
+,
 

### 2021-08-05 appendix/appendix.Rmd
adding cost to govern

@@
 
-\subsection{A Model of Legislature Size and Service Provision}
+# A Model of Legislature Size and Service Provision
+
+## Full model
 
@@
 
-We solve the game for a Sub-game Perfect Nash Equilibrium using backward induction.
-Although the game tree may extend infinitely, a Stationary Sub-game Perfect Equilibrium can be reached with no delay in the policy implementation, and the mayoral proposal being successful.
+This is a bargaining game, along the lines of @rubinsteinXXXX. For political science models similar to this model, see @baronfereXXXX and @cliffsXXXX.
+
+The solution for this game consists in finding a Stationary Sub-game Perfect Nash Equilibrium using backward induction.
+Although the game tree may extend infinitely, a Stationary Sub-game Perfect Equilibrium assumes that if a politician accepts an offer at time $t+1$, she should accept the offer at time $t$.
+This gives us an objective of finding the offer that will be accepted at any point in the game.
+Moreover, applying this reasoning we can find the optimal offer at $t=0$, which represents no delay in policy implementation.
+The mayor calibrates the offer for approval offering the benefits that councilors would receive, should they reject the offer and enter the reversal stage.
 
 \begin{definition}
-The solution for the game consists in a pair of XXXX.
+The solution for the game consists in a pair of strategic policy vectors for the mayor, and the city councilors. The mayor's policy vector is comprised of a public goods provision $g^*$ and XXXX
 \end{definition}
 
-Solving by backward induction, suppose that there were $k$ prior rejections, and the municipal resources shrank by $\delta^{k}R$.
-As at this stage the politicians are similar with regard to political affiliation, we can drop the party label.\footnote{In the extensions, we solve the game assuming that the distribution remained partisan even for the councilors.
-The results are similar, with the only difference that when partisanship is relevant for councilors, the expected provision of public goods is higher than zero.} A given councilor is recognized as the proposer with $1/N$ probability.
+Using backward induction, suppose that there were $k$ prior rejections, and the municipal resources shrank by $\delta^{k}R$.
+At this stage, the politicians are similar with regard to political affiliation, so that we drop the party label.
+A given councilor is recognized as the proposer with $1/N$ probability.
 The recognized councilor has to convince at least one-half of the council members to agree with her policy proposal.
@@
 
-We now have the entire strategy profile for the city councilors, provided that they reject the mayor's proposal.
+We now have the entire strategy profile for the city councilors, provided that they reject the initial mayor's proposal.
 Proceeding by backward induction, we solve for the mayor's proposal that wins the support of the majority of the council.
-In the mayor's proposal policy concerns come into play and the offer for a government an aligned councilor is different than the offer for an opposition councilor.
-For a government aligned councilor, assuming that the councilor is the pivotal players, the accepted offer $(\underline{x}_m^g, \underline{t}_m^g)$ has to be better than rejecting the proposal and waiting for the next round:
+In the mayor's proposal policy concerns come into play and the offer for a government-aligned councilor is different than the offer for an opposition councilor.
+For a government aligned councilor, assuming the councilor is the pivotal for the implementation, the accepted offer $(x_m^g, t_m^g)$ has to be better than rejecting the proposal, and waiting for the next round:
 
@@
 As the benefit of retention $B$ is higher than the cost of providing the targeted goods $\underline{t}$, the optimal provision of targeted goods satisfy the threshold for reelection: $t^* = t_m^g = t_i = \underline{t}$.
-Rewriting the equations with this info leads to:
+Rewriting the equations leads us to:
 
@@
 
-Solving for $x_m^g$ leads us to:
-
-\[
-x_m^g \ \geq \ -p +\dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \equiv \underline{x}_m^g
-\]
-
-For the opposition politician, the offer is equal to:
-
-,
-
-.
+And after some algebra:
+
+\[
+x_m^g \ \geq \ -p +\dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \ \equiv \ \underline{x}_m^g
+\]
+
+For the opposition councilor, the offer has to compensate the political loss of having a mayor that is not aligned with the councilor's ideology. The optimal offer satisfy:
+
+\[
+-p + x_o^g + B \ \geq \ \dfrac{1}{N}\left( \delta R -\dfrac{N}{2}(\underline{x}(1) + \underline{t}) + B)  \right) + \left(1 - \dfrac{1}{N}\right)\left(\dfrac{1}{2}\right)(\underline{x}(1) + B)
+\]
+
+And after some algebra:
+
+\[
+x_o^g \ \geq \ p + \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \ \equiv \ \underline{x}_o^g
+\]
+
+\begin{lemma}
+The offer for a government-aligned councilor is always lower than the offer for an opposition councilor.
+\end{lemma}
+
+\begin{proof}
+Note that the $\underline{x}_m^g = 2p + \underline{x}_o^g$.
+As the political disagreement is higher than zero, $\underline{x}_m^g = - 2p + \underline{x}_o^g < \underline{x}_o^g$.
+Moreover, note that $\underline{x}_m^g - \underline{x}_o^g = -2p$.
+\end{proof}
+
+This characterizes the offer that the mayor will make to win the support of the council.
+Now, let the number of government politicians be equal to $\eta_g$, and the ex-ante probability of electing a councilor aligned with the government equal to $\gamma \in (0,1)$.
+We define the cost to govern $C_g(N)$ as XXXX:
+
+\[
+C_g(N) = \dfrac{N}{2}(\underline{t} + \underline{x}_o^g) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g - \underline{x}_o^g \right)
+\]
+
+And the probability that $\eta_g$ councilors belong to the mayor's coalition is equal to $\mathbb{P}(\eta_g) = \binom{N}{\eta_g}\gamma^{\eta_g}(1-\gamma)^{N-\eta_g}$, which is the binomial probability given that the ex-ante chance to elect an aligned councilor is equal to $\gamma$.
 

### 2021-08-05 appendix/appendix.Rmd
added optimal mayor

@@
 And the probability that $\eta_g$ councilors belong to the mayor's coalition is equal to $\mathbb{P}(\eta_g) = \binom{N}{\eta_g}\gamma^{\eta_g}(1-\gamma)^{N-\eta_g}$, which is the binomial probability given that the ex-ante chance to elect an aligned councilor is equal to $\gamma$.
+
+We need now to derive the optimal rents and public goods provision that the mayor proposes.
+The mayor benefits from public goods provision, as it increases the chances of her reelection.
+However, she also wants to receive some compensation XXXX
+
+\[
+\begin{aligned}
+\max_{r, g} \quad & u(r) + B_M\pi(g)\\
+\textrm{s.t.} \quad & r + g + C_g(N) \leq R
+\end{aligned}
+\]
+
+And in equilibrium the budget binds, the optimal public goods provision maximizes:
+
+\[
+\max_{g} \{ u(R - g - C_g(N)) + B_M\pi(g) \}
+\]
+
+The first order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:
+
+\[
+u'(R - g - C_g(N)) = B_M\pi'(g)
+\]
+
+This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_g(N)) + B_M\pi''(g^*) < 0$.
+
+\begin{proposition}
+The provision of public goods increase with legislature size if the costs of govern decreases in larger legislatures.
+\end{proposition}
+
+\begin{proof}
+In order to prove this result, we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$.
+This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase.
+However, as $N$ increases discretely, we cannot take a derivative on $N$ and use the implicit function theorem.
+We use Monotone Comparative Statics [@milgromshannonXXXX] to derive these results.
+
+The mayor's expected utility
+\end{proof}
 

### 2021-08-06 appendix/appendix.Rmd
add lower bound book appendix

@@
 Note that the $\underline{x}_m^g = 2p + \underline{x}_o^g$.
-As the political disagreement is higher than zero, $\underline{x}_m^g = - 2p + \underline{x}_o^g < \underline{x}_o^g$.
-Moreover, note that $\underline{x}_m^g - \underline{x}_o^g = -2p$.
+As the political disagreement is higher than zero, $\underline{x}_m^g = - 2p + \underline{x}_m^o < \underline{x}_m^g$.
+Moreover, note that $\underline{x}_m^g - \underline{x}_m^o = -2p$.
 \end{proof}
@@
 Now, let the number of government politicians be equal to $\eta_g$, and the ex-ante probability of electing a councilor aligned with the government equal to $\gamma \in (0,1)$.
-We define the cost to govern $C_g(N)$ as XXXX:
-
-\[
-C_g(N) = \dfrac{N}{2}(\underline{t} + \underline{x}_o^g) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g - \underline{x}_o^g \right)
+We define the cost to govern $C_G(N)$ as XXXX:
+
+\[
+C_G(N) = \dfrac{N}{2}(\underline{t} + \underline{x}_o^g) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g - \underline{x}_m^o \right)
 \]
@@
 \max_{r, g} \quad & u(r) + B_M\pi(g)\\
-\textrm{s.t.} \quad & r + g + C_g(N) \leq R
+\textrm{s.t.} \quad & r + g + C_G(N) \leq R
 \end{aligned}
@@
 \[
-\max_{g} \{ u(R - g - C_g(N)) + B_M\pi(g) \}
+\max_{g} \{ u(R - g - C_G(N)) + B_M\pi(g) \}
 \]
@@
 \[
-u'(R - g - C_g(N)) = B_M\pi'(g)
-\]
-
-This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_g(N)) + B_M\pi''(g^*) < 0$.
+u'(R - g - C_G(N)) = B_M\pi'(g)
+\]
+
+This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_G(N)) + B_M\pi''(g^*) < 0$.
 
@@
 
-The mayor's expected utility
+The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1>N$, we have:
+
+\[
+\mathbb{E}\text{U}(g, N+1) - \mathbb{E}\text{U}(g', N+1) \geq \mathbb{E}\text{U}(g, N) - \mathbb{E}\text{U}(g', N)
+\]
+
+And after substituting, we have:
+
+\[
+u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g')
+\\
+\geq 
+\\
+u(R - g - C_G(N)) + B_M\pi(g) - u(R - g' - C_G(N)) - B_M\pi(g')
+\]
+
+Which is equal to:
+
+\[
+u(R - g - C_G(N+1)) - u(R - g' - C_G(N+1)) \geq 
+u(R - g - C_G(N)) - u(R - g' - C_G(N))
+\]
+
+Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:
+
+\[
+u'(R - g - C_G(N+1)) \geq 
+u'(R - g - C_G(N))
+\]
+
+This is true when the cost of govern with a council size of $N+1$ is lower than the cost of govern when the council size has $N$ councilors:
+
+\[
+C_G(N+1) \leq C_G(N)
+\]
+
+Therefore, to satisfy increasing differences in XXXX,
+
+\end{proof}
+
+This gives us our first empirical hypothesis to test: if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase.
+Moreover, the rents also increase with the legislature size.
+
+\begin{proposition}
+
+There exists a probability of electing a councilor aligned with the government $\gamma^*$ such that, for all $\gamma > \gamma^*$, the cost of govern decreases as $N$ increases, i.e.
+$C_G(N+1) \leq C_G(N)$.
+
+\end{proposition}
+
+\begin{proof}
+
+If the proposition is correct, then $C_G(N-1) - C_G(N+1) \geq 0$.
+Note that the differences for the partial binomial sums are increasing in $\gamma$ [@worsch1994lower].
+However, if we open up the difference:
+
 \end{proof}

### 2021-08-07 appendix/appendix.Rmd
appendix adding expected costs of govern 2
proof lemmas

@@
 This characterizes the offer that the mayor will make to win the support of the council.
+The next Definition helps to decompose the politician's offer into two components: rents and policy compensation.
+
+\begin{definition}
+Define the rents offered from the bargaining process as
+
+\[
+b(N) \ = \ \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right]
+\]
+
+When the legislature size is $N$, the optimal offers for an opposition member is:
+
+\[
+\underline{x}_m^o(N) = b(N) + p
+\]
+
+And the optimal offer for a government member is:
+
+\[
+\underline{x}_m^g(N) = b(N) - p
+\]
+
+\end{definition}
+
 Now, let the number of government politicians be equal to $\eta_g$, and the ex-ante probability of electing a councilor aligned with the government equal to $\gamma \in (0,1)$.
-We define the cost to govern $C_G(N)$ as XXXX:
-
-\[
-C_G(N) = \dfrac{N}{2}(\underline{t} + \underline{x}_o^g) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g - \underline{x}_m^o \right)
+We define the cost to govern $C_G(N)$ as three parts equation: first, the costs of making the electoral transfers for at least half of the councilors; second, the rents paid in bargaining; and last, the political costs, that depend on the amount of politicians that are affiliated with the mayor's party.
+After simplifications, the equation describing the costs of govern is as follows:
+
+\[
+C_G(N) = \dfrac{N}{2}(\underline{t} + b(N) + p) - 2p\sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g
 \]
@@
 
-We need now to derive the optimal rents and public goods provision that the mayor proposes.
+We need now to derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
 The mayor benefits from public goods provision, as it increases the chances of her reelection.
-However, she also wants to receive some compensation XXXX
+However, she prefers to contribute as minimum as possible for the public goods, and extract the remaining resources as political rents.
+Therefore, her objective is to maximize the expected utility subject to the budget constraint.
 
@@
 
-And in equilibrium the budget binds, the optimal public goods provision maximizes:
+In equilibrium the budget binds, and the optimal public goods provision maximizes:
 
@@
 This gives us our first empirical hypothesis to test: if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase.
-Moreover, the rents also increase with the legislature size.
+But we still need to investigate further how the costs of govern would decrease with legislature size.
+On the one hand, it seems evident that with the additional legislator, comes also an additional rent and a possible veto player.
+In the next Lemma we show that the rents always decrease when we increase the number of legislators.
+
+\begin{lemma}
+The amount of rents required to win support from a given legislator decreases when the number of legislators increase.
+\end{lemma}
+
+\begin{proof}
+
+The proof consists in showing that when we increase the size of the legislature from $N$ to $N+1$, the amount of rents decrease.
+
+\[
+\begin{aligned}
+b(N+1) - b(N) \ = \ & \dfrac{1}{2(N+1)+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-(N+1)(\underline{t} + B) + B\right] \\
+& - \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
+= \ & XXXX \\
+= \ & XXXX \\
+< \ &0
+\end{aligned}
+\]
+
+\end{proof}
+
+However, the decrease in rents is not sufficient to have lower rent extraction.
+The political costs, if high enough, can offset the gains with lower rents.
+Higher political costs result from having more members of the opposition in the legislature.
+The next proposition shows the sufficient condition for having a lower cost of govern when we increase the number of legislators.
 
@@
 
-There exists a probability of electing a councilor aligned with the government $\gamma^*$ such that, for all $\gamma > \gamma^*$, the cost of govern decreases as $N$ increases, i.e.
+There exists an ex-ante probability of electing a councilor aligned with the government $\overline{\gamma}$ such that, for all $\gamma > \overline{\gamma}$, the cost of govern decreases as $N$ increases, i.e.
 $C_G(N+1) \leq C_G(N)$.
@@
 
-If the proposition is correct, then $C_G(N-1) - C_G(N+1) \geq 0$.
-Note that the differences for the partial binomial sums are increasing in $\gamma$ [@worsch1994lower].
-However, if we open up the difference:
+If the proposition is correct, then $C_G(N) - C_G(N+1) \geq 0$. Let us rewrite the results as:
+
+\[
+\dfrac{N}{2}(\underline{t} + \underline{x}_o^g(N-1)) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g(N-1) - \underline{x}_m^o(N-1) \right) - \left(\dfrac{N}{2}+1\right)(\underline{t} + \underline{x}_o^g(N+1)) - \sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\left( \underline{x}_m^g(N+1) - \underline{x}_m^o(N+1) \right) \geq 0
+\]
+
+Rearranging the terms:
+
+\[
+- \underline{t} - \underline{x}_o^g(N+1) - \dfrac{N}{2}(\underline{x}_o^g(N+1) - \underline{x}_o^g(N-1)) -2p \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]
+\]
 

### 2021-08-09 appendix/appendix.Rmd
latex changes

@@
 ## Starting
-XXXX
+#XXXX
 
 # Required packages
-XXXX
+#XXXX
 
 # Load datasets
-XXXX
+#XXXX
 ```
@@
 
-1. The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
-2. The mayor proposes a policy vector $(r, g, \bf{x}, \bf{t})_M$.
-3. The city council votes the proposal.
-  - If the council accepts, then the policy is implemented, and the game ends. 
-  - Otherwise, the reversal policy is implemented.
-4.
-(Reversal Policy) At the beginning of each iteration of the reversal policy, one councilor is randomly recognized to be the proposer.
+\begin{enumerate}
+  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
+  \item The mayor proposes a policy vector $(r, g, \bf{x}, \bf{t})_M$.
+  \item The city council votes the proposal.
+  \begin{itemize}
+    \item If the council accepts, then the policy is implemented, and the game ends. 
+    \item Otherwise, the reversal policy is implemented.
+  \end{itemize}
+  \item (Reversal Policy) At the beginning of each iteration of the reversal policy, one councilor is randomly recognized to be the proposer.
 She proposes a vector $(\bf{x}, \bf{t})$, with $r =  g = 0$.
@@
 If the proposal is rejected, a new round of reversal start, but with the municipal resources reduced by a factor $\delta$.
+\end{enumerate}
 
@@
 
-However, the decrease in rents is not sufficient to have lower rent extraction.
+However, the decrease in rents is not sufficient to have lower costs to govern when we increase the number of legislators.
 The political costs, if high enough, can offset the gains with lower rents.
@@
 
-\begin{proposition}
+\begin{proposition}\label{mainprop}
 
-There exists an ex-ante probability of electing a councilor aligned with the government $\overline{\gamma}$ such that, for all $\gamma > \overline{\gamma}$, the cost of govern decreases as $N$ increases, i.e.
-$C_G(N+1) \leq C_G(N)$.
+There exists an ex-ante probability of electing a councilor aligned with the government $\overline{\gamma}$ such that, for all $\gamma > \overline{\gamma}$, the cost of govern decreases as $N$ increases, i.e., $C_G(N+1) \leq C_G(N)$.
 
@@
 
-If the proposition is correct, then $C_G(N) - C_G(N+1) \geq 0$. Let us rewrite the results as:
+Let us rewrite the results as:
 
 \[
-\dfrac{N}{2}(\underline{t} + \underline{x}_o^g(N-1)) + \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\left( \underline{x}_m^g(N-1) - \underline{x}_m^o(N-1) \right) - \left(\dfrac{N}{2}+1\right)(\underline{t} + \underline{x}_o^g(N+1)) - \sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\left( \underline{x}_m^g(N+1) - \underline{x}_m^o(N+1) \right) \geq 0
+XXXX \geq 0
 \]
@@
 
+Let $\Delta\eta_n(\gamma) \equiv \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]$.
+There is no closed form solution for this equation.
+We can approximate the boundaries using @wXXXX but graphically, we can have a good sense of the XXXX:
+
+XXXX GRAPH DELTA GAMMA HERE
+
+And solving for $\Delta\eta_n(\gamma)$ we have that:
+
+\[
+XXXX
+\]
+
+The natural boundaries for $\Delta\eta_n(\gamma)$ are minus-one and one.
+Minus-one means that the additional legislature seat went to the opposition while one means that the additional legislature seat went to the government.
+XXXX
+
 \end{proof}
 
-\newpage
+Taking stocks, the model provides two testable hypothesis. Let a legislature that previously had $N$ legislators, and now increased the legislature by $N+1$. Then:
 
-\subsection{Variable Sources and Descriptive Statistics\label{appsources}}
+\begin{enumerate}
+  \item[H1. ] The provision of public goods increase when the costs to govern decrease with legislature size.
+  \item[H2. ] The costs to govern decrease with legislature size when the chance of electing a government aligned legislator is sufficiently high.
+\end{enumerate}
 
-We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
+## Paper Version of the Model
 
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{Data Sources} 
-  \label{varsources}
-  \scalebox{0.75}{
-\begin{tabular}{@{\extracolsep{5pt}}llll} 
-\\[-1.8ex]\hline\hline \\[-1.8ex] 
-Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
-\hline \\[-1.8ex] 
-& & & \\
-DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
-& & & \\
-IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
-& & & \\
-INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
-& & & \\
-InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
-& & & \\
-IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
-& & & \\
-MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
-& & & \\
-TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
-& & & \\
-\hline\hline \\[-1.8ex] 
-\end{tabular} 
-}
-\end{sidewaystable}
+In the main paper, we simplify the analysis with two assumptions regarding the costs of govern.
+First, we assume a simpler reversal where there is only one reversal stage and after that a reversal policy of zero in all policy components take place.
+Second, we assume that the cost for govern will depend on the ex-ante expected number of legislator belonging to the government and the opposition.
+In this case, the rents $b(N)$ become:
 
-Now let us define each variable.
+\[
+XXXX
+\]
 
-\textbf{Outcomes Aggregated at the Municipal Level:}
+And Proposition \ref{mainprop} becomes:
 
-\begin{itemize}
-    \item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
-    \item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
-    \item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
-    \item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
-    \item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
-    \item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-    \item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-    \item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
-    \item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
-    \item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
-    \item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
-    \item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
-The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
-    \item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying.
-The estimators are cleaned to avoid the influence of schools and classrooms specific effects.
-(source: INEP, years: 2005, 2007).
-    \item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
-    \item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
-    \item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality.
-Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
-    \item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
-    \item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
-    \item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council.
-We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures).
-    \item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
-    \item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
-\end{itemize}
+\begin{proposition}
 
-\textbf{Legislation Dataset:}
+XXXX
 
-We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:
+\[
+XXXX
+\]
 
-\begin{itemize}
-    \item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
-    \item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
-    \item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
-    \item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
-    \item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
-\end{itemize}
+\end{proposition}
 
-\textbf{Online 2016 Former City Councilors Survey:}
+\begin{proof}
+XXXX
+\end{proof}
 
-We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:
-
-\begin{itemize}
-    \item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
-    \item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
-\end{itemize}
-
-In this Appendix, we present other questions we asked in the survey.
-They are meant to improve the knowledge we have about the city councilors perceptions about their representation.
-We have not added these to the main paper because they were more complimentary and not of general interest.
-The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.
-
-\input{tabs/edited/sumstatOut2016e.tex}
+All the dynamics remain the same but the second hypothesis becomes clearer, with a simplified quantity for the probability of electing a government-aligned politician, $\overline{\gamma}$.
+The simplified $\overline{\gamma}$ is helpful because it shows that the political concerns require a probability larger than one-half, with a precise amount depending on the XXXX.
 
 \newpage
-
-\subsection{Threshold Manipulation, Sorting, and Pre-treatment Consistency}
-
-The validity of our causal claim relies on three assumptions.
-First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds.
-Second, that we are consistently comparing municipalities in the same cutoffs.
-Lastly, that we have no pre-treatment differences in our sample.
-
-For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
-For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
-
-We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
-We use local polynomial orders from one to four.
-As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
-Therefore, there is no manipulation according to \citet{calonico2019regression}.
-
-We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/McCrary.pdf}}
-      \caption{\citet{McCrary2008} manipulation test}
-      \bigskip
-      \label{manipulationplot}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}.
-For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21.
-When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor.
-However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors.
-This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
-That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.
-
-To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
-Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
-The reason for the first variable is the multiple threshold assignments.
-We add GDP per capita because wealthier cities tend to be more productive and have better public services.
-The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
-The year and the northeast dummies serve to improve efficiency.
-Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.
-See the following section for further tests and simulations.
-
-For the last assumption, we should have no changes in pre-treatment covariates.
-These pre-treatment covariates are variables measured before the primary outcomes.
-As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
-
-Table \ref{validitycheck} displays the results of the validity checks.
-At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs.
-At the bottom, we estimate the pre-treatment covariate balance.
-
-\begin{table}[htb!] \centering 
-  \caption{Research Design Validity Check} 
-  \label{validitycheck} 
-    \scalebox{0.9}{
-  \begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
-\toprule
- & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
-   & \multicolumn{1}{c}{\small{(1)}} & 
- \multicolumn{1}{c}{\small{(2)}} & 
- \multicolumn{1}{c}{\small{(3)}} & 
- \multicolumn{1}{c}{\small{(4)}} \\
-
- & \multicolumn{1}{c}{\small{Additional Num.}} & 
- \multicolumn{1}{c}{\small{Placebo Add.}} & 
- \multicolumn{1}{c}{\small{Additional Num.}} & 
- \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
-  & \multicolumn{1}{c}{\small{Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
-  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
-  \multicolumn{1}{c}{\small{(Without Controls)}} & 
-  \multicolumn{1}{c}{\small{(With Controls)}} & 
-  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-\\[-1.8ex] 
- LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
-  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
-\hdashline \\[-1.8ex]   
- N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
-Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
-Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
-BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
-BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
-\midrule 
- & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{(5)}} & 
- \multicolumn{1}{c}{\small{(6)}} & 
- \multicolumn{1}{c}{\small{(7)}} & 
- \multicolumn{1}{c}{\small{(8)}} \\
-  & \multicolumn{1}{c}{\small{Number of}} & 
- \multicolumn{1}{c}{\small{Population}} & 
- \multicolumn{1}{c}{\small{GDP}} & 
- \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
-  & \multicolumn{1}{c}{\small{Seats 2000}} & 
-  \multicolumn{1}{c}{\small{2000 Census}} & 
-  \multicolumn{1}{c}{\small{2000 Census}} &
-   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
-  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
-  \hdashline \\[-1.8ex]
- N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
-Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
-Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
-BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
-BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
-\bottomrule
-\end{tabularx}
-\begin{tablenotes}
-\small
-\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
-RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, in parentheses.
-Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
-\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
-\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
-\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
-\textit{BW Bias} is the Bandwidth used to compute the standard errors.
-\end{tablenotes}
-\end{threeparttable}}
-\end{table}
-
-Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
-After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
-Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
-These tests reinforce the validity of our research designs.
-
-\pagebreak
-
-\subsection{Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision\label{appidentif}}
-
-The identification strategy requires exogenous changes in the city council size thresholds.
-Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
-
-\begin{table}[htp!]
-\centering
-\caption{City council size from the 1988 Constitution}
-\scalebox{0.75}{
-\begin{tabular}{rccrrr}
-  \hline\hline
- & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\ 
- & & & & & \multicolumn{1}{c}{(2001-2004)} \\
-  \hline
-  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\ 
-  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\ 
-  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\ 
-   \hline\hline
-\end{tabular}
-}
-\label{tabcitycouncilsize1988}
-\end{table}
-
-These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors.
-The two losing councilors started a judicial contestation that made it to the Supreme Court.
-The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55.
-Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004).
-According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
-
-\begin{table}[htp!]
-\centering
-\caption{City council size thresholds according to TSE resolution 21,702/2004}
-\scalebox{0.75}{
-\begin{tabular}{rcrrr}
-  \hline\hline
- &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
- & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
-  \hline
-  1 &  9 & 0 & 47,619 & 5,029 \\ 
-  2 &  10 & 47,620 & 95,238 & 317 \\ 
-  3 &  11 & 95,239 & 142,857 & 89 \\ 
-  4 &  12 & 142,858 & 190,476 & 43 \\ 
-  5 &  13 & 190,477 & 238,095 & 30 \\ 
-  6 &  14 & 238,096 & 285,714 & 21 \\ 
-  7 &  15 & 285,715 & 333,333 & 13 \\ 
-  8 &  16 & 333,334 & 380,952 & 13 \\ 
-  9 &  17 & 380,953 & 428,571 & 6 \\ 
-  10  & 18 & 428,572 & 476,190 & 6 \\ 
-  11  & 19 & 476,191 & 523,809 & 4 \\ 
-  12  & 20 & 523,810 & 571,428 & 5 \\ 
-  13  & 21 & 571,429 & 1,000,000 & 13 \\ 
-  14  & 33 & 1,000,001 & 1,121,952 & 1 \\ 
-  15  & 34 & 1,121,953 & 1,243,903 & 2 \\ 
-  16  & 35 & 1,243,904 & 1,365,854 & 1 \\ 
-  17  & 36 & 1,365,855 & 1,487,805 & 2 \\ 
-  18  & 37 & 1,487,806 & 1,609,756 & 1 \\ 
-  19  & 38 & 1,609,757 & 1,731,707 & 1 \\ 
-  20  & 39 & 1,731,708 & 1,853,658 & 0 \\ 
-  21  & 40 & 1,853,659 & 1,975,609 & 0 \\ 
-  22  & 41 & 1,975,610 & 4,999,999 & 4 \\ 
-  23  & 42 & 5,000,000 & 5,119,047 & 0 \\ 
-  24  & 43 & 5,119,048 & 5,238,094 & 0 \\ 
-  25  & 44 & 5,238,095 & 5,357,141 & 0 \\ 
-  26  & 45 & 5,357,142 & 5,476,188 & 0 \\ 
-  27  & 46 & 5,476,189 & 5,595,235 & 0 \\ 
-  28  & 47 & 5,595,236 & 5,714,282 & 0 \\ 
-  29  & 48 & 5,714,283 & 5,833,329 & 0 \\ 
-  30  & 49 & 5,833,330 & 5,952,376 & 0 \\ 
-  31  & 50 & 5,952,377 & 6,071,423 & 1 \\ 
-  32  & 51 & 6,071,424 & 6,190,470 & 0 \\ 
-  33  & 52 & 6,190,471 & 6,309,517 & 0 \\ 
-  34  & 53 & 6,309,518 & 6,428,564 & 0 \\ 
-  35  & 54 & 6,428,565 & 6,547,611 & 1 \\ 
-  36  & 55 & 6,547,612 & $\infty$  & 0 \\ 
-   \hline\hline
-\end{tabular}
-}
-\label{tabcitycouncilsize2004all}
-\end{table}
-
-As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants.
-Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.
-
-\begin{table}[htp!]
-\centering
-\caption{City council thresholds used in the paper}
-\scalebox{0.85}{
-\renewcommand*{\arraystretch}{1.2}
-\begin{tabular}{rcrrr}
-  \hline \hline
- & \multicolumn{1}{c}{Legislature} & \multicolumn{1}{c}{Min.} & \multicolumn{1}{c}{Max.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
- & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{(2003 pop.)} \\
-  \hline
-  1 & 9 & 0 & 47,619 & 5,029 \\ 
-  2 & 10 & 47,620 & 95,238 & 317 \\ 
-  3 & 11 & 95,239 & 142,857 & 89 \\ 
-  4 & 12 & 142,858 & 190,476 & 43 \\ 
-  5 & 13 & 190,477 & 238,095 & 30 \\ 
-  6 & 14 & 238,096 & 285,714 & 21 \\ 
-  7 & 15 & 285,715 & 333,333 & 13 \\ 
-  8 & 16 & 333,334 & 380,952 & 13 \\ 
-  9 & 17 & 380,953 & 428,571 & 6 \\ 
-  10 & 18 & 428,572 & 476,190 & 6 \\ 
-  11 & 19 & 476,191 & 523,809 & 4 \\ 
-  12 & 20 & 523,810 & 571,428 & 5 \\ 
-  13 & 21 & 571,429 & 1,000,000 & 13 \\ 
-   \hline \hline
-\end{tabular}
-}
-\label{tabcitycouncilsize2004short}
-\end{table}
-
-The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
-In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections.
-Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).
-
-To provide an overview of the data dispersion, Figure \ref{sample_plot} plots the municipalities by their proximity from the cutoffs.
-In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
-The darker the color, the closer to the population thresholds.
-In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation.
-Figure \ref{sample_plot} also shows that our municipalities are reasonably distributed around the whole country.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=7in,angle=0]{figs/sampplot2019.pdf}}
-      \caption{Municipalities by their Selection Status}
-      \bigskip
-      \label{sample_plot}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-Moreover, we could question whether the discontinuities studied here are sharp or fuzzy.
-In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced.
-For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities.
-However, this problem was absent in our RDD, as the problem identified by Cavalvanti was based on the use of thresholds approved in 2009.
-In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).
-
-\newpage
-
-\subsection{Identification Strategy in Multiple Thresholds Regression Discontinuity Design\label{ISMT}}
-
-Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes.
-Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
-The outcome variable is assumed to be $Y$.
-In the pooled model, the Local Average Treatment Effect is:
-
-\[
-LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
-\]
-
-Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff.
-The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
-To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
-For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
-As the population varies smoothly around each cutoff, it makes it a perfect control to add.
-The new estimator is:
-
-\[
-LATE_{controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C, Z_i \right]
-\]
-
-We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
-All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}.
-To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff.
-To compute the optimal bandwidth, we use the \citet{CCT2014} method.
-To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
-We also use cluster-robust standard errors at the municipal level.
-
-However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable?
-To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.
-
-Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
-We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes.
-The first three outcomes are sharp changes.
-In the first, we add variation from one to 10, with one step for each change.
-In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
-The estimated change should be equal to zero.
-In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
-This is intended to simulate a diminishing effect from one cutoff to the other.
-The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
-We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{0.9\linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/simdistrRDD.pdf}}
-      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
-      \bigskip
-      \label{simRDdd}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-A consistent estimator should fit one in the first and fourth data distribution.
-In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
-In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$.
-The first three models should present a more efficient estimation than the last three models.
-We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=4.5in,angle=0]{figs/estimsRDD.pdf}}
-      \caption{Estimations for the Different Data Generating Processes}
-      \bigskip
-      \label{estimDGP}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Placebo Regressions for the Aggregated Mechanism Outcomes\label{placmechmain}}
-
-Here we present the placebo regressions for the mechanism-aggregated outcomes.
-In Panel A of the main paper, we run the regression on alternative explanations.
-As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases.
-For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank.
-In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage.
-As expected, the placebo regressions were not statistically significant.
-
-\input{tabs/edited/appmechreg1Oct2016e.tex}
-
-\newpage
-
-\subsection{Sensitivity Analysis for Bandwidth Selection\label{sensffapp}}
-
-We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/bwsens2019.pdf}}
-      \caption{Bandwidth Sensitivity -- Main Models}
-      \bigskip
-      \label{graphbw}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/placbwsens2019.pdf}}
-      \caption{Placebo Regressions -- Bandwidth Sensitivity}
-      \bigskip
-      \label{placgraphbw}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Sensitivity to Different States in the Analysis\label{sensstate}}
-
-The literature considers that some states are more prone to inefficiencies than the rest of the country.
-Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves.
-As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size.
-We run the analysis dropping one state at a time, to investigate this statewide heterogeneity.
-The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
-
-To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks.
-The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states.
-In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo.
-Otherwise, note that all the other variables remain unchanged, except for gender.
-Gender changes because there were laws during this period mandating a minimum amount of female candidates.
-It is expected that one variable changes as a response to randomness.
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{figs/dropstatesens12019.pdf}}
-      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
-      \bigskip
-      \label{graphsensstatedrop1}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{figs/dropstatesens22019.pdf}}
-      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
-      \bigskip
-      \label{graphsensstatedrop2}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/placdropstatesens12019.pdf}}
-      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop1}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/placdropstatesens22019.pdf}}
-      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop2}
-  \end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Sensitivity to the Functional Form Analysis\label{sensfuncform}}
-
-In the paper, we run all the regressions using local linear polynomials.
-\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
-
-However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms.
-With two exceptions, the results are mostly consistent.
-First, quadratic and cubic polynomials make the significance go away in some models.
-Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions.
-Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{figs/ffsens2019.pdf}}
-      \caption{Sensitivity Analysis for the Functional Form}
-      \bigskip
-      \label{graphsensff}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/placffsens2019.pdf}}
-      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
-      \bigskip
-      \label{placgraphsensff}
-  \end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Sensitivity to Covariates\label{senstcovapp}}
-
-The control variables play an essential role in our model.
-As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
-
-However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis.
-To study the sensitivity to controls, we run the same regressions for all possible control combinations.
-Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
-The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}
-
-\begin{landscape}
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=6in,angle=0]{figs/senscov2019.pdf}}
-      \caption{Sensitivity Analysis for the Control Variable's Choices}
-      \bigskip
-      \label{graphsenscontrol}
-    \end{minipage}
-  \end{center}
-\end{figure}
-\end{landscape}
-
-For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.
-
-In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant.
-Otherwise, our model is not significant when most combinations are also insignificant.
-Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.
-
-We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
-The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/placsens1cov2019.pdf}}
-      \caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
-      \bigskip
-      \label{placsenscov1}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/placsens2cov2019.pdf}}
-      \caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
-      \bigskip
-      \label{placsenscov2}
-  \end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}
-
-To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
-This strategy is similar to adding one cutoff at a time.
-The results are stable and do not change our main conclusions.
-Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring.
-Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/rdaddcuts12019.pdf}}
-      \caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
-      \bigskip
-      \label{senscut1}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/rdaddcuts22019.pdf}}
-      \caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
-      \bigskip
-      \label{senscut2}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{0.8 \linewidth}
-      \centerline{\includegraphics[width=5.5in,angle=0]{figs/placrdaddcuts12019.pdf}}
-      \caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
-      \bigskip
-      \label{placsenscut1}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{0.8 \linewidth}
-      \centerline{\includegraphics[width=5.5in,angle=0]{figs/placrdaddcuts22019.pdf}}
-      \caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
-      \bigskip
-      \label{placsenscut2}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\newpage
-
-\subsection{Further analysis on the role of mayors, mayoral parties, and parties in the city council.}
-
-In this section, we analyze the role of political composition of city council and mayoral parties on outcomes.
-We also analyzed the revenues and transfers from the Federal government to municipalities.
-
-\subsubsection{Mayoral parties}
-
-Mayors in Brazil have considerably more discretionary power to implement policies when compared with city councilors.
-Therefore, our outcomes could be byproduct of the mayor in power.
-To avoid this possibility, we run the regressions using the mayoral parties as an outcome.
-The results below show no differences in likelihood of electing a mayor from PT, PSDB, PMDB, and PFL when we add an extra councilor.
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:17:47
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Mayors from Major Parties} 
-  \label{appmayparty} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Mayor from PT}} & \multicolumn{1}{c}{\textbf{Mayor from PSDB}} & \multicolumn{1}{c}{\textbf{Mayor from PMDB}} & \multicolumn{1}{c}{\textbf{Mayor from PFL (DEM)}} \\ 
-\hline \\[-1.8ex] 
- LATE & -0.01 & 0.11 & 0.0004 & 0.01 \\ 
-  & (0.09) & (0.12) & (0.10) & (0.06) \\ 
- N Left & 5069 & 5069 & 5069 & 5069 \\ 
-N Right & 335 & 335 & 335 & 335 \\ 
-Eff N Left & 257 & 162 & 226 & 105 \\ 
-Eff N Right & 166 & 124 & 154 & 103 \\ 
-BW Loc Poly & 10.52 & 7.585 & 9.637 & 5.605 \\ 
-BW Bias & 16.103 & 11.409 & 15.41 & 9.632 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular}}
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:17:47
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Mayors from Major Parties -- Placebo} 
-  \label{placappmayparty} 
-  \resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Mayor from PT}} & \multicolumn{1}{c}{\textbf{Mayor from PSDB}} & \multicolumn{1}{c}{\textbf{Mayor from PMDB}} & \multicolumn{1}{c}{\textbf{Mayor from PFL (DEM)}} \\ 
-\hline \\[-1.8ex] 
- LATE & 0.05 & 0.02 & 0.03 & -0.11$^{*}$ \\ 
-  & (0.05) & (0.06) & (0.07) & (0.06) \\ 
- N Left & 4526 & 4526 & 4526 & 4526 \\ 
-N Right & 878 & 878 & 878 & 878 \\ 
-Eff N Left & 486 & 823 & 609 & 544 \\ 
-Eff N Right & 319 & 453 & 372 & 335 \\ 
-BW Loc Poly & 5.568 & 8.407 & 6.551 & 6.027 \\ 
-BW Bias & 9.222 & 13.908 & 10.539 & 11.459 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular}}
-\end{table}
-
-\subsubsection{Mayoral characteristics}
-
-We also run the same regressions on mayoral characteristics.
-We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
-The results also show no variation on council size and mayoral characteristics.
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:17:50
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Mayoral Characteristics} 
-  \label{appmaychar} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
-College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
-\hline \\[-1.8ex] 
- LATE & 0.07 & -0.06 & -0.09 & 0.06 \\ 
-  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
- N Left & 5069 & 5069 & 5184 & 5183 \\ 
-N Right & 335 & 335 & 343 & 343 \\ 
-Eff N Left & 299 & 226 & 192 & 231 \\ 
-Eff N Right & 184 & 154 & 141 & 159 \\ 
-BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\ 
-BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular} }
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:17:51
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Mayoral characteristics -- Placebo} 
-  \label{placappmaychar} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
-College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
-\hline \\[-1.8ex] 
- LATE & 0.03 & 0.04 & 0.08 & -0.07 \\ 
-  & (0.05) & (0.08) & (0.07) & (0.08) \\ 
- N Left & 4526 & 4526 & 4621 & 4620 \\ 
-N Right & 878 & 878 & 906 & 906 \\ 
-Eff N Left & 567 & 707 & 683 & 759 \\ 
-Eff N Right & 342 & 406 & 397 & 427 \\ 
-BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\ 
-BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular} }
-\end{table}
-
-\subsubsection{Transfers and revenue}
-
-To investigate whether transfers are driving our results, we run the regressions on federal transfers and revenue raised within the municipalities.
-There is only a small effect on education transfer.
-The other indicators remain insignificant.
-Note that the placebo is significant, but this does not invalidate the placebo tests.
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:18:41
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Transfers and Revenue} 
-  \label{apptrev} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
-\hline \\[-1.8ex] 
- LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\ 
-  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
- N Left & 15555 & 15555 & 15460 & 14668 \\ 
-N Right & 1029 & 1029 & 1028 & 998 \\ 
-Eff N Left & 804 & 258 & 349 & 626 \\ 
-Eff N Right & 516 & 273 & 333 & 442 \\ 
-BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\ 
-BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular} }
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:18:42
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Transfers and Revenue -- Placebo} 
-  \label{plactrev} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
-\hline \\[-1.8ex] 
- LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\ 
-  & (0.03) & (0.03) & (0.06) & (0.03) \\ 
- N Left & 13865 & 13865 & 13776 & 13103 \\ 
-N Right & 2719 & 2719 & 2712 & 2563 \\ 
-Eff N Left & 807 & 636 & 1928 & 848 \\ 
-Eff N Right & 619 & 544 & 1163 & 611 \\ 
-BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\ 
-BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular} }
-\end{table}
-
-\subsubsection{City councilors party composition}
-
-As the result could be driven by party composition of the mayor, we run the regression on city council party composition. There is no effect of party composition and city council size.
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:17:54
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Councilors from Major Parties} 
-  \label{appcouncilparty} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
-\hline \\[-1.8ex] 
- LATE & -0.01 & -0.05 & -0.01 & -0.01 \\ 
-  & (0.02) & (0.05) & (0.03) & (0.02) \\ 
- N Left & 5179 & 5179 & 5179 & 5179 \\ 
-N Right & 343 & 343 & 343 & 343 \\ 
-Eff N Left & 375 & 152 & 267 & 231 \\ 
-Eff N Right & 212 & 121 & 172 & 159 \\ 
-BW Loc Poly & 13.99 & 6.8 & 10.58 & 9.63 \\ 
-BW Bias & 22.64 & 11.373 & 16.803 & 15.647 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular} }
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Fri, Oct 04, 2019 - 00:17:55
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Councilors from Major Parties -- Placebo} 
-  \label{placappcouncilparty} 
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
-\hline \\[-1.8ex] 
- LATE & 0.02 & 0.01 & 0.02 & 0.003 \\ 
-  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
- N Left & 4617 & 4617 & 4617 & 4617 \\ 
-N Right & 905 & 905 & 905 & 905 \\ 
-Eff N Left & 434 & 939 & 621 & 845 \\ 
-Eff N Right & 303 & 495 & 378 & 461 \\ 
-BW Loc Poly & 5.012 & 9.003 & 6.505 & 8.333 \\ 
-BW Bias & 8.078 & 13.701 & 11.172 & 13.303 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
-\multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-\multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
-\end{tabular} }
-\end{table}
-
-\newpage
-
-\subsection{Legislation Dataset\label{legdfr}}
-
-In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds.
-There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.
-
-To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases.
-First, we train and test the accuracy of the SVM classifier on 80\% of the dataset.
-Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
-We choose SVM as it gives the highest prediction rate.
-We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
-
-We hand-coded using five characteristics:
-
-\begin{enumerate}
-    \item \textbf{Local Public Goods}: Whether the bills provided a local public good or service.
-Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
-To lay on this category, the service should have been targeted for a fraction of the population.
-    \item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law).
-    \item \textbf{Oversight}: Legislation requesting information on the status of service provision.
-    \item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
-    \item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
-\end{enumerate}
-
-We run the SVM on the hand-coded data.
-Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded.
-In all models, we set cost equals 10 to avoid overfitting.
-
-\begin{table}
-\centering
-\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
-\label{accurClassif}
-\begin{tabular}{lc} 
-\hline
-\textbf{Variable}            & \textbf{Accuracy}  \\ 
-\hline
-Local Public Goods           & 93.8               \\
-Public Goods and Legislation & 94.2               \\
-Oversight                    & 94.9               \\
-Others                       & 93.5               \\
-Education and Health Care    & 92.5               \\
-\hline
-\end{tabular}
-\end{table}
-
-After we classify all the bills, the frequency in each category was added to the main paper.
-We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
-As expected, the results changed little from when we considered the absolute values.
-
-\newpage
-
-\subsection{City Councilors Survey\label{appsurv}}
-
-From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period.
-We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.
-
-We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
-In December 1st we closed the pool, having 174 responses.
-Figure \ref{geodistrsurv} displays a distribution of responses.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/distrrespsurvey2019.pdf}}
-      \caption{Geographical Distribution of Survey Responses}
-      \bigskip
-      \label{geodistrsurv}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative.
-We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions.
-We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
-In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
-
-\begin{table}[htp!]
-\centering
-\caption{Proportions for each bin used in the weighting process}
-\label{tabweight}
-\begin{tabular}{lccc}
-\hline
-& Sample & Population & Weighted \\
-& Proportions & Proportions. & Proportions \\
-\hline
-\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
-\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
-\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
-\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
-\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
-\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
-\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
-\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
-\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
-\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
-\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
-\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
-\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
-\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
-\end{tabular}
-\end{table}
-
-Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.
-
-The questions of interest for this research, asked in the survey were:
-
-\begin{enumerate}
-    \item No Brasil é comum que o prefeito tenha de negociar para ter maioria na Câmara de Vereadores.
-Com que frequência, o(a) Sr(a) acha que o prefeito usa os seguintes dispositivos para conseguir apoio?
-    \item Quais dessas atividades o(a) Sr(a) acredita serem mais comuns no trabalho da maioria dos vereadores?
-    \item Quais dessas atividades o(a) Sr(a) acredita que ajudam mais um vereador durante a eleição?
-\end{enumerate}
-
-A free translation to English would be:
-
-\begin{enumerate}
-    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
-    \item Which of those activities do city councilors perform the most in their representation practices?
-    \item Which of the following activities do you believe helps city councilors the most in elections?
-\end{enumerate}
-
-The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
-Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6.5in,angle=0]{figs/commonJobsCouncilorsJan2019.pdf}}
-      \caption{City Councilor's Common Activities}
-      \bigskip
-      \label{commonservice}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-The last question measures the willingness of mayors to give services to city councilors.
-This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors.
-Figure \ref{mayorneg} shows the results for the mayoral activities.
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6.5in,angle=0]{figs/strategySupportMayorsJan2019.pdf}}
-      \caption{Mayor negotiated services in exchange of support}
-      \bigskip
-      \label{mayorneg}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield.
-The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.
-
-Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors.
-Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.

### 2021-08-09 appendix/appendix.Rmd
lemma bargaining

@@
 
-\begin{lemma}
+\begin{lemma}\label{lemmabarg}
 The amount of rents required to win support from a given legislator decreases when the number of legislators increase.
@@
 & - \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
-= \ & XXXX \\
-= \ & XXXX \\
+= \ & \dfrac{1}{2N+1}\left[\left(1-\dfrac{2}{2N+3}\right)\left(2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-N(\underline{t} + B) + \underline{t}\right) \right. \\
+& - \left. 2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
+= \ & -\dfrac{1}{2N+1}\left[\dfrac{2}{2N+3}\left(2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-N(\underline{t} + B) + \underline{t}\right) \right. \\
+& + \left. \dfrac{2 R \delta (1-\delta)}{2N} + \underline{t} + B\right] \equiv \Delta b(N) \\
 < \ &0
@@
 \]
+
+Therefore, larger legislature sizes decrease the costs of bargaining.
+This because of two effects: first, the chance of being the proposer decreases; second, the chance of being selected to receive an offer also decreases.
 

### 2021-08-09 appendix/appendix.Rmd
appendix final-2 edition

@@
 
-# A Model of Legislature Size and Service Provision
+## A Model of Legislature Size and Service Provision
 
-## Full model
+### Full model
 
@@
 
-Therefore, to satisfy increasing differences in XXXX,
+Therefore, to satisfy increasing differences in XXXX, XXXX.
 
@@
 
-However, the decrease in rents is not sufficient to have lower costs to govern when we increase the number of legislators.
+Decrease in rents is not sufficient to have lower costs to govern when we increase the number of legislators.
 The political costs, if high enough, can offset the gains with lower rents.
 Higher political costs result from having more members of the opposition in the legislature.
-The next proposition shows the sufficient condition for having a lower cost of govern when we increase the number of legislators.
+The next proposition shows the next condition we need for having a lower cost of govern when we increase the number of legislators.
 
@@
 
+Let $p > \underline{t} + b(N+1) + \dfrac{N}{2}[\Delta b (N) - \Delta b (N-1)]$.
 There exists an ex-ante probability of electing a councilor aligned with the government $\overline{\gamma}$ such that, for all $\gamma > \overline{\gamma}$, the cost of govern decreases as $N$ increases, i.e., $C_G(N+1) \leq C_G(N)$.
@@
 
-Let us rewrite the results as:
+To avoid the even legislature sizes, without loss of generality let us study the case $C_G(N+1) - C_G(N-1)$.
 
 \[
-XXXX \geq 0
+\begin{aligned}
+C_G(N+1) - C_G(N-1) \ = \ & \dfrac{N+1}{2}\left(\underline{t} + b(N+1) + p\right) - 2p\sum_{\eta_g = 0}^{\frac{N}{2}+1}\mathbb{P}(\eta_g)\eta_g \\
+& - \dfrac{N}{2}\left(\underline{t} + b(N-1) + p\right) + 2p\sum_{\eta_g = 0}^{\frac{N}{2}}\mathbb{P}(\eta_g)\eta_g \\
+= \ & \underline{t} + b(N+1) + p + \dfrac{N}{2}\left[b(N+1) - b(N-1)\right] \\
+& - 2p\left[\sum_{\eta_g = 0}^{\frac{N}{2}+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{\frac{N}{2}}\mathbb{P}(\eta_g)\eta_g\right] \\
+= \ & \underline{t} + b(N+1) + p + \dfrac{N}{2}\left[\Delta b(N) - \Delta b(N-1)\right] - 2p\left[\Delta \eta_g(\gamma) \right]
+\end{aligned}
 \]
 
-Rearranging the terms:
+Where $\Delta\eta_n(\gamma) \equiv \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]$. The condition for this to be negative is:
 
 \[
-- \underline{t} - \underline{x}_o^g(N+1) - \dfrac{N}{2}(\underline{x}_o^g(N+1) - \underline{x}_o^g(N-1)) -2p \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]
+\begin{aligned}
+\Delta \eta_g(\gamma) \ \geq \ & \dfrac{1}{2p}\left[ \underline{t} + b(N+1) + p + \dfrac{N}{2}\left(\Delta b(N) - \Delta b(N-1)\right) \right] \\
+= \ & \dfrac{1}{2}\left[1 + \dfrac{\underline{t} + b(N+1) + \dfrac{N}{2}\left(\Delta b(N) - \Delta b(N-1)\right)}{p} \right]
+\end{aligned}
 \]
 
-Let $\Delta\eta_n(\gamma) \equiv \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]$.
-There is no closed form solution for this equation.
-We can approximate the boundaries using @wXXXX but graphically, we can have a good sense of the XXXX:
+There is no closed form solution for $\Delta\eta_n(\gamma)$, but we can approximate the bounds using @worsch1994lower.
+Moreover, we can simulate the differences for several legislature sizes, showing that as $N$ increases, a smaller $\gamma$ suffices to make the quantity greater than zero.
 
-XXXX GRAPH DELTA GAMMA HERE
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{1 \linewidth}
+\centerline{\includegraphics[width=6.5in,angle=0]{delta_eta_g_gamma.pdf}}
+\caption{Graph for the Binomial Expectation Difference in Support}
+\bigskip
+\label{binomdiff}
+\end{minipage}
+\end{center}
+\end{figure}
 
-And solving for $\Delta\eta_n(\gamma)$ we have that:
+Note that $\Delta\eta_n(\gamma)$ is between minus-one and one, meaning that either all legislators are opposition-aligned or all legislators are government-aligned.
+Moreover, note that $\Delta b(N) - \Delta b(N-1)$ is negative.
+As we assume that the political disagreement is large enough to satisfy $p > \underline{t} + b(N+1) + \dfrac{N}{2}[\Delta b (N) - \Delta b (N-1)]$, then:
 
 \[
-XXXX
+-1 \leq \dfrac{1}{2}\left[1 + \dfrac{\underline{t} + b(N+1) + \dfrac{N}{2}\left(\Delta b(N) - \Delta b(N-1)\right)}{p} \right] \leq 1
 \]
 
-The natural boundaries for $\Delta\eta_n(\gamma)$ are minus-one and one.
-Minus-one means that the additional legislature seat went to the opposition while one means that the additional legislature seat went to the government.
-XXXX
+And thus, there exists an $\overline{\gamma}$ such that:
+
+\[
+\Delta \eta_g(\overline{\gamma}) \ = \ \dfrac{1}{2}\left[1 + \dfrac{\underline{t} + b(N+1) + \dfrac{N}{2}\left(\Delta b(N) - \Delta b(N-1)\right)}{p} \right]
+\]
 
@@
 
-Taking stocks, the model provides two testable hypothesis. Let a legislature that previously had $N$ legislators, and now increased the legislature by $N+1$. Then:
+### Paper Version of the Model
+
+In the main paper, we simplify the analysis by assuming rational expectations regarding the number of opposition and government aligned politicians.
+If the chance of electing a government aligned politicians is $\gamma$, the expected number of government aligned politicians is $N\gamma$, and the expected number of opposition-aligned politicians is $(1-\gamma)N$.
+The differences in cost of govern, in this situation, becomes simpler to infer.
+
+\begin{proposition}
+
+Let the political disagreement $p > \underline{t} + b(N+1) + N\Delta b(N)$.
+If the chance of electing a government-aligned politician $\gamma \ \geq \ \dfrac{1}{2}\left[1 + \dfrac{\underline{t} + b(N+1) + N\Delta b(N)}{p}\right]$, then the costs of govern decrease as the legislature size increases.
+
+\end{proposition}
+
+\begin{proof}
+
+The differential cost of govern when increasing the
+
+\[
+\begin{aligned}
+C_G(N+1) - C_G(N) \ = \ & \dfrac{N+1}{2}\left(\underline{t} + b(N+1) + p (1-2\gamma)\right) \\
+& - \dfrac{N}{2}\left(\underline{t} + b(N) + p(1-2\gamma)\right) \\
+= \ & \dfrac{1}{2}\underline{t} + \dfrac{1}{2}b(N+1) + p - 2\gamma p + \dfrac{N}{2}\Delta b(N)
+\end{aligned}
+\]
+
+To the cost of govern decrease with $N$, the probability of electing a government aligned politicians has to be greater than or equal to:
+
+\[
+\gamma \ \geq \ \dfrac{1}{2}\left[1 + \dfrac{\underline{t} + b(N+1) + N\Delta b(N)}{p}\right] \ \equiv \ \overline{\gamma}
+\]
+
+Note that this formulation is similar to the one derived in Proposition \ref{mainprop}.
+
+\end{proof}
+
+All the dynamics remain the same but the second hypothesis becomes clearer, with a simplified quantity for the probability of electing a government-aligned politician, $\overline{\gamma}$.
+The simplified $\overline{\gamma}$ is helpful because it shows that the political disagreement has to be high enough to compensate the XXXX.
+
+### Main Hypotheses
+
+Taking stocks, the models provide two empirically testable hypotheses. Consider a legislature that previously had $N$ legislators, but now needs to increase its legislature by $N+1$. Then:
 
@@
 
-## Paper Version of the Model
-
-In the main paper, we simplify the analysis with two assumptions regarding the costs of govern.
-First, we assume a simpler reversal where there is only one reversal stage and after that a reversal policy of zero in all policy components take place.
-Second, we assume that the cost for govern will depend on the ex-ante expected number of legislator belonging to the government and the opposition.
-In this case, the rents $b(N)$ become:
-
-\[
-XXXX
-\]
-
-And Proposition \ref{mainprop} becomes:
-
-\begin{proposition}
-
-XXXX
-
-\[
-XXXX
-\]
-
-\end{proposition}
-
-\begin{proof}
-XXXX
-\end{proof}
-
-All the dynamics remain the same but the second hypothesis becomes clearer, with a simplified quantity for the probability of electing a government-aligned politician, $\overline{\gamma}$.
-The simplified $\overline{\gamma}$ is helpful because it shows that the political concerns require a probability larger than one-half, with a precise amount depending on the XXXX.
-
 \newpage

### 2021-08-10 appendix/appendix.Rmd
adding more packages appendix

@@
 \begin{definition}
-The solution for the game consists in a pair of strategic policy vectors for the mayor, and the city councilors. The mayor's policy vector is comprised of a public goods provision $g^*$ and XXXX
+The solution for the game consists in a pair of strategic policy vectors for the mayor, and the city councilors, indexed by the round of the implementation.
+The mayor's policy vector is comprised of a public goods provision $g^*$, rents $r^*$, $\mathbb{t}$ XXXX
 \end{definition}
@@
 \newpage
+
+\subsection{Variable Sources and Descriptive Statistics\label{appsources}}
+
+We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
+
+\begin{sidewaystable}[!htbp] \centering 
+\caption{Data Sources} 
+\label{varsources}
+\scalebox{0.75}{
+  \begin{tabular}{@{\extracolsep{5pt}}llll} 
+  \\[-1.8ex]\hline\hline \\[-1.8ex] 
+  Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
+  \hline \\[-1.8ex] 
+  & & & \\
+  DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
+  & & & \\
+  IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
+  & & & \\
+  INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
+  & & & \\
+  InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
+  & & & \\
+  IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
+  & & & \\
+  MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
+  & & & \\
+  TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
+  & & & \\
+  \hline\hline \\[-1.8ex] 
+  \end{tabular} 
+}
+\end{sidewaystable}
+
+Now let us define each variable.
+
+\textbf{Outcomes Aggregated at the Municipal Level:}
+
+\begin{itemize}
+\item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
+\item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
+\item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
+\item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
+\item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
+\item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
+\item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
+\item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
+\item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
+\item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
+IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
+The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
+    \item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality.
+IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying.
+The estimators are cleaned to avoid the influence of schools and classrooms specific effects.
+(source: INEP, years: 2005, 2007).
+\item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
+\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
+\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality.
+Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
+\item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
+    \item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
+    \item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council.
+We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures).
+    \item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
+    \item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
+\end{itemize}
+
+\textbf{Legislation Dataset:}
+
+We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:
+
+\begin{itemize}
+    \item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
+    \item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
+    \item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
+  \item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
+  \item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
+  \end{itemize}
+
+  \textbf{Online 2016 Former City Councilors Survey:}
+
+  We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:
+
+    \begin{itemize}
+  \item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
+  \item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
+  \end{itemize}
+
+  In this Appendix, we present other questions we asked in the survey.
+They are meant to improve the knowledge we have about the city councilors perceptions about their representation.
+We have not added these to the main paper because they were more complimentary and not of general interest.
+The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.
+
+  \input{tabs/edited/sumstatOut2016e.tex}
+
+  \newpage
+
+  \subsection{Threshold Manipulation, Sorting, and Pre-treatment Consistency}
+
+  The validity of our causal claim relies on three assumptions.
+First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds.
+Second, that we are consistently comparing municipalities in the same cutoffs.
+Lastly, that we have no pre-treatment differences in our sample.
+
+  For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
+For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
+
+  We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
+We use local polynomial orders from one to four.
+As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
+Therefore, there is no manipulation according to \citet{calonico2019regression}.
+
+  We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
+
+  \begin{figure}[htb!]
+  \begin{center}
+  \begin{minipage}{1 \linewidth}
+  \centerline{\includegraphics[width=5in,angle=0]{figs/McCrary.pdf}}
+  \caption{\citet{McCrary2008} manipulation test}
+  \bigskip
+  \label{manipulationplot}
+  \end{minipage}
+  \end{center}
+  \end{figure}
+
+  For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}.
+For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21.
+When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor.
+However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors.
+This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
+That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.
+
+To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
+Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
+The reason for the first variable is the multiple threshold assignments.
+We add GDP per capita because wealthier cities tend to be more productive and have better public services.
+The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
+The year and the northeast dummies serve to improve efficiency.
+Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.
+See the following section for further tests and simulations.
+
+For the last assumption, we should have no changes in pre-treatment covariates.
+These pre-treatment covariates are variables measured before the primary outcomes.
+As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
+
+Table \ref{validitycheck} displays the results of the validity checks.
+At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs.
+At the bottom, we estimate the pre-treatment covariate balance.
+
+\begin{table}[htb!] \centering 
+  \caption{Research Design Validity Check} 
+  \label{validitycheck} 
+    \scalebox{0.9}{
+  \begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+ & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
+   & \multicolumn{1}{c}{\small{(1)}} & 
+ \multicolumn{1}{c}{\small{(2)}} & 
+ \multicolumn{1}{c}{\small{(3)}} & 
+ \multicolumn{1}{c}{\small{(4)}} \\
+
+ & \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} & 
+ \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
+  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+\\[-1.8ex] 
+ LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
+  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
+\hdashline \\[-1.8ex]   
+ N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
+Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
+BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
+BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
+\midrule 
+ & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(5)}} & 
+ \multicolumn{1}{c}{\small{(6)}} & 
+ \multicolumn{1}{c}{\small{(7)}} & 
+ \multicolumn{1}{c}{\small{(8)}} \\
+  & \multicolumn{1}{c}{\small{Number of}} & 
+ \multicolumn{1}{c}{\small{Population}} & 
+ \multicolumn{1}{c}{\small{GDP}} & 
+ \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2000}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} &
+   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
+  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
+  \hdashline \\[-1.8ex]
+ N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
+Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
+Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
+BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
+BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
+RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
+After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
+Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
+These tests reinforce the validity of our research designs.
+
+\pagebreak
+
+\subsection{Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision\label{appidentif}}
+
+The identification strategy requires exogenous changes in the city council size thresholds.
+Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
+
+\begin{table}[htp!]
+\centering
+\caption{City council size from the 1988 Constitution}
+\scalebox{0.75}{
+\begin{tabular}{rccrrr}
+  \hline\hline
+ & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\ 
+ & & & & & \multicolumn{1}{c}{(2001-2004)} \\
+  \hline
+  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\ 
+  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\ 
+  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\ 
+   \hline\hline
+\end{tabular}
+}
+\label{tabcitycouncilsize1988}
+\end{table}
+
+These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors.
+The two losing councilors started a judicial contestation that made it to the Supreme Court.
+The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55.
+Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004).
+According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
+
+\begin{table}[htp!]
+\centering
+\caption{City council size thresholds according to TSE resolution 21,702/2004}
+\scalebox{0.75}{
+\begin{tabular}{rcrrr}
+  \hline\hline
+ &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
+ & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
+  \hline
+  1 &  9 & 0 & 47,619 & 5,029 \\ 
+  2 &  10 & 47,620 & 95,238 & 317 \\ 
+  3 &  11 & 95,239 & 142,857 & 89 \\ 
+  4 &  12 & 142,858 & 190,476 & 43 \\ 
+  5 &  13 & 190,477 & 238,095 & 30 \\ 
+  6 &  14 & 238,096 & 285,714 & 21 \\ 
+  7 &  15 & 285,715 & 333,333 & 13 \\ 
+  8 &  16 & 333,334 & 380,952 & 13 \\ 
+  9 &  17 & 380,953 & 428,571 & 6 \\ 
+  10  & 18 & 428,572 & 476,190 & 6 \\ 
+  11  & 19 & 476,191 & 523,809 & 4 \\ 
+  12  & 20 & 523,810 & 571,428 & 5 \\ 
+  13  & 21 & 571,429 & 1,000,000 & 13 \\ 
+  14  & 33 & 1,000,001 & 1,121,952 & 1 \\ 
+  15  & 34 & 1,121,953 & 1,243,903 & 2 \\ 
+  16  & 35 & 1,243,904 & 1,365,854 & 1 \\ 
+  17  & 36 & 1,365,855 & 1,487,805 & 2 \\ 
+  18  & 37 & 1,487,806 & 1,609,756 & 1 \\ 
+  19  & 38 & 1,609,757 & 1,731,707 & 1 \\ 
+  20  & 39 & 1,731,708 & 1,853,658 & 0 \\ 
+  21  & 40 & 1,853,659 & 1,975,609 & 0 \\ 
+  22  & 41 & 1,975,610 & 4,999,999 & 4 \\ 
+  23  & 42 & 5,000,000 & 5,119,047 & 0 \\ 
+  24  & 43 & 5,119,048 & 5,238,094 & 0 \\ 
+  25  & 44 & 5,238,095 & 5,357,141 & 0 \\ 
+  26  & 45 & 5,357,142 & 5,476,188 & 0 \\ 
+  27  & 46 & 5,476,189 & 5,595,235 & 0 \\ 
+  28  & 47 & 5,595,236 & 5,714,282 & 0 \\ 
+  29  & 48 & 5,714,283 & 5,833,329 & 0 \\ 
+  30  & 49 & 5,833,330 & 5,952,376 & 0 \\ 
+  31  & 50 & 5,952,377 & 6,071,423 & 1 \\ 
+  32  & 51 & 6,071,424 & 6,190,470 & 0 \\ 
+  33  & 52 & 6,190,471 & 6,309,517 & 0 \\ 
+  34  & 53 & 6,309,518 & 6,428,564 & 0 \\ 
+  35  & 54 & 6,428,565 & 6,547,611 & 1 \\ 
+  36  & 55 & 6,547,612 & $\infty$  & 0 \\ 
+   \hline\hline
+\end{tabular}
+}
+\label{tabcitycouncilsize2004all}
+\end{table}
+
+As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants.
+Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.
+
+\begin{table}[htp!]
+\centering
+\caption{City council thresholds used in the paper}
+\scalebox{0.85}{
+\renewcommand*{\arraystretch}{1.2}
+\begin{tabular}{rcrrr}
+  \hline \hline
+ & \multicolumn{1}{c}{Legislature} & \multicolumn{1}{c}{Min.} & \multicolumn{1}{c}{Max.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
+ & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{(2003 pop.)} \\
+  \hline
+  1 & 9 & 0 & 47,619 & 5,029 \\ 
+  2 & 10 & 47,620 & 95,238 & 317 \\ 
+  3 & 11 & 95,239 & 142,857 & 89 \\ 
+  4 & 12 & 142,858 & 190,476 & 43 \\ 
+  5 & 13 & 190,477 & 238,095 & 30 \\ 
+  6 & 14 & 238,096 & 285,714 & 21 \\ 
+  7 & 15 & 285,715 & 333,333 & 13 \\ 
+  8 & 16 & 333,334 & 380,952 & 13 \\ 
+  9 & 17 & 380,953 & 428,571 & 6 \\ 
+  10 & 18 & 428,572 & 476,190 & 6 \\ 
+  11 & 19 & 476,191 & 523,809 & 4 \\ 
+  12 & 20 & 523,810 & 571,428 & 5 \\ 
+  13 & 21 & 571,429 & 1,000,000 & 13 \\ 
+   \hline \hline
+\end{tabular}
+}
+\label{tabcitycouncilsize2004short}
+\end{table}
+
+The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
+In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections.
+Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).
+
+To provide an overview of the data dispersion, Figure \ref{sample_plot} plots the municipalities by their proximity from the cutoffs.
+In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
+The darker the color, the closer to the population thresholds.
+In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation.
+Figure \ref{sample_plot} also shows that our municipalities are reasonably distributed around the whole country.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=7in,angle=0]{figs/sampplot2019.pdf}}
+      \caption{Municipalities by their Selection Status}
+      \bigskip
+      \label{sample_plot}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+Moreover, we could question whether the discontinuities studied here are sharp or fuzzy.
+In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced.
+For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities.
+However, this problem was absent in our RDD, as the problem identified by Cavalvanti was based on the use of thresholds approved in 2009.
+In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).
+
+\newpage
+
+\subsection{Identification Strategy in Multiple Thresholds Regression Discontinuity Design\label{ISMT}}
+
+Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes.
+Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
+The outcome variable is assumed to be $Y$.
+In the pooled model, the Local Average Treatment Effect is:
+
+\[
+LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
+\]
+
+Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff.
+The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
+To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
+For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
+As the population varies smoothly around each cutoff, it makes it a perfect control to add.
+The new estimator is:
+
+\[
+LATE_{controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C, Z_i \right]
+\]
+
+We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
+All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}.
+To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff.
+To compute the optimal bandwidth, we use the \citet{CCT2014} method.
+To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
+We also use cluster-robust standard errors at the municipal level.
+
+However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable?
+To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.
+
+Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
+We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes.
+The first three outcomes are sharp changes.
+In the first, we add variation from one to 10, with one step for each change.
+In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
+The estimated change should be equal to zero.
+In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
+This is intended to simulate a diminishing effect from one cutoff to the other.
+The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
+We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{0.9\linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/simdistrRDD.pdf}}
+      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
+      \bigskip
+      \label{simRDdd}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+A consistent estimator should fit one in the first and fourth data distribution.
+In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
+In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$.
+The first three models should present a more efficient estimation than the last three models.
+We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1\linewidth}
+      \centerline{\includegraphics[width=4.5in,angle=0]{figs/estimsRDD.pdf}}
+      \caption{Estimations for the Different Data Generating Processes}
+      \bigskip
+      \label{estimDGP}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Placebo Regressions for the Aggregated Mechanism Outcomes\label{placmechmain}}
+
+Here we present the placebo regressions for the mechanism-aggregated outcomes.
+In Panel A of the main paper, we run the regression on alternative explanations.
+As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases.
+For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank.
+In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage.
+As expected, the placebo regressions were not statistically significant.
+
+\input{tabs/edited/appmechreg1Oct2016e.tex}
+
+\newpage
+
+\subsection{Sensitivity Analysis for Bandwidth Selection\label{sensffapp}}
+
+We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1\linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/bwsens2019.pdf}}
+      \caption{Bandwidth Sensitivity -- Main Models}
+      \bigskip
+      \label{graphbw}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placbwsens2019.pdf}}
+      \caption{Placebo Regressions -- Bandwidth Sensitivity}
+      \bigskip
+      \label{placgraphbw}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to Different States in the Analysis\label{sensstate}}
+
+The literature considers that some states are more prone to inefficiencies than the rest of the country.
+Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves.
+As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size.
+We run the analysis dropping one state at a time, to investigate this statewide heterogeneity.
+The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
+
+To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks.
+The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states.
+In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo.
+Otherwise, note that all the other variables remain unchanged, except for gender.
+Gender changes because there were laws during this period mandating a minimum amount of female candidates.
+It is expected that one variable changes as a response to randomness.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/dropstatesens12019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
+      \bigskip
+      \label{graphsensstatedrop1}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/dropstatesens22019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
+      \bigskip
+      \label{graphsensstatedrop2}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placdropstatesens12019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop1}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/placdropstatesens22019.pdf}}
+      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop2}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to the Functional Form Analysis\label{sensfuncform}}
+
+In the paper, we run all the regressions using local linear polynomials.
+\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
+
+However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms.
+With two exceptions, the results are mostly consistent.
+First, quadratic and cubic polynomials make the significance go away in some models.
+Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions.
+Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/ffsens2019.pdf}}
+      \caption{Sensitivity Analysis for the Functional Form}
+      \bigskip
+      \label{graphsensff}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/placffsens2019.pdf}}
+      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
+      \bigskip
+      \label{placgraphsensff}
+  \end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to Covariates\label{senstcovapp}}
+
+The control variables play an essential role in our model.
+As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
+
+However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis.
+To study the sensitivity to controls, we run the same regressions for all possible control combinations.
+Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
+The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}
+
+\begin{landscape}
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=6in,angle=0]{figs/senscov2019.pdf}}
+      \caption{Sensitivity Analysis for the Control Variable's Choices}
+\bigskip
+\label{graphsenscontrol}
+\end{minipage}
+\end{center}
+\end{figure}
+\end{landscape}
+
+For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.
+
+In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant.
+Otherwise, our model is not significant when most combinations are also insignificant.
+Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.
+
+We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
+The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=5in,angle=0]{figs/placsens1cov2019.pdf}}
+\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
+\bigskip
+\label{placsenscov1}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=5in,angle=0]{figs/placsens2cov2019.pdf}}
+\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
+\bigskip
+\label{placsenscov2}
+\end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}
+
+To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
+This strategy is similar to adding one cutoff at a time.
+The results are stable and do not change our main conclusions.
+Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring.
+Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=6in,angle=0]{figs/rdaddcuts12019.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
+\bigskip
+\label{senscut1}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=6in,angle=0]{figs/rdaddcuts22019.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
+\bigskip
+\label{senscut2}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{0.8 \linewidth}
+\centerline{\includegraphics[width=5.5in,angle=0]{figs/placrdaddcuts12019.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
+\bigskip
+\label{placsenscut1}
+\end{minipage}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{0.8 \linewidth}
+\centerline{\includegraphics[width=5.5in,angle=0]{figs/placrdaddcuts22019.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
+\bigskip
+\label{placsenscut2}
+\end{minipage}
+\end{center}
+\end{figure}
+
+\newpage
+
+\subsection{Further analysis on the role of mayors, mayoral parties, and parties in the city council.}
+
+In this section, we analyze the role of political composition of city council and mayoral parties on outcomes.
+We also analyzed the revenues and transfers from the Federal government to municipalities.
+
+\subsubsection{Mayoral parties}
+
+Mayors in Brazil have considerably more discretionary power to implement policies when compared with city councilors.
+Therefore, our outcomes could be byproduct of the mayor in power.
+To avoid this possibility, we run the regressions using the mayoral parties as an outcome.
+The results below show no differences in likelihood of electing a mayor from PT, PSDB, PMDB, and PFL when we add an extra councilor.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:47
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Mayors from Major Parties} 
+\label{appmayparty} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Mayor from PT}} & \multicolumn{1}{c}{\textbf{Mayor from PSDB}} & \multicolumn{1}{c}{\textbf{Mayor from PMDB}} & \multicolumn{1}{c}{\textbf{Mayor from PFL (DEM)}} \\ 
+  \hline \\[-1.8ex] 
+  LATE & -0.01 & 0.11 & 0.0004 & 0.01 \\ 
+  & (0.09) & (0.12) & (0.10) & (0.06) \\ 
+  N Left & 5069 & 5069 & 5069 & 5069 \\ 
+  N Right & 335 & 335 & 335 & 335 \\ 
+  Eff N Left & 257 & 162 & 226 & 105 \\ 
+  Eff N Right & 166 & 124 & 154 & 103 \\ 
+  BW Loc Poly & 10.52 & 7.585 & 9.637 & 5.605 \\ 
+  BW Bias & 16.103 & 11.409 & 15.41 & 9.632 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular}}
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:47
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Mayors from Major Parties -- Placebo} 
+\label{placappmayparty} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Mayor from PT}} & \multicolumn{1}{c}{\textbf{Mayor from PSDB}} & \multicolumn{1}{c}{\textbf{Mayor from PMDB}} & \multicolumn{1}{c}{\textbf{Mayor from PFL (DEM)}} \\ 
+  \hline \\[-1.8ex] 
+  LATE & 0.05 & 0.02 & 0.03 & -0.11$^{*}$ \\ 
+  & (0.05) & (0.06) & (0.07) & (0.06) \\ 
+  N Left & 4526 & 4526 & 4526 & 4526 \\ 
+  N Right & 878 & 878 & 878 & 878 \\ 
+  Eff N Left & 486 & 823 & 609 & 544 \\ 
+  Eff N Right & 319 & 453 & 372 & 335 \\ 
+  BW Loc Poly & 5.568 & 8.407 & 6.551 & 6.027 \\ 
+  BW Bias & 9.222 & 13.908 & 10.539 & 11.459 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular}}
+\end{table}
+
+\subsubsection{Mayoral characteristics}
+
+We also run the same regressions on mayoral characteristics.
+We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
+The results also show no variation on council size and mayoral characteristics.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:50
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Mayoral Characteristics} 
+\label{appmaychar} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
+College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
+  \hline \\[-1.8ex] 
+  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\ 
+  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
+  N Left & 5069 & 5069 & 5184 & 5183 \\ 
+  N Right & 335 & 335 & 343 & 343 \\ 
+  Eff N Left & 299 & 226 & 192 & 231 \\ 
+  Eff N Right & 184 & 154 & 141 & 159 \\ 
+  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\ 
+  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:51
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Mayoral characteristics -- Placebo} 
+\label{placappmaychar} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
+College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
+  \hline \\[-1.8ex] 
+  LATE & 0.03 & 0.04 & 0.08 & -0.07 \\ 
+  & (0.05) & (0.08) & (0.07) & (0.08) \\ 
+  N Left & 4526 & 4526 & 4621 & 4620 \\ 
+  N Right & 878 & 878 & 906 & 906 \\ 
+  Eff N Left & 567 & 707 & 683 & 759 \\ 
+  Eff N Right & 342 & 406 & 397 & 427 \\ 
+  BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\ 
+  BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\subsubsection{Transfers and revenue}
+
+To investigate whether transfers are driving our results, we run the regressions on federal transfers and revenue raised within the municipalities.
+There is only a small effect on education transfer.
+The other indicators remain insignificant.
+Note that the placebo is significant, but this does not invalidate the placebo tests.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:18:41
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Transfers and Revenue} 
+\label{apptrev} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
+  \hline \\[-1.8ex] 
+  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\ 
+  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
+  N Left & 15555 & 15555 & 15460 & 14668 \\ 
+  N Right & 1029 & 1029 & 1028 & 998 \\ 
+  Eff N Left & 804 & 258 & 349 & 626 \\ 
+  Eff N Right & 516 & 273 & 333 & 442 \\ 
+  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\ 
+  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:18:42
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Transfers and Revenue -- Placebo} 
+\label{plactrev} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
+  \hline \\[-1.8ex] 
+  LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\ 
+  & (0.03) & (0.03) & (0.06) & (0.03) \\ 
+  N Left & 13865 & 13865 & 13776 & 13103 \\ 
+  N Right & 2719 & 2719 & 2712 & 2563 \\ 
+  Eff N Left & 807 & 636 & 1928 & 848 \\ 
+  Eff N Right & 619 & 544 & 1163 & 611 \\ 
+  BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\ 
+  BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\subsubsection{City councilors party composition}
+
+As the result could be driven by party composition of the mayor, we run the regression on city council party composition. There is no effect of party composition and city council size.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:54
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Councilors from Major Parties} 
+\label{appcouncilparty} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
+  \hline \\[-1.8ex] 
+  LATE & -0.01 & -0.05 & -0.01 & -0.01 \\ 
+  & (0.02) & (0.05) & (0.03) & (0.02) \\ 
+  N Left & 5179 & 5179 & 5179 & 5179 \\ 
+  N Right & 343 & 343 & 343 & 343 \\ 
+  Eff N Left & 375 & 152 & 267 & 231 \\ 
+  Eff N Right & 212 & 121 & 172 & 159 \\ 
+  BW Loc Poly & 13.99 & 6.8 & 10.58 & 9.63 \\ 
+  BW Bias & 22.64 & 11.373 & 16.803 & 15.647 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Fri, Oct 04, 2019 - 00:17:55
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+\caption{Councilors from Major Parties -- Placebo} 
+\label{placappcouncilparty} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
+  \hline \\[-1.8ex] 
+  LATE & 0.02 & 0.01 & 0.02 & 0.003 \\ 
+  & (0.02) & (0.02) & (0.02) & (0.02) \\ 
+  N Left & 4617 & 4617 & 4617 & 4617 \\ 
+  N Right & 905 & 905 & 905 & 905 \\ 
+  Eff N Left & 434 & 939 & 621 & 845 \\ 
+  Eff N Right & 303 & 495 & 378 & 461 \\ 
+  BW Loc Poly & 5.012 & 9.003 & 6.505 & 8.333 \\ 
+  BW Bias & 8.078 & 13.701 & 11.172 & 13.303 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\newpage
+
+\subsection{Legislation Dataset\label{legdfr}}
+
+In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds.
+There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.
+
+To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases.
+First, we train and test the accuracy of the SVM classifier on 80\% of the dataset.
+Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
+We choose SVM as it gives the highest prediction rate.
+We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
+
+We hand-coded using five characteristics:
+
+  \begin{enumerate}
+\item \textbf{Local Public Goods}: Whether the bills provided a local public good or service.
+Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
+To lay on this category, the service should have been targeted for a fraction of the population.
+\item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law).
+\item \textbf{Oversight}: Legislation requesting information on the status of service provision.
+\item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
+\item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
+\end{enumerate}
+
+We run the SVM on the hand-coded data.
+Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded.
+In all models, we set cost equals 10 to avoid overfitting.
+
+\begin{table}
+\centering
+\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
+\label{accurClassif}
+\begin{tabular}{lc} 
+\hline
+\textbf{Variable}            & \textbf{Accuracy}  \\ 
+\hline
+Local Public Goods           & 93.8               \\
+Public Goods and Legislation & 94.2               \\
+Oversight                    & 94.9               \\
+Others                       & 93.5               \\
+Education and Health Care    & 92.5               \\
+\hline
+\end{tabular}
+\end{table}
+
+After we classify all the bills, the frequency in each category was added to the main paper.
+We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
+As expected, the results changed little from when we considered the absolute values.
+
+\newpage
+
+\subsection{City Councilors Survey\label{appsurv}}
+
+From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period.
+We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.
+
+We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
+In December 1st we closed the pool, having 174 responses.
+Figure \ref{geodistrsurv} displays a distribution of responses.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/distrrespsurvey2019.pdf}}
+      \caption{Geographical Distribution of Survey Responses}
+      \bigskip
+      \label{geodistrsurv}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative.
+We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions.
+We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
+In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
+
+\begin{table}[htp!]
+\centering
+\caption{Proportions for each bin used in the weighting process}
+\label{tabweight}
+\begin{tabular}{lccc}
+\hline
+& Sample & Population & Weighted \\
+& Proportions & Proportions. & Proportions \\
+\hline
+\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
+\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
+\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
+\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
+\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
+\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
+\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
+\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
+\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
+\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
+\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
+\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
+\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
+\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
+\end{tabular}
+\end{table}
+
+Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.
+
+The questions of interest for this research, asked in the survey were:
+
+\begin{enumerate}
+    \item No Brasil é comum que o prefeito tenha de negociar para ter maioria na Câmara de Vereadores.
+Com que frequência, o(a) Sr(a) acha que o prefeito usa os seguintes dispositivos para conseguir apoio?
+    \item Quais dessas atividades o(a) Sr(a) acredita serem mais comuns no trabalho da maioria dos vereadores?
+    \item Quais dessas atividades o(a) Sr(a) acredita que ajudam mais um vereador durante a eleição?
+\end{enumerate}
+
+A free translation to English would be:
+
+\begin{enumerate}
+    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
+    \item Which of those activities do city councilors perform the most in their representation practices?
+    \item Which of the following activities do you believe helps city councilors the most in elections?
+\end{enumerate}
+
+The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
+Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6.5in,angle=0]{figs/commonJobsCouncilorsJan2019.pdf}}
+      \caption{City Councilor's Common Activities}
+\bigskip
+\label{commonservice}
+\end{minipage}
+\end{center}
+\end{figure}
+
+The last question measures the willingness of mayors to give services to city councilors.
+This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors.
+Figure \ref{mayorneg} shows the results for the mayoral activities.
+
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{1 \linewidth}
+\centerline{\includegraphics[width=6.5in,angle=0]{figs/strategySupportMayorsJan2019.pdf}}
+\caption{Mayor negotiated services in exchange of support}
+\bigskip
+\label{mayorneg}
+\end{minipage}
+\end{center}
+\end{figure}
+
+Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield.
+The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.
+
+Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors.
+Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.

### 2021-08-14 appendix/appendix.Rmd
appendix fix model primitives

--- 2021-08-09 appendix/appendix.Rmd
@@
 
-# A Model of Legislature Size and Service Provision
+## A Model of Legislature Size and Service Provision
 
-## Full model
+### Primitives of the Model
 
-Consider an strategic interaction comprised of a mayor ($M$), and $N \geq 3$ of city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor is head of the local Executive, and has the prerogative of proposing a vector of policies, that is voted by the city councilors.
-The policy proposal, if accepted, is implemented.
+Consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
+The mayor is the head of the local executive branch, and has the prerogative of proposing a vector of policies, that is voted by the city councilors.
+Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors $\mathbb{x}$.
 
-Every city councilor has a party affiliation, and the party label may or may not match the mayor's affiliation.
-If the politician shares the same party as the mayor, we say that it belongs to the government coalition ($G \subset \{1, 2, \cdots, N \}$).
-Otherwise, we assume that the politician belongs to the opposition $O \not\subset G$.
-The party affiliation is important because it provides a political benefit or cost for the councilor.
-If the mayor implements the policy, then a councilor aligned with the mayor receives a policy benefit $p > 0$.
-If the politician belongs to the opposition, then the mayoral policies impose her a cost of $-p$.
-For simplicity, we assume that these costs are symmetric.
+The city council votes the mayor's proposal and if they accept it, it is implemented.
+Otherwise, a reversal policy takes place, where the decision leaves the mayor's hands and either immediately stops or transfers to the council.
+The types of reversal policies are crucial for our argument, as it changes the relative strength of the councilors in their bargaining with the mayor.
+We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan concerns; a \textit{partisan} reversal mechanism, where the council is divided in support and opposition for the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan concerns with non-partisan rent extraction.
+In the main paper, we report only the hybrid model, as it is the more realistic scenario.
+Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that partisan a mechanism with only politics (city councilors have parties, that generates political benefits and costs), and an intermediate mechanism (a more realist mechanism, including both extremes).
 
-However, if the mayor's policy proposal lose majoritarian support from the council, then we assume that a reversal policy takes place, where the resources diminish by a factor of $\delta \in (0,1)$, and a random councilor is recognized to make a proposal.\footnote{In a model similar to [Baron Ferejohn / Cliff XXXX].} The councilor proposes the new policy vector, and the council votes.
-If the policy is rejected, then another councilor is recognized to make the offer, and this goes on until one offer is finally accepted by the majority of the legislators.
-For simplicity, we assume that the councilor's offers generate no political benefits or costs, so that if a councilor proposes the policy vector, then $p=0$.
-This may sound restrictive, but we will show that councilors propose zero public goods in equilibrium, as they have only to please their particularistic constituencies to get reelected.
+To govern, the mayor has to convince at least half of the city councilors to support her policy proposals, and she has to use the policy instruments at her disposal.
+These instruments will vary depending on the mechanism that we will investigate, but they are two in nature: targeted goods for the city councilor's constituency and private goods for the city councilor.
+The targeted goods improve the councilor's reelection chances while the private goods can be understood as corruption, aimed at ``buying off'' the support of a recipient councilor.
+The use of the policy instruments, will generate a cost of govern, $C_G$, that will vary with the policy choices and the legislature size.
 
-To convince the councilors, the politician making the proposal has three vectors of policies at her disposal.
-First, the proposer may give targeted goods for the councilor $i$ that she is trying to earn support, $t_i \geq 0$.
-These targeted goods improve the reelection rates of the councilor.
-Second, the proposer may also give private goods $x_i \geq 0$ to a councilor $i$.
-Private goods do not affect the reelection rates of the politicians, but provide instant benefits for the receiver.
-Finally, the proposer can provide public goods $g \geq 0$.
-Public goods help the mayor to get reelected, and also affect the policy benefits received by the politicians, depending on the party affiliation.
-
-For the mayor, the expected utility function is a sum of the utility from rents and benefits from reelection.
-Both the utilities from rents ($u(r)$) and the probability of getting reelected $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
-The probability of getting reelected is also multiplied by the benefit from holding office $B_M > 0$.
-This term captures the tangible and intangible gains that the mayor perceives from being reelected into the position.
+Finally, the mayor has to propose a level of public goods provision ($g$) and rents ($r$).
+Public goods provision help the mayor to get reelected.
+Rents are for direct mayor's consumption, and does not contribute to the mayor's electoral success.
+This makes the mayor's expected utility a sum of the utility from rents and benefits from reelection.
+Both the utilities from rents ($u(r)$) and the probability of reelection $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
+The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
+This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
 The utility is multiplied by an indicator $\mathbb{I}$ that captures whether the mayor's proposal was accepted by the city council.\footnote{The indicator function is defined as
@@
 \[
-\mathbb{E}U(r, g, \bf{x}, \bf{t}) \ = \ \mathbb{I}(\text{Approval})(u(r) + B_M\pi(g))
+\mathbb{E}U(r, g) \ = \ \mathbb{I}(\text{Approval})(u(r) + B_M\pi(g))
 \]
 
-And the mayor chooses the optimal policy subject to a budget constraint.
-The municipality has $R$ resources, and we assume that the municipality cannot run debts.
-This budget balance constraint requires the policy vector $(r, g, \bf{x}, \bf{t})$ to satisfy the following rule:
+The policy choices of the mayor are subject to the municipal budget constraint.
+The municipality has $R$ resources, and we assume the municipality cannot run debts.
+Let $C_G$ the costs of govern.
+The budget balance constraint requires the offers that the mayor makes to the city councilors to satisfy the following rule:
 
 \[
-r + g + \sum_{i=1}^{N}t_i + \sum_{i=1}^{N} x_i \ \leq \ \delta^kR
+r + g + C_G \ \leq \ R
 \]
 
-And the mayor's proposal happens when $k=0$.
-This makes mayoral budget inequality to satisfy: $r + g + \sum_{i=1}^{N}t_i + \sum_{i=1}^{N} x_i \ \leq \ R$.
-Otherwise, in the reversal proposals, the resources diminish by a $\delta^k$ rate, with $k$ being the number of unsuccessful offers by the councilors.
+The expected utility for the city councilors depend on the mechanism that will determine the reversal policy.
+We explore three different mechanisms.
+First, in the *non-partisan legislature* mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
+Resources diminish by a factor of $\delta \in (0,1)$, and the selected councilor will have to make a proposal.
+If her proposal is accepted, it is implemented.
+If it is rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to make the proposal.
+The process than repeats, until one proposal is finally accepted.
 
-We can decompose the councilor's utility function into three major components.
-First, the political gains or losses (depending on the councilor's party affiliation); second, the rents $x_i$ offered by the policy proposer to the councilor; and finally, the transfers for the constituents $t_i$, offered by the policy proposer to the councilor.
-As the constituent transfer $t_i$ affects chance of winning the election $\pi_C(t_i)$, we multiply this chance by the benefits accrued from remaining in office, $B > 0$.
-Again, as in the mayor's case, the utility is only realized when the city council accepts the policy proposed, so that we multiply the approval indicator $\mathbb{I}(.)$.
-The councilor's expected utility is equal to:
+In the second reversal mode, the *partisan legislature* mechanism, we assume that each councilor has a party affiliation.
+Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once).
+If a city councilor belongs to a party aligned with the mayor, we say that she belongs to the government coalition ($G \subset \{1, 2, \cdots, N \}$).
+Otherwise, the city councilor belongs to the opposition $O \not\subset G$.
+The party affiliation play an essential role in the *partisan legislature* mechanism: if a city councilor that belongs to the mayor's coalition rejects the mayor's proposal, she loses the election.
+Whereas, if the city councilor belongs to the opposition, she loses the election by supporting mayor's proposal.
+Although these assumptions are strong, they capture the main underlying political dynamics.
+Partisanship means in most political interactions that if a city councilor aligns with the mayor, her electorate has preferences toward policies that the mayor would implement.
+Voting against the mayor's proposals would represent to defy the partisan brand.
 
-\[
-\mathbb{E}U(r, g, \bf{x}, \bf{t}) \ = \  \mathbb{I}(\text{Approval})((-1)^{\mathbb{I}(i \in O)}p + x_i + B\pi_C(t_i))
-\]
-
-For simplicity, we assume that the councilor's probability of reelection satisfy a simple cutoff rule:
-
-\[
-\pi_C(t_i) \ = \ \twopdo{1}{t_i \geq \underline{t}}{0}
-\]
-
-This assumption simplifies the calculations, and it is reasonable as many models have the voter's decision as a cutoff strategy [@XXXX].
-We also assume, for convenience, that $B > \underline{t}$.
-Otherwise, the councilor would prefer to pocket the targeted goods, and not being reelected.
+In the last reversal mode, which is the reversal mechanism we use in the paper, we combine both partisanship with legislature bargaining rents.
+Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the *non-partisan legislature* mechanism takes place.
+In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented.
+Opposition members, on the other hand, receive $-p$ when the mayor's proposal is implemented.
+If the mayor's proposal is rejected, as city councilors do not control the Executive, no public goods are provided ($p=0$).
+Moreover, in equilibrium, we assume that city councilors would prefer to receive rents instead of providing public goods.
 
@@
   \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
-  \item The mayor proposes a policy vector $(r, g, \bf{x}, \bf{t})_M$.
+  \item The mayor proposes a policy vector $(r, g, \bf{x})_M$.
   \item The city council votes the proposal.
   \begin{itemize}
-    \item If the council accepts, then the policy is implemented, and the game ends. 
+    \item If the council accepts, the policy is implemented and the game ends. 
     \item Otherwise, the reversal policy is implemented.
   \end{itemize}
-  \item (Reversal Policy) At the beginning of each iteration of the reversal policy, one councilor is randomly recognized to be the proposer.
-She proposes a vector $(\bf{x}, \bf{t})$, with $r =  g = 0$.
-If the proposal is accepted, it is implemented.
-If the proposal is rejected, a new round of reversal start, but with the municipal resources reduced by a factor $\delta$.
+  \item (Reversal Policy) Depends on which mechanism, we will have three different reversal policies. We will detail them below.
 \end{enumerate}
 
-This is a bargaining game, along the lines of @rubinsteinXXXX. For political science models similar to this model, see @baronfereXXXX and @cliffsXXXX.
+This is a bargaining game, along the lines of @rubinstein1982perfect. For a political science model similar to this model, see @baron1989bargaining.
 
-The solution for this game consists in finding a Stationary Sub-game Perfect Nash Equilibrium using backward induction.
-Although the game tree may extend infinitely, a Stationary Sub-game Perfect Equilibrium assumes that if a politician accepts an offer at time $t+1$, she should accept the offer at time $t$.
+The solution for this game consists in finding a Sub-game Perfect Nash Equilibrium using backward induction.
+In the model with infinitely repeated proposals, we extend the equilibrium concept to require that the equilibrium is Stationary.
+A Stationary Sub-game Perfect Equilibrium is based on the assumption that if a politician accepts an offer at time $t+1$, she should accept the same offer at time $t$.
 This gives us an objective of finding the offer that will be accepted at any point in the game.
-Moreover, applying this reasoning we can find the optimal offer at $t=0$, which represents no delay in policy implementation.
-The mayor calibrates the offer for approval offering the benefits that councilors would receive, should they reject the offer and enter the reversal stage.
+Applying this reasoning, we can find the optimal offer at $t=0$, which represents no delay in policy implementation.
 
 \begin{definition}
-The solution for the game consists in a pair of strategic policy vectors for the mayor, and the city councilors. The mayor's policy vector is comprised of a public goods provision $g^*$ and XXXX
+The solution for the game consists in a pair of strategic policy vectors that for the mayor, and the city councilors, indexed by the round of the implementation.
+The mayor's policy vector is comprised of a public goods provision $g^*$, rents $r^*$, $\mathbb{t}$ XXXX
 \end{definition}
 
-Using backward induction, suppose that there were $k$ prior rejections, and the municipal resources shrank by $\delta^{k}R$.
-At this stage, the politicians are similar with regard to political affiliation, so that we drop the party label.
-A given councilor is recognized as the proposer with $1/N$ probability.
-The recognized councilor has to convince at least one-half of the council members to agree with her policy proposal.
-Therefore, a legislator $i$, that receives an offer from a proposer ($x_i, t_i$), at round $k$, will accept the offer if it is at least as good as waiting for the next round.
+### The Mayor's Stage
 
-\[
-x_i + B\pi_C(t_i) \ \geq \ \dfrac{1}{N}\left[\delta^{k+1}R - \dfrac{N}{2}(x_{-i} + t_{-i}) + B\pi_C(t_i)\right] + \dfrac{1}{2}(x_i + B\pi_C(t_i))
-\]
+Assume that we have worked out the solution using backward induction, and when there are $N$ councilors, we find that the cost of govern for the mayor is $C_G(N)$.
+This assumption will be dropped when we work each of the cases below.
 
-At the $k$-th stage, the players are equivalent.
-Therefore, the offer $x_i, t_i$, and the offer for the other players, ($x_{-i} + t_{-i}$), are the same.
-Moreover, as $B > \underline{t}$, $t^* = t_i = t_{-i} = \underline{t}$, and the offer that would make legislator $i$ accept without further delay is:
-
-\[
-x + B \ \geq \ \dfrac{1}{N}\left(\delta^{k+1}R - \dfrac{N}{2}(x + \underline{t}) + B\right) + \dfrac{1}{2}(x + B)
-\]
-
-And after some algebra, the optimal private goods offer has to satisfy:
-
-\[
-x \geq \dfrac{1}{N}\left( \delta^{k+1}R + B \right) - \dfrac{1}{2}(B + \underline{t}) \equiv \underline{x}(k)
-\]
-
-For all $k \in \{1, 2, \cdots, \infty\}$.
-
-\begin{lemma}
-Suppose that the council rejected the mayor's offer.
-Then, at the $k$-th stage of the game, the proposer will offer $t^* = \underline{t}$ and $x^* = \underline{x}(k)$ for half of the members, keeping for her $t_i = \max\{0, \underline{t}\}$, and
-
-\[
-x_i \ = \ R\delta^k\left( 1 - \dfrac{\delta}{2} \right) + \dfrac{N}{4}(B-\underline{t}) + \dfrac{B}{2}
-\]
-
-Subject to the budget constraint:
-
-\[
-\dfrac{N}{2}\left(\underline{t}+\underline{x}(k)\right) + x_i  \ \leq \ \delta^kR
-\]
-
-The sequence of strategies derived here are an equilibrium for all $k \in \{1, 2, \cdots, \infty\}$.
-
-\end{lemma}
-
-\begin{proof}
-The proof is direct, after collecting the terms from the previous discussion.
-
-Note that after some iterations, the budget may shrink enough so that $t^* = \underline{t}$ is unfeasible.
-This means that there exists a $k^*$ such that, when $k > k^*$, $t^* = 0$, and the councilors divide the remaining budget as rents.
-This case is trivial to solve, making $\underline{x}(k) = \dfrac{1}{N}\left(\delta^{k+1}R\right)$ and $x_i = \delta^kR\left(1 - \dfrac{\delta}{2}\right)$.
-\end{proof}
-
-We now have the entire strategy profile for the city councilors, provided that they reject the initial mayor's proposal.
-Proceeding by backward induction, we solve for the mayor's proposal that wins the support of the majority of the council.
-In the mayor's proposal policy concerns come into play and the offer for a government-aligned councilor is different than the offer for an opposition councilor.
-For a government aligned councilor, assuming the councilor is the pivotal for the implementation, the accepted offer $(x_m^g, t_m^g)$ has to be better than rejecting the proposal, and waiting for the next round:
-
-\[
-p + x_m^g + B\pi_C(t_m^g) \ \geq \ \dfrac{1}{N}\left( \delta R -\dfrac{N}{2}(\underline{x}(1) + \underline{t}) + B\pi_C(t_i))  \right) + \left(1 - \dfrac{1}{N}\right)\left(\dfrac{1}{2}\right)(\underline{x}(1) + B\pi_C(t_i))
-\]
-
-Note that $\underline{x}(1)$ is the offer of private goods if the councilor rejects the mayors offer, so that $k = 1$.
-As the benefit of retention $B$ is higher than the cost of providing the targeted goods $\underline{t}$, the optimal provision of targeted goods satisfy the threshold for reelection: $t^* = t_m^g = t_i = \underline{t}$.
-Rewriting the equations leads us to:
-
-\[
-p + x_m^g + B \ \geq \ \dfrac{1}{N}\left( \delta R -\dfrac{N}{2}(\underline{x}(1) + \underline{t}) + B)  \right) + \left(1 - \dfrac{1}{N}\right)\left(\dfrac{1}{2}\right)(\underline{x}(1) + B)
-\]
-
-And after some algebra:
-
-\[
-x_m^g \ \geq \ -p +\dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \ \equiv \ \underline{x}_m^g
-\]
-
-For the opposition councilor, the offer has to compensate the political loss of having a mayor that is not aligned with the councilor's ideology. The optimal offer satisfy:
-
-\[
--p + x_o^g + B \ \geq \ \dfrac{1}{N}\left( \delta R -\dfrac{N}{2}(\underline{x}(1) + \underline{t}) + B)  \right) + \left(1 - \dfrac{1}{N}\right)\left(\dfrac{1}{2}\right)(\underline{x}(1) + B)
-\]
-
-And after some algebra:
-
-\[
-x_o^g \ \geq \ p + \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \ \equiv \ \underline{x}_o^g
-\]
-
-\begin{lemma}
-The offer for a government-aligned councilor is always lower than the offer for an opposition councilor.
-\end{lemma}
-
-\begin{proof}
-Note that the $\underline{x}_m^g = 2p + \underline{x}_o^g$.
-As the political disagreement is higher than zero, $\underline{x}_m^g = - 2p + \underline{x}_m^o < \underline{x}_m^g$.
-Moreover, note that $\underline{x}_m^g - \underline{x}_m^o = -2p$.
-\end{proof}
-
-This characterizes the offer that the mayor will make to win the support of the council.
-The next Definition helps to decompose the politician's offer into two components: rents and policy compensation.
-
-\begin{definition}
-Define the rents offered from the bargaining process as
-
-\[
-b(N) \ = \ \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right]
-\]
-
-When the legislature size is $N$, the optimal offers for an opposition member is:
-
-\[
-\underline{x}_m^o(N) = b(N) + p
-\]
-
-And the optimal offer for a government member is:
-
-\[
-\underline{x}_m^g(N) = b(N) - p
-\]
-
-\end{definition}
-
-Now, let the number of government politicians be equal to $\eta_g$, and the ex-ante probability of electing a councilor aligned with the government equal to $\gamma \in (0,1)$.
-We define the cost to govern $C_G(N)$ as three parts equation: first, the costs of making the electoral transfers for at least half of the councilors; second, the rents paid in bargaining; and last, the political costs, that depend on the amount of politicians that are affiliated with the mayor's party.
-After simplifications, the equation describing the costs of govern is as follows:
-
-\[
-C_G(N) = \dfrac{N}{2}(\underline{t} + b(N) + p) - 2p\sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g
-\]
-
-And the probability that $\eta_g$ councilors belong to the mayor's coalition is equal to $\mathbb{P}(\eta_g) = \binom{N}{\eta_g}\gamma^{\eta_g}(1-\gamma)^{N-\eta_g}$, which is the binomial probability given that the ex-ante chance to elect an aligned councilor is equal to $\gamma$.
-
-We need now to derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
+We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
 The mayor benefits from public goods provision, as it increases the chances of her reelection.
 However, she prefers to contribute as minimum as possible for the public goods, and extract the remaining resources as political rents.
-Therefore, her objective is to maximize the expected utility subject to the budget constraint.
+Her objective is to maximize the following expected utility, subject to the municipal budget constraint.
 
@@
 However, as $N$ increases discretely, we cannot take a derivative on $N$ and use the implicit function theorem.
-We use Monotone Comparative Statics [@milgromshannonXXXX] to derive these results.
+Instead, we use monotone comparative statics [@milgrom1994monotone] to derive these results.
 
@@
 
-Therefore, to satisfy increasing differences in XXXX,
-
+Therefore, to satisfy increasing differences in the public goods provision and in the legislature size, the costs of govern has to decrease with legislature size.
 \end{proof}
 
-This gives us our first empirical hypothesis to test: if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase.
-But we still need to investigate further how the costs of govern would decrease with legislature size.
-On the one hand, it seems evident that with the additional legislator, comes also an additional rent and a possible veto player.
-In the next Lemma we show that the rents always decrease when we increase the number of legislators.
+This provides us our first empirical hypothesis to test: *if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase*.
 
-\begin{lemma}\label{lemmabarg}
-The amount of rents required to win support from a given legislator decreases when the number of legislators increase.
-\end{lemma}
+At this stage, we need to solve for the costs of govern to determine whether this hypothesis is true or not.
+Below we show that it is true for the *partisan* and *hybrid* mechanisms, but it is not true for the *non-partisan* mechanism.
 
-\begin{proof}
+### Non-Partisan Legislature
 
-The proof consists in showing that when we increase the size of the legislature from $N$ to $N+1$, the amount of rents decrease.
+In the *non-partisan legislature* mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
+Suppose that there were $k$ rejections, and we are at the $k+1$-th stage in the game.
+A given councilor will accept the proposer's offer if, and only if, accept the offer is better than wait until the next stage.
+If the offer is $x_i$, then:
 
 \[
-\begin{aligned}
-b(N+1) - b(N) \ = \ & \dfrac{1}{2(N+1)+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-(N+1)(\underline{t} + B) + B\right] \\
-& - \dfrac{1}{2N+1}\left[2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
-= \ & \dfrac{1}{2N+1}\left[\left(1-\dfrac{2}{2N+3}\right)\left(2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-N(\underline{t} + B) + \underline{t}\right) \right. \\
-& - \left. 2\delta R \left(1 + \dfrac{1-\delta}{2N}\right)-N(\underline{t} + B) + B\right] \\
-= \ & -\dfrac{1}{2N+1}\left[\dfrac{2}{2N+3}\left(2\delta R \left(1 + \dfrac{1-\delta}{2(N+1)}\right)-N(\underline{t} + B) + \underline{t}\right) \right. \\
-& + \left. \dfrac{2 R \delta (1-\delta)}{2N} + \underline{t} + B\right] \equiv \Delta b(N) \\
-< \ &0
-\end{aligned}
+x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left( \dfrac{1}{2} \right)\left[ x_i \right]
 \]
 
-Therefore, larger legislature sizes decrease the costs of bargaining.
-This because of two effects: first, the chance of being the proposer decreases; second, the chance of being selected to receive an offer also decreases.
+In the left-hand side, we place the offer.
+In the right-hand side, there are two components.
+The first is the amount the councilor $i$ gets when she is the proposer.
+It is equal to the budget in the next round minus the offers that she has to make to convince half of the councilors.
+The second part is the gains if she happens to reject but still receive an offer in the following round.
+Note that the offer she makes when she is the proposer is the same as the offer she wants to receive.
+This because the city councilors are exchangeable, and the solution is symmetric for all councilors receiving an offer (this means that we could have dropped the $i$ in the solution).
+After some algebra, the offer $x_i$ has to be greater than or equal to:
 
-\end{proof}
+\[
+x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k)
+\]
 
-However, the decrease in rents is not sufficient to have lower costs to govern when we increase the number of legislators.
-The political costs, if high enough, can offset the gains with lower rents.
-Higher political costs result from having more members of the opposition in the legislature.
-The next proposition shows the sufficient condition for having a lower cost of govern when we increase the number of legislators.
+The proposer always offer the minimum possible to get the proposal approved. In the case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k)$.
 
-\begin{proposition}\label{mainprop}
+Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
+In this context, the cost of govern is equal to:
 
-There exists an ex-ante probability of electing a councilor aligned with the government $\overline{\gamma}$ such that, for all $\gamma > \overline{\gamma}$, the cost of govern decreases as $N$ increases, i.e., $C_G(N+1) \leq C_G(N)$.
+\[
+C_G(N) \ = \ \dfrac{N}{2N + 1}(\delta R)
+\]
 
+\begin{proposition}
+In the *non-partisan legislature* mechanism, the costs of govern increase as $N$ increases.
 \end{proposition}
@@
 
-Let us rewrite the results as:
+The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
 
 \[
-XXXX \geq 0
+\begin{aligned}
+C_G(N+1) - C_G(N) \ = \ & \dfrac{N+1}{2(N+1) + 1}(\delta R) - \dfrac{N}{2N + 1}(\delta R) \\
+ = \ & \dfrac{\delta R}{(2N+3)(2N+1)}  \\
+> \ &0
+\end{aligned}
 \]
 
-Rearranging the terms:
-
-\[
-- \underline{t} - \underline{x}_o^g(N+1) - \dfrac{N}{2}(\underline{x}_o^g(N+1) - \underline{x}_o^g(N-1)) -2p \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]
-\]
-
-Let $\Delta\eta_n(\gamma) \equiv \left[\sum_{\eta_g = 0}^{N/2+1}\mathbb{P}(\eta_g)\eta_g - \sum_{\eta_g = 0}^{N/2}\mathbb{P}(\eta_g)\eta_g\right]$.
-There is no closed form solution for this equation.
-We can approximate the boundaries using @wXXXX but graphically, we can have a good sense of the XXXX:
-
-XXXX GRAPH DELTA GAMMA HERE
-
-And solving for $\Delta\eta_n(\gamma)$ we have that:
-
-\[
-XXXX
-\]
-
-The natural boundaries for $\Delta\eta_n(\gamma)$ are minus-one and one.
-Minus-one means that the additional legislature seat went to the opposition while one means that the additional legislature seat went to the government.
-XXXX
+Therefore, the costs always increase in $N$.
 
@@
 
-Taking stocks, the model provides two testable hypothesis. Let a legislature that previously had $N$ legislators, and now increased the legislature by $N+1$. Then:
+\begin{corollary}
+In the *non-partisan legislature*, public goods provision decreases as the legislature size increases.
+\end{corollary}
+
+This result is crucial to understand the role of the politics in our model.
+If the costs of govern increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
+In our case, we show that there is a *political* reason for increasing the public goods provision.
+
+### Partisan Legislature
+
+We now look into the other extreme, which is a fully politicized legislature.
+In this case, when the mayor implements the policy, it generates a value of $p$.
+A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a value of $-p$.
+Moreover, as in the case of the non-partisan legislature, the mayor can also distribute $x_i$ private goods for the legislator $i$.
+In this case, when the policy is implemented, utility of an aligned legislator is equals to $x_i + p$.
+When the legislator is not aligned with the mayor, her utility is equals to $x_i - p$.
+If the policy is not implemented, then we assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
+
+A legislator aligned with the mayor will always support the mayor's policy, regardless of any private goods.
+This because as $p > 0$, the councilor always receive positive benefits from the policy.
+However, a politician not aligned with the mayor will require a compensation if her vote is needed.
+In this case, if the mayor needs the support of an opposition politician to pass her policy proposal, then she will need to compensate her for the policy costs.
+In this case:
+
+\[
+x_i \geq p
+\]
+
+Optimality dictates that the mayor will offer $x_i = p$ to an opposition legislator.
+Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
+Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor will have to compensate:
+
+\[
+C_G(N) \ = \ p\left(\dfrac{N}{2} - \gamma N\right)
+\]
+
+\begin{proposition}
+In the *partisan legislature* mechanism, if the chance of electing a mayor-aligned politician is greater than one-half, then the costs of govern decrease as $N$ increases.
+\end{proposition}
+
+\begin{proof}
+
+The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
+
+\[
+\begin{aligned}
+C_G(N+1) - C_G(N) \ = \ & p\left(\dfrac{N+1}{2} - \gamma (N+1)\right) - p\left(\dfrac{N}{2} - \gamma N\right) \\
+ = \ & p\left( \dfrac{1}{2} - \gamma  \right)
+\end{aligned}
+\]
+
+Therefore, when $\gamma < \dfrac{1}{2}$, the costs of govern increase. Otherwise, the costs decrease.
+
+\end{proof}
+
+\begin{corollary}
+In the *partisan legislature*, if the chance of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as the legislature size increases.
+\end{corollary}
+
+This result shows that when the chances of electing an aligned politician is sufficiently high, then the costs of govern decrease.
+As a response, the public goods provision (and also rents), increase.
+The rate distribution between these two vectors will be determined by the marginal change in the utility from rents and the utility from reelection.
+In any case, the amount allocated for both increase.
+
+### Hybrid Partisan and Non-partisan Legislatures
+
+The hybrid mechanism combines both partisan and non-partisan motivations. In the hybrid mechanism, a city councilor aligned with the government favors the mayor's offer if:
+
+\[
+x_i \geq \dfrac{2\delta R}{2N+1} - p
+\]
+
+An opposition politician, on the other hand, favors the mayor's offer when:
+
+\[
+x_i \geq \dfrac{2\delta R}{2N+1} + p
+\]
+
+Inspecting these equations we can decompose these costs into costs in terms of rents and costs (or benefits) from political alignment.
+In this context, the cost of govern will be a weighted average between the expected payments for councilors that belong to the mayor's coalition, versus the expected payments for the councilors that belongs to the opposition.
+The chance of a opposition member be elected is equal to $\gamma$, and taking the weighted averages, the costs become:
+
+\[
+C_G(N) \ = \ \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) + \left(\dfrac{N}{2} - \gamma N \right)p
+\]
+
+\begin{proposition}
+In the *hybrid legislature*, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then the costs of govern increase as the legislature size increases.
+Otherwise, the costs decrease when the legislature size increases.
+\end{proposition}
+
+\begin{proof}
+
+The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
+
+\[
+\begin{aligned}
+C_G(N+1) - C_G(N) \ = \ & \dfrac{N+1}{2}\left( \dfrac{2\delta R}{2(N+1)+1} - p \right) + \left(\dfrac{N+1}{2} - \gamma (N+1) \right)p \\
+& - \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) - \left(\dfrac{N}{2} - \gamma N \right)p \\
+ = \ & \dfrac{\delta R}{(2N+3)(2N+1)}\left[ 1-\gamma (2N+1)(2N+3)p \right]
+\end{aligned}
+\]
+
+The conditions for the differences in governing costs be decrease when the  legislature size increases is:
+
+\[
+\gamma \geq \dfrac{1}{p}\left[\dfrac{1}{(2N+3)(2N+1)}\right] \equiv \underline{\gamma}
+\]
+
+\end{proof}
+
+\begin{corollary}
+In the *hybrid legislature* mechanism, public goods provision decreases as the legislature size increases.
+\end{corollary}
+
+Also, note that the threshold $\gamma$ for the probability of electing a politician aligned with the government is decreasing in both the political outcome $p$ and the size of the legislature $N$.
+This means that more political benefits from policy and larger legislatures makes it easier to satisfy the electoral constraint.
+
+### Main Hypotheses
+
+Taking stocks, the models provide two empirically testable hypotheses. Consider a legislature that previously had $N$ legislators, but now needs to increase its legislature by $N+1$. Then:
 

### 2021-08-16 appendix/appendix.Rmd
appendix first quarter

@@
 author:
-  - Umberto Mignozzetti[^umberto]
   - Gabriel Cepaluni[^gabriel]
   - Danilo Freire[^danilo]
+  - Umberto Mignozzetti[^umberto]
 date: \today
@@
 The mayor is the head of the local executive branch, and has the prerogative of proposing a vector of policies, that is voted by the city councilors.
-Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors $\mathbb{x}$.
+Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.
 
@@
 The types of reversal policies are crucial for our argument, as it changes the relative strength of the councilors in their bargaining with the mayor.
-We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan concerns; a \textit{partisan} reversal mechanism, where the council is divided in support and opposition for the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan concerns with non-partisan rent extraction.
+We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan concerns; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan concerns with non-partisan rent extraction.
 In the main paper, we report only the hybrid model, as it is the more realistic scenario.
-Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that partisan a mechanism with only politics (city councilors have parties, that generates political benefits and costs), and an intermediate mechanism (a more realist mechanism, including both extremes).
+Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that the partisan a mechanism is what drives our results.
 
-To govern, the mayor has to convince at least half of the city councilors to support her policy proposals, and she has to use the policy instruments at her disposal.
-These instruments will vary depending on the mechanism that we will investigate, but they are two in nature: targeted goods for the city councilor's constituency and private goods for the city councilor.
-The targeted goods improve the councilor's reelection chances while the private goods can be understood as corruption, aimed at ``buying off'' the support of a recipient councilor.
-The use of the policy instruments, will generate a cost of govern, $C_G$, that will vary with the policy choices and the legislature size.
+To govern, the mayor has to convince at least half of the city councilors to support her policy proposals.
+Similar to selectorate models \citep{buenodemesquita2005logic}, we assume that the selectorate, i.e.
+the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
+The winning coalition, which is the minimum number of members that have to be convinced to implement the policy, is equal to half of the selectorate $N/2$.
+City councilors are moved by policy concerns $p$ and transfers received from the mayor \textbf{x}.
+The use of transfers to affect the councilors' choices generate a cost of govern, $C_G$, that vary with the reversal mechanism and the legislature size.
 
-Finally, the mayor has to propose a level of public goods provision ($g$) and rents ($r$).
+Finally, after paying the costs of govern, the mayor proposes a level of public goods provision ($g$) and rents ($r$).
 Public goods provision help the mayor to get reelected.
 Rents are for direct mayor's consumption, and does not contribute to the mayor's electoral success.
-This makes the mayor's expected utility a sum of the utility from rents and benefits from reelection.
+This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
 Both the utilities from rents ($u(r)$) and the probability of reelection $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
 The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
-The utility is multiplied by an indicator $\mathbb{I}$ that captures whether the mayor's proposal was accepted by the city council.\footnote{The indicator function is defined as
-\[
-I(condition) \ = \ \twopdo{1}{\text{Condition is satisfied.}}{0}.
-\]
-} The expected utility for the mayor is:
+This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office, and we assume that they are high enough to rule out an equilibrium with only rents and transfers.
+If the mayor's policy proposal is approved, then the expected utility for the mayor is:
 
 \[
-\mathbb{E}U(r, g) \ = \ \mathbb{I}(\text{Approval})(u(r) + B_M\pi(g))
+\mathbb{E}U(r, g) \ = \ u(r) + B_M\pi(g)
 \]
@@
 The policy choices of the mayor are subject to the municipal budget constraint.
-The municipality has $R$ resources, and we assume the municipality cannot run debts.
-Let $C_G$ the costs of govern.
-The budget balance constraint requires the offers that the mayor makes to the city councilors to satisfy the following rule:
+The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget has to be balanced.
+We also assume that there are enough resources for the mayor to govern.
+
+Let $C_G$ the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:
 
@@
 The expected utility for the city councilors depend on the mechanism that will determine the reversal policy.
-We explore three different mechanisms.
-First, in the *non-partisan legislature* mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
-Resources diminish by a factor of $\delta \in (0,1)$, and the selected councilor will have to make a proposal.
+As discussed, we explore three different mechanisms.
+First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
+The randomly selected councilor becomes now the proposer.
 If her proposal is accepted, it is implemented.
 If it is rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to make the proposal.
-The process than repeats, until one proposal is finally accepted.
+The process repeats, until one proposal is finally accepted.
 
-In the second reversal mode, the *partisan legislature* mechanism, we assume that each councilor has a party affiliation.
+In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation.
 Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once).
-If a city councilor belongs to a party aligned with the mayor, we say that she belongs to the government coalition ($G \subset \{1, 2, \cdots, N \}$).
+If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition ($G \subset \{1, 2, \cdots, N \}$).
 Otherwise, the city councilor belongs to the opposition $O \not\subset G$.
-The party affiliation play an essential role in the *partisan legislature* mechanism: if a city councilor that belongs to the mayor's coalition rejects the mayor's proposal, she loses the election.
-Whereas, if the city councilor belongs to the opposition, she loses the election by supporting mayor's proposal.
-Although these assumptions are strong, they capture the main underlying political dynamics.
-Partisanship means in most political interactions that if a city councilor aligns with the mayor, her electorate has preferences toward policies that the mayor would implement.
+The mayor's policy generate a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends of the party affiliation of the councilor.
+If the mayor's proposal is rejected, a city councilor aligned with the mayor, that would receive $p$ from the policy, now receives zero.
+On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy, and now receives zero.
+Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in terms of public goods provision are shared by councilors aligned with the mayor.
 Voting against the mayor's proposals would represent to defy the partisan brand.
 
-In the last reversal mode, which is the reversal mechanism we use in the paper, we combine both partisanship with legislature bargaining rents.
-Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the *non-partisan legislature* mechanism takes place.
+In the last reversal mechanism, the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining rents.
+Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan reversal mechanism takes place.
 In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented.
 Opposition members, on the other hand, receive $-p$ when the mayor's proposal is implemented.
-If the mayor's proposal is rejected, as city councilors do not control the Executive, no public goods are provided ($p=0$).
+If the mayor's proposal is rejected, as city councilors do not control the Executive when the two branches are separated, no public goods are provided ($p=0$).
 Moreover, in equilibrium, we assume that city councilors would prefer to receive rents instead of providing public goods.
+This aligns with the empirical evidence in most developing economies.
 
@@
   \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
-  \item The mayor proposes a policy vector $(r, g, \bf{x})_M$.
+  \item The mayor proposes a policy vector $(r, g, x)_M$.
   \item The city council votes the proposal.
@@
 
-This is a bargaining game, along the lines of @rubinstein1982perfect. For a political science model similar to this model, see @baron1989bargaining.
+This is a bargaining game, along the lines of \citet{rubinstein1982perfect}.
+For a political science models similar to this model, see \citet{baron1989bargaining} and, to some extent, \citet{buenodemesquita2005logic}.
 
-The solution for this game consists in finding a Sub-game Perfect Nash Equilibrium using backward induction.
+The solution concept we use in this model is the Sub-game Perfect Nash Equilibrium.
+A Sub-game Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game.
+The solution is found using backward induction.
 In the model with infinitely repeated proposals, we extend the equilibrium concept to require that the equilibrium is Stationary.
-A Stationary Sub-game Perfect Equilibrium is based on the assumption that if a politician accepts an offer at time $t+1$, she should accept the same offer at time $t$.
+A Stationary Sub-game Perfect Equilibrium is based on the assumption that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should accept the same offer at time $k$.
 This gives us an objective of finding the offer that will be accepted at any point in the game.
-Applying this reasoning, we can find the optimal offer at $t=0$, which represents no delay in policy implementation.
+Applying this reasoning, we can find the optimal offer at $k=0$, which represents no delay in policy implementation.
 
 \begin{definition}
-The solution for the game consists in a pair of strategic policy vectors that for the mayor, and the city councilors, indexed by the round of the implementation.
-The mayor's policy vector is comprised of a public goods provision $g^*$, rents $r^*$, $\mathbb{t}$ XXXX
+The solution for the game consists in a pair of strategic policy vectors $(g^*, r^*, x^*)_k$, for $k \in \{0, 1, \cdots, \infty\}$, such that, for the mayor and the councilors, there are no profitable deviations from the equilibrium.
 \end{definition}
 
-### The Mayor's Stage
+Moreover, we assume that the players will play no dominated strategies, even when there is less than sufficient support for implement the policy.
 
-Assume that we have worked out the solution using backward induction, and when there are $N$ councilors, we find that the cost of govern for the mayor is $C_G(N)$.
-This assumption will be dropped when we work each of the cases below.
+### The Mayor's Decision Stage
+
+Solving the game by backward induction would require us to start with the councilor's strategies.
+However, for simplicity, we will assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors.
+As we will show in a few paragraphs, this is without loss of generality as we will drop the assumption.
+We use it to simplify the exposition.
 
@@
 The mayor benefits from public goods provision, as it increases the chances of her reelection.
-However, she prefers to contribute as minimum as possible for the public goods, and extract the remaining resources as political rents.
+However, she prefers to contribute as minimum as necessary for the public goods, and extract the remaining resources as political rents.
 Her objective is to maximize the following expected utility, subject to the municipal budget constraint.
@@
 
-In equilibrium the budget binds, and the optimal public goods provision maximizes:
+In equilibrium the budget binds, and the public goods provision maximizes:
 
@@
 \begin{proposition}
-The provision of public goods increase with legislature size if the costs of govern decreases in larger legislatures.
+The provision of public goods increase with legislature size when the costs of govern decrease with legislature size.
 \end{proposition}
@@
 \begin{proof}
-In order to prove this result, we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$.
+To prove this result we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$.
 This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase.
-However, as $N$ increases discretely, we cannot take a derivative on $N$ and use the implicit function theorem.
-Instead, we use monotone comparative statics [@milgrom1994monotone] to derive these results.
+However, as $N$ increases discretely, we cannot take a the cross-partial derivative on $N$ or even use the implicit function theorem.
+Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
 
-The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1>N$, we have:
+To start, note that $\mathbb{R} \times \mathbb{N}$ is a complete lattice.
+In this case, mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$, we have:
 
@@
 
-And after substituting, we have:
+After substituting, we have:
 
 \[
-u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g')
-\\
-\geq 
-\\
+u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g') \geq 
 u(R - g - C_G(N)) + B_M\pi(g) - u(R - g' - C_G(N)) - B_M\pi(g')
@@
 
-This is true when the cost of govern with a council size of $N+1$ is lower than the cost of govern when the council size has $N$ councilors:
+And the function satisfies the increasing differences in $g$ and $N$ when the costs of govern an $N+1$-sized city council is lower than the costs of govern an $N$-sized city council:
 
@@
 
-Therefore, to satisfy increasing differences in the public goods provision and in the legislature size, the costs of govern has to decrease with legislature size.
 \end{proof}
 
-This provides us our first empirical hypothesis to test: *if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase*.
+This provides us our first empirical hypothesis to test: if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase.
 
@@
 
-### Non-Partisan Legislature
+### Non-Partisan Reversal Mechanism
 
-In the *non-partisan legislature* mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
-Suppose that there were $k$ rejections, and we are at the $k+1$-th stage in the game.
-A given councilor will accept the proposer's offer if, and only if, accept the offer is better than wait until the next stage.
+In the \textit{non-partisan reversal} mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
+To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and we are at the $k$-th stage in the game.
+A councilor will accept the proposer's offer if, and only if, to accept the offer is better than to wait until the next stage.
 If the offer is $x_i$, then:
@@
 In the right-hand side, there are two components.
-The first is the amount the councilor $i$ gets when she is the proposer.
+The first is the amount that the councilor $i$ gets when she is the proposer.
 It is equal to the budget in the next round minus the offers that she has to make to convince half of the councilors.
@@
 Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
-In this context, the cost of govern is equal to:
+In this context, the costs of govern are equal to:
 
@@
 \begin{proposition}
-In the *non-partisan legislature* mechanism, the costs of govern increase as $N$ increases.
+In the \textit{non-partisan reversal} mechanism, the costs of govern increase as the size of the legislature increases.
 \end{proposition}
@@
 
-The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
+The difference in costs when there are $N+1$ city councilors versus when there are $N$ city councilors is equal to:
 
@@
 
-Therefore, the costs always increase in $N$.
+Therefore, the costs always increase when the size of the legislature increases.
 
@@
 \begin{corollary}
-In the *non-partisan legislature*, public goods provision decreases as the legislature size increases.
+In the \textit{non-partisan reversal} mechanism, public goods provision decreases as the legislature size increases.
 \end{corollary}
@@
 If the costs of govern increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-In our case, we show that there is a *political* reason for increasing the public goods provision.
+In our case, we show that there is a \textit{political} reason for increasing the public goods provision.
 
-### Partisan Legislature
+### Partisan Reversal Mechanism
 
 We now look into the other extreme, which is a fully politicized legislature.
-In this case, when the mayor implements the policy, it generates a value of $p$.
-A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a value of $-p$.
-Moreover, as in the case of the non-partisan legislature, the mayor can also distribute $x_i$ private goods for the legislator $i$.
-In this case, when the policy is implemented, utility of an aligned legislator is equals to $x_i + p$.
+In this case, when the mayor implements the policy, it generates a value of $p > 0$.
+A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a cost of $-p$.
+Moreover, as in the case of the non-partisan reversal, the mayor can choose to distribute $x_i$ private goods for a legislator $i$.
+In this case, when the policy is implemented, the utility of an aligned legislator is equals to $x_i + p$.
 When the legislator is not aligned with the mayor, her utility is equals to $x_i - p$.
@@
 
-A legislator aligned with the mayor will always support the mayor's policy, regardless of any private goods.
-This because as $p > 0$, the councilor always receive positive benefits from the policy.
-However, a politician not aligned with the mayor will require a compensation if her vote is needed.
+A legislator aligned with the mayor will always support the mayor's policy, regardless of receiving or not private goods.
+This because as $p > 0$, the councilor always receive positive benefits from the policy.\footnote{In reality, if it was possible, the mayor could even impose a cost to the city councilors aligned with the government.
+Although this seem unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office.} However, a politician not aligned with the mayor will require a compensation if her vote is needed.
 In this case, if the mayor needs the support of an opposition politician to pass her policy proposal, then she will need to compensate her for the policy costs.
@@
 
-Optimality dictates that the mayor will offer $x_i = p$ to an opposition legislator.
+Optimality dictates that the mayor will offer $x_i = p$ to the opposition legislator.
 Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
-Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor will have to compensate:
+Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor will have to compensate minus the amount needed to implement the policy, in this case, half of them:
 
@@
 \begin{proposition}
-In the *partisan legislature* mechanism, if the chance of electing a mayor-aligned politician is greater than one-half, then the costs of govern decrease as $N$ increases.
+In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than one-half, then the costs of govern decrease as the legislature size increases.
 \end{proposition}
@@
 \begin{corollary}
-In the *partisan legislature*, if the chance of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as the legislature size increases.
+In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as the legislature size increases.
 \end{corollary}
@@
 
-### Hybrid Partisan and Non-partisan Legislatures
+### Hybrid Partisan and Non-partisan Reversal Mechanism
 
-The hybrid mechanism combines both partisan and non-partisan motivations. In the hybrid mechanism, a city councilor aligned with the government favors the mayor's offer if:
+The \textit{hybrid reversal} mechanism combines both partisan and non-partisan motivations. In the hybrid mechanism, a city councilor aligned with the government favors the mayor's offer if:
 
@@
 
-An opposition politician, on the other hand, favors the mayor's offer when:
+An opposition politician, on the other hand, favors the mayor's offer if, and only if:
 
@@
 
-Inspecting these equations we can decompose these costs into costs in terms of rents and costs (or benefits) from political alignment.
-In this context, the cost of govern will be a weighted average between the expected payments for councilors that belong to the mayor's coalition, versus the expected payments for the councilors that belongs to the opposition.
-The chance of a opposition member be elected is equal to $\gamma$, and taking the weighted averages, the costs become:
+Inspecting these equations, we can decompose these costs into costs in terms of rents and costs (or benefits) from political alignment.
+In this context, the cost of govern will be depend on the expected payments for councilors in the mayor's coalition, versus the expected payments for the councilors that belongs to the opposition.
+The chance of a opposition member be elected is equal to $\gamma$, and taking the weighted averages, these costs become:
 
@@
 \begin{proposition}
-In the *hybrid legislature*, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then the costs of govern increase as the legislature size increases.
+In the \textit{hybrid reversal} mechanism, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then the costs of govern increase as the legislature size increases.
 Otherwise, the costs decrease when the legislature size increases.
@@
 
-The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
+The difference in costs when there are $N+1$ city councilors versus the costs when there are $N$ councilors is equal to:
 
@@
 \begin{corollary}
-In the *hybrid legislature* mechanism, public goods provision decreases as the legislature size increases.
+In the \textit{hybrid reversal} mechanism, public goods provision decreases as the legislature size increases.
 \end{corollary}
 
-Also, note that the threshold $\gamma$ for the probability of electing a politician aligned with the government is decreasing in both the political outcome $p$ and the size of the legislature $N$.
-This means that more political benefits from policy and larger legislatures makes it easier to satisfy the electoral constraint.
+Also, note that the threshold $\gamma$ for the probability of electing a politician aligned with the government is decreasing in both the political value of the mayors policy $p$ and the size of the legislature $N$.
+This means that higher political values and larger legislatures makes it easier to satisfy the electoral threshold.
 
@@
 
-Taking stocks, the models provide two empirically testable hypotheses. Consider a legislature that previously had $N$ legislators, but now needs to increase its legislature by $N+1$. Then:
+Taking stocks, the models provide two empirically testable hypotheses. Consider a city council comprised of $N$ legislators, that increase the council size to $N+1$. Then:
 
@@
 
+In the paper, we show that the provision of education and healthcare improves in Brazil, and this results from the fact that the chances of electing a city councilor aligned with the mayor is of 91%.
+
 \newpage
+
+## Variable Sources and Descriptive Statistics
+\label{appsources}
+
+We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
+
+\begin{sidewaystable}[!htbp] \centering 
+\caption{Data Sources} 
+\label{varsources}
+\scalebox{0.75}{
+  \begin{tabular}{@{\extracolsep{5pt}}llll} 
+  \\[-1.8ex]\hline\hline \\[-1.8ex] 
+  Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
+  \hline \\[-1.8ex] 
+  & & & \\
+  DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
+  & & & \\
+  IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
+  & & & \\
+  INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
+  & & & \\
+  InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
+  & & & \\
+  IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
+  & & & \\
+  MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
+  & & & \\
+  TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
+  & & & \\
+  \hline\hline \\[-1.8ex] 
+  \end{tabular} 
+}
+\end{sidewaystable}
+
+Now let us define each variable.
+
+### Outcomes Aggregated at the Municipal Level
+
+\begin{itemize}
+\item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
+\item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
+\item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
+\item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
+\item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
+\item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
+\item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
+\item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
+\item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
+\item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
+IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
+The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
+\item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality.
+IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying.
+The estimators are cleaned to avoid the influence of schools and classrooms specific effects.
+(source: INEP, years: 2005, 2007).
+\item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
+\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
+\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality.
+Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
+\item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
+\item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
+\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council.
+We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures).
+\item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
+\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
+\end{itemize}
+
+### Legislation Dataset
+
+We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:
+
+\begin{itemize}
+\item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
+\item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
+\item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
+\item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
+\item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
+\end{itemize}
+
+### Online 2016 Former City Councilors Survey
+
+We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:
+
+\begin{itemize}
+\item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
+\item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
+\item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
+\item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
+\item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
+\item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
+\item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
+\item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
+\item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
+\end{itemize}
+
+In this Appendix, we present other questions we asked in the survey.
+They are meant to improve the knowledge we have about the city councilors perceptions about their representation.
+We have not added these to the main paper because they were more complimentary and not of general interest.
+The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.
+
+XXXX CHANGE HERE TABLE BELOW
+
+\begin{table}[htb!]
+\centering 
+\caption{Summary Statistics} 
+\label{tabdescrvarspaper} 
+\resizebox{0.9\textwidth}{3.5in}{
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{\fill}}l r r r r r } 
+\toprule
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
+\midrule 
+& \multicolumn{5}{c}{\textbf{Municipal Characteristics}} \\ \cline{2-6}
+Number of Seats 2000 & 5,521 & 10.76 & 2.70 & 9 & 21 \\ 
+Population 2000 & 5,474 & 22,341.96 & 44,573.67 & 697 & 567,728 \\ 
+Per-Capita GDP Census 2000 (in thousands) & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
+Proportion of Poverty Census 2000 & 5,474 & 46.58 & 22.82 & 2.89 & 93.02 \\ 
+Number of Seats 2004 & 5,527 & 9.22 & 0.94 & 9 & 21 \\ 
+& \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
+Infant Mortality 2005-2008 & 13,329 & 20.64 & 13.45 & 1.28 & 209.30 \\
+Post-Natal Mortality Rate 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
+Coverage Family Health Program 2005-2008 & 20,577 & 76.97 & 27.39 & 0.00 & 100.00 \\ 
+Prop. Born w. $6+$ Pre-Natal 2005-2008 & 16,578 & 54.02 & 24.30 & 0.57 & 100.00 \\ 
+& \multicolumn{5}{c}{\textbf{Education Outcomes}} \\ \cline{2-6}
+Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\ 
+Enrollment Middle School 2005-2008 & 7,887 & 25.18 & 7.25 & 1.00 & 92.50 \\
+Quality of Elementary School Index 2005-2008 & 9,267 & 3.73 & 0.94 & 0.70 & 8.10 \\
+Quality of Middle School Index 2005-2008 & 5,566 & 3.21 & 0.76 & 0.30 & 6.60 \\
+& \multicolumn{5}{c}{\textbf{Resources and Patronage}} \\ \cline{2-6}
+Mayoral Coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\ 
+Number of Appointed Bureaucrats 2005-2008 & 16,564 & 67.78 & 126.68 & 0 & 2,894 \\ 
+Number of Career Bureaucrats 2005-2008 & 16,558 & 436.13 & 698.17 & 0 & 11,633 \\ 
+Number Councilor Assistants 2005 & 5,523 & 4.63 & 8.55 & 0 & 213 \\ 
+& \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
+Proportion Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0.00 & 8.00 \\ 
+Proportion Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0.00 & 9.00 \\ 
+Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\ 
+Proportion Approved Legislation 2005 & 3,694 & 0.83 & 0.28 & 0.00 & 1.00 \\ 
+& \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
+Legislation -- Local Public Goods & 346,553 & 0.73 & 0.44 & 0 & 1 \\ 
+Legislation -- Public Goods & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
+Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
+Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\ 
+Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\ 
+& \multicolumn{5}{c}{\textbf{Survey -- Electoral Attractiveness of Services}} \\ \cline{2-6}
+Votes -- Help Hospital Admission & 174 & 0.82 & 0.38 & 0 & 1 \\ 
+Votes -- Help School Admission & 174 & 0.59 & 0.49 & 0 & 1 \\ 
+Votes -- Help get Medication & 174 & 0.71 & 0.46 & 0 & 1 \\ 
+Votes -- Fix Street Potholes & 174 & 0.49 & 0.50 & 0 & 1 \\ 
+Votes -- Local Public Goods & 174 & 0.81 & 0.39 & 0 & 1 \\ 
+Votes -- Legislive Duties & 174 & 0.22 & 0.42 & 0 & 1 \\ 
+Votes -- Honors Legislation & 174 & 0.18 & 0.38 & 0 & 1 \\ 
+Votes -- Oversee School Quality & 174 & 0.29 & 0.45 & 0 & 1 \\ 
+Votes -- Oversee Construction & 174 & 0.24 & 0.43 & 0 & 1 \\ 
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\small
+\textbf{Notes:} The legislation approved dataset has data on 64 of the 202 municipalities 10 thousand inhabitants from the council size thresholds.
+The survey summary statistics here are unweighted.
+Numbers of cases vary due to missingness.
+\end{tablenotes} 
+\end{threeparttable}
+}
+\end{table}
+
+\newpage
+
+### Threshold Manipulation, Sorting, and Pre-treatment Consistency
+
+The validity of our causal claim relies on three assumptions.
+First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds.
+Second, that we are consistently comparing municipalities in the same cutoffs.
+Lastly, that we have no pre-treatment differences in our sample.
+
+For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
+For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
+
+We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
+We use local polynomial orders from one to four.
+As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
+Therefore, there is no manipulation according to \citet{calonico2019regression}.
+
+We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
+
+\begin{figure}[htb!]
+  \begin{center}
+  \begin{minipage}{1 \linewidth}
+  \centerline{\includegraphics[width=5in,angle=0]{figs/McCrary.pdf}}
+  \caption{\citet{McCrary2008} manipulation test}
+  \bigskip
+  \label{manipulationplot}
+  \end{minipage}
+  \end{center}
+\end{figure}
+
+For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}.
+For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21.
+When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor.
+However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors.
+This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
+That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.
+
+To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
+Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
+The reason for the first variable is the multiple threshold assignments.
+We add GDP per capita because wealthier cities tend to be more productive and have better public services.
+The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
+The year and the northeast dummies serve to improve efficiency.
+Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.
+See the following section for further tests and simulations.
+
+For the last assumption, we should have no changes in pre-treatment covariates.
+These pre-treatment covariates are variables measured before the primary outcomes.
+As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
+
+Table \ref{validitycheck} displays the results of the validity checks.
+At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs.
+At the bottom, we estimate the pre-treatment covariate balance.
+
+XXXX CHANGE THIS
+
+\begin{table}[htb!] \centering 
+  \caption{Research Design Validity Check} 
+  \label{validitycheck} 
+    \scalebox{0.9}{
+  \begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+ & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
+   & \multicolumn{1}{c}{\small{(1)}} & 
+ \multicolumn{1}{c}{\small{(2)}} & 
+ \multicolumn{1}{c}{\small{(3)}} & 
+ \multicolumn{1}{c}{\small{(4)}} \\
+
+ & \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} & 
+ \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
+  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+\\[-1.8ex] 
+ LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
+  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
+\hdashline \\[-1.8ex]   
+ N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
+Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
+BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
+BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
+\midrule 
+ & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(5)}} & 
+ \multicolumn{1}{c}{\small{(6)}} & 
+ \multicolumn{1}{c}{\small{(7)}} & 
+ \multicolumn{1}{c}{\small{(8)}} \\
+  & \multicolumn{1}{c}{\small{Number of}} & 
+ \multicolumn{1}{c}{\small{Population}} & 
+ \multicolumn{1}{c}{\small{GDP}} & 
+ \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2000}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} &
+   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
+  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
+  \hdashline \\[-1.8ex]
+ N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
+Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
+Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
+BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
+BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
+RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
+After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
+Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
+These tests reinforce the validity of our research designs.
+
+\pagebreak
+
+## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
+\label{appidentif}
+
+The identification strategy requires exogenous changes in the city council size thresholds.
+Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
+
+\begin{table}[htp!]
+\centering
+\caption{City council size from the 1988 Constitution}
+\scalebox{0.75}{
+\begin{tabular}{rccrrr}
+  \hline\hline
+ & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\ 
+ & & & & & \multicolumn{1}{c}{(2001-2004)} \\
+  \hline
+  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\ 
+  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\ 
+  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\ 
+   \hline\hline
+\end{tabular}
+}
+\label{tabcitycouncilsize1988}
+\end{table}
+
+These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors.
+The two losing councilors started a judicial contestation that made it to the Supreme Court.
+The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55.
+Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004).
+According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
+
+\begin{table}[htp!]
+\centering
+\caption{City council size thresholds according to TSE resolution 21,702/2004}
+\scalebox{0.75}{
+\begin{tabular}{rcrrr}
+  \hline\hline
+ &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
+ & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
+  \hline
+  1 &  9 & 0 & 47,619 & 5,029 \\ 
+  2 &  10 & 47,620 & 95,238 & 317 \\ 
+  3 &  11 & 95,239 & 142,857 & 89 \\ 
+  4 &  12 & 142,858 & 190,476 & 43 \\ 
+  5 &  13 & 190,477 & 238,095 & 30 \\ 
+  6 &  14 & 238,096 & 285,714 & 21 \\ 
+  7 &  15 & 285,715 & 333,333 & 13 \\ 
+  8 &  16 & 333,334 & 380,952 & 13 \\ 
+  9 &  17 & 380,953 & 428,571 & 6 \\ 
+  10  & 18 & 428,572 & 476,190 & 6 \\ 
+  11  & 19 & 476,191 & 523,809 & 4 \\ 
+  12  & 20 & 523,810 & 571,428 & 5 \\ 
+  13  & 21 & 571,429 & 1,000,000 & 13 \\ 
+  14  & 33 & 1,000,001 & 1,121,952 & 1 \\ 
+  15  & 34 & 1,121,953 & 1,243,903 & 2 \\ 
+  16  & 35 & 1,243,904 & 1,365,854 & 1 \\ 
+  17  & 36 & 1,365,855 & 1,487,805 & 2 \\ 
+  18  & 37 & 1,487,806 & 1,609,756 & 1 \\ 
+  19  & 38 & 1,609,757 & 1,731,707 & 1 \\ 
+  20  & 39 & 1,731,708 & 1,853,658 & 0 \\ 
+  21  & 40 & 1,853,659 & 1,975,609 & 0 \\ 
+  22  & 41 & 1,975,610 & 4,999,999 & 4 \\ 
+  23  & 42 & 5,000,000 & 5,119,047 & 0 \\ 
+  24  & 43 & 5,119,048 & 5,238,094 & 0 \\ 
+  25  & 44 & 5,238,095 & 5,357,141 & 0 \\ 
+  26  & 45 & 5,357,142 & 5,476,188 & 0 \\ 
+  27  & 46 & 5,476,189 & 5,595,235 & 0 \\ 
+  28  & 47 & 5,595,236 & 5,714,282 & 0 \\ 
+  29  & 48 & 5,714,283 & 5,833,329 & 0 \\ 
+  30  & 49 & 5,833,330 & 5,952,376 & 0 \\ 
+  31  & 50 & 5,952,377 & 6,071,423 & 1 \\ 
+  32  & 51 & 6,071,424 & 6,190,470 & 0 \\ 
+  33  & 52 & 6,190,471 & 6,309,517 & 0 \\ 
+  34  & 53 & 6,309,518 & 6,428,564 & 0 \\ 
+  35  & 54 & 6,428,565 & 6,547,611 & 1 \\ 
+  36  & 55 & 6,547,612 & $\infty$  & 0 \\ 
+   \hline\hline
+\end{tabular}
+}
+\label{tabcitycouncilsize2004all}
+\end{table}
+
+As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants.
+Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.
+
+\begin{table}[htp!]
+\centering
+\caption{City council thresholds used in the paper}
+\scalebox{0.85}{
+\renewcommand*{\arraystretch}{1.2}
+\begin{tabular}{rcrrr}
+  \hline \hline
+ & \multicolumn{1}{c}{Legislature} & \multicolumn{1}{c}{Min.} & \multicolumn{1}{c}{Max.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
+ & \multicolumn{1}{c}{Size} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{Population} & \multicolumn{1}{c}{(2003 pop.)} \\
+  \hline
+  1 & 9 & 0 & 47,619 & 5,029 \\ 
+  2 & 10 & 47,620 & 95,238 & 317 \\ 
+  3 & 11 & 95,239 & 142,857 & 89 \\ 
+  4 & 12 & 142,858 & 190,476 & 43 \\ 
+  5 & 13 & 190,477 & 238,095 & 30 \\ 
+  6 & 14 & 238,096 & 285,714 & 21 \\ 
+  7 & 15 & 285,715 & 333,333 & 13 \\ 
+  8 & 16 & 333,334 & 380,952 & 13 \\ 
+  9 & 17 & 380,953 & 428,571 & 6 \\ 
+  10 & 18 & 428,572 & 476,190 & 6 \\ 
+  11 & 19 & 476,191 & 523,809 & 4 \\ 
+  12 & 20 & 523,810 & 571,428 & 5 \\ 
+  13 & 21 & 571,429 & 1,000,000 & 13 \\ 
+   \hline \hline
+\end{tabular}
+}
+\label{tabcitycouncilsize2004short}
+\end{table}
+
+The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
+In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections.
+Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).
+
+To provide an overview of the data dispersion, Figure \ref{sample_plot} plots the municipalities by their proximity from the cutoffs.
+In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
+The darker the color, the closer to the population thresholds.
+In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation.
+Figure \ref{sampleplot} also shows that our municipalities are reasonably distributed around the whole country.
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=7in,angle=0]{figs/samplePlot.pdf}}
+      \caption{Municipalities by their Selection Status}
+      \bigskip
+      \label{sampleplot}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+Moreover, we could question whether the discontinuities studied here are sharp or fuzzy.
+In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced.
+For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities.
+However, this problem was absent in our RDD, as the problem identified by Cavalcanti was based on the use of thresholds approved in 2009.
+In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).
+
+\newpage
+
+## Identification Strategy in Multiple Thresholds Regression Discontinuity Design
+\label{ISMT}
+
+Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes.
+Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
+The outcome variable is assumed to be $Y$.
+In the pooled model, the Local Average Treatment Effect is:
+
+\[
+LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
+\]
+
+Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff.
+The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
+To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
+For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
+As the population varies smoothly around each cutoff, it makes it a perfect control to add.
+The new estimator is:
+
+\[
+LATE_{controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C, Z_i \right]
+\]
+
+We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
+All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}.
+To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff.
+To compute the optimal bandwidth, we use the \citet{CCT2014} method.
+To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
+We also use cluster-robust standard errors at the municipal level.
+
+However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable?
+To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.
+
+Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
+We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes.
+The first three outcomes are sharp changes.
+In the first, we add variation from one to 10, with one step for each change.
+In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
+The estimated change should be equal to zero.
+In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
+This is intended to simulate a diminishing effect from one cutoff to the other.
+The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
+We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{0.9\linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/simdistrRDD.pdf}}
+      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
+      \bigskip
+      \label{simRDdd}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+A consistent estimator should fit one in the first and fourth data distribution.
+In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
+In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$.
+The first three models should present a more efficient estimation than the last three models.
+We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1\linewidth}
+      \centerline{\includegraphics[width=4.5in,angle=0]{figs/estimsRDD.pdf}}
+      \caption{Estimations for the Different Data Generating Processes}
+      \bigskip
+      \label{estimDGP}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\newpage
+
+## Placebo Regressions for the Aggregated Mechanism Outcomes
+\label{placmechmain}
+
+Here we present the placebo regressions for the mechanism-aggregated outcomes.
+In Panel A of the main paper, we run the regression on alternative explanations.
+As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases.
+For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank.
+In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage.
+As expected, the placebo regressions were not statistically significant.
+
+XXXX CHANGE
+
+\begin{table}[!htbp] \centering 
+\caption{Mechanism -- Aggregate Municipal Level Regressions} 
+\label{placresmechreg1} 
+\scalebox{0.9}{
+\begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l R R R R }
+\toprule
+ & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections -- Placebo Cutoffs}} \\ \cline{2-5}
+& \multicolumn{2}{c}{\textbf{Representation}} & 
+\multicolumn{2}{c}{\textbf{Elections \& Leg. Productivity}}\\ \cline{2-3}\cline{4-5}
+ & \multicolumn{1}{c}{\small{Num. Female}} & 
+ \multicolumn{1}{c}{\small{Num. Non-white}} &
+  \multicolumn{1}{c}{\small{Candidates}} & 
+  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
+   & \multicolumn{1}{c}{\small{Councilors}} & 
+ \multicolumn{1}{c}{\small{Councilors}} &
+  \multicolumn{1}{c}{\small{Per Seat}} & 
+  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+  LATE & 0.65$^{**}$ &  & -0.72 & -0.001 \\ 
+  & (0.27) &  & (0.48) & (0.06) \\ 
+  N Left & 4620 &  & 4621 & 2991 \\ 
+  N Right & 906 &  & 906 & 703 \\ 
+  Eff N Left & 412 &  & 567 & 356 \\ 
+  Eff N Right & 297 &  & 347 & 229 \\ 
+  BW Loc Poly & 4.861 &  & 6.113 & 5.58 \\ 
+  BW Bias & 8.775 &  & 10.345 & 8.896 \\ 
+\midrule
+ & \multicolumn{4}{c}{\textbf{Panel B: Resource Access and Patronage -- Placebo Cutoffs}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{Mayoral}} & 
+ \multicolumn{1}{c}{\small{Num. Politically}} & 
+ \multicolumn{1}{c}{\small{Num. Career}} & 
+ \multicolumn{1}{c}{\small{Num. Councilor}} \\
+ & \multicolumn{1}{c}{\small{Coalition Size}} & 
+ \multicolumn{1}{c}{\small{Appointed Empl.}} & 
+ \multicolumn{1}{c}{\small{Bureaucrats}} & 
+ \multicolumn{1}{c}{\small{Assistants}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.12 & 3.77 & 115.67 & -2.17 \\ 
+ & (0.34) & (17.20) & (79.96) & (1.81) \\ 
+ N Left & 4618 & 13855 & 13850 & 4618 \\ 
+ N Right & 904 & 2709 & 2708 & 905 \\ 
+ Eff N Left & 644 & 1123 & 1464 & 592 \\ 
+ Eff N Right & 388 & 825 & 957 & 361 \\ 
+ BW Loc Poly & 6.730 & 4.475 & 5.461 & 6.279 \\ 
+ BW Bias & 10.421 & 7.600 & 9.999 & 10.944 \\ 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
+RD estimates using \citet{CCT2014} optimal bandwidth selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parenthesis.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\newpage
+
+## Sensitivity Analysis for Bandwidth Selection
+\label{sensffapp}
+
+We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1\linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/bwSens.pdf}}
+      \caption{Bandwidth Sensitivity -- Main Models}
+      \bigskip
+      \label{graphbw}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
+
+\pagebreak
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placBwSens.pdf}}
+      \caption{Placebo Regressions -- Bandwidth Sensitivity}
+      \bigskip
+      \label{placgraphbw}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\newpage
+
+## Sensitivity to Different States in the Analysis
+\label{sensstate}
+
+The literature considers that some states are more prone to inefficiencies than the rest of the country.
+Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves.
+As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size.
+We run the analysis dropping one state at a time, to investigate this statewide heterogeneity.
+The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
+
+To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks.
+The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states.
+In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo.
+Otherwise, note that all the other variables remain unchanged, except for gender.
+Gender changes because there were laws during this period mandating a minimum amount of female candidates.
+It is expected that one variable changes as a response to randomness.
+
+\pagebreak
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/dropStateSens1.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
+      \bigskip
+      \label{graphsensstatedrop1}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/dropStateSens2.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
+      \bigskip
+      \label{graphsensstatedrop2}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=5in,angle=0]{figs/placDropStateSens1.pdf}}
+      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop1}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+XXXX CHANGE
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/placDropStateSens2.pdf}}
+      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop2}
+  \end{center}
+\end{figure}
+
+\newpage

### 2021-08-16 appendix/appendix.Rmd
Sensitivity Analysis Covariates Appendix

@@
 The city council votes the mayor's proposal and if they accept it, it is implemented.
-Otherwise, a reversal policy takes place, where the decision leaves the mayor's hands and either immediately stops or transfers to the council.
+Otherwise, a reversal policy takes place.
+Reversal policy in this context means that the mayor's proposal failed to secure majority of council votes.
+The decision leaves the mayor's hands, and either immediately stops or it is transferred to the council.
 The types of reversal policies are crucial for our argument, as it changes the relative strength of the councilors in their bargaining with the mayor.
 We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan concerns; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan concerns with non-partisan rent extraction.
-In the main paper, we report only the hybrid model, as it is the more realistic scenario.
+In the main paper, we focus on the hybrid model, as it is the more realistic scenario.
 Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that the partisan a mechanism is what drives our results.
@@
 This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
-Both the utilities from rents ($u(r)$) and the probability of reelection $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
-The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office, and we assume that they are high enough to rule out an equilibrium with only rents and transfers.
+Both the utilities from rents $u(r)$ and the probability of reelection $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
+This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
+We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers.
 If the mayor's policy proposal is approved, then the expected utility for the mayor is:
@@
 
-Let $C_G$ the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:
+Let $C_G$ be the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:
 
@@
 
-The expected utility for the city councilors depend on the mechanism that will determine the reversal policy.
+The expected utility for the city councilors depend on the reversal policy.
 As discussed, we explore three different mechanisms.
@@
 Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once).
-If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition ($G \subset \{1, 2, \cdots, N \}$).
+If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
 Otherwise, the city councilor belongs to the opposition $O \not\subset G$.
@@
   \end{itemize}
-  \item (Reversal Policy) Depends on which mechanism, we will have three different reversal policies. We will detail them below.
+  \item (Reversal Policy) Depends on which mechanism, we have three different reversal policies. The details are in the following sections.
 \end{enumerate}
@@
 A Stationary Sub-game Perfect Equilibrium is based on the assumption that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should accept the same offer at time $k$.
-This gives us an objective of finding the offer that will be accepted at any point in the game.
-Applying this reasoning, we can find the optimal offer at $k=0$, which represents no delay in policy implementation.
+Stationarity gives us an objective of finding an offer that would be accepted at any stage in the game.
+Applying this reasoning, we can find a sequence of offers for each point $k$ in time.
+For the mayor the optimal offer is at $k=0$, and this represents a no delay in policy implementation.
 
 \begin{definition}
-The solution for the game consists in a pair of strategic policy vectors $(g^*, r^*, x^*)_k$, for $k \in \{0, 1, \cdots, \infty\}$, such that, for the mayor and the councilors, there are no profitable deviations from the equilibrium.
+The equilibrium for the game consists in a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
 \end{definition}
 
-Moreover, we assume that the players will play no dominated strategies, even when there is less than sufficient support for implement the policy.
+Moreover, we assume that the players play no dominated strategies, even when there is less than sufficient support for implement the policy.
 
@@
 Solving the game by backward induction would require us to start with the councilor's strategies.
-However, for simplicity, we will assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors.
-As we will show in a few paragraphs, this is without loss of generality as we will drop the assumption.
-We use it to simplify the exposition.
+However, for simplicity, assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors.
+Below we define $C_G(N)$ for each of the mechanisms, but for now we use this assumption to simplify the exposition.
 
@@
 However, she prefers to contribute as minimum as necessary for the public goods, and extract the remaining resources as political rents.
-Her objective is to maximize the following expected utility, subject to the municipal budget constraint.
+The mayor's objective is to maximize the following expected utility, subject to the municipal budget constraint.
 
@@
 
-To start, note that $\mathbb{R} \times \mathbb{N}$ is a complete lattice.
-In this case, mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$, we have:
+The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} we have:
 
@@
 To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and we are at the $k$-th stage in the game.
-A councilor will accept the proposer's offer if, and only if, to accept the offer is better than to wait until the next stage.
+A councilor accepts the proposer's offer if, and only if, to accept the offer is better than to wait until the next stage.
 If the offer is $x_i$, then:
@@
 It is equal to the budget in the next round minus the offers that she has to make to convince half of the councilors.
-The second part is the gains if she happens to reject but still receive an offer in the following round.
-Note that the offer she makes when she is the proposer is the same as the offer she wants to receive.
+The second part is the gains if when the councilor happens to reject the current received offer, but still receives an offer in the following round.
+Note that the offer the councilor makes as the proposer is the same as the offer that she wants to receive.
 This because the city councilors are exchangeable, and the solution is symmetric for all councilors receiving an offer (this means that we could have dropped the $i$ in the solution).
@@
 \[
-C_G(N) \ = \ \dfrac{N}{2N + 1}(\delta R)
+C_G(N) \ = \ \dfrac{\delta R N}{2N + 1}
 \]
@@
 \begin{aligned}
-C_G(N+1) - C_G(N) \ = \ & \dfrac{N+1}{2(N+1) + 1}(\delta R) - \dfrac{N}{2N + 1}(\delta R) \\
+C_G(N+1) - C_G(N) \ = \ & \dfrac{(N+1)\delta R}{2(N+1) + 1} - \dfrac{N \delta R}{2N + 1}\\
  = \ & \dfrac{\delta R}{(2N+3)(2N+1)}  \\
@@
 
-A legislator aligned with the mayor will always support the mayor's policy, regardless of receiving or not private goods.
-This because as $p > 0$, the councilor always receive positive benefits from the policy.\footnote{In reality, if it was possible, the mayor could even impose a cost to the city councilors aligned with the government.
-Although this seem unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office.} However, a politician not aligned with the mayor will require a compensation if her vote is needed.
-In this case, if the mayor needs the support of an opposition politician to pass her policy proposal, then she will need to compensate her for the policy costs.
-In this case:
+A legislator aligned with the mayor always support the mayor's policy, regardless of receiving or not private goods.
+This because as $p > 0$, the councilor always receive positive benefits from the policy.\footnote{The mayor could even impose a cost to the city councilors aligned with the government.
+Although this seem unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office, or even take the popular fallout from a failed policy.} However, politicians not aligned with the mayor require a compensation when their votes are needed.
+In this case, if the mayor's proposal requires the support of an opposition politician, then the mayor compensates the councilor for the policy costs.
+In such case:
 
@@
 
-Optimality dictates that the mayor will offer $x_i = p$ to the opposition legislator.
+Optimality dictates that the mayor offers $x_i = p$ to the opposition legislator.
 Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
-Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor will have to compensate minus the amount needed to implement the policy, in this case, half of them:
+Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor has to compensate minus the amount needed to implement the policy, in this case, half of them:
 
@@
 As a response, the public goods provision (and also rents), increase.
-The rate distribution between these two vectors will be determined by the marginal change in the utility from rents and the utility from reelection.
+The rate distribution between these two vectors is determined by the marginal change in the utility from rents and the utility from reelection.
 In any case, the amount allocated for both increase.
@@
 
-Inspecting these equations, we can decompose these costs into costs in terms of rents and costs (or benefits) from political alignment.
-In this context, the cost of govern will be depend on the expected payments for councilors in the mayor's coalition, versus the expected payments for the councilors that belongs to the opposition.
-The chance of a opposition member be elected is equal to $\gamma$, and taking the weighted averages, these costs become:
+We can decompose these costs in two components.
+First, the costs in terms of rents.
+Second, the costs (or benefits) from political alignment.
+In this context, the governing costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's offers for councilors in the opposition.
+The ex-ante chance of a opposition member be elected is equal to $1-\gamma$, and taking the weighted averages, these costs become:
 
@@
 
-Also, note that the threshold $\gamma$ for the probability of electing a politician aligned with the government is decreasing in both the political value of the mayors policy $p$ and the size of the legislature $N$.
+Also, the threshold $\underline{\gamma}$ for the probability of electing a politician aligned with the government is decreasing in both the political value of the mayors policy $p$ and the size of the legislature $N$.
 This means that higher political values and larger legislatures makes it easier to satisfy the electoral threshold.
@@
 
-Taking stocks, the models provide two empirically testable hypotheses. Consider a city council comprised of $N$ legislators, that increase the council size to $N+1$. Then:
+Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators, that increase its council size to $N+1$. Then:
 
 \begin{enumerate}
-  \item[H1. ] The provision of public goods increase when the costs to govern decrease with legislature size.
-  \item[H2. ] The costs to govern decrease with legislature size when the chance of electing a government aligned legislator is sufficiently high.
+  \item[H1. ] The provision of public goods increase when the governing costs decrease with legislature size.
+  \item[H2. ] The governing decrease with legislature size when the chance of electing a government aligned legislator is sufficiently high.
 \end{enumerate}
@@
 \newpage
+
+## Sensitivity to the Functional Form Analysis
+\label{sensfuncform}
+
+In the paper, we run all the regressions using local linear polynomials.
+\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
+
+However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms.
+With two exceptions, the results are mostly consistent.
+First, quadratic and cubic polynomials make the significance go away in some models.
+Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions.
+Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,angle=0]{figs/ffSens.pdf}}
+      \caption{Sensitivity Analysis for the Functional Form}
+      \bigskip
+      \label{graphsensff}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+  \begin{center}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/placFfSens.pdf}}
+      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
+      \bigskip
+      \label{placgraphsensff}
+  \end{center}
+\end{figure}
+
+\newpage
+
+## Sensitivity to Covariates
+\label{senstcovapp}
+
+The control variables play an essential role in our model.
+As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
+
+However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis.
+To study the sensitivity to controls, we run the same regressions for all possible control combinations.
+Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
+The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}
+
+\begin{landscape}
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=6in,angle=0]{figs/sensCov.pdf}}
+      \caption{Sensitivity Analysis for the Control Variable's Choices}
+\bigskip
+\label{graphsenscontrol}
+\end{minipage}
+\end{center}
+\end{figure}
+\end{landscape}
+
+For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.
+
+In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant.
+Otherwise, our model is not significant when most combinations are also insignificant.
+Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.
+
+We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
+The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=5in,angle=0]{figs/placSens1Cov.pdf}}
+\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
+\bigskip
+\label{placsenscov1}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=5in,angle=0]{figs/placSens2Cov.pdf}}
+\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
+\bigskip
+\label{placsenscov2}
+\end{center}
+\end{figure}
+
+\newpage

### 2021-08-16 appendix/appendix.Rmd
Mayor's characteristics and tranfers

@@
 
-In the paper, we show that the provision of education and healthcare improves in Brazil, and this results from the fact that the chances of electing a city councilor aligned with the mayor is of 91%.
+In the paper, we show that the provision of education and healthcare improves in Brazil, and this results from the fact that the chances of electing a city councilor aligned with the mayor is of 91%, thanks to the rule of distributing seats adopted in the country.
 
@@
 \newpage
+
+\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}
+
+To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
+This strategy is similar to adding one cutoff at a time.
+The results are stable and do not change our main conclusions.
+Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring.
+Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=6in,angle=0]{figs/rdAddCuts1.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
+\bigskip
+\label{senscut1}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\centerline{\includegraphics[width=6in,angle=0]{figs/rdAddCuts2.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
+\bigskip
+\label{senscut2}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{0.8 \linewidth}
+\centerline{\includegraphics[width=5.5in,angle=0]{figs/placRDAddCuts1.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
+\bigskip
+\label{placsenscut1}
+\end{minipage}
+\end{center}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{0.8 \linewidth}
+\centerline{\includegraphics[width=5.5in,angle=0]{figs/placRDAddCuts2.pdf}}
+\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
+\bigskip
+\label{placsenscut2}
+\end{minipage}
+\end{center}
+\end{figure}
+
+\newpage
+
+## Mayor's Characteristics, Revenues, and Transfers from the Central Government
+
+Two alternative explanations could confound our results.
+First, the selection of the mayor could be affected by the city council size, and then the welfare improve by the quality of the mayor, and not by the partisan mechanism described.
+Second, the partisan mechanism could be confounded by an argument similar to the @Weingastetal1981 ``law of 1/n'', and the improvements in welfare could have been a result of higher revenues.
+This section shows that none of these concerns are true in our case.
+
+\subsubsection{Mayoral characteristics}
+
+We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
+The results show no variation on council size and mayoral characteristics.
+
+\begin{table}[!htbp] \centering 
+\caption{Mayoral Characteristics} 
+\label{appmaychar} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
+College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
+  \hline \\[-1.8ex] 
+  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\ 
+  & (0.08) & (0.13) & (0.10) & (0.14) \\ 
+  N Left & 5069 & 5069 & 5184 & 5183 \\ 
+  N Right & 335 & 335 & 343 & 343 \\ 
+  Eff N Left & 299 & 226 & 192 & 231 \\ 
+  Eff N Right & 184 & 154 & 141 & 159 \\ 
+  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\ 
+  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\begin{table}[!htbp] \centering 
+\caption{Mayoral characteristics -- Placebo} 
+\label{placappmaychar} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
+College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
+  \hline \\[-1.8ex] 
+  LATE & 0.03 & 0.04 & 0.08 & -0.07 \\ 
+  & (0.05) & (0.08) & (0.07) & (0.08) \\ 
+  N Left & 4526 & 4526 & 4621 & 4620 \\ 
+  N Right & 878 & 878 & 906 & 906 \\ 
+  Eff N Left & 567 & 707 & 683 & 759 \\ 
+  Eff N Right & 342 & 406 & 397 & 427 \\ 
+  BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\ 
+  BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\subsubsection{Revenues and Transfers}
+
+We run the regressions on federal transfers and revenue raised within the municipalities.
+There is only a small effect on education transfer, barely significant at 10%.
+The other indicators remain insignificant.
+Note that the placebo are significant, and this actually reinforce the claim that the education effect may be spurious.
+
+\begin{table}[!htbp] \centering 
+\caption{Transfers and Revenue} 
+\label{apptrev} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
+  \hline \\[-1.8ex] 
+  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\ 
+  & (0.04) & (0.03) & (0.10) & (0.04) \\ 
+  N Left & 15555 & 15555 & 15460 & 14668 \\ 
+  N Right & 1029 & 1029 & 1028 & 998 \\ 
+  Eff N Left & 804 & 258 & 349 & 626 \\ 
+  Eff N Right & 516 & 273 & 333 & 442 \\ 
+  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\ 
+  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\begin{table}[!htbp] \centering 
+\caption{Transfers and Revenue -- Placebo} 
+\label{plactrev} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\ 
+  \hline \\[-1.8ex] 
+  LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\ 
+  & (0.03) & (0.03) & (0.06) & (0.03) \\ 
+  N Left & 13865 & 13865 & 13776 & 13103 \\ 
+  N Right & 2719 & 2719 & 2712 & 2563 \\ 
+  Eff N Left & 807 & 636 & 1928 & 848 \\ 
+  Eff N Right & 619 & 544 & 1163 & 611 \\ 
+  BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\ 
+  BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \end{tabular} }
+\end{table}
+
+\newpage

### 2021-08-16 appendix/appendix.Rmd
App approved legislation section

@@
 \newpage
+
+\subsection{Legislation Dataset\label{legdfr}}
+
+In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds.
+There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.
+
+To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases.
+First, we train and test the accuracy of the SVM classifier on 80\% of the dataset.
+Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
+We choose SVM as it gives the highest prediction rate.
+We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
+
+We hand-coded using five characteristics:
+
+\begin{enumerate}
+\item \textbf{Local Public Goods}: Whether the bills provided a local public good or service.
+Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
+To lay on this category, the service should have been targeted for a fraction of the population.
+\item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law).
+\item \textbf{Oversight}: Legislation requesting information on the status of service provision.
+\item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
+\item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
+\end{enumerate}
+
+We run the SVM on the hand-coded data.
+Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded.
+In all models, we set cost equals 10 to avoid overfitting.
+
+\begin{table}
+\centering
+\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
+\label{accurClassif}
+\begin{tabular}{lc} 
+\hline
+\textbf{Variable}            & \textbf{Accuracy}  \\ 
+\hline
+Local Public Goods           & 93.8               \\
+Public Goods and Legislation & 94.2               \\
+Oversight                    & 94.9               \\
+Others                       & 93.5               \\
+Education and Health Care    & 92.5               \\
+\hline
+\end{tabular}
+\end{table}
+
+After we classify all the bills, the frequency in each category was added to the main paper.
+We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
+As expected, the results changed little from when we considered the absolute values.
+
+\newpage

### 2021-08-16 appendix/appendix.Rmd
Appendix Stage One Revisions

@@
 \newpage
+
+\subsection{City Councilors Survey\label{appsurv}}
+
+From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period.
+We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.
+
+We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
+In December 1st we closed the pool, having 174 responses.
+Figure \ref{geodistrsurv} displays a distribution of responses.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{figs/distrRespSurvey.pdf}}
+      \caption{Geographical Distribution of Survey Responses}
+      \bigskip
+      \label{geodistrsurv}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\pagebreak
+
+To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative.
+We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions.
+We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
+In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
+
+\begin{table}[htp!]
+\centering
+\caption{Proportions for each bin used in the weighting process}
+\label{tabweight}
+\begin{tabular}{lccc}
+\hline
+& Sample & Population & Weighted \\
+& Proportions & Proportions. & Proportions \\
+\hline
+\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
+\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
+\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
+\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
+\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
+\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
+\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
+\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
+\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
+\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
+\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
+\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
+\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
+\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
+\end{tabular}
+\end{table}
+
+Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.
+
+The questions of interest for this research, asked in the survey were:
+
+\begin{enumerate}
+    \item No Brasil é comum que o prefeito tenha de negociar para ter maioria na Câmara de Vereadores.
+Com que frequência, o(a) Sr(a) acha que o prefeito usa os seguintes dispositivos para conseguir apoio?
+    \item Quais dessas atividades o(a) Sr(a) acredita serem mais comuns no trabalho da maioria dos vereadores?
+    \item Quais dessas atividades o(a) Sr(a) acredita que ajudam mais um vereador durante a eleição?
+\end{enumerate}
+
+A free translation to English would be:
+
+\begin{enumerate}
+    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
+    \item Which of those activities do city councilors perform the most in their representation practices?
+    \item Which of the following activities do you believe helps city councilors the most in elections?
+\end{enumerate}
+
+The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
+Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.
+
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6.5in,angle=0]{figs/commonJobsCouncilors.pdf}}
+      \caption{City Councilor's Common Activities}
+\bigskip
+\label{commonservice}
+\end{minipage}
+\end{center}
+\end{figure}
+
+The last question measures the willingness of mayors to give services to city councilors.
+This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors.
+Figure \ref{mayorneg} shows the results for the mayoral activities.
+
+\begin{figure}[htb!]
+\begin{center}
+\begin{minipage}{1 \linewidth}
+\centerline{\includegraphics[width=6.5in,angle=0]{figs/strategySupportMayors.pdf}}
+\caption{Mayor negotiated services in exchange of support}
+\bigskip
+\label{mayorneg}
+\end{minipage}
+\end{center}
+\end{figure}
+
+Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield.
+The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.
+
+Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors.
+Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.

### 2021-08-16 appendix/appendix.Rmd
Organizing folder

@@
   \begin{minipage}{1 \linewidth}
-  \centerline{\includegraphics[width=5in,angle=0]{figs/McCrary.pdf}}
+  \centerline{\includegraphics[width=5in,angle=0]{../figures/McCrary.pdf}}
   \caption{\citet{McCrary2008} manipulation test}
@@
 
-To provide an overview of the data dispersion, Figure \ref{sample_plot} plots the municipalities by their proximity from the cutoffs.
+To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity from the cutoffs.
 In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=7in,angle=0]{figs/samplePlot.pdf}}
+      \centerline{\includegraphics[width=7in,angle=0]{../figures/samplePlot.pdf}}
       \caption{Municipalities by their Selection Status}
@@
     \begin{minipage}{0.9\linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/simdistrRDD.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/simdistrRDD.pdf}}
       \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
@@
     \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=4.5in,angle=0]{figs/estimsRDD.pdf}}
+      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
       \caption{Estimations for the Different Data Generating Processes}
@@
     \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/bwSens.pdf}}
+      \centerline{\includegraphics[width=5in,angle=0]{../figures/bwSens.pdf}}
       \caption{Bandwidth Sensitivity -- Main Models}
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/placBwSens.pdf}}
+      \centerline{\includegraphics[width=5in,angle=0]{../figures/placBwSens.pdf}}
       \caption{Placebo Regressions -- Bandwidth Sensitivity}
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{figs/dropStateSens1.pdf}}
+      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens1.pdf}}
       \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{figs/dropStateSens2.pdf}}
+      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens2.pdf}}
       \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
@@
   \begin{center}
-      \centerline{\includegraphics[width=5in,angle=0]{figs/placDropStateSens1.pdf}}
+      \centerline{\includegraphics[width=5in,angle=0]{../figures/placDropStateSens1.pdf}}
       \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
@@
   \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/placDropStateSens2.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/placDropStateSens2.pdf}}
       \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{figs/ffSens.pdf}}
+      \centerline{\includegraphics[height=8in,angle=0]{../figures/ffSens.pdf}}
       \caption{Sensitivity Analysis for the Functional Form}
@@
   \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/placFfSens.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/placFfSens.pdf}}
       \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=6in,angle=0]{figs/sensCov.pdf}}
+      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov.pdf}}
       \caption{Sensitivity Analysis for the Control Variable's Choices}
@@
 \begin{center}
-\centerline{\includegraphics[width=5in,angle=0]{figs/placSens1Cov.pdf}}
+\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens1Cov.pdf}}
 \caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
@@
 \begin{center}
-\centerline{\includegraphics[width=5in,angle=0]{figs/placSens2Cov.pdf}}
+\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens2Cov.pdf}}
 \caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
@@
 \begin{center}
-\centerline{\includegraphics[width=6in,angle=0]{figs/rdAddCuts1.pdf}}
+\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts1.pdf}}
 \caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
@@
 \begin{center}
-\centerline{\includegraphics[width=6in,angle=0]{figs/rdAddCuts2.pdf}}
+\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts2.pdf}}
 \caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
@@
 \begin{minipage}{0.8 \linewidth}
-\centerline{\includegraphics[width=5.5in,angle=0]{figs/placRDAddCuts1.pdf}}
+\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts1.pdf}}
 \caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
@@
 \begin{minipage}{0.8 \linewidth}
-\centerline{\includegraphics[width=5.5in,angle=0]{figs/placRDAddCuts2.pdf}}
+\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts2.pdf}}
 \caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/distrRespSurvey.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrRespSurvey.pdf}}
       \caption{Geographical Distribution of Survey Responses}
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6.5in,angle=0]{figs/commonJobsCouncilors.pdf}}
+      \centerline{\includegraphics[width=6.5in,angle=0]{../figures/commonJobsCouncilors.pdf}}
       \caption{City Councilor's Common Activities}
@@
 \begin{minipage}{1 \linewidth}
-\centerline{\includegraphics[width=6.5in,angle=0]{figs/strategySupportMayors.pdf}}
+\centerline{\includegraphics[width=6.5in,angle=0]{../figures/strategySupportMayors.pdf}}
 \caption{Mayor negotiated services in exchange of support}

### 2021-08-16 article/article.Rmd
Distribution of Seats Graph

@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/distrseats2019.pdf}}
-      \caption{Distribution of Municipalities by Population and City Council Size XXXX CHANGE HERE}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrSeats.pdf}}
+      \caption{Distribution of Municipalities by Population and City Council Size}
       \bigskip

### 2021-08-16 article/article.Rmd
Preliminary Compilation Article

@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/laws2019.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/lawsApproved.pdf}}
       \bigskip
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{figs/elecYieldJobsCouncilorsJan2019.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/elecYieldJobsCouncilors.pdf}}
       \bigskip

### 2021-08-18 appendix/appendix.Rmd
improving section 1 appendix

@@
 Reversal policy in this context means that the mayor's proposal failed to secure majority of council votes.
-The decision leaves the mayor's hands, and either immediately stops or it is transferred to the council.
-The types of reversal policies are crucial for our argument, as it changes the relative strength of the councilors in their bargaining with the mayor.
-We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan concerns; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan concerns with non-partisan rent extraction.
+The decision process leaves the mayor's office, and either immediately stops or it is transferred to the council.
+The types of reversal policies are crucial for our argument, as it changes the relative strength of the council in their bargaining with the mayor.
+We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features.
 In the main paper, we focus on the hybrid model, as it is the more realistic scenario.
@@
 To govern, the mayor has to convince at least half of the city councilors to support her policy proposals.
-Similar to selectorate models \citep{buenodemesquita2005logic}, we assume that the selectorate, i.e.
+Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, i.e.
 the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
 The winning coalition, which is the minimum number of members that have to be convinced to implement the policy, is equal to half of the selectorate $N/2$.
-City councilors are moved by policy concerns $p$ and transfers received from the mayor \textbf{x}.
-The use of transfers to affect the councilors' choices generate a cost of govern, $C_G$, that vary with the reversal mechanism and the legislature size.
+City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
+We leave the definition of these transfers open, as this facilitates the relation with several instruments that mayors can use to pressure city councilors.
+To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, granting portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
+The use of transfers to affect the councilors' choices and generate a governing cost of $C_G$.
+The governing costs vary with the reversal mechanism and the legislature size.
 
@@
 This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
-Both the utilities from rents $u(r)$ and the probability of reelection $\pi(g)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
+Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
 This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
-We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers.
+We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to say that mayors have a strong preference to be reelected.
 If the mayor's policy proposal is approved, then the expected utility for the mayor is:
@@
 First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
-The randomly selected councilor becomes now the proposer.
+The randomly selected councilor becomes the new proposer.
 If her proposal is accepted, it is implemented.
@@
 If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
-Otherwise, the city councilor belongs to the opposition $O \not\subset G$.
+Otherwise, the city councilor belongs to the opposition $O  = \{1, 2, \cdots, N \} \setminus G$.
 The mayor's policy generate a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends of the party affiliation of the councilor.
@@
 Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in terms of public goods provision are shared by councilors aligned with the mayor.
-Voting against the mayor's proposals would represent to defy the partisan brand.
+Voting against the mayor's proposals would represent to defy the partisan label.
 

### 2021-09-05 appendix/appendix.Rmd
changes paper

@@
 
-```{r, include=FALSE}
-## Starting
-#XXXX
-
-# Required packages
-#XXXX
-
-# Load datasets
-#XXXX
-```
-
 \newpage
@@
 Consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor is the head of the local executive branch, and has the prerogative of proposing a vector of policies, that is voted by the city councilors.
+The mayor is the head of the local executive branch and has the prerogative of proposing a vector of policies voted by the city councilors.
 Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.
 
-The city council votes the mayor's proposal and if they accept it, it is implemented.
+The city council votes the mayor's proposal, and if they accept it, it is implemented.
 Otherwise, a reversal policy takes place.
-Reversal policy in this context means that the mayor's proposal failed to secure majority of council votes.
-The decision process leaves the mayor's office, and either immediately stops or it is transferred to the council.
-The types of reversal policies are crucial for our argument, as it changes the relative strength of the council in their bargaining with the mayor.
-We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features.
-In the main paper, we focus on the hybrid model, as it is the more realistic scenario.
-Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that the partisan a mechanism is what drives our results.
-
-To govern, the mayor has to convince at least half of the city councilors to support her policy proposals.
-Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, i.e.
-the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
-The winning coalition, which is the minimum number of members that have to be convinced to implement the policy, is equal to half of the selectorate $N/2$.
+Reversal policy in this context means that the mayor's proposal failed to secure the majority of council votes.
+The decision process leaves the mayor's office and either immediately stops or is transferred to the council.
+The types of reversal policies are crucial for my argument, as it changes the relative strength of the council in their bargaining with the mayor.
+I investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided into supporters and non-supporters of the mayor; and finally, a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features.
+The main paper focuses on the hybrid model, as it is the more realistic scenario.
+Despite that, comparing the partisan and non-partisan reversal mechanisms clearly illustrates my argument that the partisan mechanism drives my results.
+
+The mayor has to convince at least half of the city councilors to support her policy proposals.
+Similar to \citet{buenodemesquita2005logic}, I assume that the selectorate, i.e., the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
+The winning coalition, the minimum number of members who have to be convinced to implement the policy, equals half of the selectorate $N/2$.
 City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
-We leave the definition of these transfers open, as this facilitates the relation with several instruments that mayors can use to pressure city councilors.
-To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, granting portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
-The use of transfers to affect the councilors' choices and generate a governing cost of $C_G$.
+I leave the definition of these transfers open, as this facilitates the relationship with several instruments that mayors can use to pressure city councilors.
+To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, giving portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
+The use of transfers affects the councilors' choices and generates a governing cost of $C_G$.
 The governing costs vary with the reversal mechanism and the legislature size.
 
-Finally, after paying the costs of govern, the mayor proposes a level of public goods provision ($g$) and rents ($r$).
-Public goods provision help the mayor to get reelected.
-Rents are for direct mayor's consumption, and does not contribute to the mayor's electoral success.
+Finally, after paying the govern costs, the mayor proposes a level of public goods provision ($g$) and rents ($r$).
+Public goods provision helps the mayor to get reelected.
+Rents are for direct mayor's consumption and do not contribute to the mayor's electoral success.
 This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
@@
 This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
-We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to say that mayors have a strong preference to be reelected.
+I assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
 If the mayor's policy proposal is approved, then the expected utility for the mayor is:
@@
 The policy choices of the mayor are subject to the municipal budget constraint.
-The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget has to be balanced.
-We also assume that there are enough resources for the mayor to govern.
-
-Let $C_G$ be the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:
+The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget must be balanced.
+I also assume that there are enough resources for the mayor to govern.
+
+Let $C_G$ be the costs of governing. The budget balance constraint requires the offers that the mayor makes to the city councilors to satisfy the following inequality:
 
@@
 
-The expected utility for the city councilors depend on the reversal policy.
-As discussed, we explore three different mechanisms.
+The expected utility for the city councilors depends on the reversal policy.
+As discussed, I explore three different mechanisms.
 First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
@@
 If her proposal is accepted, it is implemented.
-If it is rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to make the proposal.
-The process repeats, until one proposal is finally accepted.
-
-In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation.
+If rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to propose.
+The process repeats until one proposal is finally accepted.
+
+In the second reversal mode, the \textit{partisan} reversal mechanism, I assume that each councilor has a party affiliation.
 Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once).
-If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
+If a city councilor is affiliated to a party aligned with the mayor, I say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
 Otherwise, the city councilor belongs to the opposition $O = \{1, 2, \cdots, N \} \setminus G$.
-The mayor's policy generate a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends of the party affiliation of the councilor.
-If the mayor's proposal is rejected, a city councilor aligned with the mayor, that would receive $p$ from the policy, now receives zero.
-On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy, and now receives zero.
-Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in terms of public goods provision are shared by councilors aligned with the mayor.
-Voting against the mayor's proposals would represent to defy the partisan label.
-
-In the last reversal mechanism, the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining rents.
+The mayor's policy generates a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends on the party affiliation of the councilor.
+If the mayor's proposal is rejected, a city councilor aligned with the mayor that should have received $p$ from the policy now receives zero.
+On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy and now receive zero.
+Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in public goods provision are shared by councilors aligned with the mayor.
+Voting against the mayor's proposals would represent defying the partisan label.
+
+Lastly, in the \textit{hybrid} reversal mechanism, I combine partisanship with legislature bargaining costs.
 Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan reversal mechanism takes place.
 In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented.
-Opposition members, on the other hand, receive $-p$ when the mayor's proposal is implemented.
-If the mayor's proposal is rejected, as city councilors do not control the Executive when the two branches are separated, no public goods are provided ($p=0$).
-Moreover, in equilibrium, we assume that city councilors would prefer to receive rents instead of providing public goods.
+On the other hand, opposition members receive $-p$ when the mayor's proposal is implemented.
+If the mayor's proposal is rejected, as the city council does not control the Executive when the two branches are separated, no public goods are provided ($p=0$).
+Moreover, in equilibrium, I assume that city councilors would prefer to receive transfers instead of providing public goods.
 This aligns with the empirical evidence in most developing economies.
@@
   \begin{itemize}
-    \item If the council accepts, the policy is implemented and the game ends. 
+    \item If the council accepts, the policy is implemented, and the game ends. 
     \item Otherwise, the reversal policy is implemented.
   \end{itemize}
-  \item (Reversal Policy) Depends on which mechanism, we have three different reversal policies. The details are in the following sections.
+  \item (Reversal Policy) Depends on which mechanism, I propose three different reversal policies. The details are in the following sections.
 \end{enumerate}
 
-This is a bargaining game, along the lines of \citet{rubinstein1982perfect}.
-For a political science models similar to this model, see \citet{baron1989bargaining} and, to some extent, \citet{buenodemesquita2005logic}.
-
-The solution concept we use in this model is the Sub-game Perfect Nash Equilibrium.
+The solution concept I use in this model is the Sub-game Perfect Nash Equilibrium.
 A Sub-game Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game.
 The solution is found using backward induction.
-In the model with infinitely repeated proposals, we extend the equilibrium concept to require that the equilibrium is Stationary.
-A Stationary Sub-game Perfect Equilibrium is based on the assumption that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should accept the same offer at time $k$.
-Stationarity gives us an objective of finding an offer that would be accepted at any stage in the game.
-Applying this reasoning, we can find a sequence of offers for each point $k$ in time.
-For the mayor the optimal offer is at $k=0$, and this represents a no delay in policy implementation.
+In the model with infinitely repeated proposals, I extend the equilibrium concept to require that the equilibrium is Stationary.
+A Stationary Sub-game Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should take the same offer at time $k$.
+Stationarity provides the intending to find a proposal that would be accepted at any stage in the game.
+Applying this reasoning, I can find a sequence of offers for each point $k$ in time.
+For the mayor, the optimal offer is at $k=0$, representing a no delay in policy implementation.
 
 \begin{definition}
-The equilibrium for the game consists in a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
+The equilibrium for the game consists of a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
 \end{definition}
 
-Moreover, we assume that the players play no dominated strategies, even when there is less than sufficient support for implement the policy.
+Moreover, I assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.
 
@@
 
-Solving the game by backward induction would require us to start with the councilor's strategies.
-However, for simplicity, assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors.
-Below we define $C_G(N)$ for each of the mechanisms, but for now we use this assumption to simplify the exposition.
-
-We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
+Solving the game by backward induction requires me to start with the councilor's strategies.
+However, for exposure convenience, assume that I solved the game for the councilors and found the equilibrium cost of governing $C_G(N)$ when there are $N$ city councilors.
+In the next section, I define $C_G(N)$ for each mechanism using backward induction, and the definitions are well-behaved.
+In this section, I use this assumption to simplify the exposition.
+
+I now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
 The mayor benefits from public goods provision, as it increases the chances of her reelection.
-However, she prefers to contribute as minimum as necessary for the public goods, and extract the remaining resources as political rents.
-The mayor's objective is to maximize the following expected utility, subject to the municipal budget constraint.
+However, she prefers to contribute as minimum as necessary for the public goods and extract the remaining resources as political rents.
+The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.
 
@@
 
-In equilibrium the budget binds, and the public goods provision maximizes:
+In equilibrium, the budget binds, and the provision of the public goods maximizes:
 
@@
 
-The first order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:
+The first-order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:
 
@@
 \begin{proposition}
-The provision of public goods increase with legislature size when the costs of govern decrease with legislature size.
+The provision of public goods increases with legislature size when the costs of governing decrease with legislature size.
 \end{proposition}
@@
 \begin{proof}
-To prove this result we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$.
+To prove this result, I need to show that the mayor's expected utility satisfies the increasing differences in $g$ and $N$.
 This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase.
-However, as $N$ increases discretely, we cannot take a the cross-partial derivative on $N$ or even use the implicit function theorem.
-Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
-
-The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} we have:
+However, as $N$ increases discretely, I cannot take the cross-partial derivative on $N$ or even use the implicit function theorem.
+Instead, I use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
+
+The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} I have:
 
@@
 
-After substituting, we have:
+After substituting, I have:
 
@@
 
-Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:
+Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, I have:
 
@@
 
-And the function satisfies the increasing differences in $g$ and $N$ when the costs of govern an $N+1$-sized city council is lower than the costs of govern an $N$-sized city council:
+It is now clear to see that the function satisfies the increasing differences in $g$ and $N$ when the governing costs of a $N+1$-sized city council are lower than the governing costs of a $N$-sized city council:
 
@@
 
-This provides us our first empirical hypothesis to test: if the cost of govern decreases when the legislature increases, then the public goods provision increase when the legislature size increase.
-
-At this stage, we need to solve for the costs of govern to determine whether this hypothesis is true or not.
-Below we show that it is true for the *partisan* and *hybrid* mechanisms, but it is not true for the *non-partisan* mechanism.
+This provides the first empirical hypothesis to test: \textit{if the governing costs decrease when the legislature increases, then the public goods provision increase when the legislature size increase}.
+
+At this stage, I need to solve for the existence of these governing costs.
+Below I show that this proposition is valid for the *partisan* and *hybrid* mechanisms, but it is not suitable for the *non-partisan* mechanism.
 
@@
 
-In the \textit{non-partisan reversal} mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
-To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and we are at the $k$-th stage in the game.
-A councilor accepts the proposer's offer if, and only if, to accept the offer is better than to wait until the next stage.
+In the \textit{non-partisan reversal} mechanism, I assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
+To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and the game is at the $k$-th stage.
+A councilor accepts the proposer's offer if, and only if, to get the offer at $k$ is better than to wait until the next stage $k+1$.
 If the offer is $x_i$, then:
@@
 \[
-x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left( \dfrac{1}{2} \right)\left[ x_i \right]
-\]
-
-In the left-hand side, we place the offer.
-In the right-hand side, there are two components.
+x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left[\dfrac{1}{2} x_i \right]
+\]
+
+On the left-hand side, I place the offer.
+On the right-hand side, there are two components.
 The first is the amount that the councilor $i$ gets when she is the proposer.
-It is equal to the budget in the next round minus the offers that she has to make to convince half of the councilors.
-The second part is the gains if when the councilor happens to reject the current received offer, but still receives an offer in the following round.
-Note that the offer the councilor makes as the proposer is the same as the offer that she wants to receive.
-This because the city councilors are exchangeable, and the solution is symmetric for all councilors receiving an offer (this means that we could have dropped the $i$ in the solution).
+It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers she has to make to convince half of the councilors.
+The second part is the gains if the councilor rejects the current received offer but still gets an offer in the following round.
+It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the transfer amount.
+Note that the councilor's offer as the proposer is the same as the offer she wants to receive.
+This is because the city councilors are exchangeable.
+The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, I could have dropped the $i$ in the solution).
 After some algebra, the offer $x_i$ has to be greater than or equal to:
@@
 \[
-x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k)
-\]
-
-The proposer always offer the minimum possible to get the proposal approved. In the case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k)$.
+x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k, N)
+\]
+
+The proposer always offers the minimum required to get the proposal approved. In this case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.
 
 Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
-In this context, the costs of govern are equal to:
-
-\[
-C_G(N) \ = \ \dfrac{\delta R N}{2N + 1}
+In this context, the governing costs for the mayor are:
+
+\[
+C_G(N) \ = \ \dfrac{N}{2}\left[\dfrac{2 \delta R }{2N + 1}\right] \ = \ \dfrac{\delta R N}{2N + 1}
 \]
@@
 \begin{proposition}
-In the \textit{non-partisan reversal} mechanism, the costs of govern increase as the size of the legislature increases.
+In the \textit{non-partisan reversal} mechanism, the governing costs always increase when the size of the legislature increases.
 \end{proposition}
@@
 
-This result is crucial to understand the role of the politics in our model.
-If the costs of govern increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-In our case, we show that there is a \textit{political} reason for increasing the public goods provision.
+This result is crucial to understand the role of politics in my model.
+If the governing costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
+In my case, I show that there is a \textit{political} reason for increasing the public goods provision.
 
@@
 
-We now look into the other extreme, which is a fully politicized legislature.
+I now look into the other extreme, which is a fully politicized legislature.
 In this case, when the mayor implements the policy, it generates a value of $p > 0$.
 A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a cost of $-p$.
-Moreover, as in the case of the non-partisan reversal, the mayor can choose to distribute $x_i$ private goods for a legislator $i$.
-In this case, when the policy is implemented, the utility of an aligned legislator is equals to $x_i + p$.
-When the legislator is not aligned with the mayor, her utility is equals to $x_i - p$.
-If the policy is not implemented, then we assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
-
-A legislator aligned with the mayor always support the mayor's policy, regardless of receiving or not private goods.
-This because as $p > 0$, the councilor always receive positive benefits from the policy.\footnote{The mayor could even impose a cost to the city councilors aligned with the government.
-Although this seem unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office, or even take the popular fallout from a failed policy.} However, politicians not aligned with the mayor require a compensation when their votes are needed.
+Moreover, as in the non-partisan reversal, the mayor can choose to distribute $x_i$ private goods for a legislator $i$.
+In this case, when the policy is implemented, the aligned legislator's utility equals $x_i + p$.
+When the legislator is not aligned with the mayor, her utility equals $x_i - p$.
+If the policy is not implemented, then I assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
+
+A legislator aligned with the mayor always supports the mayor's policy, regardless of receiving private goods.
+This is because as $p > 0$, the councilor always receives positive benefits from the policy.\footnote{The mayor could even impose a cost to the city councilors aligned with the government.
+Although this seems unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office or even take the fallout from a failed policy.} However, politicians not aligned with the mayor require compensation when their votes are needed.
 In this case, if the mayor's proposal requires the support of an opposition politician, then the mayor compensates the councilor for the policy costs.
@@
 Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
-Then, the costs of govern when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor has to compensate minus the amount needed to implement the policy, in this case, half of them:
+Then, the costs of governing when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor has to compensate minus the amount needed to implement the policy, in this case, half of them:
 
@@
 
-This result shows that when the chances of electing an aligned politician is sufficiently high, then the costs of govern decrease.
-As a response, the public goods provision (and also rents), increase.
+This result shows that when the chances of electing an aligned politician are sufficiently high, the government costs decrease.
+As a response, the public goods provision (and also rents) increase.
 The rate distribution between these two vectors is determined by the marginal change in the utility from rents and the utility from reelection.
-In any case, the amount allocated for both increase.
+In any case, the amount allocated for both increases.
 
@@
 
-We can decompose these costs in two components.
-First, the costs in terms of rents.
+I can decompose these costs into two components—first, the costs in terms of rents.
 Second, the costs (or benefits) from political alignment.
-In this context, the governing costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's offers for councilors in the opposition.
-The ex-ante chance of a opposition member be elected is equal to $1-\gamma$, and taking the weighted averages, these costs become:
+In this context, the governing costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's proposals for councilors in the opposition.
+The ex-ante chance of an opposition member be elected equal to $1-\gamma$, and taking the weighted averages, these costs become:
 
@@
 
-The conditions for the differences in governing costs be decrease when the  legislature size increases is:
+The conditions for the differences in governing costs decrease when the legislature size increases are:
 
@@
 \begin{corollary}
-In the \textit{hybrid reversal} mechanism, public goods provision decreases as the legislature size increases.
+In the \textit{hybrid reversal} mechanism, when the chances of electing a city councilor aligned with the mayor are sufficiently high, then increasing council size lowers the bargaining costs for mayors.
 \end{corollary}
 
-Also, the threshold $\underline{\gamma}$ for the probability of electing a politician aligned with the government is decreasing in both the political value of the mayors policy $p$ and the size of the legislature $N$.
-This means that higher political values and larger legislatures makes it easier to satisfy the electoral threshold.
+The threshold $\underline{\gamma}$ for the probability of electing a politician aligned with the government is decreasing in the value of the mayor's policy $p$ and the legislature size $N$.
+This means that higher political values and larger legislatures make it easier to satisfy the electoral threshold.
 
@@
 
-Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators, that increase its council size to $N+1$. Then:
+Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators that increase its council size to $N+1$. Then:
 
 \begin{enumerate}
-  \item[H1. ] The provision of public goods increase when the governing costs decrease with legislature size.
-  \item[H2. ] The governing decrease with legislature size when the chance of electing a government aligned legislator is sufficiently high.
+  \item[H1. ] The governing costs decrease with legislature size when the chance of electing a government-aligned legislator is sufficiently high.
+  \item[H2. ] The provision of public goods increase when the governing costs decrease with legislature size.
 \end{enumerate}
 
-In the paper, we show that the provision of education and healthcare improves in Brazil, and this results from the fact that the chances of electing a city councilor aligned with the mayor is of 91%, thanks to the rule of distributing seats adopted in the country.
+In the paper, I show that the provision of education and healthcare improves in Brazil. This results from the fact that the chances of electing a city councilor aligned with the mayor are 91%.
 
@@
 
-We use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
+I use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
 
@@
 \label{varsources}
-\scalebox{0.75}{
+\scalebox{0.8}{
   \begin{tabular}{@{\extracolsep{5pt}}llll} 
@@
 
-Now let us define each variable.
-
 ### Outcomes Aggregated at the Municipal Level
@@
 \begin{itemize}
-\item \textbf{Number of Seats 2000}: Number of councilors in the municipality by the 2000 elections (source: TSE).
+\item \textbf{Number of Seats 2000}: Number of councilors in the municipality in 2000 (source: TSE).
 \item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
-\item \textbf{Per-Capita GDP Census 2000 (in millions)}: Municipal per-capita GDP computed by the IBGE Census (source: IPEA).
-\item \textbf{Proportion of Poverty Census 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a day (source: MDS).
+\item \textbf{Per-Capita GDP 2000 (in millions)}: Municipal per-capita GDP computed by the Brazilian Census (source: IPEA).
+\item \textbf{Proportion of Poverty 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a month (source: Social Development Ministry [MDS]).
 \item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
 \item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-\item \textbf{Post-Natal Mortality Rate 2005--2008}: Infant mortality computed as the number of children born alive that successfully lived 28 days, but died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-\item \textbf{Coverage Family Health Program 2005--2008}: Number of families covered by the Family Health Program (source: DataSUS).
-\item \textbf{Prop. Born w. 7+ Pre-Natal 2005--2008}: Proportion of children born who went to seven or more prenatal care consultations (source: DataSUS)
+\item \textbf{Postneonatal Mortality 2005--2008}: Infant mortality computed as the number of children that lived at least 28-days, but died before reaching one year of age divided by the number of children that reached 28-days alive, multiplied by 1,000 (source: DataSUS)
 \item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
-\item \textbf{Enrollment Middle School 2005--2008}: Number of children enrolled in middle schools, averaged by classroom size (5--9) (source: INEP)
 \item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed by the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
-The estimators are cleaned to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
-\item \textbf{Quality of Middle School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed by the student's grade in math and language, multiplied by a score capturing the distortion between the year the child is supposed to be in, and the year the child is studying.
-The estimators are cleaned to avoid the influence of schools and classrooms specific effects.
-(source: INEP, years: 2005, 2007).
+IDEB scores are composed of the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
+The INEP reweights the estimators to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
 \item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
 \item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
-\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of career bureaucrats in the municipality.
-Career bureaucrats cannot be fired by politicians and earn considerably better pensions after retirement (source: IBGE, years: 2005, 2006, and 2008)
-\item \textbf{Number of Councilor's Appointed Assistants 2005}: Number of assistants appointed for the councilor cabinet (source: InterLegis)
 \item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
-\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to city council.
-We collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: our compilation based on the TSE candidate pictures).
-\item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the number of city councilors in the municipality (source: TSE)
+\item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to the city council.
+I collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
+\item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the city council size (source: TSE)
 \item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
@@
 
-We coded the legislation approved by the councilors in 64 municipalities that are 10 thousand inhabitants away from the council size thresholds. We classified the legislation in five categories:
+I coded the legislation approved by the councilors in 63 municipalities within ten thousand inhabitants away from the council size thresholds. I classified the legislation into five categories:
 
 \begin{itemize}
-\item \textbf{Local Public Goods}: Legislation that provides a service targeted at the individual, group, or geographical level.
-\item \textbf{Public Goods or General Legislation}: Legislation that provides a service for the entire municipality, or approves a law that does not discriminate among citizens.
+\item \textbf{Public Goods}: Legislation that provides public goods or services.
 \item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
@@
 
-We run an online survey asking 174 councilors whether helping with [...service...] gives [none, few, some, or many] votes. The services were:
+I ran an online survey asking 174 councilors, among other questions, about their representation duties, which mayors used services to improve the mayor's coalition support. The services were:
 
 \begin{itemize}
-\item \textbf{Help Hospital Admission}: We asked former councilors whether helping with hospital admission gives [none, few, some, many] votes (source: survey).
-\item \textbf{Help School Admission}: We asked former councilors whether helping with school admission gives [none, few, some, many] votes (source: survey).
-\item \textbf{Help Getting Medication}: We asked former councilors whether helping voters get medication gives [none, few, some, many] votes (source: survey).
-\item \textbf{Fix Street Potholes}: We asked former councilors whether pressing the bureaucracy to fix street potholes gives [none, few, some, many] votes (source: survey).
-\item \textbf{Other Local Public Goods}: We asked former councilors whether helping voters with local public goods and services such as traffic rules, sewage constructions, potable water, and others, gives [none, few, some, many] votes (source: survey).
-\item \textbf{Legislative Duties}: We asked former councilors whether the act to discuss, propose, and vote on legislation gives [none, few, some, many] votes (source: survey).
-\item \textbf{Honors Legislation}: We asked former councilors whether proposing bills to praise local celebrities gives [none, few, some, many] votes (source: survey).
-\item \textbf{Oversee School Quality}: We asked former councilors whether overseeing school quality gives [none, few, some, many] votes (source: survey).
-\item \textbf{Oversee Construction}: We asked former councilors whether overseeing public construction gives [none, few, some, many] votes (source: survey)
+\item \textbf{Councilors Job Appointments}: The frequency that mayors appoint people allied to city councilors to bureaucratic jobs (source: survey).
+\item \textbf{Councilors Demands}: The frequency that mayors satisfy an allied councilors' demand (e.g., build a health clinic in a councilor's neighborhood) (source: survey).
+\item \textbf{Councilors Personal Requests}: The frequency that mayors satisfy an allied councilors' requests (e.g., hire an ally in the bureaucracy) (source: survey).
+\item \textbf{Councilors Legislation}: The frequency that mayors support councilors' legislative agenda (source: survey).
+\item \textbf{Councilors Constructions}: The frequency that mayors support councilors' requests for constructions (e.g., fix potholes in the councilor's neighborhoods) (source: survey).
 \end{itemize}
 
-In this Appendix, we present other questions we asked in the survey.
-They are meant to improve the knowledge we have about the city councilors perceptions about their representation.
-We have not added these to the main paper because they were more complimentary and not of general interest.
-The descriptive statistics of the variables used in the main paper follow in Table \ref{tabdescrvarspaper}.
-
-XXXX CHANGE HERE TABLE BELOW
+This Appendix presents other questions I asked in the survey.
+They are meant to improve my knowledge about the city councilors' perceptions of their municipality roles.
+I omitted these questions in the main paper because they are not of general interest to my argument.
+The descriptive statistics of the variables used in the main article follow in Table \ref{tabdescrvarspaper}.
 
@@
 \label{tabdescrvarspaper} 
-\resizebox{0.9\textwidth}{3.5in}{
+\resizebox{0.8\textwidth}{3in}{
 \begin{threeparttable}
@@
 Population 2000 & 5,474 & 22,341.96 & 44,573.67 & 697 & 567,728 \\ 
-Per-Capita GDP Census 2000 (in thousands) & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
+GDP Census 2000 & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
 Proportion of Poverty Census 2000 & 5,474 & 46.58 & 22.82 & 2.89 & 93.02 \\ 
@@
 & \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
-Infant Mortality 2005-2008 & 13,329 & 20.64 & 13.45 & 1.28 & 209.30 \\
-Post-Natal Mortality Rate 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
-Coverage Family Health Program 2005-2008 & 20,577 & 76.97 & 27.39 & 0.00 & 100.00 \\ 
-Prop. Born w. $6+$ Pre-Natal 2005-2008 & 16,578 & 54.02 & 24.30 & 0.57 & 100.00 \\ 
+Infant Mortality 2005-2008 & 13,328 & 20.64 & 13.45 & 1.28 & 209.30 \\ 
+Postneonatal Mortality 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\ 
 & \multicolumn{5}{c}{\textbf{Education Outcomes}} \\ \cline{2-6}
 Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\ 
-Enrollment Middle School 2005-2008 & 7,887 & 25.18 & 7.25 & 1.00 & 92.50 \\
-Quality of Elementary School Index 2005-2008 & 9,267 & 3.73 & 0.94 & 0.70 & 8.10 \\
-Quality of Middle School Index 2005-2008 & 5,566 & 3.21 & 0.76 & 0.30 & 6.60 \\
-& \multicolumn{5}{c}{\textbf{Resources and Patronage}} \\ \cline{2-6}
-Mayoral Coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\ 
-Number of Appointed Bureaucrats 2005-2008 & 16,564 & 67.78 & 126.68 & 0 & 2,894 \\ 
-Number of Career Bureaucrats 2005-2008 & 16,558 & 436.13 & 698.17 & 0 & 11,633 \\ 
-Number Councilor Assistants 2005 & 5,523 & 4.63 & 8.55 & 0 & 213 \\ 
+Quality of Elementary School Index 2005-2008 & 9,266 & 3.73 & 0.94 & 0.70 & 8.10 \\ 
+& \multicolumn{5}{c}{\textbf{Bargaining, Coalition, and Public Employment}} \\ \cline{2-6}
+Mayoral Pre-electoral coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\ 
+Number of Appointed Bureaucrats 2005-2008 & 16,563 & 67.77 & 126.68 & 0 & 2,894 \\ 
 & \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
-Proportion Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0.00 & 8.00 \\ 
-Proportion Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0.00 & 9.00 \\ 
+Number Female Elected 2004 & 5,526 & 1.12 & 1.20 & 0 & 8 \\ 
+Number Non-White Elected 2004 & 397 & 2.23 & 1.87 & 0 & 9 \\ 
 Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\ 
-Proportion Approved Legislation 2005 & 3,694 & 0.83 & 0.28 & 0.00 & 1.00 \\ 
+Proportion Approved Legislation 2005 & 3,693 & 0.83 & 0.28 & 0.00 & 1.00 \\ 
 & \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
-Legislation -- Local Public Goods & 346,553 & 0.73 & 0.44 & 0 & 1 \\ 
-Legislation -- Public Goods & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
+Legislation -- Public Goods & 346,553 & 0.76 & 0.43 & 0 & 1 \\ 
 Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
@@
 Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\ 
-& \multicolumn{5}{c}{\textbf{Survey -- Electoral Attractiveness of Services}} \\ \cline{2-6}
-Votes -- Help Hospital Admission & 174 & 0.82 & 0.38 & 0 & 1 \\ 
-Votes -- Help School Admission & 174 & 0.59 & 0.49 & 0 & 1 \\ 
-Votes -- Help get Medication & 174 & 0.71 & 0.46 & 0 & 1 \\ 
-Votes -- Fix Street Potholes & 174 & 0.49 & 0.50 & 0 & 1 \\ 
-Votes -- Local Public Goods & 174 & 0.81 & 0.39 & 0 & 1 \\ 
-Votes -- Legislive Duties & 174 & 0.22 & 0.42 & 0 & 1 \\ 
-Votes -- Honors Legislation & 174 & 0.18 & 0.38 & 0 & 1 \\ 
-Votes -- Oversee School Quality & 174 & 0.29 & 0.45 & 0 & 1 \\ 
-Votes -- Oversee Construction & 174 & 0.24 & 0.43 & 0 & 1 \\ 
+& \multicolumn{5}{c}{\textbf{Survey -- Strategy to Consolidate Coalition Support}} \\ \cline{2-6}
+Coalition Support -- Councilors Job Appointments & 174 & 0.64 & 0.48 & 0 & 1 \\ 
+Coalition Support -- Councilors Demands & 174 & 0.44 & 0.50 & 0 & 1 \\ 
+Coalition Support -- Councilors Personal Requests & 174 & 0.56 & 0.50 & 0 & 1 \\ 
+Coalition Support -- Councilors Legislation & 174 & 0.25 & 0.43 & 0 & 1 \\ 
+Coalition Support -- Councilors Constructions & 174 & 0.43 & 0.50 & 0 & 1 \\ 
 \bottomrule
@@
 \small
-\textbf{Notes:} The legislation approved dataset has data on 64 of the 202 municipalities 10 thousand inhabitants from the council size thresholds.
+\textbf{Notes:} The legislation approved dataset has data on 63 of the 202 municipalities 10 thousand inhabitants from the council size thresholds.
 The survey summary statistics here are unweighted.
@@
 
-### Threshold Manipulation, Sorting, and Pre-treatment Consistency
-
-The validity of our causal claim relies on three assumptions.
-First, the impossibility of municipalities to manipulate the placement at the left or right-hand side of the thresholds.
-Second, that we are consistently comparing municipalities in the same cutoffs.
-Lastly, that we have no pre-treatment differences in our sample.
+## Threshold Manipulation, Sorting, and Pre-Treatment Consistency
+
+The validity of the causal claim relies on three assumptions:
+
+\begin{enumerate}
+  \item That municipalities cannot sort themselves on the left or the right-hand side of the cutoffs by their choices.
+  \item That the regression models are consistently comparing cities in the adjacent cutoffs.
+  \item That I have no pre-treatment differences in the sample.
+\end{enumerate}
 
 For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
-For our research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
-
-We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
-We use local polynomial orders from one to four.
+For my research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
+
+I run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
+I use local polynomial orders from one to four.
 As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
@@
 
-We also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
+I also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
 
@@
 
-For the second assumption, we know that running RDD in multiple thresholds may lead to inconsistent estimates when there is an imbalance in the running variable's distribution around the cutoffs \citep{Bertanha2015, Cattaneo2016, eggers2018regression}.
-For example, in our dataset, we have twelve discontinuities, and at each threshold, we have a sharp increase of one councilor, from 9 to 21.
-When running an RDD on these discontinuities, a consistent estimator should fit an exact change of one councilor.
-However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors.
-This imbalance is because when we combine all the discontinuities, we are implying that changes in municipalities right below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
-That is incorrect, not only because we could be comparing a municipality with nine councilors with one with 21 councilors, but also because these municipalities diverge in many other aspects, such as population to GDP per capita.
-
-To avoid this problem, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
-Relying on this fact, we add five controls to our estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
-The reason for the first variable is the multiple threshold assignments.
-We add GDP per capita because wealthier cities tend to be more productive and have better public services.
-The number of seats in 2000 intends to control for the fact that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
-The year and the northeast dummies serve to improve efficiency.
-Adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.
-See the following section for further tests and simulations.
-
-For the last assumption, we should have no changes in pre-treatment covariates.
-These pre-treatment covariates are variables measured before the primary outcomes.
-As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
-
-Table \ref{validitycheck} displays the results of the validity checks.
-At the top of the table, we run the first-stage regressions, both using and not using the controlling covariates strategy proposed, for both real and the placebo cutoffs.
-At the bottom, we estimate the pre-treatment covariate balance.
-
-XXXX CHANGE THIS
-
-\begin{table}[htb!] \centering 
-  \caption{Research Design Validity Check} 
-  \label{validitycheck} 
-    \scalebox{0.9}{
-  \begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
-\toprule
- & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- First Stage}} \\ \cline{2-5}
-   & \multicolumn{1}{c}{\small{(1)}} & 
- \multicolumn{1}{c}{\small{(2)}} & 
- \multicolumn{1}{c}{\small{(3)}} & 
- \multicolumn{1}{c}{\small{(4)}} \\
-
- & \multicolumn{1}{c}{\small{Additional Num.}} & 
- \multicolumn{1}{c}{\small{Placebo Add.}} & 
- \multicolumn{1}{c}{\small{Additional Num.}} & 
- \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
-  & \multicolumn{1}{c}{\small{Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Seats 2004}} & 
-  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
-  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
-  \multicolumn{1}{c}{\small{(Without Controls)}} & 
-  \multicolumn{1}{c}{\small{(With Controls)}} & 
-  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-\\[-1.8ex] 
- LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
-  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
-\hdashline \\[-1.8ex]   
- N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
-Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
-Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
-BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
-BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
-\midrule 
- & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{(5)}} & 
- \multicolumn{1}{c}{\small{(6)}} & 
- \multicolumn{1}{c}{\small{(7)}} & 
- \multicolumn{1}{c}{\small{(8)}} \\
-  & \multicolumn{1}{c}{\small{Number of}} & 
- \multicolumn{1}{c}{\small{Population}} & 
- \multicolumn{1}{c}{\small{GDP}} & 
- \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
-  & \multicolumn{1}{c}{\small{Seats 2000}} & 
-  \multicolumn{1}{c}{\small{2000 Census}} & 
-  \multicolumn{1}{c}{\small{2000 Census}} &
-   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
-  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
-  \hdashline \\[-1.8ex]
- N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
-Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
-Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
-BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
-BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
-\bottomrule
-\end{tabularx}
-\begin{tablenotes}
-\small
-\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
-RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, in parentheses.
-Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
-\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
-\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
-\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
-\textit{BW Bias} is the Bandwidth used to compute the standard errors.
-\end{tablenotes}
-\end{threeparttable}}
-\end{table}
-
-Notice that without controls, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
-After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
-Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
-These tests reinforce the validity of our research designs.
-
 \pagebreak
@@
 The identification strategy requires exogenous changes in the city council size thresholds.
-Previous to the changes we exploit here, the 1988 Brazilian Constitution states the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
+Previous to the changes I exploit here, the 1988 Brazilian Constitution stated the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
 
@@
 The two losing councilors started a judicial contestation that made it to the Supreme Court.
-The court ruled that the Constitution meant that council size should vary proportionally with population, starting with nine legislators, until the maximum number of councilors, 55.
-Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds that should be followed in the 2004 election (Resolution 21,702/2004).
+The court ruled that the Constitution meant that council size should vary proportionally with population, beginning with nine legislators, until the maximum number of councilors, 55.
+Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds for the 2004 election (Resolution 21,702/2004).
 According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
@@
 
-As there are few municipalities above one million inhabitants, we decided to restrict our attention to municipalities with less than $571,429 + 47,619 = 619,048$ inhabitants.
-Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in our paper.
+As there are few municipalities above one million inhabitants, I decided to restrict the attention to cities with less than $571,429 + 47,619 = 619,048$ inhabitants.
+Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in my paper.
 
@@
 
-The Supreme Court ruled that the electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
-In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) propose the official population projections.
-Sorting is not an issue for our identification strategy, as IBGE is an insulated bureaucracy, insulated from local influences (see also the McCrary test above).
+The Supreme Court ruled that the electoral courts use the 2003 population projection to assign municipalities to cutoffs.
+In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) proposes the official population projections.
+Sorting is not an issue for my identification strategy, as IBGE is an insulated bureaucracy from local influences (see also the McCrary test above).
 
 To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity from the cutoffs.
-In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds.
-The darker the color, the closer to the population thresholds.
-In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation.
-Figure \ref{sampleplot} also shows that our municipalities are reasonably distributed around the whole country.
-
-XXXX CHANGE
+In the map, I give the contour of every Brazilian city, coloring it by the proximity to the council size thresholds.
+Darker colors represent municipalities closer to the population thresholds.
+In regression discontinuity, the closer a city is to the cutoff, the more influential it is in the estimation.
+Figure \ref{sampleplot} also shows that the municipalities are reasonably distributed around the whole country.
+
+\pagebreak
 
@@
 
-\pagebreak
-
-Moreover, we could question whether the discontinuities studied here are sharp or fuzzy.
-In order to be fuzzy, the laws passed by the Supreme Court had to be contested or not be perfectly enforced.
-For instance, \citet{cavalcanti2017essays} shows in his second chapter that there has been a misuse of these discontinuities.
-However, this problem was absent in our RDD, as the problem identified by Cavalcanti was based on the use of thresholds approved in 2009.
-In our case, we use the thresholds approved in 2003, and until a period before 2009 (in our case, 2008).
-
 \newpage
@@
 
-Usually when carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes.
+When carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes \citep{cattaneo2016interpreting}.
 Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
@@
 The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
-To ensure we have comparability, and that we estimate the average LATE for all cutoffs, avoiding most of the heterogeneity, we propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
+To ensure comparability, I estimate the average LATE for all cutoffs, avoiding most of the heterogeneity.
+I propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
 For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
-As the population varies smoothly around each cutoff, it makes it a perfect control to add.
+As the population runs smoothly around each cutoff, it makes it a perfect control to add.
 The new estimator is:
@@
 
-We control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
-All these control variables are smooth in each cutoff, but are significantly different from cutoff to cutoff, making them adequate control variables for our case \citep{calonico2019regression}.
-To perform the estimations, we use a triangular kernel, which places more weight on the municipalities that are closer to each cutoff.
-To compute the optimal bandwidth, we use the \citet{CCT2014} method.
-To study the sensitivity to the bandwidth choice, we vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
-We also use cluster-robust standard errors at the municipal level.
-
-However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why in this case is it advisable?
-To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment not only helps improve the consistency of our estimates but also improves their efficiency.
+I control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
+All these control variables are smooth in each cutoff but are significantly different from cutoffs, making them adequate control variables for this case \citep{calonico2019regression}.
+To perform the estimations, I use a triangular kernel, which weighs the municipalities closer to each cutoff.
+To compute the optimal bandwidth, I use the \citet{CCT2014} method.
+To study the sensitivity to the bandwidth choice, I vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
+I also use cluster-robust standard errors at the municipal level.
+
+However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why, in this case, is it advisable?
+To answer this question, I run a series of simulations to show that controlling for the variable that determines the assignment helps improve the consistency of the estimates and improves their efficiency.
 
 Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
-We add nine thresholds, at 0.1, 0.2, and so on until 0.9, and we create six types of outcomes.
+I add nine thresholds, at 0.1, 0.2, and so on until 0.9, creating six types of outcomes.
 The first three outcomes are sharp changes.
-In the first, we add variation from one to 10, with one step for each change.
-In the second, we add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
+In the first, I add variations from one to 10, with one step for each shift.
+In the second, I add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
 The estimated change should be equal to zero.
-In the third model, we add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
+In the third model, I add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
 This is intended to simulate a diminishing effect from one cutoff to the other.
-The last three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
-We then run a thousand Monte Carlo simulation for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
-
-XXXX CHANGE
+The previous three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
+I then run a thousand Monte Carlo simulations for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
 
@@
 The first three models should present a more efficient estimation than the last three models.
-We display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
-
-XXXX CHANGE
+I display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
 
@@
 
-## Placebo Regressions for the Aggregated Mechanism Outcomes
+## Placebo Regressions for Political Mechanism
 \label{placmechmain}
 
-Here we present the placebo regressions for the mechanism-aggregated outcomes.
-In Panel A of the main paper, we run the regression on alternative explanations.
-As we can see, the only female changed significantly, but the change is statistically expected in at least 10\% of cases.
-For non-white, we have not collected data on non-white legislators in the placebo cutoffs; therefore, we leave it blank.
-In Panel B, we have the placebo regressions for the primary mechanism: resource access and patronage.
-As expected, the placebo regressions were not statistically significant.
-
-XXXX CHANGE
+Here I present the placebo regressions for the mechanism-aggregated outcomes.
+In Panel A of the main paper, I run the regression on alternative explanations.
+Only the number of female councilors changed significantly, but a change is statistically expected in at least 10\% of cases.
+I have not collected data on non-white legislators in the placebo cutoffs; therefore, I leave it blank.
+In Panel B, I have the placebo regressions for the primary mechanism: bargaining costs and public appointed employees.
+As expected, the placebo regressions were statistically insignificant.
 
 \begin{table}[!htbp] \centering 
-\caption{Mechanism -- Aggregate Municipal Level Regressions} 
+\caption{Political Effects of Legislature Size -- Placebo Cutoffs} 
 \label{placresmechreg1} 
@@
 \toprule
- & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections -- Placebo Cutoffs}} \\ \cline{2-5}
+ & \multicolumn{4}{c}{\textbf{Panel A: Representation and Elections}} \\ \cline{2-5}
 & \multicolumn{2}{c}{\textbf{Representation}} & 
@@
   & (0.27) &  & (0.48) & (0.06) \\ 
-  N Left & 4620 &  & 4621 & 2991 \\ 
+ N Left & 4620 &  & 4621 & 2990 \\ 
 N Right & 906 &  & 906 & 703 \\ 
-  Eff N Left & 412 &  & 567 & 356 \\ 
-  Eff N Right & 297 &  & 347 & 229 \\ 
-  BW Loc Poly & 4.861 &  & 6.113 & 5.58 \\ 
-  BW Bias & 8.775 &  & 10.345 & 8.896 \\ 
+Eff N Left & 414 &  & 567 & 356 \\ 
+Eff N Right & 298 &  & 347 & 229 \\ 
+BW Loc Poly & 4.874 &  & 6.104 & 5.583 \\ 
+BW Bias & 8.789 &  & 10.312 & 8.89 \\ 
 \midrule
- & \multicolumn{4}{c}{\textbf{Panel B: Resource Access and Patronage -- Placebo Cutoffs}} \\ \cline{2-5}
+ & \multicolumn{4}{c}{\textbf{Panel B: Bargaining, Coalition, and Public Employment}} \\ \cline{2-5}
  & \multicolumn{1}{c}{\small{Mayoral}} & 
  \multicolumn{1}{c}{\small{Num. Politically}} & 
- \multicolumn{1}{c}{\small{Num. Career}} & 
- \multicolumn{1}{c}{\small{Num. Councilor}} \\
+ & \\
  & \multicolumn{1}{c}{\small{Coalition Size}} & 
- \multicolumn{1}{c}{\small{Appointed Empl.}} & 
- \multicolumn{1}{c}{\small{Bureaucrats}} & 
- \multicolumn{1}{c}{\small{Assistants}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.12 & 3.77 & 115.67 & -2.17 \\ 
- & (0.34) & (17.20) & (79.96) & (1.81) \\ 
- N Left & 4618 & 13855 & 13850 & 4618 \\ 
- N Right & 904 & 2709 & 2708 & 905 \\ 
- Eff N Left & 644 & 1123 & 1464 & 592 \\ 
- Eff N Right & 388 & 825 & 957 & 361 \\ 
- BW Loc Poly & 6.730 & 4.475 & 5.461 & 6.279 \\ 
- BW Bias & 10.421 & 7.600 & 9.999 & 10.944 \\ 
+ \multicolumn{1}{c}{\small{Bureaucrats}} &  & \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.13 & -0.58 & & \\ 
+  & (0.33) & (17.14)  & & \\ 
+ N Left & 4618 & 13854  & & \\ 
+N Right & 904 & 2709  & & \\ 
+Eff N Left & 654 & 1345  & & \\ 
+Eff N Right & 394 & 915  & & \\ 
+BW Loc Poly & 6.813 & 5.127  & & \\ 
+BW Bias & 10.501 & 8.194  & & \\ 
 \bottomrule
@@
 
-We present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
-
-XXXX CHANGE
+I present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, I vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
 
@@
 
-In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
-
-\pagebreak
-
-XXXX CHANGE
+In Figure \ref{placgraphbw}, I run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
+
+\pagebreak
 
@@
       \centerline{\includegraphics[width=5in,angle=0]{../figures/placBwSens.pdf}}
-      \caption{Placebo Regressions -- Bandwidth Sensitivity}
+      \caption{Bandwidth Sensitivity -- Placebo Regressions}
       \bigskip
@@
 
-## Sensitivity to Different States in the Analysis
+## Sensitivity to Brazilian States Characteristics
 \label{sensstate}
 
-The literature considers that some states are more prone to inefficiencies than the rest of the country.
-Moreover, some states had such poor Health Care and Education systems that they could be driving the results by themselves.
-As a consequence, our results could be a byproduct of structural changes in crucial states, instead of in council size.
-We run the analysis dropping one state at a time, to investigate this statewide heterogeneity.
+The literature about Brazil recognizes that the country presents considerable variability.
+Moreover, some states had such poor Health Care and Education systems that they could be driving our results.
+I run the analysis dropping one state at a time to investigate this statewide heterogeneity.
 The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
 
-To interpret the results, first, note that most coefficients remain around the same value as before the robustness checks.
-The exceptions are with the Family Health Program, which improves without Para\'{i}ba but decreases significantly without Bahia, both northeastern states.
-In the placebo, the FHP coverage increases when we remove Bahia and decrease when we add S\~{a}o Paulo.
-Otherwise, note that all the other variables remain unchanged, except for gender.
-Gender changes because there were laws during this period mandating a minimum amount of female candidates.
-It is expected that one variable changes as a response to randomness.
-
-\pagebreak
-
-XXXX CHANGE
+First, note that for infant mortality and education enrollment, all coefficients remain significant upon the removal of the state.
+For postneonatal mortality, the coefficient loses significance when removing Bahia, Pernambuco, Rio Grande do Norte, and Rio Grande do Sul.
+The mayoral coalition size remains significant in most models, losing significance when removing Rio Grande do Norte and Sao Paulo.
+The number of appointed employees lose significance when removing Espirito Santo and Sao Paulo.
+All the alternative mechanism models are insignificant, regardless of the state removed.
+
+\pagebreak
 
@@
 
-XXXX CHANGE
-
 \begin{figure}[htb!]
@@
 
-In the paper, we run all the regressions using local linear polynomials.
+In the paper, I run all the regressions using local linear polynomials.
 \citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
 
-However, we run here all the models using polynomials from local linear to a quartic, showing that our results are robust to different regression functional forms.
-With two exceptions, the results are mostly consistent.
-First, quadratic and cubic polynomials make the significance go away in some models.
-Second, quartic polynomials seem to make the Family Health Program (FHP) significant and negative, which goes in line with our theoretical predictions.
+However, I run all the models using polynomials from local linear to a quartic, showing that my results are robust to different regression functional forms.
+The results are similar in all models, with significance changing only in the quartic polynomials.
 Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
@@
 
-The control variables play an essential role in our model.
-As we argued before, without controls, the first stage is inconsistent, and we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
-
-However, if the selection of controls makes the models overestimate quantities in the directions our narrative emphasizes, this would pose a considerable credibility issue for our analysis.
-To study the sensitivity to controls, we run the same regressions for all possible control combinations.
+The control variables play an essential role in my model.
+As I argued before, without controls, the first stage is inconsistent, and I may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
+
+However, if the selection of controls makes the models overestimate quantities in the directions my narrative emphasizes, this would pose a significant credibility issue for my analysis.
+To study the sensitivity to controls, I run the same regressions for all possible control combinations.
 Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
-The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003\_2}, population in 2003 (underscore 2 means that is population by thousands); and \textit{year}.}
+The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003}, population in 2003; and \textit{year}.}
 
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov.pdf}}
+      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov1.pdf}}
       \caption{Sensitivity Analysis for the Control Variable's Choices}
@@
 
-For instance, changes in controls have a substantial effect on the detected differences in the Family Health Program coverage, as well as in Elementary Education Quality.
-
-In our view, our choice was the most conservative, as the Full Model is significant when most of the combinations also are significant.
-Otherwise, our model is not significant when most combinations are also insignificant.
-Regarding the point estimates, our analysis chooses the smaller coefficient sizes systematically for the significant variables.
-
-We also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
-The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm these expectations.
+\begin{landscape}
+\begin{figure}[htb!]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov2.pdf}}
+      \caption{Sensitivity Analysis for the Control Variable's Choices}
+\bigskip
+\label{graphsenscontrol2}
+\end{minipage}
+\end{center}
+\end{figure}
+\end{landscape}
+
+For instance, changes in controls substantially affect the detected differences in Elementary Education Quality, making some combinations of controls fit a positive effect on education quality.
+However, most combinations of controls were insignificant in this variable.
+
+My choice of full controlled model was the most conservative.
+This is because the Full Model is significant only when most of the combinations also are significant.
+Regarding the point estimates, my choices of controls tend to keep the models with smaller coefficient sizes.
+
+I also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
+The theoretical expectations here are that most of these outcomes would fail, and the graphs confirm these expectations.
 
@@
 
-To study the sensitivity to the number of cutoffs, as well as a possibility of diminishing returns from the additional legislator, we run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
+To study the sensitivity to the number of cutoffs and the possibility of diminishing returns from the additional legislator, I run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
 This strategy is similar to adding one cutoff at a time.
-The results are stable and do not change our main conclusions.
-Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns are occurring.
+The results are stable and do not change the main conclusions.
+Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns were occurring.
 Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
@@
 
-Two alternative explanations could confound our results.
-First, the selection of the mayor could be affected by the city council size, and then the welfare improve by the quality of the mayor, and not by the partisan mechanism described.
-Second, the partisan mechanism could be confounded by an argument similar to the @Weingastetal1981 ``law of 1/n'', and the improvements in welfare could have been a result of higher revenues.
-This section shows that none of these concerns are true in our case.
-
-\subsubsection{Mayoral characteristics}
-
-We select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
-The results show no variation on council size and mayoral characteristics.
+Two alternative explanations could confound the results.
+First, the mayor's selection could be affected by the city council size, and then the welfare improves by the quality of the mayor, not by the partisan mechanism described.
+Second, the partisan mechanism could be confounded by an argument similar to the @Weingastetal1981 ``law of 1/n'', and the improvements in welfare could have resulted from higher revenues.
+This section shows that none of these concerns are true in my case.
+
+\subsubsection{Mayors' characteristics}
+
+I select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
+The results show no variation in council size and mayoral characteristics.
 
@@
 
-We run the regressions on federal transfers and revenue raised within the municipalities.
-There is only a small effect on education transfer, barely significant at 10%.
+I run the regressions on federal transfers and revenue raised within the municipalities.
+There is only a negligible effect on education transfer, barely significant at 10%.
 The other indicators remain insignificant.
-Note that the placebo are significant, and this actually reinforce the claim that the education effect may be spurious.
+Note that the placebo is significant, which reinforces the claim that the education effect may be spurious.
 
@@
 
-\subsection{Legislation Dataset\label{legdfr}}
-
-In the Fall of 2018, we collected the data on the legislation approved by the city council of 64 municipalities 10 thousand inhabitants away from the thresholds.
-There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 64 had information on the legislation for the period between 2005 to 2008.
-
-To classify the legislation, we hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases.
-First, we train and test the accuracy of the SVM classifier on 80\% of the dataset.
-Then, we ran the training on the full hand-coded data and predicted the remaining.\footnote{We tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
-We choose SVM as it gives the highest prediction rate.
-We are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
-
-We hand-coded using five characteristics:
+\subsection{Legislation Dataset}
+
+In the Fall of 2018, I collected the data on the legislation approved by the city council of 63 municipalities 10 thousand inhabitants away from the thresholds.
+There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 63 had information on the legislation between 2005 to 2008.
+
+I hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases to classify the legislation.
+First, I train and test the accuracy of the SVM classifier on 80\% of the dataset.
+Then, I ran the training on the complete hand-coded data and predicted the remaining.\footnote{I tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
+I choose SVM as it gives the highest prediction rate.
+I are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
+
+I hand-coded using four characteristics:
 
@@
 Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
-To lay on this category, the service should have been targeted for a fraction of the population.
-\item \textbf{Public Goods and Legislation}: Whether a bill is about a municipal public good (e.g., improving education), or about legislation that does not discriminate against any citizen within the polity (general law).
 \item \textbf{Oversight}: Legislation requesting information on the status of service provision.
@@
 
-We run the SVM on the hand-coded data.
-Table \ref{accurClassif} shows the classification accuracy for each of the variables that we hand-coded.
-In all models, we set cost equals 10 to avoid overfitting.
-
-\begin{table}
+I run the SVM on the hand-coded data. Table \ref{accurClassif} shows the classification accuracy for each of the variables that I hand-coded. In all models, I set cost equals 10 to avoid over-fitting.
+
+\begin{table}[htb!]
 \centering
@@
 Local Public Goods           & 93.8               \\
-Public Goods and Legislation & 94.2               \\
 Oversight                    & 94.9               \\
@@
 
-After we classify all the bills, the frequency in each category was added to the main paper.
-We also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
-As expected, the results changed little from when we considered the absolute values.
+After I classify all the bills, the frequency in each category was added to the main paper.
+I also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
+As expected, the results changed little from when I considered the absolute values.
 
@@
 
-From November 21st to December 1st, 2016, we surveyed former city councilors that served in the 2005 to 2008 period.
-We asked them questions regarding how mayors secure electoral support, which services are common in the city councilor's practice, and which services give the highest electoral yield.
-
-We used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
-In December 1st we closed the pool, having 174 responses.
+From November 21st to December 1st, 2016, I surveyed former city councilors that served in the 2005 to 2008 period.
+I asked them how mayors secure electoral support, which services are standard in the city councilor's practice, and which services give the highest electoral yield.
+
+I used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
+On December 1st, I closed the pool, having 174 responses.
 Figure \ref{geodistrsurv} displays a distribution of responses.
@@
 
-To weight the survey, we use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the legislative.
-We use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, re-weighting the collected data to match the population proportions.
-We use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
+To weight the survey, I use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the bodies in Brazil.
+I use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, reweighting the collected data to match the population proportions.
+I use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
 In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
@@
 
-The questions of interest for this research, asked in the survey were:
+The questions of interest for this research asked in the survey were:
 
@@
 The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
-Figure \ref{commonservice} shows the results for each of the activities we studied the electoral yield.
+Figure \ref{commonservice} shows the results for each of the activities I studied the electoral yield.
 
@@
 
-The last question measures the willingness of mayors to give services to city councilors.
-This question is relevant, as mayors control most of the bureaucracy and the mediation of services requires a good relationship with mayors.
-Figure \ref{mayorneg} shows the results for the mayoral activities.
-
-\begin{figure}[htb!]
-\begin{center}
-\begin{minipage}{1 \linewidth}
-\centerline{\includegraphics[width=6.5in,angle=0]{../figures/strategySupportMayors.pdf}}
-\caption{Mayor negotiated services in exchange of support}
-\bigskip
-\label{mayorneg}
-\end{minipage}
-\end{center}
-\end{figure}
-
-Therefore, both Figures show that councilors do perform the tasks that give the most electoral yield.
-The exception is the category of honor legislation, which most legislators seem to perform, even though they acknowledge that it provides little electoral returns.
-
-Regarding the services that mayors use to negotiate with the coalition, note that jobs in exchange of support are the highest ranked strategy by councilors.
-Our results capture that, as an increase in city council size has a positive effect on the number of appointed employees in the municipality.
+\pagebreak

### 2021-09-05 article/article.Rmd
changes paper

@@
 All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
-abstract: "What is the effect of legislature size on social welfare?
-While the literature suggests that increasing the number of legislators broadens political representation and raises government expenditures, its implications for public service provision remain understudied.
-In this paper, we exploit exogenous changes in city-council size in Brazil and show that adding a legislator increases education and healthcare indicators.
-XXXX Education quality and preventive health care remain unaffected, but primary school enrolment and infant mortality significantly improve.
-To investigate the mechanism, we surveyed former councillors and analysed 346,553 bills proposed between 2005 and 2008.
-This analysis shows that politicians prefer to provide private and targeted goods instead of public goods.
-This paper has implications for the design of legislative institutions."
+abstract: "What is the effect of the number of legislators on public service provision?
+Despite the importance of institution designs for young democracies, little is known about the particular features that may help improve welfare.
+This paper uses a formal model to show how increasing legislature size may affect service provision.
+I show that changes in bargaining costs depend on whether the additional legislator shares the Executive's party affiliation: More opposition members reduce the Executive's equilibrium public goods provision, while more government-aligned members increase it.
+I test this theory by exploiting sharp discontinuities in city council size in Brazil.
+I show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, significantly improving primary school enrollment and infant mortality.
+To investigate the mechanism, I surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008.
+This paper has implications for the design of representative institutions."
 abstractspacing: double
-keywords: Legislature size; Legislative politics; Public goods provision; Regression discontinuity design; Brazil
-jelcodes: HXXXX
+keywords: Legislature Size; Legislative Bargaining; Local Public Goods Provision; Regression Discontinuity Design; Brazil
+jelcodes: H41; H80; I31; I38
 fontsize: 11pt
@@
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
-# XXXX
-```
-
 [^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
@@
 Legislative institutions are crucial for welfare and service provision in democratic countries.
-Historically, the division of power and the birth of a representative government placed the legislatures at the center of popular consent \citep{north1989constitutions}.
+Historically, the division of power and the birth of a representative government placed the legislatures at the center of popular consent.
 In modern democracies, most countries have assemblies at all levels of government.
-These institutions affect the information and quality of legislation \citep{krehbiel2010information}, check and veto the other political powers \citep{tsebelis2002veto}, and influence policymaking \citep{weingast1988industrial, north1989constitutions, auriol2012optimal}.
-Moreover, they also determine taxation, government expenditure \citep{Weingastetal1981, PrimoSnyder2008, stasavage2011states}, and oversee service provision \citep{mccubbins1984congressional, poulsen2018political}.
+These institutions affect the information and quality of legislation, check and veto the other political powers, and influence policymaking.
+Moreover, they also determine taxation, government spending and oversee service provision \citep{Weingastetal1981, weingast1988industrial, north1989constitutions, auriol2012optimal, stasavage2011states, poulsen2018political}.
 
 Regardless of differences in electoral rules, social composition, and procedures, all legislatures share one feature: more than one representative composes them.
-Legislature size relates to collective action problems \citep{crain1979cost, rogers2002free}, government spending \citep{Weingastetal1981, PrimoSnyder2008}, and representation \citep{allenrepresentation}, but how these components affect welfare remain understudied.
-On the one hand, enlarged legislatures increase government spending and lawmaking, and this may improve some services \citep{Weingastetal1981, }.
-On the other hand, adding a legislator can increase the number of veto players and broaden the collective action problems, hindering service provision.
-Therefore, larger legislatures have an ambiguous effect on welfare, and XXXX.
+Legislature size relates to collective action problems, bargaining between political powers, government spending, and representation, but how these components affect welfare remain understudied \citep{crain1979cost, Weingastetal1981, rogers2002free, PrimoSnyder2008, allenrepresentation}.
+On the one hand, enlarged legislatures may increase government spending and lawmaking, and this could improve some services \citep{Weingastetal1981}.
+On the other hand, adding a legislator may increase the number of veto players and broaden the collective action problems, hindering service provision \citep{tsebelis2002veto, gottlieb2019countervailing}.
+Therefore, what is the effect of increasing the legislature size on public service provision?
 
-In this paper, we propose a theory of legislature size and welfare that takes into account two crucial components: the XXXX and the partisan affiliation of the legislators.
+In this paper, I propose a local legislature size and welfare theory that incorporates two crucial features: Executive leadership and party politics.
+First, in mayor-council municipalities, mayors tend to be central in the local public service decisions.
+Mayors have the prerogative in proposing public investments, much as presidents in presidential systems.
+Second, partisanship is essential at the local level, even in settings where the ideological attachment is weak, such as in most young democracies.
+Party attachment helps structures political views \citep{samuels2014power}, and local-level elites usually belong to different factions and parties.
+They fight for power in the municipality by controlling various parties and forming distinct pre-electoral coalitions.\footnote{Elite political competition in the local level has also been linked to violence and conflict in Brazil and elsewhere \citep{hoelscher2015politics, mignozzetti2018predatory}.} In most cities, family ties are substitutes for the ideological component, but the most influential local leaders sort themselves in different political groups \citep{nunes1977coronelismo, ferraz2020political}.
 
-XXXX Umberto: Parei aqui.
+This paper incorporates partisanship and mayoral first-move advantage to a \citet{baron1989bargaining} bargaining model.
+Mayors make the initial policy proposal that consists of an investment in public goods provision, a decision to extract rents for personal gains, and a vector of side-transfers for councilors.
+If they fail to secure majoritarian support from councilors, a reversal stage occurs, where the decision leaves the mayor's office, and councilors then propose the public investments.
+In this mayor-council bargaining, costs come from the side-transfers required to secure a majority among councilors.
+I show that in a model without partisan concerns, bargaining costs always increase with larger city council size, lowering public goods provision and rents.
+However, adding partisanship decreases the bargaining costs when the chances of electing councilors aligned with the mayor are sufficiently high.
+Lower bargaining costs release funds for mayors to invest in public goods provision.
+In this case, a larger city council may have more partisan councilors aligned with the mayor, lowering the mayor's bargaining costs and increasing the equilibrium public goods provision.
 
-This paper fills this gap by studying the effects of legislature size on service provision.
-Assuming that politicians want to further their careers, we argue that two variables determine service provision: the perceived importance of the service by voters and the politician's capacity to claim credit for its provision.
-Politicians perform a simple cost-benefit analysis: if providing a service results in high electoral yield, and it is easy to claim credit for, politicians will produce this service abundantly.
-When a service is hard to claim credit for, politicians only invest their time if it is highly preferred by voters.
-Finally, when services are both hard to claim credit for and of low importance to voters, they are placed at the bottom of the politicians' priorities.
+I test these theoretical predictions by exploiting an exogenous variation in Brazilian city council sizes.
+In 2004, the judiciary reinterpreted the Constitution, unexpectedly changing the number of city councilors.
+Before the decision, towns could freely choose their legislature size, but in March 2004, the Superior Electoral Court created population thresholds, adding one councilor for each set of 47,619 inhabitants.
+Around these cutoffs, the decision represented an exogenous change in city council size, allowing me to investigate the effects of increasing the number of local legislators in Brazil.
 
-To test this theory, we exploit an exogenous variation in Brazilian city council sizes.
-In 2004, the judiciary reinterpreted the constitution, unexpectedly changing the number of city councilors in Brazilian municipalities.
-Before the decision, towns could freely choose their legislature size, but in March 2004, the Superior Electoral Court created population thresholds, adding one councilor for each set of 47,619 inhabitants.
-Around the cutoffs, this decision represents an exogenous change in city council size, allowing us to investigate the welfare effects of increasing the legislatures in Brazil.
+Studying 2005 to 2008 Brazilian mayoral term, I find that increasing city council size changed the composition of the mayoral coalition and the number of appointed bureaucrats in the municipality.
+The extra city councilor had a 91 percent chance of belonging to the mayor's pre-electoral coalition.
+This enhanced chances of electing a councilor connected with the mayor decreased the bargaining costs for the mayor, freeing investments for public services.
+Moreover, the number of appointed bureaucrats increased by 104 with the additional councilor.
+In Brazil, more appointed bureaucrats lead to higher quality workers, better service provision, and more accountability \citep{toral2019benefits}.
 
-Studying the 2005 to 2008 Brazilian mayoral term, when the ruling was in effect, we find improvements in health care and education.
-Increasing the council size by one legislator lowers infant mortality by 1.99 per one thousand infants born and increases elementary school enrollment by 2.58 children in kindergarten classrooms.
-However, the additional legislator had no influence on preventive health care and education quality.
-[] Voters place a high electoral premium on hospital care and mediating school enrollment is relatively easy to claim credit for.
-In line with our theoretical model, these services should improve with legislative size.
-On the other hand, preventive health care is harder to claim credit for, and school quality improvements are expensive and pay off only in the long-run.
-Thus, these services remain unchanged with larger legislatures.
+More support for the mayors and more politically appointed bureaucrats correlate with city councilors' service provision expectations and legislation approved in Brazilian municipalities.
+I surveyed 174 former councilors who served during the 2005-2008 term, and they corroborate that mayors use bureaucratic appointments and granting favors to secure support.
+As the formal model shows, bargaining with councilors has a resource transfer component.
+By investigating what councilors prefer to provide to voters, I find that councilors demand job appointments, as these are helpful for their reelection chances and improve municipal welfare.
+These findings align with a novel dataset I build with 346,553 laws passed in 63 municipalities within ten thousand inhabitants away from the cutoffs.
+The legislation in municipalities on the left and on the right-hand side of the cutoffs comprised local public goods.
+However, municipalities with larger city councils had around 15.0 percent more public goods provision proposals, suggesting an increase in service provision legislation.
 
-Finally, we present three sets of evidence that the results are consistent with the micro-level representation practices of city councilors.
-First, we show that the new councilor has access to government resources and uses public office appointments to mediate service provision.
-They have a 91\% chance of belonging to the mayoral coalition, and they appoint an average of 105 extra bureaucrats for many positions at the mayor's office, having loyal workers inside the municipal bureaucracy.
-Second, we analyzed 346,553 bills approved by city councilors in municipalities close to the council size thresholds.
-In line with our theory, we find that councilors prefer to provide targeted goods (72.9\% of all bills), as they satisfy the populations' needs and are easier to credit claim.
-Finally, we ran an online survey among the councilors during the period, showing that most councilors believe that voters prefer targeted services (68.8\%) to lawmaking (24.6\%) and oversight (30\%).\footnote{Councilors were able to select multiple categories, so the sum can be over 100\%.} We also refute three alternative explanations: increased representation of women and non-white legislators, change in electoral competitiveness, and a larger average of approved legislation by each councilor.
+Finally, I show that the increase in legislature size significantly impacts municipal education and health care.
+Increasing the city council size by one legislator lowers infant mortality by 2.01 children per one thousand infants born and reduces postneonatal mortality by 0.90 children per one thousand infants that survived their first 28 days.
+A larger council size also increased enrollment by 2.58 children in elementary education classrooms without significantly diminish elementary school quality.
+These services are crucial for welfare and result from an eased bargaining between the mayor and the city council.
 
-# Legislature Size, Legislative Support, and Welfare
+This paper contributes to three strands of the literature.
+First, this paper contributes to a large literature on multilateral bargaining.
+Repeated models of multilateral bargaining started with \citet{baron1989bargaining}, which extended the bilateral bargaining game proposed by \citet{rubinstein1982perfect} to more than two players.
+Several papers followed \citet{baron1989bargaining}, adding endogenous recognition power, changing the size of the required majority, adding partisanship, and testing the predictions of these models in the lab \citep{calvert2005legislative, choate2019partisan, agranov2020persistence, baranski2020determinants}.\footnote{See \citet{eraslan2019legislative} for a comprehensive review of the multilateral bargaining and \citet{ray2015coalition} for a review on coalition formation.} In this paper, I extend the \citet{baron1989bargaining} model under closed rules, adding the mayor's first move and political partisanship.
+Partisanship here is different from \citet{choate2019partisan} since I consider partisan as a zero-sum effect that is positive for politicians aligned with the mayor and negative otherwise.
+This paper investigates the often overlooked effect of legislature size on the bargaining equilibrium strategies.
+
+Second, this paper contributes to the literature regarding the political and economic effects of larger legislatures.
+Following the contribution by \citet{Weingastetal1981}, the "law of 1/n" posits that larger legislatures increase the legislative pressure for providing targeted public goods to local supporters at the expense of the entire polity \citep{alptekin2021effect}.
+The corollary of the "law of 1/n" is that increasing legislature size should promote excessive public spending.\footnote{\citet{PrimoSnyder2008} show that legislature size may result in positive or negative expenditures, depending on factors such as the degree that local public goods can exclude non-locals or deadweight costs associated with taxation.} In the US metaphor, this would explain significant infrastructure spending in smaller districts.
+However, the "law of 1/n" literature left aside the public goods provision and welfare.
+This paper is one of the first papers to study the number of local legislators on welfare.
+The model provides a theoretical expectation based on the chances of electing a politician aligned with the mayor.
+The empirical estimates confirm the theoretical predictions, with the additional fact that legislature size has a null effect on expenditures in Brazil.
+
+Finally, it contributes to a growing literature on municipal partisan politics.
+Most papers in this area estimate the effects of the mayor's party on political outcomes.
+For instance, \citet{gerber2011mayors} and \citet{de2016mayoral} find differences in governance when comparing Democratic and Republican mayors.
+Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors.
+\citet{frey2020larger}, using the discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds I study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
+This paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.
+
+# A Theory of Legislature Size, Legislative Bargaining, and Welfare
 \label{sec:theory}
 
-What is the effect of larger legislatures on public service provision?
-The most striking feature of a legislature is the fact that decisions are undertaken collectively.
-Legislators have to propose changes in the status-quo, agree upon what they want to decide, evaluate proposals put forward by mayors, discuss and improve the proposals, and decide which changes they will carry on.
+Several cities in the world are governed by the mayor-council system.
+In mayor-council cities, the power is divided between a mayor that controls the Executive branch and a city council that supports or sanctions the policies proposed by the mayor.
+In this setting, consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
+The mayor has the prerogative of proposing a vector of policies that is voted by the city councilors.
+The provision of public goods is then a bargain between the mayor and the city council.
+Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.
 
-In this sense, legislature size is critical in determining the efficiency of the decision-making process.
-Upon adding a new city councilor, the most simple change is the increased production capability.
-Legislative production, analogous to what happens in firms, may increase when adding an extra legislator \citep{crain1979cost, crain1982team, rogers2002free}.
-For instance, suppose that working full time, politicians can approve five bills a month.
-Ten politicians can together approve 50 bills, while 11 can pass 55.
-This increases the number of measures adopted, and if laws enact services to constituencies, then we shall witness an increase in service provision.\footnote{An alternative explanation relates to the Condorcet Jury Theorem.
-In these models, there is a binary choice, with one of them being ex-ante the best.
-If legislators access the best choice with a probability higher than 0.5, more legislators will increase the change of selecting the best choice \citep{myerson1998extended}.
-However, this logic assumes that politicians choose among exogenously provided proposals, which makes sense in the case of a jury, but is somewhat uncommon for legislatures.
-\citet{auriol2012optimal} compute the optimal size of chambers considering that this is the solution to the interplay between specialization costs and citizens' preferences.}
+The city council votes the mayor's proposal, and if councilors accept it, the mayor implements it.
+Otherwise, a reversal policy takes place.
+Reversal policy in this context means that the mayor's proposal failed to secure the majority of council votes.
+The decision process leaves the mayor's office, and it is transferred to the council.
+The types of reversal policies are crucial for my argument, as it changes the relative strength of the council in their bargaining with the mayor.
+I investigate two types of reversal policies: a baseline reversal with no parties and a hybrid mechanism with partisan and non-partisan concerns.
+The differences between these two mechanisms are that the non-partisan councilors only care about rents, while partisan councilors care about both rents and policy.
 
-However, increasing the size of legislatures also carries considerable costs.
-Larger legislatures can raise the transaction costs \citep{weingast1988industrial}, increase collective action problems \citep{crain1979cost}, and make  forming majorities more costly \citep{crain1982team}.
-These negative features, together with the fact that legislators may free-ride on each others' proposals, may decrease legislative productivity.
-For instance, if decisions need a majority or qualified majority to be approved, more legislators create a perverse incentive, increasing the difficulty of approval.
-Moreover, legislators are pressured to provide targeted services for their constituencies at the expense of the entire polity \citep{Weingastetal1981, PrimoSnyder2008}, and this can raise inefficiencies in expenditure allocation.
-Additionally, transaction costs within legislatures may increase the difficulty of passing bills \citep{weingast1988industrial, baron1989bargaining}.
-Therefore, it is unclear whether and how larger legislatures impact lawmaking and service provision.
+To govern, the mayor must convince at least half of the city councilors to support her policy proposals.
+Similar to \citet{buenodemesquita2005logic}, I assume that the selectorate, i.
+e., the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
+The winning coalition, the minimum number of members that must be convinced to implement the policy, is equal to half of the selectorate $N/2$.
+City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
+I leave the definition of these transfers open, as this facilitates the relationship with several instruments that mayors can use to pressure city councilors.
+Transfers may be granting electoral favors, favoring clientelistic brokers, spending in areas that the councilor has political or personal interests, providing portfolio (municipal offices) and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
+The use of transfers to affect the councilors' choices generate a bargaining cost of $C_G$.
+The bargaining costs vary with the reversal mechanism and the legislature size.
 
-In our view, to understand the effects of larger legislatures, we need to consider the political motivations behind the legislator's work.
-While an extra politician may increase the productivity frontier of a legislature, the types of services that will be favored remain unclear.
-To understand the political motivations, we need a theory that accounts for the cost-benefit calculations performed by politicians.
+Finally, after learning the bargaining costs, the mayor decides a level of public goods provision ($g$) and pockets rents ($r$).
+Public goods provision helps the mayor to get reelected.
+Rents are for direct mayor's consumption, and they do not contribute to the mayor's electoral success.\footnote{This model, similarly to \citet{cowen1994rent} and \citet{buenodemesquita2005logic} combines public goods provision and rent extraction.
+For a dynamic bargaining model that incorporates transfers to districts and public goods provision, see \citet{battaglini2012legislative}.} This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
+Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
+The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
+This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
+I assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
+If the mayor's policy proposal is approved, then the expected utility for the mayor is:
 
-When deciding which service to prioritize, politicians look into two dimensions of the service provision.
-First, the competition with other legislators motivates politicians to provide services that they believe voters want, regardless of whether these policies improve long-term welfare.
-For instance, suppose that there are three services, organized hypothetically based on beliefs about which of these three voters are more likely to reward:\footnote{Note that there is a difference between \textit{what voters want} and what \textit{politicians believe voters want}.
-Although politicians and brokers mostly access voter's beliefs accurately \citep{FinanSchechter2012, Stokesetal2013}, the crucial signal that a politician gets is vote shares, which are aggregated.
-It is hard to disentangle which service generated the highest electoral yield for the politician.
-Therefore, the politician's beliefs play an essential role in the services that they prioritize.} improving a local health clinic (most preferred), building a playground (second most preferred), or increasing the quality of education (least preferable).
-Politicians seeking recognition will mostly want to improve the health care system, which they believe will most benefit their electoral yields.
-After getting this done, they will shift efforts toward the playground construction and finally to education quality.
-Therefore, increasing legislature size will disproportionately increase the provision of services that the politicians believe voters prefer and will reward the most in the polls.
+\[
+\mathbb{E}U(r, g) \ = \ u(r) + B_M\pi(g)
+\]
 
-Second, to get reelected, besides providing the services that voters prefer, politicians have to take credit for facilitating provision \citep{fiorina1987personal, gulzar2017politicians, nielsen2017politicians, silva2017clarity}.
-Typically, the services that are easiest in terms of credit claiming are either providing local public goods, such as improving a neighborhood health clinic, or purely clientelistic and personalistic services \citep{Weingastetal1981, kuschnir2000cotidiano, Stokes2005, nichter2011electoral, Stokesetal2013, luna2014segmented, vieira2015clientelismo, bertholini2018pork}.
-This explains why clientelism and pork-barrel are persistent in democratic polities.
-Table \ref{tabcli} summarizes the incentives.
+The policy choices of the mayor are subject to the municipal budget constraint.
+The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget must be balanced.
+I also assume that there are enough resources for the mayor to govern.
 
-\begin{table}[htp!]
-\centering
-\caption{Effects of Legislature Size on Service Provision}
-\label{tabcli}
-\scalebox{1}{%
-\begin{tabular}{@{}lcc@{}}
-\toprule
-& \textbf{Hard for Credit Claim} & \textbf{Easy for Credit Claim} \\ 
-\midrule
-\multirow{3}{*}{\textbf{Low ranked by voters}} & No changes & None or mild \\
-& or deterioration & improvements \\
-& (Preventive Health)  & (Honors bills) \\[0.5em]
-\multirow{3}{*}{\textbf{High ranked by Voters}} & Mild to low & Mild to strong \\ 
-& improvement & improvement \\
-& (Infant Mortality)  & (School Enrollment) \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
+Let $C_G$ be the bargaining costs. The budget balance constraint requires the offers that the mayor makes to the city councilors to satisfy the following inequality:
 
-These two dimensions provide a simple yet powerful guide of the politicians' incentives.
-When voter places a high premium on the provision of a given service, and it is easy to claim credit for the provision, politicians will concentrate their efforts in providing it.
-The more politicians, the higher the provision of the service.
-Consider, for instance, constituency service, such as getting a child enrolled at a public school.
-The voters highly rank service such as this, and the politicians can break the school access directly, getting all the credit for the provision.
-Therefore, these services tend to increase, up to the point of being over provided.
+\[
+r + g + C_G \ \leq \ R
+\]
 
-When a service is hard to credit claim, to be provided, it has to be highly ranked by the voters.
-Consider services that decrease infant mortality.
-Although policies in this direction might be harder to be directly associated with one given politician, every politician wants to be known as the ones that diminished infant mortality.
-The death of a child has devastating effects over a polity, and no politician wants to be associated with it.
-On the other hand, every parent would be extremely thankful for the politicians that improved health care and saved their child.
-Moreover, politicians might facilitate access to medication and hospitals, which in turn is easier for credit claiming.
-Therefore, these services will have anywhere from modest to substantial improvements.
+The expected utility for the city councilors depends on the reversal policy.
+In the baseline non-partisan reversal, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
+The selected councilor becomes the new proposer.
+If her proposal is accepted, it is implemented.
+If councilors reject the offer again, the budget shrinks by a factor $\delta$, and another city councilor is recognized to propose.
+The process repeats until a proposal is finally accepted.
 
-Suppose now that service is secure to credit claim for, but gives low electoral yield.
-In this case, although the provision can be unquestionably traced back to the legislator, voters care little about the provision.
-For instance, honors and appraisal legislation are very common in Brazilian municipalities.
-However, they are perceived by politicians as low electoral yield, but the legislator that proposed the homage usually gets associated with it.
-These types of legislation increase with legislature size, but their effect on welfare is negligible.
+After studying the non-partisan baseline, I consider a situation that combines both partisan and non-partisan legislature concerns.
+Each councilor has a party affiliation.
+Party affiliations are mutually exclusive, and if a city councilor is aligned with the mayor's party, then she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
+Otherwise, the city councilor belongs to the opposition $O = \{1, 2, \cdots, N \} \setminus G$.
+The mayor's policy generates a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends on the party affiliation of the councilor.
+If councilors reject the mayor's proposal, no public goods are provided ($p=0$).
+Moreover, in equilibrium, I assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the online supplemental materials, I consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affect choices in any potential history of the game.
+The equilibrium public goods provision level is even higher than in the model presented here, as city councilors prefer to approve the mayor's proposal than run the risk of an opposition member becoming the proposer.}
 
-Finally, services that are difficult to credit-claim, or that politicians believe that voters care very little about, are expected to receive little invested effort from politicians.
-For instance, consider preventive health care.
-Preventive care refers to health measures, such as prenatal care or vaccination, undertaken to lower the chances or the severity of a disease(s) in the future.
-However, it is a compounded chance: the voter has to consume the service, but its effectiveness depends on voters getting sick.
-Nowadays, we are witnessing how hard it is to vaccinate children, despite all the scientific evidence demonstrating its effectiveness.
-Moreover, rational voters may fail to punish politicians for low investments in preventive public policies, such as natural disasters or climate change mitigation \citep{gailmard2019preventing}.
-Hence, voters might also not punish politicians for low investments in preventive health care because they might only observe whether a politician properly invested in preventive public policies in cases of emergency.
-Therefore, we shall expect little to no improvement in these types of services with larger legislatures.
+The timeline of the strategic interaction is as follows:
 
-In sum, these considerations suggest that instead of looking for overall positive or negative effects, the effects of legislature size should manifest diversely, conditional on the type of service studied.
-The most significant changes should be expected in services that voters want and that are easier to claim credit for.
-Services with only one of these characteristics will be intermediate in terms of their priority and efforts exerted by politicians in their provision and will improve with less intensity.
-Services hard to credit claim and low ranked by voters will tend to be unaffected or under-provided by lawmakers.
+\begin{enumerate}
+  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
+  \item The mayor proposes a policy vector $(r, g, x)_M$.
+  \item The city council votes the proposal.
+  \begin{itemize}
+    \item If the council accepts, the policy is implemented, and the game ends. 
+    \item Otherwise, the reversal policy is implemented.
+  \end{itemize}
+  \item (Reversal Policy) The budget is discounted by a factor $\delta \in (0,1)$, and one councilor is randomly selected to make an offer.
+If the offer is accepted, it is implemented.
+If rejected, the reversal policy stage restart.\footnote{In section B.1 of the online supplemental materials, I solved three reversal mechanisms.
+The two in here, plus a mechanism with only political concerns.}
+\end{enumerate}
+
+The solution concept I use in this model is the Subgame Perfect Nash Equilibrium.
+A Subgame Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game.
+The solution is found using backward induction.
+In the model with infinitely repeated proposals, any strategy can be shown to be a Nash equilibrium.
+Thus, a natural assumption is to extend the equilibrium concept to require the equilibrium to be stationary.
+A Stationary Subgame Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should take the same offer at time $k$ \citep{rubinstein1982perfect}.
+Stationarity gives us an objective of finding a proposal that would be accepted at any stage in the game.
+Applying this reasoning, I can characterize a sequence of offers for each point $k$ in time.
+For the mayor, the optimal offer is at $k=0$, representing a no delay in policy implementation.
+Moreover, I assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.
+
+For the solution to be of general interest, I solve bargaining costs for the expected number of opposition and government-aligned city councilors.
+This is because the solution for each fixed number of opposition and government councilors is trivial and does not help understand the overall relationship between council size and bargaining costs.
+
+## The Mayor's Decision Stage
+
+Solving the game by backward induction requires us to start with the councilor's strategies.
+However, for exposure convenience, assume that I solved the game for the councilors and found the equilibrium bargaining costs $C_G(N)$ when there are $N$ city councilors.
+I now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
+The mayor benefits from public goods provision, as it increases the chances of her reelection.
+However, she prefers to invest as minimum as necessary in public goods and extract the remaining resources as political rents.
+The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.
+
+\[
+\begin{aligned}
+\max_{r, g} \quad & u(r) + B_M\pi(g)\\
+\textrm{s.t.} \quad & r + g + C_G(N) \leq R
+\end{aligned}
+\]
+
+In equilibrium, the budget binds, and the first-order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equal to the marginal benefits of reelection:
+
+\[
+u'(R - g - C_G(N)) = B_M\pi'(g)
+\]
+
+The optimal level of public goods provision equates the marginal gains accrued from rents with the marginal benefits from reelection.
+
+\begin{proposition}\label{prop1}
+The provision of public goods increases with legislature size when the bargaining costs decrease with legislature size.
+\end{proposition}
+
+All proofs are in section B.1 of the online supplemental materials.
+The proof's intuition involves finding what happens to the mayor's marginal utility when I increase both $g$ and $N$.
+As $N$ increases discretely on a complete lattice, I use monotone comparative statics to derive the conditions for increasing differences \citep{milgrom1994monotone, ashworth2006monotone}.
+Increasing differences mean that higher $N$ leads to higher equilibrium $g$.
+
+Proposition \ref{prop1} provides the first empirical hypothesis to test: \textit{if the bargaining costs decrease when the legislature size increases, then the provision of the public goods increases when the legislature size increase}.
+Now I study each reversal mechanism to determine the condition under which the bargaining costs decrease when legislature size increases.
+
+## Baseline: Non-Partisan Legislative Bargaining
+
+In the non-partisan reversal, I assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
+This formulation is similar to the closed rules proposal in \citet{baron1989bargaining}.
+To find a Stationary Subgame Perfect Nash equilibrium, suppose that there were $k-1$ rejections, and the game is at the $k$-th stage.
+A councilor accepts the proposer's offer if, and only if, to accept the offer at $k$ is better than or equal to wait until the next stage $k+1$.
+If the offer is $x_i$, then:
+
+\[
+x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left[ 1 - \dfrac{1}{N} \right]\left[\dfrac{1}{2} x_i \right]
+\]
+
+On the left-hand side, I place the offer.
+On the right-hand side, there are two components.
+The first is the amount that the councilor $i$ gets when she is the proposer.
+It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers she makes to convince half of the councilors.
+The second part is the gains if the councilor rejects the current received offer but still gets an offer in the following round.
+It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the transfer amount.
+Note that the offer the councilor makes as the proposer is the same as the offer she wants to receive.
+This is because the city councilors are exchangeable.
+The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, I could have dropped the $i$ in the solution).
+After some algebra, the offer $x_i$ must be greater than or equal to:
+
+\[
+x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k, N)
+\]
+
+The proposer always offers the minimum required to get the proposal approved. In this case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.
+
+Proceeding backwards, at the mayor's proposal stage $k=0$ the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
+In this context, the bargaining costs for the mayor are:
+
+\[
+C_G(N) \ = \ \dfrac{N}{2}\left[\dfrac{2 \delta R }{2N + 1}\right] \ = \ \dfrac{\delta R N}{2N + 1}
+\]
+
+\begin{proposition}
+In the baseline non-partisan reversal, the bargaining costs always increase when the size of the legislature increases.
+\end{proposition}
+
+The intuition for the results is that every additional councilor will demand more resources from the mayor.
+Thus, more councilors represent higher bargaining costs.
+And if the bargaining costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
+Below I show that partisanship is the key to understand how larger legislature sizes can increase public goods provision.
+
+## Partisan and Non-Partisan Bargaining
+
+In a reversal mechanism that incorporates partisan and non-partisan motivations, a city councilor aligned with the government favors the mayor's offer if:
+
+\[
+x_i \geq \dfrac{2\delta R}{2N+1} - p
+\]
+
+An opposition politician, on the other hand, favors the mayor's offer if, and only if:
+
+\[
+x_i \geq \dfrac{2\delta R}{2N+1} + p
+\]
+
+I decompose these costs into two components—first, the costs in terms of rents.
+Second, the costs (or benefits) from political alignment.
+In this context, the bargaining costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's proposals for councilors in the opposition.
+The ex-ante chance of an opposition member be elected is equal to $1-\gamma$, and taking the weighted averages, these costs become:
+
+\[
+C_G(N) \ = \ \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) + \left(\dfrac{N}{2} - \gamma N \right)2p
+\]
+
+\begin{proposition}
+In the reversal mechanism that incorporates partisanship, if $\gamma \geq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right] \equiv \underline{\gamma}$, then the bargaining costs decrease when the legislature size increases.
+\end{proposition}
+
+The intuition for the proof is that as partisanship influences the costs and benefits of legislators, more government-aligned councilors make it cheaper to govern.
+When the partisan benefit is higher than the additional cost that a legislator generates, adding a councilor will benefit mayors if the councilor has a higher chance of sharing the same party as the mayor.
+Therefore, a higher probability of electing a legislator aligned with the mayor reverts into lower bargaining costs.
+
+Also, the threshold $\underline{\gamma}$ that captures the probability of electing a politician aligned with the government is decreasing in the political value of the mayor's policy $p$ and the size of the legislature $N$.
+This means that intensive partisanship and larger legislatures make it easier to satisfy the electoral threshold.
+
+## Main Hypotheses
+
+My model provides two empirically testable hypotheses.
+Consider a municipality with a city council comprised of $N$ legislators.
+If the city increases the size of the council to $N+1$.
+Then, in a partisan setting:
+
+\begin{enumerate}[labelindent=*, 
+style=multiline, leftmargin=*, 
+label=H\arabic*.]
+  \item The bargaining costs decrease with legislature size when the chance of electing a government-aligned legislator is sufficiently high.
+  \item The provision of public goods increases when the bargaining costs decrease with legislature size.
+\end{enumerate}
+
+## Competing Hypotheses
+
+In the paper, I show that the provision of education and healthcare improves in Brazil.
+This is because the chances of electing a city councilor aligned with the mayor are 91%, thanks to the rule of distributing seats adopted in the country.
+
+However, other pathways could explain the nexus between city council size and welfare.
+First, improvements in representation could cause changes in health care and education.
+Increasing legislature size without changing the population makes councilors represent fewer people.
+For example, in a town with 50 thousand voters and ten councilors, each councilor represents five thousand voters.
+If the same city has eleven councilors, then each councilor represents 4.5 thousand voters.
+This facilitates the representation of minorities, as they have to gather fewer votes to elect a city councilor.
+A minority representative can advocate for policies that would improve the welfare of marginalized groups \citep{pande2003can, ChattopadhyayDuflu2004, chin2011redistributive}.
+Diversity could also improve governance in municipalities \citep{rugh2011provision}.
+Moreover, more women in public offices can shift the service provision toward welfare expenditure \citep{duflo2012women, brollo2016happens, hernandez2018women, funk2019representative}.
+Therefore, an alternative hypothesis to explain the increased service provision is that larger legislatures are improving female and minority representation.\footnote{For a description of the barriers faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
+
+Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{arvate2013electoral}.
+In a political system with around thirty parties and a sample average of almost ten parties in the municipalities I study, candidates per seat can increase exponentially.
+According to the Brazilian electoral law, each party can sponsor 1.5 times the number of seats as candidates.
+If a party form a pre-electoral coalition, this number increases to two times the number of seats \citep{coneglian2008lei}.
+An election in a small town, with ten councilors, may end up with 600 candidates: (30 parties) x (two times the number of seats) x (ten seats).
+Therefore, an alternative hypothesis to explain the increased service provision is that larger council size increase the competitiveness of the election.\footnote{Despite the common assumption that competitiveness improve welfare, \citet{boulding2014political} and \citet{gottlieb2019countervailing} can increase budgetary pressure, lower social policy, lead to bargaining inefficiencies.}
+
+Finally, the mayor and the legislature carry out the provision of services.
+Similar to what happens in firms, an extra employee can increase the firm productivity frontier by improving cooperation and a synergistic output \citep{alchian1972production, holmstrom1982moral}.
+A similar argument can view the increase in council size as augmenting the public service production capability in the municipality.
+As the production of the legislature manifests into legislation, an alternative hypothesis to explain the increased service provision is that more laws proposed by the city councilors are being approved.
+
+\begin{enumerate}[labelindent=*, 
+style=multiline, leftmargin=*, 
+label=AH\arabic*.]
+  \item The representation of females increases with legislature size, improving public goods provision.
+  \item The representation of non-whites increase with legislature size, improving public goods provision.
+  \item The competitiveness of the election increases with legislature size, improving public goods provision.
+  \item The legislative production increases with legislature size, improving public goods provision.
+\end{enumerate}
+
+I show below that hypotheses H1 and H2 hold, while the data falsify the alternative hypotheses AH1 to AH4.
 
@@
 On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%.
-This reduces the ability of municipal legislators to effectively influence local spending, what makes improvements in local services dependent only on the efforts of city-level politicians.
-XXXX
+This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments.
 
-With regards to their political organisation, municipalities have one mayor and one city council.
+With regards to their political organization, municipalities have one mayor and one city council.
 Citizens choose their representatives by direct vote in the same election.
-Mayors are in charge of organising the provision of public services, as well as proposing laws and amendments to the tax code.
+Mayors oversee the provision of public services and propose laws and amendments to the tax code.
 Proposals submitted by the mayor are subject to the approval of the city council.
-Councillors, in turn, have two primary duties.
-First, they should discuss and vote legislation put forward by the mayors or by their peers.
+Councilors, in turn, have two primary duties.
+First, they should discuss and vote on legislation put forward by the mayors or by their peers.
 Second, they oversee the public budget and sanction mayors who do not comply with fiscal legislation.
-Councillors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrolment, and even paying their voters' utility bills \citep{nichter2011electoral, AlmeidaFelix2012}.
+Councilors and mayors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrollment, and even paying their voters' utility bills \citep{nichter2011electoral, lopez2017legisladores}.
 
@@
 This led to severe imbalances in the proportion of representatives per citizen across the country.
-For instance, the Nova Russas municipality had 30,009 inhabitants and 21 councillors, which accounts for one legislator per 1,429 citizens.
-In contrast, the city of Sorocaba had only 15 councillors for 528,735 inhabitants, that is, one legislator per 35,249 citizens.
+For instance, the Nova Russas municipality had 30,009 inhabitants and 21 councilors, accounting for one legislator per 1,429 citizens.
+In contrast, the city of Sorocaba had only 15 councilors for 528,735 inhabitants, that is, one legislator per 35,249 citizens.
 In 2003, this malapportionment problem gained national visibility when Mira Estrela, a small municipality with only 2,651 residents, reduced its city council from 11 to 9 seats because of fiscal considerations.
 The change motivated a legal dispute that reached the Brazilian Supreme Court.
-The Court favoured the city's decision and ruled that the size of every local council should correspond to precise population thresholds.
+The Court favored the city's decision and ruled that the size of every local council should correspond to precise population thresholds.
 
-Following the ruling of the Supreme Court, in March 2004 the Brazilian Electoral Court established a series of population cutoffs for all municipal legislatures.
-The Court specified that, following the Brazilian Constitution, cities with up to one million residents should have between 9 and 21 legislators.
+Following the ruling of the Supreme Court, in March 2004, the Brazilian Electoral Court established a series of population cutoffs for all municipal legislatures.
+Following the Brazilian Constitution, the Court specified that cities with up to one million residents should have between 9 and 21 legislators.
 The number of seats was allocated as follows.
-Each city starts with 9 councillors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members.
-This threshold implies that cities with a population between 571,428 and one million should all the same number of legislators, that is, 21 of them.
-Conversely, cities between one and four million inhabitants should have at least 33 councillors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.
+Each town starts with nine councilors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members.
+This threshold implies that cities with a population between 571,428 and one million should all have the same number of legislators, that is, 21 of them.
+Conversely, cities between one and four million inhabitants should have at least 33 councilors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.
 
-This decision makes Brazil the ideal testing ground for our theory.
+This decision makes Brazil the ideal testing ground for my theory.
 Although an endogenous decision motivated the Electoral Court ruling, the population cutoffs created sharp discontinuities in the distribution of local council seats.
-That is, cities close to the cutoffs had very similar characteristics, but those which were just above the threshold gained a new legislator.
+Cities close to the cutoffs had very similar characteristics, but those just above the threshold gained a new legislator.
 Moreover, cities could not self-select into any group, as their population estimates were calculated using the 2003 projections by the Brazilian Census Bureau (IBGE).
@@
 
-\section{Empirical Strategy}
+# Variables and Data Sources
+\label{sec:sources}
+
+I use four groups of city-level variables in the models.
+The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution.
+I add them to the models to improve the balance between treated and non-treated units.
+The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality.
+The data come from the Superior Electoral Court (Tribunal Superior Eleitoral--TSE) and the 2000 Brazilian census.
+
+Second, I look into municipal data, city councilors' characteristics, approved legislation, and an online survey with 174 former city councilors that served during 2005--2008 term to investigate the political mechanism.\footnote{I also analyzed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
+The authors asked councilors about their daily work.
+The interviews reinforced that the mayor's agenda dominates councilors' work and is partisan without strictly following party lines.
+Municipal politics is divided into families or poles of power, belonging to different party affiliations.
+Councilors from other parties gravitate around either of these groups, hence the opposition and government-aligned logic.} The municipal data contains: 1) the number of councilor's belonging to the mayor's pre-electoral coalition; 2) the number of appointed bureaucrats; 2) the councilor's gender and race; 3) the competitiveness of each city council seat; 4) the proportion of laws proposed by the city council that was approved.
+All variables come from the Superior Electoral Court, the Senate legislative support Interlegis, and the Brazilian Bureau of Statistics (IBGE).
+
+Third, I also collected 346,553 bills from cities within ten thousand inhabitants from the 2004 population thresholds.
+I selected 63 out of 202 municipalities whose voting records were available online.
+I evaluate proposal types, discriminating between local public goods, oversight, and other legislative activity.
+Examples of the local public goods are investing in a public health clinic, requesting school bureaucracy to accommodate an extra child, renovating sewage, and fixing potholes on a given street.\footnote{My theory does not differentiate between clientelism and broad service provision, as it is hard to disentangle differences in the local level legislation.
+A voter may request a particular service, such as fixing a pothole.
+Attending this request can be interpreted as a clientelistic practice.
+Still, the provision of the service generates non-excludable benefits to the adjacent neighborhood.} Oversight bills are accountability and transparency mechanisms meant to keep public services undertaken by the bureaucracy in check.
+Other legislation comprises bills that do not fit in the previous categories.
+Examples are changes in street names, motions to honor citizens or groups, and legislative and internal city council procedures.
+I provide further information about the legislation dataset and the city council survey in sections B.13 and B.14 of the online supplemental materials.
+
+The last set of variables quantify social welfare.
+The focus is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
+I measure access to education with the average enrollment in primary (K--4) municipal public schools.
+I assess education quality with the Education Development Index (\ 'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
+The index is a weighted average of student scores in Portuguese and Mathematics (0--10) multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
+To test the effect of the 2004 ruling on healthcare, I collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants that survived more than 28 days, but died before completing one year old.
+The source of all healthcare variables is the Brazilian Ministry of Health Data Center (DataSUS).
+
+Together, this evidence provides a clear picture of local-level politics patterns in Brazil, from the political mechanism to the municipal welfare consequences of the larger city council size ruling.
+Summary statistics and variable descriptions follow in section B.2 of the online supplemental materials.
+
+# Empirical Strategy
 \label{sec:empstrat}
 
-\subsection{Methodology}
-\label{sub:methods}
-
-We employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Superior Electoral Court resolution as treatment indicators.
+I employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Superior Electoral Court resolution as treatment indicators.
 Figure \ref{fig:runningvarplot} displays the distribution of municipalities within each city council size.
-These population thresholds remained in effect until 2009, when Congress amended the Brazilian Constitution.
-This study covers the period between 2005 and 2008, which constitutes the full mayoral and city-council term following the 2004 Brazilian elections.
+These population thresholds remained in effect until 2009 when Congress amended the Brazilian Constitution.
+This study covers 2005 to 2008, which constitutes the full mayoral and city-council term following the 2004 Brazilian elections.
 
@@
 
-Our identification strategy relies on three assumptions.
-First, we assume that no municipality self-selected into each side of the discontinuity.
-Second, as we run a sharp RDD, we also assume that council size increases precisely as the law mandates.
-Third, our design assumes that the pre-treatment variables, collected before the 2003 Supreme Court decision, were not affected by the 2004 ruling on council size.
-In the online appendix, we test these assumptions by building an estimator that balances the local average treatment effects (LATE).
-Our estimate is an extension of RDD and uses covariates to balance the multiple cutoff differences.
-Additionally, we propose a placebo test in which we run the same models with fake cutoffs around the original thresholds.
-Our balance and placebo tests indicate that the assumptions underlying the analyses are indeed met.
+My identification strategy relies on three assumptions.
+First, no municipality should be able to self-select into each side of the discontinuity.
+Second, as I estimate a sharp RDD, the council size should increase precisely as the law mandates.
+Third, this design assumes that the pre-treatment variables, collected before the 2003 Supreme Court decision, were not affected by the 2004 ruling on council size.
+Moreover, for all the actual models estimated here, I fitted placebo cutoffs to check whether the estimation technique leads to consistent results.
+The placebo cutoffs are the dashed lines in Figure \ref{fig:runningvarplot}.
 
-% Subsection: Variables
-\subsection{Variables and Data Sources}
-\label{sub:sources}
+For the first assumption, in section B.3 of the online supplemental materials, I test distribution imbalances running the \citet{McCrary2008} and \citet{cattaneo2019simple} tests.
+The tests show no distribution imbalances.
 
-We use four groups of city-level variables in our models.
-The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution.
-We add them to the models to improve the balance between treated and non-treated units.
-The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality.
-The data come from the Superior Electoral Court (Tribunal Superior Eleitoral--TSE) and the 2000 Brazilian census.
+For the second assumption, running RDD in multiple thresholds may lead to inconsistent estimates when there are differences in the distribution of cases around the cutoffs \citep{cattaneo2016interpreting, eggers2018regression, bertanha2020regression}.
+In the dataset, there are twelve discontinuities.
+At each threshold, there is a sharp increase of one councilor, from 9 to 21.
+When running an RDD on these discontinuities, a consistent estimator should fit the exact change of one councilor.
+However, if I pool all the discontinuities together with no correction, I find an increase in council size of 1.63 councilors (see the first estimate in Table \ref{validitycheck}).
+This imbalance is because when combining all the discontinuities, the estimation is implying that municipalities below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
+That is incorrect because the comparison is inconsistent in council size, and these municipalities diverge in many other aspects.
 
-We employ a second set of variables to quantify social welfare.
-They are our outcomes of interest.
-Our main focus here is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
-We measure access to education with the average enrolment in primary (K--4) and secondary (5--8) public schools.
-We assess education quality with the Education Development Index (\'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
-The index is a weighted average of student scores in Portuguese and Mathematics (0--10) multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
-To test the effect of the 2004 ruling on healthcare, we mapped the coverage of the Family Health Programme, a local-level primary care policy, and the proportion of pregnant women who attended more than six pre-natal consultations.
-We also gather data on post-neonatal mortality\footnote{Post-neonatal mortality rate is the probability of dying between 28 days and one year of life, expressed per 1,000 live births.} to assess healthcare quality.
-The source of all variables is the Brazilian Ministry of Health Data Centre (DataSUS).
+To avoid this problem, in section B.5 of the online supplemental materials, I show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in my case, the population in 2003), improves the consistency and efficiency of the estimates.
+Relying on this fact, I add five controls to the estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
+The reason for the first variable is the multiple threshold assignments.
+I add GDP per capita because wealthier cities tend to have better public services.
+The number of seats in 2000 intends to control that some municipalities could experience a change provoked by the previous council size, confounding my estimates.
+The year and the northeast dummies serve to improve efficiency.
+Adding controls improves efficiency in RDD and also enhances the consistency in the multiple thresholds RDD \citep{calonico2019regression}.
 
-Next, we look into municipal data, city councillors' characteristics, approved legislation, and an online survey with 174 former city councillors that served during the 2005--2008 term to test our proposed micro-level mechanisms\footnote{We also analysed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
-The authors asked councillors about their daily work.
-The interviews reinforced the idea that councillors see private goods provision as more electorally profitable than formal lawmaking or executive policy oversight.}.
-The municipal data contains: 1) the number of councillors belonging to the pre-electoral mayoral coalition; 2) the councillor's gender and race; 3) the number of mayor-appointed, councillor-appointed, and career civil servants.
-All variables come from the Superior Electoral Court and the Brazilian Institute for Geography and Statistics.
+For the last assumption, there should be no changes in pre-treatment covariates.
+These pre-treatment covariates are variables measured before the primary outcomes.
+As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
 
-Lastly, we also collect 346,553 bills from cities whose populations lie within 10 thousand inhabitants from the 2004 population thresholds.
-We selected 64 out of 202 municipalities whose voting records were available online.
-We evaluate information regarding proposal types, discriminating between local and municipal public goods, oversight, and other legislative activity.
-While local public goods consist of services targeting personal, group, or neighbourhood levels, municipal public goods comprise laws and policies covering the entire municipality.
-Examples of the first are investing in a given public health clinic, requesting school bureaucracy to accommodate an extra child, and renovating sewage and fixing potholes on a given street\footnote{Our theory does not differentiate between clientelism and service provision, as it is hard to disentangle legislator's intentions.
-On the one hand, a voter may request a particular service, such as fixing a pothole.
-Attending this request can be interpreted as a clientelistic practice, despite their non-excludable benefits to the adjoining neighborhood.
-On the other hand, upon request, facilitating hospital admission is a very particularized service, thus likely to fall under clientelistic logic.
-Saying this is vote-buying can be imprecise, as service provision might simply be a way of signaling responsiveness to the electorate's demands and efficacy.
-\citet{kuschnir2000cotidiano}'s qualitative work shows the Silveira Family in Rio de Janeiro aided the community they represented regardless of political preference.
-As a result, when one of the family members ran in an election, he had the highest vote share ever seen in Rio de Janeiro.}.
-As for the latter, examples are to ameliorate education by capacitating public teachers, and to raise public health care standards through city-wide vaccination campaigns.
-Oversight bills are accountability and transparency mechanisms meant to keep public services undertaken by the bureaucracy in check.
-Other legislation comprises bills that do not fit in the previous categories.
-Examples are changes in street names, motions to honour citizens or groups, and legislative and internal city council procedures.
+Table \ref{validitycheck} displays the results of the validity checks.
+I run the first-stage regressions at the top of the Table, both using and not using the controlling covariates strategy proposed, for both real and placebo cutoffs.
+At the bottom, I estimate the pre-treatment covariate balance.
+Furthermore, in the online supplemental materials, I run placebo checks for all the models using placebo cutoffs within the real ones.
+The results are in sections B.6 to B.12.
 
-Together, this evidence provides a clear picture of representation patterns in Brazil, from municipal welfare consequences to their micro-level mechanisms.
-Summary statistics follow in the online supplemental materials.
-
-# Results
-
-% Session: Results
-\section{Results}
-\label{sec:outcomes}
-
-\subsection{The Effect of Legislature Size on Service Provision}
-\label{sub:effects}
-
-We study the impact of legislatures on two services: education and health care. We collect eight indicators: four in education, and four in health care.
-
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{Public Service Outcomes} 
-  \label{tab:outcomes} 
+\begin{table}[htb!] \centering 
+  \caption{Research Design Validity Check} 
+  \label{validitycheck} 
     \scalebox{0.9}{
   \begin{threeparttable}
-\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c }
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
 \toprule
-& \multicolumn{4}{c}{\textbf{Education Outcomes}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes}}  \\ \cline{2-5} \cline{6-9}
+ & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- Treatment Effect on City Council Size}} \\ \cline{2-5}
    & \multicolumn{1}{c}{\small{(1)}} & 
@@
  \multicolumn{1}{c}{\small{(3)}} & 
- \multicolumn{1}{c}{\small{(4)}} & 
- \multicolumn{1}{c}{\small{(5)}} & 
+ \multicolumn{1}{c}{\small{(4)}} \\
+
+ & \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} & 
+ \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
+  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+\\[-1.8ex] 
+ LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
+  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
+\hdashline \\[-1.8ex]   
+ N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
+Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
+BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
+BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
+\midrule 
+ & \multicolumn{4}{c}{\textbf{Panel B: Validity Check --- Pre-Treatment Variables}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(5)}} & 
  \multicolumn{1}{c}{\small{(6)}} & 
@@
  \multicolumn{1}{c}{\small{(8)}} \\
- & \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Elem. School}} & 
- \multicolumn{1}{c}{\small{Middle School}} &
-\multicolumn{1}{c}{\small{Infant}} & 
- \multicolumn{1}{c}{\small{Post-Natal}} & 
- \multicolumn{1}{c}{\small{Cov. Family}} & 
- \multicolumn{1}{c}{\small{Pr. Born w. 6+}} \\ 
- & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
- \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
- \multicolumn{1}{c}{\small{Quality Index}} & 
- \multicolumn{1}{c}{\small{Quality Index}} &
- \multicolumn{1}{c}{\small{Mortality}} & 
- \multicolumn{1}{c}{\small{Mort. Rate}} & 
- \multicolumn{1}{c}{\small{Health Program}} & 
- \multicolumn{1}{c}{\small{Pre-Natal Consult.}}\\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
- LATE & 2.58$^{***}$ & -0.01 & -0.04 & -0.11 & -1.99$^{**}$ & -0.90$^{*}$ & -1.67 & -4.23 \\ 
-    & (0.81) & (1.07) & (0.13) & (0.11) & (0.78) & (0.48) & (2.09) & (4.01) \\
+  & \multicolumn{1}{c}{\small{Number of}} & 
+ \multicolumn{1}{c}{\small{Population}} & 
+ \multicolumn{1}{c}{\small{GDP}} & 
+ \multicolumn{1}{c}{\small{\% of Poverty}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2000}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} & 
+  \multicolumn{1}{c}{\small{2000 Census}} &
+   \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
+  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
   \hdashline \\[-1.8ex]
- N Left & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{7306} & \multicolumn{1}{c}{8597} & \multicolumn{1}{c}{5037} &
- \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{19280} & \multicolumn{1}{c}{15548} \\ 
- N Right & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{581} & \multicolumn{1}{c}{670} & \multicolumn{1}{c}{529} & \multicolumn{1}{c}{1030} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{1297} & \multicolumn{1}{c}{1030} \\
- Eff N Left & \multicolumn{1}{c}{196} & \multicolumn{1}{c}{475} & \multicolumn{1}{c}{387} & \multicolumn{1}{c}{279} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{314} & \multicolumn{1}{c}{281} & \multicolumn{1}{c}{615} \\
- Eff N Right & \multicolumn{1}{c}{202} & \multicolumn{1}{c}{312} & \multicolumn{1}{c}{283} & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{390} & \multicolumn{1}{c}{242} & \multicolumn{1}{c}{301} & \multicolumn{1}{c}{438} \\
- BW Loc Poly & 5.132 & 11.208 & 8.724 & 7.824 
- 7.720 & 7.183 & 4.185 & 8.891 \\ 
- BW Bias & 10.615 & 16.694 & 15.186 & 13.714 
- 12.289 & 10.726 & 8.310 & 15.007 \\ 
-\midrule 
- & \multicolumn{4}{c}{\textbf{Education Outcomes -- Placebo Cutoffs}} & \multicolumn{4}{c}{\textbf{Health Care Outcomes -- Placebo Cutoffs}}\\ \cline{2-5} \cline{6-9}
-  & \multicolumn{1}{c}{\small{(9)}} & 
- \multicolumn{1}{c}{\small{(10)}} & 
- \multicolumn{1}{c}{\small{(11)}} & 
- \multicolumn{1}{c}{\small{(12)}} & 
- \multicolumn{1}{c}{\small{(13)}} & 
- \multicolumn{1}{c}{\small{(14)}} & 
- \multicolumn{1}{c}{\small{(15)}} & 
- \multicolumn{1}{c}{\small{(16)}} \\
- & \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Average}} & 
- \multicolumn{1}{c}{\small{Elem. School}} & 
- \multicolumn{1}{c}{\small{Middle School}}&
- \multicolumn{1}{c}{\small{Infant}} & 
- \multicolumn{1}{c}{\small{Post-Natal}} & 
- \multicolumn{1}{c}{\small{Cov. Family}} & 
- \multicolumn{1}{c}{\small{Pr. Born w. 6+}}\\ 
- & \multicolumn{1}{c}{\small{Enroll. K-4}} & 
- \multicolumn{1}{c}{\small{Enroll. 5-8}} & 
- \multicolumn{1}{c}{\small{Quality Index}} & 
- \multicolumn{1}{c}{\small{Quality Index}} &
- \multicolumn{1}{c}{\small{Mortality}} & 
- \multicolumn{1}{c}{\small{Mort. Rate}} & 
- \multicolumn{1}{c}{\small{Health Program}} & 
- \multicolumn{1}{c}{\small{Pre-Natal Consult.}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5} \cline{6-6} \cline{7-7} \cline{8-8} \cline{9-9}
-  LATE & 0.45 & 0.97 & -0.10 & -0.12
-  & -1.14 & -0.25 & 1.85 & -2.22 \\ 
-  & (0.61) & (0.98) & (0.11) & (0.09)
-  & (1.05) & (0.65) & (1.25) & (2.92) \\ 
-  \hdashline \\[-1.8ex]   
- N Left & \multicolumn{1}{c}{9040} & \multicolumn{1}{c}{6350} & \multicolumn{1}{c}{7529} & \multicolumn{1}{c}{4243} & \multicolumn{1}{c}{10614} & \multicolumn{1}{c}{4449} & \multicolumn{1}{c}{17198} & \multicolumn{1}{c}{13861} \\
- N Right & \multicolumn{1}{c}{1802} & \multicolumn{1}{c}{1537} & \multicolumn{1}{c}{1738} & \multicolumn{1}{c}{1323} & \multicolumn{1}{c}{2715} & \multicolumn{1}{c}{1664} & \multicolumn{1}{c}{3379} & \multicolumn{1}{c}{2717} \\
- Eff N Left & \multicolumn{1}{c}{1186} & \multicolumn{1}{c}{1138} & \multicolumn{1}{c}{1202} & \multicolumn{1}{c}{931} & \multicolumn{1}{c}{1213} & \multicolumn{1}{c}{775} & \multicolumn{1}{c}{2575} & \multicolumn{1}{c}{1575} \\
- Eff N Right & \multicolumn{1}{c}{724} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{734} & \multicolumn{1}{c}{580} & \multicolumn{1}{c}{890} & \multicolumn{1}{c}{557} & \multicolumn{1}{c}{1483} & \multicolumn{1}{c}{1004} \\
- BW Loc Poly & 6.325 & 6.975 & 6.686 & 7.198 
- & 4.840 & 5.360 & 6.999 & 5.796 \\ 
- BW Bias & 9.860 & 12.598 & 10.029 & 11.004 
- & 7.268 & 7.943 & 11.213 & 9.559 \\ 
+ N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
+Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
+Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
+BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
+BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
 \bottomrule
@@
 \small
-\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
-RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, are in parentheses.
-The control variables are: population, GDP per capita, number of seats in 2000, year, and a dummy for the northeast region.
-\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
+\item \textbf{Note:} $ ^{***} $ p $ < $ .01; $ ^{**} $ p $ < $ .05; $ ^{*} $ p $ < $ .1.
+RD local linear estimates using \citet{calonico2019regression} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
 \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
 \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
-\textit{BW Bias} is the bandwidth used to compute the standard errors.
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
 \end{tablenotes}
 \end{threeparttable}}
-\end{sidewaystable}
+\end{table}
 
-XXXX Rewrite all this!
+Note that without adding covariates, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
+After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
+Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
+These tests reinforce the validity of my research design.
 
-Each of the outcomes is further divided into two groups.
-In the first group, we include services that are easier to provide or credit claim, or both.
-These services are preferred by the electorate and have an intensive advertising effect for the councillor.
-In this category, we have school enrollment and infant mortality.
-In the second group are services either considered less critical by voters or harder to credit claim.
-They are harder to translate into votes or to target and advertise.
-In our models, we use preventive health care and quality of education to illustrate.
-According to our theory, we expect that increasing legislature size has a positive effect on desirable services that are easy to target.
+# Results
+\label{sec:results}
 
-Table \ref{tab:outcomes} presents the results for education and health care outcomes.
-The data shows that, with the addition of a city councillor, enrollment in elementary schools increased by 2.58 children on average per school.
-This represents a change of around 0.20 standard deviations.
-From 5th to 8th grades, council size has no effect on school enrollment.
-Due to high dropout rates at this stage, spots for extra students remain vacant.
-Results are insignificant for quality indicators.\footnote{As education quality improves in the medium to long term, we look into the 2015 education quality index in the Online Supplemental Materials.
-Effects are null, pointing to no delayed benefits.} As expected, the placebo regressions are also insignificant.
+To test the formal model's predictions, I present four sets of empirical results.
+First, I show that the alternative hypothesis, which emphasizes representation, competitiveness, and legislative productivity, fails to receive empirical support.
+Second, I show that the bargaining costs hypothesis is confirmed and that the additional legislator also promotes more appointments of bureaucrats.
+This aligns with the councilor's reported strategies employed by mayors to consolidate their support from city councilors.
+Third, I show that municipalities with an extra city councilor approve more public goods laws in general and on education and healthcare.
+Finally, I show that all these pieces of evidence result in improvements in infant mortality and elementary school enrollment, two vital services for welfare.
 
-Although Brazil achieved universal elementary school enrolment, enrolling a child in public school is particularly difficult in the early years.
-At the same time, taking care of small children is a considerable burden for poor households.
-Citizens thus reach out to councillors who can pressure school's bureaucracy to accommodate an extra child.
-Such an effort has virtually no cost to the politician, and grants her direct recognition, benefiting her electorally.
+## Council Size, Bargaining Costs, and Alternative Hypotheses
+\label{sub:bargcosts}
 
-Consequences for infant mortality rates are also substantial.
-1.99 deaths per 1,000 children born are prevented with every extra legislator.
-This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
-Moreover, post-neonatal mortality decreases by 0.90 casualties per 1,000 births, which improves health care by 0.14 standard deviations.
-As expected, placebo regressions were statistically insignificant.
-However, the Family Health Program coverage and the proportion of children born with more than six prenatal consultations seems to decrease.
-This apparent inconsistency with the other indicators will be discussed further in the text.
+Table \ref{tab:bargain} tests the first hypothesis and the alternative hypotheses about the nexus between city council size and bargaining costs.
+The formal model's central premise is that larger legislature sizes produce lower bargaining costs when the chances to elect politicians aligned with the mayor are sufficiently high.
+However, the results could stem from different mechanisms, such as minority and female representation, competition, and increased council-sponsored legislative productivity.
+In Panel A, I counter the alternative explanations, while in Panel B, I present evidence that corroborates my findings.
 
-% Sub-Section: Mechanisms
-\subsection{Applying the Mechanism and Testing Hypotheses}
-\label{sub:mechanism}
+\pagebreak
 
-We test our hypotheses in Table \ref{tab:mechanism-reg} dividing the municipal outcome data in two panels.
-In Panel A, we counter alternative explanations for our mechanism.
-In Panel B, we present evidence that corroborates our arguments.
 \begin{table}[!htbp] \centering 
-  \caption{Mechanism Regressions -- Aggregated Municipal Level Outcomes} 
-  \label{tab:mechanism-reg} 
+  \caption{Political Effects of Increasing the Number of Legislators} 
+  \label{tab:bargain} 
 \scalebox{0.9}{
@@
  N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{270} \\ 
-Eff N Left & \multicolumn{1}{c}{194} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
-Eff N Right & \multicolumn{1}{c}{144} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{142} \\ 
-BW Loc Poly & 8.564 & 2.954 & 8.126 & 11.080 \\ 
-BW Bias & 13.569 & 4.917 & 12.049 & 16.921 \\[1.0ex] 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{269} \\ 
+Eff N Left & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{141} \\ 
+BW Loc Poly & 8.623 & 2.958 & 8.144 & 10.976 \\ 
+BW Bias & 13.565 & 4.922 & 12.018 & 16.708 \\[1.0ex] 
 \midrule 
-& \multicolumn{4}{c}{\textbf{Panel B: Access to Resources and Patronage}} \\ \cline{2-5}
+& \multicolumn{4}{c}{\textbf{Panel B: Partisan Alignment and Bureaucratic Appointments}} \\ \cline{2-5}
  & \multicolumn{1}{c}{\small{(5)}} 
- & \multicolumn{1}{c}{\small{(6)}} 
- & \multicolumn{1}{c}{\small{(7)}} 
- & \multicolumn{1}{c}{\small{(8)}} \\
+ & \multicolumn{1}{c}{\small{(6)}} & & \\
  & \multicolumn{1}{c}{\small{Mayoral}} & 
- \multicolumn{1}{c}{\small{Num. Politically}} & 
- \multicolumn{1}{c}{\small{Num. Career}} & 
- \multicolumn{1}{c}{\small{Num. councillor}} \\
+ \multicolumn{1}{c}{\small{Num. Politically}} & & \\
  & \multicolumn{1}{c}{\small{Coalition Size}} & 
- \multicolumn{1}{c}{\small{Appointed Empl.}} & 
  \multicolumn{1}{c}{\small{Bureaucrats}} & 
- \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.91$^{*}$ & 105.09$^{*}$ & 71.57 & 2.09 \\ 
-  & (0.50) & (62.12) & (218.12) & (4.37) \\ 
+  & \\[1ex] \cline{2-2} \cline{3-3}
+ LATE & 0.91$^{*}$ & 104.49$^{*}$ & & \\ 
+  & (0.50) & (61.53) & & \\ 
     \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{5168} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1028} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
-Eff N Left & \multicolumn{1}{c}{240} & \multicolumn{1}{c}{351} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
-Eff N Right & \multicolumn{1}{c}{161} & \multicolumn{1}{c}{334} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
-BW Loc Poly & 9.906 & 6.019 & 7.695 & 5.134 \\ 
-BW Bias & 15.846 & 10.170 & 11.780 & 8.902 \\ 
+ N Left & \multicolumn{1}{c}{5179} & \multicolumn{1}{c}{15536} & & \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1027} & & \\ 
+Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & & \\ 
+Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & & \\ 
+BW Loc Poly & 10.025 & 6.242 & & \\ 
+BW Bias & 15.889 & 10.243 & & \\ 
 \bottomrule
@@
 
-Panel A (Table \ref{mechreg1}) tests perspectives proposed by the literature.
-One of them is that better representation of under-served groups could broaden health care and education provision \citep{pande2003can, chattopadhyay2004women, chin2011redistributive, duflo2012women}.
-However, columns (1) and (2) show that neither gender nor representation of non-white legislators significantly improves public service provision for minorities.
-Alternatively, enhanced competition is also thought to improve responsiveness, alleviating the principal-agent problem between voters and politicians.
-Yet, we show that competition (3) or bills approval (4) remain unchanged when we increase council size.
+Panel A (Table \ref{tab:bargain}) tests the hypotheses AH1 to AH4.
+AH1 and AH2 established that better representation of under-served groups could improve welfare.
+However, columns (1) and (2) show that neither gender nor representation of non-white legislators significantly increases with changes in city council size.
+AH3 stated that enhanced competition could improve responsiveness, increasing service provision.
+Looking at competition per seat in municipalities with larger city councils, Column (3) in Panel A shows a null effect of council size on the competition.
+Finally, AH4 stated that council-sponsored legislation could be increasing in larger councils.
+Yet, Column (4) shows that it remains unchanged when there is an increase in council size.
 
-Panel B (Table \ref{mechreg1}) illustrates our mechanism.
-Column (5) shows that there is a 91\% chance of the extra legislator belonging to the mayoral coalition.
-This suggests that these additions will likely enhance welfare effects due to increased governability\footnote{It is possible that the new coalition councillor facilitates mayor's lawmaking process.
-Indeed, we might actually be estimating the effects of mayors on policy-making.
-Their relationship with the central government is fundamental for service provision \citep{bueno2018bypassing}.
-In the Online Supplemental Materials, we investigate whether mayoral and council party composition vary across cities, and find that it remains unchanged around the thresholds.}.
-Column (6) demonstrates that adding one councillor increases the number of appointed employees by 105 with a standard deviation of over 0.30.
-This attests councillors' strong ties with the administration and facilitates service provision.
+Panel B (Table \ref{tab:bargain}) illustrates the mechanism put forward in the formal model.
+Column (5) shows a 91\% chance of the extra legislator belonging to the mayoral coalition.
+The model hypothesis stated that the probability of electing a city councilor allied with the mayor is sufficiently high.
+However, sufficiently high can be ambiguous, and it depends on the intensity of the political disagreement and the current legislature size.
+In any case, 91\% chance is a considerably large quantity, and the extra city councilor is going to the mayoral coalition nine in every ten legislature size increases.
+This strengthens the bargaining position of the mayor and diminishes bargaining costs.\footnote{The effect of city council size on the number of mayor-aligned politicians stems from the rounding rule adopted by the proportional representation system in Brazil.
+The rounding rule favors the coalitions with more votes.
+Most of the time, the coalition of the elected mayor is the one that receives more votes.} Column (6) demonstrates that adding one councilor increases appointed employees by around 104 extra employees per additional city councilor.
+When negotiating with city councilors, these employees are a great bargaining chip, and they are also associated with better service provision.
 
-Additionally, we consider the number of career employees\footnote{Career bureaucrats have to undergo rigorous selection that prevents them from being fired for political reasons.} and find that improvements in state capacity and welfare are not consequences of bureaucratic agency.
-Column (7) points that the number of career bureaucrats does not significantly explain access to resources.
-Finally, adding a legislator has a null effect on the average number of appointed cabinet employees (column (8)).
-
-\subsection{Disaggregating Data on Approved Legislation and City councillor Survey}
+## Approved Legislation and City Councilor's Survey
 \label{sub:survey}
 
-To evidence our mechanism's operation in city councillors' ordinary legislative activities, we examine two datasets: one composed by the approved bills, and the other by answers to the online survey.
-Figure \ref{LEGAPPR} showcases the results of the analysis of approved legislation.
+To evidence the mechanism's operation, I build two novel datasets.
+First, I run a survey with former city councilors, asking how the mayor consolidate its coalition support within the city council.
+Second, I collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
+I hand-coded 3,466 laws into four categories: public goods, oversight, education and healthcare-related legislation, and other legislative duties.
+After hand-coding these laws, I used a supporting vector machine to classify the remainder laws.
+From the algorithms I used, the supporting vector machine performed better than the alternatives.
+
+\pagebreak
 
@@
   \begin{center}
-  \caption{Legislation Approved in Municipalities Closer to the City Council Thresholds}
+  \caption{Mayoral Instruments for Securing Councilors' Support}
+    \begin{minipage}{1 \linewidth}
+      \centerline{\includegraphics[width=6in,angle=0]{../figures/strategySupportMayors.pdf}}
+      \bigskip
+      \label{survelec}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+This paper assumes that city councilors want to extract rents and to get reelected.
+The rents come from their continuation value in the repeated game, and the partisanship discounts them.
+Figure \ref{survelec} shows that 65.9 percent of councilors mentioned that mayors use job appointments to consolidate their coalition support.
+59.0 percent of the surveyed councilors mentioned that mayors use personal favors, such as shifting resources to places where the councilors have electoral support, to solidify their governing coalition.
+Granting favors works as rent transfers for councilors.
+Job appointments are also convenient for the mayors because patronage in Brazil has positive results in terms of welfare \citep{toral2019benefits}.
+
+\begin{figure}[htb!]
+  \begin{center}
+  \caption{Legislation Approval Patterns in the Municipalities Closer to the City Council Size Thresholds}
     \begin{minipage}{1 \linewidth}
@@
 
-As previously argued, lawmakers decide on service provision based on the feasibility of credit-claiming.
-The top-two preferred legislation categories share this feature.
-In addition,\textit{local public goods} carries high electoral yield, which explains it ranking above \textit{others}.
-Graph 2A (Figure \ref{LEGAPPR}) presents the frequency of approved proposals.
-The overwhelming majority belongs to \textit{local public goods} (72.9\%), followed by \textit{others} (17.4\%).\footnote{Note that the sum is below 100\%.
-This is due to the SVM algorithm classifying around 3.5\% of laws as belonging to none of the categories above.
-For more information, see \citet{collingwood2013rtexttools}.} Graph 2B (Figure \ref{LEGAPPR}) depicts the average number of bills per legislator and, evidently, reflects the same pattern: \textit{local public goods} also amount to the highest, at 290.7 (S.E.
-56.95), and \textit{others} follows with 77.6 (S.E.
-15.50).
-Measuring the production of each representative builds on the idea that adding legislators – who provide more services – generates greater welfare.
+I have established in Table \ref{tab:bargain} column (4) that the quantity of laws approved by councilors remain constant.
+However, this tells us little about the composition of the legislation in municipalities with larger council sizes.
+In Figure \ref{LEGAPPR}, I show that the per capita amount of laws related to local public goods provision increased in the towns that received the extra legislator, vis-a-vis the baseline of cities that did not get an additional councilor.
+One additional city councilor increased the amount of per capita public goods laws by 15.0 percent.
+Also, the number of laws that focus on healthcare and education increased by 19.7 percent.
+Looking specifically into healthcare and education legislation, the proportion of public goods laws increased by 15.7 percent, showing that the policy proposals of the mayor and councilors shifted toward local and citywide public goods.\footnote{Public goods here are not restricted to citywide goods.
+Any service that benefits citizens, regardless of whether they are targeted to citizens or not, is considered public goods.
+For example, building a health clinic in a particular district can virtually exclude the citizens that are not living in the neighborhood.
+However, I am still considering these public goods, albeit targeted at a specific locality.}
 
-Health care and education services, which compose 11.1\% of total approved bills (44.3 per legislator), are mainly addressed through \textit{local public goods}.
-According to Graph 2C (Figure \ref{LEGAPPR}), they represent 80.6\% of proposals in these sectors, followed by \textit{municipal public goods} (7.8\%).
-Productivity follows the same pattern (Graph 2D, Figure \ref{LEGAPPR}).
-Legislators propose 36.4 (in absolute terms) of the first, and 4.2 of the latter.
-Therefore, not only in general, but also specifically for education and health care, \textit{local public goods} are the preferred choice of councillors in Brazilian municipal chambers.
+## The Effect of Legislature Size on Welfare
+\label{sub:effects}
 
-In our online survey with former city councillors, we asked about their legislative activity, the amount of votes it yielded, and how they negotiated with the mayor.
-While most results are in the Online Supplemental Materials, Figure \ref{survelec} displays the services councillors believe to generate the highest electoral results.
+I study the impact of legislature size on education and health care. I collect four indicators: two in education and two in health care.
 
-\begin{figure}[htb!]
-  \begin{center}
-  \caption{Electoral Attractiveness of Councilor's Activities and Practices}
-    \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/elecYieldJobsCouncilors.pdf}}
-      \bigskip
-      \label{survelec}
-    \end{minipage}
-  \end{center}
-\end{figure}
+\begin{table}[!htbp] \centering 
+  \caption{Legislature Size and Welfare} 
+  \label{tab:outcomes} 
+\scalebox{0.9}{
+\begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+& \multicolumn{4}{c}{\textbf{Council Size and Welfare -- Main Estimates}} \\ \cline{2-5}
+ & \multicolumn{1}{c}{\small{(1)}} 
+ & \multicolumn{1}{c}{\small{(2)}} 
+ & \multicolumn{1}{c}{\small{(3)}} 
+ & \multicolumn{1}{c}{\small{(4)}} \\
+ & \multicolumn{1}{c}{\small{Infant}} & 
+ \multicolumn{1}{c}{\small{Postneonatal}} &
+  \multicolumn{1}{c}{\small{School}} & 
+  \multicolumn{1}{c}{\small{Education}} \\ 
+   & \multicolumn{1}{c}{\small{Mortality}} & 
+ \multicolumn{1}{c}{\small{Mortality}} &
+  \multicolumn{1}{c}{\small{Enrollment}} & 
+  \multicolumn{1}{c}{\small{Quality}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+LATE & -2.01$^{**}$ & -0.90$^{*}$ & 2.52$^{***}$ & -0.03 \\ 
+  & (0.79) & (0.48) & (0.80) & (0.13) \\ 
+  \hdashline \\[-1.8ex] 
+ N Left & \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{8597} \\ 
+N Right & \multicolumn{1}{c}{1029} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{669} \\ 
+Eff N Left & \multicolumn{1}{c}{501} & \multicolumn{1}{c}{324} & \multicolumn{1}{c}{206} & \multicolumn{1}{c}{409} \\ 
+Eff N Right & \multicolumn{1}{c}{381} & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{291} \\ 
+BW Loc Poly & 7.527 & 7.564 & 5.425 & 9.05 \\ 
+BW Bias & 11.95 & 11.01 & 10.58 & 15.107 \\ [1.0ex] 
+\midrule 
+& \multicolumn{4}{c}{\textbf{Council Size and Welfare -- Placebo Estimates}} \\ \cline{2-5}
+& \multicolumn{1}{c}{\small{(5)}} 
+ & \multicolumn{1}{c}{\small{(6)}} 
+ & \multicolumn{1}{c}{\small{(7)}} 
+ & \multicolumn{1}{c}{\small{(8)}} \\
+& \multicolumn{1}{c}{\small{Infant}} & 
+ \multicolumn{1}{c}{\small{Postneonatal}} &
+  \multicolumn{1}{c}{\small{School}} & 
+  \multicolumn{1}{c}{\small{Education}} \\ 
+   & \multicolumn{1}{c}{\small{Mortality}} & 
+ \multicolumn{1}{c}{\small{Mortality}} &
+  \multicolumn{1}{c}{\small{Enrollment}} & 
+  \multicolumn{1}{c}{\small{Quality}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+LATE & -1.14 & -0.19 & 0.44 & -0.10 \\ 
+  & (1.05) & (0.22) & (0.61) & (0.11) \\ 
+    \hdashline \\[-1.8ex] 
+ N Left & \multicolumn{1}{c}{10613} & \multicolumn{1}{c}{17236} & \multicolumn{1}{c}{9040} & \multicolumn{1}{c}{7528} \\ 
+N Right & \multicolumn{1}{c}{2715} & \multicolumn{1}{c}{3624} & \multicolumn{1}{c}{1802} & \multicolumn{1}{c}{1738} \\ 
+Eff N Left & \multicolumn{1}{c}{1210} & \multicolumn{1}{c}{780} & \multicolumn{1}{c}{1210} & \multicolumn{1}{c}{1255} \\ 
+Eff N Right & \multicolumn{1}{c}{890} & \multicolumn{1}{c}{664} & \multicolumn{1}{c}{728} & \multicolumn{1}{c}{752} \\ 
+BW Loc Poly & 4.838 & 2.807 & 6.364 & 6.873 \\ 
+BW Bias & 7.143 & 8.041 & 9.68 & 10.291 \\
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
+RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
 
-The service that best secures votes, according to 84.3\% of the interviewed, is access to hospital facilities; to 56.0\%, it is school admission; and to 71.0\%, it is access to medication.
-82.6\% of respondents confirm that local public goods are electorally beneficial, and 50.2\% indicated that, namely, fixing potholes on public roads resulting in some or many votes.
-Second in their evaluation is public school quality oversight (34.7\%), followed by  reported public construction oversight (25.3\%).
-These last two services, despite being preferred by voters and easy to credit-claim, require more investment.
-Coordination costs related to mayor negotiation and bureaucratic mediation also force them to recur to less demanding options, for instance, honors legislation.
-This is likely the reason why more approved bills fall under the \textit{others} label than under \textit{oversight}.
+Table \ref{tab:outcomes} shows that increasing the city council in one legislator generates welfare improvement in municipalities.
+In healthcare, increasing legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
+This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
+Moreover, postneonatal mortality decreases by 0.90 casualties per 1,000 births, which remains around the 0.14 standard deviations improvement as infant mortality.
+Infant mortality is a primary outcome for welfare, and it correlates with several other indicators of well-being \citep{world2005health}.
+The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in sizable welfare effects.
+As expected, placebo regressions were statistically insignificant.
 
-\section{Discussion}
+In terms of education, with the addition of a city councilor, enrollment in elementary schools increased by 2.58 children on average per school.
+This represents a change of around 0.20 standard deviations.
+Besides the influence of the mayoral support, enrollment can also directly impact the councilor's representation: Councilors can pressure the bureaucracy to accommodate a few extra students.
+With support from the mayor, they can help voters get access to schools, improving the voter's welfare.
+The education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
+As expected, the placebo regressions are insignificant.
 
-%CLIENTELISM
+# Discussion
 
-Although city councillors should have governing advantages for being the closest representatives to citizens, the literature often presents them as inefficient and clientelistic \citep{Castroetal2009, AlmeidaFelix2012, leal2012coronelismo}.
-This proximity to the community results in better informed decision-making and accountability.
-However, it also creates perverse incentives to corruption, patronage and overprovision of electorally beneficial services.
-Poor management could be driven by private interests, or by limitations restraining governability.
-It is unrealistic to think that all politicians have free rein to approve and implement policies at their will.
-Bureaucracy and strong executives balance the assembly, who, in turn, develops strategies to enforce its will.
+This paper shows that partisanship considerably decreases bargaining costs, improving welfare.
+The crucial actors in providing public goods are the mayors, but they cannot do it alone.
+Legislatures are a solid check to the mayor's policy.
+Bargaining with them in a country plagued by corruption can be costly \citep{bertholini2017price}.
+Therefore, an extra ally in the city council may help ease the bargaining and improve welfare.
 
-A councillor can only provide services which she can control or influence.
-In a Brazilian municipality, mayors directly control budget and staff allocation.
-Consequently, councillors must side with the mayor to participate in policy-making.
-Efforts towards establishing alliances start in the pre-electoral coalition period.
-If a candidate is part of the mayoral coalition, she credibly signals being able to deliver her platform promises.
-As the Electoral Justice allocates seats according to vote shares (D'Hondt method), pre-electoral coalitions have advantages since extremely popular candidates' votes thrust smaller candidates into office.
-Pre-electoral coalitions become crucial for mayors' governability after the election.
+Increasing the council size results in gains in elementary school enrollment and decreases infant mortality.
+Education quality remains unchanged but increasing enrollment without affecting quality should be interpreted as positive.
+The analysis of the legislation approved shows that the frequency of local public goods legislation increases in municipalities above the council size thresholds.
+Finally, the city council survey demonstrates that councilors and mayors align regarding appointing more public servants to the public administration.
 
-Bureaucrats also mediate most of the access to resources, and may filter councillor's demands, either for or against them.
-To influence service provision, city councillors sometimes recur to patronage, which is a strategy mobilized to ensure collaborative administrations.
-It is characterized by the employment of bureaucrats attached to an incumbent's personal figure.
-These politically-appointed employees have incentives to support the councillor's interests unconditionally \citep{Robinson2013}.
-Loyalty of the administration – through patronage or not – thus appears as fundamental in the political game.
+\citet{Ames2001} argues that the Brazilian democracy is deadlocked because the Executive has its hands tied by a legislature that demand constantly provision of particularistic and private goods.
+Indeed, the most successful presidents after 1995 had to build multiparty coalitions by negotiating with parties \citep{limongi1998bases, raile2011executive}.
+Despite evidence that side payments cemented these coalitions, many social and economic policies have been implemented.
+For instance, education and healthcare improved tremendously during the Cardoso and Lula governments \citep{acemoglu2012nations}.
+Of the presidents that defied the coalition system, Rousseff was impeached in her second term.
+Bolsonaro can be considered one of the most ineffective presidents in Brazilian history.
 
-Another limitation to representative agency is based on perception, as politicians imperfectly observe voters' preferences.
-The online survey provides us with clues on how councillor's beliefs could translate into their policy choices.
-\textit{Local public goods} is the preferred type of legislation across sources.
-We assembled five specific welfare-improving policies into the \textit{local public goods} category (Figure \ref{survelec}), namely \textit{hospital admission aid} (84.3\% answered it gives some to many votes), \textit{other local public goods} (82.6\%), \textit{access to medication} (71.0\%), \textit{school admission aid} (56.0\%), and \textit{street repairs} (50.2\%).
-They all pushed down remaining categories.
-\textit{School quality oversight} places second at overwhelming distance (34.7\%).
-In the approved legislation dataset (Graph 2A, Figure \ref{LEGAPPR}), \textit{local public goods} is equally favoured (72.9\%), followed by \textit{others} legislation (17.4\%), which we know to represent mostly honors bills.
+Municipalities work very similarly in terms of the incentives for legislative-executive bargaining.
+The stakes are lower, and the negotiations involve only one legislative branch.
+Still, in a system such as the Brazilian, with more than thirty-five registered parties, mayors have a difficult task in aggregate and consolidate support for their agendas.
+Having extra help in the council can tilt the bargaining towards cheaper governing, improving public goods provision.
 
-If councillors aim for reelection, why do approved legislation frequencies not reflect answers to the survey?
-Comparison points to an inconsistency that circles back to the aforementioned limitations.
-Since negative exposure of executive and bureaucratic underachievement tensions political coalitions, and is less attractive to voters than policy-making.
-Logically, councillors will dedicate more to \textit{local public goods} than to \textit{oversight}.
-This does not attest their lack of competence, efficiency or honesty, but rather evidences the hardship of coordinating efforts and collectively making decisions under diverging goals and interests.
+Moreover, this paper is not arguing that these benefits result from the absence of corruption or clientelism.
+Both the formal model and empirical evidence by \citet{britto2020corruption} show that corruption increases with legislature size.
+As the model shows, city councilors receive a side transfer from mayors to support their agenda.
+Mayors also divide the resources saved in the bargain into public goods and rents.
+The rate for the division depends on the marginal changes of the rents and public goods, but these two components receive the extra resources.
+In this case, the mayor's rents may be primarily corruption, and the councilor's transfers can be clientelistic, aimed at improving the councilor's reelection chances.
 
-# Conclusion
-\label{sec:conclusion}
-
-In this paper, we argue that political motivation determines the services that gain traction with larger legislatures.
-Councillors, guided by reelection, invest in policies they believe voters want and for which credit-claiming is feasible.
-Consequently, many essential welfare services are underprovided, giving place to locally-targeted policies.
-For instance, our theory explains why patterns of poor education persist in developing countries.
-In 2000, among the 32 countries that participated in the OECD's \textit{Programme for International Student Assessment} (PISA), Brazil ranked last.
-Between 2006 and 2015, there were virtually no improvements in scores.
-Counterintuitively, school enrolment was close to 99\% since 2010.
-Although desired by voters, ameliorating education quality is difficult to trace back to specific politicians.
-In this logic, they have incentives to target education through tangible yet low-reaching measures, such as raising the amount of children attending schools.
-
-We run a RDD to capture the effect of adding representatives to a municipal council.
-We focus on the effects of exogenously imposing thresholds to chamber sizes.
-We compare cities with similar populations, but located on different sides of the cutoff.
-We also collect data on the approved legislation during the 2005-2008 term, and perform an online survey with former representatives.
-Empirically, larger municipal chambers prevents death in infancy and stimulate educational enrollment.
-These changes do not, however, coincide with improvements in education and health care quality.
-We find that councillors prefer investing in local public goods, and they access resources via attachment to mayors and through bureaucratic mediation.
-
-Our study has implications for policy-making and for the literature on distributive politics.
-First, we provide tools to predict welfare effects of changing the number of seats in municipal councils.
-We also contribute to comprehend the strategies politicians may use to adapt to these modifications.
-For example, an extra legislator will hardly add diversity to council activities, since there is a 91\% probability she will integrate the mayoral coalition.
-As for academia, we offer a simple theory to understand the underprovision of essential public goods as education and health care.
-We add complexity to the common belief that politicians in developing countries are purely clientelistic, inefficient or dishonest.
-We conclude that the political architecture of the assembly floor creates perverse incentives.
+This paper opens two critical questions for future analysis.
+First, if the mechanism I claim is at work, more support means better public goods, which brings the question: Why having a city council, if when the city council checks the mayor, public goods provision may decrease?
+The evidence is inconclusive, and \citet{poulsen2018political} show that checks for the mayors also improve service provision.
+It may be that there is a non-linear effect in the relation between rents and public goods, making after some threshold mayors revert to only rents.
+Moreover, it could be that after some threshold of support, support is ineffective and even harmful, as it may trigger an intense form of elite capture.
+This question needs further investigation, and my results suggest that mayors with more support improve welfare.
+Second, it remains uncertain how other legislative design parameters affect welfare.
+For example, city councils may vary in size and the monetary compensation for councilors, committee structure, and internal power structure.
+These components may interact with size and within each other, and understanding how size plays with other features would contribute to building a better theory of how the city council size affects welfare.
+Both these questions are crucial for institution design and welfare in developing democracies.
 

### 2021-10-01 appendix/appendix.Rmd
proofreading the appendix

@@
 
+[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+
 [^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
 
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
-
 \appendix
-\addtocounter{section}{2}
+\addtocounter{section}{1}
 
@@
 
-### Primitives of the Model
-
-Consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor is the head of the local executive branch and has the prerogative of proposing a vector of policies voted by the city councilors.
-Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.
-
-The city council votes the mayor's proposal, and if they accept it, it is implemented.
-Otherwise, a reversal policy takes place.
-Reversal policy in this context means that the mayor's proposal failed to secure the majority of council votes.
-The decision process leaves the mayor's office and either immediately stops or is transferred to the council.
-The types of reversal policies are crucial for my argument, as it changes the relative strength of the council in their bargaining with the mayor.
-I investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided into supporters and non-supporters of the mayor; and finally, a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features.
+### Model Primitives
+
+Consider an strategic interaction between a mayor $M$ and $N \geq 3$ city councilors indexed as $i \in \{1, 2, \cdots, N \}$.
+The mayor is the head of the local executive branch and submits policy proposals to the city councilors.
+Policy proposals comprise funds allocated to public goods provision ($g$), rents for the mayor ($r$), and transfers to the city councilors (\textbf{x}).
+
+The city council votes the mayor's proposal, which is implemented if they accept it.
+Otherwise, a reversal policy takes place, indicating that the mayor failed to secure the majority of the councilors' votes.
+In this case, the policy proposal either stops or is transferred to the council.
+The different types of reversal policies are crucial for our argument, as they change the bargaining position of the councilors relative to the mayor.
+We investigate three types of reversal policies: 1) a \textit{non-partisan} reversal mechanism, in which city councilors have no partisan affiliation; 2) a \textit{partisan} reversal mechanism, where the council is divided into supporters and non-supporters of the mayor; 3) and finally, a \textit{hybrid} reversal mechanism, which combines partisan and non-partisan features.
 The main paper focuses on the hybrid model, as it is the more realistic scenario.
-Despite that, comparing the partisan and non-partisan reversal mechanisms clearly illustrates my argument that the partisan mechanism drives my results.
-
-The mayor has to convince at least half of the city councilors to support her policy proposals.
-Similar to \citet{buenodemesquita2005logic}, I assume that the selectorate, i.e., the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
-The winning coalition, the minimum number of members who have to be convinced to implement the policy, equals half of the selectorate $N/2$.
-City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
-I leave the definition of these transfers open, as this facilitates the relationship with several instruments that mayors can use to pressure city councilors.
-To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, giving portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
-The use of transfers affects the councilors' choices and generates a governing cost of $C_G$.
-The governing costs vary with the reversal mechanism and the legislature size.
-
-Finally, after paying the govern costs, the mayor proposes a level of public goods provision ($g$) and rents ($r$).
+However, comparing the partisan and non-partisan reversal mechanisms provides further evidence that the partisan mechanism drives our results.
+
+The mayor needs to secure the support of at least half of the city councilors to implement his or her policy.
+Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate is composed by the $N$ city councilors.
+That is, these are the individuals who have a say in the mayor's policy proposals.
+The winning coalition, which is the minimum number of members required to implement the policy, equals half of the selectorate ($N/2$).
+City councilors are motivated by policy concerns $p$ and transfers received either from the mayor or from a councilor \textbf{x} who proposes the policy.
+We leave the content of these transfers open, as this allows us to analyze how mayors combine transfers with other incentives to pressure city councilors.
+For instance, a mayor may grant councilors electoral favors, spend in areas where they have political or personal interests, offer portfolio or public sector jobs to associates, or even provide campaign contributions and bribes.
+These transfers affect the councilors' decisions and generate governing costs $C_G$.
+Governing costs vary according to the type of reversal mechanism and the size of the legislature.
+
+Finally, after paying the aforementioned governing costs, the mayor proposes some level of public goods provision $g$ and rents $r$.
 Public goods provision helps the mayor to get reelected.
-Rents are for direct mayor's consumption and do not contribute to the mayor's electoral success.
-This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
-Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
-I assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
+Rents are for the mayor's direct benefit and do not contribute to his or her electoral success.
+This makes the mayor's expected utility a sum of the gains from rents plus the benefits from reelection.
+Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or more public goods increase his or her utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
+This benefit captures the tangible and intangible gains the mayor receives from holding the public office.
+We assume these benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
 If the mayor's policy proposal is approved, then the expected utility for the mayor is:
@@
 
-The policy choices of the mayor are subject to the municipal budget constraint.
-The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget must be balanced.
-I also assume that there are enough resources for the mayor to govern.
-
-Let $C_G$ be the costs of governing. The budget balance constraint requires the offers that the mayor makes to the city councilors to satisfy the following inequality:
+The mayor's policy choices are subject to municipal budget constraints.
+The municipality has $R > 0$ resources and cannot run deficits, that is, it must always balance its budget.
+We also assume that there are enough resources for the mayor to govern.
+
+Let $C_G$ be the mayor's governing costs. The budget balance constraints implies that mayors will only offer public services and rents that satisfy following inequality:
 
@@
 
-The expected utility for the city councilors depends on the reversal policy.
-As discussed, I explore three different mechanisms.
-First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
+The expected utility for the city councilors depends on which reversal policy takes place.
+As mentioned above, we explore the implications of three different mechanisms.
+First, in the \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor $\delta \in (0,1)$ and with the random selection of one councilor.
 The randomly selected councilor becomes the new proposer.
 If her proposal is accepted, it is implemented.
-If rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to propose.
-The process repeats until one proposal is finally accepted.
-
-In the second reversal mode, the \textit{partisan} reversal mechanism, I assume that each councilor has a party affiliation.
-Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once).
-If a city councilor is affiliated to a party aligned with the mayor, I say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
+If rejected, the budget shrinks again by a factor $\delta$, and another city councilor is chosen to propose the policy.
+The process continues until one proposal is finally accepted.
+
+In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation.
+Party affiliations are mutually exclusive, that is, one councilor cannot belong to two parties at once.
+If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
 Otherwise, the city councilor belongs to the opposition $O = \{1, 2, \cdots, N \} \setminus G$.
-The mayor's policy generates a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends on the party affiliation of the councilor.
-If the mayor's proposal is rejected, a city councilor aligned with the mayor that should have received $p$ from the policy now receives zero.
-On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy and now receive zero.
-Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in public goods provision are shared by councilors aligned with the mayor.
-Voting against the mayor's proposals would represent defying the partisan label.
-
-Lastly, in the \textit{hybrid} reversal mechanism, I combine partisanship with legislature bargaining costs.
-Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan reversal mechanism takes place.
-In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented.
-On the other hand, opposition members receive $-p$ when the mayor's proposal is implemented.
-If the mayor's proposal is rejected, as the city council does not control the Executive when the two branches are separated, no public goods are provided ($p=0$).
-Moreover, in equilibrium, I assume that city councilors would prefer to receive transfers instead of providing public goods.
-This aligns with the empirical evidence in most developing economies.
+The mayor-sponsored policy generates a political value of $p > 0$ for the councilors, and whether this adds or reduces the councilor's utility depends on his or her party affiliation.
+If the mayor's proposal is rejected, a city councilor aligned with the mayor receives zero instead of $p$.
+In contrast, a city councilor from the opposition receives zero if the proposal is rejected and $-p$ if is is enacted.
+Although these assumptions are rather strong, they capture the underlying political dynamics of political partisanship, in which councilors and mayors in the same coalition share similar policy preferences.
+Voting against the mayor's proposals defies the partisan logic.
+
+Lastly, in the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining costs.
+Here councilors receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan mechanism takes place.
+In the mayor's proposal stage, city councilors in the mayor's coalition receive a benefit of $p > 0$ when the mayor's policy is implemented.
+Opposition members receive $-p$ if the mayor's proposal is implemented.
+In case the mayor's proposal is rejected, as the city council does not control the executive when the two branches are separated, there is no provision of public goods ($p=0$).
+Moreover, in equilibrium, we assume that city councilors prefer to receive transfers instead of providing public goods.
+This is in line with the empirical evidence from most developing economies [e.g., @FerrazFinan2011; @Nichter2010].
 
@@
 \begin{enumerate}
-  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
+  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators have been elected.
   \item The mayor proposes a policy vector $(r, g, x)_M$.
@@
   \begin{itemize}
-    \item If the council accepts, the policy is implemented, and the game ends. 
-    \item Otherwise, the reversal policy is implemented.
+    \item If the council accepts the proposal, it is implemented and the game ends.
+    \item Otherwise, a reversal policy is implemented.
   \end{itemize}
-  \item (Reversal Policy) Depends on which mechanism, I propose three different reversal policies. The details are in the following sections.
+  \item (Reversal Policy) We propose three reversal policies, namely \textit{partisan}, \textit{non-partisan}, and \textit{hybrid}.
+We have introduced them above and will discuss them in further detail in the following sections.
 \end{enumerate}
 
-The solution concept I use in this model is the Sub-game Perfect Nash Equilibrium.
-A Sub-game Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game.
-The solution is found using backward induction.
-In the model with infinitely repeated proposals, I extend the equilibrium concept to require that the equilibrium is Stationary.
-A Stationary Sub-game Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should take the same offer at time $k$.
-Stationarity provides the intending to find a proposal that would be accepted at any stage in the game.
-Applying this reasoning, I can find a sequence of offers for each point $k$ in time.
-For the mayor, the optimal offer is at $k=0$, representing a no delay in policy implementation.
+The solution concept we use in this model is the subgame perfect Nash equilibrium.
+This game requires that the strategies follow a Nash equilibrium in each subgame.
+We find the solution by backward induction.
+In the model with infinitely repeated proposals, we extend the equilibrium concept and require that the equilibrium is stationary.
+This implies that if the politician accepts an offer at time $k+1$, they should take the same offer at time $k$.
+This assumption holds at each point of the game.
+Stationarity provides a method to find a proposal that the politician accepts at any stage in the game.
+In our case, the optimal offer for the mayor is at $k=0$, which indicates an immediate policy implementation.
 
 \begin{definition}
-The equilibrium for the game consists of a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
+The game equilibrium consists of a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that the mayor and the councilors have no profitable deviations from the equilibrium at any stage of the game.
 \end{definition}
 
-Moreover, I assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.
+Moreover, we assume that players have no dominated strategies, even if the policy is not implemented due to insufficient support.
 
@@
 
-Solving the game by backward induction requires me to start with the councilor's strategies.
-However, for exposure convenience, assume that I solved the game for the councilors and found the equilibrium cost of governing $C_G(N)$ when there are $N$ city councilors.
-In the next section, I define $C_G(N)$ for each mechanism using backward induction, and the definitions are well-behaved.
-In this section, I use this assumption to simplify the exposition.
-
-I now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
-The mayor benefits from public goods provision, as it increases the chances of her reelection.
-However, she prefers to contribute as minimum as necessary for the public goods and extract the remaining resources as political rents.
-The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.
+Solving the game by backward induction requires us to know which strategies councilors may adopt.
+However, assume for now that we have solved the game for the councilors and found the equilibrium cost of governing $C_G(N)$ when there are $N$ city councilors.
+In the next section, we define $C_G(N)$ for each mechanism using backward induction and show that the definitions are well-behaved.
+Here we start from this assumption just to simplify our exposition.
+
+We derive the optimal rents ($r$) and public goods provision ($g$) a mayor should propose.
+Mayors benefits from public goods provision, as it increases their chances of reelection.
+However, they would rather provide the lowest necessary amount of public goods and extract the remaining resources as political rents.
+As we noted previously, their objective is to maximize their expected utility, subject to the municipal budget constraint.
 
@@
 
-In equilibrium, the budget binds, and the provision of the public goods maximizes:
+In equilibrium, the budget binds, and the provision of the public goods maximizes to:
 
@@
 
-The first-order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:
+The first-order condition for an optimal public goods provision makes the marginal benefits of increasing rents---in this case, the marginal costs of providing the public goods---equal to the marginal benefits of reelection:
 
@@
 \begin{proposition}
-The provision of public goods increases with legislature size when the costs of governing decrease with legislature size.
+Public goods provision increases with legislature size if governing costs decrease with legislature size.
 \end{proposition}
@@
 \begin{proof}
-To prove this result, I need to show that the mayor's expected utility satisfies the increasing differences in $g$ and $N$.
-This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase.
-However, as $N$ increases discretely, I cannot take the cross-partial derivative on $N$ or even use the implicit function theorem.
-Instead, I use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
-
-The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} I have:
+To prove this result, we need to show that the mayor's expected utility satisfies the increasing differences in $g$ and $N$.
+This means that, when increasing the size of the council, the optimal solution $g^*$ should also increase.
+However, as $N$ increases discretely, we cannot take the cross-partial derivative on $N$ or use the implicit function theorem.
+Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
+
+The mayor's expected utility satifies the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{The requirement that the decision and type space are a complete lattice is satisfied for $\mathbb{R} \times \mathbb{N}$.} we have:
 
@@
 
-After substituting, I have:
+After some substitutions, we have:
 
@@
 
-Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, I have:
+By multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:
 
@@
 
-It is now clear to see that the function satisfies the increasing differences in $g$ and $N$ when the governing costs of a $N+1$-sized city council are lower than the governing costs of a $N$-sized city council:
+It is now clear that the function satisfies the increasing differences in $g$ and $N$ when the governing costs of a $N+1$-sized city council are lower than the governing costs of a $N$-sized city council:
 
@@
 
-This provides the first empirical hypothesis to test: \textit{if the governing costs decrease when the legislature increases, then the public goods provision increase when the legislature size increase}.
-
-At this stage, I need to solve for the existence of these governing costs.
-Below I show that this proposition is valid for the *partisan* and *hybrid* mechanisms, but it is not suitable for the *non-partisan* mechanism.
+This provides the first empirical hypothesis we test in our article: \textit{public goods provision increases along with legislature size, but only if governing costs decrease when legislature size increases}.
+
+At this stage, we need to solve for the existence of these governing costs.
+In the following sections we show that while this proposition is valid for the *partisan* and *hybrid* mechanisms, it is not applicable to the *non-partisan* mechanism.
 
@@
 
-In the \textit{non-partisan reversal} mechanism, I assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
-To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and the game is at the $k$-th stage.
-A councilor accepts the proposer's offer if, and only if, to get the offer at $k$ is better than to wait until the next stage $k+1$.
+In the \textit{non-partisan reversal} mechanism, we assume that if the council rejects the mayor's proposal, a reversal policy starts with the random selection of one councilor.
+To find the stationary subgame perfect Nash equilibrium, suppose that there were $k-1$ rejections and the game is at the $k$-th stage.
+A councilor accepts the proposer's offer if, and only if, getting the offer at $k$ is better than waiting until the next stage $k+1$.
 If the offer is $x_i$, then:
@@
 
-On the left-hand side, I place the offer.
-On the right-hand side, there are two components.
-The first is the amount that the councilor $i$ gets when she is the proposer.
-It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers she has to make to convince half of the councilors.
-The second part is the gains if the councilor rejects the current received offer but still gets an offer in the following round.
-It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the transfer amount.
-Note that the councilor's offer as the proposer is the same as the offer she wants to receive.
-This is because the city councilors are exchangeable.
-The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, I could have dropped the $i$ in the solution).
-After some algebra, the offer $x_i$ has to be greater than or equal to:
+We place the offer on the left-hand side.
+There are two components on the right-hand side.
+The first is the amount that the councilor $i$ receives when he/she is the proposer.
+The amount is equal to the chance that they are recognized as the proposer, times the budget in the next round, minus the offers they have to make to convince half of the councilors.
+The second part denotes the gains obtained by the councilor if he/she rejects the current offer but still receives an offer in the following round.
+This is equal to the chance that they are not recognized as the proposer, times the chance that they receive a transfer, times the transfer amount.
+Note that the councilor's offer as the proposer is the same as the offer they want to receive, as city councilors are exchangeable.
+The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution).
+After some calculations, the offer $x_i$ has to be greater than or equal to:
 
@@
 
-Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
+Proceeding backwards, at the mayor's proposal stage $k=0$, the mayor offers $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
 In this context, the governing costs for the mayor are:
@@
 \begin{proposition}
-In the \textit{non-partisan reversal} mechanism, the governing costs always increase when the size of the legislature increases.
+In the \textit{non-partisan reversal} mechanism, governing costs always increase when legislature size increases.
 \end{proposition}
@@
 
-The difference in costs when there are $N+1$ city councilors versus when there are $N$ city councilors is equal to:
+Comparing city councils of size $N$ with those of size $N+1$, we find that the difference is costs is:
 
@@
 
-Therefore, the costs always increase when the size of the legislature increases.
+Therefore, costs always increase when legislature size increases.
 
@@
 \begin{corollary}
-In the \textit{non-partisan reversal} mechanism, public goods provision decreases as the legislature size increases.
+In the \textit{non-partisan reversal} mechanism, public goods provision decreases as legislature size increases.
 \end{corollary}
 
-This result is crucial to understand the role of politics in my model.
-If the governing costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-In my case, I show that there is a \textit{political} reason for increasing the public goods provision.
+This result is crucial for us to explain the role of politics in our model.
+If governing costs increase with legislature size, then any increase in public goods provision associated with legislature size comes from a different mechanism.
+In this case, we show that there is a \textit{political} reason to increase the provision of public goods.
 
@@
 
-I now look into the other extreme, which is a fully politicized legislature.
+We now focus on the other extreme, which is a fully politicized legislature.
 In this case, when the mayor implements the policy, it generates a value of $p > 0$.
 A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a cost of $-p$.
-Moreover, as in the non-partisan reversal, the mayor can choose to distribute $x_i$ private goods for a legislator $i$.
+Moreover, as in the non-partisan reversal, the mayor may choose to distribute $x_i$ private goods for a legislator $i$.
 In this case, when the policy is implemented, the aligned legislator's utility equals $x_i + p$.
-When the legislator is not aligned with the mayor, her utility equals $x_i - p$.
-If the policy is not implemented, then I assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
+When the legislator is not aligned with the mayor, their utility equals $x_i - p$.
+If the policy is not implemented, then we assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
 
 A legislator aligned with the mayor always supports the mayor's policy, regardless of receiving private goods.
-This is because as $p > 0$, the councilor always receives positive benefits from the policy.\footnote{The mayor could even impose a cost to the city councilors aligned with the government.
-Although this seems unrealistic, it is mostly the case when government-aligned legislators are recognized to draft legislation for the mayor's office or even take the fallout from a failed policy.} However, politicians not aligned with the mayor require compensation when their votes are needed.
+This is because $p > 0$, that is, the councilor always receives positive benefits from the policy.\footnote{The mayor could even impose costs to aligned city councilors.
+Although this seems unrealistic, it is mostly the case when government-aligned legislators are called to draft legislation for the mayor's office or to take the fallout from a failed policy.} However, politicians who not aligned with the mayor require compensation when their votes are needed.
 In this case, if the mayor's proposal requires the support of an opposition politician, then the mayor compensates the councilor for the policy costs.
@@
 Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
-Then, the costs of governing when the legislature size is $N$ is equal to the expected number of politicians in the opposition that the mayor has to compensate minus the amount needed to implement the policy, in this case, half of them:
+Then, the governing costs when the legislature size is $N$ equals the expected number of opposition members the mayor has to compensate, minus the amount needed to implement the policy.
+In this case, it is half of the city council:
 
@@
 \begin{proposition}
-In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than one-half, then the costs of govern decrease as the legislature size increases.
+In the \textit{partisan reversal} mechanism, if the chances of electing a mayor-aligned politician are greater than $1/2$, then governing costs decrease as legislature size increases.
 \end{proposition}
@@
 
-The differences in costs when there are $N+1$ versus when there are $N$ legislators are equal to:
+When we compare the difference in costs between $N$ and $N+1$ legislators, we find that:
 
@@
 
-Therefore, when $\gamma < \dfrac{1}{2}$, the costs of govern increase. Otherwise, the costs decrease.
+Therefore, when $\gamma < \dfrac{1}{2}$, governing costs increase. Otherwise, such costs decrease.
 
@@
 \begin{corollary}
-In the \textit{partisan reversal} mechanism, if the chance of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as the legislature size increases.
+In the \textit{partisan reversal} mechanism, if the chances of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as legislature size increases.
 \end{corollary}
 
-This result shows that when the chances of electing an aligned politician are sufficiently high, the government costs decrease.
-As a response, the public goods provision (and also rents) increase.
-The rate distribution between these two vectors is determined by the marginal change in the utility from rents and the utility from reelection.
-In any case, the amount allocated for both increases.
+This result shows that, when the likelihood of electing an aligned politician is sufficiently high, governing costs tend to decrease.
+Consequently, the provision of public goods tends increases, as well as the rents.
+The marginal change in the utility from rents and the utility from reelection determines the allocation between these two vectors.
+In any case, the amount distributed to both increases.
 
@@
 
-The \textit{hybrid reversal} mechanism combines both partisan and non-partisan motivations. In the hybrid mechanism, a city councilor aligned with the government favors the mayor's offer if:
+The \textit{hybrid reversal} mechanism combines both partisan and non-partisan motivations. Here, a city councilor aligned with the government favors the mayor's offer if:
 
@@
 
-An opposition politician, on the other hand, favors the mayor's offer if, and only if:
+An opposition politician, in contrast, favors the mayor's offer if, and only if:
 
@@
 
-I can decompose these costs into two components—first, the costs in terms of rents.
+We divide these costs into two components.
+First, the costs in terms of rents.
 Second, the costs (or benefits) from political alignment.
-In this context, the governing costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's proposals for councilors in the opposition.
-The ex-ante chance of an opposition member be elected equal to $1-\gamma$, and taking the weighted averages, these costs become:
+In this context, governing costs depend on what the mayor offers to their supporters in the council versus what they provide to members of the opposition.
+The ex-ante chance of an opposition member being elected is equal to $1-\gamma$, therefore, after taking the weighted averages, these costs become:
 
@@
 \begin{proposition}
-In the \textit{hybrid reversal} mechanism, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then the costs of govern increase as the legislature size increases.
-Otherwise, the costs decrease when the legislature size increases.
+In the \textit{hybrid reversal} mechanism, if $\gamma \leq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right]$, then governing costs increase as legislature size increases.
+Otherwise, such costs decrease when legislature size increases.
 \end{proposition}
@@
 
-The difference in costs when there are $N+1$ city councilors versus the costs when there are $N$ councilors is equal to:
+When we compare the costs of $N$ versus $N+1$ legislators, we find that:
 
@@
 
-The conditions for the differences in governing costs decrease when the legislature size increases are:
+The conditions for the difference in governing costs to decrease when legislature size increases are as follows:
 
@@
 \begin{corollary}
-In the \textit{hybrid reversal} mechanism, when the chances of electing a city councilor aligned with the mayor are sufficiently high, then increasing council size lowers the bargaining costs for mayors.
+In the \textit{hybrid reversal} mechanism, when the chances of electing a mayor-aligned city councilor are sufficiently high, then increasing council size lowers the bargaining costs for mayors.
 \end{corollary}
 
-The threshold $\underline{\gamma}$ for the probability of electing a politician aligned with the government is decreasing in the value of the mayor's policy $p$ and the legislature size $N$.
-This means that higher political values and larger legislatures make it easier to satisfy the electoral threshold.
+The threshold $\underline{\gamma}$ for the probability of electing an aligned politician decreases according to the value of the mayor's policy $p$ and the legislature size $N$.
+Higher political values and larger legislatures make it easier to satisfy the electoral threshold.
 
@@
 
-Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators that increase its council size to $N+1$. Then:
+Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators that increase its size to $N+1$. Then:
 
 \begin{enumerate}
-  \item[H1. ] The governing costs decrease with legislature size when the chance of electing a government-aligned legislator is sufficiently high.
-  \item[H2. ] The provision of public goods increase when the governing costs decrease with legislature size.
+  \item[H1. ] Governing costs decrease with legislature size when the chances of electing a government-aligned legislator are sufficiently high.
+  \item[H2. ] Public goods provision increases if governing costs decrease with legislature size.
 \end{enumerate}
 
-In the paper, I show that the provision of education and healthcare improves in Brazil. This results from the fact that the chances of electing a city councilor aligned with the mayor are 91%.
+In the main paper, we show that larger legislatures improve the provision of public education and health care in Brazil.
+What drives this result is the 91% chance of electing a mayor-aligned city councilor to the local chamber.
 
@@
 
-I use three information sources, either from Brazilian governmental agencies or available online. Table \ref{varsources} displays the primary sources and their respective URLs.
-
-\begin{sidewaystable}[!htbp] \centering 
+We use three data sources in our work, mainly from Brazilian governmental agencies. Table \ref{tab:varsources} displays the primary sources we use here and their respective URLs.
+
+\begin{table}[!htbp] \centering
+\small
 \caption{Data Sources}
-\label{varsources}
+\label{tab:varsources}
 \scalebox{0.8}{
@@
   \\[-1.8ex]\hline\hline \\[-1.8ex]
-  Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{URL} \\ 
+  Source Code & \multicolumn{1}{c}{Source Name} & \multicolumn{1}{c}{Data Provided} & \multicolumn{1}{c}{URL} \\
   \hline \\[-1.8ex]
   & & & \\
-  DataSUS & Brazilian Health Ministry Data Service & Collects data on Health Care & \url{http://www.datasus.gov.br} \\
+  DataSUS & Brazilian Health Ministry Data Service & Health care data & \url{http://www.datasus.gov.br} \\
   & & & \\
-  IBGE & Brazilian Institute of Geography and Statistics & Collects data Geography, Economics and Demography & \url{http://www.ibge.gov.br} \\ 
+  IBGE & Brazilian Institute of Geography and Statistics & Geographic, economic, and demographic data & \url{http://www.ibge.gov.br} \\
   & & & \\
-  INEP & Data Service of Ministry of Education & Collects data on performance of Education & \url{http://www.inep.gov.br} \\ 
+  INEP & Ministry of Education Data Service & Education performance & \url{http://www.inep.gov.br} \\
   & & & \\
-  InterLegis & Senate Legislative Data Service & Collect Data on Legislative in Brazil & \url{http://www.interlegis.leg.br} \\
+  InterLegis & Senate Legislative Data Service & Legislative data & \url{http://www.interlegis.leg.br} \\
   & & & \\
-  IPEA & Brazilian Institute of Applied Economics & Collects data on the Economy & \url{http://www.ipeadata.gov.br} \\ 
+  IPEA & Brazilian Institute of Applied Economics & Economic data & \url{http://www.ipeadata.gov.br} \\
   & & & \\
-  MDS & Social Security Ministry & Collect data on Social Coverage and Effectiveness of Social Programs & \url{http://www.mds.gov.br} \\ 
+  MDS & Social Security Ministry & Coverage of social programs & \url{http://www.mds.gov.br} \\
   & & & \\
-  TSE & Superior Electoral Tribunal & Collects data on elections results & \url{http://www.tse.jus.br} \\
+  TSE & Supreme Electoral Court & Electoral data & \url{http://www.tse.jus.br} \\
   & & & \\
@@
 }
-\end{sidewaystable}
+\end{table}
+\normalsize
 
@@
 \begin{itemize}
-\item \textbf{Number of Seats 2000}: Number of councilors in the municipality in 2000 (source: TSE).
-\item \textbf{Population 2000}: Municipal population according to the 2000 Brazilian Census (source: IBGE).
-\item \textbf{Per-Capita GDP 2000 (in millions)}: Municipal per-capita GDP computed by the Brazilian Census (source: IPEA).
-\item \textbf{Proportion of Poverty 2000}: Proportion of poverty in the municipality defined as people living on less than R\$ 70.00 a month (source: Social Development Ministry [MDS]).
-\item \textbf{Number of Seats 2004}: Number of city-councilors in a municipality according to the Electoral Justice decision (source: TSE).
-\item \textbf{Infant Mortality 2005--2008}: Infant mortality computed as the number of children born alive that died before reaching one year of age divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-\item \textbf{Postneonatal Mortality 2005--2008}: Infant mortality computed as the number of children that lived at least 28-days, but died before reaching one year of age divided by the number of children that reached 28-days alive, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Number of Seats 2000}: Number of city councilors in 2000 (source: TSE).
+\item \textbf{Population 2000}: City population according to the 2000 Brazilian Census (source: IBGE).
+\item \textbf{Per-Capita GDP 2000 (in millions)}: Municipal per capita GDP measured by the Brazilian Census (source: IPEA).
+\item \textbf{Proportion of Poverty 2000}: Percentage of citizens earning less than R\$ 70.00 per month (source: Social Development Ministry [MDS]).
+\item \textbf{Number of Seats 2004}: Number of city councilors in 2004 according to the Electoral Court (source: TSE).
+\item \textbf{Infant Mortality 2005--2008}: Number of children who died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Postneonatal Mortality 2005--2008}: Number of children alive for at least 28 days who died before reaching one year of age, divided by the total number of children who lived for 28 days, multiplied by 1,000 (source: DataSUS)
 \item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
-\item \textbf{Quality of Elementary School Index 2005--2008}: IDEB score averaged by schools in the municipality.
-IDEB scores are composed of the student's grades in math and language, multiplied by an indicator of the distortion between the year the child is supposed to be and the year the child is.
-The INEP reweights the estimators to avoid influences of schools and classroom specific effects (source: INEP, years: 2005, 2007).
-\item \textbf{Mayoral Pre-Electoral Coalition Size 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
-\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration that were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
+\item \textbf{Quality of Elementary School 2005--2008}: Average municipal IDEB scores.
+IDEB scores are estimated as follows.
+The Ministry of Education takes the average of the students' grades in math and Portuguese, then multiply the those numbers by the student yearly approval rate.
+INEP reweights the estimators to avoid schools and classroom specific effects (source: INEP, years: 2005, 2007).
+\item \textbf{Size of Mayoral Pre-Electoral Coalition 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
+\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration who were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
 \item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
 \item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to the city council.
-I collected this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
-\item \textbf{Competition per Seat 2004}: Number of people running for city-councilor divided by the city council size (source: TSE)
+We collect this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
+\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the city council size (source: TSE)
 \item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
@@
 
-I coded the legislation approved by the councilors in 63 municipalities within ten thousand inhabitants away from the council size thresholds. I classified the legislation into five categories:
+We code the legislation approved by the councilors of 63 municipalities around a ten thousand inhabitants buffer from the council size thresholds. We classify the legislation into four categories:
 
@@
 \item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
-\item \textbf{Others}: Legislation that is not classified as Local Public Goods, Public Goods, or Oversight. Usually honors or procedures.
-\item \textbf{Education and Health Care}: Legislation about Education or Health Care provision.
+\item \textbf{Education and Health Care}: Legislation about education or health care provision.
+\item \textbf{Others}: Legislation that is not classified as local public goods, public goods, or oversight. Usually honors or procedures.
 \end{itemize}
@@
 
-I ran an online survey asking 174 councilors, among other questions, about their representation duties, which mayors used services to improve the mayor's coalition support. The services were:
+We ran an online survey asking 174 councilors about their representation duties and how mayors allocate public services to expand his or her government coalition. The services we include are:
 
 \begin{itemize}
-\item \textbf{Councilors Job Appointments}: The frequency that mayors appoint people allied to city councilors to bureaucratic jobs (source: survey).
-\item \textbf{Councilors Demands}: The frequency that mayors satisfy an allied councilors' demand (e.g., build a health clinic in a councilor's neighborhood) (source: survey).
-\item \textbf{Councilors Personal Requests}: The frequency that mayors satisfy an allied councilors' requests (e.g., hire an ally in the bureaucracy) (source: survey).
-\item \textbf{Councilors Legislation}: The frequency that mayors support councilors' legislative agenda (source: survey).
-\item \textbf{Councilors Constructions}: The frequency that mayors support councilors' requests for constructions (e.g., fix potholes in the councilor's neighborhoods) (source: survey).
+\item \textbf{Councilors Job Appointments}: How often mayors appoint people allied to city councilors to bureaucratic jobs (source: survey).
+\item \textbf{Councilors Demands}: How often mayors satisfy an allied councilors' demand (e.g., build a health clinic in a councilor's neighborhood) (source: survey).
+\item \textbf{Councilors Personal Requests}: How often mayors satisfy an allied councilors' requests (e.g., hire an ally in the bureaucracy) (source: survey).
+\item \textbf{Councilors Legislation}: How often that mayors support the councilors' legislative agenda (source: survey).
+\item \textbf{Councilors Constructions}: How often mayors support councilors' requests for constructions (e.g., fix potholes in the councilor's neighborhoods) (source: survey).
 \end{itemize}
 
-This Appendix presents other questions I asked in the survey.
-They are meant to improve my knowledge about the city councilors' perceptions of their municipality roles.
-I omitted these questions in the main paper because they are not of general interest to my argument.
-The descriptive statistics of the variables used in the main article follow in Table \ref{tabdescrvarspaper}.
+This Appendix contains other questions that we asked in the survey.
+They are meant to improve our knowledge about the city councilors' perceptions of the roles the municipality and themselves play in the government.
+We omitted these questions in the main paper because they are not of general interest to our argument.
+The descriptive statistics of the variables used in the main article follow in Table \ref{tab:descrvarspaper}.
 
@@
 \caption{Summary Statistics}
-\label{tabdescrvarspaper} 
-\resizebox{0.8\textwidth}{3in}{
+\label{tab:descrvarspaper}
+\resizebox{\textwidth}{3in}{
 \begin{threeparttable}
@@
 Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\
-Quality of Elementary School Index 2005-2008 & 9,266 & 3.73 & 0.94 & 0.70 & 8.10 \\ 
+Quality of Elementary School 2005-2008 & 9,266 & 3.73 & 0.94 & 0.70 & 8.10 \\
 & \multicolumn{5}{c}{\textbf{Bargaining, Coalition, and Public Employment}} \\ \cline{2-6}
@@
 Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\
+Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\
 Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\
-Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\ 
 & \multicolumn{5}{c}{\textbf{Survey -- Strategy to Consolidate Coalition Support}} \\ \cline{2-6}
@@
 \small
-\textbf{Notes:} The legislation approved dataset has data on 63 of the 202 municipalities 10 thousand inhabitants from the council size thresholds.
-The survey summary statistics here are unweighted.
+\textbf{Notes:} The legislation approved dataset contains information on 63 of the 202 municipalities 10 thousand inhabitants away from the council size thresholds.
+Survey summary statistics are unweighted.
 Numbers of cases vary due to missingness.
@@
 
-The validity of the causal claim relies on three assumptions:
+The validity of our causal claim relies on three assumptions:
 
 \begin{enumerate}
-  \item That municipalities cannot sort themselves on the left or the right-hand side of the cutoffs by their choices.
-  \item That the regression models are consistently comparing cities in the adjacent cutoffs.
-  \item That I have no pre-treatment differences in the sample.
+  \item Municipalities cannot place themselves on the left- or the right-hand side of the cutoffs.
+  \item Regression models correctly compare cities in the adjacent cutoffs.
+  \item There are no pre-treatment differences in the sample.
 \end{enumerate}
 
-For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant in the left or the right of the cutoff.
-For my research, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
-
-I run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
-I use local polynomial orders from one to four.
+For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant on either side of the cutoff.
+In our sample, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
+
+We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
+We use local polynomial orders from one to four.
 As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
-Therefore, there is no manipulation according to \citet{calonico2019regression}.
-
-I also graph the \citet{McCrary2008} test, pooling all the discontinuities. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
+Therefore, we also see no evidence of manipulation.
+
+Lastly, we graph the \citet{McCrary2008} test, pooling all the discontinuities together. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
 
@@
 
-\pagebreak
-
 ## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
@@
 The identification strategy requires exogenous changes in the city council size thresholds.
-Previous to the changes I exploit here, the 1988 Brazilian Constitution stated the following distribution of seats per population size, presented in Table \ref{tabcitycouncilsize1988}.
+Prior to the changes we exploit here, the 1988 Brazilian Constitution stated the following distribution of seats per population size, presented in Table \ref{tab:citycouncilsize1988}.
 
@@
 \caption{City council size from the 1988 Constitution}
-\scalebox{0.75}{
+\label{tab:citycouncilsize1988}
+\scalebox{1}{
 \begin{tabular}{rccrrr}
@@
 }
-\label{tabcitycouncilsize1988}
 \end{table}
 
-These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease the council size from eleven to nine councilors.
-The two losing councilors started a judicial contestation that made it to the Supreme Court.
-The court ruled that the Constitution meant that council size should vary proportionally with population, beginning with nine legislators, until the maximum number of councilors, 55.
-Following this decision, the Superior Electoral Tribunal (TSE) decided the thresholds for the 2004 election (Resolution 21,702/2004).
-According to their decision, the legislature should increase as displayed in Table \ref{tabcitycouncilsize2004all}.
+These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease its own council size from eleven to nine councilors.
+The two losing councilors contested the measure and took the proposal to the Supreme Federal Court (STF).
+The Justices ruled that council sizes should vary according to the city population, from a minimum of nine legislators to a maximum of 55.
+Following this decision, the Supreme Electoral Court (TSE) set the thresholds for the 2004 election (Resolution 21,702/2004).
+According to their decision, the legislature should increase as displayed in Table \ref{tab:citycouncilsize2004all}.
 
@@
 \caption{City council size thresholds according to TSE resolution 21,702/2004}
-\scalebox{0.75}{
+\scalebox{1}{
 \begin{tabular}{rcrrr}
@@
 }
-\label{tabcitycouncilsize2004all}
+\label{tab:citycouncilsize2004all}
 \end{table}
 
-As there are few municipalities above one million inhabitants, I decided to restrict the attention to cities with less than $571,429 + 47,619 = 619,048$ inhabitants.
-Table \ref{tabcitycouncilsize2004short} displays the frequency of municipality by thresholds used in my paper.
+As Brazil has only a few municipalities with a population higher than one million inhabitants, we focus on cities with less than $571,429 + 47,619 = 619,048$ inhabitants.
+Table \ref{tab:citycouncilsize2004short} displays the number of municipalities by the thresholds we use in this paper.
 
@@
 \caption{City council thresholds used in the paper}
-\scalebox{0.85}{
+\scalebox{1}{
 \renewcommand*{\arraystretch}{1.2}
@@
 }
-\label{tabcitycouncilsize2004short}
+\label{tab:citycouncilsize2004short}
 \end{table}
 
-The Supreme Court ruled that the electoral courts use the 2003 population projection to assign municipalities to cutoffs.
-In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) proposes the official population projections.
-Sorting is not an issue for my identification strategy, as IBGE is an insulated bureaucracy from local influences (see also the McCrary test above).
-
-To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity from the cutoffs.
-In the map, I give the contour of every Brazilian city, coloring it by the proximity to the council size thresholds.
+The Supreme Court stated that local electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
+In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) makes the official population projections.
+We have strong reason to believe that sorting is not a threat to our identification strategy, as IBGE is notably insulated from local politics (see also the McCrary test above).
+
+To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity to the cutoffs.
+In the map, we give the contour of every Brazilian city, coloring it by the proximity to the council size thresholds.
 Darker colors represent municipalities closer to the population thresholds.
-In regression discontinuity, the closer a city is to the cutoff, the more influential it is in the estimation.
-Figure \ref{sampleplot} also shows that the municipalities are reasonably distributed around the whole country.
-
-\pagebreak
+In regression discontinuity models, the closer a city is to the cutoff, the more influential it is in the estimation.
+Figure \ref{sampleplot} also shows that the municipalities around the cutoff are reasonably distributed across the country.
 
@@
       \centerline{\includegraphics[width=7in,angle=0]{../figures/samplePlot.pdf}}
-      \caption{Municipalities by their Selection Status}
+      \caption{Municipalities and their Selection Status}
       \bigskip
@@
 
-## Identification Strategy in Multiple Thresholds Regression Discontinuity Design
+## Identification Strategy in Regression Discontinuity Designs with Multiple Thresholds
 \label{ISMT}
 
-When carrying out regression discontinuity with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes \citep{cattaneo2016interpreting}.
+When estimating regression discontinuities with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes \citep{cattaneo2016interpreting}.
 Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
 The outcome variable is assumed to be $Y$.
-In the pooled model, the Local Average Treatment Effect is:
-
-\[
-LATE_{nocontrols} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
-\]
-
-Nevertheless, this may be problematic as the municipal characteristics in each cutoff may vary from cutoff to cutoff.
-The population imbalance certainly carries out heterogeneity, in the way shown by \citet{Cattaneo2016}.
-To ensure comparability, I estimate the average LATE for all cutoffs, avoiding most of the heterogeneity.
-I propose to add a set of controls denoted by $Z_i$ that vary between cutoffs.
+In the pooled model, the Local Average Treatment Effect (LATE) is:
+
+\[
+LATE_{no\_controls} \quad = \quad \E \left[ \lim_{x \downarrow c_i} \E[Y_i | X_i] - \lim_{x \uparrow c_i} \E[Y_i | X_i] | \forall c_i \in C \right]
+\]
+
+Nevertheless, this may be problematic as municipal characteristics may vary between cutoffs.
+For instance, population imbalance is a known source of heterogeneity, as shown by \citet{Cattaneo2016}.
+To ensure that cases are comparable, we estimate the average LATE for all cutoffs.
+We add a set of controls $Z_i$ to reduce heterogeneity.
 For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
-As the population runs smoothly around each cutoff, it makes it a perfect control to add.
+As the population runs smoothly around each cutoff, it makes this variable an ideal control to add to our models.
 The new estimator is:
@@
 
-I control for Population, GDP, a dummy for the Northeast States, seats before the 2003 decision, and year.
-All these control variables are smooth in each cutoff but are significantly different from cutoffs, making them adequate control variables for this case \citep{calonico2019regression}.
-To perform the estimations, I use a triangular kernel, which weighs the municipalities closer to each cutoff.
-To compute the optimal bandwidth, I use the \citet{CCT2014} method.
-To study the sensitivity to the bandwidth choice, I vary the bandwidth from 50\% to 200\% of the optimal bandwidth size.
-I also use cluster-robust standard errors at the municipal level.
-
-However, as it is uncommon for a regression discontinuity to use control variables, some readers may ask why, in this case, is it advisable?
-To answer this question, I run a series of simulations to show that controlling for the variable that determines the assignment helps improve the consistency of the estimates and improves their efficiency.
-
-Consider the data distributed in one of the four forms depicted by Figure \ref{simRDdd}.
-I add nine thresholds, at 0.1, 0.2, and so on until 0.9, creating six types of outcomes.
-The first three outcomes are sharp changes.
-In the first, I add variations from one to 10, with one step for each shift.
-In the second, I add 1 in the first cut, zero in the second cut, and -1 in the third cut, repeating this pattern for the remaining cutoffs.
+We control for population, GDP, whether the state is located in the Northeast region, seats before the 2003 decision, and year.
+All control variables are smooth around each cutoff but are significantly different across cutoffs, making them adequate controls for our purposes \citep{calonico2019regression}.
+We use a triangular kernel in our estimations, which gives more weigh to municipalities closer to each cutoff.
+To compute the optimal bandwidth, we use the \citet{CCT2014} method.
+We vary the bandwidth from 50\% to 200\% of the optimal bandwidth size to assess whether our results are robust to bandwidth choice.
+We also use cluster-robust standard errors at the municipal level.
+
+However, as it is uncommon for regression discontinuity designs to include control variables, some readers may ask why we have added these covariates in the first place.
+To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment helps improve both the consistency and the efficiency of the estimates.
+
+Consider data distributed according to one of the four forms depicted in Figure \ref{simRDdd}.
+We add nine thresholds, at 0.1, 0.2, and so on until 0.9, to create different outcomes.
+The first three are sharp changes.
+First, we vary from one to 10, moving one step at each shift.
+In the second case, we add 1 to the first discontinuity, zero to the second, and -1 to the third, repeating this pattern for the remaining cutoffs.
 The estimated change should be equal to zero.
-In the third model, I add one in the first cut, $1+0.9$ in the second cut, $1+0.9+0.8$ in the third cut, and so on until the last cutoff.
-This is intended to simulate a diminishing effect from one cutoff to the other.
-The previous three outcomes are the same as depicted here, added by a Normal random disturbance, mean zero, and variance 0.01.
-I then run a thousand Monte Carlo simulations for each combination, $4 \times 6 \times 2 = 48$ in total, fitting a regression with and without the running variable as a control.
+In the third model, we again add one to the first cutoff, but $1+0.9$ to the second, $1+0.9+0.8$ to the third, and repeat this process until the last cutoff.
+This simulates a diminishing effect from one cutoff to the other.
+The previous three outcomes are the same as depicted here, plus a Normal random disturbance with mean equal to zero and variance equal to 0.01.
+We then run a thousand Monte Carlo simulations for each combination, fitting regressions with and without the running variable as a covariate.
 
@@
 
-A consistent estimator should fit one in the first and fourth data distribution.
-In the second and fifth, the change should be of $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
-In the third and sixth models the change should be equal to $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$, and the average change should be equal to $0.5$.
-The first three models should present a more efficient estimation than the last three models.
-I display the results in Figure \ref{estimDGP}, showing that the controlled models are more consistent and efficient.
+A consistent estimator should fit either the first or the fourth data distributions.
+In the second distribution, the change should be equal to $(1, 0, -1, 1, 0, -1, 1, 0, -1)$, and the average change here is equal to zero.
+In the third model, the change should be $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$ and the average change should be equal to $0.5$.
+We display the results in Figure \ref{estimDGP}, showing that the models with control variables are more consistent and efficient.
 
@@
 
-\newpage
-
 ## Placebo Regressions for Political Mechanism
@@
 
-Here I present the placebo regressions for the mechanism-aggregated outcomes.
-In Panel A of the main paper, I run the regression on alternative explanations.
-Only the number of female councilors changed significantly, but a change is statistically expected in at least 10\% of cases.
-I have not collected data on non-white legislators in the placebo cutoffs; therefore, I leave it blank.
-In Panel B, I have the placebo regressions for the primary mechanism: bargaining costs and public appointed employees.
-As expected, the placebo regressions were statistically insignificant.
+Here we present the placebo regressions for the mechanism-aggregated outcomes.
+In Panel A of the main paper, we run the regression on alternative explanations.
+Only the number of female councilors changed significantly, but that is to be expected in at least 10% of cases.
+We have not collected data on non-white legislators for the placebo cutoffs; therefore, we leave it blank.
+In Panel B, we have the placebo regressions for the primary mechanism, which concerns bargaining costs and public appointed employees.
+As expected, the placebo regressions are statistically insignificant.
 
@@
 RD estimates using \citet{CCT2014} optimal bandwidth selection and triangular kernel.
-Robust standard errors, clustered at the municipal level, in parenthesis.
-Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.
 \end{tablenotes}
@@
 
-\newpage
-
-## Sensitivity Analysis for Bandwidth Selection
+## Sensitivity Analysis of Bandwidth Selection
 \label{sensffapp}
 
-I present here the sensitivity to the bandwidth selection. Following the suggestions of \citet{Bueno2015}, I vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
+In this section we present the sensitivity tests for bandwidth selection. Following the suggestion of \citet{Bueno2015}, we vary the bandwidth from 50\% to 200\% of the \citet{CCT2014} estimate.
 
@@
 
-In Figure \ref{placgraphbw}, I run the same bandwidth analysis for the placebo outcomes. The results, as expected, show mostly insignificant results.
+In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, are mostly statistically insignificant.
 
@@
 
-## Sensitivity to Brazilian States Characteristics
+## Sensitivity Analysis of State Characteristics
 \label{sensstate}
 
-The literature about Brazil recognizes that the country presents considerable variability.
-Moreover, some states had such poor Health Care and Education systems that they could be driving our results.
-I run the analysis dropping one state at a time to investigate this statewide heterogeneity.
-The results are in Figures \ref{graphsensstatedrop1},\ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
-
-First, note that for infant mortality and education enrollment, all coefficients remain significant upon the removal of the state.
-For postneonatal mortality, the coefficient loses significance when removing Bahia, Pernambuco, Rio Grande do Norte, and Rio Grande do Sul.
-The mayoral coalition size remains significant in most models, losing significance when removing Rio Grande do Norte and Sao Paulo.
-The number of appointed employees lose significance when removing Espirito Santo and Sao Paulo.
+Given its massive size and large social inequalities, Brazil presents considerable geographic variation.
+In this respect, some states have such poor health care and education systems that they could be driving our results.
+We run the analysis dropping one state at a time to investigate this statewide heterogeneity.
+The results are in Figures \ref{graphsensstatedrop1}, \ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
+
+First, note that for infant mortality and education enrollment, all coefficients remain significant even after removing some states from our sample.
+For postneonatal mortality, the coefficient loses significance when we remove the states of Bahia, Pernambuco, Rio Grande do Norte, and Rio Grande do Sul.
+The mayoral coalition size remains significant in most models, losing significance when we remove Rio Grande do Norte and São Paulo.
+The number of appointed employees loses significance after removing Espirito Santo and São Paulo.
 All the alternative mechanism models are insignificant, regardless of the state removed.
@@
       \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens2.pdf}}
-      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
+      \caption{Sensitivity Analysis of State Characteristics -- Mechanism Outcomes}
       \bigskip
@@
       \centerline{\includegraphics[width=5in,angle=0]{../figures/placDropStateSens1.pdf}}
-      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
+      \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Welfare Outcomes}
       \bigskip
@@
       \centerline{\includegraphics[width=6in,angle=0]{../figures/placDropStateSens2.pdf}}
-      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
+      \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Mechanism Outcomes}
       \bigskip
@@
 
-## Sensitivity to the Functional Form Analysis
+## Sensitivity Analysis of Model Functional Form
 \label{sensfuncform}
 
-In the paper, I run all the regressions using local linear polynomials.
-\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better in terms of consistency than cubic and quartic.
-
-However, I run all the models using polynomials from local linear to a quartic, showing that my results are robust to different regression functional forms.
+In the paper, we run all the regressions using local linear polynomials.
+\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better than cubic and quartic models in terms of consistency.
+
+However, to assess the robustness of our results, we also run every model using different polynomials, from local linear to a quartic, to show that our results are robust to different regression functional forms.
 The results are similar in all models, with significance changing only in the quartic polynomials.
@@
       \centerline{\includegraphics[height=8in,angle=0]{../figures/ffSens.pdf}}
-      \caption{Sensitivity Analysis for the Functional Form}
+      \caption{Sensitivity Analysis of Model Functional Form}
       \bigskip
@@
       \centerline{\includegraphics[width=6in,angle=0]{../figures/placFfSens.pdf}}
-      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
+      \caption{Sensitivity Analysis of Model Functional Form -- Placebo Cutoffs}
       \bigskip
@@
 
-## Sensitivity to Covariates
+## Sensitivity Analysis of Covariates
 \label{senstcovapp}
 
-The control variables play an essential role in my model.
-As I argued before, without controls, the first stage is inconsistent, and I may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
-
-However, if the selection of controls makes the models overestimate quantities in the directions my narrative emphasizes, this would pose a significant credibility issue for my analysis.
-To study the sensitivity to controls, I run the same regressions for all possible control combinations.
-Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{In the Figure, \textit{NC} stands for No Controls.
+Control variables play a major role in our model.
+As we have argued above, our estimates may be inconsistent without the addition of control variables, as we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
+
+However, if the selection of control variables makes the models biased towards our main arguments, this would pose a significant credibility threat to our results.
+To study the sensitivity to controls, we run the same regressions for all possible control combinations.
+Figure \ref{graphsenscontrol} displays the results for this sensitivity test.\footnote{\textit{NC} stands for No Controls.
 The controls used are \textit{gdp}, the municipal GDP in a given year; \textit{nseats2000}, the number of seats before the 2003 Supreme Court decision; \textit{northeast}, a dummy variable for Northeast Brazil; \textit{pop2003}, population in 2003; and \textit{year}.}
@@
       \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov1.pdf}}
-      \caption{Sensitivity Analysis for the Control Variable's Choices}
+      \caption{Sensitivity Analysis of Control Variables}
 \bigskip
@@
       \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov2.pdf}}
-      \caption{Sensitivity Analysis for the Control Variable's Choices}
+      \caption{Sensitivity Analysis of Control Variables}
 \bigskip
@@
 
-For instance, changes in controls substantially affect the detected differences in Elementary Education Quality, making some combinations of controls fit a positive effect on education quality.
-However, most combinations of controls were insignificant in this variable.
-
-My choice of full controlled model was the most conservative.
-This is because the Full Model is significant only when most of the combinations also are significant.
-Regarding the point estimates, my choices of controls tend to keep the models with smaller coefficient sizes.
-
-I also plot sensitivity tests to covariates in the placebo regressions in Figures \ref{placsenscov1} and \ref{placsenscov2}.
-The theoretical expectations here are that most of these outcomes would fail, and the graphs confirm these expectations.
+For instance, changes in controls substantially affect the quality of elementary education, where some sets of control variables leading to a positive effect.
+However, most combinations of controls were insignificant.
+
+We included the model with all controls to be conservative in our estimations.
+This is because the full model is significant only when most of the combinations also are significant.
+Regarding the point estimates, our variable choices tend to keep the models which have smaller coefficient sizes.
+
+We also plot sensitivity tests to covariates in the placebo regressions.
+They are displayed in Figures \ref{placsenscov1} and \ref{placsenscov2}.
+The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm our expectations.
 
@@
 
-\subsection{Sensitivity to Additional Cutoffs\label{senscutapp}}
-
-To study the sensitivity to the number of cutoffs and the possibility of diminishing returns from the additional legislator, I run regressions limiting the population sizes to half the cutoffs, from the second cutoff to the last.
+\subsection{Sensitivity Analysis of Additional Cutoffs\label{senscutapp}}
+
+Here we evaluate the robustness of our results when we change the number of cutoffs.
+We run a series of regressions limiting the population sizes to half the cutoffs, starting from the second cutoff to the last.
 This strategy is similar to adding one cutoff at a time.
-The results are stable and do not change the main conclusions.
-Moreover, there is no increasing or decreasing pattern, which would indicate that differential returns were occurring.
+The results are stable and do not change our main conclusions.
+Moreover, there are no clear increasing or decreasing patterns, which would indicate the existence of differential returns.
 Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
@@
 \centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts1.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
+\caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
 \bigskip
@@
 \centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts2.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
+\caption{Sensitivity to Additional Cutoffs -- Mechanism Outcomes}
 \bigskip
@@
 \centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts1.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
+\caption{Sensitivity to Additional Cutoffs -- Placebo Welfare Outcomes}
 \bigskip
@@
 \centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts2.pdf}}
-\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
+\caption{Sensitivity to Additional Cutoffs -- Placebo Mechanism Outcomes}
 \bigskip
@@
 
-Two alternative explanations could confound the results.
-First, the mayor's selection could be affected by the city council size, and then the welfare improves by the quality of the mayor, not by the partisan mechanism described.
-Second, the partisan mechanism could be confounded by an argument similar to the @Weingastetal1981 ``law of 1/n'', and the improvements in welfare could have resulted from higher revenues.
-This section shows that none of these concerns are true in my case.
+Two alternative explanations may confound our results.
+First, the mayor's selection could be affected by the size of the city council, thus public welfare improves due to the quality of the mayor and not because of the partisan mechanism we have described.
+Second, the partisan mechanism could be capturing a dynamic similar to @Weingastetal1981 "law of 1/n", whereby welfare improvements are caused by higher available revenues.
+This section shows that none of these concerns are valid in our case.
 
@@
 
-I select four characteristics: gender, schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
+We select four characteristics of the city mayors: gender, level of schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
 The results show no variation in council size and mayoral characteristics.
@@
 \begin{table}[!htbp] \centering
-\caption{Mayoral Characteristics} 
+\caption{Mayor Characteristics}
 \label{appmaychar}
@@
 \begin{table}[!htbp] \centering
-\caption{Mayoral characteristics -- Placebo} 
+\caption{Mayor Characteristics -- Placebo}
 \label{placappmaychar}
@@
   \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
-  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
+  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
   \end{tabular} }
@@
 
-I run the regressions on federal transfers and revenue raised within the municipalities.
-There is only a negligible effect on education transfer, barely significant at 10%.
+We run another series of models on federal transfers and revenue raised within the municipalities.
+There is only a negligible effect on education transfers, yet it is barely significant at 10%.
 The other indicators remain insignificant.
@@
   \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
-  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\ 
-  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\ 
+  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
+  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
   \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\
@@
 
-In the Fall of 2018, I collected the data on the legislation approved by the city council of 63 municipalities 10 thousand inhabitants away from the thresholds.
-There are 202 municipalities at a 10 thousand inhabitants distance from the cutoff, but only 63 had information on the legislation between 2005 to 2008.
-
-I hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machines algorithm to the remaining 99\% cases to classify the legislation.
-First, I train and test the accuracy of the SVM classifier on 80\% of the dataset.
-Then, I ran the training on the complete hand-coded data and predicted the remaining.\footnote{I tested SVM, Naive-Bayes, Random Forests, and Neural Networks.
-I choose SVM as it gives the highest prediction rate.
-I are using a simple bag-of-words classifier, with the R package RTextTools \citep{collingwood2013rtexttools}.}
-
-I hand-coded using four characteristics:
+In the Fall of 2018, we collected data on the legislation approved by the city councils of 63 municipalities, all of which were 10 thousand inhabitants away from the thresholds we discussed above.
+There are 202 municipalities 10 thousand inhabitants away from the cutoff, but only 63 had relevant information about local legislation between 2005 to 2008.
+
+We hand-coded 1\% of the dataset (3,466 cases) and applied a Supporting Vector Machine (SVM) algorithm to the remaining 99\% cases to classify the legislation.
+First, we trained and tested the accuracy of the SVM classifier on 80\% of the dataset.
+Then, we ran the training algorithm on the complete hand-coded data and predicted the remaining cases.\footnote{We tested SVM, Naïve Bayes, Random Forests, and Neural Networks for this task.
+We have chosen SVM as it gives the highest prediction rate of all of the algorithms we have tried.
+We use a simple bag-of-words classifier provided by the `RTextTools` package for `R` \citep{collingwood2013rtexttools}.}
+
+We hand-coded these data according to four characteristics:
 
 \begin{enumerate}
-\item \textbf{Local Public Goods}: Whether the bills provided a local public good or service.
-Bills here are, for example, proposals to fix street potholes, staff a given health clinic, purchase equipment to a given school.
+\item \textbf{Local Public Goods}: Whether the bills provided a local public good or service to citizens.
+For instance, bills that aim to fix street potholes, staff a given health clinic, or purchase equipment to a given school.
 \item \textbf{Oversight}: Legislation requesting information on the status of service provision.
-\item \textbf{Others}: Legislation that is not categorized as any of the previous three listed. Legislation here includes honors to notable citizens and procedure legislation, among others.
 \item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
+\item \textbf{Others}: Legislation not categorized as any of the previous three, such as honors to notable citizens.
 \end{enumerate}
 
-I run the SVM on the hand-coded data. Table \ref{accurClassif} shows the classification accuracy for each of the variables that I hand-coded. In all models, I set cost equals 10 to avoid over-fitting.
+Table \ref{accurClassif} shows the classification accuracy for each of the variables that we have hand-coded. In all models, we set cost to 10 to avoid overfitting.
 
@@
 \centering
-\caption{Accuracy SVM Classifier (tested in 20\% of the data)}
+\caption{Accuracy of SVM Classifier (tested in 20\% of the data)}
 \label{accurClassif}
@@
 Oversight                    & 94.9               \\
+Education and Health Care    & 92.5               \\
 Others                       & 93.5               \\
-Education and Health Care    & 92.5               \\
 \hline
@@
 
-After I classify all the bills, the frequency in each category was added to the main paper.
-I also add the productivity per legislator, consisting of a ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
-As expected, the results changed little from when I considered the absolute values.
+After we classified all the bills, we added the frequency of each category to the main paper.
+We have also added the productivity per legislator, which consists of the ratio of the legislation approved in the municipality in the four-year term, divided by the council size.
+As expected, the results changed little when we used this alternative measure.
 
@@
 
-From November 21st to December 1st, 2016, I surveyed former city councilors that served in the 2005 to 2008 period.
-I asked them how mayors secure electoral support, which services are standard in the city councilor's practice, and which services give the highest electoral yield.
-
-I used 3,240 emails from politicians that ran in the 2016 election, filtering the politicians that hold public office in 2005.
-On December 1st, I closed the pool, having 174 responses.
-Figure \ref{geodistrsurv} displays a distribution of responses.
+From November 21^st^ to December 1^st^, 2016, we surveyed former city councilors elected for the 2005-2008 term.
+We asked them how mayors secure electoral support, which services are commonly discussed in the city council, and which services give them the highest electoral yield.
+
+We sent 3,240 emails to politicians who had ran in the 2016 election and held public offices in 2005.
+On December 1^st^, we closed the pool and obtained 174 responses.
+Figure \ref{geodistrsurv} displays the distribution of responses.
 
@@
 
-To weight the survey, I use the Legislative Census, which was conducted ran in 2005 by the Brazilian Senate company \textit{Interlegis} to improve the quality of the bodies in Brazil.
-I use the categories of Brazilian region, legislature size (9 to 15 or more), gender, and age less than 39, reweighting the collected data to match the population proportions.
-I use the proportions on each bin to weight the graphs and statistics generated after the raking process.\footnote{The R package \textit{survey} describes in detail the raking process \citep{lumley2004analysis}.
+To weight the survey, we use the Legislative Census, conducted by *Interlegis* on the behalf of the Brazilian Senate.
+The company was hired to improve the quality of Brazilian government branches.
+We include the following categories in the weighting procedure: region of Brazil, legislature size (9 to 15 or more), gender, and age less than 39.
+We use the proportions in each bin to weight the graphs and statistics generated after the raking process.\footnote{The `survey` package for `R` describes the raking process in more detail \citep{lumley2004analysis}.
 In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
@@
 & Sample & Population & Weighted \\
-& Proportions & Proportions. & Proportions \\
+& Proportions & Proportions & Proportions \\
 \hline
@@
 
-Note that the algorithm performed well, with minimal differences occurring only after the third decimal place.
-
-The questions of interest for this research asked in the survey were:
+Note that the algorithm performs very well, with minimal differences occurring only after the third decimal place.
+
+The survey included the following questions of interest:
 
@@
 
-A free translation to English would be:
+English translation:
 
 \begin{enumerate}
-    \item In Brazil, it is common that mayors negotiate the majority within the city council. What is the frequency that mayors use the following services in exchange for support?
-    \item Which of those activities do city councilors perform the most in their representation practices?
+    \item In Brazil, mayors commonly negotiate to establish a government majority in the city council. How often do you think mayors use the following goods in exchange for support?
+    \item Which of those activities do city councilors perform most often in their duties?
     \item Which of the following activities do you believe helps city councilors the most in elections?
@@
 
-The second question is essential, as it reports whether councilors do the activities that give more electoral yield.
-Figure \ref{commonservice} shows the results for each of the activities I studied the electoral yield.
+The second question is particularly relevant to our argument, as it indicates whether councilors engage in activities that give them high electoral yields.
+Figure \ref{commonservice} shows the results for each of the activities we analyzed.
 

### 2021-10-02 appendix/appendix.Rmd
small edits to appendix text

@@
 As mentioned above, we explore the implications of three different mechanisms.
-First, in the \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor $\delta \in (0,1)$ and with the random selection of one councilor.
+First, in the \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor $\delta \in (0,1)$ and the random selection of one councilor.
 The randomly selected councilor becomes the new proposer.
 If her proposal is accepted, it is implemented.
-If rejected, the budget shrinks again by a factor $\delta$, and another city councilor is chosen to propose the policy.
-The process continues until one proposal is finally accepted.
+If rejected, the budget shrinks again by $\delta$ and another city councilor is chosen to propose the policy.
+The process continues until the proposal is finally accepted.
 
@@
 We derive the optimal rents ($r$) and public goods provision ($g$) a mayor should propose.
-Mayors benefits from public goods provision, as it increases their chances of reelection.
+Mayors benefit from public goods provision, as it increases their chances of reelection.
 However, they would rather provide the lowest necessary amount of public goods and extract the remaining resources as political rents.
@@
 \begin{proposition}
-Public goods provision increases with legislature size if governing costs decrease with legislature size.
+Public goods provision increases with larger legislatures if governing costs decrease in larger legislatures.
 \end{proposition}
@@
 There are two components on the right-hand side.
-The first is the amount that the councilor $i$ receives when he/she is the proposer.
+The first is the amount that councilor $i$ receives when he/she is the proposer.
 The amount is equal to the chance that they are recognized as the proposer, times the budget in the next round, minus the offers they have to make to convince half of the councilors.
@@
 
-We use three data sources in our work, mainly from Brazilian governmental agencies. Table \ref{tab:varsources} displays the primary sources we use here and their respective URLs.
+We use three data sources in our work, mainly from Brazilian governmental agencies. Table \ref{tab:varsources} presents the variables we use here and their respective URLs.
 
@@
 \item \textbf{Population 2000}: City population according to the 2000 Brazilian Census (source: IBGE).
-\item \textbf{Per-Capita GDP 2000 (in millions)}: Municipal per capita GDP measured by the Brazilian Census (source: IPEA).
+\item \textbf{Per Capita GDP 2000 (Millions)}: Municipal per capita GDP measured by the Brazilian Census (source: IPEA).
 \item \textbf{Proportion of Poverty 2000}: Percentage of citizens earning less than R\$ 70.00 per month (source: Social Development Ministry [MDS]).
@@
 \begin{itemize}
-\item \textbf{Councilors Job Appointments}: How often mayors appoint people allied to city councilors to bureaucratic jobs (source: survey).
-\item \textbf{Councilors Demands}: How often mayors satisfy an allied councilors' demand (e.g., build a health clinic in a councilor's neighborhood) (source: survey).
-\item \textbf{Councilors Personal Requests}: How often mayors satisfy an allied councilors' requests (e.g., hire an ally in the bureaucracy) (source: survey).
-\item \textbf{Councilors Legislation}: How often that mayors support the councilors' legislative agenda (source: survey).
-\item \textbf{Councilors Constructions}: How often mayors support councilors' requests for constructions (e.g., fix potholes in the councilor's neighborhoods) (source: survey).
+\item \textbf{Councilors Job Appointments}: Whether mayors appoint supporters of the city councilors to bureaucratic jobs (source: survey).
+\item \textbf{Councilors Demands}: Whether mayors satisfy the public service demands of an allied councilor (e.g., build a health clinic in a councilor's neighborhood) (source: survey).
+\item \textbf{Councilors Personal Requests}: Whether mayors satisfy the private requests of an allied councilor (e.g., hire an ally in the bureaucracy) (source: survey).
+\item \textbf{Councilors Legislation}: Whether mayors support the councilors' legislative agenda (source: survey).
+\item \textbf{Councilors Constructions}: Whether mayors support councilors' requests for more public works (e.g. fix potholes in the councilor's neighborhoods) (source: survey).
 \end{itemize}
 
-This Appendix contains other questions that we asked in the survey.
-They are meant to improve our knowledge about the city councilors' perceptions of the roles the municipality and themselves play in the government.
+This Appendix contains other questions we asked in the survey.
+We collected them to improve our knowledge about the perceptions city councilors have about the roles the municipality and themselves play in the government.
 We omitted these questions in the main paper because they are not of general interest to our argument.
@@
 
-For the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant on either side of the cutoff.
+Regarding the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant on either side of the cutoff.
 In our sample, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
@@
 We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
-We use local polynomial orders from one to four.
-As the null hypothesis is no manipulation, the p-values for each polynomial order are: local linear (p-value $=0.442$); quadratic (p-value $=0.740$); cubic (p-value $=0.998$); and quartic (p-value $=0.620$).
+We use local polynomials ranging from first to fourth order.
+As the null hypothesis implies that there is no manipulation, the $p$-values for each polynomial order are: local linear ($p$-value $=0.442$); quadratic ($p$-value $=0.740$); cubic ($p$-value $=0.998$); and quartic ($p$-value $=0.620$).
 Therefore, we also see no evidence of manipulation.
@@
 
-As Brazil has only a few municipalities with a population higher than one million inhabitants, we focus on cities with less than $571,429 + 47,619 = 619,048$ inhabitants.
+As Brazil has only a few municipalities with more than one million inhabitants, we focus on cities with less than $571,429 + 47,619 = 619,048$ inhabitants.
 Table \ref{tab:citycouncilsize2004short} displays the number of municipalities by the thresholds we use in this paper.
@@
 In regression discontinuity models, the closer a city is to the cutoff, the more influential it is in the estimation.
-Figure \ref{sampleplot} also shows that the municipalities around the cutoff are reasonably distributed across the country.
+Figure \ref{sampleplot} also shows that the municipalities around the cutoff are reasonably well distributed across the country.
 
@@
 
-When estimating regression discontinuities with multiple cutoffs, authors pool all the discontinuities together and estimate the effect of council size on outcomes \citep{cattaneo2016interpreting}.
+When estimating regression discontinuities with multiple cutoffs, authors usually pool all the discontinuities together to estimate the treatment effect on the outcomes of interest \citep{cattaneo2016interpreting}.
 Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
@@
 
-Nevertheless, this may be problematic as municipal characteristics may vary between cutoffs.
+Nevertheless, this may be problematic in our case as municipal characteristics may vary between cutoffs.
 For instance, population imbalance is a known source of heterogeneity, as shown by \citet{Cattaneo2016}.
@@
     \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{../figures/bwSens.pdf}}
+      \centerline{\includegraphics[width=5in,height=4in,angle=0]{../figures/bwSens.pdf}}
       \caption{Bandwidth Sensitivity -- Main Models}
@@
 
-\pagebreak
-
-\begin{figure}[htb!]
+\begin{figure}[H]
   \begin{center}
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[width=5in,angle=0]{../figures/placBwSens.pdf}}
+      \centerline{\includegraphics[width=5in,height=4in,angle=0]{../figures/placBwSens.pdf}}
       \caption{Bandwidth Sensitivity -- Placebo Regressions}
@@
 
+\begin{figure}[H]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=5.9in,width=0.9\linewidth,angle=0]{../figures/dropStateSens1.pdf}}
+      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
+      \bigskip
+      \label{graphsensstatedrop1}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\begin{figure}[H]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=8in,width=0.9\linewidth,angle=0]{../figures/dropStateSens2.pdf}}
+      \caption{Sensitivity Analysis of State Characteristics -- Mechanism Outcomes}
+      \bigskip
+      \label{graphsensstatedrop2}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
+\begin{figure}[H]
+  \begin{center}
+      \centerline{\includegraphics[width=0.9\linewidth,angle=0]{../figures/placDropStateSens1.pdf}}
+      \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Welfare Outcomes}
+      \bigskip
+      \label{placgraphsensstatedrop1}
+  \end{center}
+\end{figure}
+
 \pagebreak
@@
   \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens1.pdf}}
-      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
-      \bigskip
-      \label{graphsensstatedrop1}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens2.pdf}}
-      \caption{Sensitivity Analysis of State Characteristics -- Mechanism Outcomes}
-      \bigskip
-      \label{graphsensstatedrop2}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=5in,angle=0]{../figures/placDropStateSens1.pdf}}
-      \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Welfare Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop1}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/placDropStateSens2.pdf}}
+      \centerline{\includegraphics[width=0.9\linewidth,angle=0]{../figures/placDropStateSens2.pdf}}
       \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Mechanism Outcomes}
@@
 
+\begin{figure}[H]
+  \begin{center}
+    \begin{minipage}{\linewidth}
+      \centerline{\includegraphics[height=7in,angle=0]{../figures/ffSens.pdf}}
+      \caption{Sensitivity Analysis of Model Functional Form}
+      \bigskip
+      \label{graphsensff}
+    \end{minipage}
+  \end{center}
+\end{figure}
+
 \pagebreak
 
-\begin{figure}[htb!]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=8in,angle=0]{../figures/ffSens.pdf}}
-      \caption{Sensitivity Analysis of Model Functional Form}
-      \bigskip
-      \label{graphsensff}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
+\begin{figure}[H]
   \begin{center}
@@
 
-\subsection{Sensitivity Analysis of Additional Cutoffs\label{senscutapp}}
+## Sensitivity Analysis of Additional Cutoffs
 
@@
 
+\begin{figure}[H]
+\begin{center}
+\centerline{\includegraphics[width=6in,height=6.5in,angle=0]{../figures/rdAddCuts1.pdf}}
+\caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
+\bigskip
+\label{senscut1}
+\end{center}
+\end{figure}
+
 \pagebreak
 
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts1.pdf}}
-\caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
-\bigskip
-\label{senscut1}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
+\begin{figure}[H]
 \begin{center}

### 2021-10-03 article/article.Rmd
text edits, article and appendix

@@
 title:  |
-        | Legislature Size and Welfare:
-        | Evidence from Brazil
+        | Legislature Size and Welfare: Evidence from Brazil
 author: 
@@
 All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
-abstract: "What is the effect of the number of legislators on public service provision?
-Despite the importance of institution designs for young democracies, little is known about the particular features that may help improve welfare.
-This paper uses a formal model to show how increasing legislature size may affect service provision.
-I show that changes in bargaining costs depend on whether the additional legislator shares the Executive's party affiliation: More opposition members reduce the Executive's equilibrium public goods provision, while more government-aligned members increase it.
-I test this theory by exploiting sharp discontinuities in city council size in Brazil.
-I show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, significantly improving primary school enrollment and infant mortality.
-To investigate the mechanism, I surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008.
+abstract: "How does legislature size impact public service provision?
+Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood.
+In this paper, we use a formal model to show that increasing legislature size improves the provision of public goods.
+We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it.
+We test this theory by exploiting sharp discontinuities in city council size in Brazil.
+We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures.
+To explore possible mechanisms, we surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008.
 This paper has implications for the design of representative institutions."
@@
 
+[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+
 [^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
 
@@
 
-Legislative institutions are crucial for welfare and service provision in democratic countries.
-Historically, the division of power and the birth of a representative government placed the legislatures at the center of popular consent.
+Legislative institutions are crucial for citizen welfare and service provision in democratic countries.
+Historically, the division of power and the birth of a representative government placed legislatures at the center of the political stage.
 In modern democracies, most countries have assemblies at all levels of government.
-These institutions affect the information and quality of legislation, check and veto the other political powers, and influence policymaking.
-Moreover, they also determine taxation, government spending and oversee service provision \citep{Weingastetal1981, weingast1988industrial, north1989constitutions, auriol2012optimal, stasavage2011states, poulsen2018political}.
+These institutions regulate the quantity and quality of legislation, check and veto other political powers, and influence policymaking.
+Moreover, legislatures also determine taxation, government spending and oversee public programs \citep{auriol2012optimal, north1989constitutions, poulsen2018political, stasavage2011states, Weingastetal1981, weingast1988industrial}.
 
-Regardless of differences in electoral rules, social composition, and procedures, all legislatures share one feature: more than one representative composes them.
-Legislature size relates to collective action problems, bargaining between political powers, government spending, and representation, but how these components affect welfare remain understudied \citep{crain1979cost, Weingastetal1981, rogers2002free, PrimoSnyder2008, allenrepresentation}.
-On the one hand, enlarged legislatures may increase government spending and lawmaking, and this could improve some services \citep{Weingastetal1981}.
-On the other hand, adding a legislator may increase the number of veto players and broaden the collective action problems, hindering service provision \citep{tsebelis2002veto, gottlieb2019countervailing}.
-Therefore, what is the effect of increasing the legislature size on public service provision?
+Regardless of eventual differences in electoral rules, social composition, and internal procedures, all legislatures share one feature: they are collective bodies.
+As such, the number of representatives in parliament has important consequences for whole polity.
+Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{allenrepresentation, crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, PrimoSnyder2008, Weingastetal1981}.
+However, how legislature size impacts social welfare remain less understood.
+On the one hand, enlarged legislatures may increase government spending and lawmaking, which can lead to more public goods \citep{Weingastetal1981}.
+On the other hand, adding a legislator may increase the number of veto players and exacerbate collective action problems, thus hindering service provision \citep{gottlieb2019countervailing, tsebelis2002veto}.
+Therefore, what is the effect of larger legislatures on public service provision?
 
-In this paper, I propose a local legislature size and welfare theory that incorporates two crucial features: Executive leadership and party politics.
-First, in mayor-council municipalities, mayors tend to be central in the local public service decisions.
-Mayors have the prerogative in proposing public investments, much as presidents in presidential systems.
+In this paper, we propose a local legislature size and welfare theory that incorporates two crucial features: Executive leadership and party politics.
+First, in mayor-council municipalities, mayors tend to be central in local public service decisions.
+Mayors have the prerogative to boost public investments, like presidents in federal governments.
 Second, partisanship is essential at the local level, even in settings where the ideological attachment is weak, such as in most young democracies.
-Party attachment helps structures political views \citep{samuels2014power}, and local-level elites usually belong to different factions and parties.
-They fight for power in the municipality by controlling various parties and forming distinct pre-electoral coalitions.\footnote{Elite political competition in the local level has also been linked to violence and conflict in Brazil and elsewhere \citep{hoelscher2015politics, mignozzetti2018predatory}.} In most cities, family ties are substitutes for the ideological component, but the most influential local leaders sort themselves in different political groups \citep{nunes1977coronelismo, ferraz2020political}.
+Party attachment structures political views \citep{samuels2014power}, and local-level elites usually belong to different factions and parties.
+They fight for power in the municipality by controlling various parties and forming distinct pre-electoral coalitions.\footnote{Elite political competition in the local level has also been linked to violence and conflict in Brazil and elsewhere \citep{hoelscher2015politics, mignozzetti2018predatory}.} In many cities, family ties may be substitutes for the ideological component, but influential local leaders usually sort themselves into different political groups \citep{ferraz2020political, nunes1977coronelismo}.
 
@@
 Mayors make the initial policy proposal that consists of an investment in public goods provision, a decision to extract rents for personal gains, and a vector of side-transfers for councilors.
-If they fail to secure majoritarian support from councilors, a reversal stage occurs, where the decision leaves the mayor's office, and councilors then propose the public investments.
-In this mayor-council bargaining, costs come from the side-transfers required to secure a majority among councilors.
-I show that in a model without partisan concerns, bargaining costs always increase with larger city council size, lowering public goods provision and rents.
-However, adding partisanship decreases the bargaining costs when the chances of electing councilors aligned with the mayor are sufficiently high.
+If they fail to secure majoritarian support from councilors, a reversal stage occurs, where the decision leaves the mayor's office and councilors propose the public investments.
+In this mayor-council bargaining process, costs come from the side-transfers required to secure a majority among councilors.
+We show that in a model without partisan concerns, bargaining costs always increase with larger city councils, which in turn lower public goods provision and rents.
+However, partisanship decreases bargaining costs when the chances of electing councilors aligned with the mayor are sufficiently high.
 Lower bargaining costs release funds for mayors to invest in public goods provision.
-In this case, a larger city council may have more partisan councilors aligned with the mayor, lowering the mayor's bargaining costs and increasing the equilibrium public goods provision.
+In this case, a larger city council may have more partisan councilors aligned with the mayor, reducing the mayor's bargaining costs and increasing the equilibrium public goods provision.
 
-I test these theoretical predictions by exploiting an exogenous variation in Brazilian city council sizes.
-In 2004, the judiciary reinterpreted the Constitution, unexpectedly changing the number of city councilors.
-Before the decision, towns could freely choose their legislature size, but in March 2004, the Superior Electoral Court created population thresholds, adding one councilor for each set of 47,619 inhabitants.
-Around these cutoffs, the decision represented an exogenous change in city council size, allowing me to investigate the effects of increasing the number of local legislators in Brazil.
+We test these theoretical predictions by exploiting an exogenous variation in Brazilian city council sizes.
+In 2004, the judiciary reinterpreted the Brazilian Constitution and unexpectedly changed the number of councilors in several municipalities.
+Until then, towns could freely determine their legislature size, but in March 2004 the Supreme Electoral Court created population thresholds and added one councilor to each set of 47,619 inhabitants.
+Around these cutoffs, the decision represented an exogenous change in city council size, allowing us to investigate the effects of increasing the number of local legislators in Brazil.
 
-Studying 2005 to 2008 Brazilian mayoral term, I find that increasing city council size changed the composition of the mayoral coalition and the number of appointed bureaucrats in the municipality.
+We find that larger city councils changed the composition of mayoral coalitions and the number of appointed bureaucrats in the municipality.
 The extra city councilor had a 91 percent chance of belonging to the mayor's pre-electoral coalition.
-This enhanced chances of electing a councilor connected with the mayor decreased the bargaining costs for the mayor, freeing investments for public services.
+This enhanced the chances of electing a councilor connected with the mayor, which then decreased the bargaining costs for the mayor and boosted investments in public services.
 Moreover, the number of appointed bureaucrats increased by 104 with the additional councilor.
-In Brazil, more appointed bureaucrats lead to higher quality workers, better service provision, and more accountability \citep{toral2019benefits}.
+In Brazil, appointing bureaucrats leads to higher quality workers, better service provision, and more accountability \citep{toral2019benefits}.
 
-More support for the mayors and more politically appointed bureaucrats correlate with city councilors' service provision expectations and legislation approved in Brazilian municipalities.
-I surveyed 174 former councilors who served during the 2005-2008 term, and they corroborate that mayors use bureaucratic appointments and granting favors to secure support.
-As the formal model shows, bargaining with councilors has a resource transfer component.
-By investigating what councilors prefer to provide to voters, I find that councilors demand job appointments, as these are helpful for their reelection chances and improve municipal welfare.
-These findings align with a novel dataset I build with 346,553 laws passed in 63 municipalities within ten thousand inhabitants away from the cutoffs.
-The legislation in municipalities on the left and on the right-hand side of the cutoffs comprised local public goods.
-However, municipalities with larger city councils had around 15.0 percent more public goods provision proposals, suggesting an increase in service provision legislation.
+Higher mayor support and more appointed bureaucrats correlate with city councilors' service provision expectations and legislation approved in Brazilian municipalities.
+We surveyed 174 former councilors who served during the 2005-2008 term, and they corroborate that mayors use bureaucratic appointments and political favors to secure support.
+As the formal model shows, bargaining with councilors requires offering transfers to the representatives.
+By investigating what councilors prefer to provide to voters, we find that councilors mainly demand job appointments, as these increase their reelection chances and improve municipal welfare.
+These findings align with a novel dataset we built with 346,553 laws passed in 63 municipalities within ten thousand inhabitants away from the cutoffs.
+The legislation in municipalities on the left and on the right-hand side of the cutoffs mentioned local public goods.
+However, municipalities with larger city councils had around 15 percent more public goods provision proposals, what is in line with our expectations.
 
-Finally, I show that the increase in legislature size significantly impacts municipal education and health care.
+Finally, we show that the increase in legislature size significantly impacts municipal education and health care.
 Increasing the city council size by one legislator lowers infant mortality by 2.01 children per one thousand infants born and reduces postneonatal mortality by 0.90 children per one thousand infants that survived their first 28 days.
@@
 This paper contributes to three strands of the literature.
-First, this paper contributes to a large literature on multilateral bargaining.
-Repeated models of multilateral bargaining started with \citet{baron1989bargaining}, which extended the bilateral bargaining game proposed by \citet{rubinstein1982perfect} to more than two players.
-Several papers followed \citet{baron1989bargaining}, adding endogenous recognition power, changing the size of the required majority, adding partisanship, and testing the predictions of these models in the lab \citep{calvert2005legislative, choate2019partisan, agranov2020persistence, baranski2020determinants}.\footnote{See \citet{eraslan2019legislative} for a comprehensive review of the multilateral bargaining and \citet{ray2015coalition} for a review on coalition formation.} In this paper, I extend the \citet{baron1989bargaining} model under closed rules, adding the mayor's first move and political partisanship.
-Partisanship here is different from \citet{choate2019partisan} since I consider partisan as a zero-sum effect that is positive for politicians aligned with the mayor and negative otherwise.
+First, this paper dialogues with a large literature on multilateral bargaining.
+Repeated models of multilateral bargaining started with \citet{baron1989bargaining}, who extended the bilateral bargaining game proposed by \citet{rubinstein1982perfect} to more than two players.
+Several papers followed \citet{baron1989bargaining}, manipulating endogenous recognition power, the size of the required majority, and partisanship in the models \citep{agranov2020persistence, baranski2020determinants, calvert2005legislative, choate2019partisan}.\footnote{See \citet{eraslan2019legislative} for a comprehensive review of multilateral bargaining and \citet{ray2015coalition} for a review on coalition formation.} In this paper, we extend the \citet{baron1989bargaining} model under closed rules and add the mayor's first move and political partisanship.
+Partisanship here is different from \citet{choate2019partisan} since we consider partisanship as a zero-sum effect that is positive for politicians aligned with the mayor and negative otherwise.
 This paper investigates the often overlooked effect of legislature size on the bargaining equilibrium strategies.
 
-Second, this paper contributes to the literature regarding the political and economic effects of larger legislatures.
-Following the contribution by \citet{Weingastetal1981}, the "law of 1/n" posits that larger legislatures increase the legislative pressure for providing targeted public goods to local supporters at the expense of the entire polity \citep{alptekin2021effect}.
-The corollary of the "law of 1/n" is that increasing legislature size should promote excessive public spending.\footnote{\citet{PrimoSnyder2008} show that legislature size may result in positive or negative expenditures, depending on factors such as the degree that local public goods can exclude non-locals or deadweight costs associated with taxation.} In the US metaphor, this would explain significant infrastructure spending in smaller districts.
-However, the "law of 1/n" literature left aside the public goods provision and welfare.
-This paper is one of the first papers to study the number of local legislators on welfare.
-The model provides a theoretical expectation based on the chances of electing a politician aligned with the mayor.
-The empirical estimates confirm the theoretical predictions, with the additional fact that legislature size has a null effect on expenditures in Brazil.
+Second, this paper contributes to the literature on the political and economic effects of larger legislatures.
+Following the contribution by \citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures increase the legislative pressure for providing targeted public goods to local supporters at the expense of the entire polity \citep{freire2021legislature}.
+The corollary of the "law of $1/n$" is that increasing legislature size promotes excessive public spending.\footnote{\citet{PrimoSnyder2008} show that legislature size may result in positive or negative expenditures, depending on factors such as the degree that local public goods can exclude non-locals or deadweight costs associated with taxation.} In the US metaphor, this would explain significant infrastructure spending in smaller districts.
+However, the "law of $1/n$" literature rarely mentions the relationship between public goods provision and welfare.
+This paper is one of the first to study how the number of local legislators affects welfare.
+Our model provides a theoretical expectation based on the chances of electing a politician aligned with the mayor.
+The empirical estimates confirm our theoretical predictions, with the additional fact that legislature size has a null effect on expenditures in Brazil.
 
-Finally, it contributes to a growing literature on municipal partisan politics.
+Finally, our article also contributes to a growing literature on municipal partisan politics.
 Most papers in this area estimate the effects of the mayor's party on political outcomes.
@@
 Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors.
-\citet{frey2020larger}, using the discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds I study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
+\citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
 This paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.
@@
 In mayor-council cities, the power is divided between a mayor that controls the Executive branch and a city council that supports or sanctions the policies proposed by the mayor.
-In this setting, consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$.
+In this setting, consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
 The mayor has the prerogative of proposing a vector of policies that is voted by the city councilors.
@@
 
-The city council votes the mayor's proposal, and if councilors accept it, the mayor implements it.
+The city council votes the mayor's proposal, and if councilors accept it, the proposal is implemented.
 Otherwise, a reversal policy takes place.
 Reversal policy in this context means that the mayor's proposal failed to secure the majority of council votes.
-The decision process leaves the mayor's office, and it is transferred to the council.
-The types of reversal policies are crucial for my argument, as it changes the relative strength of the council in their bargaining with the mayor.
-I investigate two types of reversal policies: a baseline reversal with no parties and a hybrid mechanism with partisan and non-partisan concerns.
+The decision process then leaves the mayor's office and it is transferred to the council.
+The types of reversal policies are crucial for our argument, as it changes the relative strength of the council when they bargain with the mayor.
+We investigate two types of reversal policies: a baseline reversal with no parties and a hybrid mechanism with partisan and non-partisan concerns.
 The differences between these two mechanisms are that the non-partisan councilors only care about rents, while partisan councilors care about both rents and policy.
 
-To govern, the mayor must convince at least half of the city councilors to support her policy proposals.
-Similar to \citet{buenodemesquita2005logic}, I assume that the selectorate, i.
-e., the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors.
-The winning coalition, the minimum number of members that must be convinced to implement the policy, is equal to half of the selectorate $N/2$.
-City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
-I leave the definition of these transfers open, as this facilitates the relationship with several instruments that mayors can use to pressure city councilors.
-Transfers may be granting electoral favors, favoring clientelistic brokers, spending in areas that the councilor has political or personal interests, providing portfolio (municipal offices) and public jobs within the municipal bureaucracy, or even campaign contributions and bribes.
-The use of transfers to affect the councilors' choices generate a bargaining cost of $C_G$.
-The bargaining costs vary with the reversal mechanism and the legislature size.
+The mayor must convince at least half of the city councilors to support her policy proposals.
+Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, that is, the individuals who have a say in the mayor's policy proposals, are the $N$ city councilors.
+The winning coalition, the minimum number of members that must be convinced to implement the policy, is equal to half of the selectorate ($N/2$).
+City councilors are motivated by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
+We leave the definition of these transfers open, as this allows us to analyze how mayors combine transfers with other incentives to pressure city councilors.
+Exemples of transfers are granting electoral favors, favoring clientelistic brokers, spending in areas that the councilor has political or personal interests, providing portfolio (municipal offices) and public jobs within the municipal bureaucracy, or even giving campaign contributions and bribes.
+The use of transfers to influence the councilors' choices generate a bargaining cost of $C_G$.
+Bargaining costs vary according to the reversal mechanism and the size of the legislature.
 
-Finally, after learning the bargaining costs, the mayor decides a level of public goods provision ($g$) and pockets rents ($r$).
+Finally, after learning the bargaining costs, the mayor provides a level of public goods provision $g$ and pockets rents $r$.
 Public goods provision helps the mayor to get reelected.
-Rents are for direct mayor's consumption, and they do not contribute to the mayor's electoral success.\footnote{This model, similarly to \citet{cowen1994rent} and \citet{buenodemesquita2005logic} combines public goods provision and rent extraction.
+Rents are for direct mayor's consumption, and they do not contribute to the mayor's electoral success.\footnote{This model, similar to \citet{cowen1994rent} and \citet{buenodemesquita2005logic}, combines public goods provision and rent extraction.
 For a dynamic bargaining model that incorporates transfers to districts and public goods provision, see \citet{battaglini2012legislative}.} This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
@@
 The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office.
-I assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
+This benefit captures the tangible and intangible gains that the mayor receives from holding the public office.
+We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
 If the mayor's policy proposal is approved, then the expected utility for the mayor is:
@@
 
-The policy choices of the mayor are subject to the municipal budget constraint.
-The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget must be balanced.
-I also assume that there are enough resources for the mayor to govern.
+The policy choices of the mayor are subject to municipal budget constraints.
+The municipality has $R > 0$ resources and cannot run debts, meaning that the budget must be balanced.
+We also assume that there are enough resources for the mayor to govern.
 
-Let $C_G$ be the bargaining costs. The budget balance constraint requires the offers that the mayor makes to the city councilors to satisfy the following inequality:
+Let $C_G$ be the bargaining costs. The budget balance constraint requires that the offers the mayor makes to the city councilors must satisfy the following inequality:
 
@@
 If her proposal is accepted, it is implemented.
-If councilors reject the offer again, the budget shrinks by a factor $\delta$, and another city councilor is recognized to propose.
+If councilors reject the offer again, the budget shrinks by $\delta$, and another city councilor is recognized to propose.
 The process repeats until a proposal is finally accepted.
 
-After studying the non-partisan baseline, I consider a situation that combines both partisan and non-partisan legislature concerns.
+We now consider a situation that combines both partisan and non-partisan legislature concerns.
 Each councilor has a party affiliation.
@@
 If councilors reject the mayor's proposal, no public goods are provided ($p=0$).
-Moreover, in equilibrium, I assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the online supplemental materials, I consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affect choices in any potential history of the game.
+Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the Supplementary Materials, we consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affects choices in any potential history of the game.
 The equilibrium public goods provision level is even higher than in the model presented here, as city councilors prefer to approve the mayor's proposal than run the risk of an opposition member becoming the proposer.}
@@
   \begin{itemize}
-    \item If the council accepts, the policy is implemented, and the game ends. 
+    \item If the council accepts the proposal, the policy is implemented and the game ends. 
     \item Otherwise, the reversal policy is implemented.
@@
 If the offer is accepted, it is implemented.
-If rejected, the reversal policy stage restart.\footnote{In section B.1 of the online supplemental materials, I solved three reversal mechanisms.
-The two in here, plus a mechanism with only political concerns.}
+If rejected, the reversal policy stage restart.\footnote{In section A.1 of the Supplementary Materials, we solve three reversal mechanisms.
+The two we present here, plus a mechanism with only political concerns.}
 \end{enumerate}
 
-The solution concept I use in this model is the Subgame Perfect Nash Equilibrium.
-A Subgame Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game.
-The solution is found using backward induction.
+The solution concept we use in this model is the subgame perfect Nash equilibrium.
+This game requires that the strategies follow a Nash equilibrium in each subgame.
+We find the solution using backward induction.
 In the model with infinitely repeated proposals, any strategy can be shown to be a Nash equilibrium.
 Thus, a natural assumption is to extend the equilibrium concept to require the equilibrium to be stationary.
-A Stationary Subgame Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should take the same offer at time $k$ \citep{rubinstein1982perfect}.
-Stationarity gives us an objective of finding a proposal that would be accepted at any stage in the game.
-Applying this reasoning, I can characterize a sequence of offers for each point $k$ in time.
+A stationary subgame perfect equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should take the same offer at time $k$ \citep{rubinstein1982perfect}.
+Stationarity gives us a method to find a proposal that would be accepted at any stage of the game.
+Hence, we can characterize a sequence of offers for each point $k$ in time.
 For the mayor, the optimal offer is at $k=0$, representing a no delay in policy implementation.
-Moreover, I assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.
+Moreover, we assume that the players play no dominated strategies, even when there is insufficient support for the policy.
 
-For the solution to be of general interest, I solve bargaining costs for the expected number of opposition and government-aligned city councilors.
-This is because the solution for each fixed number of opposition and government councilors is trivial and does not help understand the overall relationship between council size and bargaining costs.
+For the solution to be of general interest, we solve the bargaining costs for the expected number of opposition and government-aligned city councilors.
+This is because the solution for each fixed number of opposition and government councilors does not help us understand the overall relationship between council size and bargaining costs.
 
@@
 
-Solving the game by backward induction requires us to start with the councilor's strategies.
-However, for exposure convenience, assume that I solved the game for the councilors and found the equilibrium bargaining costs $C_G(N)$ when there are $N$ city councilors.
-I now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
+Solving the game by backward induction requires us to start with the councilors' strategies.
+However, to conserve space, assume that we solved the game for the councilors and found the equilibrium bargaining costs $C_G(N)$ when there are $N$ city councilors.
+We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
 The mayor benefits from public goods provision, as it increases the chances of her reelection.
@@
 
-In equilibrium, the budget binds, and the first-order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equal to the marginal benefits of reelection:
+In equilibrium, the budget binds, and the first-order condition for an optimal public goods provision makes the marginal benefits to increase rents.
+In this case, it means that the marginal costs of providing the public goods is equal to the marginal benefits of reelection:
 
@@
 
-All proofs are in section B.1 of the online supplemental materials.
-The proof's intuition involves finding what happens to the mayor's marginal utility when I increase both $g$ and $N$.
-As $N$ increases discretely on a complete lattice, I use monotone comparative statics to derive the conditions for increasing differences \citep{milgrom1994monotone, ashworth2006monotone}.
+All proofs are in section A.1 of the Supplementary Materials.
+The proof's intuition involves finding what happens to the mayor's marginal utility when we increase both $g$ and $N$.
+As $N$ increases discretely on a complete lattice, we use monotone comparative statics to derive the conditions for increasing differences \citep{milgrom1994monotone, ashworth2006monotone}.
 Increasing differences mean that higher $N$ leads to higher equilibrium $g$.
@@
 Proposition \ref{prop1} provides the first empirical hypothesis to test: \textit{if the bargaining costs decrease when the legislature size increases, then the provision of the public goods increases when the legislature size increase}.
-Now I study each reversal mechanism to determine the condition under which the bargaining costs decrease when legislature size increases.
+Now we study each reversal mechanism to determine the condition under which the bargaining costs decrease when legislature size increases.
 
@@
 
-In the non-partisan reversal, I assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly.
+In the non-partisan reversal, we assume that when the council rejects the mayor's office, a reversal stage starts with the random selection of one councilor.
 This formulation is similar to the closed rules proposal in \citet{baron1989bargaining}.
-To find a Stationary Subgame Perfect Nash equilibrium, suppose that there were $k-1$ rejections, and the game is at the $k$-th stage.
+To find a stationary subgame perfect Nash equilibrium, suppose that there were $k-1$ rejections, and the game is at the $k$-th stage.
 A councilor accepts the proposer's offer if, and only if, to accept the offer at $k$ is better than or equal to wait until the next stage $k+1$.
@@
 
-On the left-hand side, I place the offer.
-On the right-hand side, there are two components.
+We place the offer on the left-hand side.
+There are two components on the right-hand side.
 The first is the amount that the councilor $i$ gets when she is the proposer.
 It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers she makes to convince half of the councilors.
-The second part is the gains if the councilor rejects the current received offer but still gets an offer in the following round.
+The second part represents the gains if the councilor rejects the current received offer but still gets an offer in the following round.
 It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the transfer amount.
@@
 This is because the city councilors are exchangeable.
-The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, I could have dropped the $i$ in the solution).
+The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution).
 After some algebra, the offer $x_i$ must be greater than or equal to:
@@
 \begin{proposition}
-In the baseline non-partisan reversal, the bargaining costs always increase when the size of the legislature increases.
+In the baseline non-partisan reversal, bargaining costs always increase when the size of the legislature increases.
 \end{proposition}
 
-The intuition for the results is that every additional councilor will demand more resources from the mayor.
+The intuition for the results is that every additional councilor demands more resources from the mayor.
 Thus, more councilors represent higher bargaining costs.
 And if the bargaining costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-Below I show that partisanship is the key to understand how larger legislature sizes can increase public goods provision.
+Below we show that partisanship is the key to understand how larger legislature sizes can increase public goods provision.
 
@@
 
-I decompose these costs into two components—first, the costs in terms of rents.
+We decompose these costs into two components.
+First, the costs in terms of rents.
 Second, the costs (or benefits) from political alignment.
-In this context, the bargaining costs depend on the mayor's offers for councilors in the mayor's coalition versus the mayor's proposals for councilors in the opposition.
-The ex-ante chance of an opposition member be elected is equal to $1-\gamma$, and taking the weighted averages, these costs become:
+In this context, the bargaining costs depend on the mayor's offers for councilors in her coalition versus the mayor's proposals for councilors in the opposition.
+As the ex-ante chance of an opposition member being elected is equal to $1-\gamma$, after taking the weighted averages these costs become:
 
@@
 
-Also, the threshold $\underline{\gamma}$ that captures the probability of electing a politician aligned with the government is decreasing in the political value of the mayor's policy $p$ and the size of the legislature $N$.
+Also, the threshold $\underline{\gamma}$ that captures the probability of electing a mayor-aligned policitian decreases along with the political value of policy $p$ and the size of the legislature $N$.
 This means that intensive partisanship and larger legislatures make it easier to satisfy the electoral threshold.
@@
 
-My model provides two empirically testable hypotheses.
+Our model provides two empirically testable hypotheses.
 Consider a municipality with a city council comprised of $N$ legislators.
-If the city increases the size of the council to $N+1$.
-Then, in a partisan setting:
+Then the city increases the size of the council to $N+1$.
+Thus, in a partisan setting:
 
@@
 label=H\arabic*.]
-  \item The bargaining costs decrease with legislature size when the chance of electing a government-aligned legislator is sufficiently high.
-  \item The provision of public goods increases when the bargaining costs decrease with legislature size.
+  \item Bargaining costs decrease with legislature size when the chances of electing a government-aligned legislator are sufficiently high.
+  \item Public goods provision increases if bargaining costs decrease with legislature size.
 \end{enumerate}
@@
 
-In the paper, I show that the provision of education and healthcare improves in Brazil.
-This is because the chances of electing a city councilor aligned with the mayor are 91%, thanks to the rule of distributing seats adopted in the country.
+In this paper, we show that the provision of education and health care in Brazil improves with larger legislatures.
+This is because the chances of electing a city councilor aligned with the mayor are 91 percent, thanks to the rule of distributing seats adopted in the country.
 
-However, other pathways could explain the nexus between city council size and welfare.
-First, improvements in representation could cause changes in health care and education.
+However, other pathways may also explain the nexus between city council size and welfare.
+First, improvements in representation could change the provision of health care and education.
 Increasing legislature size without changing the population makes councilors represent fewer people.
@@
 This facilitates the representation of minorities, as they have to gather fewer votes to elect a city councilor.
-A minority representative can advocate for policies that would improve the welfare of marginalized groups \citep{pande2003can, ChattopadhyayDuflu2004, chin2011redistributive}.
+A minority representative can advocate for policies that would improve the welfare of marginalized groups \citep{ChattopadhyayDuflu2004, chin2011redistributive, pande2003can}.
 Diversity could also improve governance in municipalities \citep{rugh2011provision}.
-Moreover, more women in public offices can shift the service provision toward welfare expenditure \citep{duflo2012women, brollo2016happens, hernandez2018women, funk2019representative}.
-Therefore, an alternative hypothesis to explain the increased service provision is that larger legislatures are improving female and minority representation.\footnote{For a description of the barriers faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
+For instance, more women in public offices may shift service provision toward welfare expenditure \citep{brollo2016happens, duflo2012women, funk2019representative, hernandez2018women}.
+Therefore, an alternative hypothesis to explain the increased service provision is that larger legislatures improve female and minority representation in Brazil.\footnote{For a description of the barriers faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
 
 Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{arvate2013electoral}.
-In a political system with around thirty parties and a sample average of almost ten parties in the municipalities I study, candidates per seat can increase exponentially.
+In a political system with around thirty parties and a sample average of almost ten parties in the municipalities we study, candidates per seat can increase exponentially.
 According to the Brazilian electoral law, each party can sponsor 1.5 times the number of seats as candidates.
@@
 Finally, the mayor and the legislature carry out the provision of services.
-Similar to what happens in firms, an extra employee can increase the firm productivity frontier by improving cooperation and a synergistic output \citep{alchian1972production, holmstrom1982moral}.
-A similar argument can view the increase in council size as augmenting the public service production capability in the municipality.
-As the production of the legislature manifests into legislation, an alternative hypothesis to explain the increased service provision is that more laws proposed by the city councilors are being approved.
+Similar to what happens in firms, an extra employee can increase the firm productivity frontier by improving cooperation and synergistic outputs \citep{alchian1972production, holmstrom1982moral}.
+A similar argument would posit that the increase in council size increases the public service production capability in the municipality.
+As the production of the legislature manifests itself into legislation, an alternative hypothesis to explain the increased service provision is that more laws proposed by the city councilors are being approved.
 
@@
 label=AH\arabic*.]
-  \item The representation of females increases with legislature size, improving public goods provision.
-  \item The representation of non-whites increase with legislature size, improving public goods provision.
-  \item The competitiveness of the election increases with legislature size, improving public goods provision.
-  \item The legislative production increases with legislature size, improving public goods provision.
+  \item Female representation increases with legislature size, improving public goods provision.
+  \item Non-white representation increase with legislature size, improving public goods provision.
+  \item Election competitiveness increases with legislature size, improving public goods provision.
+  \item Legislative production increases with legislature size, improving public goods provision.
 \end{enumerate}
 
-I show below that hypotheses H1 and H2 hold, while the data falsify the alternative hypotheses AH1 to AH4.
+We show below that hypotheses H1 and H2 hold, while the data falsify the alternative hypotheses AH1 to AH4.
 
@@
 In 2004, Brazil comprised 5,560 municipalities.
-According to the Brazilian Constitution, each city must provide healthcare, primary education, transportation, and infrastructure to its citizens.
+According to the Brazilian Constitution, each city must provide health care, primary education, transportation, and infrastructure to its citizens.
 Municipalities have the authority to enact local laws and collect taxes on housing and services.
@@
 Second, they oversee the public budget and sanction mayors who do not comply with fiscal legislation.
-Councilors and mayors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrollment, and even paying their voters' utility bills \citep{nichter2011electoral, lopez2017legisladores}.
+Councilors and mayors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrollment, and even paying their voters' utility bills \citep{lopez2017legisladores, nichter2011electoral}.
 
@@
 
-Following the ruling of the Supreme Court, in March 2004, the Brazilian Electoral Court established a series of population cutoffs for all municipal legislatures.
+Following the ruling of the Supreme Court, in March 2004 the Supreme Electoral Court established a series of population cutoffs for all municipal legislatures.
 Following the Brazilian Constitution, the Court specified that cities with up to one million residents should have between 9 and 21 legislators.
@@
 
-This decision makes Brazil the ideal testing ground for my theory.
+This decision makes Brazil the ideal testing ground for our theory.
 Although an endogenous decision motivated the Electoral Court ruling, the population cutoffs created sharp discontinuities in the distribution of local council seats.
@@
 
-I use four groups of city-level variables in the models.
+We use four groups of city-level variables in our models.
 The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution.
-I add them to the models to improve the balance between treated and non-treated units.
+We add them to the estimates to improve the balance between treated and non-treated units.
 The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality.
-The data come from the Superior Electoral Court (Tribunal Superior Eleitoral--TSE) and the 2000 Brazilian census.
+The data come from the Supreme Electoral Court and the 2000 Brazilian census.
 
-Second, I look into municipal data, city councilors' characteristics, approved legislation, and an online survey with 174 former city councilors that served during 2005--2008 term to investigate the political mechanism.\footnote{I also analyzed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
+Second, we look into municipal data, city councilors' characteristics, approved legislation, and an online survey with 174 former city councilors that served during 2005--2008 term to investigate potencial political mechanisms.\footnote{We also analyzed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
 The authors asked councilors about their daily work.
-The interviews reinforced that the mayor's agenda dominates councilors' work and is partisan without strictly following party lines.
-Municipal politics is divided into families or poles of power, belonging to different party affiliations.
-Councilors from other parties gravitate around either of these groups, hence the opposition and government-aligned logic.} The municipal data contains: 1) the number of councilor's belonging to the mayor's pre-electoral coalition; 2) the number of appointed bureaucrats; 2) the councilor's gender and race; 3) the competitiveness of each city council seat; 4) the proportion of laws proposed by the city council that was approved.
-All variables come from the Superior Electoral Court, the Senate legislative support Interlegis, and the Brazilian Bureau of Statistics (IBGE).
+The interviews reinforced that the mayor's agenda dominates councilors' work and it is partisan without strictly following party lines.
+Municipal politics is divided into families or poles of power that belong to different party affiliations.
+Councilors from other parties gravitate around these groups, hence the opposition and government-aligned logic.} The municipal data contains: 1) the number of councilor's belonging to the mayor's pre-electoral coalition; 2) the number of appointed bureaucrats; 2) the councilor's gender and race; 3) the competitiveness of each city council seat; 4) the proportion of laws proposed by the city council that was approved.
+All variables come from the Supreme Electoral Court, the Senate legislative support Interlegis, and the Brazilian Bureau of Statistics.
 
-Third, I also collected 346,553 bills from cities within ten thousand inhabitants from the 2004 population thresholds.
-I selected 63 out of 202 municipalities whose voting records were available online.
-I evaluate proposal types, discriminating between local public goods, oversight, and other legislative activity.
-Examples of the local public goods are investing in a public health clinic, requesting school bureaucracy to accommodate an extra child, renovating sewage, and fixing potholes on a given street.\footnote{My theory does not differentiate between clientelism and broad service provision, as it is hard to disentangle differences in the local level legislation.
+Third, we also collected 346,553 bills from cities within ten thousand inhabitants from the 2004 population thresholds.
+We selected 63 out of 202 municipalities whose voting records were available online.
+We evaluate proposal types, discriminating between local public goods, oversight, and other legislative activity.
+Examples of the local public goods are investing in a public health clinic, requesting school staff to accommodate an extra child, renovating sewage, and fixing potholes on a given street.\footnote{Our theory does not differentiate between clientelism and broad service provision, as it is hard to disentangle differences in the local level legislation.
 A voter may request a particular service, such as fixing a pothole.
 Attending this request can be interpreted as a clientelistic practice.
-Still, the provision of the service generates non-excludable benefits to the adjacent neighborhood.} Oversight bills are accountability and transparency mechanisms meant to keep public services undertaken by the bureaucracy in check.
+Still, the provision of the service generates non-excludable benefits to the adjacent neighborhood.} Oversight bills are accountability and transparency mechanisms meant to keep public services provision in check.
 Other legislation comprises bills that do not fit in the previous categories.
 Examples are changes in street names, motions to honor citizens or groups, and legislative and internal city council procedures.
-I provide further information about the legislation dataset and the city council survey in sections B.13 and B.14 of the online supplemental materials.
+We provide further information about the legislation dataset and the city council survey in sections A.13 and A.14 of the Supplementary Materials.
 
 The last set of variables quantify social welfare.
-The focus is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
-I measure access to education with the average enrollment in primary (K--4) municipal public schools.
-I assess education quality with the Education Development Index (\ 'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
-The index is a weighted average of student scores in Portuguese and Mathematics (0--10) multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
-To test the effect of the 2004 ruling on healthcare, I collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants that survived more than 28 days, but died before completing one year old.
-The source of all healthcare variables is the Brazilian Ministry of Health Data Center (DataSUS).
+Our focus is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
+We measure access to education with the average enrollment in primary (K--4) municipal public schools.
+We assess education quality with the Education Development Index (\ 'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
+The index is a weighted average of student scores in Portuguese and Mathematics (0--10), multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
+To test the effect of the 2004 ruling on healthcare, we collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants who survived more than 28 days, but died before reaching one year of age.
+The source of all health care variables is the Brazilian Ministry of Health Data Center (DataSUS).
 
 Together, this evidence provides a clear picture of local-level politics patterns in Brazil, from the political mechanism to the municipal welfare consequences of the larger city council size ruling.
-Summary statistics and variable descriptions follow in section B.2 of the online supplemental materials.
+Summary statistics and variable descriptions follow in section A.2 of the Supplementary Materials.
 
@@
 
-I employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Superior Electoral Court resolution as treatment indicators.
+We employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Supreme Electoral Court resolution as treatment indicators.
 Figure \ref{fig:runningvarplot} displays the distribution of municipalities within each city council size.
@@
 
-\vspace{.5cm}
+Our identification strategy relies on three assumptions.
+First, no municipality should be able to self-select into each side of the discontinuity.
+Second, as we estimate a sharp RDD, the council size should increase precisely as the law mandates.
+Third, this design assumes that the pre-treatment variables, collected before the 2003 Supreme Federal Court decision, were not affected by the 2004 ruling on council size.
+Moreover, for all the actual models estimated here, we fitted placebo cutoffs to check whether the estimation technique leads to consistent results.
+The placebo cutoffs are the dashed lines in Figure \ref{fig:runningvarplot}.
 
@@
 
-My identification strategy relies on three assumptions.
-First, no municipality should be able to self-select into each side of the discontinuity.
-Second, as I estimate a sharp RDD, the council size should increase precisely as the law mandates.
-Third, this design assumes that the pre-treatment variables, collected before the 2003 Supreme Court decision, were not affected by the 2004 ruling on council size.
-Moreover, for all the actual models estimated here, I fitted placebo cutoffs to check whether the estimation technique leads to consistent results.
-The placebo cutoffs are the dashed lines in Figure \ref{fig:runningvarplot}.
-
-For the first assumption, in section B.3 of the online supplemental materials, I test distribution imbalances running the \citet{McCrary2008} and \citet{cattaneo2019simple} tests.
+For the first assumption, in section A.3 of the online supplemental materials, we assess distribution imbalances running the \citet{McCrary2008} and \citet{cattaneo2019simple} tests.
 The tests show no distribution imbalances.
@@
 When running an RDD on these discontinuities, a consistent estimator should fit the exact change of one councilor.
-However, if I pool all the discontinuities together with no correction, I find an increase in council size of 1.63 councilors (see the first estimate in Table \ref{validitycheck}).
-This imbalance is because when combining all the discontinuities, the estimation is implying that municipalities below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
+However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors (see the first estimate in Table \ref{validitycheck}).
+This imbalance occurs because when we combine all the discontinuities, the model implies that municipalities below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
 That is incorrect because the comparison is inconsistent in council size, and these municipalities diverge in many other aspects.
 
-To avoid this problem, in section B.5 of the online supplemental materials, I show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in my case, the population in 2003), improves the consistency and efficiency of the estimates.
-Relying on this fact, I add five controls to the estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
+To avoid this problem, in section A.5 of the Supplemental Materials, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
+Relying on this fact, we add five controls to the estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
 The reason for the first variable is the multiple threshold assignments.
-I add GDP per capita because wealthier cities tend to have better public services.
-The number of seats in 2000 intends to control that some municipalities could experience a change provoked by the previous council size, confounding my estimates.
-The year and the northeast dummies serve to improve efficiency.
+We add GDP per capita because wealthier cities tend to have better public services.
+The number of seats in 2000 intends to control that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
+The year and the Northeast dummies serve to improve efficiency.
 Adding controls improves efficiency in RDD and also enhances the consistency in the multiple thresholds RDD \citep{calonico2019regression}.
@@
 Table \ref{validitycheck} displays the results of the validity checks.
-I run the first-stage regressions at the top of the Table, both using and not using the controlling covariates strategy proposed, for both real and placebo cutoffs.
-At the bottom, I estimate the pre-treatment covariate balance.
-Furthermore, in the online supplemental materials, I run placebo checks for all the models using placebo cutoffs within the real ones.
-The results are in sections B.6 to B.12.
+We present the first-stage regressions at the top of the Table, with and without covariates, for both real and placebo cutoffs.
+At the bottom, we estimate the pre-treatment covariate balance.
+Furthermore, in the Supplementary Materials, we run placebo checks for all the models using placebo cutoffs within the real ones.
+The results are available in sections A.6 to A.12.
 
@@
 Robust standard errors, clustered at the municipal level, in parentheses.
-Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.
+Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.
 \textit{N Left} and \textit{N Right} represent the total number of observation in the left and right sides of the thresholds (untreated).
@@
 
-Note that without adding covariates, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
-After adding covariates, the results improve, and the point estimates are now one for the primary model and zero for the placebo regressions, which are the correct values.
+Note that without the covariates, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
+When we add the covariates, the results improve and the point estimates are now one for the primary model and zero for the placebo regressions.
+These are the correct values.
 Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
-These tests reinforce the validity of my research design.
+These tests reinforce the validity of our research design.
 
@@
 
-To test the formal model's predictions, I present four sets of empirical results.
-First, I show that the alternative hypothesis, which emphasizes representation, competitiveness, and legislative productivity, fails to receive empirical support.
-Second, I show that the bargaining costs hypothesis is confirmed and that the additional legislator also promotes more appointments of bureaucrats.
-This aligns with the councilor's reported strategies employed by mayors to consolidate their support from city councilors.
-Third, I show that municipalities with an extra city councilor approve more public goods laws in general and on education and healthcare.
-Finally, I show that all these pieces of evidence result in improvements in infant mortality and elementary school enrollment, two vital services for welfare.
+To test the formal model's predictions, we present four sets of empirical results.
+First, we show that the alternative hypothesis, which emphasizes representation, competitiveness, and legislative productivity, fails to receive empirical support.
+Second, we confirm the bargaining costs hypothesis and find that the additional legislator also promotes more appointments of bureaucrats.
+This aligns with the councilors' descriptions of the strategies mayors employ to consolidate support from city councilors.
+Third, we show that municipalities with an extra city councilor approve more public goods laws in general and on education and health care.
+Finally, we show that all these pieces of evidence result in improvements in infant mortality and elementary school enrollment, two vital services for welfare.
 
@@
 However, the results could stem from different mechanisms, such as minority and female representation, competition, and increased council-sponsored legislative productivity.
-In Panel A, I counter the alternative explanations, while in Panel B, I present evidence that corroborates my findings.
+In Panel A, we counter the alternative explanations, while in Panel B, we present evidence that corroborates our findings.
+
+Panel A (Table \ref{tab:bargain}) tests hypotheses AH1 to AH4.
+AH1 and AH2 establish that better representation of under-served groups could improve welfare.
+However, columns (1) and (2) show that larger city councils do not increase the representation of females or non-whites.
+AH3 states that enhanced competition could improve responsiveness, increasing service provision.
+Looking at competition per seat in municipalities with larger city councils, Column (3) in Panel A shows a null effect of council size on the competition.
+Finally, AH4 states that council-sponsored legislation could be increasing in larger councils.
+Yet, Column (4) shows that it remains unchanged when council sizes increase.
 
@@
 
-Panel A (Table \ref{tab:bargain}) tests the hypotheses AH1 to AH4.
-AH1 and AH2 established that better representation of under-served groups could improve welfare.
-However, columns (1) and (2) show that neither gender nor representation of non-white legislators significantly increases with changes in city council size.
-AH3 stated that enhanced competition could improve responsiveness, increasing service provision.
-Looking at competition per seat in municipalities with larger city councils, Column (3) in Panel A shows a null effect of council size on the competition.
-Finally, AH4 stated that council-sponsored legislation could be increasing in larger councils.
-Yet, Column (4) shows that it remains unchanged when there is an increase in council size.
-
 Panel B (Table \ref{tab:bargain}) illustrates the mechanism put forward in the formal model.
@@
 In any case, 91\% chance is a considerably large quantity, and the extra city councilor is going to the mayoral coalition nine in every ten legislature size increases.
-This strengthens the bargaining position of the mayor and diminishes bargaining costs.\footnote{The effect of city council size on the number of mayor-aligned politicians stems from the rounding rule adopted by the proportional representation system in Brazil.
+This strengthens the political position of the mayor and diminishes bargaining costs.\footnote{The effect of city council size on the number of mayor-aligned politicians stems from the rounding rule adopted by the proportional representation system in Brazil.
 The rounding rule favors the coalitions with more votes.
@@
 
-To evidence the mechanism's operation, I build two novel datasets.
-First, I run a survey with former city councilors, asking how the mayor consolidate its coalition support within the city council.
-Second, I collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
-I hand-coded 3,466 laws into four categories: public goods, oversight, education and healthcare-related legislation, and other legislative duties.
-After hand-coding these laws, I used a supporting vector machine to classify the remainder laws.
-From the algorithms I used, the supporting vector machine performed better than the alternatives.
-
-\pagebreak
+We built two novel datasets to provide evidence for our mechanism.
+First, we ran a survey with former city councilors, asking how the mayor consolidate its coalition support within the city council.
+Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
+We hand-coded 3,466 laws into four categories: public goods, oversight, education and health care-related legislation, and other legislative duties.
+After hand-coding these laws, we used a Supporting Vector Machine (SVM) algorithm to classify the remainder laws.
+From all of the algorithms we tested, SVM achieved the highest performance.
 
@@
 This paper assumes that city councilors want to extract rents and to get reelected.
-The rents come from their continuation value in the repeated game, and the partisanship discounts them.
+The rents come from continuing in the repeated game, and the partisanship discounts that benefit.
 Figure \ref{survelec} shows that 65.9 percent of councilors mentioned that mayors use job appointments to consolidate their coalition support.
-59.0 percent of the surveyed councilors mentioned that mayors use personal favors, such as shifting resources to places where the councilors have electoral support, to solidify their governing coalition.
+Moreover, 59.0 percent of the surveyed councilors affirmed that mayors use personal favors, such as shifting resources to places where the councilors have electoral support, to solidify their governing coalition.
 Granting favors works as rent transfers for councilors.
@@
 
-I have established in Table \ref{tab:bargain} column (4) that the quantity of laws approved by councilors remain constant.
-However, this tells us little about the composition of the legislation in municipalities with larger council sizes.
-In Figure \ref{LEGAPPR}, I show that the per capita amount of laws related to local public goods provision increased in the towns that received the extra legislator, vis-a-vis the baseline of cities that did not get an additional councilor.
-One additional city councilor increased the amount of per capita public goods laws by 15.0 percent.
+We have established in Table \ref{tab:bargain} column (4) that the quantity of laws councilors approve remain constant.
+However, this tells us little about the legislation composition in municipalities with larger council sizes.
+In Figure \ref{LEGAPPR}, we show that the per capita number of laws related to local public goods provision increases in towns that receive the extra legislator, vis-à-vis baseline cities that did not get an additional councilor.
+One additional city councilor increased the per capita amount of laws on public goods by 15.0 percent.
 Also, the number of laws that focus on healthcare and education increased by 19.7 percent.
-Looking specifically into healthcare and education legislation, the proportion of public goods laws increased by 15.7 percent, showing that the policy proposals of the mayor and councilors shifted toward local and citywide public goods.\footnote{Public goods here are not restricted to citywide goods.
+Looking specifically into healthcare and education legislation, the proportion of laws discussing public goods increased by 15.7 percent, showing that policy proposals by both the mayor and the councilors shift toward local and citywide public goods.\footnote{Public goods here are not restricted to citywide goods.
 Any service that benefits citizens, regardless of whether they are targeted to citizens or not, is considered public goods.
 For example, building a health clinic in a particular district can virtually exclude the citizens that are not living in the neighborhood.
-However, I am still considering these public goods, albeit targeted at a specific locality.}
+However, we am still considering these as public goods, albeit targeted at a specific locality.}
 
@@
 
-I study the impact of legislature size on education and health care. I collect four indicators: two in education and two in health care.
+We now study the impact of legislature size on education and health care. We use four indicators in this paper: two in education and two in health care.
 
@@
 
-Table \ref{tab:outcomes} shows that increasing the city council in one legislator generates welfare improvement in municipalities.
-In healthcare, increasing legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
+Table \ref{tab:outcomes} shows that increasing the city council by one legislator generates welfare improvement in municipalities.
+In health care, increasing the legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
 This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
@@
 
-Increasing the council size results in gains in elementary school enrollment and decreases infant mortality.
-Education quality remains unchanged but increasing enrollment without affecting quality should be interpreted as positive.
-The analysis of the legislation approved shows that the frequency of local public goods legislation increases in municipalities above the council size thresholds.
-Finally, the city council survey demonstrates that councilors and mayors align regarding appointing more public servants to the public administration.
+Increasing the council size results in gains in elementary school enrollment and in lower infant mortality.
+Education quality remains unchanged, but increasing enrollment without affecting quality should be interpreted as positive.
+The analysis of the approved legislation shows that the frequency of laws on local public goods increases in municipalities above the council size thresholds.
+Finally, the city council survey demonstrates that councilors and mayors agree about appointing more public servants to the public administration.
 
@@
 Despite evidence that side payments cemented these coalitions, many social and economic policies have been implemented.
-For instance, education and healthcare improved tremendously during the Cardoso and Lula governments \citep{acemoglu2012nations}.
+For instance, education and health care notably improved during the Cardoso and Lula governments \citep{acemoglu2012nations}.
 Of the presidents that defied the coalition system, Rousseff was impeached in her second term.
@@
 The stakes are lower, and the negotiations involve only one legislative branch.
-Still, in a system such as the Brazilian, with more than thirty-five registered parties, mayors have a difficult task in aggregate and consolidate support for their agendas.
-Having extra help in the council can tilt the bargaining towards cheaper governing, improving public goods provision.
+Still, in a system such as Brazil's, with more than thirty-five registered parties, mayors face substantial challenges to the support for their agendas.
+Having extra help in the council can tilt the bargaining towards cheaper governing, thus improving public goods provision.
 
-Moreover, this paper is not arguing that these benefits result from the absence of corruption or clientelism.
-Both the formal model and empirical evidence by \citet{britto2020corruption} show that corruption increases with legislature size.
+Moreover, we do not argue that these benefits result from the absence of corruption or clientelism.
+Both the formal model and empirical evidence provided by \citet{britto2020corruption} show that corruption increases with legislature size.
 As the model shows, city councilors receive a side transfer from mayors to support their agenda.
@@
 
-This paper opens two critical questions for future analysis.
-First, if the mechanism I claim is at work, more support means better public goods, which brings the question: Why having a city council, if when the city council checks the mayor, public goods provision may decrease?
-The evidence is inconclusive, and \citet{poulsen2018political} show that checks for the mayors also improve service provision.
-It may be that there is a non-linear effect in the relation between rents and public goods, making after some threshold mayors revert to only rents.
-Moreover, it could be that after some threshold of support, support is ineffective and even harmful, as it may trigger an intense form of elite capture.
-This question needs further investigation, and my results suggest that mayors with more support improve welfare.
-Second, it remains uncertain how other legislative design parameters affect welfare.
-For example, city councils may vary in size and the monetary compensation for councilors, committee structure, and internal power structure.
-These components may interact with size and within each other, and understanding how size plays with other features would contribute to building a better theory of how the city council size affects welfare.
+Our findings have implications that extend well beyond Brazil.
+As several countries have local city councils and multiparty systems, the dynamics we expose here may explain how fragmented legislatives are not synonymous with policy paralysis.
+This runs in contrast with well-established theories that point out that multipartism may be a peril to democratic regimes \citep{mainwaring1993presidentialism, stepan1993constitutional}.
+Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citet{pereira2012surprising}.
+
+This paper opens two questions for future analysis.
+First, if the mechanism we suggest is indeed at work, more support for the Executive means better public goods.
+Therefore, one may ask what should be the city council's checking prerogatives, as the they significantly reduce the provision of public services.
+The evidence so far is inconclusive, and \citet{poulsen2018political} show that checks for the mayors may also improve service provision.
+It may be the relationship between rents and public goods is non-linear, making mayors revert to only rents past a certain threshold.
+Moreover, it could be that, at some point, legislative support is ineffective or even harmful to democracies, as it may trigger an intense form of elite capture.
+This question needs further investigation, and our results suggest that mayors with more support improve welfare.
+Second, it remains uncertain how other legislative features affect welfare.
+For example, city councils may vary in size, monetary compensation for councilors, committee structure, and internal power structure.
+These components may interact with each other, and understanding how size plays with other features would improve our knowledge about city councils size affect welfare.
 Both these questions are crucial for institution design and welfare in developing democracies.

### 2021-10-06 article/article.Rmd
update references
some copyediting

@@
 Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood.
-In this paper, we use a formal model to show that increasing legislature size improves the provision of public goods.
+In this paper, we use a formal model to show that increasing legislature size improves public goods provision.
 We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it.
@@
 Increasing the city council size by one legislator lowers infant mortality by 2.01 children per one thousand infants born and reduces postneonatal mortality by 0.90 children per one thousand infants that survived their first 28 days.
-A larger council size also increased enrollment by 2.58 children in elementary education classrooms without significantly diminish elementary school quality.
+A larger council size also increased enrollment by 2.58 children in elementary education classrooms without significantly diminishing elementary school quality.
 These services are crucial for welfare and result from an eased bargaining between the mayor and the city council.
@@
 In mayor-council cities, the power is divided between a mayor that controls the Executive branch and a city council that supports or sanctions the policies proposed by the mayor.
-In this setting, consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor has the prerogative of proposing a vector of policies that is voted by the city councilors.
+In this setting, consider a strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
+The mayor has the prerogative of proposing a vector of policies on which city councilors vote.
 The provision of public goods is then a bargain between the mayor and the city council.
@@
 The winning coalition, the minimum number of members that must be convinced to implement the policy, is equal to half of the selectorate ($N/2$).
-City councilors are motivated by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}.
+City councilors are motivated by policy concerns $p$ and transfers received from the mayor or the councilor nominated as the proposer \textbf{x}.
 We leave the definition of these transfers open, as this allows us to analyze how mayors combine transfers with other incentives to pressure city councilors.
@@
 If her proposal is accepted, it is implemented.
-If councilors reject the offer again, the budget shrinks by $\delta$, and another city councilor is recognized to propose.
+If councilors reject the offer again, the budget shrinks by $\delta$, and another city councilor is nominated to propose.
 The process repeats until a proposal is finally accepted.
@@
 
-In equilibrium, the budget binds, and the first-order condition for an optimal public goods provision makes the marginal benefits to increase rents.
-In this case, it means that the marginal costs of providing the public goods is equal to the marginal benefits of reelection:
+In equilibrium, the budget binds, and the first-order condition for optimal public goods provision indicates that the marginal costs of providing public goods is equal to the marginal benefits of reelection:
 
@@
 \begin{proposition}\label{prop1}
-The provision of public goods increases with legislature size when the bargaining costs decrease with legislature size.
+Public goods provision increases with legislature size when the bargaining costs decrease with legislature size.
 \end{proposition}
@@
 
-Proposition \ref{prop1} provides the first empirical hypothesis to test: \textit{if the bargaining costs decrease when the legislature size increases, then the provision of the public goods increases when the legislature size increase}.
+Proposition \ref{prop1} provides the first empirical hypothesis to test: \textit{if the bargaining costs decrease when the legislature size increases, then public goods provision increases when the legislature size increase}.
 Now we study each reversal mechanism to determine the condition under which the bargaining costs decrease when legislature size increases.
@@
 And if the bargaining costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-Below we show that partisanship is the key to understand how larger legislature sizes can increase public goods provision.
+Below we show that partisanship is the key to understand how this relationship.
 
@@
 
-Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{arvate2013electoral}.
+Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{gottlieb2019countervailing}.
 In a political system with around thirty parties and a sample average of almost ten parties in the municipalities we study, candidates per seat can increase exponentially.
 According to the Brazilian electoral law, each party can sponsor 1.5 times the number of seats as candidates.
-If a party form a pre-electoral coalition, this number increases to two times the number of seats \citep{coneglian2008lei}.
+If a party forms a pre-electoral coalition, this number increases to two times the number of seats \citep{coneglian2008lei}.
 An election in a small town, with ten councilors, may end up with 600 candidates: (30 parties) x (two times the number of seats) x (ten seats).
@@
 The last set of variables quantify social welfare.
-Our focus is on the impact of legislature size on education and healthcare, which are the two most important public services the municipal government should provide to citizens.
+Our focus is on the impact of legislature size on education and health care, which are the two most important public services the municipal government should provide to citizens.
 We measure access to education with the average enrollment in primary (K--4) municipal public schools.
-We assess education quality with the Education Development Index (\ 'Indice de Desenvolvimento da Educa\c{c}\~{a}o B\'asica--IDEB), which the Ministry of Education has issued biannually since 2007.
+We assess education quality with the Education Development Index (Índice de Desenvolvimento da Educação Básica--IDEB), which the Ministry of Education has issued biannually since 2007.
 The index is a weighted average of student scores in Portuguese and Mathematics (0--10), multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
-To test the effect of the 2004 ruling on healthcare, we collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants who survived more than 28 days, but died before reaching one year of age.
+To test the effect of the 2004 ruling on health care, we collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants who survived more than 28 days, but died before reaching one year of age.
 The source of all health care variables is the Brazilian Ministry of Health Data Center (DataSUS).
@@
 The number of seats in 2000 intends to control that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
-The year and the Northeast dummies serve to improve efficiency.
+The year and the Northeast dummies were added to improve efficiency.
 Adding controls improves efficiency in RDD and also enhances the consistency in the multiple thresholds RDD \citep{calonico2019regression}.
@@
 For the last assumption, there should be no changes in pre-treatment covariates.
-These pre-treatment covariates are variables measured before the primary outcomes.
+These pre-treatment covariates are measured before the primary outcomes.
 As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
@@
 Furthermore, in the Supplementary Materials, we run placebo checks for all the models using placebo cutoffs within the real ones.
-The results are available in sections A.6 to A.12.
+The results are available in sections A.6 to A.12 of the Supplementary Materials.
 
@@
 We built two novel datasets to provide evidence for our mechanism.
-First, we ran a survey with former city councilors, asking how the mayor consolidate its coalition support within the city council.
+First, we ran a survey with former city councilors, asking how mayors consolidate their coalition support within the city council.
 Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
@@
 One additional city councilor increased the per capita amount of laws on public goods by 15.0 percent.
-Also, the number of laws that focus on healthcare and education increased by 19.7 percent.
-Looking specifically into healthcare and education legislation, the proportion of laws discussing public goods increased by 15.7 percent, showing that policy proposals by both the mayor and the councilors shift toward local and citywide public goods.\footnote{Public goods here are not restricted to citywide goods.
+Also, the number of laws that focus on health care and education increased by 19.7 percent.
+Looking specifically into health care and education legislation, the proportion of laws discussing public goods increased by 15.7 percent, showing that policy proposals by both the mayor and the councilors shift toward local and citywide public goods.\footnote{Public goods here are not restricted to citywide goods.
 Any service that benefits citizens, regardless of whether they are targeted to citizens or not, is considered public goods.
@@
 With support from the mayor, they can help voters get access to schools, improving the voter's welfare.
-The education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
+Education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
 As expected, the placebo regressions are insignificant.
@@
 
-\citet{Ames2001} argues that the Brazilian democracy is deadlocked because the Executive has its hands tied by a legislature that demand constantly provision of particularistic and private goods.
+\citet{Ames2001} argues that the Brazilian democracy is deadlocked because the Executive has its hands tied by a legislature that demands constantly provision of particularistic and private goods.
 Indeed, the most successful presidents after 1995 had to build multiparty coalitions by negotiating with parties \citep{limongi1998bases, raile2011executive}.
@@
 First, if the mechanism we suggest is indeed at work, more support for the Executive means better public goods.
-Therefore, one may ask what should be the city council's checking prerogatives, as the they significantly reduce the provision of public services.
+Therefore, one may ask what should be the city council's checking prerogatives, as they significantly reduce the provision of public services.
 The evidence so far is inconclusive, and \citet{poulsen2018political} show that checks for the mayors may also improve service provision.

### 2021-10-06 appendix/appendix.Rmd
text edits, article and appendix
remove author information

@@
 author:
-  - Gabriel Cepaluni[^gabriel]
-  - Danilo Freire[^danilo]
-  - Umberto Mignozzetti[^umberto]
-date: \today
 fontfamily: libertine
@@
 
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
-
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
 \appendix
@@
 If rejected, the budget shrinks again by $\delta$ and another city councilor is chosen to propose the policy.
-The process continues until the proposal is finally accepted.
+The process continues until a proposal is finally accepted.
 

### 2021-10-06 article/article.Rmd
remove author information

@@
 author: 
-  - Gabriel Cepaluni[^gabriel]
-  - Danilo Freire[^danilo]
-  - Umberto Mignozzetti[^umberto]
 date: \today
-thanks: "We thank Cedric Antunes, Victor Araujo, Eric Arias, Taylor Boas, Natalia Bueno, Andrea Freitas, Saad Gulzar, James Mahon, Lucas Novaes, Nelson Ruiz, Catarina Roman, David Skarbek, and Denis Stukal for their valuable comments.
-We also thank the participants of seminars and conferences at CEPESP, CUNY, INSPER, IPSA, LACEA, LASA, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.
-We gratefully acknowledge the financial support of the São Paulo Research Foundation (FAPESP), grant number 2017/07290-5.
-All materials required to replicate this study are available at <https://github.com/umbertomig/legislature-size-welfare>."
 abstract: "How does legislature size impact public service provision?
@@
 ```
-
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
-
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
 

### 2021-10-06 letter/letter.Rmd
add cover letter

---
author: 
    - Danilo Freire
opening: Dear Editors,
closing: Sincerely Yours,
address:
    - The Editors
    - American Journal of Political Science
return-address: 
    - Danilo Freire
    - School of Social and Political Sciences
    - University of Lincoln
    - Brayford Pool, Lincoln LN6 7TS
    - United Kingdom
letterhead: 
signature: 
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: onehalf
margin: 2cm
papersize: a4paper
fontsize: 12pt
inline-links: true
signature-before: -4ex
signature-after: 0ex
colorlinks: true
output: 
    pdf_document:
        template: letter-template.latex
---

I am writing to submit our manuscript entitled "Legislature Size and Welfare: Evidence from Brazil" for consideration as an \textit{American Journal of Political Science} research article. We present a game theory model showing that larger city councils increase local public goods provision. Partisanship is the main mechanism we explore in our article. Our evidence comes from exogenous changes in Brazilian electoral legislation, which granted additional legislators to hundreds of municipalities based on population thresholds. Our regression discontinuity models indicate that increasing local legislatures leads to higher primary school enrollment and lower infant mortality rates without any significant decrease in the quality of public service. We also survey former city councilors and analyze the content of 346,553 bills to provide further evidence for our mechanism.

Our findings contribute to large literatures on multilateral bargaining, citizen welfare, and municipal party politics. We believe our paper appeals especially to researchers in Comparative Politics, particularly those studying legislative activity and representative institutions. We incentivise scholars in these areas to investigate the relationship between fragmented parliaments and strong executives more closely, and also to search for other mechanisms that may link legislature features with public service provision.

We also provide extensive supplementary material with data, code, and additional analyses, for consultation on \href{https://github.com/umbertomig/legislature-size-welfare}{this GitHub repository}. The appendix describes our model and data sources in detail, and it also includes a series of additional tests that show the robustness of our results.

Each of the authors confirms that this manuscript has not been previously published and is not currently under consideration by any other journal. All of the authors have approved the contents of this paper and have agreed to the \textit{American Journal of Political Science}'s submission policies.

Should you select our manuscript for peer review, we would like to kindly suggest the following potential reviewers/referees because they would have the requisite background to evaluate our findings and interpretation objectively.

\vspace{.5cm}

\begin{itemize}
    \item John Matsusaka, Charles F. Sexton Chair in American Enterprise, Marshall School of Business, University of Southern California. Professor Matsusaka has written extensively about the ``law of $1/n$'' and is familiar with the literature. Email: \href{mailto:matsusak@usc.edu}{matsusak@usc.edu}.
    \item Neil Malhotra, Edith M. Cornell Professor of Political Economy, Graduate School of Business, Stanford University. Professor Malhotra has written a fundamental article about the ``law of $1/n$''. Email: \href{mailto:neilm@stanford.edu}{neilm@stanford.edu}.
    \item David M. Primo, Ani and Mark Gabrellian Professor, Department of Political Science, University of Rochester. Professor Primo has argued about the existence of a ``reverse law of $1/n$'' and has several papers on the topic. Email: \href{mailto:david.primo@rochester.edu}{david.primo@rochester.edu}.
    \item Mia Costa, Assistant Professor, Department of Government, Dartmouth College. Professor Costa has experience with meta-analysis and research methods. Email: \href{mailto:mia.costa@dartmouth.edu}{mia.costa@dartmouth.edu}.
\end{itemize}

To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise.

Each named author has equally contributed to conducting the underlying research and drafting this manuscript. To the best of our knowledge, the authors have no conflict of interest, financial or otherwise.

Author names, affiliation and contact details:

\begin{itemize}
\item Gabriel Cepaluni: Associate Professor, Department of International Relations, São Paulo State University, \url{gabi.cepal@gmail.com}.
    \item Danilo Freire: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, \url{dfreire@lincoln.ac.uk}. Corresponding author.
    \item Umberto Mignozzetti: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, \url{umberto.mignozzetti@emory.edu}.
\end{itemize}

\vspace{1cm}

### 2021-10-06 article/article.Rmd
edits to text
remove duplicated citation

@@
 As such, the number of representatives in parliament has important consequences for whole polity.
-Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{allenrepresentation, crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, PrimoSnyder2008, Weingastetal1981}.
+Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{allenrepresentation, crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
 However, how legislature size impacts social welfare remain less understood.

### 2021-10-06 article/article.Rmd
remove citation

@@
 As such, the number of representatives in parliament has important consequences for whole polity.
-Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{allenrepresentation, crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
+Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
 However, how legislature size impacts social welfare remain less understood.

### 2021-10-06 letter/letter.Rmd
remove citation
add reviewers to letter

@@
 \begin{itemize}
-    \item John Matsusaka, Charles F.
-Sexton Chair in American Enterprise, Marshall School of Business, University of Southern California.
-Professor Matsusaka has written extensively about the ``law of $1/n$'' and is familiar with the literature.
-Email: \href{mailto:matsusak@usc.edu}{matsusak@usc.edu}.
-    \item Neil Malhotra, Edith M.
-Cornell Professor of Political Economy, Graduate School of Business, Stanford University.
-Professor Malhotra has written a fundamental article about the ``law of $1/n$''.
-Email: \href{mailto:neilm@stanford.edu}{neilm@stanford.edu}.
-    \item David M.
-Primo, Ani and Mark Gabrellian Professor, Department of Political Science, University of Rochester.
-Professor Primo has argued about the existence of a ``reverse law of $1/n$'' and has several papers on the topic.
-Email: \href{mailto:david.primo@rochester.edu}{david.primo@rochester.edu}.
-    \item Mia Costa, Assistant Professor, Department of Government, Dartmouth College.
-Professor Costa has experience with meta-analysis and research methods.
-Email: \href{mailto:mia.costa@dartmouth.edu}{mia.costa@dartmouth.edu}.
+    \item Claudio Ferraz. Professor of Economics at the Vancouver School of Economics, University of British Columbia. Email: \url{claudio.ferraz@ubc.ca}.
+    \item Thomas Fujiwara. Associate Professor of Economics and International Affairs, Princeton University. Email: \url{fujiwara@princeton.edu}
+    \item F. Daniel Hidalgo. Cecil and Ida Green Associate Professor of Political Science, Massachusetts Institute of Technology. Email: \url{dhidalgo@mit.edu}.
+    \item Guillermo Toral. Assistant Professor of Political Science, Vanderbilt University. Email: \url{guillermo.toral@vanderbilt.edu}.
 \end{itemize}
@@
 To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise.
+All of them have written extensively about public service provision and government accountability in Brazil using modern causal inference methods.
 

### 2021-10-06 letter/letter.Rmd
change cover letter

@@
 Partisanship is the main mechanism we explore in our article.
-Our evidence comes from exogenous changes in Brazilian electoral legislation, which granted additional legislators to hundreds of municipalities based on population thresholds.
+Our evidence comes from exogenous changes in Brazil's electoral legislation, which granted additional legislators to hundreds of municipalities based on population thresholds.
 Our regression discontinuity models indicate that increasing local legislatures leads to higher primary school enrollment and lower infant mortality rates without any significant decrease in the quality of public service.
@@
 
-We also provide extensive supplementary material with data, code, and additional analyses, for consultation on \href{https://github.com/umbertomig/legislature-size-welfare}{this GitHub repository}.
-The appendix describes our model and data sources in detail, and it also includes a series of additional tests that show the robustness of our results.
+We also provide extensive supplementary materials to accompany the manuscript.
+They are available for consultation on \href{https://github.com/umbertomig/legislature-size-welfare}{this GitHub repository}.
+The appendix describes our model and data sources in detail, and it also includes a series of additional tests to demonstrate the robustness of our findings.
 

### 2021-10-06 article/article.Rmd
add new reference

@@
 As such, the number of representatives in parliament has important consequences for whole polity.
-Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
+Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{crain1979cost, freire2021legislature, frey2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
 However, how legislature size impacts social welfare remain less understood.

### 2021-10-06 letter/letter.Rmd
add reviewer

@@
     \item Guillermo Toral. Assistant Professor of Political Science, Vanderbilt University. Email: \url{guillermo.toral@vanderbilt.edu}.
+    \item Ryan Hübert. Assistant Professor of Political Science, University of California, Davis. Email: \url{rhubert@ucdavis.edu}.
 \end{itemize}
@@
 To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise.
-All of them have written extensively about public service provision and government accountability in Brazil using modern causal inference methods.
+All of them have written extensively about public service delivery, government accountability, and economic policy analysis using modern causal inference methods.
 

### 2021-10-16 appendix/appendix.Rmd
changes appendix

@@
 
-\newpage
-
-## A Model of Legislature Size and Service Provision
-
-### Model Primitives
-
-Consider an strategic interaction between a mayor $M$ and $N \geq 3$ city councilors indexed as $i \in \{1, 2, \cdots, N \}$.
-The mayor is the head of the local executive branch and submits policy proposals to the city councilors.
-Policy proposals comprise funds allocated to public goods provision ($g$), rents for the mayor ($r$), and transfers to the city councilors (\textbf{x}).
-
-The city council votes the mayor's proposal, which is implemented if they accept it.
-Otherwise, a reversal policy takes place, indicating that the mayor failed to secure the majority of the councilors' votes.
-In this case, the policy proposal either stops or is transferred to the council.
-The different types of reversal policies are crucial for our argument, as they change the bargaining position of the councilors relative to the mayor.
-We investigate three types of reversal policies: 1) a \textit{non-partisan} reversal mechanism, in which city councilors have no partisan affiliation; 2) a \textit{partisan} reversal mechanism, where the council is divided into supporters and non-supporters of the mayor; 3) and finally, a \textit{hybrid} reversal mechanism, which combines partisan and non-partisan features.
-The main paper focuses on the hybrid model, as it is the more realistic scenario.
-However, comparing the partisan and non-partisan reversal mechanisms provides further evidence that the partisan mechanism drives our results.
-
-The mayor needs to secure the support of at least half of the city councilors to implement his or her policy.
-Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate is composed by the $N$ city councilors.
-That is, these are the individuals who have a say in the mayor's policy proposals.
-The winning coalition, which is the minimum number of members required to implement the policy, equals half of the selectorate ($N/2$).
-City councilors are motivated by policy concerns $p$ and transfers received either from the mayor or from a councilor \textbf{x} who proposes the policy.
-We leave the content of these transfers open, as this allows us to analyze how mayors combine transfers with other incentives to pressure city councilors.
-For instance, a mayor may grant councilors electoral favors, spend in areas where they have political or personal interests, offer portfolio or public sector jobs to associates, or even provide campaign contributions and bribes.
-These transfers affect the councilors' decisions and generate governing costs $C_G$.
-Governing costs vary according to the type of reversal mechanism and the size of the legislature.
-
-Finally, after paying the aforementioned governing costs, the mayor proposes some level of public goods provision $g$ and rents $r$.
-Public goods provision helps the mayor to get reelected.
-Rents are for the mayor's direct benefit and do not contribute to his or her electoral success.
-This makes the mayor's expected utility a sum of the gains from rents plus the benefits from reelection.
-Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or more public goods increase his or her utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains the mayor receives from holding the public office.
-We assume these benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
-If the mayor's policy proposal is approved, then the expected utility for the mayor is:
-
-\[
-\mathbb{E}U(r, g) \ = \ u(r) + B_M\pi(g)
-\]
-
-The mayor's policy choices are subject to municipal budget constraints.
-The municipality has $R > 0$ resources and cannot run deficits, that is, it must always balance its budget.
-We also assume that there are enough resources for the mayor to govern.
-
-Let $C_G$ be the mayor's governing costs. The budget balance constraints implies that mayors will only offer public services and rents that satisfy following inequality:
-
-\[
-r + g + C_G \ \leq \ R
-\]
-
-The expected utility for the city councilors depends on which reversal policy takes place.
-As mentioned above, we explore the implications of three different mechanisms.
-First, in the \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor $\delta \in (0,1)$ and the random selection of one councilor.
-The randomly selected councilor becomes the new proposer.
-If her proposal is accepted, it is implemented.
-If rejected, the budget shrinks again by $\delta$ and another city councilor is chosen to propose the policy.
-The process continues until a proposal is finally accepted.
-
-In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation.
-Party affiliations are mutually exclusive, that is, one councilor cannot belong to two parties at once.
-If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
-Otherwise, the city councilor belongs to the opposition $O = \{1, 2, \cdots, N \} \setminus G$.
-The mayor-sponsored policy generates a political value of $p > 0$ for the councilors, and whether this adds or reduces the councilor's utility depends on his or her party affiliation.
-If the mayor's proposal is rejected, a city councilor aligned with the mayor receives zero instead of $p$.
-In contrast, a city councilor from the opposition receives zero if the proposal is rejected and $-p$ if is is enacted.
-Although these assumptions are rather strong, they capture the underlying political dynamics of political partisanship, in which councilors and mayors in the same coalition share similar policy preferences.
-Voting against the mayor's proposals defies the partisan logic.
-
-Lastly, in the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining costs.
-Here councilors receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan mechanism takes place.
-In the mayor's proposal stage, city councilors in the mayor's coalition receive a benefit of $p > 0$ when the mayor's policy is implemented.
-Opposition members receive $-p$ if the mayor's proposal is implemented.
-In case the mayor's proposal is rejected, as the city council does not control the executive when the two branches are separated, there is no provision of public goods ($p=0$).
-Moreover, in equilibrium, we assume that city councilors prefer to receive transfers instead of providing public goods.
-This is in line with the empirical evidence from most developing economies [e.g., @FerrazFinan2011; @Nichter2010].
-
-The timeline of the game is as follows:
-
-\begin{enumerate}
-  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators have been elected.
-  \item The mayor proposes a policy vector $(r, g, x)_M$.
-  \item The city council votes the proposal.
-  \begin{itemize}
-    \item If the council accepts the proposal, it is implemented and the game ends.
-    \item Otherwise, a reversal policy is implemented.
-  \end{itemize}
-  \item (Reversal Policy) We propose three reversal policies, namely \textit{partisan}, \textit{non-partisan}, and \textit{hybrid}.
-We have introduced them above and will discuss them in further detail in the following sections.
-\end{enumerate}
-
-The solution concept we use in this model is the subgame perfect Nash equilibrium.
-This game requires that the strategies follow a Nash equilibrium in each subgame.
-We find the solution by backward induction.
-In the model with infinitely repeated proposals, we extend the equilibrium concept and require that the equilibrium is stationary.
-This implies that if the politician accepts an offer at time $k+1$, they should take the same offer at time $k$.
-This assumption holds at each point of the game.
-Stationarity provides a method to find a proposal that the politician accepts at any stage in the game.
-In our case, the optimal offer for the mayor is at $k=0$, which indicates an immediate policy implementation.
-
-\begin{definition}
-The game equilibrium consists of a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that the mayor and the councilors have no profitable deviations from the equilibrium at any stage of the game.
-\end{definition}
-
-Moreover, we assume that players have no dominated strategies, even if the policy is not implemented due to insufficient support.
-
-### The Mayor's Decision Stage
-
-Solving the game by backward induction requires us to know which strategies councilors may adopt.
-However, assume for now that we have solved the game for the councilors and found the equilibrium cost of governing $C_G(N)$ when there are $N$ city councilors.
-In the next section, we define $C_G(N)$ for each mechanism using backward induction and show that the definitions are well-behaved.
-Here we start from this assumption just to simplify our exposition.
-
-We derive the optimal rents ($r$) and public goods provision ($g$) a mayor should propose.
-Mayors benefit from public goods provision, as it increases their chances of reelection.
-However, they would rather provide the lowest necessary amount of public goods and extract the remaining resources as political rents.
-As we noted previously, their objective is to maximize their expected utility, subject to the municipal budget constraint.
-
-\[
-\begin{aligned}
-\max_{r, g} \quad & u(r) + B_M\pi(g)\\
-\textrm{s.t.} \quad & r + g + C_G(N) \leq R
-\end{aligned}
-\]
-
-In equilibrium, the budget binds, and the provision of the public goods maximizes to:
-
-\[
-\max_{g} \{ u(R - g - C_G(N)) + B_M\pi(g) \}
-\]
-
-The first-order condition for an optimal public goods provision makes the marginal benefits of increasing rents---in this case, the marginal costs of providing the public goods---equal to the marginal benefits of reelection:
-
-\[
-u'(R - g - C_G(N)) = B_M\pi'(g)
-\]
-
-This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_G(N)) + B_M\pi''(g^*) < 0$.
+\pagebreak
+
+## A Model of Legisture Size and Service Provision (Proofs)
 
@@
 
-This provides the first empirical hypothesis we test in our article: \textit{public goods provision increases along with legislature size, but only if governing costs decrease when legislature size increases}.
-
-At this stage, we need to solve for the existence of these governing costs.
-In the following sections we show that while this proposition is valid for the *partisan* and *hybrid* mechanisms, it is not applicable to the *non-partisan* mechanism.
-
-### Non-Partisan Reversal Mechanism
-
-In the \textit{non-partisan reversal} mechanism, we assume that if the council rejects the mayor's proposal, a reversal policy starts with the random selection of one councilor.
-To find the stationary subgame perfect Nash equilibrium, suppose that there were $k-1$ rejections and the game is at the $k$-th stage.
-A councilor accepts the proposer's offer if, and only if, getting the offer at $k$ is better than waiting until the next stage $k+1$.
-If the offer is $x_i$, then:
-
-\[
-x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left[\dfrac{1}{2} x_i \right]
-\]
-
-We place the offer on the left-hand side.
-There are two components on the right-hand side.
-The first is the amount that councilor $i$ receives when he/she is the proposer.
-The amount is equal to the chance that they are recognized as the proposer, times the budget in the next round, minus the offers they have to make to convince half of the councilors.
-The second part denotes the gains obtained by the councilor if he/she rejects the current offer but still receives an offer in the following round.
-This is equal to the chance that they are not recognized as the proposer, times the chance that they receive a transfer, times the transfer amount.
-Note that the councilor's offer as the proposer is the same as the offer they want to receive, as city councilors are exchangeable.
-The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution).
-After some calculations, the offer $x_i$ has to be greater than or equal to:
-
-\[
-x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k, N)
-\]
-
-The proposer always offers the minimum required to get the proposal approved. In this case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.
-
-Proceeding backwards, at the mayor's proposal stage $k=0$, the mayor offers $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
-In this context, the governing costs for the mayor are:
-
-\[
-C_G(N) \ = \ \dfrac{N}{2}\left[\dfrac{2 \delta R }{2N + 1}\right] \ = \ \dfrac{\delta R N}{2N + 1}
-\]
-
 \begin{proposition}
@@
 
-This result is crucial for us to explain the role of politics in our model.
-If governing costs increase with legislature size, then any increase in public goods provision associated with legislature size comes from a different mechanism.
-In this case, we show that there is a \textit{political} reason to increase the provision of public goods.
-
-### Partisan Reversal Mechanism
-
-We now focus on the other extreme, which is a fully politicized legislature.
-In this case, when the mayor implements the policy, it generates a value of $p > 0$.
-A legislator aligned with the mayor receives a benefit $p$ while an opposition legislator receives a cost of $-p$.
-Moreover, as in the non-partisan reversal, the mayor may choose to distribute $x_i$ private goods for a legislator $i$.
-In this case, when the policy is implemented, the aligned legislator's utility equals $x_i + p$.
-When the legislator is not aligned with the mayor, their utility equals $x_i - p$.
-If the policy is not implemented, then we assume a reversal policy of zero in all choice vectors $g = x_i = p = 0$.
-
-A legislator aligned with the mayor always supports the mayor's policy, regardless of receiving private goods.
-This is because $p > 0$, that is, the councilor always receives positive benefits from the policy.\footnote{The mayor could even impose costs to aligned city councilors.
-Although this seems unrealistic, it is mostly the case when government-aligned legislators are called to draft legislation for the mayor's office or to take the fallout from a failed policy.} However, politicians who not aligned with the mayor require compensation when their votes are needed.
-In this case, if the mayor's proposal requires the support of an opposition politician, then the mayor compensates the councilor for the policy costs.
-In such case:
-
-\[
-x_i \geq p
-\]
-
-Optimality dictates that the mayor offers $x_i = p$ to the opposition legislator.
-Let $\gamma$ be the ex-ante probability of electing a politician aligned with the mayor.
-Then, the governing costs when the legislature size is $N$ equals the expected number of opposition members the mayor has to compensate, minus the amount needed to implement the policy.
-In this case, it is half of the city council:
-
-\[
-C_G(N) \ = \ p\left(\dfrac{N}{2} - \gamma N\right)
-\]
-
-\begin{proposition}
-In the \textit{partisan reversal} mechanism, if the chances of electing a mayor-aligned politician are greater than $1/2$, then governing costs decrease as legislature size increases.
-\end{proposition}
-
-\begin{proof}
-
-When we compare the difference in costs between $N$ and $N+1$ legislators, we find that:
-
-\[
-\begin{aligned}
-C_G(N+1) - C_G(N) \ = \ & p\left(\dfrac{N+1}{2} - \gamma (N+1)\right) - p\left(\dfrac{N}{2} - \gamma N\right) \\
- = \ & p\left( \dfrac{1}{2} - \gamma \right)
-\end{aligned}
-\]
-
-Therefore, when $\gamma < \dfrac{1}{2}$, governing costs increase. Otherwise, such costs decrease.
-
-\end{proof}
-
-\begin{corollary}
-In the \textit{partisan reversal} mechanism, if the chances of electing a mayor-aligned politician is greater than $1/2$, then public goods provision increase as legislature size increases.
-\end{corollary}
-
-This result shows that, when the likelihood of electing an aligned politician is sufficiently high, governing costs tend to decrease.
-Consequently, the provision of public goods tends increases, as well as the rents.
-The marginal change in the utility from rents and the utility from reelection determines the allocation between these two vectors.
-In any case, the amount distributed to both increases.
-
-### Hybrid Partisan and Non-partisan Reversal Mechanism
-
-The \textit{hybrid reversal} mechanism combines both partisan and non-partisan motivations. Here, a city councilor aligned with the government favors the mayor's offer if:
-
-\[
-x_i \geq \dfrac{2\delta R}{2N+1} - p
-\]
-
-An opposition politician, in contrast, favors the mayor's offer if, and only if:
-
-\[
-x_i \geq \dfrac{2\delta R}{2N+1} + p
-\]
-
-We divide these costs into two components.
-First, the costs in terms of rents.
-Second, the costs (or benefits) from political alignment.
-In this context, governing costs depend on what the mayor offers to their supporters in the council versus what they provide to members of the opposition.
-The ex-ante chance of an opposition member being elected is equal to $1-\gamma$, therefore, after taking the weighted averages, these costs become:
-
-\[
-C_G(N) \ = \ \dfrac{N}{2}\left( \dfrac{2\delta R}{2N+1} - p \right) + \left(\dfrac{N}{2} - \gamma N \right)p
-\]
-
 \begin{proposition}
@@
 
-The threshold $\underline{\gamma}$ for the probability of electing an aligned politician decreases according to the value of the mayor's policy $p$ and the legislature size $N$.
-Higher political values and larger legislatures make it easier to satisfy the electoral threshold.
-
-### Main Hypotheses
-
-Our model provides two empirically testable hypotheses. Consider a city council comprised of $N$ legislators that increase its size to $N+1$. Then:
-
-\begin{enumerate}
-  \item[H1. ] Governing costs decrease with legislature size when the chances of electing a government-aligned legislator are sufficiently high.
-  \item[H2. ] Public goods provision increases if governing costs decrease with legislature size.
-\end{enumerate}
-
-In the main paper, we show that larger legislatures improve the provision of public education and health care in Brazil.
-What drives this result is the 91% chance of electing a mayor-aligned city councilor to the local chamber.
-
-\newpage
+\pagebreak
 
@@
 \label{appsources}
-
-We use three data sources in our work, mainly from Brazilian governmental agencies. Table \ref{tab:varsources} presents the variables we use here and their respective URLs.
 
@@
 \end{itemize}
-
-This Appendix contains other questions we asked in the survey.
-We collected them to improve our knowledge about the perceptions city councilors have about the roles the municipality and themselves play in the government.
-We omitted these questions in the main paper because they are not of general interest to our argument.
-The descriptive statistics of the variables used in the main article follow in Table \ref{tab:descrvarspaper}.
 
@@
 
-\newpage
-
 ## Threshold Manipulation, Sorting, and Pre-Treatment Consistency
 
-The validity of our causal claim relies on three assumptions:
-
-\begin{enumerate}
-  \item Municipalities cannot place themselves on the left- or the right-hand side of the cutoffs.
-  \item Regression models correctly compare cities in the adjacent cutoffs.
-  \item There are no pre-treatment differences in the sample.
-\end{enumerate}
-
-Regarding the first assumption, \citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant on either side of the cutoff.
+\citet{McCrary2008} proposes a measure of the distributional imbalance around the discontinuity, testing whether cases are more abundant on either side of the cutoff.
 In our sample, the McCrary statistic is 0.391 (SE $=$ 0.299), showing no evidence of manipulation.
@@
 
-Lastly, we graph the \citet{McCrary2008} test, pooling all the discontinuities together. The results follow in Figure \ref{manipulationplot} and show no signs of manipulation.
-
-\begin{figure}[htb!]
-  \begin{center}
-  \begin{minipage}{1 \linewidth}
-  \centerline{\includegraphics[width=5in,angle=0]{../figures/McCrary.pdf}}
-  \caption{\citet{McCrary2008} manipulation test}
-  \bigskip
-  \label{manipulationplot}
-  \end{minipage}
-  \end{center}
-\end{figure}
-
 ## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
@@
 
-The identification strategy requires exogenous changes in the city council size thresholds.
-Prior to the changes we exploit here, the 1988 Brazilian Constitution stated the following distribution of seats per population size, presented in Table \ref{tab:citycouncilsize1988}.
-
-\begin{table}[htp!]
-\centering
-\caption{City council size from the 1988 Constitution}
-\label{tab:citycouncilsize1988}
-\scalebox{1}{
-\begin{tabular}{rccrrr}
-  \hline\hline
- & \multicolumn{1}{c}{Min. Leg.} & \multicolumn{1}{c}{Max. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
- & & & & & \multicolumn{1}{c}{(2001-2004)} \\
-  \hline
-  1 & 9  & 21 & 0 & 1,000,000 &  5,537 \\
-  2 & 33 & 41 & 1,000,001 & 5,000,000 & 11 \\
-  3 & 42 & 55 & 5,000,001 & $\infty$ & 2 \\
-   \hline\hline
-\end{tabular}
-}
-\end{table}
-
-These cutoffs were in place until 2003, when the municipality of Mira Estrela decided to decrease its own council size from eleven to nine councilors.
-The two losing councilors contested the measure and took the proposal to the Supreme Federal Court (STF).
-The Justices ruled that council sizes should vary according to the city population, from a minimum of nine legislators to a maximum of 55.
-Following this decision, the Supreme Electoral Court (TSE) set the thresholds for the 2004 election (Resolution 21,702/2004).
-According to their decision, the legislature should increase as displayed in Table \ref{tab:citycouncilsize2004all}.
-
-\begin{table}[htp!]
-\centering
-\caption{City council size thresholds according to TSE resolution 21,702/2004}
-\scalebox{1}{
-\begin{tabular}{rcrrr}
-  \hline\hline
- &  \multicolumn{1}{c}{Num. Leg.} & \multicolumn{1}{c}{Min. Pop.} & \multicolumn{1}{c}{Max. Pop.} & \multicolumn{1}{c}{Num. Mun. Bin} \\
- & & & & \multicolumn{1}{c}{(2003 pop. proj.)} \\
-  \hline
-  1 &  9 & 0 & 47,619 & 5,029 \\
-  2 &  10 & 47,620 & 95,238 & 317 \\
-  3 &  11 & 95,239 & 142,857 & 89 \\
-  4 &  12 & 142,858 & 190,476 & 43 \\
-  5 &  13 & 190,477 & 238,095 & 30 \\
-  6 &  14 & 238,096 & 285,714 & 21 \\
-  7 &  15 & 285,715 & 333,333 & 13 \\
-  8 &  16 & 333,334 & 380,952 & 13 \\
-  9 &  17 & 380,953 & 428,571 & 6 \\
-  10  & 18 & 428,572 & 476,190 & 6 \\
-  11  & 19 & 476,191 & 523,809 & 4 \\
-  12  & 20 & 523,810 & 571,428 & 5 \\
-  13  & 21 & 571,429 & 1,000,000 & 13 \\
-  14  & 33 & 1,000,001 & 1,121,952 & 1 \\
-  15  & 34 & 1,121,953 & 1,243,903 & 2 \\
-  16  & 35 & 1,243,904 & 1,365,854 & 1 \\
-  17  & 36 & 1,365,855 & 1,487,805 & 2 \\
-  18  & 37 & 1,487,806 & 1,609,756 & 1 \\
-  19  & 38 & 1,609,757 & 1,731,707 & 1 \\
-  20  & 39 & 1,731,708 & 1,853,658 & 0 \\
-  21  & 40 & 1,853,659 & 1,975,609 & 0 \\
-  22  & 41 & 1,975,610 & 4,999,999 & 4 \\
-  23  & 42 & 5,000,000 & 5,119,047 & 0 \\
-  24  & 43 & 5,119,048 & 5,238,094 & 0 \\
-  25  & 44 & 5,238,095 & 5,357,141 & 0 \\
-  26  & 45 & 5,357,142 & 5,476,188 & 0 \\
-  27  & 46 & 5,476,189 & 5,595,235 & 0 \\
-  28  & 47 & 5,595,236 & 5,714,282 & 0 \\
-  29  & 48 & 5,714,283 & 5,833,329 & 0 \\
-  30  & 49 & 5,833,330 & 5,952,376 & 0 \\
-  31  & 50 & 5,952,377 & 6,071,423 & 1 \\
-  32  & 51 & 6,071,424 & 6,190,470 & 0 \\
-  33  & 52 & 6,190,471 & 6,309,517 & 0 \\
-  34  & 53 & 6,309,518 & 6,428,564 & 0 \\
-  35  & 54 & 6,428,565 & 6,547,611 & 1 \\
-  36  & 55 & 6,547,612 & $\infty$  & 0 \\
-   \hline\hline
-\end{tabular}
-}
-\label{tab:citycouncilsize2004all}
-\end{table}
-
-As Brazil has only a few municipalities with more than one million inhabitants, we focus on cities with less than $571,429 + 47,619 = 619,048$ inhabitants.
 Table \ref{tab:citycouncilsize2004short} displays the number of municipalities by the thresholds we use in this paper.
@@
 
-The Supreme Court stated that local electoral courts should use the 2003 population projection to assign municipalities to cutoffs.
-In Brazil, the Brazilian Institute of Geography and Statistics (IBGE) makes the official population projections.
-We have strong reason to believe that sorting is not a threat to our identification strategy, as IBGE is notably insulated from local politics (see also the McCrary test above).
-
 To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity to the cutoffs.
@@
 
-\newpage
-
 ## Identification Strategy in Regression Discontinuity Designs with Multiple Thresholds
@@
 Nevertheless, this may be problematic in our case as municipal characteristics may vary between cutoffs.
-For instance, population imbalance is a known source of heterogeneity, as shown by \citet{Cattaneo2016}.
-To ensure that cases are comparable, we estimate the average LATE for all cutoffs.
-We add a set of controls $Z_i$ to reduce heterogeneity.
+For instance, population imbalance is a known source of heterogeneity.
+To ensure that cases are comparable, we add a set of controls $Z_i$ to reduce heterogeneity.
 For instance, the population that determines the change from one threshold to another also determines all the cutoffs.
@@
 We control for population, GDP, whether the state is located in the Northeast region, seats before the 2003 decision, and year.
-All control variables are smooth around each cutoff but are significantly different across cutoffs, making them adequate controls for our purposes \citep{calonico2019regression}.
 We use a triangular kernel in our estimations, which gives more weigh to municipalities closer to each cutoff.
@@
 
-However, as it is uncommon for regression discontinuity designs to include control variables, some readers may ask why we have added these covariates in the first place.
-To answer this question, we run a series of simulations to show that controlling for the variable that determines the assignment helps improve both the consistency and the efficiency of the estimates.
+As it is uncommon for regression discontinuity designs to include control variables, we run a series of simulations to show that controlling for the variable that determines the assignment helps improve both the consistency and the efficiency of the estimates.
 
@@
     \begin{minipage}{0.9\linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/simdistrRDD.pdf}}
+      \centerline{\includegraphics[height=3in,angle=0]{../figures/simdistrRDD.pdf}}
       \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
@@
     \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
+      \centerline{\includegraphics[width=4in,angle=0]{../figures/estimsRDD.pdf}}
       \caption{Estimations for the Different Data Generating Processes}
@@
 \end{figure}
+
+\pagebreak
 
@@
 
-In Figure \ref{placgraphbw}, we run the same bandwidth analysis for the placebo outcomes. The results, as expected, are mostly statistically insignificant.
-
-\begin{figure}[H]
-  \begin{center}
-    \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[width=5in,height=4in,angle=0]{../figures/placBwSens.pdf}}
-      \caption{Bandwidth Sensitivity -- Placebo Regressions}
-      \bigskip
-      \label{placgraphbw}
-    \end{minipage}
-  \end{center}
-\end{figure}
-
-\newpage
+\pagebreak
 
@@
 We run the analysis dropping one state at a time to investigate this statewide heterogeneity.
-The results are in Figures \ref{graphsensstatedrop1}, \ref{graphsensstatedrop2}, \ref{placgraphsensstatedrop1}, and \ref{placgraphsensstatedrop2}.
-
-First, note that for infant mortality and education enrollment, all coefficients remain significant even after removing some states from our sample.
-For postneonatal mortality, the coefficient loses significance when we remove the states of Bahia, Pernambuco, Rio Grande do Norte, and Rio Grande do Sul.
-The mayoral coalition size remains significant in most models, losing significance when we remove Rio Grande do Norte and São Paulo.
-The number of appointed employees loses significance after removing Espirito Santo and São Paulo.
-All the alternative mechanism models are insignificant, regardless of the state removed.
+The results are in Figures \ref{graphsensstatedrop1} and \ref{graphsensstatedrop2}.
 
@@
 
-\begin{figure}[H]
-  \begin{center}
-      \centerline{\includegraphics[width=0.9\linewidth,angle=0]{../figures/placDropStateSens1.pdf}}
-      \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Welfare Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop1}
-  \end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-  \begin{center}
-      \centerline{\includegraphics[width=0.9\linewidth,angle=0]{../figures/placDropStateSens2.pdf}}
-      \caption{Sensitivity Analysis of State Characteristics with Placebo Cutoffs -- Mechanism Outcomes}
-      \bigskip
-      \label{placgraphsensstatedrop2}
-  \end{center}
-\end{figure}
-
-\newpage
-
 ## Sensitivity Analysis of Model Functional Form
@@
 In the paper, we run all the regressions using local linear polynomials.
-\citet{GelmanImbens2014} show that local linear and quadratic polynomials are better than cubic and quartic models in terms of consistency.
-
 However, to assess the robustness of our results, we also run every model using different polynomials, from local linear to a quartic, to show that our results are robust to different regression functional forms.
 The results are similar in all models, with significance changing only in the quartic polynomials.
-Figures \ref{graphsensff} and \ref{placgraphsensff} present the results for the real and the placebo cutoffs.
+Figure \ref{graphsensff} presents the results.
 
@@
 
-\pagebreak
-
-\begin{figure}[H]
-  \begin{center}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/placFfSens.pdf}}
-      \caption{Sensitivity Analysis of Model Functional Form -- Placebo Cutoffs}
-      \bigskip
-      \label{placgraphsensff}
-  \end{center}
-\end{figure}
-
-\newpage
-
 ## Sensitivity Analysis of Covariates
@@
 Control variables play a major role in our model.
-As we have argued above, our estimates may be inconsistent without the addition of control variables, as we may be capturing differences \textit{between} cutoffs, instead of \textit{within} cutoffs.
-
-However, if the selection of control variables makes the models biased towards our main arguments, this would pose a significant credibility threat to our results.
 To study the sensitivity to controls, we run the same regressions for all possible control combinations.
@@
 Regarding the point estimates, our variable choices tend to keep the models which have smaller coefficient sizes.
-
-We also plot sensitivity tests to covariates in the placebo regressions.
-They are displayed in Figures \ref{placsenscov1} and \ref{placsenscov2}.
-The theoretical expectations here are that most of these outcomes would fail, and the graphs indeed confirm our expectations.
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens1Cov.pdf}}
-\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
-\bigskip
-\label{placsenscov1}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens2Cov.pdf}}
-\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
-\bigskip
-\label{placsenscov2}
-\end{center}
-\end{figure}
-
-\newpage
 
@@
 Moreover, there are no clear increasing or decreasing patterns, which would indicate the existence of differential returns.
-Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs, while Figures \ref{placsenscut1} and \ref{placsenscut2} present the same results for the placebo cutoffs.
+Figures \ref{senscut1} and \ref{senscut2} display the results for the main cutoffs.
 
@@
 \begin{center}
-\centerline{\includegraphics[width=6in,height=6.5in,angle=0]{../figures/rdAddCuts1.pdf}}
+\centerline{\includegraphics[width=6in,height=5in,angle=0]{../figures/rdAddCuts1.pdf}}
 \caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
@@
 \end{figure}
-
-\pagebreak
 
@@
 \end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\begin{minipage}{0.8 \linewidth}
-\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts1.pdf}}
-\caption{Sensitivity to Additional Cutoffs -- Placebo Welfare Outcomes}
-\bigskip
-\label{placsenscut1}
-\end{minipage}
-\end{center}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[htb!]
-\begin{center}
-\begin{minipage}{0.8 \linewidth}
-\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts2.pdf}}
-\caption{Sensitivity to Additional Cutoffs -- Placebo Mechanism Outcomes}
-\bigskip
-\label{placsenscut2}
-\end{minipage}
-\end{center}
-\end{figure}
-
-\newpage
 
@@
 We select four characteristics of the city mayors: gender, level of schooling, whether the mayor was reelected in 2004, and whether the mayor was reelected in 2008.
-The results show no variation in council size and mayoral characteristics.
+The results in Table \ref{appmaychar} show no variation in council size and mayoral characteristics.
 
@@
 
-\begin{table}[!htbp] \centering
-\caption{Mayor Characteristics -- Placebo}
-\label{placappmaychar}
-\resizebox{\textwidth}{!}{
-  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
-  \\[-1.8ex]\hline \\[-1.8ex]
-  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w.
-College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
-  \hline \\[-1.8ex]
-  LATE & 0.03 & 0.04 & 0.08 & -0.07 \\
-  & (0.05) & (0.08) & (0.07) & (0.08) \\
-  N Left & 4526 & 4526 & 4621 & 4620 \\
-  N Right & 878 & 878 & 906 & 906 \\
-  Eff N Left & 567 & 707 & 683 & 759 \\
-  Eff N Right & 342 & 406 & 397 & 427 \\
-  BW Loc Poly & 6.197 & 7.413 & 7.006 & 7.71 \\
-  BW Bias & 10.241 & 12.64 & 13.536 & 12.648 \\
-  \hline \\[-1.8ex]
-  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
-  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
-  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
-  \end{tabular} }
-\end{table}
-
 \subsubsection{Revenues and Transfers}
 
-We run another series of models on federal transfers and revenue raised within the municipalities.
+In Table \ref{apptrev}, we run another series of models on federal transfers and revenue raised within the municipalities.
 There is only a negligible effect on education transfers, yet it is barely significant at 10%.
 The other indicators remain insignificant.
-Note that the placebo is significant, which reinforces the claim that the education effect may be spurious.
+
+\pagebreak
 
@@
 
-\begin{table}[!htbp] \centering
-\caption{Transfers and Revenue -- Placebo}
-\label{plactrev}
-\resizebox{\textwidth}{!}{
-  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
-  \\[-1.8ex]\hline \\[-1.8ex]
-  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\
-  \hline \\[-1.8ex]
-  LATE & 0.07$^{**}$ & 0.04 & 0.03 & 0.07$^{**}$ \\
-  & (0.03) & (0.03) & (0.06) & (0.03) \\
-  N Left & 13865 & 13865 & 13776 & 13103 \\
-  N Right & 2719 & 2719 & 2712 & 2563 \\
-  Eff N Left & 807 & 636 & 1928 & 848 \\
-  Eff N Right & 619 & 544 & 1163 & 611 \\
-  BW Loc Poly & 3.418 & 3.028 & 6.738 & 3.67 \\
-  BW Bias & 6.021 & 5.36 & 10.871 & 6.222 \\
-  \hline \\[-1.8ex]
-  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
-  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
-  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\
-  \end{tabular} }
-\end{table}
-
-\newpage
-
 \subsection{Legislation Dataset}
@@
 
-\newpage
-
 \subsection{City Councilors Survey\label{appsurv}}
@@
 
-\begin{figure}[htb!]
+\begin{figure}[H]
   \begin{center}
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrRespSurvey.pdf}}
+      \centerline{\includegraphics[width=4in,angle=0]{../figures/distrRespSurvey.pdf}}
       \caption{Geographical Distribution of Survey Responses}
@@
 
-Note that the algorithm performs very well, with minimal differences occurring only after the third decimal place.
-
 The survey included the following questions of interest:
@@
 
-\begin{figure}[htb!]
+\begin{figure}[H]
   \begin{center}

### 2021-10-16 appendix/appendix.Rmd
fix figure size

@@
 ## A Model of Legisture Size and Service Provision (Proofs)
+
+In this section, we show the proofs for the model included in the main paper.
 
@@
 \label{appsources}
+
+Our data come mainly from Brazilian public agencies. Further information about them are available below.
 
@@
     \begin{minipage}{0.9\linewidth}
-      \centerline{\includegraphics[height=3in,angle=0]{../figures/simdistrRDD.pdf}}
-      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
+      \centerline{\includegraphics[height=3.45in,angle=0]{../figures/simdistrRDD.pdf}}
+      \caption{Simulation: RD with Multiple Thresholds -- Data Distribution}
       \bigskip
@@
     \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=4in,angle=0]{../figures/estimsRDD.pdf}}
+      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
       \caption{Estimations for the Different Data Generating Processes}
@@
 
-## Placebo Regressions for Political Mechanism
+## Placebo Regressions for the Political Mechanism
 \label{placmechmain}
@@
     \begin{minipage}{1\linewidth}
-      \centerline{\includegraphics[width=5in,height=4in,angle=0]{../figures/bwSens.pdf}}
+      \centerline{\includegraphics[width=7in,height=7.5in,angle=0]{../figures/bwSens.pdf}}
       \caption{Bandwidth Sensitivity -- Main Models}
@@
     \begin{minipage}{\linewidth}
-      \centerline{\includegraphics[height=5.9in,width=0.9\linewidth,angle=0]{../figures/dropStateSens1.pdf}}
+      \centerline{\includegraphics[height=8in,width=0.9\linewidth,angle=0]{../figures/dropStateSens1.pdf}}
       \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
@@
 \begin{center}
-\centerline{\includegraphics[width=6in,height=5in,angle=0]{../figures/rdAddCuts1.pdf}}
+\centerline{\includegraphics[width=6.5in,height=5.5in,angle=0]{../figures/rdAddCuts1.pdf}}
 \caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
@@
 
-\subsubsection{Mayors' characteristics}
+### Mayors' Characteristics
 
@@
   \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
   \end{tabular} }
@@
 
-\subsubsection{Revenues and Transfers}
+### Revenues and Transfers
 
@@
   \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
-  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\
+  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
   \end{tabular} }
@@
 
-\subsection{Legislation Dataset}
+## Legislation Dataset
 
-In the Fall of 2018, we collected data on the legislation approved by the city councils of 63 municipalities, all of which were 10 thousand inhabitants away from the thresholds we discussed above.
+In Fall 2018, we collected data on the legislation approved by the city councils of 63 municipalities, all of which were 10 thousand inhabitants away from the thresholds we discussed above.
 There are 202 municipalities 10 thousand inhabitants away from the cutoff, but only 63 had relevant information about local legislation between 2005 to 2008.
@@
 
-\subsection{City Councilors Survey\label{appsurv}}
+## City Councilors Survey
+\label{appsurv}
 
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=4in,angle=0]{../figures/distrRespSurvey.pdf}}
+      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/distrRespSurvey.pdf}}
       \caption{Geographical Distribution of Survey Responses}
@@
 \textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
-\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
-\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
-\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
-\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
-\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
+\textbf{Region = Central-West} & 0.11         & 0.08       & 0.08           \\
+\textbf{Region = Northeast}     & 0.33         & 0.32       & 0.32           \\
+\textbf{Region = North}        & 0.05         & 0.08       & 0.08           \\
+\textbf{Region = Southeast}      & 0.30         & 0.30       & 0.30           \\
+\textbf{Region = South}          & 0.20         & 0.21       & 0.21           \\ \hline
 \end{tabular}

### 2021-10-16 appendix/appendix.Rmd
remove boldface table a8

@@
 \hline
-\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
-\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
-\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
-\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
-\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
-\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
-\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
-\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
-\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
-\textbf{Region = Central-West} & 0.11         & 0.08       & 0.08           \\
-\textbf{Region = Northeast}     & 0.33         & 0.32       & 0.32           \\
-\textbf{Region = North}        & 0.05         & 0.08       & 0.08           \\
-\textbf{Region = Southeast}      & 0.30         & 0.30       & 0.30           \\
-\textbf{Region = South}          & 0.20         & 0.21       & 0.21           \\ \hline
+Age lower than 39         & 0.50         & 0.34       & 0.34           \\
+Female            & 0.18         & 0.12       & 0.12           \\
+Number of Seats = 9            & 0.83         & 0.90       & 0.90           \\
+Number of Seats = 10           & 0.10         & 0.06       & 0.06           \\
+Number of Seats = 11           & 0.01         & 0.02       & 0.01           \\
+Number of Seats = 12           & 0.01         & 0.01       & 0.01           \\
+Number of Seats = 13           & 0.006        & 0.005      & 0.005          \\
+Number of Seats = 14           & 0.01         & 0.004      & 0.005          \\
+Number of Seats = 15 or more          & 0.02         & 0.009      & 0.008          \\
+Region = Central-West & 0.11         & 0.08       & 0.08           \\
+Region = Northeast     & 0.33         & 0.32       & 0.32           \\
+Region = North        & 0.05         & 0.08       & 0.08           \\
+Region = Southeast      & 0.30         & 0.30       & 0.30           \\
+Region = South          & 0.20         & 0.21       & 0.21           \\ \hline
 \end{tabular}

### 2021-10-16 article/article.Rmd
edit citation article

--- 2021-10-06 article/article.Rmd
@@
 This runs in contrast with well-established theories that point out that multipartism may be a peril to democratic regimes \citep{mainwaring1993presidentialism, stepan1993constitutional}.
-Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citet{pereira2012surprising}.
+Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}.
 

### 2021-11-04 article/article.Rmd
adding para theory and para intro

@@
 Regardless of eventual differences in electoral rules, social composition, and internal procedures, all legislatures share one feature: they are collective bodies.
-As such, the number of representatives in parliament has important consequences for whole polity.
+As such, the number of representatives has important consequences for the whole polity.
 Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
-However, how legislature size impacts social welfare remain less understood.
+However, how legislature size impacts social welfare remains less understood.
 On the one hand, enlarged legislatures may increase government spending and lawmaking, which can lead to more public goods \citep{Weingastetal1981}.
@@
 Mayors make the initial policy proposal that consists of an investment in public goods provision, a decision to extract rents for personal gains, and a vector of side-transfers for councilors.
-If they fail to secure majoritarian support from councilors, a reversal stage occurs, where the decision leaves the mayor's office and councilors propose the public investments.
+If they fail to secure majoritarian support from councilors, a reversal stage occurs, where the decision leaves the mayor's office, and councilors propose the public investments.
 In this mayor-council bargaining process, costs come from the side-transfers required to secure a majority among councilors.
@@
 In 2004, the judiciary reinterpreted the Brazilian Constitution and unexpectedly changed the number of councilors in several municipalities.
-Until then, towns could freely determine their legislature size, but in March 2004 the Supreme Electoral Court created population thresholds and added one councilor to each set of 47,619 inhabitants.
+Until then, towns could freely determine their legislature size, but in March 2004, the Supreme Electoral Court created population thresholds and added one councilor to each set of 47,619 inhabitants.
 Around these cutoffs, the decision represented an exogenous change in city council size, allowing us to investigate the effects of increasing the number of local legislators in Brazil.
@@
 The legislation in municipalities on the left and on the right-hand side of the cutoffs mentioned local public goods.
-However, municipalities with larger city councils had around 15 percent more public goods provision proposals, what is in line with our expectations.
+However, municipalities with larger city councils had around 15 percent more public goods provision proposals, which is in line with our expectations.
 
@@
 A larger council size also increased enrollment by 2.58 children in elementary education classrooms without significantly diminishing elementary school quality.
-These services are crucial for welfare and result from an eased bargaining between the mayor and the city council.
+These services are crucial for welfare and result from eased bargaining between the mayor and the city council.
 
-This paper contributes to three strands of the literature.
+This paper contributes to four strands of the literature.
 First, this paper dialogues with a large literature on multilateral bargaining.
@@
 
-Second, this paper contributes to the literature on the political and economic effects of larger legislatures.
+Second, this paper contributes to the literature on the effects of larger legislatures in service provision.
 Following the contribution by \citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures increase the legislative pressure for providing targeted public goods to local supporters at the expense of the entire polity \citep{freire2021legislature}.
@@
 
-Finally, our article also contributes to a growing literature on municipal partisan politics.
+Third, our article also contributes to a growing literature on municipal partisan politics.
 Most papers in this area estimate the effects of the mayor's party on political outcomes.
@@
 \citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
-This paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.
+Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.
+
+Finally, this paper contributes to a growing literature on the causes and effects of legislature sizes.
+Most papers on legislature size study the trade-off between representation and efficiency \citet{Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}.
+However, a few new papers explore the effects of legislature size on lawmaking and partisanship \citep{rush2013conclusion, kirkland2014chamber}.
+For instance, \citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures.
+In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively.
+\citet{marland2019fewer} questions the economic crises mechanism, showing that political elites shrink legislatures mostly to signal to the public the priority of their austerity agenda.
+In this paper, we show that legislature size affects welfare by changing the partisan composition of legislatures.
 
@@
 
-Several cities in the world are governed by the mayor-council system.
-In mayor-council cities, the power is divided between a mayor that controls the Executive branch and a city council that supports or sanctions the policies proposed by the mayor.
-In this setting, consider a strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
+The design of institutions is crucial for long term welfare \citep{north1989constitutions, buenodemesquita2005logic, acemoglu2012nations} and democratic consolidation \citep{lijphart2018institutional, gandhi2019institutional}.
+One particular problem that each polity faces is determination of the size of its legislative bodies.
+The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{Stigler1976, muzzio1989size}.
+
+The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{taagepera1972size, Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}.
+Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases.
+This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}.
+Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures.
+The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{rush2013conclusion, kirkland2014chamber}.
+It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}.
+Balancing these two incentives is crucial for the optimal legislative composition \citep{taagepera1972size, auriol2012optimal}.
+
+However, the legislature size scholarship has overlooked two questions: first, does legislature size matter in contexts where the legislative bodies are not the pivotal decision-maker?
+And second, what is the ultimate effect of legislature size on welfare?
+On the one hand, legislature size's effects on welfare represent a significant gap in the political economy literature.
+It is likely generated by the predominance of the "law of 1/n" scholarship, which emphasized larger legislatures' overspending consequence.
+Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}.
+Of these papers, only \citet{lewis2019legislature} investigated its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} Moreover, \citet{frey2020larger} finds, for the Brazilian case after the 2009 legislature size and salaries constitutional amendment, a null effect in service provision from 2012 to 2016.
+These findings suggest that the legislature size and welfare nexus need a dedicated theoretical and empirical assessment.
+
+On the other hand, albeit the division of power, in most mayor-council (or presidential) systems, the Executive dominates the service provision.
+For instance, while the New York Times cited the New York City Mayor Bill De Blasio 2,084 times in 2021, it mentioned the 49 seating city councilors 440 times in the same period.
+To avoid the COVID crisis when the Executive was in the spotlight, we expanded the search for the past five years.
+In this new search, Bill De Blasio was mentioned 8,978 while the 49 seating city councilors were mentioned 2,046 times.\footnote{These figures were computed using the Dow Jones Factiva Database in November 2021.} The mayor was cited, on average, over four times more than all the city councilors combined.
+This Executive dominance has implications for policymaking, as coalitions and affinity with the Executive are going to be crucial for service provision \citep{buenodemesquita2005logic}.
+
+In a mayor-council setting, consider a strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
 The mayor has the prerogative of proposing a vector of policies on which city councilors vote.
@@
 If councilors reject the mayor's proposal, no public goods are provided ($p=0$).
-Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the Supplementary Materials, we consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affects choices in any potential history of the game.
+Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the Full Supplementary Materials (available in the paper's GitHub page), we consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affects choices in any potential history of the game.
 The equilibrium public goods provision level is even higher than in the model presented here, as city councilors prefer to approve the mayor's proposal than run the risk of an opposition member becoming the proposer.}
@@
 
-Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{gottlieb2019countervailing}.
+Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{besley2010political}.
 In a political system with around thirty parties and a sample average of almost ten parties in the municipalities we study, candidates per seat can increase exponentially.
@@
 
-\pagebreak
-
 \begin{table}[!htbp] \centering 

### 2021-11-09 article/article.Rmd
article

@@
 However, a few new papers explore the effects of legislature size on lawmaking and partisanship \citep{rush2013conclusion, kirkland2014chamber}.
-For instance, \citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures.
+For instance, \citet{kirkland2014chamber} shows that in larger legislatures it is harder for politicians to know each other well and collaborate, making them rely more heavily on party cues and committee structures.
 In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively.
@@
 
-The design of institutions is crucial for long term welfare \citep{north1989constitutions, buenodemesquita2005logic, acemoglu2012nations} and democratic consolidation \citep{lijphart2018institutional, gandhi2019institutional}.
+The design of institutions is crucial for long term welfare \citep{north1989constitutions, buenodemesquita2005logic, acemoglu2012nations}.
 One particular problem that each polity faces is determination of the size of its legislative bodies.
@@
 Otherwise, the city councilor belongs to the opposition $O = \{1, 2, \cdots, N \} \setminus G$.
-The mayor's policy generates a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends on the party affiliation of the councilor.
-If councilors reject the mayor's proposal, no public goods are provided ($p=0$).
-Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the Full Supplementary Materials (available in the paper's GitHub page), we consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affects choices in any potential history of the game.
+The mayor's policy generates a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends on the party affiliation of the councilor.\footnote{One example of partisan benefits is that, as the mayor shares partisan ties with members of the government coalition, a fraction of the public goods provision can be claimed by councilors as their contribution.
+We propose an extension in the Full Supplementary Materials (available in [REDACTED FOR PEER REVIEW]) that assumes $p = \phi g$, where $\phi$ is the fraction of the public goods provision that can be credit claimed by the city councilor aligned with the mayor.} If councilors reject the mayor's proposal, no public goods are provided ($p=0$).
+Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the Full Supplementary Materials, we consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affects choices in any potential history of the game.
 The equilibrium public goods provision level is even higher than in the model presented here, as city councilors prefer to approve the mayor's proposal than run the risk of an opposition member becoming the proposer.}
@@
 \end{enumerate}
-
-## Competing Hypotheses
-
-In this paper, we show that the provision of education and health care in Brazil improves with larger legislatures.
-This is because the chances of electing a city councilor aligned with the mayor are 91 percent, thanks to the rule of distributing seats adopted in the country.
-
-However, other pathways may also explain the nexus between city council size and welfare.
-First, improvements in representation could change the provision of health care and education.
-Increasing legislature size without changing the population makes councilors represent fewer people.
-For example, in a town with 50 thousand voters and ten councilors, each councilor represents five thousand voters.
-If the same city has eleven councilors, then each councilor represents 4.5 thousand voters.
-This facilitates the representation of minorities, as they have to gather fewer votes to elect a city councilor.
-A minority representative can advocate for policies that would improve the welfare of marginalized groups \citep{ChattopadhyayDuflu2004, chin2011redistributive, pande2003can}.
-Diversity could also improve governance in municipalities \citep{rugh2011provision}.
-For instance, more women in public offices may shift service provision toward welfare expenditure \citep{brollo2016happens, duflo2012women, funk2019representative, hernandez2018women}.
-Therefore, an alternative hypothesis to explain the increased service provision is that larger legislatures improve female and minority representation in Brazil.\footnote{For a description of the barriers faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
-
-Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{besley2010political}.
-In a political system with around thirty parties and a sample average of almost ten parties in the municipalities we study, candidates per seat can increase exponentially.
-According to the Brazilian electoral law, each party can sponsor 1.5 times the number of seats as candidates.
-If a party forms a pre-electoral coalition, this number increases to two times the number of seats \citep{coneglian2008lei}.
-An election in a small town, with ten councilors, may end up with 600 candidates: (30 parties) x (two times the number of seats) x (ten seats).
-Therefore, an alternative hypothesis to explain the increased service provision is that larger council size increase the competitiveness of the election.\footnote{Despite the common assumption that competitiveness improve welfare, \citet{boulding2014political} and \citet{gottlieb2019countervailing} can increase budgetary pressure, lower social policy, lead to bargaining inefficiencies.}
-
-Finally, the mayor and the legislature carry out the provision of services.
-Similar to what happens in firms, an extra employee can increase the firm productivity frontier by improving cooperation and synergistic outputs \citep{alchian1972production, holmstrom1982moral}.
-A similar argument would posit that the increase in council size increases the public service production capability in the municipality.
-As the production of the legislature manifests itself into legislation, an alternative hypothesis to explain the increased service provision is that more laws proposed by the city councilors are being approved.
-
-\begin{enumerate}[labelindent=*, 
-style=multiline, leftmargin=*, 
-label=AH\arabic*.]
-  \item Female representation increases with legislature size, improving public goods provision.
-  \item Non-white representation increase with legislature size, improving public goods provision.
-  \item Election competitiveness increases with legislature size, improving public goods provision.
-  \item Legislative production increases with legislature size, improving public goods provision.
-\end{enumerate}
-
-We show below that hypotheses H1 and H2 hold, while the data falsify the alternative hypotheses AH1 to AH4.
 
@@
 To test the formal model's predictions, we present four sets of empirical results.
-First, we show that the alternative hypothesis, which emphasizes representation, competitiveness, and legislative productivity, fails to receive empirical support.
-Second, we confirm the bargaining costs hypothesis and find that the additional legislator also promotes more appointments of bureaucrats.
+First, we confirm the bargaining costs hypothesis and find that the additional legislator also promotes more appointments of bureaucrats.
 This aligns with the councilors' descriptions of the strategies mayors employ to consolidate support from city councilors.
-Third, we show that municipalities with an extra city councilor approve more public goods laws in general and on education and health care.
-Finally, we show that all these pieces of evidence result in improvements in infant mortality and elementary school enrollment, two vital services for welfare.
+Second, we show that municipalities with an extra city councilor approve more public goods laws in general and on education and health care.
+Third, we show that all these pieces of evidence result in improvements in infant mortality and elementary school enrollment, two vital services for welfare.
+Finally, we point that the results are robust to alternative channels for the influence of legislature size on welfare, demonstrating that representation of women and non-whites, competitiveness, and legislative productivity, fail to receive empirical support.
 
-## Council Size, Bargaining Costs, and Alternative Hypotheses
+## Council Size, Bargaining Costs, and Job Appointments
 \label{sub:bargcosts}
 
-Table \ref{tab:bargain} tests the first hypothesis and the alternative hypotheses about the nexus between city council size and bargaining costs.
 The formal model's central premise is that larger legislature sizes produce lower bargaining costs when the chances to elect politicians aligned with the mayor are sufficiently high.
-However, the results could stem from different mechanisms, such as minority and female representation, competition, and increased council-sponsored legislative productivity.
-In Panel A, we counter the alternative explanations, while in Panel B, we present evidence that corroborates our findings.
-
-Panel A (Table \ref{tab:bargain}) tests hypotheses AH1 to AH4.
-AH1 and AH2 establish that better representation of under-served groups could improve welfare.
-However, columns (1) and (2) show that larger city councils do not increase the representation of females or non-whites.
-AH3 states that enhanced competition could improve responsiveness, increasing service provision.
-Looking at competition per seat in municipalities with larger city councils, Column (3) in Panel A shows a null effect of council size on the competition.
-Finally, AH4 states that council-sponsored legislation could be increasing in larger councils.
-Yet, Column (4) shows that it remains unchanged when council sizes increase.
+Moreover, the main bargaining chip between the Executive and the Legislative is job appointments.
+This is more so when the city councilors are aligned with the mayor.
+As job appointments are crucial for governing, we study the number of politically appointed bureaucrats, career bureaucrats, and councilors' assistants.
+Politically appointed bureaucrats are associated with better service provision in Brazil, as their tenure in office depends directly on the survival of the politician supporting them \citep{toral2019benefits}.
+Career bureaucrats pass through a rigorous examination, limiting their usefulness as bargaining chips between city councilors and mayors.
+Moreover, career bureaucrats cannot be fired once hired, which considerably constrains politicians' pressure on them.
+Finally, city councilors who want to influence policy may employ more staff members and assistants to their offices.
+This could influence policymaking through city councilor's pressuring on the bureaucracy, defying our hypothesized mechanism.
+Our theoretical expectations for these regressions are that larger council size affects the political alignment of city councilors and the number of politically appointed bureaucrats.
+It should not affect the number of career bureaucrats or city council assistants, as it is more valuable to have a political appointee that politicians can pressure, working directly with voters.
+Table \ref{tab:bargain} tests the first hypothesis about the nexus between city council size and bargaining costs and explores the consequences of larger legislatures on the municipal bureaucracy.
 
@@
 \toprule
-& \multicolumn{4}{c}{\textbf{Panel A: Representation, Competition, and Legislation Approval}} \\ \cline{2-5}
  & \multicolumn{1}{c}{\small{(1)}} 
- & \multicolumn{1}{c}{\small{(2)}} 
- & \multicolumn{1}{c}{\small{(3)}} 
- & \multicolumn{1}{c}{\small{(4)}} \\
- & \multicolumn{1}{c}{\small{Num. Female}} & 
- \multicolumn{1}{c}{\small{Num. Non-white}} &
-  \multicolumn{1}{c}{\small{Candidates}} & 
-  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
-   & \multicolumn{1}{c}{\small{councillors}} & 
- \multicolumn{1}{c}{\small{councillors}} &
-  \multicolumn{1}{c}{\small{Per Seat}} & 
-  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-LATE & 0.22 & 0.60 & -0.19 & -0.02 \\ 
-  & (0.38) & (0.85) & (1.11) & (0.08) \\ 
+ & \multicolumn{1}{c}{\small{(2)}} &
+ \multicolumn{1}{c}{\small{(3)}} & 
+ \multicolumn{1}{c}{\small{(4)}} \\
+ & \multicolumn{1}{c}{\small{Mayoral}} & 
+ \multicolumn{1}{c}{\small{Num. Politically}} & 
+ \multicolumn{1}{c}{\small{Num. Career}} & 
+ \multicolumn{1}{c}{\small{Num. Councilor}} \\
+ & \multicolumn{1}{c}{\small{Coalition Size}} & 
+ \multicolumn{1}{c}{\small{Appointed Bureaucrats}} & 
+ \multicolumn{1}{c}{\small{Bureaucrats}} & 
+ \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+ LATE & 0.91$^{*}$ & 104.49$^{*}$ & 71.57 & 2.09 \\ 
+  & (0.50) & (61.53) & (218.12) & (4.37) \\ 
     \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{269} \\ 
-Eff N Left & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
-Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{141} \\ 
-BW Loc Poly & 8.623 & 2.958 & 8.144 & 10.976 \\ 
-BW Bias & 13.565 & 4.922 & 12.018 & 16.708 \\[1.0ex] 
-\midrule 
-& \multicolumn{4}{c}{\textbf{Panel B: Partisan Alignment and Bureaucratic Appointments}} \\ \cline{2-5}
- & \multicolumn{1}{c}{\small{(5)}} 
- & \multicolumn{1}{c}{\small{(6)}} & & \\
- & \multicolumn{1}{c}{\small{Mayoral}} & 
- \multicolumn{1}{c}{\small{Num. Politically}} & & \\
- & \multicolumn{1}{c}{\small{Coalition Size}} & 
- \multicolumn{1}{c}{\small{Bureaucrats}} & 
-  & \\[1ex] \cline{2-2} \cline{3-3}
- LATE & 0.91$^{*}$ & 104.49$^{*}$ & & \\ 
-  & (0.50) & (61.53) & & \\ 
-    \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{5179} & \multicolumn{1}{c}{15536} & & \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1027} & & \\ 
-Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & & \\ 
-Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & & \\ 
-BW Loc Poly & 10.025 & 6.242 & & \\ 
-BW Bias & 15.889 & 10.243 & & \\ 
+ N Left & \multicolumn{1}{c}{5179} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
+Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
+Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
+BW Loc Poly & 10.025 & 6.242 & 7.695 & 5.134 \\ 
+BW Bias & 15.889 & 10.243 & 11.780 & 8.902 \\ 
 \bottomrule
@@
 
-Panel B (Table \ref{tab:bargain}) illustrates the mechanism put forward in the formal model.
-Column (5) shows a 91\% chance of the extra legislator belonging to the mayoral coalition.
+Column (1) shows a 91\% chance of the extra legislator belonging to the mayoral coalition.
 The model hypothesis stated that the probability of electing a city councilor allied with the mayor is sufficiently high.
@@
 The rounding rule favors the coalitions with more votes.
-Most of the time, the coalition of the elected mayor is the one that receives more votes.} Column (6) demonstrates that adding one councilor increases appointed employees by around 104 extra employees per additional city councilor.
-When negotiating with city councilors, these employees are a great bargaining chip, and they are also associated with better service provision.
+Most of the time, the coalition of the elected mayor is the one that receives more votes.} Column (2) demonstrates that adding one councilor increases appointed employees by around 104 extra employees per additional city councilor.
+When negotiating with city councilors, these employees are a great bargaining chip, and they are also associated with better service provision \citep{ toral2019benefits}.
+As expected, legislature size has a null effect on the number of career bureaucrats (Column 3) and councilors' staff members (Column 4).
 
@@
 
-We have established in Table \ref{tab:bargain} column (4) that the quantity of laws councilors approve remain constant.
-However, this tells us little about the legislation composition in municipalities with larger council sizes.
 In Figure \ref{LEGAPPR}, we show that the per capita number of laws related to local public goods provision increases in towns that receive the extra legislator, vis-à-vis baseline cities that did not get an additional councilor.
@@
 For example, building a health clinic in a particular district can virtually exclude the citizens that are not living in the neighborhood.
-However, we am still considering these as public goods, albeit targeted at a specific locality.}
+However, we are still considering these as public goods, albeit targeted at a specific locality.}
 
@@
 \toprule
-& \multicolumn{4}{c}{\textbf{Council Size and Welfare -- Main Estimates}} \\ \cline{2-5}
  & \multicolumn{1}{c}{\small{(1)}} 
@@
 BW Bias & 11.95 & 11.01 & 10.58 & 15.107 \\ [1.0ex] 
-\midrule 
-& \multicolumn{4}{c}{\textbf{Council Size and Welfare -- Placebo Estimates}} \\ \cline{2-5}
-& \multicolumn{1}{c}{\small{(5)}} 
- & \multicolumn{1}{c}{\small{(6)}} 
- & \multicolumn{1}{c}{\small{(7)}} 
- & \multicolumn{1}{c}{\small{(8)}} \\
-& \multicolumn{1}{c}{\small{Infant}} & 
- \multicolumn{1}{c}{\small{Postneonatal}} &
-  \multicolumn{1}{c}{\small{School}} & 
-  \multicolumn{1}{c}{\small{Education}} \\ 
-   & \multicolumn{1}{c}{\small{Mortality}} & 
- \multicolumn{1}{c}{\small{Mortality}} &
-  \multicolumn{1}{c}{\small{Enrollment}} & 
-  \multicolumn{1}{c}{\small{Quality}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-LATE & -1.14 & -0.19 & 0.44 & -0.10 \\ 
-  & (1.05) & (0.22) & (0.61) & (0.11) \\ 
-    \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{10613} & \multicolumn{1}{c}{17236} & \multicolumn{1}{c}{9040} & \multicolumn{1}{c}{7528} \\ 
-N Right & \multicolumn{1}{c}{2715} & \multicolumn{1}{c}{3624} & \multicolumn{1}{c}{1802} & \multicolumn{1}{c}{1738} \\ 
-Eff N Left & \multicolumn{1}{c}{1210} & \multicolumn{1}{c}{780} & \multicolumn{1}{c}{1210} & \multicolumn{1}{c}{1255} \\ 
-Eff N Right & \multicolumn{1}{c}{890} & \multicolumn{1}{c}{664} & \multicolumn{1}{c}{728} & \multicolumn{1}{c}{752} \\ 
-BW Loc Poly & 4.838 & 2.807 & 6.364 & 6.873 \\ 
-BW Bias & 7.143 & 8.041 & 9.68 & 10.291 \\
 \bottomrule
@@
 The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in sizable welfare effects.
-As expected, placebo regressions were statistically insignificant.
 
@@
 Education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
-As expected, the placebo regressions are insignificant.
+
+## Effects of Legislature Size Changes on Representation, Competitiveness, and Legislative Productivity
+
+In this paper, we show that the provision of education and health care in Brazil improves with larger legislatures.
+This is because the chances of electing a city councilor aligned with the mayor are 91 percent, thanks to the rule of distributing seats adopted in the country.
+In the Supplemental Materials, we also run regressions in placebo cutoffs between the actual cutoffs, showing that our estimates are consistently null when we are supposed to find insignificant results.
+
+However, other pathways may also explain the nexus between city council size and welfare.
+First, improvements in representation could change the provision of health care and education.
+Increasing legislature size without changing the population makes councilors represent fewer people.
+For example, in a town with 50 thousand voters and ten councilors, each councilor represents five thousand voters.
+If the same city has eleven councilors, then each councilor represents 4.5 thousand voters.
+This facilitates the representation of minorities, as they have to gather fewer votes to elect a city councilor.
+A minority representative can advocate for policies that would improve the welfare of marginalized groups \citep{ChattopadhyayDuflu2004, chin2011redistributive, pande2003can}.
+Diversity could also improve governance in municipalities \citep{rugh2011provision}.
+For instance, more women in public offices may shift service provision toward welfare expenditure \citep{brollo2016happens, duflo2012women, funk2019representative, hernandez2018women}.
+Therefore, an alternative hypothesis to explain the increased service provision is that larger legislatures improve female and minority representation in Brazil.\footnote{For a description of the barriers faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
+
+Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{besley2010political}.
+In a political system with around thirty parties and a sample average of almost ten parties in the municipalities we study, candidates per seat can increase exponentially.
+According to the Brazilian electoral law, each party can sponsor 1.5 times the number of seats as candidates.
+If a party forms a pre-electoral coalition, this number increases to two times the number of seats \citep{coneglian2008lei}.
+An election in a small town, with ten councilors, may end up with 600 candidates: (30 parties) x (two times the number of seats) x (ten seats).
+Therefore, an alternative hypothesis to explain the increased service provision is that larger council size increase the competitiveness of the election.\footnote{Despite the common assumption that competitiveness improve welfare, \citet{boulding2014political} and \citet{gottlieb2019countervailing} show that more competition can increase budgetary pressure, lower social policy, lead to bargaining inefficiencies.}
+
+Finally, the mayor and the legislature carry out the provision of services.
+Similar to what happens in firms, an extra employee can increase the firm productivity frontier by improving cooperation and synergistic outputs \citep{alchian1972production, holmstrom1982moral}.
+A similar argument would posit that the increase in council size increases the public service production capability in the municipality.
+As the production of the legislature manifests itself into legislation, an alternative hypothesis to explain the increased service provision is that more laws proposed by the city councilors are being approved.
+
+\begin{table}[!htbp] \centering 
+  \caption{Robustness: Effects of Legislature Size Changes on Representation, Competitiveness, and Legislative Productivity} 
+  \label{tab:robust} 
+\scalebox{0.9}{
+\begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+ & \multicolumn{1}{c}{\small{(1)}} 
+ & \multicolumn{1}{c}{\small{(2)}} 
+ & \multicolumn{1}{c}{\small{(3)}} 
+ & \multicolumn{1}{c}{\small{(4)}} \\
+ & \multicolumn{1}{c}{\small{Num. Female}} & 
+ \multicolumn{1}{c}{\small{Num. Non-white}} &
+  \multicolumn{1}{c}{\small{Candidates}} & 
+  \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
+   & \multicolumn{1}{c}{\small{councillors}} & 
+ \multicolumn{1}{c}{\small{councillors}} &
+  \multicolumn{1}{c}{\small{Per Seat}} & 
+  \multicolumn{1}{c}{\small{Approved Council}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+LATE & 0.22 & 0.60 & -0.19 & -0.02 \\ 
+  & (0.38) & (0.85) & (1.11) & (0.08) \\ 
+  \hdashline \\[-1.8ex] 
+ N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{269} \\ 
+Eff N Left & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{141} \\ 
+BW Loc Poly & 8.623 & 2.958 & 8.144 & 10.976 \\ 
+BW Bias & 13.565 & 4.922 & 12.018 & 16.708 \\[1.0ex] 
+\bottomrule
+\end{tabularx}
+\begin{tablenotes}
+\small
+\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1.
+RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel.
+Robust standard errors, clustered at the municipal level, in parentheses.
+Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region.
+\textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated).
+\textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth.
+\textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE).
+\textit{BW Bias} is the Bandwidth used to compute the standard errors.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+Table \ref{tab:robust} tests whether our results could stem from these different mechanisms.
+Columns (1) and (2) test the hypotheses that better representation of under-served groups could improve welfare.
+As we can see, larger city councils do not increase the representation of females or non-whites.
+Column (3) shows that the competition per seat in municipalities with larger city councils remain statistically equal to zero.
+Finally, Column (4) shows that the proportion of legislation passed by the city council remains unchanged when council sizes increase.
 
@@
 Our findings have implications that extend well beyond Brazil.
-As several countries have local city councils and multiparty systems, the dynamics we expose here may explain how fragmented legislatives are not synonymous with policy paralysis.
-This runs in contrast with well-established theories that point out that multipartism may be a peril to democratic regimes \citep{mainwaring1993presidentialism, stepan1993constitutional}.
+A general form of our argument is that it is easy for a politician to negotiate with members of her in-group \citep{abbink2019, g9030057}.
+Specifically, several countries have divisions between Executive and Legislative, such as the federal level of presidential systems, state governments, and local city councils.
+As these political bodies are influenced by political allegiances, the dynamics we expose here generalize to most of them.
+Depending on legislative support, changing legislature size could increase the chance of electing politicians that are not aligned with the Executive, decreasing welfare.
+Despite the particular effects on political support and welfare, the logic described in this paper would remain relevant for empirically accessing the welfare effects of enlarged legislatures.
 Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}.

### 2021-11-10 appendix/appendix.Rmd
change size fig 10
format figures and add affiliations

@@
 author:
+  - Umberto Mignozzeti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
+date: \today
 fontfamily: libertine
@@
 
-\pagebreak
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+
+[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+
+\newpage
 
@@
 \begin{center}
-\centerline{\includegraphics[width=6.5in,height=5.5in,angle=0]{../figures/rdAddCuts1.pdf}}
+\centerline{\includegraphics[width=5.2in,height=5.5in,angle=0]{../figures/rdAddCuts1.pdf}}
 \caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}

### 2021-11-10 article/article.Rmd
format figures and add affiliations

--- 2021-11-04 article/article.Rmd
@@
 author: 
+  - Umberto Mignozzeti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
 date: \today
@@
 jelcodes: H41; H80; I31; I38
-fontsize: 11pt
+fontsize: 12pt
 margin: 2cm
@@
 ```
+
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+
+[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
 
@@
 Most papers in this area estimate the effects of the mayor's party on political outcomes.
-For instance, \citet{gerber2011mayors} and \citet{de2016mayoral} find differences in governance when comparing Democratic and Republican mayors.
+For instance, \citet{de2016mayoral} and \citet{gerber2011mayors} find differences in governance when comparing Democratic and Republican mayors.
 Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors.
@@
 Finally, this paper contributes to a growing literature on the causes and effects of legislature sizes.
-Most papers on legislature size study the trade-off between representation and efficiency \citet{Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}.
-However, a few new papers explore the effects of legislature size on lawmaking and partisanship \citep{rush2013conclusion, kirkland2014chamber}.
-For instance, \citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures.
+Most papers on legislature size study the trade-off between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, Stigler1976}.
+However, some recent articles explore the effects of legislature size on lawmaking and partisanship.
+\citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures.
 In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively.
 \citet{marland2019fewer} questions the economic crises mechanism, showing that political elites shrink legislatures mostly to signal to the public the priority of their austerity agenda.
-In this paper, we show that legislature size affects welfare by changing the partisan composition of legislatures.
+In this article, we show that legislature size affects welfare by changing the partisan composition of legislatures.
 
@@
 
-The design of institutions is crucial for long term welfare \citep{north1989constitutions, buenodemesquita2005logic, acemoglu2012nations} and democratic consolidation \citep{lijphart2018institutional, gandhi2019institutional}.
+The design of institutions is crucial for long term welfare \citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions} and democratic consolidation \citep{gandhi2019institutional, lijphart2018institutional}.
 One particular problem that each polity faces is determination of the size of its legislative bodies.
-The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{Stigler1976, muzzio1989size}.
+The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{muzzio1989size, Stigler1976}.
 
-The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{taagepera1972size, Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}.
+The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, rush2013conclusion, Stigler1976, taagepera1972size}.
 Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases.
@@
 Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures.
-The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{rush2013conclusion, kirkland2014chamber}.
+The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{kirkland2014chamber, rush2013conclusion}.
 It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}.
-Balancing these two incentives is crucial for the optimal legislative composition \citep{taagepera1972size, auriol2012optimal}.
+Balancing these two incentives is crucial for the optimal legislative composition \citep{auriol2012optimal, taagepera1972size}.
 
@@
 Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}.
-Of these papers, only \citet{lewis2019legislature} investigated its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} Moreover, \citet{frey2020larger} finds, for the Brazilian case after the 2009 legislature size and salaries constitutional amendment, a null effect in service provision from 2012 to 2016.
-These findings suggest that the legislature size and welfare nexus need a dedicated theoretical and empirical assessment.
+Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2020larger} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016.
+These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.
 
-On the other hand, albeit the division of power, in most mayor-council (or presidential) systems, the Executive dominates the service provision.
+Despite the division of power, the Executive dominates the debates on public service provision in most mayor-council (or presidential) systems.
 For instance, while the New York Times cited the New York City Mayor Bill De Blasio 2,084 times in 2021, it mentioned the 49 seating city councilors 440 times in the same period.
@@
 For the mayor, the optimal offer is at $k=0$, representing a no delay in policy implementation.
-Moreover, we assume that the players play no dominated strategies, even when there is insufficient support for the policy.
+We assume that players have no dominated strategies, even when there is insufficient support for the policy.
 
@@
 
-Table \ref{validitycheck} displays the results of the validity checks.
-We present the first-stage regressions at the top of the Table, with and without covariates, for both real and placebo cutoffs.
-At the bottom, we estimate the pre-treatment covariate balance.
-Furthermore, in the Supplementary Materials, we run placebo checks for all the models using placebo cutoffs within the real ones.
-The results are available in sections A.6 to A.12 of the Supplementary Materials.
-
 \begin{table}[htb!] \centering 
@@
 
+Table \ref{validitycheck} displays the results of the validity checks.
+We present the first-stage regressions at the top of the Table, with and without covariates, for both real and placebo cutoffs.
+At the bottom, we estimate the pre-treatment covariate balance.
+Furthermore, in the Supplementary Materials, we run placebo checks for all the models using placebo cutoffs within the real ones.
+The results are available in sections A.6 to A.12 of the Supplementary Materials.
+
 Note that without the covariates, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
@@
 
-\begin{table}[!htbp] \centering 
+\begin{table}[!htpb] \centering 
   \caption{Political Effects of Increasing the Number of Legislators} 
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/lawsApproved.pdf}}
+      \centerline{\includegraphics[width=6in,angle=0,height=6.5in]{../figures/lawsApproved.pdf}}
       \bigskip
@@
 
-\begin{table}[!htbp] \centering 
+Table \ref{tab:outcomes} shows that increasing the city council by one legislator generates welfare improvement in municipalities.
+In health care, increasing the legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
+This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
+Moreover, postneonatal mortality decreases by 0.90 casualties per 1,000 births, which remains around the 0.14 standard deviations improvement as infant mortality.
+Infant mortality is a primary outcome for welfare, and it correlates with several other indicators of well-being \citep{world2005health}.
+The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in large welfare effects.
+As expected, placebo regressions were statistically insignificant.
+
+In terms of education, with the addition of a city councilor, enrollment in elementary schools increased by 2.58 children on average per school.
+This represents a change of around 0.20 standard deviations.
+Besides the influence of the mayoral support, enrollment can also directly impact the councilor's representation: Councilors can pressure the bureaucracy to accommodate a few extra students.
+With support from the mayor, they can help voters get access to schools, improving the voter's welfare.
+Education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
+As expected, the placebo regressions are insignificant.
+
+\begin{table}[!htpb] \centering 
   \caption{Legislature Size and Welfare} 
@@
 
-Table \ref{tab:outcomes} shows that increasing the city council by one legislator generates welfare improvement in municipalities.
-In health care, increasing the legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
-This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
-Moreover, postneonatal mortality decreases by 0.90 casualties per 1,000 births, which remains around the 0.14 standard deviations improvement as infant mortality.
-Infant mortality is a primary outcome for welfare, and it correlates with several other indicators of well-being \citep{world2005health}.
-The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in sizable welfare effects.
-As expected, placebo regressions were statistically insignificant.
-
-In terms of education, with the addition of a city councilor, enrollment in elementary schools increased by 2.58 children on average per school.
-This represents a change of around 0.20 standard deviations.
-Besides the influence of the mayoral support, enrollment can also directly impact the councilor's representation: Councilors can pressure the bureaucracy to accommodate a few extra students.
-With support from the mayor, they can help voters get access to schools, improving the voter's welfare.
-Education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
-As expected, the placebo regressions are insignificant.
-
 # Discussion

### 2021-11-11 article/article.Rmd
submission 2nd attempt

--- 2021-11-09 article/article.Rmd
@@
 Finally, this paper contributes to a growing literature on the causes and effects of legislature sizes.
-Most papers on legislature size study the trade-off between representation and efficiency \citet{Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}.
-However, a few new papers explore the effects of legislature size on lawmaking and partisanship \citep{rush2013conclusion, kirkland2014chamber}.
-For instance, \citet{kirkland2014chamber} shows that in larger legislatures it is harder for politicians to know each other well and collaborate, making them rely more heavily on party cues and committee structures.
+Most papers on legislature size study the trade-off between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, Stigler1976}.
+However, some recent articles explore the effects of legislature size on lawmaking and partisanship.
+\citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures.
 In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively.
 \citet{marland2019fewer} questions the economic crises mechanism, showing that political elites shrink legislatures mostly to signal to the public the priority of their austerity agenda.
-In this paper, we show that legislature size affects welfare by changing the partisan composition of legislatures.
+In this article, we show that legislature size affects welfare by changing the partisan composition of legislatures.
 
@@
 
-The design of institutions is crucial for long term welfare \citep{north1989constitutions, buenodemesquita2005logic, acemoglu2012nations}.
+The design of institutions is crucial for long term welfare \citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions} and democratic consolidation \citep{gandhi2019institutional, lijphart2018institutional}.
 One particular problem that each polity faces is determination of the size of its legislative bodies.
-The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{Stigler1976, muzzio1989size}.
+The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{muzzio1989size, Stigler1976}.
 
-The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{taagepera1972size, Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}.
+The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, rush2013conclusion, Stigler1976, taagepera1972size}.
 Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases.
@@
 
-# Results
+# Empirical Results
 \label{sec:results}
@@
 
-## Effects of Legislature Size Changes on Representation, Competitiveness, and Legislative Productivity
+## Robustness to Alternative Mechanisms
 

### 2022-03-08 article/article.Rmd
Update article.Rmd

@@
 And if the bargaining costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-Below we show that partisanship is the key to understand how this relationship.
+Below we show that partisanship is the key to understand how this relationship works.
 
@@
 
-Table \ref{tab:outcomes} shows that increasing the city council by one legislator generates welfare improvement in municipalities.
-In health care, increasing the legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
-This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
-Moreover, postneonatal mortality decreases by 0.90 casualties per 1,000 births, which remains around the 0.14 standard deviations improvement as infant mortality.
-Infant mortality is a primary outcome for welfare, and it correlates with several other indicators of well-being \citep{world2005health}.
-The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in sizable welfare effects.
-
-In terms of education, with the addition of a city councilor, enrollment in elementary schools increased by 2.58 children on average per school.
-This represents a change of around 0.20 standard deviations.
-Besides the influence of the mayoral support, enrollment can also directly impact the councilor's representation: Councilors can pressure the bureaucracy to accommodate a few extra students.
-With support from the mayor, they can help voters get access to schools, improving the voter's welfare.
-Education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
-
 ## Robustness to Alternative Mechanisms

### 2022-03-10 Memo/Memo_Template.Rmd
Memo

---
title: "Dinner"
to: Ralf
from: Martin
date: "`r Sys.time()`"
output: 
  pdf_document:
    template: article-template.latex
logo: "\\includegraphics[width=.25\\textwidth]{unnamed.png}"

---
We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript. We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result. Below, we intersperse our reactions and revisions to the suggestions enumerated in the editor's decision letter and the three manuscript reviews. We adopt the following conventions:

\begin{itemize}
\item Suggestions identified in reviewers' reports are in \textit{italicized text}. We provide direct quotation of their reviewers' reports, which have been lightly edited for clarifications or to conserve space.
\item Our responses to the reviewers' suggestions are in standard text.
\item The specific locations in the manuscript and online appendix where incorporated
revisions can be found are shown in \textbf{bold text}.
\end{itemize}

\section{Suggestions Raised by Reviewer 1}
\begin{itemize}
\item \textit{Overall the literature review is strong. I would recommend a couple of additions. Include among them is an important work the authors should cite on legislative size and spending and that is Gilligan and Matsusaka's 2001 article entitled ""Fiscal Policy, Legislature Size, and Political Parties: Evidence from the First Half of the Twentieth Century." Their findings are relevant for this study and should be referenced. In addition, the recently published book Population and Politics: The Impact of Scale by Gerring and Veenendaal which has a comprehensive analysis of this topic should also be incorporated into the literature review.\ldots }

\vspace{.2cm}
We thank the reviewer 1 for these two relevant additions. \textbf{We cite Gilligan and Matsusaka's 2001 article on page XXX:}: XXXX. \textbf{The Gerring and Veenendaal's book citation is on page XXX:} XXX. 
\vspace{.5cm}

\item \textit{In examining the relationship between legislative size and welfare why were education and health care selected as the independent variables? Was that decision based on data availability or were there another basis for the decision? It is not clear in the text of the manuscript.}

\vspace{.2cm}
The decision was based both on the relevance of these variables and due to data availability. We explain our decision on \textbf{page XXX}: XXX. We thank R1 for the opportunity to clarify the selection of these two central variables to our paper.
\vspace{.5cm}

\vspace{.2cm}
\item \textit{The details of the online survey conducted of Brazilian city councilors are lacking. What is the empirical contribution to the study? Beyond the online format what were the other administrative details involved with collecting that data?}

We agree with R1 that needed to provide more information on the online survey. Therefore, we detailed our procedures in the \textbf{Appendix Section XXX}.

\vspace{.5cm}

\item \textit{The models include a dummy variable for the northeast region. What specifically about this region would require adding it to the model. I am generally skeptical about including such a variable particularly since clustered standard errors are being estimated for municipal level. Is there logical reason to control for regional effects here? Very curious modeling decision by the authors.}

\vspace{.2cm}
\textbf{We now show the analysis without the dummy variable (page XXX) for the northeast region in the main paper and move the regressions with the dummy to the Appendix (page XXX).} The results are virtually the same. We agree with R1 that the inclusion of the dummy variable might generate unecessary confusion and are not central to our argument. \textbf{Therefore, we also explain on page XXX why we included the dummy variable for the northeast region on page XXX}: XXX.

\vspace{.5cm}

\end{itemize}
\section{Suggestions Raised by Reviewer 2}
\begin{itemize}
\item \textit{One minor issue for the author(s) to consider in future research: on p. 14 the paper states, "On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%. This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments." There is an alternative mechanism that the author(s) has not considered and that has been shown to work in resource allocations to municipalities in Japan under similar circumstances. A recent paper by Amy Catalinac, Bruce Bueno de Mesquita and Alastair Smith tests a formal model in which variance in centrally-provided local municipality resources is a function of a tournament among municipalities within a larger legislative district ("A Tournament Theory of Pork Barrel Politics: The Case of Japan" Comparative Political Studies 2020). Perhaps future research might compare the impact of the tournament structure with the local city council effects in Brazil as studied here.}

\vspace{.2cm}
We incorporate the suggestion for future research in the conclusion: XXX \textbf{(page XXX)}. We also agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article.

\vspace{.5cm}

\end{itemize}
\section{Suggestions Raised by Reviewer 3}
\begin{itemize}
\item \textit{The central story rests on some assumptions that I would like to see justified. Do mayor's generally want to spend more, and the city council holds them back? Why? I wonder about this assumption. Why does increasing the size of the city council usually result in pro-mayor additions? Under what conditions might increasing the size of the council bring in more diverse viewpoints or more polarized policy stances? What role is partisanship playing? It seems like it is mainly a proxy for agreement between councilors and the mayor, but do different parties have strongly different policy preferences? Does that matter for the results presented here?}

\vspace{.2cm}
We collapse two paragraphs from R3 since they speak to core topics in our paper, such as the allocation of the resources and polarization. First, \textbf{in the Appendix,} page XXX, we show that an extra-legislator does not increase the municipal spending significantly. Therefore, our results speaks more about the allocation of resources than on public spending. Also, \textbf{in the Appendix, page XX,} we show that the mayors' party and the representativeness of the extra legislator is not driving the results. Unfortunately.

\vspace{.5cm}

\item \textit{I wonder about the scope conditions. The evidence for the patterns presented from Brazil are very convincing, but I'd like to see more discussion of why these patterns hold in Brazil and how they might be different/ similar elsewhere.}

\vspace{.2cm}
We acknowledge that the external valitidy of our findings might be conditional on the time period of our study, since Frye (XXX) finds... We also mention that, unlikely many papers in the literature, we cannot corroborate the assertion that one extra legislator increases public spending, representativeness, and corruption. See the relevant passages on pages XXX.

\vspace{.5cm}

\end{itemize}

### 2022-03-11 Memo/Memo_Template.Rmd
up
Elaborando o memorandum e adicionando trechos em negrito no artigo.

@@
 ---
-title: "Dinner"
-to: Ralf
-from: Martin
+title: 
+to:
+from: 
 date: "`r Sys.time()`"
@@
     template: article-template.latex
-logo: "\\includegraphics[width=.25\\textwidth]{unnamed.png}"
+bibliography: references.bib
 
@@
 I would recommend a couple of additions.
-Include among them is an important work the authors should cite on legislative size and spending and that is Gilligan and Matsusaka's 2001 article entitled ""Fiscal Policy, Legislature Size, and Political Parties: Evidence from the First Half of the Twentieth Century." Their findings are relevant for this study and should be referenced.
-In addition, the recently published book Population and Politics: The Impact of Scale by Gerring and Veenendaal which has a comprehensive analysis of this topic should also be incorporated into the literature review.\ldots }
+Include among them is an important work the authors should cite on legislative size and spending and that is \citet{GilliganMatsusaka2001} article entitled "Fiscal Policy, Legislature Size, and Political Parties: Evidence from the First Half of the Twentieth Century." Their findings are relevant for this study and should be referenced.
+In addition, the recently published book Population and Politics: The Impact of Scale by Gerring and Veenendaal which has a comprehensive analysis of this topic should also be incorporated into the literature review.}
 
@@
 We thank the reviewer 1 for these two relevant additions.
-\textbf{We cite Gilligan and Matsusaka's 2001 article on page XXX:}: XXXX.
-\textbf{The Gerring and Veenendaal's book citation is on page XXX:} XXX.
+We cite \citet{GilliganMatsusaka2001} article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p.
+85]{gerring2020population}.
+
 \vspace{.5cm}
@@
 
-We agree with R1 that needed to provide more information on the online survey. Therefore, we detailed our procedures in the \textbf{Appendix Section XXX}.
+We agree with R1 that needed to provide more information on the online survey.
+Therefore, we detailed our procedures in the \textbf{Appendix Section A.14, on pages 22-23}.
+We also reference it \textbf{on pages 17 and 22 (footnote 13)} in the main article.
 
@@
 \textbf{Therefore, we also explain on page XXX why we included the dummy variable for the northeast region on page XXX}: XXX.
+Gilligan and Matsusaka.
 
@@
 This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments." There is an alternative mechanism that the author(s) has not considered and that has been shown to work in resource allocations to municipalities in Japan under similar circumstances.
-A recent paper by Amy Catalinac, Bruce Bueno de Mesquita and Alastair Smith tests a formal model in which variance in centrally-provided local municipality resources is a function of a tournament among municipalities within a larger legislative district ("A Tournament Theory of Pork Barrel Politics: The Case of Japan" Comparative Political Studies 2020).
+A recent paper by \citet{catalinac2020tournament} tests a formal model in which variance in centrally-provided local municipality resources is a function of a tournament among municipalities within a larger legislative district.
 Perhaps future research might compare the impact of the tournament structure with the local city council effects in Brazil as studied here.}
@@
 \vspace{.2cm}
-We incorporate the suggestion for future research in the conclusion: XXX \textbf{(page XXX)}.
-We also agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article.
+We agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article.
+In our \textbf{conclusion, on page 27,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."
 
@@
 \vspace{.2cm}
-We collapse two paragraphs from R3 since they speak to core topics in our paper, such as the allocation of the resources and polarization.
-First, \textbf{in the Appendix,} page XXX, we show that an extra-legislator does not increase the municipal spending significantly.
-Therefore, our results speaks more about the allocation of resources than on public spending.
-Also, \textbf{in the Appendix, page XX,} we show that the mayors' party and the representativeness of the extra legislator is not driving the results.
-Unfortunately.
+We collapse two paragraphs from R3 since they speak to core topics in our paper.
+\textbf{In the Appendix Table XXX, on page XXX,} we show that an extra-legislator usually does not increase the municipal spending significantly.
+Therefore, our results speak more about the allocation of resources than on public spending.
+\textbf{On page 15, in the Background on the Brazilian Case Section,} we clarify why increasing the city council size usually results in a pro-mayor legislator.
+"Additionally, Brazil's formula for apportioning legislative seats (a combination of the Hara quota and the D'Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat.
+As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p.
+68]{Ames2001}.
+Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition." See also \textbf{footnote 12, on page 21-22.} Unfortunately, we could not find evidence that an extra-legislator improves descriptive representation in the city council, for instance, more female or non-white legislators \textbf{(see Table 4).} Finally, \textbf{in the Appendix, on page XX,} we show that the mayors' party is not driving the results.
 
@@
 \vspace{.2cm}
-We acknowledge that the external valitidy of our findings might be conditional on the time period of our study, since Frye (XXX) finds...
-We also mention that, unlikely many papers in the literature, we cannot corroborate the assertion that one extra legislator increases public spending, representativeness, and corruption.
-See the relevant passages on pages XXX.
+We acknowledge that the external valitidy of our findings might be conditional on the time period or related to contexto characteristics of our study.
+\textbf{On page 5,} we write: "\citet{frey2021legislature}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
+Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage." \textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending.
+Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.
+\citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016.
+Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways.
+These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment." Additionally, \textbf{in the Discussion Section, on page 27,} we write about the implications of our findings beyond Brazil.
+In this paragraph, we added the following sentence: "However, as the [...]"
 

### 2022-03-11 article/article.Rmd
Memo
up
Elaborando o memorandum e adicionando trechos em negrito no artigo.

@@
 Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors.
-\citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
+\citet{frey2021legislature}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
 Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.
@@
 This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}.
-Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures.
+\textbf{However, legislature size does not \textit{necessarily} assure representativeness \citep[p.
+85]{gerring2020population}.} Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures.
 The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{kirkland2014chamber, rush2013conclusion}.
@@
 Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}.
-Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2020larger} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016.
-These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.
+Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016.
+\textbf{Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways.} These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.
 
@@
 Conversely, cities between one and four million inhabitants should have at least 33 councilors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.
+\textbf{Additionally, Brazil’s formula for apportioning legislative seats (a combination of the Hara quota and the D’Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat.
+As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p.
+68]{Ames2001}.
+Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition.}
 
@@
 We built two novel datasets to provide evidence for our mechanism.
-First, we ran a survey with former city councilors, asking how mayors consolidate their coalition support within the city council.
-Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
+First, we ran a survey with former city councilors, asking how mayors consolidate their coalition support within the city council.\footnote{We provide further information about the city council survey in section A.14 of the Supplementary Materials.} Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
 We hand-coded 3,466 laws into four categories: public goods, oversight, education and health care-related legislation, and other legislative duties.
@@
 Having extra help in the council can tilt the bargaining towards cheaper governing, thus improving public goods provision.
+\textbf{Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}.}
 

### 2022-03-11 Memo/Memo_Template.Rmd
update AJPS revision

@@
 ---
+
 We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript.
@@
 \begin{itemize}
-\item Suggestions identified in reviewers' reports are in \textit{italicized text}.
-We provide direct quotation of their reviewers' reports, which have been lightly edited for clarifications or to conserve space.
+\item Suggestions identified in reviewers' reports are in \textit{italicized text}. We provide direct quotations of their reviewers' reports, lightly edited for clarifications or to conserve space.
 \item Our responses to the reviewers' suggestions are in standard text.
-\item The specific locations in the manuscript and online appendix where incorporated
+\item The specific locations in the manuscript and online Appendix where incorporated
 revisions can be found are shown in \textbf{bold text}.
@@
 \vspace{.2cm}
-We thank the reviewer 1 for these two relevant additions.
-We cite \citet{GilliganMatsusaka2001} article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p.
+We thank reviewer 1 for these two relevant additions.
+We cite \citet{GilliganMatsusaka2001}'s article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p.
 85]{gerring2020population}.
@@
 \vspace{.2cm}
-The decision was based both on the relevance of these variables and due to data availability.
-We explain our decision on \textbf{page XXX}: XXX.
-We thank R1 for the opportunity to clarify the selection of these two central variables to our paper.
+We thank R1 for the opportunity to clarify the selection of these two central variables for our paper.
+We explain our decision on \textbf{page 17}: "Access to basic education and health care are relevant goals to developing countries.
+For instance, according to Brazil's 1988 Constitution, municipalities have to spend 25\% of their budget on education and 15\% on health care.
+Consequently, the Health Ministry Data Service and the Ministry of Education Data Service provide readily available quality data on health care and education."
+
 \vspace{.5cm}
@@
 
-We agree with R1 that needed to provide more information on the online survey.
+We agree with R1 that we needed to provide more information on the online survey.
 Therefore, we detailed our procedures in the \textbf{Appendix Section A.14, on pages 22-23}.
@@
 \vspace{.2cm}
-\textbf{We now show the analysis without the dummy variable (page XXX) for the northeast region in the main paper and move the regressions with the dummy to the Appendix (page XXX).} The results are virtually the same.
-We agree with R1 that the inclusion of the dummy variable might generate unecessary confusion and are not central to our argument.
-\textbf{Therefore, we also explain on page XXX why we included the dummy variable for the northeast region on page XXX}: XXX.
-Gilligan and Matsusaka.
+\textbf{FALTA FAZER: Dummy para a região Nordeste: estimar os modelos sem a dummy e reportar este resultado no artigo.
+Corrigir as menções aos coeficientes caso eles mudem.
+Colocar as regressões com a dummy no apêndice.}
 
@@
 \vspace{.2cm}
-We agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article.
-In our \textbf{conclusion, on page 27,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."
+We agree with R2 that testing the proposed mechanism is an extremely exciting project for a follow-up article.
+In our \textbf{conclusion, on page 29,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."
 
@@
 \vspace{.2cm}
-We collapse two paragraphs from R3 since they speak to core topics in our paper.
+\textbf{FALTA COMPLETAR:} We collapse two paragraphs from R3 since they speak to core topics in our paper.
 \textbf{In the Appendix Table XXX, on page XXX,} we show that an extra-legislator usually does not increase the municipal spending significantly.
@@
 \vspace{.2cm}
-We acknowledge that the external valitidy of our findings might be conditional on the time period or related to contexto characteristics of our study.
-\textbf{On page 5,} we write: "\citet{frey2021legislature}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
-Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage." \textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending.
+We acknowledge that the external validity of our findings might be conditional on the contextual characteristics of our study.
+\textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending.
 Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.
@@
 Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways.
-These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment." Additionally, \textbf{in the Discussion Section, on page 27,} we write about the implications of our findings beyond Brazil.
-In this paragraph, we added the following sentence: "However, as the [...]"
+These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment."
+Additionally, \textbf{in the Discussion Section, on page 29,} we write about the implications of our findings beyond Brazil.
+In this paragraph, we added the following new sentence: "As a caveat, our results might not be externally valid under different institutional norms (e.g., election rules or methods to allocating legislative seats) or at other governmental levels (federal or state).
+The findings presented here might also not be linear, since the impact of an extra-legislator should be heterogeneous depending upon the size of different legislatures or jurisdictions."
 

### 2022-03-11 article/article.Rmd
update AJPS revision

@@
 Our focus is on the impact of legislature size on education and health care, which are the two most important public services the municipal government should provide to citizens.
-We measure access to education with the average enrollment in primary (K--4) municipal public schools.
+\textbf{Access to basic education and health care are relevant goals to developing countries.
+For instance, according to Brazil's 1988 Constitution, municipalities have to spend 25\% of their budget on education and 15\% on health care.
+Consequently, the Health Ministry Data Service and the Ministry of Education Data Service provide readily available quality data on health care and education.} We measure access to education with the average enrollment in primary (K--4) municipal public schools.
 We assess education quality with the Education Development Index (Índice de Desenvolvimento da Educação Básica--IDEB), which the Ministry of Education has issued biannually since 2007.
@@
 Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}.
+\textbf{As a caveat, our results might not be externally valid under different institutional norms (e.g., election rules or methods to allocating legislative seats) or at other governmental levels (federal or state).
+The findings presented here might also not be linear, since the impact of an extra-legislator should be heterogeneous depending upon the size of different legislatures or jurisdictions.}
 

### 2022-04-15 Memo/memo.Rmd
add large text revision

--- 2022-03-11 Memo/Memo_Template.Rmd
@@
 title: 
-to:
-from: 
 date: "`r Sys.time()`"
@@
   pdf_document:
-    template: article-template.latex
+    template: memo-template.latex
 bibliography: references.bib 
-
 ---
 
-We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript.
+\noindent Dear Editors and Reviewers,
+\vspace{.5cm}
+
+\noindent We would like to thank you all for the opportunity to revise our
+manuscript, "Legislature Size and Welfare: Evidence from Brazil" (Ms. No.
+AJPS-44979). We have made several revisions to the paper along the lines
+suggested by the editors and reviewers and we believe the manuscript has
+improved significantly as a result.
+
+We have also incorporated additional literature into the manuscript, which has
+indeed given the paper a clearer theoretical framework through which our
+results can be interpreted.
+
+Below we discuss in more detail these changes and the several other changes we
+have made to the manuscript in response to comments from the editors and
+reviewers. We thank the editors again for the opportunity to revise the
+manuscript, and the reviewers for their extremely helpful comments.
+
+\vspace{.5cm}
+\noindent Sincerely,
+
+\vspace{.2cm}
+\noindent The Authors
+
+\newpage
+
+the editor and the three anonymous reviewers for their thoughtful consideration of our manuscript.
 We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result.

### 2022-04-15 article/article.Rmd
add large text revision

--- 2022-03-08 article/article.Rmd
@@
 abstract: "How does legislature size impact public service provision?
-Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood.
-In this paper, we use a formal model to show that increasing legislature size improves public goods provision.
-We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it.
+Despite the importance of institutional design for democratic governance, the effect of legislative features on citizen welfare remains little understood.
+In this paper, we use a formal model to show that increasing legislature size improves public goods delivery.
+We argue that changes in bargaining costs depend on whether additional legislators share the executive's party affiliation: More opposition members reduce the executive's public goods provision, while more government-aligned members increase it.
 We test this theory by exploiting sharp discontinuities in city council size in Brazil.
 We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures.
-To explore possible mechanisms, we surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008.
+To explore possible mechanisms, we surveyed former city councilors and analyzed 346,553 bills proposed between 2005 and 2008.
 This paper has implications for the design of representative institutions."
@@
 
-Legislative institutions are crucial for citizen welfare and service provision in democratic countries.
-Historically, the division of power and the birth of a representative government placed legislatures at the center of the political stage.
-In modern democracies, most countries have assemblies at all levels of government.
-These institutions regulate the quantity and quality of legislation, check and veto other political powers, and influence policymaking.
-Moreover, legislatures also determine taxation, government spending and oversee public programs \citep{auriol2012optimal, north1989constitutions, poulsen2018political, stasavage2011states, Weingastetal1981, weingast1988industrial}.
-
-Regardless of eventual differences in electoral rules, social composition, and internal procedures, all legislatures share one feature: they are collective bodies.
-As such, the number of representatives has important consequences for the whole polity.
-Indeed, legislature size is known to have a significant effect on collective action strategies, the bargaining power between state branches, government spending, and representation \citep{crain1979cost, freire2021legislature, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
-However, how legislature size impacts social welfare remains less understood.
-On the one hand, enlarged legislatures may increase government spending and lawmaking, which can lead to more public goods \citep{Weingastetal1981}.
-On the other hand, adding a legislator may increase the number of veto players and exacerbate collective action problems, thus hindering service provision \citep{gottlieb2019countervailing, tsebelis2002veto}.
-Therefore, what is the effect of larger legislatures on public service provision?
-
-In this paper, we propose a local legislature size and welfare theory that incorporates two crucial features: Executive leadership and party politics.
-First, in mayor-council municipalities, mayors tend to be central in local public service decisions.
-Mayors have the prerogative to boost public investments, like presidents in federal governments.
-Second, partisanship is essential at the local level, even in settings where the ideological attachment is weak, such as in most young democracies.
-Party attachment structures political views \citep{samuels2014power}, and local-level elites usually belong to different factions and parties.
-They fight for power in the municipality by controlling various parties and forming distinct pre-electoral coalitions.\footnote{Elite political competition in the local level has also been linked to violence and conflict in Brazil and elsewhere \citep{hoelscher2015politics, mignozzetti2018predatory}.} In many cities, family ties may be substitutes for the ideological component, but influential local leaders usually sort themselves into different political groups \citep{ferraz2020political, nunes1977coronelismo}.
-
-This paper incorporates partisanship and mayoral first-move advantage to a \citet{baron1989bargaining} bargaining model.
-Mayors make the initial policy proposal that consists of an investment in public goods provision, a decision to extract rents for personal gains, and a vector of side-transfers for councilors.
-If they fail to secure majoritarian support from councilors, a reversal stage occurs, where the decision leaves the mayor's office, and councilors propose the public investments.
-In this mayor-council bargaining process, costs come from the side-transfers required to secure a majority among councilors.
-We show that in a model without partisan concerns, bargaining costs always increase with larger city councils, which in turn lower public goods provision and rents.
-However, partisanship decreases bargaining costs when the chances of electing councilors aligned with the mayor are sufficiently high.
-Lower bargaining costs release funds for mayors to invest in public goods provision.
-In this case, a larger city council may have more partisan councilors aligned with the mayor, reducing the mayor's bargaining costs and increasing the equilibrium public goods provision.
-
-We test these theoretical predictions by exploiting an exogenous variation in Brazilian city council sizes.
-In 2004, the judiciary reinterpreted the Brazilian Constitution and unexpectedly changed the number of councilors in several municipalities.
-Until then, towns could freely determine their legislature size, but in March 2004, the Supreme Electoral Court created population thresholds and added one councilor to each set of 47,619 inhabitants.
-Around these cutoffs, the decision represented an exogenous change in city council size, allowing us to investigate the effects of increasing the number of local legislators in Brazil.
-
-We find that larger city councils changed the composition of mayoral coalitions and the number of appointed bureaucrats in the municipality.
-The extra city councilor had a 91 percent chance of belonging to the mayor's pre-electoral coalition.
-This enhanced the chances of electing a councilor connected with the mayor, which then decreased the bargaining costs for the mayor and boosted investments in public services.
-Moreover, the number of appointed bureaucrats increased by 104 with the additional councilor.
-In Brazil, appointing bureaucrats leads to higher quality workers, better service provision, and more accountability \citep{toral2019benefits}.
-
-Higher mayor support and more appointed bureaucrats correlate with city councilors' service provision expectations and legislation approved in Brazilian municipalities.
-We surveyed 174 former councilors who served during the 2005-2008 term, and they corroborate that mayors use bureaucratic appointments and political favors to secure support.
-As the formal model shows, bargaining with councilors requires offering transfers to the representatives.
-By investigating what councilors prefer to provide to voters, we find that councilors mainly demand job appointments, as these increase their reelection chances and improve municipal welfare.
-These findings align with a novel dataset we built with 346,553 laws passed in 63 municipalities within ten thousand inhabitants away from the cutoffs.
-The legislation in municipalities on the left and on the right-hand side of the cutoffs mentioned local public goods.
-However, municipalities with larger city councils had around 15 percent more public goods provision proposals, which is in line with our expectations.
-
-Finally, we show that the increase in legislature size significantly impacts municipal education and health care.
-Increasing the city council size by one legislator lowers infant mortality by 2.01 children per one thousand infants born and reduces postneonatal mortality by 0.90 children per one thousand infants that survived their first 28 days.
-A larger council size also increased enrollment by 2.58 children in elementary education classrooms without significantly diminishing elementary school quality.
-These services are crucial for welfare and result from eased bargaining between the mayor and the city council.
-
-This paper contributes to four strands of the literature.
-First, this paper dialogues with a large literature on multilateral bargaining.
-Repeated models of multilateral bargaining started with \citet{baron1989bargaining}, who extended the bilateral bargaining game proposed by \citet{rubinstein1982perfect} to more than two players.
-Several papers followed \citet{baron1989bargaining}, manipulating endogenous recognition power, the size of the required majority, and partisanship in the models \citep{agranov2020persistence, baranski2020determinants, calvert2005legislative, choate2019partisan}.\footnote{See \citet{eraslan2019legislative} for a comprehensive review of multilateral bargaining and \citet{ray2015coalition} for a review on coalition formation.} In this paper, we extend the \citet{baron1989bargaining} model under closed rules and add the mayor's first move and political partisanship.
-Partisanship here is different from \citet{choate2019partisan} since we consider partisanship as a zero-sum effect that is positive for politicians aligned with the mayor and negative otherwise.
-This paper investigates the often overlooked effect of legislature size on the bargaining equilibrium strategies.
-
-Second, this paper contributes to the literature on the effects of larger legislatures in service provision.
-Following the contribution by \citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures increase the legislative pressure for providing targeted public goods to local supporters at the expense of the entire polity \citep{freire2021legislature}.
-The corollary of the "law of $1/n$" is that increasing legislature size promotes excessive public spending.\footnote{\citet{PrimoSnyder2008} show that legislature size may result in positive or negative expenditures, depending on factors such as the degree that local public goods can exclude non-locals or deadweight costs associated with taxation.} In the US metaphor, this would explain significant infrastructure spending in smaller districts.
-However, the "law of $1/n$" literature rarely mentions the relationship between public goods provision and welfare.
-This paper is one of the first to study how the number of local legislators affects welfare.
-Our model provides a theoretical expectation based on the chances of electing a politician aligned with the mayor.
-The empirical estimates confirm our theoretical predictions, with the additional fact that legislature size has a null effect on expenditures in Brazil.
-
-Third, our article also contributes to a growing literature on municipal partisan politics.
-Most papers in this area estimate the effects of the mayor's party on political outcomes.
-For instance, \citet{de2016mayoral} and \citet{gerber2011mayors} find differences in governance when comparing Democratic and Republican mayors.
-Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors.
-\citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors.
-Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.
-
-Finally, this paper contributes to a growing literature on the causes and effects of legislature sizes.
-Most papers on legislature size study the trade-off between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, Stigler1976}.
-However, some recent articles explore the effects of legislature size on lawmaking and partisanship.
-\citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures.
-In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively.
-\citet{marland2019fewer} questions the economic crises mechanism, showing that political elites shrink legislatures mostly to signal to the public the priority of their austerity agenda.
-In this article, we show that legislature size affects welfare by changing the partisan composition of legislatures.
+Legislative institutions are crucial for citizen welfare and public service
+provision in democratic countries. Historically, the division of power and the
+birth of representative governments placed legislatures at the center of the
+political stage. In modern democracies, most countries have assemblies at all
+levels of government. These institutions regulate the quantity and quality of
+legislation, check and veto other political powers, and influence policymaking.
+Moreover, legislatures also determine taxation, government spending and oversee
+public programs \citep{auriol2012optimal, north1989constitutions,
+poulsen2018political, stasavage2011states, Weingastetal1981}.
+
+Regardless of eventual differences in electoral rules, social composition, and
+internal procedures, all legislatures share one common feature: They are
+collective bodies. As such, the number of elected representatives has important
+consequences for the whole polity. Legislature size is known to have a
+significant effect on collective action strategies, the bargaining power
+between state branches, government spending, and representation
+\citep{crain1979cost, freire2021legislature, gerring2020population,
+PrimoSnyder2008, rogers2002free, Weingastetal1981}. However, how legislature
+size impacts social welfare remains less understood. On the one hand, enlarged
+legislatures may reduce political particularism and increase overall government
+spending, which can lead to more public goods \citep{gerring2020population,
+GilliganMatsusaka2001, Weingastetal1981}. On the other hand, adding more
+representatives to a legislature may exacerbate collective action problems,
+thus hindering service provision \citep{gottlieb2019countervailing,
+tsebelis2002veto}. Therefore, what is the effect of larger legislatures on
+public service delivery?
+
+In this paper, we propose a new theory based on executive leadership and party
+politics to explain how city council size impacts local public goods provision.
+First, in mayor-council municipalities, mayors are the main responsible for
+public service decisions and have the power to boost public investment similar
+to presidents and governors. Second, partisanship plays a key role in city
+politics, even in countries in which ideological attachment is relatively weak.
+Party attachment structures political views \citep{samuels2014power}, and
+local-level elites usually belong to different factions and parties. They fight
+for power in the municipality by controlling various parties and forming
+distinct pre-electoral coalitions.\footnote{Elite political competition in the
+local level has also been linked to violence and conflict in Brazil and
+elsewhere \citep{hoelscher2015politics, mignozzetti2018predatory}.} In many
+cities, family ties may be substitutes for the ideological component, but
+influential local leaders usually sort themselves into different political
+groups \citep{ferraz2020political, nunes1977coronelismo}.
+
+This paper incorporates partisanship and mayoral first-move advantage to a
+\citet{baron1989bargaining} bargaining model. Mayors make the initial policy
+proposal, which consists of investments in public goods provision, rents for
+personal gains, and a vector of side-transfers for councilors. If mayors fail
+to secure majoritarian support from councilors, a reversal stage occurs, in
+which the decision leaves the mayor's office and councilors propose the public
+investments. In this mayor-council bargaining process, costs come from the
+side-transfers required to secure a majority among councilors. We show that in
+a model without partisan concerns, bargaining costs always increase with larger
+city councils, which in turn lower public goods provision and rents. However,
+partisanship decreases bargaining costs when the chances of electing councilors
+aligned with the mayor are sufficiently high. Lower bargaining costs release
+funds for mayors to invest in public goods provision. In this case, a larger
+city council may have more partisan councilors aligned with the mayor, reducing
+the mayor's bargaining costs and increasing the equilibrium public goods
+provision.
+
+We test these theoretical predictions by exploiting exogenous variation in city
+council size in Brazil. In 2004, the judiciary reinterpreted the Brazilian
+Constitution and unexpectedly changed the number of councilors in several
+municipalities. Until then, cities could freely determine their legislature
+size, but in March 2004 the Supreme Electoral Court created population
+thresholds and added one councilor to each set of 47,619 inhabitants. Around
+these cutoffs, the decision represented an exogenous change in city council
+size, allowing us to investigate the effects of increasing the number of local
+legislators in Brazil.
+
+We find that larger city councils changed the composition of mayoral coalitions
+and the number of appointed bureaucrats in the municipality. The extra city
+councilor had a 91 percent chance of belonging to the mayor's pre-electoral
+coalition. With a larger coalition, mayors face lower bargaining costs and are
+able to boost public investments with fewer constraints. Each additional
+legislator also leads to 104 new appointed bureaucrats, and research shows that
+political appointees civil servants improve public service provision and
+enhance accountability in Brazil \citep{toral2019benefits}.
+
+To provide further evidence for our mechanisms, we surveyed 174 former
+councilors who served during the 2005-2008 term, the period we analyse in this
+paper. They confirm that mayors indeed use bureaucratic appointments and
+political favors to secure legislative support. As our formal model shows,
+bargaining with councilors requires offering transfers to the representatives.
+By asking councilors what they would like to provide to voters, we find that
+councilors mainly demand job appointments, as these increase their reelection
+prospects and improve municipal welfare. These findings are in line with
+quantitative results from a novel dataset we built with 346,553 laws passed in
+63 municipalities within ten thousand inhabitants away from the cutoffs. We see
+that legislation in municipalities both on the left- and on the right-hand side
+of the cutoffs mention public goods provision. However, municipalities with
+larger city councils have 15 percent more proposals about public goods
+provision, which is consistent with our argument.
+
+Finally, we show that the increase in legislature size significantly impacts
+municipal education and health care. Increasing the city council size by one
+legislator lowers infant mortality by 2.01 children per one thousand infants
+born and reduces postneonatal mortality by 0.90 children per one thousand
+infants that survived their first 28 days. Larger councils also increase
+enrollment by 2.58 children in elementary education classrooms without reducing
+school quality. These services are crucial for citizen welfare and result from
+eased bargaining between the mayor and the city council.
+
+This paper contributes to four strands of the literature. First, this paper
+dialogues with a large literature on multilateral bargaining. Repeated models
+of multilateral bargaining started with \citet{baron1989bargaining}, who
+extended the bilateral bargaining game proposed by
+\citet{rubinstein1982perfect} to more than two players. Several papers followed
+\citet{baron1989bargaining} and included endogenous recognition power, the size
+of the required majority, and partisanship in the model
+\citep{agranov2020persistence, baranski2020determinants,
+calvert2005legislative, choate2019partisan}.\footnote{See
+\citet{eraslan2019legislative} for a comprehensive review of multilateral
+bargaining and \citet{ray2015coalition} for a review on coalition formation.}
+In this paper, we extend the \citet{baron1989bargaining} model under closed
+rules and add the mayor's first move and political partisanship. We consider
+partisanship as a zero-sum effect that is positive for politicians aligned with
+the mayor and negative otherwise. This paper investigates the often overlooked
+effect of legislature size on the bargaining equilibrium strategies.
+
+Second, this paper contributes to the literature on the effects of larger
+legislatures in service provision. Following the seminal contribution by
+\citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
+increase the legislative pressure for providing targeted public goods to local
+supporters at the expense of the entire polity \citep{freire2021legislature}.
+This question has become more relevant since legislature size has increased
+consistently over time \citep{gerring2020population}. The corollary of the "law
+of $1/n$" is that increasing legislature size promotes excessive public
+spending, regardless of the partisan makeup of the legislature
+\citep{GilliganMatsusaka2001}.\footnote{\citet{PrimoSnyder2008} show that
+legislature size may result in positive or negative expenditures, depending on
+factors such as the degree that local public goods can exclude non-locals or
+deadweight costs associated with taxation.} In the US metaphor, this would
+explain significant infrastructure spending in smaller districts. However, the
+"law of $1/n$" literature rarely mentions the relationship between public goods
+provision and welfare. This paper is one of the first to study how the number
+of local legislators affects welfare. Our model provides a theoretical
+expectation based on the chances of electing a politician aligned with the
+mayor. The empirical estimates confirm our theoretical predictions, with the
+additional fact that legislature size has a null effect on expenditures in
+Brazil.
+
+Third, our article also contributes to the growing literature on municipal
+partisan politics. Most papers in this field estimate the effects of the
+mayor's party on political outcomes. For instance, \citet{de2016mayoral} and
+\citet{gerber2011mayors} find differences in governance when comparing
+Democratic and Republican mayors. Specifically about Brazil,
+\citet{gouvea2021partisanship} shows that social policy expenditure increase
+with left-wing mayors. \citet{frey2021legislature}, using discontinuities in
+city council size after the 2009 constitutional amendment that reverted the
+thresholds we study here, shows that changes in council size lower the support
+for candidates backed by the municipal mayors. Our paper reinforces the view
+that partisanship matters locally, even in countries with weak ideological
+linkage.
+
+Finally, this paper contributes to the literature on the causes and effects of
+legislature sizes. While most papers on legislature size analyse the trade-off
+between representation and efficiency \citep{frederick2008people,
+jacobs2015explaining, muzzio1989size, Stigler1976}, recent articles have
+explored the effects of legislature size on lawmaking and partisanship in
+further detail. \citet{kirkland2014chamber} shows that larger legislatures make
+it harder for politicians to know and collaborate with each other, so they rely
+more heavily on party cues and committee structures. In considering the causes
+of changes in legislature sizes, \citet{jacobs2015explaining} show that
+population shifts increase and economic crises decrease the number of
+legislators. \citet{marland2019fewer} questions the economic crises mechanism,
+showing that political elites shrink legislatures mostly to signal to the
+public the priority of their austerity agenda. In this article, we show that
+council size affects welfare by changing the partisan composition of
+the legislatures.
 
@@
 
-The design of institutions is crucial for long term welfare \citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions} and democratic consolidation \citep{gandhi2019institutional, lijphart2018institutional}.
-One particular problem that each polity faces is determination of the size of its legislative bodies.
-The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{muzzio1989size, Stigler1976}.
-
-The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, rush2013conclusion, Stigler1976, taagepera1972size}.
-Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases.
-This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}.
-Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures.
-The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{kirkland2014chamber, rush2013conclusion}.
-It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}.
-Balancing these two incentives is crucial for the optimal legislative composition \citep{auriol2012optimal, taagepera1972size}.
-
-However, the legislature size scholarship has overlooked two questions: first, does legislature size matter in contexts where the legislative bodies are not the pivotal decision-maker?
-And second, what is the ultimate effect of legislature size on welfare?
-On the one hand, legislature size's effects on welfare represent a significant gap in the political economy literature.
-It is likely generated by the predominance of the "law of 1/n" scholarship, which emphasized larger legislatures' overspending consequence.
-Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}.
-Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2020larger} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016.
-These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.
-
-Despite the division of power, the Executive dominates the debates on public service provision in most mayor-council (or presidential) systems.
-For instance, while the New York Times cited the New York City Mayor Bill De Blasio 2,084 times in 2021, it mentioned the 49 seating city councilors 440 times in the same period.
-To avoid the COVID crisis when the Executive was in the spotlight, we expanded the search for the past five years.
-In this new search, Bill De Blasio was mentioned 8,978 while the 49 seating city councilors were mentioned 2,046 times.\footnote{These figures were computed using the Dow Jones Factiva Database in November 2021.} The mayor was cited, on average, over four times more than all the city councilors combined.
-This Executive dominance has implications for policymaking, as coalitions and affinity with the Executive are going to be crucial for service provision \citep{buenodemesquita2005logic}.
-
-In a mayor-council setting, consider a strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor has the prerogative of proposing a vector of policies on which city councilors vote.
-The provision of public goods is then a bargain between the mayor and the city council.
-Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.
-
-The city council votes the mayor's proposal, and if councilors accept it, the proposal is implemented.
-Otherwise, a reversal policy takes place.
-Reversal policy in this context means that the mayor's proposal failed to secure the majority of council votes.
-The decision process then leaves the mayor's office and it is transferred to the council.
-The types of reversal policies are crucial for our argument, as it changes the relative strength of the council when they bargain with the mayor.
-We investigate two types of reversal policies: a baseline reversal with no parties and a hybrid mechanism with partisan and non-partisan concerns.
-The differences between these two mechanisms are that the non-partisan councilors only care about rents, while partisan councilors care about both rents and policy.
-
-The mayor must convince at least half of the city councilors to support her policy proposals.
-Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, that is, the individuals who have a say in the mayor's policy proposals, are the $N$ city councilors.
-The winning coalition, the minimum number of members that must be convinced to implement the policy, is equal to half of the selectorate ($N/2$).
-City councilors are motivated by policy concerns $p$ and transfers received from the mayor or the councilor nominated as the proposer \textbf{x}.
-We leave the definition of these transfers open, as this allows us to analyze how mayors combine transfers with other incentives to pressure city councilors.
-Exemples of transfers are granting electoral favors, favoring clientelistic brokers, spending in areas that the councilor has political or personal interests, providing portfolio (municipal offices) and public jobs within the municipal bureaucracy, or even giving campaign contributions and bribes.
-The use of transfers to influence the councilors' choices generate a bargaining cost of $C_G$.
-Bargaining costs vary according to the reversal mechanism and the size of the legislature.
-
-Finally, after learning the bargaining costs, the mayor provides a level of public goods provision $g$ and pockets rents $r$.
-Public goods provision helps the mayor to get reelected.
-Rents are for direct mayor's consumption, and they do not contribute to the mayor's electoral success.\footnote{This model, similar to \citet{cowen1994rent} and \citet{buenodemesquita2005logic}, combines public goods provision and rent extraction.
-For a dynamic bargaining model that incorporates transfers to districts and public goods provision, see \citet{battaglini2012legislative}.} This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection.
-Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.
-The probability of reelection is multiplied by the benefit from holding office $B_M > 0$.
-This benefit captures the tangible and intangible gains that the mayor receives from holding the public office.
-We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to saying that mayors strongly prefer to be reelected.
-If the mayor's policy proposal is approved, then the expected utility for the mayor is:
+Institutional design has a major impact on long-term welfare
+\citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions}
+and democratic consolidation \citep{gandhi2019institutional,
+lijphart2018institutional}. One particular problem that all polities face is
+how to determine the optimal size of their legislative bodies. The literature
+on this topic is extensive, and modern attempts to provide a solution to the
+legislature size problem started in the early eighteenth century with
+the Federalists versus Anti-Federalists debates \citep{muzzio1989size,
+Stigler1976}.
+
+The literature on legislature size highlights that the number of legislators
+causes tension between representation and efficiency
+\citep{frederick2008people, jacobs2015explaining, muzzio1989size,
+rush2013conclusion, Stigler1976, taagepera1972size}. Larger legislatures
+improve representation as both the election thresholds and the ratio of
+population-per-politician decrease, which facilitate the electoral success of
+ethnic and political minorities \citep{allenrepresentation,
+gerring2020population}. However, better representation is often countered by
+the decline in efficiency in larger legislatures \citep{Weingastetal1981}. The
+enlarged size makes it harder for members to coordinate and collaborate without
+partisanship and legislative structures \citep{kirkland2014chamber,
+rush2013conclusion}. It also increases the potential number of veto players,
+decreasing policymaking efficiency \citep{tsebelis2002veto}. Balancing these
+two incentives is crucial for the optimal legislative composition
+\citep{auriol2012optimal, taagepera1972size}.
+
+This literature has often overlooked two important questions. First, does
+legislature size matter in contexts where legislative bodies are not the
+pivotal decision-maker? And second, what is the ultimate effect of legislature
+size on welfare? These gaps are likely generated by the predominance of the
+"law of 1/n" scholarship in political economy debates, which focus mainly on
+the relationship between legislature size and overspending. Since
+\citet{Weingastetal1981}, 30 papers have systematically tested the effects of
+legislature size on government expenditures \citep{freire2021legislature}. Of
+these papers, only \citet{lewis2019legislature} investigates its effects on
+welfare, showing that larger legislatures have a negative welfare
+effect.\footnote{\citet{koppel2004public} also shows, using a repeated game
+where the proposal prerogative rotates in a legislature, that larger
+legislatures increase the chances of non-cooperative outcomes, lowering public
+goods provision.} \citet{frey2021legislature} analyzes the Brazilian case after
+the 2009 legislature size change and finds a null effect in service provision
+from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} finds that in the US
+legislature size is associated primarily with higher spending on geographically
+concentrated benefits, such as education and highways. These results suggest
+that the legislature size and welfare nexus needs a dedicated theoretical and
+empirical assessment.
+
+Despite the importance of legislatures, the executive still dominates the
+public debate on public service provision in most mayor-council (or
+presidential) systems. For instance, while in 2021 the New York Times cited
+Mayor Bill De Blasio 2,084 times, it mentioned the 49 seating city councilors
+only 440 times in the same year. When we expand the search for the past five
+years, we see that De Blasio was mentioned 8,978 while the 49 seating city
+councilors were mentioned 2,046 times.\footnote{We computed these figures using
+the Dow Jones Factiva Database in November 2021.} On average, the mayor was
+cited four times more often than all the city councilors combined. This
+executive dominance has implications for policymaking, as coalitions and
+affinity with the executive are going to be crucial for service provision
+\citep{buenodemesquita2005logic}.
+
+## Model Setup
+
+In a mayor-council setting, consider a strategic interaction between a mayor
+($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
+The mayor has the prerogative of proposing a vector of policies on which city
+councilors vote. The provision of public goods is then a bargain between the
+mayor and the city council. Policy proposals are a combination of public goods
+provision $g$, rents for the mayor $r$, and a vector of transfer for city
+councilors \textbf{x}.
+
+The city council votes the mayor's proposal, and if councilors accept it, the
+proposal is implemented. Otherwise, a reversal policy takes place. Reversal
+policy in this context means that the mayor's proposal failed to secure the
+majority of council votes. The decision process then leaves the mayor's office
+and is transferred to the council. The types of reversal policies are crucial
+for our argument, as they change the relative strength of the council when
+legislators bargain with the mayor. We investigate two types of reversal
+policies: A baseline reversal with no parties and a hybrid mechanism with
+partisan and non-partisan concerns. The differences between these two
+mechanisms are that the non-partisan councilors only care about rents, while
+partisan councilors care about both rents and policy.
+
+The mayor must convince at least half of the city councilors to support her
+policy proposals. Similar to \citet{buenodemesquita2005logic}, we assume that
+the selectorate, that is, the individuals who have a say in the mayor's policy
+proposals, are the $N$ city councilors. The winning coalition, the minimum
+number of members that must be convinced to implement the policy, is equal to
+half of the selectorate ($N/2$). City councilors are motivated by policy
+concerns $p$ and transfers received from the mayor or the councilor nominated
+as the proposer \textbf{x}. We leave the definition of these transfers open, as
+this allows us to analyze how mayors combine transfers with other incentives to
+pressure city councilors. Exemples of transfers are granting electoral favors,
+funding clientelistic brokers, spending in areas that the councilor has
+political or personal interests, providing portfolio (municipal offices) and
+public jobs within the municipal bureaucracy, or even giving campaign
+contributions and bribes. The use of transfers to influence the councilors'
+choices generate a bargaining cost of $C_G$. Bargaining costs vary according to
+the reversal mechanism and the size of the legislature.
+
+Finally, after learning the bargaining costs, the mayor provides a level of
+public goods provision $g$ and pockets rents $r$. Public goods provision helps
+the mayor to get reelected. Rents are for the mayor's direct consumption and do
+not contribute to the mayor's electoral success.\footnote{This model, similar
+to \citet{cowen1994rent} and \citet{buenodemesquita2005logic}, combines public
+goods provision and rent extraction. For a dynamic bargaining model that
+incorporates transfers to districts and public goods provision, see
+\citet{battaglini2012legislative}.} This makes the mayor's expected utility a
+sum of the gains from rents and the benefits from reelection. Both the
+utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are
+concave functions, meaning that more rents or public goods increase the utility
+at a decreasing rate. The probability of reelection is multiplied by the
+benefit from holding office $B_M > 0$. This benefit captures the tangible and
+intangible gains that the mayor receives from holding the public office. We
+assume that the benefits are high enough to rule out an equilibrium with only
+rents and transfers, which is equivalent to saying that mayors strongly prefer
+to be reelected. If the mayor's policy proposal is approved, then the expected
+utility for the mayor is:
 
@@
 The policy choices of the mayor are subject to municipal budget constraints.
-The municipality has $R > 0$ resources and cannot run debts, meaning that the budget must be balanced.
-We also assume that there are enough resources for the mayor to govern.
-
-Let $C_G$ be the bargaining costs. The budget balance constraint requires that the offers the mayor makes to the city councilors must satisfy the following inequality:
+The municipality has $R > 0$ resources and cannot run debts, meaning that the
+budget must be balanced. We also assume that there are enough resources for the
+mayor to govern.
+
+Let $C_G$ be the bargaining costs. The budget balance constraint requires that
+the offers the mayor makes to the city councilors must satisfy the following
+inequality:
 
@@
 
-The expected utility for the city councilors depends on the reversal policy.
-In the baseline non-partisan reversal, when the council rejects the mayor's proposal, a reversal stage starts with resources diminishing by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly.
-The selected councilor becomes the new proposer.
-If her proposal is accepted, it is implemented.
-If councilors reject the offer again, the budget shrinks by $\delta$, and another city councilor is nominated to propose.
-The process repeats until a proposal is finally accepted.
-
-We now consider a situation that combines both partisan and non-partisan legislature concerns.
-Each councilor has a party affiliation.
-Party affiliations are mutually exclusive, and if a city councilor is aligned with the mayor's party, then she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$.
-Otherwise, the city councilor belongs to the opposition $O = \{1, 2, \cdots, N \} \setminus G$.
-The mayor's policy generates a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends on the party affiliation of the councilor.\footnote{One example of partisan benefits is that, as the mayor shares partisan ties with members of the government coalition, a fraction of the public goods provision can be claimed by councilors as their contribution.
-We propose an extension in the Full Supplementary Materials (available in [REDACTED FOR PEER REVIEW]) that assumes $p = \phi g$, where $\phi$ is the fraction of the public goods provision that can be credit claimed by the city councilor aligned with the mayor.} If councilors reject the mayor's proposal, no public goods are provided ($p=0$).
-Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods.\footnote{In the Full Supplementary Materials, we consider a version of the model where public goods provision depends on the party affiliation of the proposer so that it affects choices in any potential history of the game.
-The equilibrium public goods provision level is even higher than in the model presented here, as city councilors prefer to approve the mayor's proposal than run the risk of an opposition member becoming the proposer.}
+The expected utility for the city councilors depends on the type of reversal
+policy. In the baseline non-partisan reversal, when the council rejects the
+mayor's proposal, a reversal stage starts with resources diminishing by a
+factor of $\delta \in (0,1)$ and the random selection of one councilor. The
+selected councilor becomes the next proposer. If the new proposal is accepted,
+it is implemented. If councilors reject the offer again, the budget shrinks by
+$\delta$ and another city councilor is nominated to propose. The process
+repeats until a proposal is finally accepted.
+
+We now consider a situation that combines both partisan and non-partisan
+legislature concerns. Each councilor has a party affiliation. Party
+affiliations are mutually exclusive, and if a city councilor is aligned with
+the mayor's party, then she belongs to the government coalition $G \subset \{1,
+2, \cdots, N \}$. Otherwise, the city councilor belongs to the opposition $O =
+\{1, 2, \cdots, N \} \setminus G$. The mayor's policy generates a political
+value of $p > 0$ for the councilors, and whether it adds or subtracts from the
+councilor's utility depends on the party affiliation of the
+councilor.\footnote{One example of partisan benefits is that, as the mayor
+shares partisan ties with members of the government coalition, a fraction of
+the public goods provision can be claimed by councilors as their contribution.
+We propose an extension in the Online Supplementary Materials, which assumes $p
+= \phi g$, where $\phi$ is the fraction of the public goods provision that can
+be credit claimed by the city councilor aligned with the mayor.} If councilors
+reject the mayor's proposal, no public goods are provided ($p=0$). Moreover, in
+equilibrium, we assume that city councilors would prefer to receive transfers
+instead of providing public goods.\footnote{In the Online Supplementary
+Materials, we consider a version of the model in which public goods provision
+depends on the party affiliation of the proposer so that it affects choices in
+any potential history of the game. In equilibrium, the level of public goods
+provision is even higher than in the model presented here, as city councilors
+prefer to approve the mayor's proposal than run the risk of an opposition
+member becoming the proposer.}
 
@@
 If the offer is accepted, it is implemented.
-If rejected, the reversal policy stage restart.\footnote{In section A.1 of the Supplementary Materials, we solve three reversal mechanisms.
-The two we present here, plus a mechanism with only political concerns.}
+If rejected, the reversal policy stage restarts.\footnote{In section A.1 of the Supplementary Materials, we solve three reversal mechanisms.
+We include the two mechanisms we present here, plus a third mechanism with only political concerns.}
 \end{enumerate}
 
-The solution concept we use in this model is the subgame perfect Nash equilibrium.
-This game requires that the strategies follow a Nash equilibrium in each subgame.
-We find the solution using backward induction.
-In the model with infinitely repeated proposals, any strategy can be shown to be a Nash equilibrium.
-Thus, a natural assumption is to extend the equilibrium concept to require the equilibrium to be stationary.
-A stationary subgame perfect equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should take the same offer at time $k$ \citep{rubinstein1982perfect}.
-Stationarity gives us a method to find a proposal that would be accepted at any stage of the game.
-Hence, we can characterize a sequence of offers for each point $k$ in time.
-For the mayor, the optimal offer is at $k=0$, representing a no delay in policy implementation.
-We assume that players have no dominated strategies, even when there is insufficient support for the policy.
-
-For the solution to be of general interest, we solve the bargaining costs for the expected number of opposition and government-aligned city councilors.
-This is because the solution for each fixed number of opposition and government councilors does not help us understand the overall relationship between council size and bargaining costs.
+The solution concept we use in this model is the subgame perfect Nash
+equilibrium. This game requires that the strategies follow a Nash equilibrium
+in each subgame. We find the solution using backward induction. In the model
+with infinitely repeated proposals, any strategy can be shown to be a Nash
+equilibrium. Thus, a natural assumption is to extend the equilibrium concept to
+require the equilibrium to be stationary. A stationary subgame perfect
+equilibrium requires that, at each given point of the game, if a politician
+accepts an offer at time $k+1$, she should take the same offer at time $k$
+\citep{rubinstein1982perfect}. Stationarity gives us a method to find a
+proposal that would be accepted at any stage of the game. Hence, we can
+characterize a sequence of offers for each point $k$ in time. For the mayor,
+the optimal offer is at $k=0$, representing a no delay in policy
+implementation. We assume that players have no dominated strategies, even when
+there is insufficient support for the policy.
+
+For the solution to be of general interest, we solve the bargaining costs for
+the expected number of opposition and government-aligned city councilors. This
+is because the solution for each fixed number of opposition and government
+councilors does not help us understand the overall relationship between council
+size and bargaining costs.
 
@@
 
-Solving the game by backward induction requires us to start with the councilors' strategies.
-However, to conserve space, assume that we solved the game for the councilors and found the equilibrium bargaining costs $C_G(N)$ when there are $N$ city councilors.
-We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor.
-The mayor benefits from public goods provision, as it increases the chances of her reelection.
-However, she prefers to invest as minimum as necessary in public goods and extract the remaining resources as political rents.
-The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.
+Solving the game by backward induction requires us to start with the
+councilors' strategies. However, to conserve space, assume that we solved the
+game for the councilors and found the equilibrium bargaining costs $C_G(N)$
+when there are $N$ city councilors. We now derive the optimal rents ($r$) and
+public goods provision ($g$) proposed by the mayor. The mayor benefits from
+public goods provision, as it increases the chances of her reelection. However,
+she prefers to invest as minimum as necessary in public goods and extract the
+remaining resources as political rents. The mayor's objective is to maximize
+her expected utility, subject to the municipal budget constraint.
 
@@
 
-In equilibrium, the budget binds, and the first-order condition for optimal public goods provision indicates that the marginal costs of providing public goods is equal to the marginal benefits of reelection:
+In equilibrium, the budget binds, and the first-order condition for optimal
+public goods provision indicates that the marginal costs of providing public
+goods is equal to the marginal benefits of reelection:
 
@@
 
-The optimal level of public goods provision equates the marginal gains accrued from rents with the marginal benefits from reelection.
+The optimal level of public goods provision equates the marginal gains accrued
+from rents with the marginal benefits from reelection.
 
@@
 
-All proofs are in section A.1 of the Supplementary Materials.
-The proof's intuition involves finding what happens to the mayor's marginal utility when we increase both $g$ and $N$.
-As $N$ increases discretely on a complete lattice, we use monotone comparative statics to derive the conditions for increasing differences \citep{milgrom1994monotone, ashworth2006monotone}.
-Increasing differences mean that higher $N$ leads to higher equilibrium $g$.
-
-Proposition \ref{prop1} provides the first empirical hypothesis to test: \textit{if the bargaining costs decrease when the legislature size increases, then public goods provision increases when the legislature size increase}.
-Now we study each reversal mechanism to determine the condition under which the bargaining costs decrease when legislature size increases.
+All proofs are in section A.1 of the Supplementary Materials. The proof's
+intuition involves finding what happens to the mayor's marginal utility when we
+increase both $g$ and $N$. As $N$ increases discretely on a complete lattice,
+we use monotone comparative statics to derive the conditions for increasing
+differences \citep{milgrom1994monotone, ashworth2006monotone}. Increasing
+differences mean that higher $N$ leads to higher equilibrium $g$.
+
+Proposition \ref{prop1} provides our first empirically testable hypothesis:
+\textit{if bargaining costs decrease when legislature size increases,
+then public goods provision increases when legislature size increases}. Now
+we study each reversal mechanism to determine the condition under which the
+bargaining costs decrease when legislature size increases.
 
@@
 
-In the non-partisan reversal, we assume that when the council rejects the mayor's office, a reversal stage starts with the random selection of one councilor.
-This formulation is similar to the closed rules proposal in \citet{baron1989bargaining}.
-To find a stationary subgame perfect Nash equilibrium, suppose that there were $k-1$ rejections, and the game is at the $k$-th stage.
-A councilor accepts the proposer's offer if, and only if, to accept the offer at $k$ is better than or equal to wait until the next stage $k+1$.
-If the offer is $x_i$, then:
+In the non-partisan reversal mechanism, we assume that when the council rejects
+the mayor's office, a reversal stage starts with the random selection of one
+councilor. This formulation is similar to the closed rules proposal in
+\citet{baron1989bargaining}. To find a stationary subgame perfect Nash
+equilibrium, suppose that there were $k-1$ rejections, and the game is at the
+$k$-th stage. A councilor accepts the proposer's offer if, and only if, to
+accept the offer at $k$ is better than or equal to wait until the next stage
+$k+1$. If the offer is $x_i$, then:
 
@@
 
-We place the offer on the left-hand side.
-There are two components on the right-hand side.
-The first is the amount that the councilor $i$ gets when she is the proposer.
-It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers she makes to convince half of the councilors.
-The second part represents the gains if the councilor rejects the current received offer but still gets an offer in the following round.
-It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the transfer amount.
-Note that the offer the councilor makes as the proposer is the same as the offer she wants to receive.
-This is because the city councilors are exchangeable.
-The solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution).
-After some algebra, the offer $x_i$ must be greater than or equal to:
+We place the offer on the left-hand side. There are two components on the
+right-hand side. The first is the amount that the councilor $i$ gets when she
+is the proposer. It is equal to the chance that she is recognized as the
+proposer times the budget in the next round minus the offers she makes to
+convince half of the councilors. The second part represents the gains if the
+councilor rejects the current received offer but still gets an offer in the
+following round. It is equal to the chance that she is not recognized as the
+proposer times the chance that she receives a transfer times the transfer
+amount. Note that the offer the councilor makes as the proposer is the same as
+the offer she wants to receive. This is because the city councilors are
+exchangeable. The solution is symmetric for all councilors receiving an offer
+(this means that, without loss of generality, we could have dropped the $i$ in
+the solution). After some algebra, the offer $x_i$ must be greater than or
+equal to:
 
@@
 
-The proposer always offers the minimum required to get the proposal approved. In this case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.
-
-Proceeding backwards, at the mayor's proposal stage $k=0$ the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors.
-In this context, the bargaining costs for the mayor are:
+The proposer always offers the minimum required to get the proposal approved.
+In this case, the offer at any given stage $k$ is going to be equal to
+$\underline{x}(k, N)$.
+
+Proceeding backwards, at the mayor's proposal stage $k=0$ the mayor is going to
+offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the
+councilors. In this context, the bargaining costs for the mayor are:
 
@@
 \begin{proposition}
-In the baseline non-partisan reversal, bargaining costs always increase when the size of the legislature increases.
+In the baseline non-partisan reversal, bargaining costs always increase when legislature size increases.
 \end{proposition}
 
-The intuition for the results is that every additional councilor demands more resources from the mayor.
-Thus, more councilors represent higher bargaining costs.
-And if the bargaining costs increase with legislature size, then any increase in public goods provision associated with legislature size has come from a different mechanism.
-Below we show that partisanship is the key to understand how this relationship works.
+The intuition for the results is that every additional councilor demands more
+resources from the mayor. Thus, more councilors represent higher bargaining
+costs. And if the bargaining costs increase with legislature size, then any
+increase in public goods provision associated with legislature size has come
+from a different mechanism. Below we demonstrate that partisanship is the key
+to understand how this relationship works.
 
@@
 
-In a reversal mechanism that incorporates partisan and non-partisan motivations, a city councilor aligned with the government favors the mayor's offer if:
+In a reversal mechanism that incorporates partisan and non-partisan
+motivations, a city councilor aligned with the government favors the mayor's
+offer if:
 
@@
 
-An opposition politician, on the other hand, favors the mayor's offer if, and only if:
+An opposition politician, on the other hand, favors the mayor's offer if, and
+only if:
 
@@
 
-We decompose these costs into two components.
-First, the costs in terms of rents.
-Second, the costs (or benefits) from political alignment.
-In this context, the bargaining costs depend on the mayor's offers for councilors in her coalition versus the mayor's proposals for councilors in the opposition.
-As the ex-ante chance of an opposition member being elected is equal to $1-\gamma$, after taking the weighted averages these costs become:
+We decompose these costs into two components. First, the costs in terms of
+rents. Second, the costs (or benefits) from political alignment. In this
+context, the bargaining costs depend on the mayor's offers for councilors in
+her coalition versus the mayor's proposals for councilors in the opposition. As
+the ex-ante chance of an opposition member being elected is equal to
+$1-\gamma$, after taking the weighted averages these costs become:
 
@@
 \begin{proposition}
-In the reversal mechanism that incorporates partisanship, if $\gamma \geq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right] \equiv \underline{\gamma}$, then the bargaining costs decrease when the legislature size increases.
+In the reversal mechanism that incorporates partisanship, if $\gamma \geq \dfrac{1}{p}\left[ \dfrac{1}{(2N+1)(2N+3)} \right] \equiv \underline{\gamma}$, then bargaining costs decrease when legislature size increases.
 \end{proposition}
 
-The intuition for the proof is that as partisanship influences the costs and benefits of legislators, more government-aligned councilors make it cheaper to govern.
-When the partisan benefit is higher than the additional cost that a legislator generates, adding a councilor will benefit mayors if the councilor has a higher chance of sharing the same party as the mayor.
-Therefore, a higher probability of electing a legislator aligned with the mayor reverts into lower bargaining costs.
-
-Also, the threshold $\underline{\gamma}$ that captures the probability of electing a mayor-aligned policitian decreases along with the political value of policy $p$ and the size of the legislature $N$.
-This means that intensive partisanship and larger legislatures make it easier to satisfy the electoral threshold.
+The intuition for the proof is that as partisanship influences the costs and
+benefits of legislators, more government-aligned councilors make it easier for
+the mayor to govern. When the partisan benefit is higher than the additional
+cost that a legislator generates, adding a councilor will benefit mayors if the
+councilor has a higher chance of sharing the same party as the mayor.
+Therefore, a higher probability of electing a legislator aligned with the mayor
+reverts into lower bargaining costs.
+
+Also, the threshold $\underline{\gamma}$ that captures the probability of
+electing a mayor-aligned policitian decreases along with the political value of
+policy $p$ and the size of the legislature $N$. This means that intensive
+partisanship and larger legislatures make it easier to satisfy the electoral
+threshold.
 
@@
 
-Our model provides two empirically testable hypotheses.
-Consider a municipality with a city council comprised of $N$ legislators.
-Then the city increases the size of the council to $N+1$.
-Thus, in a partisan setting:
+Our model provides two empirically testable hypotheses. Consider a municipality
+with a city council comprised of $N$ legislators. Then the city increases the
+size of the council to $N+1$. Thus, in a partisan setting:
 
@@
 
-In 2004, Brazil comprised 5,560 municipalities.
-According to the Brazilian Constitution, each city must provide health care, primary education, transportation, and infrastructure to its citizens.
-Municipalities have the authority to enact local laws and collect taxes on housing and services.
-However, their room for fiscal manipulation is limited.
-On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%.
-This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments.
-
-With regards to their political organization, municipalities have one mayor and one city council.
-Citizens choose their representatives by direct vote in the same election.
-Mayors oversee the provision of public services and propose laws and amendments to the tax code.
-Proposals submitted by the mayor are subject to the approval of the city council.
-Councilors, in turn, have two primary duties.
-First, they should discuss and vote on legislation put forward by the mayors or by their peers.
-Second, they oversee the public budget and sanction mayors who do not comply with fiscal legislation.
-Councilors and mayors also provide an array of public and personal services for their constituents, such as helping voters access public hospitals, facilitating school enrollment, and even paying their voters' utility bills \citep{lopez2017legisladores, nichter2011electoral}.
-
-Until 2004, there was no specific regulation on the size of city councils.
-The 1988 Brazilian Constitution set only broad guidelines about the number of council seats in each municipality, which allowed cities to determine how many legislators they should have in their local chambers.
-This led to severe imbalances in the proportion of representatives per citizen across the country.
-For instance, the Nova Russas municipality had 30,009 inhabitants and 21 councilors, accounting for one legislator per 1,429 citizens.
-In contrast, the city of Sorocaba had only 15 councilors for 528,735 inhabitants, that is, one legislator per 35,249 citizens.
-In 2003, this malapportionment problem gained national visibility when Mira Estrela, a small municipality with only 2,651 residents, reduced its city council from 11 to 9 seats because of fiscal considerations.
-The change motivated a legal dispute that reached the Brazilian Supreme Court.
-The Court favored the city's decision and ruled that the size of every local council should correspond to precise population thresholds.
-
-Following the ruling of the Supreme Court, in March 2004 the Supreme Electoral Court established a series of population cutoffs for all municipal legislatures.
-Following the Brazilian Constitution, the Court specified that cities with up to one million residents should have between 9 and 21 legislators.
-The number of seats was allocated as follows.
-Each town starts with nine councilors, then adds one legislator for every 47,619 inhabitants until their councils reach 21 members.
-This threshold implies that cities with a population between 571,428 and one million should all have the same number of legislators, that is, 21 of them.
-Conversely, cities between one and four million inhabitants should have at least 33 councilors, and this number increases up to 41 members following the previous formula of one additional legislator per 47,619 inhabitants.
-
-This decision makes Brazil the ideal testing ground for our theory.
-Although an endogenous decision motivated the Electoral Court ruling, the population cutoffs created sharp discontinuities in the distribution of local council seats.
-Cities close to the cutoffs had very similar characteristics, but those just above the threshold gained a new legislator.
-Moreover, cities could not self-select into any group, as their population estimates were calculated using the 2003 projections by the Brazilian Census Bureau (IBGE).
-This change in council size also happened only seven months before the election, making it impossible for candidates to adjust their service provision strategies for the 2004 election.
-Therefore, the ruling allows us to study the effect of larger legislatures on public service provision during the 2005-2008 term while holding all else constant.
+In 2004, Brazil comprised 5,560 municipalities. According to the Brazilian
+Constitution, each city must provide health care, primary education,
+transportation, and infrastructure to its citizens. Municipalities have the
+authority to enact local laws and collect taxes on housing and services.
+However, their room for fiscal manipulation is limited. On average, municipal
+taxes account for only 5\% of the local budgets, while mandatory transfers from
+state and federal governments correspond to the remaining 95\%. This reduces
+the ability of municipal legislators to effectively increase local spending,
+which makes improvements in local services dependent only on the composition of
+their local investments.
+
+With regards to their political organization, municipalities have one mayor and
+one city council. Citizens choose their representatives by direct vote in the
+same election. Mayors oversee the provision of public services and propose laws
+and amendments to the tax code. Proposals submitted by the mayor are subject to
+the approval of the city council. Councilors, in turn, have two primary duties.
+First, they should discuss and vote on legislation put forward by the mayors or
+by their peers. Second, they oversee the public budget and sanction mayors who
+do not comply with fiscal legislation. Councilors and mayors also provide an
+array of public and personal services for their constituents, such as helping
+voters access public hospitals, facilitating school enrollment, and even paying
+their voters' utility bills \citep{lopez2017legisladores,
+nichter2011electoral}.
+
+Until 2004, there was no specific regulation on the size of city councils. The
+1988 Brazilian Constitution set only broad guidelines about the number of
+council seats in each municipality, thus allowing cities to determine how many
+legislators they should have in their local chambers. This led to severe
+imbalances in the proportion of representatives per citizen across the country.
+For instance, the Nova Russas municipality had 30,009 inhabitants and 21
+councilors, accounting for one legislator per 1,429 citizens. In contrast, the
+city of Sorocaba had only 15 councilors for 528,735 inhabitants, that is, one
+legislator per 35,249 citizens. In 2003, this malapportionment problem gained
+national visibility when Mira Estrela, a small municipality with only 2,651
+residents, reduced its city council from 11 to 9 seats because of fiscal
+considerations. The change motivated a legal dispute that reached the Brazilian
+Supreme Court. The Court favored the city's decision and ruled that the size of
+every local council should correspond to precise population thresholds.
+
+Following the ruling of the Supreme Court, in March 2004 the Supreme Electoral
+Court established a series of population cutoffs for all municipal
+legislatures. Following the Brazilian Constitution, the Court specified that
+cities with up to one million residents should have between 9 and 21
+legislators. The number of seats was allocated as follows. Each town starts
+with nine councilors, then adds one legislator for every 47,619 inhabitants
+until their councils reach 21 members. This threshold implies that cities with
+a population between 571,428 and one million should all have the same number of
+legislators, that is, 21 of them. Conversely, cities between one and four
+million inhabitants should have at least 33 councilors, and this number
+increases up to 41 members following the previous formula of one additional
+legislator per 47,619 inhabitants.
+
+Brazil also adopts a unique formula to allocate seats, which combines the Hare
+quota and the D'Hondt method and favors larger parties
+\citep{nicolau2015sistemas}. This poses a major obstacle for small parties to
+reach the electoral quorum, so they often join party coalitions to improve
+their chances of winning legislative seats \citep[p. 68]{Ames2001}. In Brazil,
+mayors are usually members of the largest coalitions
+\citep{poulsen2018political}, thus there is an incentive for candidates to side
+with the mayor before and after the election.
+
+These factors make Brazil the ideal testing ground for our theory. Although an
+endogenous decision motivated the Electoral Court ruling, the population
+cutoffs created sharp discontinuities in the distribution of local council
+seats. Cities close to the cutoffs had very similar characteristics, but those
+just above the threshold gained a new legislator. Moreover, cities could not
+self-select into any group, as their population estimates were calculated using
+the 2003 projections by the Brazilian Census Bureau (IBGE). This change in
+council size also happened only seven months before the election, making it
+impossible for candidates to adjust their service provision strategies for the
+2004 election. Therefore, the ruling allows us to study the effect of larger
+legislatures on public service provision during the 2005-2008 term while
+holding all else constant.
 
@@
 
-We use four groups of city-level variables in our models.
-The first group includes pre-treatment control variables that were not affected by the 2004 council size resolution.
-We add them to the estimates to improve the balance between treated and non-treated units.
-The covariates are: 1) the number of council seats in the previous term; 2) city population; 3) city GDP; 4) the proportion of low-income families in each municipality.
-The data come from the Supreme Electoral Court and the 2000 Brazilian census.
-
-Second, we look into municipal data, city councilors' characteristics, approved legislation, and an online survey with 174 former city councilors that served during 2005--2008 term to investigate potencial political mechanisms.\footnote{We also analyzed 108 structured interviews conducted by \citet{lopez2017legisladores} at the Brazilian Economics Planning Institute (IPEA) in 2009.
-The authors asked councilors about their daily work.
-The interviews reinforced that the mayor's agenda dominates councilors' work and it is partisan without strictly following party lines.
-Municipal politics is divided into families or poles of power that belong to different party affiliations.
-Councilors from other parties gravitate around these groups, hence the opposition and government-aligned logic.} The municipal data contains: 1) the number of councilor's belonging to the mayor's pre-electoral coalition; 2) the number of appointed bureaucrats; 2) the councilor's gender and race; 3) the competitiveness of each city council seat; 4) the proportion of laws proposed by the city council that was approved.
-All variables come from the Supreme Electoral Court, the Senate legislative support Interlegis, and the Brazilian Bureau of Statistics.
-
-Third, we also collected 346,553 bills from cities within ten thousand inhabitants from the 2004 population thresholds.
-We selected 63 out of 202 municipalities whose voting records were available online.
-We evaluate proposal types, discriminating between local public goods, oversight, and other legislative activity.
-Examples of the local public goods are investing in a public health clinic, requesting school staff to accommodate an extra child, renovating sewage, and fixing potholes on a given street.\footnote{Our theory does not differentiate between clientelism and broad service provision, as it is hard to disentangle differences in the local level legislation.
-A voter may request a particular service, such as fixing a pothole.
-Attending this request can be interpreted as a clientelistic practice.
-Still, the provision of the service generates non-excludable benefits to the adjacent neighborhood.} Oversight bills are accountability and transparency mechanisms meant to keep public services provision in check.
-Other legislation comprises bills that do not fit in the previous categories.
-Examples are changes in street names, motions to honor citizens or groups, and legislative and internal city council procedures.
-We provide further information about the legislation dataset and the city council survey in sections A.13 and A.14 of the Supplementary Materials.
-
-The last set of variables quantify social welfare.
-Our focus is on the impact of legislature size on education and health care, which are the two most important public services the municipal government should provide to citizens.
-We measure access to education with the average enrollment in primary (K--4) municipal public schools.
-We assess education quality with the Education Development Index (Índice de Desenvolvimento da Educação Básica--IDEB), which the Ministry of Education has issued biannually since 2007.
-The index is a weighted average of student scores in Portuguese and Mathematics (0--10), multiplied by the harmonic mean of public school promotion rates in a given year (0--100).
-To test the effect of the 2004 ruling on health care, we collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants who survived more than 28 days, but died before reaching one year of age.
-The source of all health care variables is the Brazilian Ministry of Health Data Center (DataSUS).
-
-Together, this evidence provides a clear picture of local-level politics patterns in Brazil, from the political mechanism to the municipal welfare consequences of the larger city council size ruling.
-Summary statistics and variable descriptions follow in section A.2 of the Supplementary Materials.
+We use four groups of city-level variables in our models. The first group
+includes pre-treatment control variables that were not affected by the 2004
+council size resolution. We add them to the estimates to improve the balance
+between treated and non-treated units. The covariates are: 1) the number of
+council seats in the previous term; 2) city population; 3) city GDP; 4) the
+proportion of low-income families in each municipality. The data come from the
+Supreme Electoral Court and the 2000 Brazilian census.
+
+Second, we look into municipal data, city councilors' characteristics, approved
+legislation, and an online survey with 174 former city councilors that served
+during 2005--2008 term to investigate potencial political
+mechanisms.\footnote{We also analyzed 108 structured interviews conducted by
+\citet{lopez2017legisladores} at the Brazilian Economics Planning Institute
+(IPEA) in 2009. The authors asked councilors about their daily work. The
+interviews reinforced that the mayor's agenda dominates councilors' work and it
+is partisan without strictly following party lines. Municipal politics is
+divided into families or powerful groups that belong to different party
+affiliations. Councilors from other parties gravitate around these groups,
+hence the opposition and government-aligned logic.} The municipal data
+contains: 1) the number of councilor's belonging to the mayor's pre-electoral
+coalition; 2) the number of appointed bureaucrats; 2) the councilor's gender
+and race; 3) the competitiveness of each city council seat; 4) the proportion
+of laws proposed by the city council that was approved. All variables come from
+the Supreme Electoral Court, the Senate legislative support Interlegis, and the
+Brazilian Bureau of Statistics.
+
+Third, we also collected 346,553 bills from cities within ten thousand
+inhabitants from the 2004 population thresholds. We selected 63 out of 202
+municipalities whose voting records were available online. We evaluate proposal
+types, discriminating between local public goods, oversight, and other
+legislative activity. Examples of the local public goods are investing in a
+public health clinic, requesting school staff to accommodate an extra child,
+renovating sewage, and fixing potholes on a given street.\footnote{Our theory
+does not differentiate between clientelism and broad service provision, as it
+is hard to disentangle differences in the local level legislation. A voter may
+request a particular service, such as fixing a pothole. Attending this request
+can be interpreted as a clientelistic practice. Still, the provision of the
+service generates non-excludable benefits to the adjacent neighborhood.}
+Oversight bills are accountability and transparency mechanisms meant to keep
+public services provision in check. Other legislation comprises bills that do
+not fit in the previous categories, such as changes in street names, motions to
+honor citizens or groups, and legislative and internal city council procedures.
+We provide further information about the legislation dataset and the city
+council survey in sections A.13 and A.14 of the Supplementary Materials.
+
+The last set of variables quantifies social welfare. Our focus is on the impact
+of legislature size on education and health care, which are the two most
+important public services the municipal government should provide to citizens.
+According to Brazilian Constitution, municipalities must spend 25\% of their
+budget on education and 15\% on health care. Consequently, the Ministry of
+Health and the Ministry of Education provide readily available, fine-grained
+data on health care and education at the municipal level, which we leverage in
+this study. We measure access to education with the average enrollment in
+primary (K--4) municipal public schools. We assess education quality with the
+Education Development Index (Índice de Desenvolvimento da Educação
+Básica--IDEB), which the Ministry of Education has issued biannually since
+2007. The index is a weighted average of student scores in Portuguese and
+Mathematics (0--10), multiplied by the harmonic mean of public school
+promotion rates in a given year (0--100). To test the effect of the 2004
+ruling on health care, we collect data on infant mortality per thousand
+children born and on postneonatal infant mortality, which is the death of
+infants who survived more than 28 days, but died before reaching one year
+of age. The source of all health care variables is the Brazilian Ministry
+of Health Data Center (DataSUS).
+
+Together, this evidence provides a clear picture of local-level politics in
+Brazil, from the political mechanism to the municipal welfare consequences of
+the council size ruling. Summary statistics and variable descriptions follow in
+section A.2 of the Supplementary Materials.
 
@@
 
-We employ a regression discontinuity design (RDD) using the population thresholds established by the 2004 Supreme Electoral Court resolution as treatment indicators.
-Figure \ref{fig:runningvarplot} displays the distribution of municipalities within each city council size.
-These population thresholds remained in effect until 2009 when Congress amended the Brazilian Constitution.
-This study covers 2005 to 2008, which constitutes the full mayoral and city-council term following the 2004 Brazilian elections.
-
-Our identification strategy relies on three assumptions.
-First, no municipality should be able to self-select into each side of the discontinuity.
-Second, as we estimate a sharp RDD, the council size should increase precisely as the law mandates.
-Third, this design assumes that the pre-treatment variables, collected before the 2003 Supreme Federal Court decision, were not affected by the 2004 ruling on council size.
-Moreover, for all the actual models estimated here, we fitted placebo cutoffs to check whether the estimation technique leads to consistent results.
-The placebo cutoffs are the dashed lines in Figure \ref{fig:runningvarplot}.
+We employ a regression discontinuity design (RDD) using the population
+thresholds established by the 2004 Supreme Electoral Court resolution as
+treatment indicators. Figure \ref{fig:runningvarplot} displays the distribution
+of municipalities within each city council size. These population thresholds
+remained in effect until 2009 when Congress amended the Brazilian Constitution.
+This study covers 2005 to 2008, which constitutes the full mayoral and
+city-council term following the 2004 Brazilian elections.
+
+Our identification strategy relies on three assumptions. First, no municipality
+should be able to self-select into each side of the discontinuity. Second, as
+we estimate a sharp RDD, the council size should increase precisely as the law
+mandates. Third, this design assumes that the pre-treatment variables,
+collected before the 2003 Supreme Federal Court decision, were not affected by
+the 2004 ruling on council size. Moreover, for all the actual models estimated
+here, we fitted placebo cutoffs to check whether the estimation technique leads
+to consistent results. The placebo cutoffs are the dashed lines in Figure
+\ref{fig:runningvarplot}.
 
@@
 
-For the first assumption, in section A.3 of the online supplemental materials, we assess distribution imbalances running the \citet{McCrary2008} and \citet{cattaneo2019simple} tests.
-The tests show no distribution imbalances.
-
-For the second assumption, running RDD in multiple thresholds may lead to inconsistent estimates when there are differences in the distribution of cases around the cutoffs \citep{cattaneo2016interpreting, eggers2018regression, bertanha2020regression}.
-In the dataset, there are twelve discontinuities.
-At each threshold, there is a sharp increase of one councilor, from 9 to 21.
-When running an RDD on these discontinuities, a consistent estimator should fit the exact change of one councilor.
-However, if we pool all the discontinuities together with no correction, we find an increase in council size of 1.63 councilors (see the first estimate in Table \ref{validitycheck}).
-This imbalance occurs because when we combine all the discontinuities, the model implies that municipalities below the 47,619 cutoffs (9 to 10 councilors) are comparable to changes in towns right above the 571,428 cutoffs (20 to 21 council members).
-That is incorrect because the comparison is inconsistent in council size, and these municipalities diverge in many other aspects.
-
-To avoid this problem, in section A.5 of the Supplemental Materials, we show by simulation that adding controls, especially the variables responsible for the multiple threshold assignments (in our case, the population in 2003), improves the consistency and efficiency of the estimates.
-Relying on this fact, we add five controls to the estimates: population in 2003; GDP per capita; the number of seats in 2000; year; and a dummy for the northeast municipalities.
-The reason for the first variable is the multiple threshold assignments.
-We add GDP per capita because wealthier cities tend to have better public services.
-The number of seats in 2000 intends to control that some municipalities could experience a change provoked by the previous council size, confounding our estimates.
-The year and the Northeast dummies were added to improve efficiency.
-Adding controls improves efficiency in RDD and also enhances the consistency in the multiple thresholds RDD \citep{calonico2019regression}.
-
-For the last assumption, there should be no changes in pre-treatment covariates.
-These pre-treatment covariates are measured before the primary outcomes.
-As the threshold rule selected by the Brazilian Electoral Court was unpredictable, it should not detect any variation before the thresholds were in place.
-
-\begin{table}[htb!] \centering 
+For the first assumption, in section A.3 of the online supplemental materials,
+we assess distribution imbalances running the \citet{McCrary2008} and
+\citet{cattaneo2019simple} tests. The tests show no distribution imbalances.
+
+For the second assumption, running RDD in multiple thresholds may lead to
+inconsistent estimates when there are differences in the distribution of cases
+around the cutoffs \citep{cattaneo2016interpreting, eggers2018regression,
+bertanha2020regression}. In the dataset, there are twelve discontinuities. At
+each threshold, there is a sharp increase of one councilor, from 9 to 21. When
+running an RDD on these discontinuities, a consistent estimator should fit the
+exact change of one councilor. However, if we pool all the discontinuities
+together with no correction, we find an increase in council size of 1.63
+councilors (see the first estimate in Table \ref{validitycheck}). This
+imbalance occurs because when we combine all the discontinuities, the model
+implies that municipalities below the 47,619 cutoffs (9 to 10 councilors) are
+comparable to changes in towns right above the 571,428 cutoffs (20 to 21
+council members). That is incorrect because the comparison is inconsistent in
+council size, and these municipalities diverge in many other aspects.
+
+To avoid this problem, in section A.5 of the Supplemental Materials, we show by
+simulation that adding controls, especially the variables responsible for the
+multiple threshold assignments (in our case, the population in 2003), improves
+the consistency and efficiency of the estimates. Relying on this fact, we add
+five controls to the estimates: population in 2003; GDP per capita; the number
+of seats in 2000; year; and a dummy for Northeast municipalities. The
+reason for the first variable is the multiple threshold assignments. We add GDP
+per capita because wealthier cities tend to have better public services. The
+number of seats in 2000 intends to control that some municipalities could
+experience a change provoked by the previous council size, confounding our
+estimates. The year and the Northeast dummies were added to improve efficiency.
+Adding controls improves efficiency in RDD and also enhances the consistency in
+the multiple thresholds RDD \citep{calonico2019regression}.
+
+For the last assumption, there should be no changes in pre-treatment
+covariates. These pre-treatment covariates are measured before the primary
+outcomes. As the threshold rule selected by the Brazilian Electoral Court was
+unpredictable, it should not detect any variation before the thresholds were in
+place.
+
+Table \ref{validitycheck} displays the results of the validity checks. We
+present the first-stage regressions at the top of the Table, with and without
+covariates, for both real and placebo cutoffs. At the bottom, we estimate the
+pre-treatment covariate balance. Furthermore, in the Supplementary Materials,
+we run placebo checks for all the models using placebo cutoffs within the real
+ones. The results are available in sections A.6 to A.12 of the Supplementary
+Materials.
+
+\singlespacing
+
+\begin{table}[H] \centering 
   \caption{Research Design Validity Check} 
@@
 
-Table \ref{validitycheck} displays the results of the validity checks.
-We present the first-stage regressions at the top of the Table, with and without covariates, for both real and placebo cutoffs.
-At the bottom, we estimate the pre-treatment covariate balance.
-Furthermore, in the Supplementary Materials, we run placebo checks for all the models using placebo cutoffs within the real ones.
-The results are available in sections A.6 to A.12 of the Supplementary Materials.
-
-Note that without the covariates, the first stage overestimates the change in the primary treatment and underestimates the effect in the placebo regressions.
-When we add the covariates, the results improve and the point estimates are now one for the primary model and zero for the placebo regressions.
-These are the correct values.
-Moreover, Panel B of Table \ref{validitycheck} shows that the pre-treatment covariates remain unchanged around the thresholds.
-These tests reinforce the validity of our research design.
+\doublespacing
+
+Note that without the covariates, the first stage overestimates the change in
+the primary treatment and underestimates the effect in the placebo regressions.
+When we add the covariates, the results improve and the point estimates are now
+one for the primary model and zero for the placebo regressions. These are the
+correct values. Moreover, Panel B of Table \ref{validitycheck} shows that the
+pre-treatment covariates remain unchanged around the thresholds. These tests
+reinforce the validity of our research design.
 
@@
 
-To test the formal model's predictions, we present four sets of empirical results.
-First, we confirm the bargaining costs hypothesis and find that the additional legislator also promotes more appointments of bureaucrats.
-This aligns with the councilors' descriptions of the strategies mayors employ to consolidate support from city councilors.
-Second, we show that municipalities with an extra city councilor approve more public goods laws in general and on education and health care.
-Third, we show that all these pieces of evidence result in improvements in infant mortality and elementary school enrollment, two vital services for welfare.
-Finally, we point that the results are robust to alternative channels for the influence of legislature size on welfare, demonstrating that representation of women and non-whites, competitiveness, and legislative productivity, fail to receive empirical support.
+To test the predictions from our formal model, we present four sets of
+empirical results. First, we confirm the bargaining costs hypothesis and find
+that the additional legislator also promotes more appointments of bureaucrats.
+This aligns with the councilors' descriptions of the strategies mayors employ
+to consolidate support from city councilors. Second, we show that
+municipalities with an extra city councilor approve more legislation about
+public goods provision in general and about education and health care in
+particular. Third, we show that all these pieces of evidence result in
+improvements in infant mortality and elementary school enrollment, two vital
+services for welfare. Finally, we also show that our results are robust to
+alternative channels for the influence of legislature size on welfare,
+demonstrating that representation of women and non-whites, competitiveness, and
+legislative productivity fail to receive empirical support.
 
@@
 
-The formal model's central premise is that larger legislature sizes produce lower bargaining costs when the chances to elect politicians aligned with the mayor are sufficiently high.
-Moreover, the main bargaining chip between the Executive and the Legislative is job appointments.
-This is more so when the city councilors are aligned with the mayor.
-As job appointments are crucial for governing, we study the number of politically appointed bureaucrats, career bureaucrats, and councilors' assistants.
-Politically appointed bureaucrats are associated with better service provision in Brazil, as their tenure in office depends directly on the survival of the politician supporting them \citep{toral2019benefits}.
-Career bureaucrats pass through a rigorous examination, limiting their usefulness as bargaining chips between city councilors and mayors.
-Moreover, career bureaucrats cannot be fired once hired, which considerably constrains politicians' pressure on them.
-Finally, city councilors who want to influence policy may employ more staff members and assistants to their offices.
-This could influence policymaking through city councilor's pressuring on the bureaucracy, defying our hypothesized mechanism.
-Our theoretical expectations for these regressions are that larger council size affects the political alignment of city councilors and the number of politically appointed bureaucrats.
-It should not affect the number of career bureaucrats or city council assistants, as it is more valuable to have a political appointee that politicians can pressure, working directly with voters.
-Table \ref{tab:bargain} tests the first hypothesis about the nexus between city council size and bargaining costs and explores the consequences of larger legislatures on the municipal bureaucracy.
+The main premise of our model is that larger legislature size produces lower
+bargaining costs when the chances of electing government-aligned politicians
+are sufficiently high. Moreover, the main bargaining chip between the executive
+and the legislative is job appointments, even more so when the city councilors
+are aligned with the mayor. As job appointments are an important factor for
+local governance, we analyze the number of politically appointed bureaucrats,
+career bureaucrats, and councilors' assistants. A higher number of political
+appointees is associated with better service provision in Brazil, as their
+tenure in office depends directly on the survival of the politician supporting
+them \citep{toral2019benefits}. Career bureaucrats pass through a rigorous
+examination, limiting their usefulness as bargaining chips between city
+councilors and mayors. Moreover, career bureaucrats cannot be fired once hired,
+which considerably constrains politicians' pressure on them. Finally, city
+councilors who want to influence policy may employ more staff members and
+assistants to their offices. This could influence policymaking through city
+councilors putting pressure on the bureaucracy, defying our hypothesized
+mechanism. Our theoretical expectations for these regressions are that larger
+council size affects the political alignment of city councilors and the number
+of politically appointed bureaucrats. It should not affect the number of career
+bureaucrats or city council assistants, as it is more valuable to have a
+political appointee that politicians can pressure, working directly with
+voters. Table \ref{tab:bargain} tests the first hypothesis about the nexus
+between city council size and bargaining costs and explores the consequences of
+larger legislatures on the municipal bureaucracy.
 
@@
 
-Column (1) shows a 91\% chance of the extra legislator belonging to the mayoral coalition.
-The model hypothesis stated that the probability of electing a city councilor allied with the mayor is sufficiently high.
-However, sufficiently high can be ambiguous, and it depends on the intensity of the political disagreement and the current legislature size.
-In any case, 91\% chance is a considerably large quantity, and the extra city councilor is going to the mayoral coalition nine in every ten legislature size increases.
-This strengthens the political position of the mayor and diminishes bargaining costs.\footnote{The effect of city council size on the number of mayor-aligned politicians stems from the rounding rule adopted by the proportional representation system in Brazil.
-The rounding rule favors the coalitions with more votes.
-Most of the time, the coalition of the elected mayor is the one that receives more votes.} Column (2) demonstrates that adding one councilor increases appointed employees by around 104 extra employees per additional city councilor.
-When negotiating with city councilors, these employees are a great bargaining chip, and they are also associated with better service provision \citep{ toral2019benefits}.
-As expected, legislature size has a null effect on the number of career bureaucrats (Column 3) and councilors' staff members (Column 4).
+Column (1) shows a 91\% chance of the extra legislator belonging to the mayoral
+coalition. The model hypothesis stated that the probability of electing a city
+councilor aligned with the mayor is sufficiently high. However, sufficiently
+high can be ambiguous, and it depends on the intensity of the political
+disagreement and the current legislature size. In any case, 91\% chance is a
+considerably large quantity, and the extra city councilor is going to the
+mayoral coalition nine in every ten legislature size increases. This
+strengthens the political position of the mayor and diminishes bargaining
+costs.\footnote{The effect of city council size on the number of mayor-aligned
+politicians stems from the rounding rule adopted by the proportional
+representation system in Brazil. The rounding rule favors the coalitions with
+more votes. Most of the time, the coalition of the elected mayor is the one
+that receives more votes.} Column (2) demonstrates that adding one councilor
+increases appointed employees by around 104 extra employees per additional city
+councilor. When negotiating with city councilors, these employees are a great
+bargaining chip, and they are also associated with better service provision
+\citep{toral2019benefits}. As expected, legislature size has a null effect on
+the number of career bureaucrats (Column 3) and councilors' staff members
+(Column 4).
 
@@
 
-We built two novel datasets to provide evidence for our mechanism.
-First, we ran a survey with former city councilors, asking how mayors consolidate their coalition support within the city council.
-Second, we collected 346,553 laws approved in 63 municipalities within ten thousand inhabitants away from the city council size thresholds.
-We hand-coded 3,466 laws into four categories: public goods, oversight, education and health care-related legislation, and other legislative duties.
-After hand-coding these laws, we used a Supporting Vector Machine (SVM) algorithm to classify the remainder laws.
-From all of the algorithms we tested, SVM achieved the highest performance.
+We built two novel datasets to provide evidence for our mechanism. First, we
+ran a survey with former city councilors, asking how mayors consolidate their
+coalition support within the city council.\footnote{We provide further
+information about the city council survey in section A.14 of the Supplementary
+Materials.} Second, we collected 346,553 laws approved in 63 municipalities
+within ten thousand inhabitants away from the city council size thresholds. We
+hand-coded 3,466 laws into four categories: public goods, oversight, education
+and health care-related legislation, and other legislative duties. After
+hand-coding these laws, we used a Supporting Vector Machine (SVM) algorithm to
+classify the remainder laws. From all of the algorithms we tested, SVM achieved
+the highest performance.
 
@@
 
-This paper assumes that city councilors want to extract rents and to get reelected.
-The rents come from continuing in the repeated game, and the partisanship discounts that benefit.
-Figure \ref{survelec} shows that 65.9 percent of councilors mentioned that mayors use job appointments to consolidate their coalition support.
-Moreover, 59.0 percent of the surveyed councilors affirmed that mayors use personal favors, such as shifting resources to places where the councilors have electoral support, to solidify their governing coalition.
-Granting favors works as rent transfers for councilors.
-Job appointments are also convenient for the mayors because patronage in Brazil has positive results in terms of welfare \citep{toral2019benefits}.
+We assume that city councilors want to extract rents and to get reelected.
+The rents come from continuing in the repeated game, and the partisanship
+discounts that benefit. Figure \ref{survelec} shows that 65.9 percent of
+councilors mentioned that mayors use job appointments to consolidate their
+coalition support. Moreover, 59.0 percent of the surveyed councilors affirmed
+that mayors use personal favors, such as shifting resources to places where the
+councilors have electoral support, to solidify their governing coalition.
+Granting favors works as rent transfers for councilors. Job appointments are
+also convenient for the mayors because patronage in Brazil has positive results
+in terms of welfare \citep{toral2019benefits}.
 
@@
 
-In Figure \ref{LEGAPPR}, we show that the per capita number of laws related to local public goods provision increases in towns that receive the extra legislator, vis-à-vis baseline cities that did not get an additional councilor.
-One additional city councilor increased the per capita amount of laws on public goods by 15.0 percent.
-Also, the number of laws that focus on health care and education increased by 19.7 percent.
-Looking specifically into health care and education legislation, the proportion of laws discussing public goods increased by 15.7 percent, showing that policy proposals by both the mayor and the councilors shift toward local and citywide public goods.\footnote{Public goods here are not restricted to citywide goods.
-Any service that benefits citizens, regardless of whether they are targeted to citizens or not, is considered public goods.
-For example, building a health clinic in a particular district can virtually exclude the citizens that are not living in the neighborhood.
-However, we are still considering these as public goods, albeit targeted at a specific locality.}
+In Figure \ref{LEGAPPR}, we show that the per capita number of laws related to
+local public goods provision increases in towns that receive the extra
+legislator, vis-à-vis baseline cities that did not get an additional councilor.
+One additional city councilor increased the per capita amount of laws on public
+goods by 15.0 percent. Also, the number of laws that focus on health care and
+education increased by 19.7 percent. Looking specifically into health care and
+education legislation, the proportion of laws discussing public goods increased
+by 15.7 percent, showing that policy proposals by both the mayor and the
+councilors shift toward local and citywide public goods.\footnote{Public goods
+here are not restricted to citywide goods. Any service that benefits citizens,
+regardless of whether they are targeted to citizens or not, is considered
+public goods. For example, building a health clinic in a particular district
+can virtually exclude the citizens that are not living in the neighborhood.
+However, we are still considering these as public goods.}
 
@@
 
-We now study the impact of legislature size on education and health care. We use four indicators in this paper: two in education and two in health care.
-
-Table \ref{tab:outcomes} shows that increasing the city council by one legislator generates welfare improvement in municipalities.
-In health care, increasing the legislature size decreases infant mortality in 2.01 deaths per 1,000 children born.
-This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations.
-Moreover, postneonatal mortality decreases by 0.90 casualties per 1,000 births, which remains around the 0.14 standard deviations improvement as infant mortality.
-Infant mortality is a primary outcome for welfare, and it correlates with several other indicators of well-being \citep{world2005health}.
-The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in large welfare effects.
-As expected, placebo regressions were statistically insignificant.
-
-In terms of education, with the addition of a city councilor, enrollment in elementary schools increased by 2.58 children on average per school.
-This represents a change of around 0.20 standard deviations.
-Besides the influence of the mayoral support, enrollment can also directly impact the councilor's representation: Councilors can pressure the bureaucracy to accommodate a few extra students.
-With support from the mayor, they can help voters get access to schools, improving the voter's welfare.
-Education quality remains unchanged, but with more students in the classroom, it could potentially decrease.
-As expected, the placebo regressions are insignificant.
+We now study the impact of legislature size on education and health care. Table
+\ref{tab:outcomes} shows that increasing the city council by one legislator
+generates welfare improvement in municipalities. Regarding health care,
+increasing the legislature size decreases infant mortality in 2.01 deaths per
+1,000 children born. This impact is significant in absolute terms and
+represents an effect of 0.14 in standard deviations. Moreover, postneonatal
+mortality decreases by 0.90 casualties per 1,000 births, which remains around
+the 0.14 standard deviations improvement as infant mortality. Infant mortality
+is a primary outcome for welfare, and it correlates with several other
+indicators of well-being \citep{world2005health}. The fact that infant
+mortality improved in the Brazilian case shows that the increased mayor's
+support mechanism results in large welfare effects. As expected, placebo
+regressions were statistically insignificant.
+
+In terms of education, with the addition of a city councilor, enrollment in
+elementary schools increased by 2.58 children on average per school. This
+represents a change of around 0.20 standard deviations. Besides the influence
+of the mayoral support, enrollment can also directly impact the councilor's
+representation: Councilors can pressure the bureaucracy to accommodate a few
+extra students. With support from the mayor, they can help voters get access to
+schools, improving the welfare of voters. Education quality remains unchanged,
+but with more students in the classroom, it could potentially decrease. As
+expected, the placebo regressions are insignificant.
 
@@
 
-In this paper, we show that the provision of education and health care in Brazil improves with larger legislatures.
-This is because the chances of electing a city councilor aligned with the mayor are 91 percent, thanks to the rule of distributing seats adopted in the country.
-In the Supplemental Materials, we also run regressions in placebo cutoffs between the actual cutoffs, showing that our estimates are consistently null when we are supposed to find insignificant results.
-
-However, other pathways may also explain the nexus between city council size and welfare.
-First, improvements in representation could change the provision of health care and education.
-Increasing legislature size without changing the population makes councilors represent fewer people.
-For example, in a town with 50 thousand voters and ten councilors, each councilor represents five thousand voters.
-If the same city has eleven councilors, then each councilor represents 4.5 thousand voters.
-This facilitates the representation of minorities, as they have to gather fewer votes to elect a city councilor.
-A minority representative can advocate for policies that would improve the welfare of marginalized groups \citep{ChattopadhyayDuflu2004, chin2011redistributive, pande2003can}.
-Diversity could also improve governance in municipalities \citep{rugh2011provision}.
-For instance, more women in public offices may shift service provision toward welfare expenditure \citep{brollo2016happens, duflo2012women, funk2019representative, hernandez2018women}.
-Therefore, an alternative hypothesis to explain the increased service provision is that larger legislatures improve female and minority representation in Brazil.\footnote{For a description of the barriers faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
-
-Second, more seats could increase the competitiveness in the election, making politicians provide more services \citep{besley2010political}.
-In a political system with around thirty parties and a sample average of almost ten parties in the municipalities we study, candidates per seat can increase exponentially.
-According to the Brazilian electoral law, each party can sponsor 1.5 times the number of seats as candidates.
-If a party forms a pre-electoral coalition, this number increases to two times the number of seats \citep{coneglian2008lei}.
-An election in a small town, with ten councilors, may end up with 600 candidates: (30 parties) x (two times the number of seats) x (ten seats).
-Therefore, an alternative hypothesis to explain the increased service provision is that larger council size increase the competitiveness of the election.\footnote{Despite the common assumption that competitiveness improve welfare, \citet{boulding2014political} and \citet{gottlieb2019countervailing} show that more competition can increase budgetary pressure, lower social policy, lead to bargaining inefficiencies.}
+In this paper, we show that the provision of education and health care in
+Brazil improves with larger legislatures. This is because the chances of
+electing a city councilor aligned with the mayor are 91 percent, thanks to the
+rule of distributing seats adopted in the country. In the Supplemental
+Materials, we also run regressions in placebo cutoffs between the actual
+cutoffs, showing that our estimates are consistently null when we are indeed
+supposed to find insignificant results.
+
+However, other pathways may also explain the nexus between city council size
+and welfare. First, improvements in representation could change the provision
+of health care and education. Increasing legislature size without changing the
+population makes councilors represent fewer people. For example, in a town with
+50 thousand voters and ten councilors, each councilor represents five thousand
+voters. If the same city has eleven councilors, then each councilor represents
+4.5 thousand voters. This facilitates the representation of minorities, as they
+have to gather fewer votes to elect a city councilor. A minority representative
+can advocate for policies that would improve the welfare of marginalized groups
+\citep{ChattopadhyayDuflu2004, chin2011redistributive, pande2003can}. Diversity
+could also improve governance in municipalities \citep{rugh2011provision}. For
+instance, more women in public offices may shift service provision toward
+welfare expenditure \citep{brollo2016happens, duflo2012women,
+funk2019representative, hernandez2018women}. Therefore, an alternative
+hypothesis to explain the increased service provision is that larger
+legislatures improve female and minority representation in Brazil.\footnote{For
+a description of the barriers faced by non-white politicians in Brazil, see
+\citet{janusz2021race}.}
+
+Second, more seats could increase the competitiveness in the election, making
+politicians provide more services \citep{besley2010political}. In a political
+system with around thirty parties and a sample average of almost ten parties in
+the municipalities we study, candidates per seat can increase exponentially.
+According to the Brazilian electoral law, each party can sponsor 1.5 candidates
+per seat. If a party forms a pre-electoral coalition, this number increases to
+two times the number of seats \citep{coneglian2008lei}. An election in a small
+town, with ten councilors, may end up with 600 candidates: (30 parties) x (two
+times the number of seats) x (ten seats). Therefore, an alternative explanation
+for better service provision is that a larger council size increases the
+competitiveness of the election.\footnote{Despite the common assumption that
+competitiveness improve welfare, \citet{boulding2014political} and
+\citet{gottlieb2019countervailing} show that more competition can increase
+budgetary pressure, lower social policy, lead to bargaining inefficiencies.}
 
 Finally, the mayor and the legislature carry out the provision of services.
-Similar to what happens in firms, an extra employee can increase the firm productivity frontier by improving cooperation and synergistic outputs \citep{alchian1972production, holmstrom1982moral}.
-A similar argument would posit that the increase in council size increases the public service production capability in the municipality.
-As the production of the legislature manifests itself into legislation, an alternative hypothesis to explain the increased service provision is that more laws proposed by the city councilors are being approved.
+Similar to what happens in firms, an extra employee can increase the firm
+productivity frontier by improving cooperation and synergistic outputs
+\citep{alchian1972production, holmstrom1982moral}. A similar argument would
+posit that the increase in council size increases the capability for
+municipalities to provide public services. As legislative productivity
+manifests itself as legislation, an alternative hypothesis to explain the
+increased service provision is that more legislation is being approved by the
+city council.
 
@@
 
-Table \ref{tab:robust} tests whether our results could stem from these different mechanisms.
-Columns (1) and (2) test the hypotheses that better representation of under-served groups could improve welfare.
-As we can see, larger city councils do not increase the representation of females or non-whites.
-Column (3) shows that the competition per seat in municipalities with larger city councils remain statistically equal to zero.
-Finally, Column (4) shows that the proportion of legislation passed by the city council remains unchanged when council sizes increase.
+Table \ref{tab:robust} tests whether our results could stem from these
+different mechanisms. Columns (1) and (2) test the hypotheses that better
+representation of under-served groups could improve welfare. As we can see,
+larger city councils do not increase the representation of females or
+non-whites. Column (3) shows that the competition per seat in municipalities
+with larger city councils remain statistically equal to zero. Finally, Column
+(4) shows that the proportion of legislation passed by the city council remains
+unchanged when council size increases.
 
@@
 
-This paper shows that partisanship considerably decreases bargaining costs, improving welfare.
-The crucial actors in providing public goods are the mayors, but they cannot do it alone.
-Legislatures are a solid check to the mayor's policy.
-Bargaining with them in a country plagued by corruption can be costly \citep{bertholini2017price}.
-Therefore, an extra ally in the city council may help ease the bargaining and improve welfare.
-
-Increasing the council size results in gains in elementary school enrollment and in lower infant mortality.
-Education quality remains unchanged, but increasing enrollment without affecting quality should be interpreted as positive.
-The analysis of the approved legislation shows that the frequency of laws on local public goods increases in municipalities above the council size thresholds.
-Finally, the city council survey demonstrates that councilors and mayors agree about appointing more public servants to the public administration.
-
-\citet{Ames2001} argues that the Brazilian democracy is deadlocked because the Executive has its hands tied by a legislature that demands constantly provision of particularistic and private goods.
-Indeed, the most successful presidents after 1995 had to build multiparty coalitions by negotiating with parties \citep{limongi1998bases, raile2011executive}.
-Despite evidence that side payments cemented these coalitions, many social and economic policies have been implemented.
-For instance, education and health care notably improved during the Cardoso and Lula governments \citep{acemoglu2012nations}.
-Of the presidents that defied the coalition system, Rousseff was impeached in her second term.
-Bolsonaro can be considered one of the most ineffective presidents in Brazilian history.
-
-Municipalities work very similarly in terms of the incentives for legislative-executive bargaining.
-The stakes are lower, and the negotiations involve only one legislative branch.
-Still, in a system such as Brazil's, with more than thirty-five registered parties, mayors face substantial challenges to the support for their agendas.
-Having extra help in the council can tilt the bargaining towards cheaper governing, thus improving public goods provision.
-
-Moreover, we do not argue that these benefits result from the absence of corruption or clientelism.
-Both the formal model and empirical evidence provided by \citet{britto2020corruption} show that corruption increases with legislature size.
-As the model shows, city councilors receive a side transfer from mayors to support their agenda.
-Mayors also divide the resources saved in the bargain into public goods and rents.
-The rate for the division depends on the marginal changes of the rents and public goods, but these two components receive the extra resources.
-In this case, the mayor's rents may be primarily corruption, and the councilor's transfers can be clientelistic, aimed at improving the councilor's reelection chances.
-
-Our findings have implications that extend well beyond Brazil.
-A general form of our argument is that it is easy for a politician to negotiate with members of her in-group \citep{abbink2019, g9030057}.
-Specifically, several countries have divisions between Executive and Legislative, such as the federal level of presidential systems, state governments, and local city councils.
-As these political bodies are influenced by political allegiances, the dynamics we expose here generalize to most of them.
-Depending on legislative support, changing legislature size could increase the chance of electing politicians that are not aligned with the Executive, decreasing welfare.
-Despite the particular effects on political support and welfare, the logic described in this paper would remain relevant for empirically accessing the welfare effects of enlarged legislatures.
-Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}.
-
-This paper opens two questions for future analysis.
-First, if the mechanism we suggest is indeed at work, more support for the Executive means better public goods.
-Therefore, one may ask what should be the city council's checking prerogatives, as they significantly reduce the provision of public services.
-The evidence so far is inconclusive, and \citet{poulsen2018political} show that checks for the mayors may also improve service provision.
-It may be the relationship between rents and public goods is non-linear, making mayors revert to only rents past a certain threshold.
-Moreover, it could be that, at some point, legislative support is ineffective or even harmful to democracies, as it may trigger an intense form of elite capture.
-This question needs further investigation, and our results suggest that mayors with more support improve welfare.
-Second, it remains uncertain how other legislative features affect welfare.
-For example, city councils may vary in size, monetary compensation for councilors, committee structure, and internal power structure.
-These components may interact with each other, and understanding how size plays with other features would improve our knowledge about city councils size affect welfare.
-Both these questions are crucial for institution design and welfare in developing democracies.
-
-\newpage
+This paper shows that partisanship considerably decreases bargaining costs and
+improves citizen welfare. The crucial actors in providing public goods are the
+mayors, but they cannot do it alone. Legislatures are a solid check to the
+mayor's policy. Bargaining with them in a country plagued by corruption can be
+costly \citep{bertholini2017price}. Therefore, an extra ally in the city
+council may help ease the bargaining and increase social welfare.
+
+Increasing the council size results in gains in elementary school enrollment
+and in lower infant mortality. Education quality remains unchanged, but
+increasing enrollment without affecting quality should be interpreted as a
+positive outcome. The analysis of the approved legislation shows that the
+frequency of laws on local public goods increases in municipalities above the
+council size thresholds. Finally, our survey data demonstrate that councilors
+and mayors agree about appointing more public servants to the public
+administration.
+
+\citet{Ames2001} argues that the Brazilian democracy is prone to deadlocks
+because the executive has its hands tied by legislators that demand consistent
+provision of particularistic and private goods. Indeed, the most successful
+presidents after 1995 had to build multiparty coalitions by negotiating with
+parties \citep{limongi1998bases, raile2011executive}. Despite evidence that
+side payments cemented these coalitions, many social and economic policies have
+since been implemented. For instance, education and health care notably
+improved during the Cardoso and Lula governments \citep{acemoglu2012nations}.
+Presidents who challenged the coalition system did not succeed. For instance,
+former President Rousseff was impeached in her second term. Bolsonaro can be
+considered one of the most ineffective presidents in Brazilian history.
+
+Municipalities work similarly in terms of the incentives for
+legislative-executive bargaining. The stakes are lower, and the negotiations
+involve only one legislative branch. Still, in a system such as Brazil's, with
+more than thirty-five registered parties, mayors face substantial challenges to
+the support for their agendas. Having extra help in the council can tilt the
+bargaining towards cheaper governing costs, thus improving public goods
+provision.
+
+However, we do not argue that these benefits result from the absence of
+corruption or clientelism. Both the formal model and empirical evidence
+provided by \citet{britto2020corruption} show that corruption increases with
+legislature size. As the model shows, city councilors receive a side transfer
+from mayors to support their agenda. Mayors also divide the resources saved in
+the bargain into public goods and rents. The rate for the division depends on
+the marginal changes of the rents and public goods, but these two components
+receive the extra resources. In this case, the mayor's rents may be primarily
+corruption, and the councilor's transfers can be clientelistic, aimed at
+improving the councilor's reelection chances.
+
+Our findings have implications that extend well beyond Brazil. A general form
+of our argument is that it is easy for a politician to negotiate with members
+of her in-group \citep{abbink2019, g9030057}. Specifically, several countries
+have separate executive and legislative powers, such as the federal level of
+presidential systems, state governments, and local city councils. As these
+political bodies are influenced by political allegiances, the dynamics we
+expose here may be generalizable. Depending on legislative support, changing
+the legislature size could increase the chance of electing politicians that are
+not aligned with the executive, hence decreasing welfare. Despite the
+particular effects on political support and welfare, the logic described in
+this paper would remain relevant for empirically accessing the effect of
+enlarged legislatures on welfare. Our findings may also help scholars
+understand why other countries in Latin America and Asia can generate effective
+governance despite having strong executives and large coalitions
+\citep{pereira2012surprising}.
+
+This paper opens several questions for future analysis. First, if the mechanism
+we suggest is indeed at work, one may ask what should be the city council's
+checking prerogatives, as they significantly reduce the provision of public
+services. The evidence so far is inconclusive, and \citet{poulsen2018political}
+show that checks for the mayors may also improve service provision. Second,
+future research could evaluate whether additional legislators help mayors gain
+access to federal or state transfers in countries where resources are centrally
+provided, such as Japan. As suggested by \citet{catalinac2020tournament}, in
+these situations the national government can create a tournament between
+municipalities and provide resources to those which offer more electoral
+support. Scholars might want to analyze whether this tournament structure
+interacts with the mechanisms we suggest in this paper. Third, scholars might
+want to investigate whether our findings remain valid under different
+conditions. It is possible that the mechanisms we present here are non-linear,
+with additional legislators having a positive or negative impact on welfare
+depending on certain electoral characteristics. Finally, it remains uncertain
+how other legislative features affect citizen well-being. For example, city
+councils may vary in size, monetary compensation for councilors, committee
+structure, and internal power structure. Understanding how legislature size
+interacts with other features would improve our knowledge about how local
+legislatures impact public service delivery. These questions are crucial for
+institution design and welfare in developing democracies.
+
 \setlength{\parindent}{0cm}

### 2022-04-15 article/article.Rmd
proofreading

@@
 We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures.
-To explore possible mechanisms, we surveyed former city councilors and analyzed 346,553 bills proposed between 2005 and 2008.
+To explore possible mechanisms, we surveyed 174 former city councilors and analyzed 346,553 bills proposed between 2005 and 2008.
 This paper has implications for the design of representative institutions."
 abstractspacing: double
-keywords: Legislature Size; Legislative Bargaining; Local Public Goods Provision; Regression Discontinuity Design; Brazil
+keywords: legislature size; legislative bargaining; local public goods provision; regression discontinuity design; Brazil
 jelcodes: H41; H80; I31; I38
@@
 Legislative institutions are crucial for citizen welfare and public service
-provision in democratic countries. Historically, the division of power and the
-birth of representative governments placed legislatures at the center of the
-political stage. In modern democracies, most countries have assemblies at all
-levels of government. These institutions regulate the quantity and quality of
-legislation, check and veto other political powers, and influence policymaking.
-Moreover, legislatures also determine taxation, government spending and oversee
-public programs \citep{auriol2012optimal, north1989constitutions,
-poulsen2018political, stasavage2011states, Weingastetal1981}.
+provision in democratic countries. Historically, the separation of powers and
+the birth of representative governments placed legislatures at the center of
+the political stage. In modern democracies, most countries have assemblies at
+all levels of government. These institutions regulate the quantity and quality
+of legislation, check and veto other political powers, and influence
+policymaking. Moreover, legislatures also determine taxation, government
+spending and oversee public programs \citep{auriol2012optimal,
+north1989constitutions, poulsen2018political, stasavage2011states,
+Weingastetal1981}.
 
@@
 
-In this paper, we propose a new theory based on executive leadership and party
+In this paper, we propose a theory based on executive leadership and party
 politics to explain how city council size impacts local public goods provision.
 First, in mayor-council municipalities, mayors are the main responsible for
-public service decisions and have the power to boost public investment similar
-to presidents and governors. Second, partisanship plays a key role in city
-politics, even in countries in which ideological attachment is relatively weak.
-Party attachment structures political views \citep{samuels2014power}, and
-local-level elites usually belong to different factions and parties. They fight
-for power in the municipality by controlling various parties and forming
-distinct pre-electoral coalitions.\footnote{Elite political competition in the
-local level has also been linked to violence and conflict in Brazil and
-elsewhere \citep{hoelscher2015politics, mignozzetti2018predatory}.} In many
-cities, family ties may be substitutes for the ideological component, but
-influential local leaders usually sort themselves into different political
-groups \citep{ferraz2020political, nunes1977coronelismo}.
+public service decisions, and like presidents and governors, they can boost
+local public investments by altering the government budget. Second,
+partisanship plays a key role in city politics, even in countries in which
+ideological attachment is relatively weak. Party attachment structures
+political views \citep{samuels2014power}, and local-level elites usually belong
+to different factions and parties. They fight for power in the municipality by
+controlling various parties and forming distinct pre-electoral
+coalitions.\footnote{Elite political competition in the local level has also
+been linked to violence and conflict in Brazil and elsewhere
+\citep{hoelscher2015politics, mignozzetti2018predatory}.} In many cities,
+family ties may be substitutes for the ideological component, but influential
+local leaders usually sort themselves into different political groups
+\citep{ferraz2020political, nunes1977coronelismo}.
 
@@
 city councils, which in turn lower public goods provision and rents. However,
-partisanship decreases bargaining costs when the chances of electing councilors
-aligned with the mayor are sufficiently high. Lower bargaining costs release
-funds for mayors to invest in public goods provision. In this case, a larger
-city council may have more partisan councilors aligned with the mayor, reducing
-the mayor's bargaining costs and increasing the equilibrium public goods
-provision.
+partisanship decreases bargaining costs when the chances of electing
+government-aligned councilors are sufficiently high. Lower bargaining costs
+release funds for mayors to invest in public goods provision. In this case, a
+larger city council may add more members to the government coalition, thus
+reducing the mayor's bargaining costs and increasing the equilibrium public
+goods provision.
 
@@
 By asking councilors what they would like to provide to voters, we find that
-councilors mainly demand job appointments, as these increase their reelection
-prospects and improve municipal welfare. These findings are in line with
-quantitative results from a novel dataset we built with 346,553 laws passed in
-63 municipalities within ten thousand inhabitants away from the cutoffs. We see
-that legislation in municipalities both on the left- and on the right-hand side
-of the cutoffs mention public goods provision. However, municipalities with
-larger city councils have 15 percent more proposals about public goods
-provision, which is consistent with our argument.
+councilors mainly demand job appointments, which are regarded as an effective
+means to boost their reelection prospects and improve municipal welfare. These
+findings are in line with quantitative results from a novel dataset we built
+with 346,553 laws passed in 63 municipalities within ten thousand inhabitants
+away from the cutoffs. While all municipalities mention public goods in their
+legislation, those with larger city councils have 15 percent more proposals
+about public service delivery, which is consistent with our argument.
 
@@
 born and reduces postneonatal mortality by 0.90 children per one thousand
-infants that survived their first 28 days. Larger councils also increase
+infants who survived their first 28 days. Larger councils also increase
 enrollment by 2.58 children in elementary education classrooms without reducing
@@
 bargaining and \citet{ray2015coalition} for a review on coalition formation.}
-In this paper, we extend the \citet{baron1989bargaining} model under closed
+In this article, we extend the \citet{baron1989bargaining} model under closed
 rules and add the mayor's first move and political partisanship. We consider
 partisanship as a zero-sum effect that is positive for politicians aligned with
-the mayor and negative otherwise. This paper investigates the often overlooked
-effect of legislature size on the bargaining equilibrium strategies.
+the mayor and negative otherwise. We investigate the often overlooked effect of
+legislature size on the bargaining equilibrium strategies.
 
@@
 only 440 times in the same year. When we expand the search for the past five
-years, we see that De Blasio was mentioned 8,978 while the 49 seating city
-councilors were mentioned 2,046 times.\footnote{We computed these figures using
-the Dow Jones Factiva Database in November 2021.} On average, the mayor was
-cited four times more often than all the city councilors combined. This
-executive dominance has implications for policymaking, as coalitions and
+years, we see that De Blasio was mentioned 8,978 times while the 49 seating
+city councilors were mentioned only 2,046 times.\footnote{We computed these
+figures using the Dow Jones Factiva Database in November 2021.} On average, the
+mayor was cited four times more often than all the city councilors combined.
+This executive dominance has implications for policymaking, as coalitions and
 affinity with the executive are going to be crucial for service provision
@@
 Solving the game by backward induction requires us to start with the
-councilors' strategies. However, to conserve space, assume that we solved the
+councilors' strategies. To conserve space, assume that we solved the
 game for the councilors and found the equilibrium bargaining costs $C_G(N)$
@@
 \begin{proposition}\label{prop1}
-Public goods provision increases with legislature size when the bargaining costs decrease with legislature size.
+Public goods provision increases with legislature size if bargaining costs decrease with legislature size.
 \end{proposition}
@@
 Also, the threshold $\underline{\gamma}$ that captures the probability of
-electing a mayor-aligned policitian decreases along with the political value of
+electing a government supporter decreases along with the political value of
 policy $p$ and the size of the legislature $N$. This means that intensive
@@
 label=H\arabic*.]
-  \item Bargaining costs decrease with legislature size when the chances of electing a government-aligned legislator are sufficiently high.
+  \item Bargaining costs decrease with legislature size when the chances of electing a government partisan are sufficiently high.
   \item Public goods provision increases if bargaining costs decrease with legislature size.
@@
 1988 Brazilian Constitution set only broad guidelines about the number of
-council seats in each municipality, thus allowing cities to determine how many
-legislators they should have in their local chambers. This led to severe
-imbalances in the proportion of representatives per citizen across the country.
-For instance, the Nova Russas municipality had 30,009 inhabitants and 21
-councilors, accounting for one legislator per 1,429 citizens. In contrast, the
-city of Sorocaba had only 15 councilors for 528,735 inhabitants, that is, one
-legislator per 35,249 citizens. In 2003, this malapportionment problem gained
-national visibility when Mira Estrela, a small municipality with only 2,651
-residents, reduced its city council from 11 to 9 seats because of fiscal
-considerations. The change motivated a legal dispute that reached the Brazilian
-Supreme Court. The Court favored the city's decision and ruled that the size of
-every local council should correspond to precise population thresholds.
+council seats in each municipality, allowing cities to determine how many
+legislators their local chambers should have. This led to severe imbalances in
+the representation ratio across the country. For instance, the Nova Russas
+municipality had 30,009 inhabitants and 21 councilors, or one legislator per
+1,429 citizens. In contrast, the city of Sorocaba had only 15 councilors for
+528,735 inhabitants, that is, one legislator per 35,249 citizens. In 2003, this
+malapportionment problem gained national visibility when Mira Estrela, a small
+municipality with only 2,651 residents, reduced its city council from 11 to 9
+seats because of fiscal considerations. The change motivated a legal dispute
+that reached the Brazilian Supreme Court. The Court favored the city's decision
+and ruled that the size of every local council should correspond to precise
+population thresholds.
 
@@
 Brazil also adopts a unique formula to allocate seats, which combines the Hare
-quota and the D'Hondt method and favors larger parties
+quota and the D'Hondt method and strongly favors larger parties
 \citep{nicolau2015sistemas}. This poses a major obstacle for small parties to
@@
 
-Third, we also collected 346,553 bills from cities within ten thousand
-inhabitants from the 2004 population thresholds. We selected 63 out of 202
-municipalities whose voting records were available online. We evaluate proposal
-types, discriminating between local public goods, oversight, and other
-legislative activity. Examples of the local public goods are investing in a
-public health clinic, requesting school staff to accommodate an extra child,
-renovating sewage, and fixing potholes on a given street.\footnote{Our theory
-does not differentiate between clientelism and broad service provision, as it
-is hard to disentangle differences in the local level legislation. A voter may
-request a particular service, such as fixing a pothole. Attending this request
-can be interpreted as a clientelistic practice. Still, the provision of the
-service generates non-excludable benefits to the adjacent neighborhood.}
-Oversight bills are accountability and transparency mechanisms meant to keep
-public services provision in check. Other legislation comprises bills that do
-not fit in the previous categories, such as changes in street names, motions to
-honor citizens or groups, and legislative and internal city council procedures.
-We provide further information about the legislation dataset and the city
-council survey in sections A.13 and A.14 of the Supplementary Materials.
+Third, we collected 346,553 bills from cities within ten thousand inhabitants
+from the 2004 population thresholds. We selected 63 out of 202 municipalities
+whose voting records were available online. We evaluated proposal types,
+discriminating between local public goods, oversight, and other legislative
+activity. Examples of the local public goods are investing in a public health
+clinic, requesting school staff to accommodate an extra child, renovating
+sewage, and fixing potholes on a given street.\footnote{Our theory does not
+differentiate between clientelism and broad service provision, as it is hard to
+disentangle differences in the local level legislation. A voter may request a
+particular service, such as fixing a pothole. Attending this request can be
+interpreted as a clientelistic practice. Still, the provision of the service
+generates non-excludable benefits to the adjacent neighborhood.} Oversight
+bills are accountability and transparency mechanisms meant to keep public
+services provision in check. Other legislation comprises bills that do not fit
+in the previous categories, such as changes in street names, motions to honor
+citizens or groups, and legislative and internal city council procedures. We
+provide further information about the legislation dataset and the city council
+survey in sections A.13 and A.14 of the Supplementary Materials.
 
@@
 Brazil, from the political mechanism to the municipal welfare consequences of
-the council size ruling. Summary statistics and variable descriptions follow in
-section A.2 of the Supplementary Materials.
+the council size ruling. Summary statistics and variable descriptions are
+available in section A.2 of the Supplementary Materials.
 
@@
 
+\vspace{.4cm}
+
 \begin{table}[!htpb] \centering 
@@
 coalition. The model hypothesis stated that the probability of electing a city
-councilor aligned with the mayor is sufficiently high. However, sufficiently
-high can be ambiguous, and it depends on the intensity of the political
-disagreement and the current legislature size. In any case, 91\% chance is a
-considerably large quantity, and the extra city councilor is going to the
-mayoral coalition nine in every ten legislature size increases. This
+councilor who is aligned with the mayor is sufficiently high. However,
+sufficiently high can be ambiguous, and it depends on the intensity of the
+political disagreement and the current legislature size. In any case, 91\%
+chance is a considerably large quantity, and the extra city councilor is going
+to the mayoral coalition nine in every ten legislature size increases. This
 strengthens the political position of the mayor and diminishes bargaining
@@
 regressions were statistically insignificant.
-
-In terms of education, with the addition of a city councilor, enrollment in
-elementary schools increased by 2.58 children on average per school. This
-represents a change of around 0.20 standard deviations. Besides the influence
-of the mayoral support, enrollment can also directly impact the councilor's
-representation: Councilors can pressure the bureaucracy to accommodate a few
-extra students. With support from the mayor, they can help voters get access to
-schools, improving the welfare of voters. Education quality remains unchanged,
-but with more students in the classroom, it could potentially decrease. As
-expected, the placebo regressions are insignificant.
 
@@
 
+In terms of education, with the addition of a city councilor, enrollment in
+elementary schools increased by 2.58 children on average per school. This
+represents a change of around 0.20 standard deviations. Besides the influence
+of the mayoral support, enrollment can also directly impact the councilor's
+representation: Councilors can pressure the bureaucracy to accommodate a few
+extra students. With support from the mayor, they can help voters get access to
+schools, improving the welfare of voters. Education quality remains unchanged,
+but with more students in the classroom, it could potentially decrease. Again,
+the placebo regressions are insignificant.
+
 ## Robustness to Alternative Mechanisms
@@
 Brazil improves with larger legislatures. This is because the chances of
-electing a city councilor aligned with the mayor are 91 percent, thanks to the
-rule of distributing seats adopted in the country. In the Supplemental
-Materials, we also run regressions in placebo cutoffs between the actual
-cutoffs, showing that our estimates are consistently null when we are indeed
-supposed to find insignificant results.
+electing a government-aligned candidate are 91 percent thanks to the rule of
+distributing seats adopted in the country. In the Supplemental Materials, we
+also run regressions in placebo cutoffs between the actual cutoffs, showing
+that our estimates are consistently null when we are indeed supposed to find
+insignificant results.
 
@@
 with additional legislators having a positive or negative impact on welfare
-depending on certain electoral characteristics. Finally, it remains uncertain
-how other legislative features affect citizen well-being. For example, city
+depending on certain electoral characteristics. Finally, it remains unclear how
+other legislative features affect citizen well-being. For example, city
 councils may vary in size, monetary compensation for councilors, committee
 structure, and internal power structure. Understanding how legislature size
-interacts with other features would improve our knowledge about how local
-legislatures impact public service delivery. These questions are crucial for
-institution design and welfare in developing democracies.
+interacts with other features would improve our knowledge about the impact of
+local and national legislatures impact public services. These questions are
+crucial for institution design and welfare in developing democracies.
 

### 2022-04-18 Memo/memo.Rmd
add memo, small edits to manuscript

--- 2022-03-11 Memo/Memo_Template.Rmd
@@
 ---
-title: 
-to:
-from: 
-date: "`r Sys.time()`"
+title:  |
+        | Legislature Size and Welfare: Evidence from Brazil
+author: Response to Reviewers
+date: \today
+fontsize: 12pt
+margin: 2cm
+urlcolor: darkblue
+linkcolor: Mahogany
+citecolor: Mahogany
+spacing: single
+papersize: a4paper
+bibliography: references.bib
+biblio-style: apalike
 output:
   pdf_document:
-    template: article-template.latex
-bibliography: references.bib
-
+    citation_package: natbib
+    fig_caption: yes
+    number_sections: no
+    keep_tex: no
+    toc: no
+    toc_depth: 3
+    template: memo-template.latex
+    md_extensions: +raw_attribute
 ---
 
-We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript.
-We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result.
-Below, we intersperse our reactions and revisions to the suggestions enumerated in the editor's decision letter and the three manuscript reviews.
-We adopt the following conventions:
+\noindent Dear Editors and Reviewers,
+\vspace{.5cm}
 
-\begin{itemize}
-\item Suggestions identified in reviewers' reports are in \textit{italicized text}. We provide direct quotations of their reviewers' reports, lightly edited for clarifications or to conserve space.
-\item Our responses to the reviewers' suggestions are in standard text.
-\item The specific locations in the manuscript and online Appendix where incorporated
-revisions can be found are shown in \textbf{bold text}.
-\end{itemize}
+\noindent We would like to thank you all for the opportunity to revise our
+manuscript, "Legislature Size and Welfare: Evidence from Brazil" (Ms. No.
+AJPS-44979). We have made several revisions to the paper along the lines
+suggested by the Editors and Reviewers and we believe the manuscript has
+improved significantly as a result.
 
-\section{Suggestions Raised by Reviewer 1}
-\begin{itemize}
-\item \textit{Overall the literature review is strong.
-I would recommend a couple of additions.
-Include among them is an important work the authors should cite on legislative size and spending and that is \citet{GilliganMatsusaka2001} article entitled "Fiscal Policy, Legislature Size, and Political Parties: Evidence from the First Half of the Twentieth Century." Their findings are relevant for this study and should be referenced.
-In addition, the recently published book Population and Politics: The Impact of Scale by Gerring and Veenendaal which has a comprehensive analysis of this topic should also be incorporated into the literature review.}
+Following Reviewers 1 and 2, we have incorporated additional literature into
+the manuscript, which has given the paper a clearer theoretical framework
+through which our results can be interpreted. We have also discussed the scope
+conditions of our findings in further detail and included a new paragraph
+explaining why newly-elected councilors tend to join pro-mayor coalitions, thus
+addressing two important concerns raised by Reviewer 3. We believe these
+changes have made the paper clearer and more comprehensive.
+
+In response to comments from Reviewer 1, we have revised our Methods section to
+clarify our selection of independent variables, including the use of dummy
+variables to improve the accuracy of our estimates, and to provide further
+information about our online survey. Additionally, we have included a new
+section in the Supplemental Materials to explain how our survey was conducted
+and how they contribute to our results. We believe these addition also give the
+paper a better theoretical frame to help readers sort through the (many)
+results we present.
+
+Below we discuss in more detail these changes and the several others we have
+made to the manuscript in response to comments from the editors and reviewers.
+We thank the editors again for the opportunity to revise the manuscript, and
+the reviewers for their extremely helpful comments.
+
+\vspace{.5cm}
+\noindent Sincerely,
 
 \vspace{.2cm}
-We thank reviewer 1 for these two relevant additions.
-We cite \citet{GilliganMatsusaka2001}'s article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p.
-85]{gerring2020population}.
+\noindent The Authors
 
-\vspace{.5cm}
+# Reviewer 1 Comments and Responses
 
-\item \textit{In examining the relationship between legislative size and welfare why were education and health care selected as the independent variables?
-Was that decision based on data availability or were there another basis for the decision?
-It is not clear in the text of the manuscript.}
+\noindent 1) Reviewer 1 writes: "Overall the literature review is strong. I
+would recommend a couple of additions. Include among them is an important work
+the authors should cite on legislative size and spending and that is Gilligan
+and Matsusaka's 2001 article entitled 'Fiscal Policy, Legislature Size, and
+Political Parties: Evidence from the First Half of the Twentieth Century.'
+Their findings are relevant for this study and should be referenced. In
+addition, the recently published book \textit{Population and Politics: The
+Impact of Scale} by Gerring and Veenendaal which has a comprehensive analysis
+of this topic should also be incorporated into the literature review."
 
 \vspace{.2cm}
-We thank R1 for the opportunity to clarify the selection of these two central variables for our paper.
-We explain our decision on \textbf{page 17}: "Access to basic education and health care are relevant goals to developing countries.
-For instance, according to Brazil's 1988 Constitution, municipalities have to spend 25\% of their budget on education and 15\% on health care.
-Consequently, the Health Ministry Data Service and the Ministry of Education Data Service provide readily available quality data on health care and education."
 
-\vspace{.5cm}
+\noindent \textbf{Response:}
+
+\begin{quote}
+
+We thank Reviewer 1 for these two relevant suggestions. We now cite Gilligan
+and Matsusaka's 2001 article three times in our paper. We mention it twice in
+our Introduction, first on page 2: ``\textit{On the one hand, enlarged
+legislatures may reduce political particularism and increase overall government
+spending, which can lead to more public goods (Gerring and Veenendaal 2020;
+Gilligan and Matsusaka 2001; Weingast et al. 1981)}'', and then on page 4:
+``\textit{The corollary of the "law of $1/n$" is that increasing legislature
+size promotes excessive public spending, regardless of the partisan makeup of
+the legislature (Gilligan and Matsusaka 2001)}''. We also cite it in our Theory
+section (page 7): ``\textit{Yet, Gilligan and Matsusaka (2001) find that in the
+US legislature size is associated primarily with higher spending on
+geographically concentrated benefits, such as education and highways}''.
+
+We cite Gerring and Veenendaal's book four times. We mention it twice on page
+2: ``\textit{Legislature size is known to have a significant effect on
+collective action strategies, the bargaining power between state branches,
+government spending, and representation (Crain 1979; Freire et al. 2021;
+Gerring and Veenendaal 2020; Primo and Snyder Jr. 2008; Rogers 2002; Weingast
+et al. 1981). However, how legislature size impacts social welfare remains less
+understood. On the one hand, enlarged legislatures may reduce political
+particularism and increase overall government spending, which can lead to more
+public goods (Gerring and Veenendaal 2020; Gilligan and Matsusaka 2001;
+Weingast et al. 1981)}''. We mention the book again on page 4:
+``\textit{Following the seminal contribution by Weingast et al. (1981), the
+"law of $1/n$" posits that larger legislatures increase the legislative pressure
+for providing targeted public goods to local supporters at the expense of the
+entire polity (Freire et al. 2021). This question has become more relevant
+since legislature size has increased consistently over time (Gerring and
+Veenendaal 2020)}''. Finally, we also cite it on page 6: ``\textit{Larger
+legislatures improve representation as both the election thresholds and the
+ratio of population-per-politician decrease, which facilitate the electoral
+success of ethnic and political minorities (Allen and Stoll 2014; Gerring and
+Veenendaal 2020)}.''
+
+\end{quote}
+
+\noindent 2) Reviewer 1 writes: "In examining the relationship between
+legislative size and welfare why were education and health care selected as the
+independent variables? Was that decision based on data availability or were
+there another basis for the decision? It is not clear in the text of the
+manuscript."
 
 \vspace{.2cm}
-\item \textit{The details of the online survey conducted of Brazilian city councilors are lacking.
-What is the empirical contribution to the study?
-Beyond the online format what were the other administrative details involved with collecting that data?}
 
-We agree with R1 that we needed to provide more information on the online survey.
-Therefore, we detailed our procedures in the \textbf{Appendix Section A.14, on pages 22-23}.
-We also reference it \textbf{on pages 17 and 22 (footnote 13)} in the main article.
+\noindent \textbf{Response:}
 
-\vspace{.5cm}
+\begin{quote}
 
-\item \textit{The models include a dummy variable for the northeast region.
-What specifically about this region would require adding it to the model.
-I am generally skeptical about including such a variable particularly since clustered standard errors are being estimated for municipal level.
-Is there logical reason to control for regional effects here?
-Very curious modeling decision by the authors.}
+We thank Reviewer 1 for the opportunity to clarify the selection of these two
+sets of variables for our paper. We explain our decision on page 17:
+"\textit{Our focus is on the impact of legislature size on education and health
+care, which are the two most important public services the municipal government
+should provide to citizens. According to Brazilian Constitution, municipalities
+must spend 25\% of their budget on education and 15\% on health care.
+Consequently, the Ministry of Health and the Ministry of Education provide
+readily available, fine-grained data on health care and education at the
+municipal level, which we leverage in this study}."
+
+\end{quote}
+
+\noindent 3) Reviewer 1 writes: "The details of the online survey conducted of
+Brazilian city councilors are lacking. What is the empirical contribution to
+the study? Beyond the online format what were the other administrative details
+involved with collecting that data?"
 
 \vspace{.2cm}
-\textbf{FALTA FAZER: Dummy para a região Nordeste: estimar os modelos sem a dummy e reportar este resultado no artigo.
-Corrigir as menções aos coeficientes caso eles mudem.
-Colocar as regressões com a dummy no apêndice.}
 
-\vspace{.5cm}
+\noindent \textbf{Response:}
 
-\end{itemize}
-\section{Suggestions Raised by Reviewer 2}
-\begin{itemize}
-\item \textit{One minor issue for the author(s) to consider in future research: on p.
-14 the paper states, "On average, municipal taxes account for only 5\% of the local budgets, while mandatory transfers from state and federal governments correspond to the remaining 95\%.
-This reduces the ability of municipal legislators to effectively increase local spending, which makes improvements in local services dependent only on the composition of their local investments." There is an alternative mechanism that the author(s) has not considered and that has been shown to work in resource allocations to municipalities in Japan under similar circumstances.
-A recent paper by \citet{catalinac2020tournament} tests a formal model in which variance in centrally-provided local municipality resources is a function of a tournament among municipalities within a larger legislative district.
-Perhaps future research might compare the impact of the tournament structure with the local city council effects in Brazil as studied here.}
+\begin{quote}
+
+We agree with Reviewer 1 that we needed to provide more information on the
+online survey. Therefore, we have detailed our procedures in Section A.14 of
+the Supplementary Materials (pages 22-23), and we also reference the survey on
+pages 17 and 22 (footnote 13) in the main article.
+
+\end{quote}
+
+\noindent 4) Reviewer 1 writes: "The models include a dummy variable for the
+northeast region. What specifically about this region would require adding it
+to the model. I am generally skeptical about including such a variable
+particularly since clustered standard errors are being estimated for municipal
+level. Is there logical reason to control for regional effects here? Very
+curious modeling decision by the authors."
 
 \vspace{.2cm}
-We agree with R2 that testing the proposed mechanism is an extremely exciting project for a follow-up article.
-In our \textbf{conclusion, on page 29,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."
 
-\vspace{.5cm}
+\noindent \textbf{Response:}
 
-\end{itemize}
-\section{Suggestions Raised by Reviewer 3}
-\begin{itemize}
-\item \textit{The central story rests on some assumptions that I would like to see justified.
-Do mayor's generally want to spend more, and the city council holds them back?
-Why?
-I wonder about this assumption.
-Why does increasing the size of the city council usually result in pro-mayor additions?
-Under what conditions might increasing the size of the council bring in more diverse viewpoints or more polarized policy stances?
-What role is partisanship playing?
-It seems like it is mainly a proxy for agreement between councilors and the mayor, but do different parties have strongly different policy preferences?
-Does that matter for the results presented here?}
+\begin{quote}
+
+\textbf{TO DO.}
 
 \vspace{.2cm}
-\textbf{FALTA COMPLETAR:} We collapse two paragraphs from R3 since they speak to core topics in our paper.
-\textbf{In the Appendix Table XXX, on page XXX,} we show that an extra-legislator usually does not increase the municipal spending significantly.
-Therefore, our results speak more about the allocation of resources than on public spending.
-\textbf{On page 15, in the Background on the Brazilian Case Section,} we clarify why increasing the city council size usually results in a pro-mayor legislator.
-"Additionally, Brazil's formula for apportioning legislative seats (a combination of the Hara quota and the D'Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat.
-As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p.
-68]{Ames2001}.
-Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition." See also \textbf{footnote 12, on page 21-22.} Unfortunately, we could not find evidence that an extra-legislator improves descriptive representation in the city council, for instance, more female or non-white legislators \textbf{(see Table 4).} Finally, \textbf{in the Appendix, on page XX,} we show that the mayors' party is not driving the results.
 
-\vspace{.5cm}
+We would like to thank Reviewer 1 for their helpful comments and suggestions.
+\end{quote}
 
-\item \textit{I wonder about the scope conditions.
-The evidence for the patterns presented from Brazil are very convincing, but I'd like to see more discussion of why these patterns hold in Brazil and how they might be different/ similar elsewhere.}
+# Reviewer 2 Comments and Responses
+
+\noindent 1) Reviewer 2 writes: "One minor issue for the author(s) to consider
+in future research: on p. 14 the paper states, "On average, municipal taxes
+account for only 5\% of the local budgets, while mandatory transfers from state
+and federal governments correspond to the remaining 95\%. This reduces the
+ability of municipal legislators to effectively increase local spending, which
+makes improvements in local services dependent only on the composition of their
+local investments." There is an alternative mechanism that the author(s) has
+not considered and that has been shown to work in resource allocations to
+municipalities in Japan under similar circumstances. A recent paper by Amy
+Catalinac, Bruce Bueno de Mesquita and Alastair Smith tests a formal model in
+which variance in centrally-provided local municipality resources is a function
+of a tournament among municipalities within a larger legislative district.
+Perhaps future research might compare the impact of the tournament structure
+with the local city council effects in Brazil as studied here."
 
 \vspace{.2cm}
-We acknowledge that the external validity of our findings might be conditional on the contextual characteristics of our study.
-\textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending.
-Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.
-\citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016.
-Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways.
-These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment."
-Additionally, \textbf{in the Discussion Section, on page 29,} we write about the implications of our findings beyond Brazil.
-In this paragraph, we added the following new sentence: "As a caveat, our results might not be externally valid under different institutional norms (e.g., election rules or methods to allocating legislative seats) or at other governmental levels (federal or state).
-The findings presented here might also not be linear, since the impact of an extra-legislator should be heterogeneous depending upon the size of different legislatures or jurisdictions."
 
-\vspace{.5cm}
+\noindent \textbf{Response:}
 
-\end{itemize}
+\begin{quote}
+
+We agree with R2 that testing the proposed mechanism is an extremely exciting
+project for a follow-up article. In the Discussion section (page 29), we write:
+"\textit{Second, future research could evaluate whether additional legislators
+help mayors gain access to federal or state transfers in countries where
+resources are centrally provided, such as Japan. As suggested by Catalinac et
+al. (2020), in these situations the national government can create a tournament
+between municipalities and provide resources to those which offer more
+electoral support. Scholars might want to analyze whether this tournament
+structure interacts with the mechanisms we suggest in this paper}."
+
+\vspace{.2cm}
+
+We would like to thank Reviewer 2 for their helpful comments and suggestions.
+
+\end{quote}
+
+# Reviewer 3 Comments and Responses
+
+\noindent 1) Reviewer 3 writes: "The central story rests on some assumptions
+that I would like to see justified. Do mayor's generally want to spend more,
+and the city council holds them back? Why? I wonder about this assumption. Why
+does increasing the size of the city council usually result in pro-mayor
+additions? Under what conditions might increasing the size of the council bring
+in more diverse viewpoints or more polarized policy stances? What role is
+partisanship playing? It seems like it is mainly a proxy for agreement between
+councilors and the mayor, but do different parties have strongly different
+policy preferences? Does that matter for the results presented here?"
+
+\vspace{.2cm}
+
+\noindent \textbf{Response:}
+
+\begin{quote}
+
+We collapse two concerns from Reviewer 3 since they both speak to core topics
+in our paper. In Table \textbf{XX} of the Supplementary Materials (page
+\textbf{XX}), we show that an additional legislator usually does not lead to
+significant increases in public expenditure. Therefore, our results speak more
+about the allocation of resources than about government spending. In our
+section titled "Background on the Brazilian Case" (page 15), we clarify why
+increasing the city council size often results in a pro-mayor legislator. We
+write: "\textit{Brazil also adopts a unique formula to allocate seats, which
+combines the Hare quota and the D’Hondt method and strongly favors larger
+parties (Nicolau 2015). This poses a major obstacle for small parties to reach
+the electoral quorum, so they often join party coalitions to improve their
+chances of winning legislative seats (Ames 2001, p. 68). In Brazil, mayors are
+usually members of the largest coalitions (Poulsen and Varjao 2018), thus there
+is an incentive for candidates to side with the mayor before and after the
+election}." We mention that information again on page 22, footnote 12:
+"\textit{The effect of city council size on the number of mayor-aligned
+politicians stems from the rounding rule adopted by the proportional
+representation system in Brazil. The rounding rule favors the coalitions with
+more votes. Most of the time, the coalition of the elected mayor is the one
+that receives more votes.}".
+
+We did not find evidence that electing an additional legislator improves
+descriptive representation in the city council. For instance, we see no
+significant increase in the number of more female or non-white legislators, as
+shown in Table 4 (page 27). Finally, we show in Section \textbf{AAA} of the
+Supplementary Materials (page \textbf{XX}) that the mayors' parties are driving
+our results.
+
+\end{quote}
+
+\noindent 2) Reviewer 3 writes: "Finally, I wonder about the scope conditions.
+The evidence for the patterns presented from Brazil are very convincing, but
+I'd like to see more discussion of why these patterns hold in Brazil and how
+they might be different/ similar elsewhere."
+
+\vspace{.2cm}
+
+\noindent \textbf{Response:}
+
+\begin{quote}
+
+We entirely agree with Reviewer 3 that we need to discuss the scope conditions
+of our findings in more detail. We acknowledge that the external validity of
+our findings might be conditional on the contextual characteristics of our
+study. We have rewritten two paragraphs in the Discussion (page 29) to highligh
+the implications and limits of our findings. We write: "\textit{Our findings
+have implications that extend well beyond Brazil. A general form of our
+argument is that it is easy for a politician to negotiate with members of her
+in-group (Abbink and Harris 2019; Alt et al. 2018). Specifically, several
+countries have separate executive and legislative powers, such as the federal
+level of presidential systems, state governments, and local city councils. As
+these political bodies are influenced by political allegiances, the dynamics we
+expose here may be generalizable. Depending on legislative support, changing
+the legislature size could increase the chance of electing politicians that are
+not aligned with the executive, hence decreasing welfare. Despite the
+particular effects on political support and welfare, the logic described in
+this paper would remain relevant for empirically accessing the effect of
+enlarged legislatures on welfare. mtex-ac)vOur findings may also help scholars
+understand why other countries in Latin America and Asia can generate effective
+governance despite having strong executives and large coalitions (Pereira and
+Melo 2012)}".
+
+In the next paragraph (page 29), we indicate some of the limitations of our
+findings and encourage scholars to conduct further research on the topic. We
+write: "\textit{This paper opens several questions for future analysis. [...]
+Third, scholars might want to investigate whether our findings remain valid
+under different conditions. It is possible that the mechanisms we present here
+are non-linear, with additional legislators having a positive or negative
+impact on welfare depending on certain electoral characteristics. Finally, it
+remains unclear how other legislative features affect citizen well-being. For
+example, city councils may vary in size, monetary compensation for councilors,
+committee structure, and internal power structure. Understanding how
+legislature size interacts with other features would improve our knowledge
+about the impact of local and national legislatures impact public services.
+These questions are crucial for institution design and welfare in developing
+democracies.}"
+
+We would like to thank Reviewer 3 for their comments and suggestions.
+\end{quote}

### 2022-04-18 article/article.Rmd
add memo, small edits to manuscript

@@
 the 2009 legislature size change and finds a null effect in service provision
-from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} finds that in the US
+from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} find that in the US
 legislature size is associated primarily with higher spending on geographically

### 2022-04-18 Memo/memo.Rmd
change sentence response r3 memo

@@
 this paper would remain relevant for empirically accessing the effect of
-enlarged legislatures on welfare. mtex-ac)vOur findings may also help scholars
+enlarged legislatures on welfare. Our findings may also help scholars
 understand why other countries in Latin America and Asia can generate effective

### 2022-04-18 Memo/memo.Rmd
capitalise some words

@@
 Below we discuss in more detail these changes and the several others we have
-made to the manuscript in response to comments from the editors and reviewers.
-We thank the editors again for the opportunity to revise the manuscript, and
-the reviewers for their extremely helpful comments.
+made to the manuscript in response to comments from the Editors and Reviewers.
+We thank the Editors again for the opportunity to revise the manuscript, and
+the Reviewers for their extremely helpful comments.
 

### 2022-04-18 Memo/memo.Rmd
edits to memo

@@
 information about our online survey. Additionally, we have included a new
-section in the Supplemental Materials to explain how our survey was conducted
-and how they contribute to our results. We believe these addition also give the
+section in the Supplemental Materials to explain how we conducted our survey
+and how it contributes to our results. We believe these addition also give the
 paper a better theoretical frame to help readers sort through the (many)

### 2022-05-15 article/article.Rmd
Update article.Rmd

@@
 experience a change provoked by the previous council size, confounding our
-estimates. The year and the Northeast dummies were added to improve efficiency.
-Adding controls improves efficiency in RDD and also enhances the consistency in
-the multiple thresholds RDD \citep{calonico2019regression}.
+estimates. The Northeast dummy was added to control for the fact that the Lula
+administration heavily invested in the region from 2003 until 2010, improving 
+several development indicators \citep{de2015politica}. The years were added 
+to improve efficiency. Moreover, adding controls improves efficiency in RDD
+\citep{calonico2019regression} and also enhances the consistency in the 
+multiple thresholds RDD.
 

### 2022-05-15 Memo/memo.Rmd
typo
partial revision

@@
 section in the Supplemental Materials to explain how we conducted our survey
-and how it contributes to our results. We believe these addition also give the
+and how it contributes to our results. We believe these additions also give the
 paper a better theoretical frame to help readers sort through the (many)
@@
 
-\textbf{TO DO.}
+We thank Reviewer 1 for the opportunity to clarify the selection of the control variables in our empirical analysis.
+The inclusion of control variables in our model has two purposes.
+The first one is to improving the consistency of the estimates.
+In section XXXX of the appendix, we show by simulation that adding controls improve the consistency of the point estimate, for several distributions of the running variables.
+In the section XXXX of the appendix, we show that for our data, it improves consistency significantly in both the main estimates and the placebo one.
+Table XXXX in section XXXX (reproduced below), shows that without controls, the estimated treatment effect is overXXXX and underXXXX.
+The reason for this improvement is that having control variables make the subpopulations more comparable across thresholds.
+
+XXXX PUT TABLE HERE
+
+The second reason, per \citet{calonico2019regression} results, is that adding control variables improve efficiency in the estimates. Adding XXXX and XXXX, XXXX.
+
+To reflect these informations, we rewrote paragraph XXXX in section XXXX of the main text to:
+
+``XXXX''
 

### 2022-05-15 Memo/memo.Rmd
starting changes

@@
 
-We thank Reviewer 1 for the opportunity to clarify the selection of the control variables in our empirical analysis.
-The inclusion of control variables in our model has two purposes.
+We thank Reviewer 1 for the opportunity to clarify the selection of control variables in our empirical analysis.
+The inclusion of controls in our model has two purposes.
 The first one is to improving the consistency of the estimates.
-In section XXXX of the appendix, we show by simulation that adding controls improve the consistency of the point estimate, for several distributions of the running variables.
+In section XXXX of the appendix, we show by simulation that adding controls improve the consistency of the point estimates.
+This is true for several distributions of the running variables and XXXX assumptions for the treatment effects.
 In the section XXXX of the appendix, we show that for our data, it improves consistency significantly in both the main estimates and the placebo one.

### 2022-05-16 Memo/memo.Rmd
commit change memo

--- 2022-04-18 Memo/memo.Rmd
@@
 
-\textbf{TO DO.}
+We thank Reviewer 1 for the opportunity to clarify the selection of control variables in our empirical analysis.
+The inclusion of controls in our model has two purposes.
+The first one is to improve the consistency of the estimates.
+In section A.5 of the Appendix, we show by simulation that adding controls enhances the consistency of the point estimates.
+This is true for several distributions of the running variables and many assumptions regarding the shape of the treatment effects.
+Section 5 of the Main Paper demonstrates that it improves consistency significantly in both the main estimates and the placebo ones.
+Table 1 in Section 5 of the Main Paper (reproduced below), shows that without controls, we would overestimate the treatment effects (finding an increase of 1.63 legislators instead of a sharp increase of one legislator), and underestimate the placebo treatment effects (finding a significant decrease of 0.31 legislators where there was supposed to be no effects in legislature size).
+This substantial improvement is because having control variables makes the subpopulations in each threshold more comparable across all the thresholds, avoiding comparing cases to the left (right) of one given threshold with points in the right (left) of a different threshold.
+
+\begin{table}[H] \centering 
+  \caption{Research Design Validity Check (reproduction from the main paper)}
+    \scalebox{0.9}{
+  \begin{threeparttable}
+\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
+\toprule
+ & \multicolumn{4}{c}{\textbf{Panel A: Validity Check --- Treatment Effect on City Council Size}} \\ \cline{2-5}
+   & \multicolumn{1}{c}{\small{(1)}} & 
+ \multicolumn{1}{c}{\small{(2)}} & 
+ \multicolumn{1}{c}{\small{(3)}} & 
+ \multicolumn{1}{c}{\small{(4)}} \\
+
+ & \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} & 
+ \multicolumn{1}{c}{\small{Additional Num.}} & 
+ \multicolumn{1}{c}{\small{Placebo Add.}} \\ 
+  & \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Seats 2004}} & 
+  \multicolumn{1}{c}{\small{Num. Seats 2004}} \\
+  & \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(Without Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} & 
+  \multicolumn{1}{c}{\small{(With Controls)}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
+\\[-1.8ex] 
+ LATE & 1.63$^{***}$ & -0.31$^{**}$ & 1.00$^{***}$ & -0.00 \\ 
+  & (0.51) & (0.14) & (0.0004) & (0.0000) \\ 
+\hdashline \\[-1.8ex]   
+ N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
+Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
+Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
+BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
+BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
+\bottomrule
+\end{tabularx}
+\end{threeparttable}}
+\end{table}
+
+The second reason, per \citet{calonico2019regression} results, is that adding control variables improves the efficiency of our estimates.
+We add five controls to the main specifications.
+We added the population in 2003 because it conditions the multiple assignments.
+Adding the GDP per capita ensures that the gains detected are not resulting from the hot job market experienced during the period.
+We add the number of seats in 2000 to ensure that the results come from the current legislature size decision and not from their past seat allocation.
+We add the year to control for likely seasonal effects.
+Finally, we added a dummy for Northeast states.
+The Northeast region received considerable attention from the Federal Government in the 2000s.
+According to \citet{de2015politica}, the Lula government in 2003 recreated the Superintendency for the Development of the Northeast (SUDENE), investing BRL 84 Billion from 2003 to 2010.
+This amounts to around 70% of all targeted regional investments.
+One example of these investments is the number of Federal Educational Institutions: the Federal Government created about 100 university campuses in the region.
+Moreover, infant mortality in the Northeast region decreased from 22.4 deaths per 1000 infants born in 2005 to 19.6 deaths per 1000 infants born in 2008.
+Education quality improved from a 2.69 score in 2005 to a 3.14 score in 2007 (0 to 10 quality of education score).
+For this reason, adding a dummy for Northeast states is essential for ensuring the consistency and the efficiency of our estimates.
+
+To reflect these pieces of information, we rewrote paragraph five in Section 5 of the Main Text to:
+
+``\textit{(...) In the dataset, there are twelve discontinuities. At
+each threshold, there is a sharp increase of one councilor, from 9 to 21. When
+running an RDD on these discontinuities, a consistent estimator should fit the
+exact change of one councilor. However, if we pool all the discontinuities
+together with no correction, we find an increase in council size of 1.63
+councilors (see the first estimate in Table 1). This
+imbalance occurs because when we combine all the discontinuities, the model
+implies that municipalities below the 47,619 cutoffs (9 to 10 councilors) are
+comparable to changes in towns right above the 571,428 cutoffs (20 to 21
+council members). That is incorrect because the comparison is inconsistent in
+council size, and these municipalities diverge in many other aspects.}
+
+\textit{To avoid this problem, in section A.5 of the Supplemental Materials, we show by
+simulation that adding controls, especially the variables responsible for the
+multiple threshold assignments (in our case, the population in 2003), improves
+the consistency and efficiency of the estimates. Relying on this fact, we add
+five controls to the estimates: population in 2003; GDP per capita; the number
+of seats in 2000; year; and a dummy for Northeast municipalities. The
+reason for the first variable is the multiple threshold assignments. We add GDP
+per capita because wealthier cities tend to have better public services. The
+number of seats in 2000 intends to control that some municipalities could
+experience a change provoked by the previous council size, confounding our
+estimates. The Northeast dummy was added to control for the fact that the Lula
+administration heavily invested in the region from 2003 until 2010, improving 
+several development indicators \citep{de2015politica}. The years were added 
+to improve efficiency and control for seasonal effects.
+Moreover, adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.}''
+
+And we added the discussions here to the Appendix at the end of Section A.5.
+
+We want to highlight further that this decision to add controls in our case is also because of consistency.
+Even though clustered standard errors may provide the best standard errors for our model, this would not affect the consistency.
+And the consistency here relies on making the subpopulations comparable, i.e., the subpopulation of towns between 9 and 10 legislators as comparable as the subpopulation of towns between 10 and 11 legislators, and so on.
 

### 2022-05-16 Memo/memo.Rmd
update memo and appendix

@@
 papersize: a4paper
-bibliography: references.bib
+bibliography: ../article/references.bib
 biblio-style: apalike
@@
 In response to comments from Reviewer 1, we have revised our Methods section to
-clarify our selection of independent variables, including the use of dummy
-variables to improve the accuracy of our estimates, and to provide further
-information about our online survey. Additionally, we have included a new
-section in the Supplemental Materials to explain how we conducted our survey
-and how it contributes to our results. We believe these additions also give the
-paper a better theoretical frame to help readers sort through the (many)
-results we present.
+clarify our selection of independent variables, including the use of covariates
+to improve the efficiency and consistency of our estimates. Additionally, we
+have included a new section in the Supplemental Materials to explain how we
+conducted our survey and how it contributes to our results. We believe these
+additions also give the paper a better theoretical frame to help readers sort
+through the results we present.
 
@@
 
-We thank Reviewer 1 for these two relevant suggestions. We now cite Gilligan
-and Matsusaka's 2001 article three times in our paper. We mention it twice in
-our Introduction, first on page 2: ``\textit{On the one hand, enlarged
-legislatures may reduce political particularism and increase overall government
-spending, which can lead to more public goods (Gerring and Veenendaal 2020;
-Gilligan and Matsusaka 2001; Weingast et al. 1981)}'', and then on page 4:
+We thank Reviewer 1 for these two relevant suggestions. We now cite Gilligan and
+Matsusaka's 2001 article three times in our paper. We mention it twice in our
+Introduction, first on page 2: ``\textit{On the one hand, enlarged legislatures
+may reduce political particularism and increase overall government spending,
+which can lead to more public goods  \citep{gerring2020population,
+GilliganMatsusaka2001, Weingastetal1981}}'', and then in the end of page 4:
 ``\textit{The corollary of the "law of $1/n$" is that increasing legislature
 size promotes excessive public spending, regardless of the partisan makeup of
-the legislature (Gilligan and Matsusaka 2001)}''. We also cite it in our Theory
-section (page 7): ``\textit{Yet, Gilligan and Matsusaka (2001) find that in the
+the legislature \citep{GilliganMatsusaka2001}}''. We also cite it in our Theory
+section (page 7): ``\textit{Yet, \citet{GilliganMatsusaka2001} find that in the
 US legislature size is associated primarily with higher spending on
@@
 
-We cite Gerring and Veenendaal's book four times. We mention it twice on page
-2: ``\textit{Legislature size is known to have a significant effect on
-collective action strategies, the bargaining power between state branches,
-government spending, and representation (Crain 1979; Freire et al. 2021;
-Gerring and Veenendaal 2020; Primo and Snyder Jr. 2008; Rogers 2002; Weingast
-et al. 1981). However, how legislature size impacts social welfare remains less
-understood. On the one hand, enlarged legislatures may reduce political
-particularism and increase overall government spending, which can lead to more
-public goods (Gerring and Veenendaal 2020; Gilligan and Matsusaka 2001;
-Weingast et al. 1981)}''. We mention the book again on page 4:
-``\textit{Following the seminal contribution by Weingast et al. (1981), the
-"law of $1/n$" posits that larger legislatures increase the legislative pressure
-for providing targeted public goods to local supporters at the expense of the
-entire polity (Freire et al. 2021). This question has become more relevant
-since legislature size has increased consistently over time (Gerring and
-Veenendaal 2020)}''. Finally, we also cite it on page 6: ``\textit{Larger
-legislatures improve representation as both the election thresholds and the
-ratio of population-per-politician decrease, which facilitate the electoral
-success of ethnic and political minorities (Allen and Stoll 2014; Gerring and
-Veenendaal 2020)}.''
+We cite Gerring and Veenendaal's book four times. We mention it twice on page 2:
+``\textit{Legislature size is known to have a significant effect on collective
+action strategies, the bargaining power between state branches, government
+spending, and representation \citep{crain1979cost, freire2021legislature,
+gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
+However, how legislature size impacts social welfare remains less understood. On
+the one hand, enlarged legislatures may reduce political particularism and
+increase overall government spending, which can lead to more public goods
+\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}}''. We
+mention the book again on page 4: ``\textit{Following the seminal contribution
+by \citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
+increase the legislative pressure for providing targeted public goods to local
+supporters at the expense of the entire polity \citep{freire2021legislature}. This
+question has become more relevant since legislature size has increased
+consistently over time \citep{gerring2020population}}''. Finally, we also cite
+it on page 6: ``\textit{Larger legislatures improve representation as both the
+election thresholds and the ratio of population-per-politician decrease, which
+facilitate the electoral success of ethnic and political minorities
+\citep{allenrepresentation, gerring2020population}}.''
 
@@
 We thank Reviewer 1 for the opportunity to clarify the selection of these two
-sets of variables for our paper. We explain our decision on page 17:
-"\textit{Our focus is on the impact of legislature size on education and health
-care, which are the two most important public services the municipal government
-should provide to citizens. According to Brazilian Constitution, municipalities
-must spend 25\% of their budget on education and 15\% on health care.
-Consequently, the Ministry of Health and the Ministry of Education provide
+sets of variables for our paper. We included an explanation for our choice on
+page 17: "\textit{Our focus is on the impact of legislature size on education
+and health care, which are the two most important public services the municipal
+government should provide to citizens. According to the Brazilian Constitution,
+municipalities must spend 25\% of their budget on education and 15\% on health
+care. Consequently, the Ministry of Health and the Ministry of Education provide
 readily available, fine-grained data on health care and education at the
@@
 We agree with Reviewer 1 that we needed to provide more information on the
-online survey. Therefore, we have detailed our procedures in Section A.14 of
-the Supplementary Materials (pages 22-23), and we also reference the survey on
-pages 17 and 22 (footnote 13) in the main article.
+online survey. Therefore, we have detailed our procedures in Section A.14 of the
+Supplementary Materials (pages 22-23), and we also reference the survey on pages
+17 and 22 (footnote 13) in the main article. We rewrote paragraph 2 of Section
+6.2 to clarify the importance of the survey results in our paper. It reads as
+follows: ``\textit{We assume that city councilors want to extract rents and to
+get reelected. The rents come from continuing in the repeated game, and the
+partisanship discounts that benefit. Figure 2 shows that 65.9 percent of
+councilors mentioned that mayors use job appointments to consolidate their
+coalition support. Moreover, 59.0 percent of the surveyed councilors affirmed
+that mayors use personal favors, such as shifting resources to places where the
+councilors have electoral support, to solidify their governing coalition. This
+provides further evidence that mayors do offer city councilors the benefits they
+demand. In this regard, granting favors works as rent transfers for councilors.
+Job appointments are also convenient for the mayors because patronage in Brazil
+has positive results in terms of welfare \citep{toral2019benefits}.}''
 
@@
 
-We thank Reviewer 1 for the opportunity to clarify the selection of control variables in our empirical analysis.
-The inclusion of controls in our model has two purposes.
-The first one is to improve the consistency of the estimates.
-In section A.5 of the Appendix, we show by simulation that adding controls enhances the consistency of the point estimates.
-This is true for several distributions of the running variables and many assumptions regarding the shape of the treatment effects.
-Section 5 of the Main Paper demonstrates that it improves consistency significantly in both the main estimates and the placebo ones.
-Table 1 in Section 5 of the Main Paper (reproduced below), shows that without controls, we would overestimate the treatment effects (finding an increase of 1.63 legislators instead of a sharp increase of one legislator), and underestimate the placebo treatment effects (finding a significant decrease of 0.31 legislators where there was supposed to be no effects in legislature size).
-This substantial improvement is because having control variables makes the subpopulations in each threshold more comparable across all the thresholds, avoiding comparing cases to the left (right) of one given threshold with points in the right (left) of a different threshold.
+We thank Reviewer 1 for the opportunity to clarify the selection of control
+variables in our empirical analysis. The inclusion of controls in our model has
+two purposes. The first one is to improve the consistency of the estimates. In
+Section A.5 of the Appendix, we use simulation to show that the inclusion of
+covariates enhances the consistency of our point estimates. The simulation
+indicates improved consistency for several distributions of the running
+variables and different treatment effects. Section 5 of the manuscript
+demonstrates that it improves consistency in both the main estimates and the
+placebo ones. Table 1 (page 20, reproduced below) shows that without controls,
+we would overestimate the treatment effects (finding an increase of 1.63
+legislators instead of an increase of exactly one legislator), and underestimate
+the placebo treatment effects (finding a significant decrease of 0.31
+legislators where there was supposed to be no effects in legislature size). This
+substantial improvement is because having control variables makes the
+subpopulations in each threshold more comparable across all the thresholds,
+avoiding comparing cases to the left (right) of one given threshold with points
+in the right (left) of a different threshold.
 
@@
 
-The second reason, per \citet{calonico2019regression} results, is that adding control variables improves the efficiency of our estimates.
-We add five controls to the main specifications.
-We added the population in 2003 because it conditions the multiple assignments.
-Adding the GDP per capita ensures that the gains detected are not resulting from the hot job market experienced during the period.
-We add the number of seats in 2000 to ensure that the results come from the current legislature size decision and not from their past seat allocation.
-We add the year to control for likely seasonal effects.
-Finally, we added a dummy for Northeast states.
-The Northeast region received considerable attention from the Federal Government in the 2000s.
-According to \citet{de2015politica}, the Lula government in 2003 recreated the Superintendency for the Development of the Northeast (SUDENE), investing BRL 84 Billion from 2003 to 2010.
-This amounts to around 70% of all targeted regional investments.
-One example of these investments is the number of Federal Educational Institutions: the Federal Government created about 100 university campuses in the region.
-Moreover, infant mortality in the Northeast region decreased from 22.4 deaths per 1000 infants born in 2005 to 19.6 deaths per 1000 infants born in 2008.
-Education quality improved from a 2.69 score in 2005 to a 3.14 score in 2007 (0 to 10 quality of education score).
-For this reason, adding a dummy for Northeast states is essential for ensuring the consistency and the efficiency of our estimates.
+The second reason is that adding control variables improves the efficiency of
+our estimates \citep{calonico2019regression}. We add five controls to the main
+specifications. We include the 2003 population because it conditions the
+multiple threshold assignments. We add GDP per capita to control for Brazil's
+economic expansion during the 2000s. We also add the number of seats in 2000 to
+ensure that our results come from the current legislature size and not from past
+seat allocations. Year was included in the models to control for seasonal
+effects. Finally, we add a dummy for Northeast states. The Northeast region
+received considerable attention from the Federal Government in the 2000s.
+According to \citet{de2015politica}, in 2003 the Lula administration recreated
+the Superintendency for the Development of the Northeast (SUDENE), investing BRL
+84 Billion from 2003 to 2010. This amounts to around 70% of all targeted
+regional investments. One example of these investments is that the Federal
+Government created about 100 new universities in the Northeast region. Moreover,
+infant mortality in the region decreased from 22.4 deaths per 1000 infants born
+in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger federal
+investments. In turn, education quality improved from 2.69 in 2005 to a 3.14
+score in 2007 (0 to 10 quality of education score). For this reason, adding a
+dummy for Northeast states is essential for ensuring the consistency and the
+efficiency of our estimates.
 
-To reflect these pieces of information, we rewrote paragraph five in Section 5 of the Main Text to:
+To reflect these pieces of information, we rewrote paragraph five in Section 5
+of the manuscript to (page 19):
 
-``\textit{(...) In the dataset, there are twelve discontinuities. At
-each threshold, there is a sharp increase of one councilor, from 9 to 21. When
-running an RDD on these discontinuities, a consistent estimator should fit the
-exact change of one councilor. However, if we pool all the discontinuities
-together with no correction, we find an increase in council size of 1.63
-councilors (see the first estimate in Table 1). This
-imbalance occurs because when we combine all the discontinuities, the model
-implies that municipalities below the 47,619 cutoffs (9 to 10 councilors) are
-comparable to changes in towns right above the 571,428 cutoffs (20 to 21
-council members). That is incorrect because the comparison is inconsistent in
-council size, and these municipalities diverge in many other aspects.}
-
-\textit{To avoid this problem, in section A.5 of the Supplemental Materials, we show by
-simulation that adding controls, especially the variables responsible for the
-multiple threshold assignments (in our case, the population in 2003), improves
-the consistency and efficiency of the estimates. Relying on this fact, we add
-five controls to the estimates: population in 2003; GDP per capita; the number
-of seats in 2000; year; and a dummy for Northeast municipalities. The
-reason for the first variable is the multiple threshold assignments. We add GDP
-per capita because wealthier cities tend to have better public services. The
-number of seats in 2000 intends to control that some municipalities could
-experience a change provoked by the previous council size, confounding our
-estimates. The Northeast dummy was added to control for the fact that the Lula
-administration heavily invested in the region from 2003 until 2010, improving 
-several development indicators \citep{de2015politica}. The years were added 
-to improve efficiency and control for seasonal effects.
-Moreover, adding controls improves efficiency in RDD \citep{calonico2019regression} and also enhances the consistency in the multiple thresholds RDD.}''
+``[...] \textit{we add five controls to the estimates: population in 2003; GDP
+per capita; the number of seats in 2000; year; and a dummy for Northeast
+municipalities. The reason for the first variable is the multiple threshold
+assignments. We add GDP per capita because wealthier cities tend to have better
+public services. The number of seats in 2000 intends to control that some
+municipalities could experience a change provoked by the previous council size,
+confounding our estimates. The Northeast dummy was added to control for the fact
+that the Lula administration heavily invested in the region from 2003 until
+2010, improving several development indicators \citep{de2015politica}. The years
+were added to improve efficiency and control for seasonal effects. Moreover,
+adding controls improves efficiency in RDD \citep{calonico2019regression} and
+also enhances the consistency in the multiple thresholds RDD.}''
 
@@
 
-We want to highlight further that this decision to add controls in our case is also because of consistency.
-Even though clustered standard errors may provide the best standard errors for our model, this would not affect the consistency.
-And the consistency here relies on making the subpopulations comparable, i.e., the subpopulation of towns between 9 and 10 legislators as comparable as the subpopulation of towns between 10 and 11 legislators, and so on.
+We want to highlight further that this decision to add controls in our case is
+also because of consistency. Even though clustered standard errors may provide
+the best standard errors for our model, this would not affect the consistency.
+And the consistency here relies on making the subpopulations comparable, i.e.,
+the subpopulation of towns between 9 and 10 legislators as comparable as the
+subpopulation of towns between 10 and 11 legislators, and so on.
 
@@
 
-We agree with R2 that testing the proposed mechanism is an extremely exciting
+We agree with Reviewer 2 that testing the proposed mechanism is an exciting
 project for a follow-up article. In the Discussion section (page 29), we write:
@@
 help mayors gain access to federal or state transfers in countries where
-resources are centrally provided, such as Japan. As suggested by Catalinac et
-al. (2020), in these situations the national government can create a tournament
-between municipalities and provide resources to those which offer more
-electoral support. Scholars might want to analyze whether this tournament
-structure interacts with the mechanisms we suggest in this paper}."
+resources are centrally provided, such as Japan. As suggested by
+\citet{catalinac2020tournament}, in these situations the national government can
+create a tournament between municipalities and provide resources to those which
+offer more electoral support. Scholars might want to analyze whether this
+tournament structure interacts with the mechanisms we suggest in this paper}."
 
@@
 
-We collapse two concerns from Reviewer 3 since they both speak to core topics
-in our paper. In Table \textbf{XX} of the Supplementary Materials (page
-\textbf{XX}), we show that an additional legislator usually does not lead to
-significant increases in public expenditure. Therefore, our results speak more
-about the allocation of resources than about government spending. In our
-section titled "Background on the Brazilian Case" (page 15), we clarify why
-increasing the city council size often results in a pro-mayor legislator. We
-write: "\textit{Brazil also adopts a unique formula to allocate seats, which
-combines the Hare quota and the D’Hondt method and strongly favors larger
-parties (Nicolau 2015). This poses a major obstacle for small parties to reach
-the electoral quorum, so they often join party coalitions to improve their
-chances of winning legislative seats (Ames 2001, p. 68). In Brazil, mayors are
-usually members of the largest coalitions (Poulsen and Varjao 2018), thus there
-is an incentive for candidates to side with the mayor before and after the
-election}." We mention that information again on page 22, footnote 12:
-"\textit{The effect of city council size on the number of mayor-aligned
-politicians stems from the rounding rule adopted by the proportional
-representation system in Brazil. The rounding rule favors the coalitions with
-more votes. Most of the time, the coalition of the elected mayor is the one
-that receives more votes.}".
+We collapse two concerns from Reviewer 3 since they both speak to core topics in
+our paper. In Table 6 of the Supplementary Materials (page 21), we show that an
+additional legislator usually does not lead to significant increases in public
+expenditure. Therefore, our results speak more about the allocation of resources
+than about government spending. In our section titled "Background on the
+Brazilian Case" (page 14), we clarify why increasing the city council size often
+results in a pro-mayor legislator. We write (page 15): "\textit{Brazil also
+adopts a unique formula to allocate seats, which combines the Hare quota and the
+D’Hondt method and strongly favors larger parties \citep{nicolau2015sistemas}.
+This poses a major obstacle for small parties to reach the electoral quorum, so
+they often join party coalitions to improve their chances of winning legislative
+seats \citep[68]{Ames2001}. In Brazil, mayors are usually members of the largest
+coalitions \citep{poulsen2018political}, thus there is an incentive for
+candidates to side with the mayor before and after the election}." We mention
+that information again on page 22, footnote 12: "\textit{The effect of city
+council size on the number of mayor-aligned politicians stems from the rounding
+rule adopted by the proportional representation system in Brazil. The rounding
+rule favors the coalitions with more votes. Most of the time, the coalition of
+the elected mayor is the one that receives more votes.}".
 
@@
 descriptive representation in the city council. For instance, we see no
-significant increase in the number of more female or non-white legislators, as
-shown in Table 4 (page 27). Finally, we show in Section \textbf{AAA} of the
-Supplementary Materials (page \textbf{XX}) that the mayors' parties are driving
-our results.
+significant increase in the number of female or non-white legislators, as shown
+in Table 4 (page 27). Finally, we show in the table below that the mayors'
+parties are not driving our results. This result is also available on our GitHub
+repository. We ommitted it from the Supplementary Materials to conserve space.
+
+\begin{table}[!htbp] \centering 
+\caption{Councilors from Major Parties} 
+\label{appcouncilparty} 
+\resizebox{\textwidth}{!}{
+  \begin{tabular}{@{\extracolsep{\fill}}l c c c c} 
+  \\[-1.8ex]\hline \\[-1.8ex] 
+  & \multicolumn{1}{c}{\textbf{Councilors from PT}} & \multicolumn{1}{c}{\textbf{Councilors from PSDB}} & \multicolumn{1}{c}{\textbf{Councilors from PMDB}} & \multicolumn{1}{c}{\textbf{Councilors from PFL (DEM)}} \\
+  \hline \\[-1.8ex] 
+  LATE & -0.01 & -0.05 & -0.01 & -0.01 \\ 
+  & (0.02) & (0.05) & (0.03) & (0.02) \\ 
+  N Left & 5179 & 5179 & 5179 & 5179 \\ 
+  N Right & 343 & 343 & 343 & 343 \\ 
+  Eff N Left & 375 & 152 & 267 & 231 \\ 
+  Eff N Right & 212 & 121 & 172 & 159 \\ 
+  BW Loc Poly & 13.99 & 6.8 & 10.58 & 9.63 \\ 
+  BW Bias & 22.64 & 11.373 & 16.803 & 15.647 \\ 
+  \hline \\[-1.8ex] 
+  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\ 
+  \end{tabular} }
+\end{table}
 
@@
 of our findings in more detail. We acknowledge that the external validity of
-our findings might be conditional on the contextual characteristics of our
+our results might be conditional on the contextual characteristics of our
 study. We have rewritten two paragraphs in the Discussion (page 29) to highligh
-the implications and limits of our findings. We write: "\textit{Our findings
+the implication of our results. We write: "\textit{Our findings
 have implications that extend well beyond Brazil. A general form of our
 argument is that it is easy for a politician to negotiate with members of her
-in-group (Abbink and Harris 2019; Alt et al. 2018). Specifically, several
+in-group \citep{abbink2019, g9030057}. Specifically, several
 countries have separate executive and legislative powers, such as the federal
 level of presidential systems, state governments, and local city councils. As
-these political bodies are influenced by political allegiances, the dynamics we
+these institutions are influenced by political allegiances, the dynamics we
 expose here may be generalizable. Depending on legislative support, changing
@@
 understand why other countries in Latin America and Asia can generate effective
-governance despite having strong executives and large coalitions (Pereira and
-Melo 2012)}".
+governance despite having strong executives and large coalitions
+\citep{pereira2012surprising}.}".
 
@@
 legislature size interacts with other features would improve our knowledge
-about the impact of local and national legislatures impact public services.
+about how local and national legislatures impact public services.
 These questions are crucial for institution design and welfare in developing
@@
 \end{quote}
+
+\newpage

### 2022-05-16 appendix/appendix.Rmd
update memo and appendix

@@
 
+The inclusion of controls in our model has two purposes. The first one is to
+improve the consistency of the estimates. The second reason is that adding
+control variables improves the efficiency of our estimates
+\citep{calonico2019regression}. We add five controls to the main
+specifications. We include the 2003 population because it conditions the
+multiple threshold assignments. We add GDP per capita to control for Brazil's
+economic expansion during the 2000s. We also add the number of seats in 2000 to
+ensure that our results come from the current legislature size and not from
+past seat allocations. Year was included in the models to control for seasonal
+effects. Finally, we add a dummy for Northeast states. The Northeast region
+received considerable attention from the Federal Government in the 2000s.
+According to \citet{de2015politica}, in 2003 the Lula administration recreated
+the Superintendency for the Development of the Northeast (SUDENE), investing
+BRL 84 Billion from 2003 to 2010. This amounts to around 70% of all targeted
+regional investments. One example of these investments is that the Federal
+Government created about 100 new universities in the Northeast region.
+Moreover, infant mortality in the region decreased from 22.4 deaths per 1000
+infants born in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger
+federal investments. In turn, education quality improved from 2.69 in 2005 to a
+3.14 score in 2007 (0 to 10 quality of education score). For this reason,
+adding a dummy for Northeast states is essential for ensuring the consistency
+and the efficiency of our estimates.
+
 \begin{figure}[htb!]

### 2022-05-16 article/article.Rmd
update memo and appendix

@@
 important public services the municipal government should provide to citizens.
-According to Brazilian Constitution, municipalities must spend 25\% of their
+According to the Brazilian Constitution, municipalities must spend 25\% of their
 budget on education and 15\% on health care. Consequently, the Ministry of
@@
 
-We assume that city councilors want to extract rents and to get reelected.
-The rents come from continuing in the repeated game, and the partisanship
-discounts that benefit. Figure \ref{survelec} shows that 65.9 percent of
-councilors mentioned that mayors use job appointments to consolidate their
-coalition support. Moreover, 59.0 percent of the surveyed councilors affirmed
-that mayors use personal favors, such as shifting resources to places where the
-councilors have electoral support, to solidify their governing coalition.
-Granting favors works as rent transfers for councilors. Job appointments are
-also convenient for the mayors because patronage in Brazil has positive results
-in terms of welfare \citep{toral2019benefits}.
+We assume that city councilors want to extract rents and to get reelected. The
+rents come from continuing in the repeated game, and the partisanship discounts
+that benefit. Figure \ref{survelec} shows that 65.9 percent of councilors
+mentioned that mayors use job appointments to consolidate their coalition
+support. Moreover, 59.0 percent of the surveyed councilors affirmed that mayors
+use personal favors, such as shifting resources to places where the councilors
+have electoral support, to solidify their governing coalition. This provides
+further evidence that mayors do offer city councilors the benefits they demand.
+In this regard, granting favors works as rent transfers for councilors. Job
+appointments are also convenient for the mayors because patronage in Brazil has
+positive results in terms of welfare \citep{toral2019benefits}.
 
@@
 presidential systems, state governments, and local city councils. As these
-political bodies are influenced by political allegiances, the dynamics we
+institutions are influenced by political allegiances, the dynamics we
 expose here may be generalizable. Depending on legislative support, changing
@@
 structure, and internal power structure. Understanding how legislature size
-interacts with other features would improve our knowledge about the impact of
-local and national legislatures impact public services. These questions are
-crucial for institution design and welfare in developing democracies.
+interacts with other features would improve our knowledge about how local and
+national legislatures impact public services. These questions are crucial for
+institution design and welfare in developing democracies.
 

### 2022-05-16 appendix/appendix.Rmd
update appendix

@@
 author:
-  - Umberto Mignozzeti[^umberto]
-  - Gabriel Cepaluni[^gabriel]
-  - Danilo Freire[^danilo]
 date: \today
@@
 
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
-[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
-
 \newpage
 
-## A Model of Legisture Size and Service Provision (Proofs)
+## A Model of Legislature Size and Service Provision (Proofs)
 
-In this section, we show the proofs for the model included in the main paper.
+In this section, we show the proofs for the model included in the article.
 
@@
 This means that, when increasing the size of the council, the optimal solution $g^*$ should also increase.
-However, as $N$ increases discretely, we cannot take the cross-partial derivative on $N$ or use the implicit function theorem.
+However, as $N$ increases discretely, we cannot take the cross-partial derivative on $N$ and $g$ or use the implicit function theorem.
 Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
@@
 
-Our data come mainly from Brazilian public agencies. Further information about them are available below.
+Our data come mainly from Brazilian public agencies. Further information about them is available below.
 
@@
   & & & \\
-  INEP & Ministry of Education Data Service & Education performance & \url{http://www.inep.gov.br} \\
+  INEP & Ministry of Education Data Service & Educational performance & \url{http://www.inep.gov.br} \\
   & & & \\
@@
 The Ministry of Education takes the average of the students' grades in math and Portuguese, then multiply the those numbers by the student yearly approval rate.
-INEP reweights the estimators to avoid schools and classroom specific effects (source: INEP, years: 2005, 2007).
+INEP reweights the estimators to avoid school and classroom specific distortions (source: INEP, years: 2005, 2007).
 \item \textbf{Size of Mayoral Pre-Electoral Coalition 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
 \item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration who were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
-\item \textbf{Number of Females Elected 2004}: Number of females elected to city council (source: TSE)
+\item \textbf{Number of Females Elected 2004}: Number of females elected to the city council (source: TSE)
 \item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to the city council.
-We collect this data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
+We collect these data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
 \item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the city council size (source: TSE)
@@
 \item \textbf{Oversight}: Legislation that requests information to the mayor's office or the bureaucracy about the provision of services.
+\item \textbf{Others}: Legislation that is not classified as public goods or oversight. Usually honors or procedures.
 \item \textbf{Education and Health Care}: Legislation about education or health care provision.
-\item \textbf{Others}: Legislation that is not classified as local public goods, public goods, or oversight. Usually honors or procedures.
 \end{itemize}
@@
 \begin{itemize}
-\item \textbf{Councilors Job Appointments}: Whether mayors appoint supporters of the city councilors to bureaucratic jobs (source: survey).
-\item \textbf{Councilors Demands}: Whether mayors satisfy the public service demands of an allied councilor (e.g., build a health clinic in a councilor's neighborhood) (source: survey).
-\item \textbf{Councilors Personal Requests}: Whether mayors satisfy the private requests of an allied councilor (e.g., hire an ally in the bureaucracy) (source: survey).
-\item \textbf{Councilors Legislation}: Whether mayors support the councilors' legislative agenda (source: survey).
-\item \textbf{Councilors Constructions}: Whether mayors support councilors' requests for more public works (e.g. fix potholes in the councilor's neighborhoods) (source: survey).
+\item \textbf{Councilors Job Appointments}: Whether mayors appoint supporters of the city councilors to bureaucratic jobs (source: own survey).
+\item \textbf{Councilors Demands}: Whether mayors satisfy the public service demands of an allied councilor (e.g., build a health clinic in a councilor's neighborhood) (source: own survey).
+\item \textbf{Councilors Personal Requests}: Whether mayors satisfy the private requests of an allied councilor (e.g., hire an ally in the bureaucracy) (source: own survey).
+\item \textbf{Councilors Legislation}: Whether mayors support the councilors' legislative agenda (source: own survey).
+\item \textbf{Councilors Constructions}: Whether mayors support councilors' requests for more public works (i.e., fix potholes in the councilor's neighborhoods) (source: own survey).
 \end{itemize}
@@
 \small
-\textbf{Notes:} The legislation approved dataset contains information on 63 of the 202 municipalities 10 thousand inhabitants away from the council size thresholds.
+\textbf{Notes:} The legislation approved dataset contains information on 63 of the 202 municipalities which are 10 thousand inhabitants away from the council size thresholds.
 Survey summary statistics are unweighted.
@@
 
-We run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
+We also run the \citet{cattaneo2019simple} manipulation test, which is based on the density of the local polynomial estimator.
 We use local polynomials ranging from first to fourth order.
 As the null hypothesis implies that there is no manipulation, the $p$-values for each polynomial order are: local linear ($p$-value $=0.442$); quadratic ($p$-value $=0.740$); cubic ($p$-value $=0.998$); and quartic ($p$-value $=0.620$).
-Therefore, we also see no evidence of manipulation.
+Therefore, the test also shows no evidence of manipulation.
 
@@
 When estimating regression discontinuities with multiple cutoffs, authors usually pool all the discontinuities together to estimate the treatment effect on the outcomes of interest \citep{cattaneo2016interpreting}.
-Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoffs thresholds associated with the running variable $X$.
+Let $C = \{c_0, c_1, \cdots, c_n, c_{n+1}\}$ be the set of cutoff thresholds associated with the running variable $X$.
 The outcome variable is assumed to be $Y$.
@@
 
-We control for population, GDP, whether the state is located in the Northeast region, seats before the 2003 decision, and year.
+The inclusion of controls in our model has another purpose, which is to improve the efficiency of our estimates \citep{calonico2019regression}.
+We add five controls to the main specifications.
+We include the 2003 population because it conditions the multiple threshold assignments.
+We add GDP per capita to control for Brazil's economic expansion during the 2000s.
+We also add the number of seats in 2000 to ensure that our results come from the current legislature size and not from past seat allocations.
+Year was included in the models to control for seasonal effects.
+Finally, we add a dummy for Northeast states.
+The Northeast region received considerable attention from the Federal Government in the 2000s.
+According to \citet{de2015politica}, in 2003 the Lula administration recreated the Superintendency for the Development of the Northeast (SUDENE), investing BRL 84 Billion from 2003 to 2010.
+This amounts to around 70% of all targeted regional investments.
+One example of these investments is that the Federal Government created about 100 new universities in the Northeast region.
+Moreover, infant mortality in the region decreased from 22.4 deaths per 1000 infants born in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger federal investments.
+In turn, education quality improved from 2.69 in 2005 to a 3.14 score in 2007 (0 to 10 quality of education score).
+For this reason, adding a dummy for Northeast states is essential for ensuring the consistency and the efficiency of our estimates.
+
 We use a triangular kernel in our estimations, which gives more weigh to municipalities closer to each cutoff.
@@
 In the third model, the change should be $(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)$ and the average change should be equal to $0.5$.
-We display the results in Figure \ref{estimDGP}, showing that the models with control variables are more consistent and efficient.
-
-The inclusion of controls in our model has two purposes. The first one is to
-improve the consistency of the estimates. The second reason is that adding
-control variables improves the efficiency of our estimates
-\citep{calonico2019regression}. We add five controls to the main
-specifications. We include the 2003 population because it conditions the
-multiple threshold assignments. We add GDP per capita to control for Brazil's
-economic expansion during the 2000s. We also add the number of seats in 2000 to
-ensure that our results come from the current legislature size and not from
-past seat allocations. Year was included in the models to control for seasonal
-effects. Finally, we add a dummy for Northeast states. The Northeast region
-received considerable attention from the Federal Government in the 2000s.
-According to \citet{de2015politica}, in 2003 the Lula administration recreated
-the Superintendency for the Development of the Northeast (SUDENE), investing
-BRL 84 Billion from 2003 to 2010. This amounts to around 70% of all targeted
-regional investments. One example of these investments is that the Federal
-Government created about 100 new universities in the Northeast region.
-Moreover, infant mortality in the region decreased from 22.4 deaths per 1000
-infants born in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger
-federal investments. In turn, education quality improved from 2.69 in 2005 to a
-3.14 score in 2007 (0 to 10 quality of education score). For this reason,
-adding a dummy for Northeast states is essential for ensuring the consistency
-and the efficiency of our estimates.
+We display the results in Figure \ref{estimDGP}, showing that the models with control variables are the most consistent and efficient.
 
@@
 In this respect, some states have such poor health care and education systems that they could be driving our results.
-We run the analysis dropping one state at a time to investigate this statewide heterogeneity.
+We run the analyses dropping one state at a time to investigate this statewide heterogeneity.
 The results are in Figures \ref{graphsensstatedrop1} and \ref{graphsensstatedrop2}.
@@
 In the paper, we run all the regressions using local linear polynomials.
-However, to assess the robustness of our results, we also run every model using different polynomials, from local linear to a quartic, to show that our results are robust to different regression functional forms.
-The results are similar in all models, with significance changing only in the quartic polynomials.
+However, to assess the robustness of our results, we also run every model using different polynomial orders, from local linear to quartic, showing that our results are robust to different regression functional forms.
 Figure \ref{graphsensff} presents the results.
@@
 Two alternative explanations may confound our results.
-First, the mayor's selection could be affected by the size of the city council, thus public welfare improves due to the quality of the mayor and not because of the partisan mechanism we have described.
+First, the mayor's selection could be affected by the size of the city council.
+Thus, public welfare can improve due to the quality of the mayor and not because of the partisan mechanism we describe.
 Second, the partisan mechanism could be capturing a dynamic similar to @Weingastetal1981 "law of 1/n", whereby welfare improvements are caused by higher available revenues.
@@
 In Fall 2018, we collected data on the legislation approved by the city councils of 63 municipalities, all of which were 10 thousand inhabitants away from the thresholds we discussed above.
-There are 202 municipalities 10 thousand inhabitants away from the cutoff, but only 63 had relevant information about local legislation between 2005 to 2008.
+There are 202 municipalities that are 10 thousand inhabitants away from the cutoff, but only 63 had relevant information about local legislation between 2005 to 2008.
 
@@
 \item \textbf{Oversight}: Legislation requesting information on the status of service provision.
+\item \textbf{Others}: Legislation not categorized as any of the previous two, such as honors to notable citizens.
 \item \textbf{Health Care and Education}: Bills on education and health care, broadly defined.
-\item \textbf{Others}: Legislation not categorized as any of the previous three, such as honors to notable citizens.
 \end{enumerate}
@@
     \item Which of those activities do city councilors perform most often in their duties?
-    \item Which of the following activities do you believe helps city councilors the most in elections?
+    \item Which of the following activities do you believe help city councilors the most in elections?
 \end{enumerate}

### 2022-05-17 Memo/memo.Rmd
update memo and appendix

@@
 the Superintendency for the Development of the Northeast (SUDENE), investing BRL
-84 Billion from 2003 to 2010. This amounts to around 70% of all targeted
+84 Billion from 2003 to 2010. This amounts to around 70\% of all targeted
 regional investments. One example of these investments is that the Federal
@@
 rule favors the coalitions with more votes. Most of the time, the coalition of
-the elected mayor is the one that receives more votes.}".
+the elected mayor is the one that receives more votes.}"
 
@@
 study. We have rewritten two paragraphs in the Discussion (page 29) to highligh
-the implication of our results. We write: "\textit{Our findings
-have implications that extend well beyond Brazil. A general form of our
-argument is that it is easy for a politician to negotiate with members of her
-in-group \citep{abbink2019, g9030057}. Specifically, several
-countries have separate executive and legislative powers, such as the federal
-level of presidential systems, state governments, and local city councils. As
-these institutions are influenced by political allegiances, the dynamics we
-expose here may be generalizable. Depending on legislative support, changing
-the legislature size could increase the chance of electing politicians that are
-not aligned with the executive, hence decreasing welfare. Despite the
-particular effects on political support and welfare, the logic described in
-this paper would remain relevant for empirically accessing the effect of
-enlarged legislatures on welfare. Our findings may also help scholars
-understand why other countries in Latin America and Asia can generate effective
-governance despite having strong executives and large coalitions
+the implication of our results. We write: "\textit{Our findings have
+implications that extend well beyond Brazil. A general form of our argument is
+that it is easy for a politician to negotiate with members of her in-group
+\citep{abbink2019, alt2018giving}. Specifically, several countries have
+separate executive and legislative powers, such as the federal level of
+presidential systems, state governments, and local city councils. As these
+institutions are influenced by political allegiances, the dynamics we expose
+here may be generalizable. Depending on legislative support, changing the
+legislature size could increase the chance of electing politicians that are not
+aligned with the executive, hence decreasing welfare. Despite the particular
+effects on political support and welfare, the logic described in this paper
+would remain relevant for empirically accessing the effect of enlarged
+legislatures on welfare. Our findings may also help scholars understand why
+other countries in Latin America and Asia can generate effective governance
+despite having strong executives and large coalitions
 \citep{pereira2012surprising}.}".

### 2022-05-17 article/article.Rmd
update memo and appendix
edits to article

@@
 In this paper, we use a formal model to show that increasing legislature size improves public goods delivery.
-We argue that changes in bargaining costs depend on whether additional legislators share the executive's party affiliation: More opposition members reduce the executive's public goods provision, while more government-aligned members increase it.
+We argue that changes in bargaining costs depend on whether additional legislators share the executive's party affiliation: More opposition members reduce the equilibrium public goods provision, while more government-aligned members increase it.
 We test this theory by exploiting sharp discontinuities in city council size in Brazil.
-We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures.
+We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality rates.
 To explore possible mechanisms, we surveyed 174 former city councilors and analyzed 346,553 bills proposed between 2005 and 2008.
@@
 the political stage. In modern democracies, most countries have assemblies at
-all levels of government. These institutions regulate the quantity and quality
-of legislation, check and veto other political powers, and influence
+all levels of government. These institutions regulate the quantity and the
+quality of legislation, check and veto other political powers, and influence
 policymaking. Moreover, legislatures also determine taxation, government
@@
 First, in mayor-council municipalities, mayors are the main responsible for
-public service decisions, and like presidents and governors, they can boost
-local public investments by altering the government budget. Second,
-partisanship plays a key role in city politics, even in countries in which
-ideological attachment is relatively weak. Party attachment structures
-political views \citep{samuels2014power}, and local-level elites usually belong
-to different factions and parties. They fight for power in the municipality by
-controlling various parties and forming distinct pre-electoral
-coalitions.\footnote{Elite political competition in the local level has also
-been linked to violence and conflict in Brazil and elsewhere
+public service decisions and can boost local public investments by altering the
+government budget. Second, partisanship plays a key role in city politics, even
+in countries in which ideological attachment is relatively weak. Party
+attachment structures political views \citep{samuels2014power}, and local-level
+elites usually belong to different factions and parties. They fight for power
+in the municipality by controlling various parties and forming distinct
+pre-electoral coalitions.\footnote{Elite political competition in the local
+level has also been linked to violence and conflict in Brazil and elsewhere
 \citep{hoelscher2015politics, mignozzetti2018predatory}.} In many cities,
@@
 of our argument is that it is easy for a politician to negotiate with members
-of her in-group \citep{abbink2019, g9030057}. Specifically, several countries
+of her in-group \citep{abbink2019, alt2018giving}. Specifically, several countries
 have separate executive and legislative powers, such as the federal level of

### 2022-05-17 article/article.Rmd
edit article

@@
 government-aligned councilors are sufficiently high. Lower bargaining costs
-release funds for mayors to invest in public goods provision. In this case, a
-larger city council may add more members to the government coalition, thus
-reducing the mayor's bargaining costs and increasing the equilibrium public
-goods provision.
+release funds for mayors to invest in public goods. In this case, a larger city
+council may add more members to the government coalition, thus reducing the
+mayor's bargaining costs and increasing the equilibrium public goods provision.
 
@@
 legislator also leads to 104 new appointed bureaucrats, and research shows that
-political appointees civil servants improve public service provision and
-enhance accountability in Brazil \citep{toral2019benefits}.
+political appointees improve public service provision and enhance
+accountability in Brazil \citep{toral2019benefits}.
 
@@
 explain significant infrastructure spending in smaller districts. However, the
-"law of $1/n$" literature rarely mentions the relationship between public goods
-provision and welfare. This paper is one of the first to study how the number
-of local legislators affects welfare. Our model provides a theoretical
-expectation based on the chances of electing a politician aligned with the
-mayor. The empirical estimates confirm our theoretical predictions, with the
-additional fact that legislature size has a null effect on expenditures in
-Brazil.
+literature on the "law of $1/n$" rarely mentions the relationship between
+public goods provision and welfare. This paper is one of the first to study how
+the number of local legislators affects citizen well-being. Our model provides
+a theoretical expectation based on the chances of electing a politician aligned
+with the mayor. The empirical estimates confirm our theoretical predictions,
+with the additional fact that legislature size has a null effect on
+expenditures in Brazil.
 
@@
 Democratic and Republican mayors. Specifically about Brazil,
-\citet{gouvea2021partisanship} shows that social policy expenditure increase
+\citet{gouvea2021partisanship} show that social policy expenditure increases
 with left-wing mayors. \citet{frey2021legislature}, using discontinuities in
@@
 mayors, but they cannot do it alone. Legislatures are a solid check to the
-mayor's policy. Bargaining with them in a country plagued by corruption can be
+mayor's agenda. Bargaining with them in a country plagued by corruption can be
 costly \citep{bertholini2017price}. Therefore, an extra ally in the city
@@
 council size thresholds. Finally, our survey data demonstrate that councilors
-and mayors agree about appointing more public servants to the public
+and mayors agree about appointing more civil servants to the public
 administration.
@@
 \citet{Ames2001} argues that the Brazilian democracy is prone to deadlocks
-because the executive has its hands tied by legislators that demand consistent
-provision of particularistic and private goods. Indeed, the most successful
-presidents after 1995 had to build multiparty coalitions by negotiating with
-parties \citep{limongi1998bases, raile2011executive}. Despite evidence that
-side payments cemented these coalitions, many social and economic policies have
+because the executive has its hands tied by legislators who demand consistent
+provision of private goods. Indeed, the most successful presidents after 1995
+had to build extensive coalitions by negotiating with several parties
+\citep{limongi1998bases, raile2011executive}. Despite evidence that side
+payments cemented these coalitions, many social and economic policies have
 since been implemented. For instance, education and health care notably
-improved during the Cardoso and Lula governments \citep{acemoglu2012nations}.
-Presidents who challenged the coalition system did not succeed. For instance,
-former President Rousseff was impeached in her second term. Bolsonaro can be
-considered one of the most ineffective presidents in Brazilian history.
+improved during the Cardoso and Lula administrations
+\citep{acemoglu2012nations}. Presidents who challenged the coalition system did
+not succeed. For instance, former President Rousseff was impeached in her
+second term. Bolsonaro can be considered one of the most ineffective presidents
+in Brazilian history.
 
@@
 more than thirty-five registered parties, mayors face substantial challenges to
-the support for their agendas. Having extra help in the council can tilt the
+approve their political agendas. Having extra help in the council can tilt the
 bargaining towards cheaper governing costs, thus improving public goods
@@
 provided by \citet{britto2020corruption} show that corruption increases with
-legislature size. As the model shows, city councilors receive a side transfer
-from mayors to support their agenda. Mayors also divide the resources saved in
-the bargain into public goods and rents. The rate for the division depends on
-the marginal changes of the rents and public goods, but these two components
-receive the extra resources. In this case, the mayor's rents may be primarily
-corruption, and the councilor's transfers can be clientelistic, aimed at
-improving the councilor's reelection chances.
+legislature size. As the model shows, city councilors may receive a side
+transfer from the mayor to support her agenda. Mayors also divide the resources
+saved in the bargain into public goods and rents. The rate for the division
+depends on the marginal changes of the rents and public goods, but these two
+components receive the extra resources. In this case, the mayor's rents may be
+primarily corruption, and the councilor's transfers can be clientelistic, aimed
+at improving the councilor's reelection chances.
 

### 2022-05-17 Memo/memo.Rmd
edit memo

@@
 In response to comments from Reviewer 1, we have revised our Methods section to
-clarify our selection of independent variables, including the use of covariates
-to improve the efficiency and consistency of our estimates. Additionally, we
-have included a new section in the Supplemental Materials to explain how we
+clarify our selection of independent variables, particularly the use of
+covariates to improve the efficiency and consistency of our estimates. Moreover,
+we have also added a new section in the Supplemental Materials to explain how we
 conducted our survey and how it contributes to our results. We believe these
@@
 We thank Reviewer 1 for these two relevant suggestions. We now cite Gilligan and
-Matsusaka's 2001 article three times in our paper. We mention it twice in our
-Introduction, first on page 2: ``\textit{On the one hand, enlarged legislatures
-may reduce political particularism and increase overall government spending,
-which can lead to more public goods  \citep{gerring2020population,
-GilliganMatsusaka2001, Weingastetal1981}}'', and then in the end of page 4:
-``\textit{The corollary of the "law of $1/n$" is that increasing legislature
-size promotes excessive public spending, regardless of the partisan makeup of
-the legislature \citep{GilliganMatsusaka2001}}''. We also cite it in our Theory
+Matsusaka's 2001 article three times in our paper. We mention their article
+twice in our Introduction, first on page 2: ``\textit{On the one hand, enlarged
+legislatures may reduce political particularism and increase overall government
+spending, which can lead to more public goods  \citep{gerring2020population,
+GilliganMatsusaka2001, Weingastetal1981}}'', and then on page 5: ``\textit{[The]
+corollary of the "law of $1/n$" is that increasing legislature size promotes
+excessive public spending, regardless of the partisan makeup of the legislature
+\citep{GilliganMatsusaka2001}}''. We cite the article once more in our Theory
 section (page 7): ``\textit{Yet, \citet{GilliganMatsusaka2001} find that in the
@@
 
-We cite Gerring and Veenendaal's book four times. We mention it twice on page 2:
-``\textit{Legislature size is known to have a significant effect on collective
-action strategies, the bargaining power between state branches, government
-spending, and representation \citep{crain1979cost, freire2021legislature,
-gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
-However, how legislature size impacts social welfare remains less understood. On
-the one hand, enlarged legislatures may reduce political particularism and
-increase overall government spending, which can lead to more public goods
-\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}}''. We
-mention the book again on page 4: ``\textit{Following the seminal contribution
-by \citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
-increase the legislative pressure for providing targeted public goods to local
-supporters at the expense of the entire polity \citep{freire2021legislature}. This
-question has become more relevant since legislature size has increased
-consistently over time \citep{gerring2020population}}''. Finally, we also cite
-it on page 6: ``\textit{Larger legislatures improve representation as both the
-election thresholds and the ratio of population-per-politician decrease, which
-facilitate the electoral success of ethnic and political minorities
+We now cite Gerring and Veenendaal's book four times. We mention it twice on
+page 2: ``\textit{Legislature size is known to have a significant effect on
+collective action strategies, the bargaining power between state branches,
+government spending, and representation \citep{crain1979cost,
+freire2021legislature, gerring2020population, PrimoSnyder2008, rogers2002free,
+Weingastetal1981}. However, how legislature size impacts social welfare remains
+less understood. On the one hand, enlarged legislatures may reduce political
+particularism and increase overall government spending, which can lead to more
+public goods \citep{gerring2020population, GilliganMatsusaka2001,
+Weingastetal1981}}''. We mention it again on page 4: ``\textit{Following the
+seminal contribution by \citet{Weingastetal1981}, the "law of $1/n$" posits that
+larger legislatures increase the legislative pressure for providing targeted
+public goods to local supporters at the expense of the entire polity
+\citep{freire2021legislature}. This question has become more relevant since
+legislature size has increased consistently over time
+\citep{gerring2020population}}''. Finally, we also cite the book on page 6:
+``\textit{Larger legislatures improve representation as both the election
+thresholds and the ratio of population-per-politician decrease, which facilitate
+the electoral success of ethnic and political minorities
 \citep{allenrepresentation, gerring2020population}}.''
@@
 
-We thank Reviewer 1 for the opportunity to clarify the selection of these two
-sets of variables for our paper. We included an explanation for our choice on
-page 17: "\textit{Our focus is on the impact of legislature size on education
-and health care, which are the two most important public services the municipal
-government should provide to citizens. According to the Brazilian Constitution,
+We thank Reviewer 1 for the opportunity to clarify why we have selected these
+two sets of variables. We included an explanation for our decision on page 17:
+"\textit{Our focus is on the impact of legislature size on education and health
+care, which are the two most important public services the municipal government
+should provide to citizens. According to the Brazilian Constitution,
 municipalities must spend 25\% of their budget on education and 15\% on health
@@
 
-We agree with Reviewer 1 that we needed to provide more information on the
-online survey. Therefore, we have detailed our procedures in Section A.14 of the
-Supplementary Materials (pages 22-23), and we also reference the survey on pages
-17 and 22 (footnote 13) in the main article. We rewrote paragraph 2 of Section
-6.2 to clarify the importance of the survey results in our paper. It reads as
-follows: ``\textit{We assume that city councilors want to extract rents and to
-get reelected. The rents come from continuing in the repeated game, and the
+We agree with Reviewer 1 that we needed to provide more information about our
+online survey. Therefore, we have detailed our survey procedures in Section A.14
+of the Supplementary Materials (pages 22-23), and we also briefly discuss our
+survey methodology on pages 17 and 22 (footnote 13) of the main article.
+Furthermore, we have rewritten paragraph 2 of Section 6.2 to clarify the
+importance of the survey results in our paper. It now reads as follows:
+``\textit{We assume that city councilors want to extract rents and to get
+reelected. The rents come from continuing in the repeated game, and the
 partisanship discounts that benefit. Figure 2 shows that 65.9 percent of
@@
 
-We thank Reviewer 1 for the opportunity to clarify the selection of control
-variables in our empirical analysis. The inclusion of controls in our model has
-two purposes. The first one is to improve the consistency of the estimates. In
-Section A.5 of the Appendix, we use simulation to show that the inclusion of
-covariates enhances the consistency of our point estimates. The simulation
-indicates improved consistency for several distributions of the running
-variables and different treatment effects. Section 5 of the manuscript
-demonstrates that it improves consistency in both the main estimates and the
-placebo ones. Table 1 (page 20, reproduced below) shows that without controls,
-we would overestimate the treatment effects (finding an increase of 1.63
-legislators instead of an increase of exactly one legislator), and underestimate
-the placebo treatment effects (finding a significant decrease of 0.31
-legislators where there was supposed to be no effects in legislature size). This
-substantial improvement is because having control variables makes the
-subpopulations in each threshold more comparable across all the thresholds,
-avoiding comparing cases to the left (right) of one given threshold with points
-in the right (left) of a different threshold.
+We thank Reviewer 1 for this constructive comment. The inclusion of control
+variables in our model has two purposes. Firstly, the covariates improve the
+consistency of our empirical results. In Section A.5 of the Appendix, we use
+simulations to show that the inclusion of covariates enhances the consistency of
+our RDD estimates. The simulations indicate that the controls improve
+consistency even if we assume different distributions for the running variables
+and for the treatment effects. Similaly, Section 5 of the manuscript
+demonstrates that the covariates improve consistency in both the main estimates
+and the placebo ones. Table 1 (page 20, reproduced below) shows that without
+controls, we would overestimate the treatment effects (finding an increase of
+1.63 legislators instead of an increase of exactly one legislator), and
+underestimate the placebo treatment effects (finding a significant decrease of
+0.31 legislators where there was supposed to be no effects in legislature size).
+This substantial improvement is attributed to the addition of control variables,
+which make the subpopulations in each threshold more comparable across all the
+thresholds. Thus, we avoid spurious comparisons between cases on the left
+(right) of one threshold and those on the right (left) of a different threshold.
 
@@
 
-The second reason is that adding control variables improves the efficiency of
-our estimates \citep{calonico2019regression}. We add five controls to the main
+Secondly, the addition of control variables also improves the efficiency of our
+estimates \citep{calonico2019regression}. We add five controls to the main
 specifications. We include the 2003 population because it conditions the
@@
 effects. Finally, we add a dummy for Northeast states. The Northeast region
-received considerable attention from the Federal Government in the 2000s.
+received considerable attention from the federal government in the 2000s.
 According to \citet{de2015politica}, in 2003 the Lula administration recreated
@@
 84 Billion from 2003 to 2010. This amounts to around 70\% of all targeted
-regional investments. One example of these investments is that the Federal
-Government created about 100 new universities in the Northeast region. Moreover,
-infant mortality in the region decreased from 22.4 deaths per 1000 infants born
-in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger federal
-investments. In turn, education quality improved from 2.69 in 2005 to a 3.14
-score in 2007 (0 to 10 quality of education score). For this reason, adding a
-dummy for Northeast states is essential for ensuring the consistency and the
-efficiency of our estimates.
+regional investments. One example of these investments is that the federal
+government created about 100 new universities in the Northeast region during
+that period. Moreover, infant mortality in the Brazilian Northeast decreased
+from 22.4 deaths per 1000 infants born in 2005 to 19.6 deaths in 2008 largely
+due to substantial federal investments in the region. In turn, education quality
+improved from 2.69 in 2005 to a 3.14 score in 2007 (0 to 10 quality of education
+score). For this reason, adding a dummy for Northeast states is essential for
+ensuring the consistency and the efficiency of our estimates.
 
-To reflect these pieces of information, we rewrote paragraph five in Section 5
+To reflect these pieces of information, we have rewritten paragraph five in Section 5
 of the manuscript to (page 19):
 
-``[...] \textit{we add five controls to the estimates: population in 2003; GDP
-per capita; the number of seats in 2000; year; and a dummy for Northeast
-municipalities. The reason for the first variable is the multiple threshold
-assignments. We add GDP per capita because wealthier cities tend to have better
-public services. The number of seats in 2000 intends to control that some
-municipalities could experience a change provoked by the previous council size,
-confounding our estimates. The Northeast dummy was added to control for the fact
-that the Lula administration heavily invested in the region from 2003 until
-2010, improving several development indicators \citep{de2015politica}. The years
-were added to improve efficiency and control for seasonal effects. Moreover,
-adding controls improves efficiency in RDD \citep{calonico2019regression} and
-also enhances the consistency in the multiple thresholds RDD.}''
+``[...] \textit{we add
+five controls to the estimates: Population in 2003; GDP per capita; the number
+of seats in 2000; year; and a dummy for Northeast municipalities. The reason
+for the inclusion of first variable is the multiple threshold assignments. We
+add GDP per capita because wealthier cities tend to have better public
+services. We include number of seats in 2000 because some municipalities could
+have experienced a change provoked by the previous council size, thus
+confounding our estimates. The Northeast dummy was added to control for the
+fact that the Lula administration heavily invested in the region from 2003
+until 2010, improving several development indicators \citep{de2015politica}. We
+included an indicator for year to improve efficiency and control for seasonal
+effects. Moreover, adding controls improves efficiency in RDD
+\citep{calonico2019regression} and also enhances the consistency in the
+multiple thresholds RDD.}''
 
-And we added the discussions here to the Appendix at the end of Section A.5.
+We have also added a similar discussion to Section A.5 of the Supplementary
+Materials.
 
 We want to highlight further that this decision to add controls in our case is
-also because of consistency. Even though clustered standard errors may provide
-the best standard errors for our model, this would not affect the consistency.
-And the consistency here relies on making the subpopulations comparable, i.e.,
-the subpopulation of towns between 9 and 10 legislators as comparable as the
-subpopulation of towns between 10 and 11 legislators, and so on.
+mainly to ensure that our estimates are consistent. Even though clustered
+standard errors are adequate for our purposes, they do not improve the
+consistency of our estimates. In our case, the model consistency relies on
+making the subpopulations comparable. That is, the subpopulation of
+municipalities who have 9 and 10 legislators should be comparable with that of
+of cities between 10 and 11 legislators, and so on.
 
@@
 in Table 4 (page 27). Finally, we show in the table below that the mayors'
-parties are not driving our results. This result is also available on our GitHub
-repository. We ommitted it from the Supplementary Materials to conserve space.
+parties are not driving our results. We have ommitted the table from the
+Supplementary Materials to conserve space, but it is available on the article's
+GitHub repository.
 
@@
 
-We entirely agree with Reviewer 3 that we need to discuss the scope conditions
+We entirely agree with Reviewer 3 that we needed to discuss the scope conditions
 of our findings in more detail. We acknowledge that the external validity of
@@
 
-We would like to thank Reviewer 3 for their comments and suggestions.
+We would like to thank Reviewer 3 for their helpful comments and suggestions.
 \end{quote}

### 2022-05-17 article/article.Rmd
edit memo

@@
 the consistency and efficiency of the estimates. Relying on this fact, we add
-five controls to the estimates: population in 2003; GDP per capita; the number
-of seats in 2000; year; and a dummy for Northeast municipalities. The
-reason for the first variable is the multiple threshold assignments. We add GDP
-per capita because wealthier cities tend to have better public services. The
-number of seats in 2000 intends to control that some municipalities could
-experience a change provoked by the previous council size, confounding our
-estimates. The Northeast dummy was added to control for the fact that the Lula
-administration heavily invested in the region from 2003 until 2010, improving 
-several development indicators \citep{de2015politica}. The years were added 
-to improve efficiency. Moreover, adding controls improves efficiency in RDD
+five controls to the estimates: Population in 2003; GDP per capita; the number
+of seats in 2000; year; and a dummy for Northeast municipalities. The reason
+for the inclusion of first variable is the multiple threshold assignments. We
+add GDP per capita because wealthier cities tend to have better public
+services. We include number of seats in 2000 because some municipalities could
+have experienced a change provoked by the previous council size, thus
+confounding our estimates. The Northeast dummy was added to control for the
+fact that the Lula administration heavily invested in the region from 2003
+until 2010, improving several development indicators \citep{de2015politica}. We
+included an indicator for year to improve efficiency and control for seasonal
+effects. Moreover, adding controls improves efficiency in RDD
 \citep{calonico2019regression} and also enhances the consistency in the

### 2022-05-17 Memo/memo.Rmd
small changes to memo and appendix

@@
 online survey. Therefore, we have detailed our survey procedures in Section A.14
-of the Supplementary Materials (pages 22-23), and we also briefly discuss our
+of the Supplementary Materials (pages 23-24), and we also briefly discuss our
 survey methodology on pages 17 and 22 (footnote 13) of the main article.
@@
 
-To reflect these pieces of information, we have rewritten paragraph five in Section 5
-of the manuscript to (page 19):
+To reflect these pieces of information, we have rewritten paragraph five in
+Section 5 of the manuscript to (page 19):
 

### 2022-05-17 appendix/appendix.Rmd
update memo and appendix
small changes to memo and appendix

@@
 
-In this section, we show the proofs for the model included in the article.
+In this section, we show the proofs for the formal model we present in the article.
 
@@
 This means that, when increasing the size of the council, the optimal solution $g^*$ should also increase.
-However, as $N$ increases discretely, we cannot take the cross-partial derivative on $N$ and $g$ or use the implicit function theorem.
+However, as $N$ increases discretely, we cannot take the cross-partial derivative on $g$ and $N$ or use the implicit function theorem.
 Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.
@@
 
-Therefore, costs always increase when legislature size increases.
+Therefore, governing costs always increase when legislature size increases.
 
@@
 We collect these data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
-\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the city council size (source: TSE)
+\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the size of the city council (source: TSE)
 \item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
@@
 \item \textbf{Education and Health Care}: Legislation about education or health care provision.
-\end{itemize}
-
-### Online 2016 Former City Councilors Survey
-
-We ran an online survey asking 174 councilors about their representation duties and how mayors allocate public services to expand his or her government coalition. The services we include are:
-
-\begin{itemize}
-\item \textbf{Councilors Job Appointments}: Whether mayors appoint supporters of the city councilors to bureaucratic jobs (source: own survey).
-\item \textbf{Councilors Demands}: Whether mayors satisfy the public service demands of an allied councilor (e.g., build a health clinic in a councilor's neighborhood) (source: own survey).
-\item \textbf{Councilors Personal Requests}: Whether mayors satisfy the private requests of an allied councilor (e.g., hire an ally in the bureaucracy) (source: own survey).
-\item \textbf{Councilors Legislation}: Whether mayors support the councilors' legislative agenda (source: own survey).
-\item \textbf{Councilors Constructions}: Whether mayors support councilors' requests for more public works (i.e., fix potholes in the councilor's neighborhoods) (source: own survey).
 \end{itemize}
@@
 \end{table}
+
+### Online 2016 Former City Councilors Survey
+
+We ran an online survey asking 174 councilors about their representation duties and how mayors allocate public services to expand his or her government coalition. The services we include are:
+
+\begin{itemize}
+\item \textbf{Councilors Job Appointments}: Whether mayors appoint supporters of the city councilors to bureaucratic jobs (source: own survey).
+\item \textbf{Councilors Demands}: Whether mayors satisfy the public service demands of an allied councilor (e.g., build a health clinic in a councilor's neighborhood) (source: own survey).
+\item \textbf{Councilors Personal Requests}: Whether mayors satisfy the private requests of an allied councilor (e.g., hire an ally in the bureaucracy) (source: own survey).
+\item \textbf{Councilors Legislation}: Whether mayors support the councilors' legislative agenda (source: own survey).
+\item \textbf{Councilors Constructions}: Whether mayors support councilors' requests for more public works (i.e., fix potholes in the councilor's neighborhoods) (source: own survey).
+\end{itemize}
 
@@
 This amounts to around 70% of all targeted regional investments.
-One example of these investments is that the Federal Government created about 100 new universities in the Northeast region.
-Moreover, infant mortality in the region decreased from 22.4 deaths per 1000 infants born in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger federal investments.
+One example of these investments is that the federal government created about 100 new universities in the Northeast region during that period.
+Moreover, infant mortality in the Brazilian Northeast decreased from 22.4 deaths per 1000 infants born in 2005 to 19.6 deaths in 2008 largely due to substantial federal investments in the region.
 In turn, education quality improved from 2.69 in 2005 to a 3.14 score in 2007 (0 to 10 quality of education score).
@@
     \begin{minipage}{0.9\linewidth}
-      \centerline{\includegraphics[height=3.45in,angle=0]{../figures/simdistrRDD.pdf}}
+      \centerline{\includegraphics[height=5in,angle=0]{../figures/simdistrRDD.pdf}}
       \caption{Simulation: RD with Multiple Thresholds -- Data Distribution}
@@
 As expected, the placebo regressions are statistically insignificant.
+
+\vspace{.2cm}
 
@@
 
-For instance, changes in controls substantially affect the quality of elementary education, where some sets of control variables leading to a positive effect.
+For instance, changes in the controls variables substantially affect the quality of elementary education, where some sets of controls lead to a positive effect.
 However, most combinations of controls were insignificant.
@@
 
-Here we evaluate the robustness of our results when we change the number of cutoffs.
+Here we evaluate the robustness of our results when we vary the number of cutoffs.
 We run a series of regressions limiting the population sizes to half the cutoffs, starting from the second cutoff to the last.
@@
 Thus, public welfare can improve due to the quality of the mayor and not because of the partisan mechanism we describe.
-Second, the partisan mechanism could be capturing a dynamic similar to @Weingastetal1981 "law of 1/n", whereby welfare improvements are caused by higher available revenues.
+Second, the partisan mechanism could be capturing a dynamic similar to Weingast et al.'s [-@Weingastetal1981] "law of 1/n", whereby welfare improvements are caused by higher available revenues.
 This section shows that none of these concerns are valid in our case.
@@
 We have chosen SVM as it gives the highest prediction rate of all of the algorithms we have tried.
-We use a simple bag-of-words classifier provided by the `RTextTools` package for `R` \citep{collingwood2013rtexttools}.}
+We use a simple bag-of-words classifier provided by the \texttt{RTextTools} package for \texttt{R} \citep{collingwood2013rtexttools}.}
 
@@
 We include the following categories in the weighting procedure: region of Brazil, legislature size (9 to 15 or more), gender, and age less than 39.
-We use the proportions in each bin to weight the graphs and statistics generated after the raking process.\footnote{The `survey` package for `R` describes the raking process in more detail \citep{lumley2004analysis}.
+We use the proportions in each bin to weight the graphs and statistics generated after the raking process.\footnote{The \texttt{survey} package for \texttt{R} describes the raking process in more detail \citep{lumley2004analysis}.
 In summary, it iterates the post-stratification procedure until the sample marginals match the population marginals for all variables.} Table \ref{tabweight} shows the sample, population, and weighted proportions.
@@
 \begin{enumerate}
-    \item In Brazil, mayors commonly negotiate to establish a government majority in the city council. How often do you think mayors use the following goods in exchange for support?
+    \item In Brazil, mayors usually negotiate to establish a government majority in the city council. How often do you think mayors use the following goods in exchange for support?
     \item Which of those activities do city councilors perform most often in their duties?
-    \item Which of the following activities do you believe help city councilors the most in elections?
+    \item Which of the following activities do you believe helps city councilors the most in elections?
 \end{enumerate}
@@
 \end{figure}
-
-\pagebreak

### 2022-05-17 article/article.Rmd
copyediting files

@@
 the political stage. In modern democracies, most countries have assemblies at
-all levels of government. These institutions regulate the quantity and the
-quality of legislation, check and veto other political powers, and influence
-policymaking. Moreover, legislatures also determine taxation, government
-spending and oversee public programs \citep{auriol2012optimal,
+all levels of government. These institutions regulate the quantity and quality
+of legislation, check and veto other political powers, and influence
+policymaking. Moreover, legislatures also determine taxation, regulate
+government spending, and oversee public programs \citep{auriol2012optimal,
 north1989constitutions, poulsen2018political, stasavage2011states,
@@
 
-Regardless of eventual differences in electoral rules, social composition, and
+Regardless of eventual differences in electoral rules, social composition, or
 internal procedures, all legislatures share one common feature: They are
@@
 consequences for the whole polity. Legislature size is known to have a
-significant effect on collective action strategies, the bargaining power
-between state branches, government spending, and representation
-\citep{crain1979cost, freire2021legislature, gerring2020population,
-PrimoSnyder2008, rogers2002free, Weingastetal1981}. However, how legislature
-size impacts social welfare remains less understood. On the one hand, enlarged
-legislatures may reduce political particularism and increase overall government
-spending, which can lead to more public goods \citep{gerring2020population,
-GilliganMatsusaka2001, Weingastetal1981}. On the other hand, adding more
-representatives to a legislature may exacerbate collective action problems,
-thus hindering service provision \citep{gottlieb2019countervailing,
-tsebelis2002veto}. Therefore, what is the effect of larger legislatures on
-public service delivery?
+significant effect on the bargaining power between state branches, public
+expenditures, and representation \citep{crain1979cost, freire2021legislature,
+gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
+However, how legislature size impacts social welfare remains less understood.
+On the one hand, larger legislatures may reduce political particularism and
+increase overall government spending, which can lead to more public goods
+\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}. On the
+other hand, adding representatives to a legislature may exacerbate collective
+action problems, thus hindering service provision
+\citep{gottlieb2019countervailing, tsebelis2002veto}. Therefore, what is the
+effect of larger legislatures on public service delivery?
 
@@
 which the decision leaves the mayor's office and councilors propose the public
-investments. In this mayor-council bargaining process, costs come from the
-side-transfers required to secure a majority among councilors. We show that in
-a model without partisan concerns, bargaining costs always increase with larger
-city councils, which in turn lower public goods provision and rents. However,
-partisanship decreases bargaining costs when the chances of electing
-government-aligned councilors are sufficiently high. Lower bargaining costs
-release funds for mayors to invest in public goods. In this case, a larger city
-council may add more members to the government coalition, thus reducing the
-mayor's bargaining costs and increasing the equilibrium public goods provision.
+investments. In this bargaining process, costs come from the side-transfers
+required to secure a majority among councilors. We show that in a model without
+partisan concerns, bargaining costs always increase with larger city councils,
+which in turn lower public goods provision and rents. However, partisanship
+decreases bargaining costs when the chances of electing government-aligned
+councilors are sufficiently high. Lower bargaining costs release funds for
+mayors to invest in public goods. In this case, a larger city council may add
+more members to the government coalition, thus reducing the mayor's bargaining
+costs and increasing the equilibrium public goods provision.
 
@@
 municipalities. Until then, cities could freely determine their legislature
-size, but in March 2004 the Supreme Electoral Court created population
+size. But in March 2004 the Supreme Electoral Court created population
 thresholds and added one councilor to each set of 47,619 inhabitants. Around
@@
 able to boost public investments with fewer constraints. Each additional
-legislator also leads to 104 new appointed bureaucrats, and research shows that
-political appointees improve public service provision and enhance
+legislator also leads to 104 politically appointed bureaucrats, and research
+shows that political appointees improve public service provision and enhance
 accountability in Brazil \citep{toral2019benefits}.
@@
 of multilateral bargaining started with \citet{baron1989bargaining}, who
-extended the bilateral bargaining game proposed by
-\citet{rubinstein1982perfect} to more than two players. Several papers followed
-\citet{baron1989bargaining} and included endogenous recognition power, the size
-of the required majority, and partisanship in the model
-\citep{agranov2020persistence, baranski2020determinants,
-calvert2005legislative, choate2019partisan}.\footnote{See
-\citet{eraslan2019legislative} for a comprehensive review of multilateral
-bargaining and \citet{ray2015coalition} for a review on coalition formation.}
-In this article, we extend the \citet{baron1989bargaining} model under closed
-rules and add the mayor's first move and political partisanship. We consider
-partisanship as a zero-sum effect that is positive for politicians aligned with
-the mayor and negative otherwise. We investigate the often overlooked effect of
-legislature size on the bargaining equilibrium strategies.
+expanded the bilateral bargaining game proposed by
+\citet{rubinstein1982perfect} to more than two players. Several authors then
+analysed the effect of endogenous recognition power, the size of the required
+majority, and partisanship on these models \citep{agranov2020persistence,
+baranski2020determinants, calvert2005legislative,
+choate2019partisan}.\footnote{See \citet{eraslan2019legislative} for a
+comprehensive review of multilateral bargaining and \citet{ray2015coalition}
+for a review on coalition formation.} In this article, we extend
+\citeauthor{baron1989bargaining}'s (\citeyear{baron1989bargaining}) model under
+closed rules and add the mayor's first move and political partisanship. We
+consider partisanship as a zero-sum effect that is positive for politicians
+aligned with the mayor and negative otherwise. We investigate the often
+overlooked effect of legislature size on the bargaining equilibrium strategies.
 
 Second, this paper contributes to the literature on the effects of larger
-legislatures in service provision. Following the seminal contribution by
-\citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
-increase the legislative pressure for providing targeted public goods to local
+legislatures on service provision. Following the seminal contribution by
+\citet{Weingastetal1981}, the "law of $1/n$" posits that larger chambers
+provide incentives for legislators to provide targeted public goods to local
 supporters at the expense of the entire polity \citep{freire2021legislature}.
@@
 factors such as the degree that local public goods can exclude non-locals or
-deadweight costs associated with taxation.} In the US metaphor, this would
+deadweight costs associated with taxation.} In the US case, this would
 explain significant infrastructure spending in smaller districts. However, the
@@
 
-Third, our article also contributes to the growing literature on municipal
+Third, our article also dialogues with the growing literature on municipal
 partisan politics. Most papers in this field estimate the effects of the
@@
 Democratic and Republican mayors. Specifically about Brazil,
-\citet{gouvea2021partisanship} show that social policy expenditure increases
-with left-wing mayors. \citet{frey2021legislature}, using discontinuities in
-city council size after the 2009 constitutional amendment that reverted the
+\citet{gouvea2021partisanship} show that social spending increases with
+left-wing mayors. \citet{frey2021legislature}, using discontinuities in city
+council size after the 2009 constitutional amendment that reverted the
 thresholds we study here, shows that changes in council size lower the support
@@
 more heavily on party cues and committee structures. In considering the causes
-of changes in legislature sizes, \citet{jacobs2015explaining} show that
-population shifts increase and economic crises decrease the number of
-legislators. \citet{marland2019fewer} questions the economic crises mechanism,
+of changes in legislature sizes, \citet{jacobs2015explaining} show that while
+population shifts tend to increase the number of local legislators, economic
+crises decrease them. \citet{marland2019fewer} questions the latter mechanism,
 showing that political elites shrink legislatures mostly to signal to the
 public the priority of their austerity agenda. In this article, we show that
-council size affects welfare by changing the partisan composition of
-the legislatures.
+council size affects welfare by changing the partisan composition of the
+legislatures.
 
@@
 
-Institutional design has a major impact on long-term welfare
+Institutional design has a lasting impact on social welfare
 \citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions}
@@
 how to determine the optimal size of their legislative bodies. The literature
-on this topic is extensive, and modern attempts to provide a solution to the
-legislature size problem started in the early eighteenth century with
-the Federalists versus Anti-Federalists debates \citep{muzzio1989size,
-Stigler1976}.
+on this topic is extensive, and modern attempts to address the legislature size
+problem started in the early eighteenth century with the Federalists versus
+Anti-Federalists debates \citep{muzzio1989size, Stigler1976}.
 
@@
 gerring2020population}. However, better representation is often countered by
-the decline in efficiency in larger legislatures \citep{Weingastetal1981}. The
-enlarged size makes it harder for members to coordinate and collaborate without
-partisanship and legislative structures \citep{kirkland2014chamber,
-rush2013conclusion}. It also increases the potential number of veto players,
-decreasing policymaking efficiency \citep{tsebelis2002veto}. Balancing these
-two incentives is crucial for the optimal legislative composition
+the decline in efficiency in larger legislatures \citep{Weingastetal1981}. In
+large council, it is harder for members to collaborate with each other without
+some type of partisanship or formal legislative structure
+\citep{kirkland2014chamber, rush2013conclusion}. Larger chambers also have more
+potential veto players, who may decrease policymaking efficiency
+\citep{tsebelis2002veto}. In this sense, balancing representation and
+efficiency is key to find the optimal legislative composition
 \citep{auriol2012optimal, taagepera1972size}.
 
-This literature has often overlooked two important questions. First, does
-legislature size matter in contexts where legislative bodies are not the
-pivotal decision-maker? And second, what is the ultimate effect of legislature
-size on welfare? These gaps are likely generated by the predominance of the
-"law of 1/n" scholarship in political economy debates, which focus mainly on
-the relationship between legislature size and overspending. Since
-\citet{Weingastetal1981}, 30 papers have systematically tested the effects of
-legislature size on government expenditures \citep{freire2021legislature}. Of
-these papers, only \citet{lewis2019legislature} investigates its effects on
-welfare, showing that larger legislatures have a negative welfare
-effect.\footnote{\citet{koppel2004public} also shows, using a repeated game
-where the proposal prerogative rotates in a legislature, that larger
-legislatures increase the chances of non-cooperative outcomes, lowering public
-goods provision.} \citet{frey2021legislature} analyzes the Brazilian case after
-the 2009 legislature size change and finds a null effect in service provision
-from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} find that in the US
-legislature size is associated primarily with higher spending on geographically
-concentrated benefits, such as education and highways. These results suggest
-that the legislature size and welfare nexus needs a dedicated theoretical and
-empirical assessment.
+However, two questions have often been overlooked in these debates. First, does
+legislature size matter in contexts where legislative bodies are not pivotal
+decision-makers? Second, what is the ultimate effect of legislature size on
+welfare? These gaps are likely generated by the predominance of the "law of
+1/n" scholarship in this literature, which focuses mainly on the relationship
+between legislature size and overspending. Since \citet{Weingastetal1981}, 30
+papers have tested the effects of legislature size on government expenditures
+\citep{freire2021legislature}, and the only article which examined its effects
+on welfare found negative results
+\citep{lewis2019legislature}.\footnote{\citet{koppel2004public} uses a repeated
+game where the proposal prerogative rotates in a legislature and finds that
+larger legislatures increase the chances of non-cooperative outcomes, lowering
+public goods provision.} \citet{frey2021legislature} analyzes the Brazilian
+case after the 2009 legislature size change and finds a null effect in service
+provision from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} find that in
+the US legislature size is associated primarily with higher spending on
+geographically concentrated benefits, such as education and highways. These
+results suggest that the legislature size and welfare nexus needs a dedicated
+theoretical and empirical assessment.
 
@@
 ($M$) and $N \geq 3$ city councilors indexed in $i \in \{1, 2, \cdots, N \}$.
-The mayor has the prerogative of proposing a vector of policies on which city
-councilors vote. The provision of public goods is then a bargain between the
-mayor and the city council. Policy proposals are a combination of public goods
-provision $g$, rents for the mayor $r$, and a vector of transfer for city
+The mayor has the prerogative of proposing a vector of policies to be voted by
+the city councilors. The provision of public goods is then a bargain between
+the mayor and the city council. Policy proposals are a combination of public
+goods provision $g$, rents for the mayor $r$, and a vector of transfer for city
 councilors \textbf{x}.
 
-The city council votes the mayor's proposal, and if councilors accept it, the
-proposal is implemented. Otherwise, a reversal policy takes place. Reversal
+The city council votes the mayor's proposal and the proposal is implemented if
+most councilors accept it. Otherwise, a reversal policy takes place. Reversal
 policy in this context means that the mayor's proposal failed to secure the
@@
 the selectorate, that is, the individuals who have a say in the mayor's policy
-proposals, are the $N$ city councilors. The winning coalition, the minimum
-number of members that must be convinced to implement the policy, is equal to
-half of the selectorate ($N/2$). City councilors are motivated by policy
-concerns $p$ and transfers received from the mayor or the councilor nominated
-as the proposer \textbf{x}. We leave the definition of these transfers open, as
-this allows us to analyze how mayors combine transfers with other incentives to
-pressure city councilors. Exemples of transfers are granting electoral favors,
-funding clientelistic brokers, spending in areas that the councilor has
-political or personal interests, providing portfolio (municipal offices) and
-public jobs within the municipal bureaucracy, or even giving campaign
-contributions and bribes. The use of transfers to influence the councilors'
-choices generate a bargaining cost of $C_G$. Bargaining costs vary according to
-the reversal mechanism and the size of the legislature.
+proposals, are the $N$ city councilors. The winning coalition, which is the
+minimum number of members that must be convinced to implement the policy, is
+equal to half of the selectorate ($N/2$). City councilors are motivated by
+policy concerns $p$ and transfers received from the mayor or the councilor
+nominated as the proposer \textbf{x}. We leave the definition of these
+transfers open, as this allows us to analyze how mayors combine transfers with
+other incentives to pressure city councilors. Exemples of transfers are
+granting electoral favors, funding clientelistic brokers, spending in areas in
+which the councilor has political or personal interests, or providing portfolio
+(municipal offices) and public jobs within the municipal bureaucracy. The use
+of transfers to influence the councilors' choices generate a bargaining cost of
+$C_G$. Bargaining costs vary according to the reversal mechanism and the size
+of the legislature.
 
@@
 the mayor to get reelected. Rents are for the mayor's direct consumption and do
-not contribute to the mayor's electoral success.\footnote{This model, similar
-to \citet{cowen1994rent} and \citet{buenodemesquita2005logic}, combines public
+not contribute to her electoral success.\footnote{This model, similar to
+\citet{cowen1994rent} and \citet{buenodemesquita2005logic}, combines public
 goods provision and rent extraction. For a dynamic bargaining model that
@@
 the public goods provision can be claimed by councilors as their contribution.
-We propose an extension in the Online Supplementary Materials, which assumes $p
-= \phi g$, where $\phi$ is the fraction of the public goods provision that can
-be credit claimed by the city councilor aligned with the mayor.} If councilors
+We propose an extension in the Supplemental Materials, which assumes $p = \phi
+g$, where $\phi$ is the fraction of the public goods provision that can be
+credit claimed by the city councilor aligned with the mayor.} If councilors
 reject the mayor's proposal, no public goods are provided ($p=0$). Moreover, in
 equilibrium, we assume that city councilors would prefer to receive transfers
-instead of providing public goods.\footnote{In the Online Supplementary
-Materials, we consider a version of the model in which public goods provision
-depends on the party affiliation of the proposer so that it affects choices in
-any potential history of the game. In equilibrium, the level of public goods
-provision is even higher than in the model presented here, as city councilors
-prefer to approve the mayor's proposal than run the risk of an opposition
-member becoming the proposer.}
+instead of providing public goods.\footnote{In the Supplemental Materials, we
+consider a version of the model in which public goods provision depends on the
+party affiliation of the proposer so that it affects choices in any potential
+history of the game. In equilibrium, the level of public goods provision is
+even higher than in the model presented here, as city councilors prefer to
+approve the mayor's proposal than run the risk of an opposition member becoming
+the proposer.}
 
@@
 If the offer is accepted, it is implemented.
-If rejected, the reversal policy stage restarts.\footnote{In section A.1 of the Supplementary Materials, we solve three reversal mechanisms.
+If rejected, the reversal policy stage restarts.\footnote{In section A.1 of the Supplemental Materials, we solve three reversal mechanisms.
 We include the two mechanisms we present here, plus a third mechanism with only political concerns.}
@@
 
-All proofs are in section A.1 of the Supplementary Materials. The proof's
+All proofs are in section A.1 of the Supplemental Materials. The proof's
 intuition involves finding what happens to the mayor's marginal utility when we
@@
 convince half of the councilors. The second part represents the gains if the
-councilor rejects the current received offer but still gets an offer in the
-following round. It is equal to the chance that she is not recognized as the
-proposer times the chance that she receives a transfer times the transfer
-amount. Note that the offer the councilor makes as the proposer is the same as
-the offer she wants to receive. This is because the city councilors are
-exchangeable. The solution is symmetric for all councilors receiving an offer
-(this means that, without loss of generality, we could have dropped the $i$ in
-the solution). After some algebra, the offer $x_i$ must be greater than or
-equal to:
+councilor rejects the current offer but still gets an offer in the following
+round. It is equal to the chance that she is not recognized as the proposer
+times the chance that she receives a transfer times the transfer amount. Note
+that the offer the councilor makes as the proposer is the same as the offer she
+wants to receive. This is because city councilors are exchangeable. The
+solution is symmetric for all councilors receiving an offer (this means that,
+without loss of generality, we could have dropped the $i$ in the solution).
+After some algebra, the offer $x_i$ must be greater than or equal to:
 
@@
 costs. And if the bargaining costs increase with legislature size, then any
-increase in public goods provision associated with legislature size has come
+increase in public goods provision associated with legislature size has to come
 from a different mechanism. Below we demonstrate that partisanship is the key
@@
 
-We decompose these costs into two components. First, the costs in terms of
-rents. Second, the costs (or benefits) from political alignment. In this
-context, the bargaining costs depend on the mayor's offers for councilors in
-her coalition versus the mayor's proposals for councilors in the opposition. As
-the ex-ante chance of an opposition member being elected is equal to
-$1-\gamma$, after taking the weighted averages these costs become:
+We decompose these costs into two components, which are the costs in terms of
+rents and the costs (or benefits) from political alignment. In this context,
+the bargaining costs depend on what the mayor offers for councilors in her
+coalition versus what she provides to members of the opposition. As the ex-ante
+chance of an opposition member being elected is equal to $1-\gamma$, after
+taking the weighted averages these costs become:
 
@@
 
-The intuition for the proof is that as partisanship influences the costs and
-benefits of legislators, more government-aligned councilors make it easier for
-the mayor to govern. When the partisan benefit is higher than the additional
-cost that a legislator generates, adding a councilor will benefit mayors if the
-councilor has a higher chance of sharing the same party as the mayor.
-Therefore, a higher probability of electing a legislator aligned with the mayor
-reverts into lower bargaining costs.
+The intuition for the proof is the following. As partisanship influences the
+costs and benefits of legislators, more government-aligned councilors make it
+easier for the mayor to govern. When the partisan benefit is higher than the
+additional cost that a legislator generates, adding a councilor will benefit
+mayors if the councilor has a higher chance of sharing the same party as the
+mayor. Therefore, a higher probability of electing a legislator aligned with
+the mayor reverts into lower bargaining costs.
 
@@
 
-In 2004, Brazil comprised 5,560 municipalities. According to the Brazilian
+In 2004, Brazil comprised 5,560 municipalities. According to the 1988 Brazilian
 Constitution, each city must provide health care, primary education,
@@
 Until 2004, there was no specific regulation on the size of city councils. The
-1988 Brazilian Constitution set only broad guidelines about the number of
-council seats in each municipality, allowing cities to determine how many
-legislators their local chambers should have. This led to severe imbalances in
-the representation ratio across the country. For instance, the Nova Russas
+Brazilian Constitution set only broad guidelines about the number of council
+seats in each municipality, allowing cities to determine how many legislators
+their local chambers should have. This led to severe imbalances in the
+representation ratio across the country. For instance, the Nova Russas
 municipality had 30,009 inhabitants and 21 councilors, or one legislator per
@@
 Court established a series of population cutoffs for all municipal
-legislatures. Following the Brazilian Constitution, the Court specified that
-cities with up to one million residents should have between 9 and 21
-legislators. The number of seats was allocated as follows. Each town starts
-with nine councilors, then adds one legislator for every 47,619 inhabitants
-until their councils reach 21 members. This threshold implies that cities with
-a population between 571,428 and one million should all have the same number of
-legislators, that is, 21 of them. Conversely, cities between one and four
-million inhabitants should have at least 33 councilors, and this number
-increases up to 41 members following the previous formula of one additional
-legislator per 47,619 inhabitants.
+legislatures. The Court specified that cities with up to one million residents
+should have between 9 and 21 legislators. The number of seats was allocated as
+follows. Each town starts with nine councilors, then adds one legislator for
+every 47,619 inhabitants until their councils reach 21 members. This threshold
+implies that cities with a population between 571,428 and one million should
+all have the same number of legislators, that is, 21 of them. Conversely,
+cities between one and four million inhabitants should have at least 33
+councilors, and this number increases up to 41 members following the previous
+formula of one additional legislator per 47,619 inhabitants.
 
@@
 (IPEA) in 2009. The authors asked councilors about their daily work. The
-interviews reinforced that the mayor's agenda dominates councilors' work and it
-is partisan without strictly following party lines. Municipal politics is
+interviewees confirmed that the mayor's agenda dominates councilors' work and
+it is partisan without strictly following party lines. Municipal politics is
 divided into families or powerful groups that belong to different party
 affiliations. Councilors from other parties gravitate around these groups,
-hence the opposition and government-aligned logic.} The municipal data
-contains: 1) the number of councilor's belonging to the mayor's pre-electoral
-coalition; 2) the number of appointed bureaucrats; 2) the councilor's gender
-and race; 3) the competitiveness of each city council seat; 4) the proportion
-of laws proposed by the city council that was approved. All variables come from
-the Supreme Electoral Court, the Senate legislative support Interlegis, and the
-Brazilian Bureau of Statistics.
+hence the clear government versus opposition logic.} The municipal data
+contain: 1) the number of councilors who belong to the mayor's pre-electoral
+coalition; 2) the number of appointed bureaucrats; 3) the councilor's gender
+and race; 4) the competitiveness of each city council seat; 5) the proportion
+of laws proposed by the city council that was approved. The variables come from
+the Supreme Electoral Court (TSE), the Senate Legislative Data Service
+(InterLegis), and the Brazilian Bureau of Statistics (IBGE).
 
@@
 differentiate between clientelism and broad service provision, as it is hard to
-disentangle differences in the local level legislation. A voter may request a
+disentangle between the two in local legislation. A voter may request a
 particular service, such as fixing a pothole. Attending this request can be
@@
 provide further information about the legislation dataset and the city council
-survey in sections A.13 and A.14 of the Supplementary Materials.
+survey in sections A.13 and A.14 of the Supplemental Materials.
 
@@
 the council size ruling. Summary statistics and variable descriptions are
-available in section A.2 of the Supplementary Materials.
+available in section A.2 of the Supplemental Materials.
 
@@
 
+\vspace{.2cm}
+
 \begin{figure}[htb!]
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrSeats.pdf}}
+      \centerline{\includegraphics[width=6.8in,angle=0]{../figures/distrSeats.pdf}}
       \caption{Distribution of Municipalities by Population and City Council Size}
@@
 
-For the first assumption, in section A.3 of the online supplemental materials,
+For the first assumption, in section A.3 of the Supplemental Materials
 we assess distribution imbalances running the \citet{McCrary2008} and
@@
 
-To avoid this problem, in section A.5 of the Supplemental Materials, we show by
+To avoid this problem, in section A.5 of the Supplemental Materials we show by
 simulation that adding controls, especially the variables responsible for the
@@
 covariates, for both real and placebo cutoffs. At the bottom, we estimate the
-pre-treatment covariate balance. Furthermore, in the Supplementary Materials,
+pre-treatment covariate balance. Furthermore, in the Supplemental Materials,
 we run placebo checks for all the models using placebo cutoffs within the real
-ones. The results are available in sections A.6 to A.12 of the Supplementary
+ones. The results are available in sections A.6 to A.12 of the Supplemental
 Materials.
@@
 demonstrating that representation of women and non-whites, competitiveness, and
-legislative productivity fail to receive empirical support.
+legislative productivity fail to receive empirical support in our analyses.
 
@@
 coalition support within the city council.\footnote{We provide further
-information about the city council survey in section A.14 of the Supplementary
+information about the city council survey in section A.14 of the Supplemental
 Materials.} Second, we collected 346,553 laws approved in 63 municipalities
 within ten thousand inhabitants away from the city council size thresholds. We
-hand-coded 3,466 laws into four categories: public goods, oversight, education
+hand-coded 3,466 laws into four categories: Public goods, oversight, education
 and health care-related legislation, and other legislative duties. After
@@
 the highest performance.
+
+\vspace{.2cm}
 
@@
 
-We assume that city councilors want to extract rents and to get reelected. The
+We assume that city councilors want to extract rents and be reelected. The
 rents come from continuing in the repeated game, and the partisanship discounts
@@
 In this paper, we show that the provision of education and health care in
-Brazil improves with larger legislatures. This is because the chances of
-electing a government-aligned candidate are 91 percent thanks to the rule of
-distributing seats adopted in the country. In the Supplemental Materials, we
-also run regressions in placebo cutoffs between the actual cutoffs, showing
+Brazil improves with larger legislatures. This is because there is a 91-percent
+chance of electing a government-aligned candidate, largely due to the rule used
+to distribute legislative seats in the country. In the Supplemental Materials,
+we also run regressions in placebo cutoffs between the actual cutoffs, showing
 that our estimates are consistently null when we are indeed supposed to find
@@
 
-Second, more seats could increase the competitiveness in the election, making
-politicians provide more services \citep{besley2010political}. In a political
-system with around thirty parties and a sample average of almost ten parties in
-the municipalities we study, candidates per seat can increase exponentially.
-According to the Brazilian electoral law, each party can sponsor 1.5 candidates
-per seat. If a party forms a pre-electoral coalition, this number increases to
-two times the number of seats \citep{coneglian2008lei}. An election in a small
-town, with ten councilors, may end up with 600 candidates: (30 parties) x (two
-times the number of seats) x (ten seats). Therefore, an alternative explanation
-for better service provision is that a larger council size increases the
+Second, more seats could increase the election competitiveness, forcing
+politicians to provide more services to remain competitive
+\citep{besley2010political}. In a political system with around thirty parties
+and a sample average of almost ten parties in the municipalities we study,
+candidates per seat can increase exponentially. According to the Brazilian
+electoral law, each party can sponsor 1.5 candidates per seat. If a party forms
+a pre-electoral coalition, this number increases to two times the number of
+seats \citep{coneglian2008lei}. An election in a small town, with ten
+councilors, may end up with 600 candidates: (30 parties) x (two times the
+number of seats) x (ten seats). Therefore, an alternative explanation for
+better service provision is that a larger council size increases the
 competitiveness of the election.\footnote{Despite the common assumption that
@@
 
-Finally, the mayor and the legislature carry out the provision of services.
-Similar to what happens in firms, an extra employee can increase the firm
-productivity frontier by improving cooperation and synergistic outputs
+Finally, both the mayor and the legislature carry out the provision of
+services. Similar to what happens in firms, an extra employee can increase the
+firm productivity frontier by improving cooperation and synergistic outputs
 \citep{alchian1972production, holmstrom1982moral}. A similar argument would
@@
 different mechanisms. Columns (1) and (2) test the hypotheses that better
-representation of under-served groups could improve welfare. As we can see,
-larger city councils do not increase the representation of females or
-non-whites. Column (3) shows that the competition per seat in municipalities
-with larger city councils remain statistically equal to zero. Finally, Column
-(4) shows that the proportion of legislation passed by the city council remains
-unchanged when council size increases.
+representation of under-served groups could improve welfare. As we see, larger
+city councils do not increase the representation of females or non-whites.
+Column (3) shows that the competition per seat in municipalities with larger
+city councils remain statistically equal to zero. Finally, Column (4) shows
+that the proportion of legislation passed by the city council remains unchanged
+when council size increases.
 
@@
 This paper shows that partisanship considerably decreases bargaining costs and
-improves citizen welfare. The crucial actors in providing public goods are the
-mayors, but they cannot do it alone. Legislatures are a solid check to the
-mayor's agenda. Bargaining with them in a country plagued by corruption can be
+improves citizen welfare. The main providers of public goods are the mayors,
+but they cannot do it alone. Legislatures provide a solid check to the mayor's
+agenda. Bargaining with legislators in a country plagued by corruption can be
 costly \citep{bertholini2017price}. Therefore, an extra ally in the city
@@
 positive outcome. The analysis of the approved legislation shows that the
-frequency of laws on local public goods increases in municipalities above the
-council size thresholds. Finally, our survey data demonstrate that councilors
-and mayors agree about appointing more civil servants to the public
+frequency of laws discussing local public goods increases in municipalities
+above the council size thresholds. Finally, our survey data demonstrate that
+councilors and mayors agree about appointing more civil servants to the public
 administration.
@@
 provision of private goods. Indeed, the most successful presidents after 1995
-had to build extensive coalitions by negotiating with several parties
-\citep{limongi1998bases, raile2011executive}. Despite evidence that side
-payments cemented these coalitions, many social and economic policies have
-since been implemented. For instance, education and health care notably
-improved during the Cardoso and Lula administrations
-\citep{acemoglu2012nations}. Presidents who challenged the coalition system did
-not succeed. For instance, former President Rousseff was impeached in her
-second term. Bolsonaro can be considered one of the most ineffective presidents
-in Brazilian history.
+had to build extensive coalitions and negotiate with several parties to secure
+legislative support \citep{limongi1998bases, raile2011executive}. Despite
+evidence that side payments cemented these coalitions, many social and economic
+policies have since been implemented. For instance, education and health care
+notably improved during the Cardoso and Lula administrations
+\citep{acemoglu2012nations}. In contrast, presidents who challenged the
+coalition system did not succeed. For instance, former President Rousseff was
+impeached in her second term. Bolsonaro can be considered one of the most
+ineffective presidents in Brazilian history.
 
 Municipalities work similarly in terms of the incentives for
-legislative-executive bargaining. The stakes are lower, and the negotiations
-involve only one legislative branch. Still, in a system such as Brazil's, with
-more than thirty-five registered parties, mayors face substantial challenges to
-approve their political agendas. Having extra help in the council can tilt the
-bargaining towards cheaper governing costs, thus improving public goods
-provision.
+legislative-executive bargaining. In this case, the stakes are lower and the
+negotiations involve only one legislative branch. But in a system such as
+Brazil's, with more than thirty-five registered parties, mayors face
+substantial challenges to approve their political agendas. Having extra help in
+the council can tilt the bargaining towards cheaper governing costs, thus
+improving public goods provision.
 
@@
 depends on the marginal changes of the rents and public goods, but these two
-components receive the extra resources. In this case, the mayor's rents may be
-primarily corruption, and the councilor's transfers can be clientelistic, aimed
-at improving the councilor's reelection chances.
+components receive the extra resources. In some cases, the mayor's rents may be
+primarily corruption, and the councilor's transfers can be clientelistic and
+aimed at improving his or her reelection prospects.
 
@@
 checking prerogatives, as they significantly reduce the provision of public
-services. The evidence so far is inconclusive, and \citet{poulsen2018political}
+services. The evidence so far is inconclusive, as \citet{poulsen2018political}
 show that checks for the mayors may also improve service provision. Second,

### 2022-05-17 appendix/appendix.Rmd
change title supplemental materials

@@
 title: |
-       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
+       | Supplemental Materials for "Legislature Size and Welfare: Evidence from Brazil"
 author:

### 2022-05-17 memorandum/memo.Rmd
some housekeeping

--- 2022-05-17 Memo/memo.Rmd
@@
 online survey. Therefore, we have detailed our survey procedures in Section A.14
-of the Supplementary Materials (pages 23-24), and we also briefly discuss our
+of the Supplemental Materials (pages 23-24), and we also briefly discuss our
 survey methodology on pages 17 and 22 (footnote 13) of the main article.
@@
 
-We have also added a similar discussion to Section A.5 of the Supplementary
+We have also added a similar discussion to Section A.5 of the Supplemental
 Materials.
@@
 We collapse two concerns from Reviewer 3 since they both speak to core topics in
-our paper. In Table 6 of the Supplementary Materials (page 21), we show that an
+our paper. In Table 6 of the Supplemental Materials (page 21), we show that an
 additional legislator usually does not lead to significant increases in public
@@
 parties are not driving our results. We have ommitted the table from the
-Supplementary Materials to conserve space, but it is available on the article's
+Supplemental Materials to conserve space, but it is available on the article's
 GitHub repository.

### 2022-05-28 article/article.Rmd
reduce word count article and memo

@@
 the birth of representative governments placed legislatures at the center of
-the political stage. In modern democracies, most countries have assemblies at
-all levels of government. These institutions regulate the quantity and quality
-of legislation, check and veto other political powers, and influence
-policymaking. Moreover, legislatures also determine taxation, regulate
-government spending, and oversee public programs \citep{auriol2012optimal,
-north1989constitutions, poulsen2018political, stasavage2011states,
+the political stage. Today, these institutions check and veto other political
+powers, determine taxation, and oversee public programs at all levels of
+government \citep{auriol2012optimal, poulsen2018political, stasavage2011states,
 Weingastetal1981}.
@@
 internal procedures, all legislatures share one common feature: They are
-collective bodies. As such, the number of elected representatives has important
-consequences for the whole polity. Legislature size is known to have a
-significant effect on the bargaining power between state branches, public
-expenditures, and representation \citep{crain1979cost, freire2021legislature,
+collective bodies. As such, the number of representatives has important
+consequences for the whole polity. Legislature size has a significant effect on
+the bargaining power between state branches, public expenditures, and
+representation \citep{crain1979cost, freire2021legislature,
 gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
 However, how legislature size impacts social welfare remains less understood.
-On the one hand, larger legislatures may reduce political particularism and
-increase overall government spending, which can lead to more public goods
-\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}. On the
-other hand, adding representatives to a legislature may exacerbate collective
-action problems, thus hindering service provision
-\citep{gottlieb2019countervailing, tsebelis2002veto}. Therefore, what is the
-effect of larger legislatures on public service delivery?
+Larger legislatures may reduce political particularism and increase overall
+government spending, which leads to more public goods
+\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}. But
+adding representatives to a legislature may exacerbate collective action
+problems, thus hindering service provision \citep{gottlieb2019countervailing,
+tsebelis2002veto}. Therefore, what is the effect of larger legislatures on
+public service delivery?
 
@@
 politics to explain how city council size impacts local public goods provision.
-First, in mayor-council municipalities, mayors are the main responsible for
-public service decisions and can boost local public investments by altering the
-government budget. Second, partisanship plays a key role in city politics, even
-in countries in which ideological attachment is relatively weak. Party
-attachment structures political views \citep{samuels2014power}, and local-level
-elites usually belong to different factions and parties. They fight for power
-in the municipality by controlling various parties and forming distinct
-pre-electoral coalitions.\footnote{Elite political competition in the local
-level has also been linked to violence and conflict in Brazil and elsewhere
-\citep{hoelscher2015politics, mignozzetti2018predatory}.} In many cities,
-family ties may be substitutes for the ideological component, but influential
-local leaders usually sort themselves into different political groups
-\citep{ferraz2020political, nunes1977coronelismo}.
-
-This paper incorporates partisanship and mayoral first-move advantage to a
+We incorporate partisanship and mayoral first-move advantage to a
 \citet{baron1989bargaining} bargaining model. Mayors make the initial policy
@@
 We test these theoretical predictions by exploiting exogenous variation in city
-council size in Brazil. In 2004, the judiciary reinterpreted the Brazilian
-Constitution and unexpectedly changed the number of councilors in several
-municipalities. Until then, cities could freely determine their legislature
-size. But in March 2004 the Supreme Electoral Court created population
-thresholds and added one councilor to each set of 47,619 inhabitants. Around
-these cutoffs, the decision represented an exogenous change in city council
-size, allowing us to investigate the effects of increasing the number of local
-legislators in Brazil.
+council size in Brazil. Brazilian cities could freely determine their
+legislature size, but in March 2004 the Supreme Electoral Court unexpectedly
+reinterpreted the 1988 Constitution and added one councilor to each set of
+47,619 inhabitants. Around these cutoffs, the decision represented an exogenous
+change in city council size, allowing us to investigate the effects of
+increasing the number of local legislators in Brazil.
 
@@
 To provide further evidence for our mechanisms, we surveyed 174 former
-councilors who served during the 2005-2008 term, the period we analyse in this
+councilors who served during the 2005-2008 term, the period we analyze in this
 paper. They confirm that mayors indeed use bureaucratic appointments and
@@
 bargaining with councilors requires offering transfers to the representatives.
-By asking councilors what they would like to provide to voters, we find that
-councilors mainly demand job appointments, which are regarded as an effective
-means to boost their reelection prospects and improve municipal welfare. These
-findings are in line with quantitative results from a novel dataset we built
-with 346,553 laws passed in 63 municipalities within ten thousand inhabitants
-away from the cutoffs. While all municipalities mention public goods in their
-legislation, those with larger city councils have 15 percent more proposals
-about public service delivery, which is consistent with our argument.
+Councilors also demand several job appointments, which are regarded as an
+effective means to boost their reelection prospects and improve municipal
+welfare. These findings are in line with quantitative results from a novel
+dataset we built with 346,553 laws passed in 63 municipalities within ten
+thousand inhabitants away from the cutoffs. While all municipalities mention
+public goods in their legislation, those with larger city councils have 15
+percent more proposals about public service delivery.
 
@@
 dialogues with a large literature on multilateral bargaining. Repeated models
-of multilateral bargaining started with \citet{baron1989bargaining}, who
-expanded the bilateral bargaining game proposed by
-\citet{rubinstein1982perfect} to more than two players. Several authors then
-analysed the effect of endogenous recognition power, the size of the required
-majority, and partisanship on these models \citep{agranov2020persistence,
-baranski2020determinants, calvert2005legislative,
-choate2019partisan}.\footnote{See \citet{eraslan2019legislative} for a
-comprehensive review of multilateral bargaining and \citet{ray2015coalition}
-for a review on coalition formation.} In this article, we extend
-\citeauthor{baron1989bargaining}'s (\citeyear{baron1989bargaining}) model under
-closed rules and add the mayor's first move and political partisanship. We
-consider partisanship as a zero-sum effect that is positive for politicians
-aligned with the mayor and negative otherwise. We investigate the often
-overlooked effect of legislature size on the bargaining equilibrium strategies.
+of multilateral bargaining started with \citet{baron1989bargaining}, and
+scholars have recently analysed how endogenous recognition power, the size of
+the required majority, and partisanship impact these results
+\citep{agranov2020persistence, baranski2020determinants,
+calvert2005legislative, choate2019partisan}. Here we include the mayor's first
+move and political partisanship to Baron and Ferejohn's
+(\citeyear{baron1989bargaining}) and investigate the often-overlooked effect of
+legislature size on bargaining equilibrium strategies.
 
@@
 factors such as the degree that local public goods can exclude non-locals or
-deadweight costs associated with taxation.} In the US case, this would
-explain significant infrastructure spending in smaller districts. However, the
-literature on the "law of $1/n$" rarely mentions the relationship between
-public goods provision and welfare. This paper is one of the first to study how
-the number of local legislators affects citizen well-being. Our model provides
-a theoretical expectation based on the chances of electing a politician aligned
-with the mayor. The empirical estimates confirm our theoretical predictions,
-with the additional fact that legislature size has a null effect on
-expenditures in Brazil.
-
-Third, our article also dialogues with the growing literature on municipal
-partisan politics. Most papers in this field estimate the effects of the
-mayor's party on political outcomes. For instance, \citet{de2016mayoral} and
+deadweight costs associated with taxation.} However, the literature on the "law
+of $1/n$" rarely mentions the relationship between public goods provision and
+welfare. To our knowledge, this paper is one of the first to study how the
+number of local legislators affects citizen well-being.
+
+Third, our article dialogues with the growing literature on municipal partisan
+politics. Most papers in this field estimate the effects of the mayor's party
+on political outcomes. For instance, \citet{de2016mayoral} and
 \citet{gerber2011mayors} find differences in governance when comparing
@@
 \citet{gouvea2021partisanship} show that social spending increases with
-left-wing mayors. \citet{frey2021legislature}, using discontinuities in city
-council size after the 2009 constitutional amendment that reverted the
-thresholds we study here, shows that changes in council size lower the support
-for candidates backed by the municipal mayors. Our paper reinforces the view
-that partisanship matters locally, even in countries with weak ideological
-linkage.
-
-Finally, this paper contributes to the literature on the causes and effects of
+left-wing mayors. Using discontinuities created by a constitutional amendment
+that reverted the thresholds we study here, \citet{frey2021legislature} shows
+that changes in council size lower the support for mayor-backed candidates. Our
+paper reinforces the view that partisanship matters locally, even in countries
+with weak ideological linkage.
+
+Finally, this paper also contributes to the literature on the causes and effects of
 legislature sizes. While most papers on legislature size analyse the trade-off
 between representation and efficiency \citep{frederick2008people,
-jacobs2015explaining, muzzio1989size, Stigler1976}, recent articles have
+jacobs2015explaining, Stigler1976}, recent articles have
 explored the effects of legislature size on lawmaking and partisanship in
@@
 it harder for politicians to know and collaborate with each other, so they rely
-more heavily on party cues and committee structures. In considering the causes
-of changes in legislature sizes, \citet{jacobs2015explaining} show that while
-population shifts tend to increase the number of local legislators, economic
-crises decrease them. \citet{marland2019fewer} questions the latter mechanism,
+more heavily on party cues and committee structures.
+\citet{jacobs2015explaining} show that population shifts tend to increase the
+number of local legislators, but legislature size tends to decrease during
+economic crises. \citet{marland2019fewer} questions the latter mechanism,
 showing that political elites shrink legislatures mostly to signal to the
@@
 Institutional design has a lasting impact on social welfare
-\citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions}
-and democratic consolidation \citep{gandhi2019institutional,
-lijphart2018institutional}. One particular problem that all polities face is
-how to determine the optimal size of their legislative bodies. The literature
-on this topic is extensive, and modern attempts to address the legislature size
-problem started in the early eighteenth century with the Federalists versus
-Anti-Federalists debates \citep{muzzio1989size, Stigler1976}.
+\citep{acemoglu2012nations, buenodemesquita2005logic}.
+One issue that all polities face is how to determine the optimal size of their
+legislative bodies. The literature on this topic is extensive, and modern
+attempts to address the legislature size problem started in the early
+eighteenth century with the Federalists versus Anti-Federalists debates
+\citep{Stigler1976}.
 
@@
 causes tension between representation and efficiency
-\citep{frederick2008people, jacobs2015explaining, muzzio1989size,
-rush2013conclusion, Stigler1976, taagepera1972size}. Larger legislatures
-improve representation as both the election thresholds and the ratio of
-population-per-politician decrease, which facilitate the electoral success of
-ethnic and political minorities \citep{allenrepresentation,
-gerring2020population}. However, better representation is often countered by
-the decline in efficiency in larger legislatures \citep{Weingastetal1981}. In
-large council, it is harder for members to collaborate with each other without
-some type of partisanship or formal legislative structure
-\citep{kirkland2014chamber, rush2013conclusion}. Larger chambers also have more
-potential veto players, who may decrease policymaking efficiency
+\citep{frederick2008people, jacobs2015explaining, taagepera1972size}. On the
+one hand, larger legislatures improve representation and facilitate the
+electoral success of ethnic and political minorities
+\citep{allenrepresentation, gerring2020population}. On the other hand, better
+representation is often countered by the decline in efficiency in larger
+legislatures \citep{Weingastetal1981}. In large councils, it is harder for
+members to collaborate with each other without some type of partisanship or
+formal legislative structure \citep{kirkland2014chamber}. Larger chambers also
+have more potential veto players, who may decrease policymaking efficiency
 \citep{tsebelis2002veto}. In this sense, balancing representation and
@@
 \citep{freire2021legislature}, and the only article which examined its effects
-on welfare found negative results
-\citep{lewis2019legislature}.\footnote{\citet{koppel2004public} uses a repeated
-game where the proposal prerogative rotates in a legislature and finds that
-larger legislatures increase the chances of non-cooperative outcomes, lowering
-public goods provision.} \citet{frey2021legislature} analyzes the Brazilian
-case after the 2009 legislature size change and finds a null effect in service
-provision from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} find that in
-the US legislature size is associated primarily with higher spending on
-geographically concentrated benefits, such as education and highways. These
-results suggest that the legislature size and welfare nexus needs a dedicated
-theoretical and empirical assessment.
-
-Despite the importance of legislatures, the executive still dominates the
-public debate on public service provision in most mayor-council (or
-presidential) systems. For instance, while in 2021 the New York Times cited
-Mayor Bill De Blasio 2,084 times, it mentioned the 49 seating city councilors
-only 440 times in the same year. When we expand the search for the past five
-years, we see that De Blasio was mentioned 8,978 times while the 49 seating
-city councilors were mentioned only 2,046 times.\footnote{We computed these
-figures using the Dow Jones Factiva Database in November 2021.} On average, the
-mayor was cited four times more often than all the city councilors combined.
-This executive dominance has implications for policymaking, as coalitions and
-affinity with the executive are going to be crucial for service provision
-\citep{buenodemesquita2005logic}.
+on welfare found negative results \citep{lewis2019legislature}.
+\citet{frey2021legislature} analyzes the Brazilian case after the 2009 change
+in legislature size and finds a null effect in service provision from 2012 to
+2016. Yet, \citet{GilliganMatsusaka2001} find that in the US legislature size
+is associated primarily with higher spending on geographically concentrated
+benefits, such as education and highways. These results suggest that the
+legislature size and welfare nexus needs a dedicated theoretical and empirical
+assessment.
 
@@
 for our argument, as they change the relative strength of the council when
-legislators bargain with the mayor. We investigate two types of reversal
+legislators bargain with the mayor. Here we investigate two types of reversal
 policies: A baseline reversal with no parties and a hybrid mechanism with
@@
 transfers open, as this allows us to analyze how mayors combine transfers with
-other incentives to pressure city councilors. Exemples of transfers are
+other incentives to pressure city councilors. Examples of transfers are
 granting electoral favors, funding clientelistic brokers, spending in areas in
 which the councilor has political or personal interests, or providing portfolio
-(municipal offices) and public jobs within the municipal bureaucracy. The use
+(municipal offices) and public jobs within the bureaucracy. The use
 of transfers to influence the councilors' choices generate a bargaining cost of
@@
 the mayor to get reelected. Rents are for the mayor's direct consumption and do
-not contribute to her electoral success.\footnote{This model, similar to
-\citet{cowen1994rent} and \citet{buenodemesquita2005logic}, combines public
-goods provision and rent extraction. For a dynamic bargaining model that
-incorporates transfers to districts and public goods provision, see
-\citet{battaglini2012legislative}.} This makes the mayor's expected utility a
+not contribute to her electoral success. This makes the mayor's expected utility a
 sum of the gains from rents and the benefits from reelection. Both the
@@
 value of $p > 0$ for the councilors, and whether it adds or subtracts from the
-councilor's utility depends on the party affiliation of the
-councilor.\footnote{One example of partisan benefits is that, as the mayor
-shares partisan ties with members of the government coalition, a fraction of
-the public goods provision can be claimed by councilors as their contribution.
-We propose an extension in the Supplemental Materials, which assumes $p = \phi
-g$, where $\phi$ is the fraction of the public goods provision that can be
-credit claimed by the city councilor aligned with the mayor.} If councilors
-reject the mayor's proposal, no public goods are provided ($p=0$). Moreover, in
-equilibrium, we assume that city councilors would prefer to receive transfers
-instead of providing public goods.\footnote{In the Supplemental Materials, we
-consider a version of the model in which public goods provision depends on the
-party affiliation of the proposer so that it affects choices in any potential
-history of the game. In equilibrium, the level of public goods provision is
-even higher than in the model presented here, as city councilors prefer to
-approve the mayor's proposal than run the risk of an opposition member becoming
-the proposer.}
-
-The timeline of the strategic interaction is as follows:
-
-\begin{enumerate}
-  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
-  \item The mayor proposes a policy vector $(r, g, x)_M$.
-  \item The city council votes the proposal.
-  \begin{itemize}
-    \item If the council accepts the proposal, the policy is implemented and the game ends. 
-    \item Otherwise, the reversal policy is implemented.
-  \end{itemize}
-  \item (Reversal Policy) The budget is discounted by a factor $\delta \in (0,1)$, and one councilor is randomly selected to make an offer.
-If the offer is accepted, it is implemented.
-If rejected, the reversal policy stage restarts.\footnote{In section A.1 of the Supplemental Materials, we solve three reversal mechanisms.
-We include the two mechanisms we present here, plus a third mechanism with only political concerns.}
-\end{enumerate}
+councilor's utility depends on the party affiliation of the councilor. If
+councilors reject the mayor's proposal, no public goods are provided ($p=0$).
+Moreover, in equilibrium, we assume that city councilors would prefer to
+receive transfers instead of providing public goods.
 
@@
 equilibrium. This game requires that the strategies follow a Nash equilibrium
-in each subgame. We find the solution using backward induction. In the model
-with infinitely repeated proposals, any strategy can be shown to be a Nash
+in each subgame. We find the solution using backward induction. Since the model
+may have infinitely repeated proposals, any strategy can be shown to be a Nash
 equilibrium. Thus, a natural assumption is to extend the equilibrium concept to
@@
 equilibrium requires that, at each given point of the game, if a politician
-accepts an offer at time $k+1$, she should take the same offer at time $k$
-\citep{rubinstein1982perfect}. Stationarity gives us a method to find a
-proposal that would be accepted at any stage of the game. Hence, we can
-characterize a sequence of offers for each point $k$ in time. For the mayor,
-the optimal offer is at $k=0$, representing a no delay in policy
-implementation. We assume that players have no dominated strategies, even when
-there is insufficient support for the policy.
+accepts an offer at time $k+1$, she should take the same offer at time $k$.
+Stationarity gives us a method to find a proposal that would be accepted at any
+stage of the game. Hence, we can characterize a sequence of offers for each
+point $k$ in time. For the mayor, the optimal offer is at $k=0$, representing a
+no delay in policy implementation. We assume that players have no dominated
+strategies, even when there is insufficient support for the policy.
 
@@
 we use monotone comparative statics to derive the conditions for increasing
-differences \citep{milgrom1994monotone, ashworth2006monotone}. Increasing
-differences mean that higher $N$ leads to higher equilibrium $g$.
+differences \citep{ashworth2006monotone}. Increasing differences mean that
+higher $N$ leads to higher equilibrium $g$.
 
@@
 that reached the Brazilian Supreme Court. The Court favored the city's decision
-and ruled that the size of every local council should correspond to precise
-population thresholds.
-
-Following the ruling of the Supreme Court, in March 2004 the Supreme Electoral
-Court established a series of population cutoffs for all municipal
-legislatures. The Court specified that cities with up to one million residents
-should have between 9 and 21 legislators. The number of seats was allocated as
-follows. Each town starts with nine councilors, then adds one legislator for
-every 47,619 inhabitants until their councils reach 21 members. This threshold
+and ruled that the size of every local council should follow population thresholds.
+
+Following this ruling of the Supreme Court, in March 2004 the Electoral Court
+established a series of population cutoffs for all municipal legislatures. The
+Court specified that cities with up to one million residents should have
+between 9 and 21 legislators. The number of seats was allocated as follows.
+Each city starts with nine councilors, then adds one legislator for every
+47,619 inhabitants until their councils reach 21 members. This threshold
 implies that cities with a population between 571,428 and one million should
-all have the same number of legislators, that is, 21 of them. Conversely,
-cities between one and four million inhabitants should have at least 33
-councilors, and this number increases up to 41 members following the previous
-formula of one additional legislator per 47,619 inhabitants.
+all have 21 legislators. Conversely, cities between one and four million
+inhabitants should have at least 33 councilors, and this number increases up to
+41 members following the previous formula of one additional legislator per
+47,619 inhabitants.
 
@@
 \citep{nicolau2015sistemas}. This poses a major obstacle for small parties to
-reach the electoral quorum, so they often join party coalitions to improve
+reach the electoral quorum, so they often join electoral coalitions to improve
 their chances of winning legislative seats \citep[p. 68]{Ames2001}. In Brazil,
@@
 legislation, and an online survey with 174 former city councilors that served
-during 2005--2008 term to investigate potencial political
-mechanisms.\footnote{We also analyzed 108 structured interviews conducted by
-\citet{lopez2017legisladores} at the Brazilian Economics Planning Institute
-(IPEA) in 2009. The authors asked councilors about their daily work. The
-interviewees confirmed that the mayor's agenda dominates councilors' work and
-it is partisan without strictly following party lines. Municipal politics is
-divided into families or powerful groups that belong to different party
-affiliations. Councilors from other parties gravitate around these groups,
-hence the clear government versus opposition logic.} The municipal data
-contain: 1) the number of councilors who belong to the mayor's pre-electoral
-coalition; 2) the number of appointed bureaucrats; 3) the councilor's gender
-and race; 4) the competitiveness of each city council seat; 5) the proportion
-of laws proposed by the city council that was approved. The variables come from
-the Supreme Electoral Court (TSE), the Senate Legislative Data Service
-(InterLegis), and the Brazilian Bureau of Statistics (IBGE).
+during 2005--2008 term to investigate potencial political mechanisms. The
+municipal data contain: 1) the number of councilors who belong to the mayor's
+pre-electoral coalition; 2) the number of appointed bureaucrats; 3) the
+councilor's gender and race; 4) the competitiveness of each city council seat;
+5) the proportion of laws proposed by the city council that was approved. The
+variables come from the Supreme Electoral Court (TSE), the Senate Legislative
+Data Service (InterLegis), and the Brazilian Bureau of Statistics (IBGE).
 
@@
 
-Together, this evidence provides a clear picture of local-level politics in
-Brazil, from the political mechanism to the municipal welfare consequences of
-the council size ruling. Summary statistics and variable descriptions are
-available in section A.2 of the Supplemental Materials.
-
 # Empirical Strategy
@@
 
-For the first assumption, in section A.3 of the Supplemental Materials
-we assess distribution imbalances running the \citet{McCrary2008} and
-\citet{cattaneo2019simple} tests. The tests show no distribution imbalances.
+In section A.3 of the Supplemental Materials we assess distribution imbalances
+by running the \citet{McCrary2008} and \citet{cattaneo2019simple} tests. The tests
+show no distribution imbalances.
 
@@
 inconsistent estimates when there are differences in the distribution of cases
-around the cutoffs \citep{cattaneo2016interpreting, eggers2018regression,
-bertanha2020regression}. In the dataset, there are twelve discontinuities. At
-each threshold, there is a sharp increase of one councilor, from 9 to 21. When
-running an RDD on these discontinuities, a consistent estimator should fit the
-exact change of one councilor. However, if we pool all the discontinuities
-together with no correction, we find an increase in council size of 1.63
-councilors (see the first estimate in Table \ref{validitycheck}). This
-imbalance occurs because when we combine all the discontinuities, the model
-implies that municipalities below the 47,619 cutoffs (9 to 10 councilors) are
-comparable to changes in towns right above the 571,428 cutoffs (20 to 21
-council members). That is incorrect because the comparison is inconsistent in
-council size, and these municipalities diverge in many other aspects.
-
-To avoid this problem, in section A.5 of the Supplemental Materials we show by
-simulation that adding controls, especially the variables responsible for the
-multiple threshold assignments (in our case, the population in 2003), improves
-the consistency and efficiency of the estimates. Relying on this fact, we add
-five controls to the estimates: Population in 2003; GDP per capita; the number
-of seats in 2000; year; and a dummy for Northeast municipalities. The reason
-for the inclusion of first variable is the multiple threshold assignments. We
-add GDP per capita because wealthier cities tend to have better public
-services. We include number of seats in 2000 because some municipalities could
-have experienced a change provoked by the previous council size, thus
-confounding our estimates. The Northeast dummy was added to control for the
-fact that the Lula administration heavily invested in the region from 2003
-until 2010, improving several development indicators \citep{de2015politica}. We
-included an indicator for year to improve efficiency and control for seasonal
-effects. Moreover, adding controls improves efficiency in RDD
-\citep{calonico2019regression} and also enhances the consistency in the
-multiple thresholds RDD.
+around the cutoffs \citep{cattaneo2016interpreting}. In the dataset, there are
+twelve discontinuities (from 9 to 21 legislators), but if we pool all the
+discontinuities together with no correction, we find an increase in council
+size of 1.63 councilors (see the first estimate in Table \ref{validitycheck}).
+This imbalance occurs because when we combine all the discontinuities, the
+model implies that municipalities below the 47,619 cutoffs (9 to 10 councilors)
+are comparable to changes in towns right above the 571,428 cutoffs (20 to 21
+council members).
+
+In section A.5 of the Supplemental Materials we show by simulation that adding
+controls, especially the variables responsible for the multiple threshold
+assignments (in our case, the population in 2003), improves the consistency and
+efficiency of the estimates. Relying on this fact, we add five controls to the
+estimates: Population in 2003; GDP per capita; the number of seats in 2000;
+year; and a dummy for Northeast municipalities. The reason for the inclusion of
+first variable is the multiple threshold assignments. We add GDP per capita
+because wealthier cities tend to have better public services. We include the
+number of seats in 2000 because some municipalities could have experienced a
+change provoked by the previous council size, thus confounding our estimates.
+The Northeast dummy was added to control for the fact that the Lula
+administration invested heavily in the region from 2003 until 2010, improving
+several development indicators \citep{de2015politica}. We included an indicator
+for year to improve efficiency and control for seasonal effects. Moreover,
+adding controls improves efficiency in RDD \citep{calonico2019regression} and
+also enhances the consistency in the multiple thresholds RDD.
 
@@
 outcomes. As the threshold rule selected by the Brazilian Electoral Court was
-unpredictable, it should not detect any variation before the thresholds were in
+unpredictable, we should not detect any variation before the thresholds were in
 place.
-
-Table \ref{validitycheck} displays the results of the validity checks. We
-present the first-stage regressions at the top of the Table, with and without
-covariates, for both real and placebo cutoffs. At the bottom, we estimate the
-pre-treatment covariate balance. Furthermore, in the Supplemental Materials,
-we run placebo checks for all the models using placebo cutoffs within the real
-ones. The results are available in sections A.6 to A.12 of the Supplemental
-Materials.
 
@@
 
-Note that without the covariates, the first stage overestimates the change in
-the primary treatment and underestimates the effect in the placebo regressions.
-When we add the covariates, the results improve and the point estimates are now
-one for the primary model and zero for the placebo regressions. These are the
-correct values. Moreover, Panel B of Table \ref{validitycheck} shows that the
-pre-treatment covariates remain unchanged around the thresholds. These tests
-reinforce the validity of our research design.
+\newpage
+
+Table \ref{validitycheck} displays the results of the validity checks. We
+present the first-stage regressions at the top of the Table, with and without
+covariates, for both real and placebo cutoffs. At the bottom, we estimate the
+pre-treatment covariate balance. In sections A.6 to A.12 of the Supplemental
+Materials, we run placebo checks for all the models using placebo cutoffs
+within the real ones.
 
@@
 improvements in infant mortality and elementary school enrollment, two vital
-services for welfare. Finally, we also show that our results are robust to
-alternative channels for the influence of legislature size on welfare,
-demonstrating that representation of women and non-whites, competitiveness, and
-legislative productivity fail to receive empirical support in our analyses.
+services for welfare. Finally, we also find that our results are robust to
+alternative channels for the influence of legislature size on welfare.
 
@@
 and the legislative is job appointments, even more so when the city councilors
-are aligned with the mayor. As job appointments are an important factor for
-local governance, we analyze the number of politically appointed bureaucrats,
-career bureaucrats, and councilors' assistants. A higher number of political
-appointees is associated with better service provision in Brazil, as their
-tenure in office depends directly on the survival of the politician supporting
-them \citep{toral2019benefits}. Career bureaucrats pass through a rigorous
-examination, limiting their usefulness as bargaining chips between city
-councilors and mayors. Moreover, career bureaucrats cannot be fired once hired,
-which considerably constrains politicians' pressure on them. Finally, city
-councilors who want to influence policy may employ more staff members and
-assistants to their offices. This could influence policymaking through city
-councilors putting pressure on the bureaucracy, defying our hypothesized
-mechanism. Our theoretical expectations for these regressions are that larger
-council size affects the political alignment of city councilors and the number
-of politically appointed bureaucrats. It should not affect the number of career
-bureaucrats or city council assistants, as it is more valuable to have a
-political appointee that politicians can pressure, working directly with
-voters. Table \ref{tab:bargain} tests the first hypothesis about the nexus
-between city council size and bargaining costs and explores the consequences of
-larger legislatures on the municipal bureaucracy.
+are aligned with the mayor. A higher number of political appointees is
+associated with better service provision in Brazil, as their tenure in office
+depends directly on the survival of the politician supporting them
+\citep{toral2019benefits}. Career bureaucrats pass through a rigorous
+examination and cannot be fired once hired, which considerably constrains
+politicians' pressure on them. Finally, city councilors who want to influence
+policy may employ more staff members and assistants to their offices. This
+could influence policymaking through city councilors putting pressure on the
+bureaucracy, defying our hypothesized mechanism. Our theoretical expectations
+for these regressions are that larger council size affects the political
+alignment of city councilors and the number of politically appointed
+bureaucrats. It should not affect the number of career bureaucrats or city
+council assistants, as it is more valuable to have a political appointee that
+politicians can pressure, working directly with voters. Table \ref{tab:bargain}
+tests the first hypothesis about the nexus between city council size and
+bargaining costs and explores the consequences of larger legislatures on the
+municipal bureaucracy.
 
@@
 coalition. The model hypothesis stated that the probability of electing a city
-councilor who is aligned with the mayor is sufficiently high. However,
-sufficiently high can be ambiguous, and it depends on the intensity of the
-political disagreement and the current legislature size. In any case, 91\%
-chance is a considerably large quantity, and the extra city councilor is going
-to the mayoral coalition nine in every ten legislature size increases. This
-strengthens the political position of the mayor and diminishes bargaining
-costs.\footnote{The effect of city council size on the number of mayor-aligned
-politicians stems from the rounding rule adopted by the proportional
-representation system in Brazil. The rounding rule favors the coalitions with
-more votes. Most of the time, the coalition of the elected mayor is the one
-that receives more votes.} Column (2) demonstrates that adding one councilor
-increases appointed employees by around 104 extra employees per additional city
-councilor. When negotiating with city councilors, these employees are a great
-bargaining chip, and they are also associated with better service provision
-\citep{toral2019benefits}. As expected, legislature size has a null effect on
+councilor who is aligned with the mayor is sufficiently high. Sufficiently high
+can be ambiguous, but in any case, 91\% chance is a considerably large
+quantity. This strengthens the political position of the mayor and diminishes
+bargaining costs.\footnote{The effect of city council size on the number of
+mayor-aligned politicians stems from the rounding rule adopted by the
+proportional representation system in Brazil. The rounding rule favors the
+coalitions with more votes. Most of the time, the coalition of the elected
+mayor is the one that receives more votes.} Column (2) demonstrates that adding
+one councilor increases appointed employees by around 104 extra employees per
+additional city councilor. As expected, legislature size has a null effect on
 the number of career bureaucrats (Column 3) and councilors' staff members
@@
 ran a survey with former city councilors, asking how mayors consolidate their
-coalition support within the city council.\footnote{We provide further
-information about the city council survey in section A.14 of the Supplemental
-Materials.} Second, we collected 346,553 laws approved in 63 municipalities
-within ten thousand inhabitants away from the city council size thresholds. We
-hand-coded 3,466 laws into four categories: Public goods, oversight, education
-and health care-related legislation, and other legislative duties. After
-hand-coding these laws, we used a Supporting Vector Machine (SVM) algorithm to
-classify the remainder laws. From all of the algorithms we tested, SVM achieved
-the highest performance.
+coalition support within the city council. Second, we collected 346,553 laws
+approved in 63 municipalities within ten thousand inhabitants away from the
+city council size thresholds. We hand-coded 3,466 laws into four categories:
+Public goods, oversight, education and health care-related legislation, and
+other legislative duties. After hand-coding these laws, we used a Supporting
+Vector Machine (SVM) algorithm to classify the remainder laws. From all of the
+algorithms we tested, SVM achieved the highest performance.
 
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0]{../figures/strategySupportMayors.pdf}}
+      \centerline{\includegraphics[width=5in,angle=0]{../figures/strategySupportMayors.pdf}}
       \bigskip
@@
     \begin{minipage}{1 \linewidth}
-      \centerline{\includegraphics[width=6in,angle=0,height=6.5in]{../figures/lawsApproved.pdf}}
+      \centerline{\includegraphics[width=5in,angle=0,height=6in]{../figures/lawsApproved.pdf}}
       \bigskip
@@
 
-In Figure \ref{LEGAPPR}, we show that the per capita number of laws related to
-local public goods provision increases in towns that receive the extra
-legislator, vis-à-vis baseline cities that did not get an additional councilor.
-One additional city councilor increased the per capita amount of laws on public
-goods by 15.0 percent. Also, the number of laws that focus on health care and
-education increased by 19.7 percent. Looking specifically into health care and
-education legislation, the proportion of laws discussing public goods increased
-by 15.7 percent, showing that policy proposals by both the mayor and the
-councilors shift toward local and citywide public goods.\footnote{Public goods
-here are not restricted to citywide goods. Any service that benefits citizens,
-regardless of whether they are targeted to citizens or not, is considered
-public goods. For example, building a health clinic in a particular district
-can virtually exclude the citizens that are not living in the neighborhood.
-However, we are still considering these as public goods.}
+In Figure \ref{LEGAPPR}, we show that one additional city councilor increased
+the per capita amount of laws on public goods by 15.0 percent. Also, the number
+of laws that focus on health care and education increased by 19.7 percent.
+Looking specifically into health care and education legislation, the proportion
+of laws discussing public goods increased by 15.7 percent, showing that policy
+proposals by both the mayor and the councilors shift toward local and citywide
+public goods.
 
@@
 
-In this paper, we show that the provision of education and health care in
-Brazil improves with larger legislatures. This is because there is a 91-percent
-chance of electing a government-aligned candidate, largely due to the rule used
-to distribute legislative seats in the country. In the Supplemental Materials,
-we also run regressions in placebo cutoffs between the actual cutoffs, showing
-that our estimates are consistently null when we are indeed supposed to find
-insignificant results.
-
-However, other pathways may also explain the nexus between city council size
-and welfare. First, improvements in representation could change the provision
-of health care and education. Increasing legislature size without changing the
-population makes councilors represent fewer people. For example, in a town with
-50 thousand voters and ten councilors, each councilor represents five thousand
-voters. If the same city has eleven councilors, then each councilor represents
-4.5 thousand voters. This facilitates the representation of minorities, as they
-have to gather fewer votes to elect a city councilor. A minority representative
-can advocate for policies that would improve the welfare of marginalized groups
-\citep{ChattopadhyayDuflu2004, chin2011redistributive, pande2003can}. Diversity
-could also improve governance in municipalities \citep{rugh2011provision}. For
-instance, more women in public offices may shift service provision toward
-welfare expenditure \citep{brollo2016happens, duflo2012women,
-funk2019representative, hernandez2018women}. Therefore, an alternative
-hypothesis to explain the increased service provision is that larger
-legislatures improve female and minority representation in Brazil.\footnote{For
-a description of the barriers faced by non-white politicians in Brazil, see
-\citet{janusz2021race}.}
+Other pathways may also explain the nexus between city council size and
+welfare. First, improvements in representation could change the provision of
+health care and education. Increasing legislature size without changing the
+population makes councilors represent fewer people. This facilitates the
+representation of minorities, as they have to gather fewer votes to elect a
+city councilor. A minority representative can advocate for policies that would
+improve the welfare of marginalized groups \citep{ChattopadhyayDuflu2004,
+chin2011redistributive}. Diversity could also improve governance in
+municipalities \citep{rugh2011provision}. For instance, more women in public
+offices may shift service provision toward welfare expenditure
+\citep{brollo2016happens, duflo2012women, funk2019representative,
+hernandez2018women}. Therefore, an alternative hypothesis to explain the
+increased service provision is that larger legislatures improve female and
+minority representation in Brazil.\footnote{For a description of the barriers
+faced by non-white politicians in Brazil, see \citet{janusz2021race}.}
 
@@
 a pre-electoral coalition, this number increases to two times the number of
-seats \citep{coneglian2008lei}. An election in a small town, with ten
-councilors, may end up with 600 candidates: (30 parties) x (two times the
-number of seats) x (ten seats). Therefore, an alternative explanation for
+seats \citep{coneglian2008lei}. Therefore, an alternative explanation for
 better service provision is that a larger council size increases the
-competitiveness of the election.\footnote{Despite the common assumption that
-competitiveness improve welfare, \citet{boulding2014political} and
+competitiveness of the election.\footnote{\citet{boulding2014political} and
 \citet{gottlieb2019countervailing} show that more competition can increase
-budgetary pressure, lower social policy, lead to bargaining inefficiencies.}
+budgetary pressure and lower social policy, leading to bargaining inefficiencies.}
 
 Finally, both the mayor and the legislature carry out the provision of
-services. Similar to what happens in firms, an extra employee can increase the
-firm productivity frontier by improving cooperation and synergistic outputs
-\citep{alchian1972production, holmstrom1982moral}. A similar argument would
-posit that the increase in council size increases the capability for
-municipalities to provide public services. As legislative productivity
-manifests itself as legislation, an alternative hypothesis to explain the
-increased service provision is that more legislation is being approved by the
-city council.
+services. As in firms, an extra employee can increase the firm productivity
+frontier by improving cooperation and synergistic outputs
+\citep{holmstrom1982moral}. A similar argument would posit that the increase in
+council size increases the capability for municipalities to provide public
+services. As legislative productivity manifests itself as legislation, an
+alternative hypothesis to explain the increased service provision is that more
+legislation is being approved by the city council.
 
@@
 costly \citep{bertholini2017price}. Therefore, an extra ally in the city
-council may help ease the bargaining and increase social welfare.
+council may ease the bargaining process and increase social welfare.
 
@@
 provision of private goods. Indeed, the most successful presidents after 1995
-had to build extensive coalitions and negotiate with several parties to secure
-legislative support \citep{limongi1998bases, raile2011executive}. Despite
-evidence that side payments cemented these coalitions, many social and economic
-policies have since been implemented. For instance, education and health care
-notably improved during the Cardoso and Lula administrations
+had to build extensive coalitions to secure legislative support
+\citep{limongi1998bases, raile2011executive}. Despite evidence that side
+payments cemented these coalitions, many social and economic policies have
+since been implemented. For instance, education and health care notably
+improved during the Cardoso and Lula administrations
 \citep{acemoglu2012nations}. In contrast, presidents who challenged the
@@
 
-Municipalities work similarly in terms of the incentives for
-legislative-executive bargaining. In this case, the stakes are lower and the
+Municipalities work similarly. In this case, the stakes are lower and the
 negotiations involve only one legislative branch. But in a system such as
-Brazil's, with more than thirty-five registered parties, mayors face
-substantial challenges to approve their political agendas. Having extra help in
-the council can tilt the bargaining towards cheaper governing costs, thus
-improving public goods provision.
+Brazil's, with more than thirty-five registered parties
+\citep{samuels2014power}, mayors face substantial challenges to approve their
+political agendas. Additional support in the council reduce governing costs and
+improve public goods provision.
 
@@
 Our findings have implications that extend well beyond Brazil. A general form
-of our argument is that it is easy for a politician to negotiate with members
-of her in-group \citep{abbink2019, alt2018giving}. Specifically, several countries
-have separate executive and legislative powers, such as the federal level of
-presidential systems, state governments, and local city councils. As these
-institutions are influenced by political allegiances, the dynamics we
+of our argument is that it is easier for a politician to negotiate with
+in-group members \citep{abbink2019, alt2018giving}. Specifically, several
+countries have separate executive and legislative powers, such as the federal
+level of presidential systems, state governments, and local city councils. As
+these institutions are influenced by political allegiances, the dynamics we
 expose here may be generalizable. Depending on legislative support, changing

### 2022-05-28 memorandum/memo.Rmd
reduce word count article and memo

@@
 \begin{quote}
-
-We thank Reviewer 1 for these two relevant suggestions. We now cite Gilligan and
-Matsusaka's 2001 article three times in our paper. We mention their article
-twice in our Introduction, first on page 2: ``\textit{On the one hand, enlarged
+We thank Reviewer 1 for these two relevant suggestions. We now cite Gilligan
+and Matsusaka's 2001 article three times in our paper. We mention their article
+twice in our Introduction, first on page 2: ``\textit{Larger
 legislatures may reduce political particularism and increase overall government
-spending, which can lead to more public goods  \citep{gerring2020population,
-GilliganMatsusaka2001, Weingastetal1981}}'', and then on page 5: ``\textit{[The]
-corollary of the "law of $1/n$" is that increasing legislature size promotes
-excessive public spending, regardless of the partisan makeup of the legislature
-\citep{GilliganMatsusaka2001}}''. We cite the article once more in our Theory
-section (page 7): ``\textit{Yet, \citet{GilliganMatsusaka2001} find that in the
-US legislature size is associated primarily with higher spending on
-geographically concentrated benefits, such as education and highways}''.
+spending, which leads to more public goods  \citep{gerring2020population,
+GilliganMatsusaka2001, Weingastetal1981}}'', and then on page 4:
+``\textit{The corollary of the "law of $1/n$" is that increasing legislature
+size promotes excessive public spending, regardless of the partisan makeup of
+the legislature \citep{GilliganMatsusaka2001}}''. We cite the article once more
+in our Theory section (page 6): ``\textit{Yet, \citet{GilliganMatsusaka2001}
+find that in the US legislature size is associated primarily with higher
+spending on geographically concentrated benefits, such as education and
+highways}.''
 
 We now cite Gerring and Veenendaal's book four times. We mention it twice on
-page 2: ``\textit{Legislature size is known to have a significant effect on
-collective action strategies, the bargaining power between state branches,
-government spending, and representation \citep{crain1979cost,
-freire2021legislature, gerring2020population, PrimoSnyder2008, rogers2002free,
-Weingastetal1981}. However, how legislature size impacts social welfare remains
-less understood. On the one hand, enlarged legislatures may reduce political
-particularism and increase overall government spending, which can lead to more
-public goods \citep{gerring2020population, GilliganMatsusaka2001,
-Weingastetal1981}}''. We mention it again on page 4: ``\textit{Following the
-seminal contribution by \citet{Weingastetal1981}, the "law of $1/n$" posits that
-larger legislatures increase the legislative pressure for providing targeted
-public goods to local supporters at the expense of the entire polity
-\citep{freire2021legislature}. This question has become more relevant since
-legislature size has increased consistently over time
-\citep{gerring2020population}}''. Finally, we also cite the book on page 6:
-``\textit{Larger legislatures improve representation as both the election
-thresholds and the ratio of population-per-politician decrease, which facilitate
-the electoral success of ethnic and political minorities
-\citep{allenrepresentation, gerring2020population}}.''
+page 2: ``\textit{Legislature size has a significant effect on collective action
+strategies, the bargaining power between state branches, government spending,
+and representation \citep{crain1979cost, freire2021legislature,
+gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
+However, how legislature size impacts social welfare remains less understood.
+Larger legislatures may reduce political particularism and increase overall
+government spending, which leads to more public goods
+\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}}.'' We
+mention it again on page 4: ``\textit{Following the seminal contribution by
+\citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
+increase the legislative pressure for providing targeted public goods to local
+supporters at the expense of the entire polity \citep{freire2021legislature}.
+This question has become more relevant since legislature size has increased
+consistently over time \citep{gerring2020population}}.'' Finally, we also cite
+the book on page 5: ``\textit{On the one hand, larger legislatures improve
+representation and facilitate the electoral success of ethnic and political
+minorities\citep{allenrepresentation, gerring2020population}}.''
 
@@
 We thank Reviewer 1 for the opportunity to clarify why we have selected these
-two sets of variables. We included an explanation for our decision on page 17:
-"\textit{Our focus is on the impact of legislature size on education and health
-care, which are the two most important public services the municipal government
-should provide to citizens. According to the Brazilian Constitution,
+two sets of variables. We included an explanation for our decision on pages
+14-15: "\textit{Our focus is on the impact of legislature size on education and
+health care, which are the two most important public services the municipal
+government should provide to citizens. According to the Brazilian Constitution,
 municipalities must spend 25\% of their budget on education and 15\% on health
-care. Consequently, the Ministry of Health and the Ministry of Education provide
-readily available, fine-grained data on health care and education at the
-municipal level, which we leverage in this study}."
+care. Consequently, the Ministry of Health and the Ministry of Education
+provide readily available, fine-grained data on health care and education at
+the municipal level, which we leverage in this study}."
 
@@
 We agree with Reviewer 1 that we needed to provide more information about our
-online survey. Therefore, we have detailed our survey procedures in Section A.14
-of the Supplemental Materials (pages 23-24), and we also briefly discuss our
-survey methodology on pages 17 and 22 (footnote 13) of the main article.
-Furthermore, we have rewritten paragraph 2 of Section 6.2 to clarify the
-importance of the survey results in our paper. It now reads as follows:
-``\textit{We assume that city councilors want to extract rents and to get
-reelected. The rents come from continuing in the repeated game, and the
-partisanship discounts that benefit. Figure 2 shows that 65.9 percent of
-councilors mentioned that mayors use job appointments to consolidate their
-coalition support. Moreover, 59.0 percent of the surveyed councilors affirmed
-that mayors use personal favors, such as shifting resources to places where the
-councilors have electoral support, to solidify their governing coalition. This
-provides further evidence that mayors do offer city councilors the benefits they
-demand. In this regard, granting favors works as rent transfers for councilors.
-Job appointments are also convenient for the mayors because patronage in Brazil
-has positive results in terms of welfare \citep{toral2019benefits}.}''
+online survey. Therefore, we have detailed our survey procedures in Section
+A.14 of the Supplemental Materials (pages 23-24), and we also briefly discuss
+our survey methodology on page 14 of the main article. Furthermore, we have
+rewritten the second paragraph of Section 6.2 to clarify the importance of the
+survey results in our paper. It now reads as follows: ``\textit{We assume that
+city councilors want to extract rents and to get reelected. The rents come from
+continuing in the repeated game, and the partisanship discounts that benefit.
+Figure 2 shows that 65.9 percent of councilors mentioned that mayors use job
+appointments to consolidate their coalition support. Moreover, 59.0 percent of
+the surveyed councilors affirmed that mayors use personal favors, such as
+shifting resources to places where the councilors have electoral support, to
+solidify their governing coalition. This provides further evidence that mayors
+do offer city councilors the benefits they demand. In this regard, granting
+favors works as rent transfers for councilors. Job appointments are also
+convenient for the mayors because patronage in Brazil has positive results in
+terms of welfare \citep{toral2019benefits}.}''
 
@@
 demonstrates that the covariates improve consistency in both the main estimates
-and the placebo ones. Table 1 (page 20, reproduced below) shows that without
+and the placebo ones. Table \ref{validitycheck} (page 17, reproduced below) shows that without
 controls, we would overestimate the treatment effects (finding an increase of
@@
   \caption{Research Design Validity Check (reproduction from the main paper)}
+    \label{validitycheck} 
     \scalebox{0.9}{
@@
 To reflect these pieces of information, we have rewritten paragraph five in
-Section 5 of the manuscript to (page 19):
+Section 5 of the manuscript (pages 16-17). It now reads:
 
-``[...] \textit{we add
-five controls to the estimates: Population in 2003; GDP per capita; the number
-of seats in 2000; year; and a dummy for Northeast municipalities. The reason
-for the inclusion of first variable is the multiple threshold assignments. We
-add GDP per capita because wealthier cities tend to have better public
-services. We include number of seats in 2000 because some municipalities could
-have experienced a change provoked by the previous council size, thus
-confounding our estimates. The Northeast dummy was added to control for the
-fact that the Lula administration heavily invested in the region from 2003
-until 2010, improving several development indicators \citep{de2015politica}. We
-included an indicator for year to improve efficiency and control for seasonal
-effects. Moreover, adding controls improves efficiency in RDD
-\citep{calonico2019regression} and also enhances the consistency in the
+``[...] \textit{we add five controls to the estimates: Population in 2003; GDP
+per capita; the number of seats in 2000; year; and a dummy for Northeast
+municipalities. The reason for the inclusion of first variable is the multiple
+threshold assignments. We add GDP per capita because wealthier cities tend to
+have better public services. We include the number of seats in 2000 because
+some municipalities could have experienced a change provoked by the previous
+council size, thus confounding our estimates. The Northeast dummy was added to
+control for the fact that the Lula administration invested heavily in the
+region from 2003 until 2010, improving several development indicators
+\citep{de2015politica}. We included an indicator for year to improve efficiency
+and control for seasonal effects. Moreover, adding controls improves efficiency
+in RDD \citep{calonico2019regression} and also enhances the consistency in the
 multiple thresholds RDD.}''
@@
 We agree with Reviewer 2 that testing the proposed mechanism is an exciting
-project for a follow-up article. In the Discussion section (page 29), we write:
+project for a follow-up article. In the Discussion section (page 26), we write:
 "\textit{Second, future research could evaluate whether additional legislators
@@
 than about government spending. In our section titled "Background on the
-Brazilian Case" (page 14), we clarify why increasing the city council size often
-results in a pro-mayor legislator. We write (page 15): "\textit{Brazil also
+Brazilian Case" (page 12), we clarify why increasing the city council size often
+results in a pro-mayor legislator. We write (page 13): "\textit{Brazil also
 adopts a unique formula to allocate seats, which combines the Hare quota and the
@@
 This poses a major obstacle for small parties to reach the electoral quorum, so
-they often join party coalitions to improve their chances of winning legislative
+they often join electoral coalitions to improve their chances of winning legislative
 seats \citep[68]{Ames2001}. In Brazil, mayors are usually members of the largest
@@
 candidates to side with the mayor before and after the election}." We mention
-that information again on page 22, footnote 12: "\textit{The effect of city
+that information again on page 19, footnote 3: "\textit{The effect of city
 council size on the number of mayor-aligned politicians stems from the rounding
@@
 significant increase in the number of female or non-white legislators, as shown
-in Table 4 (page 27). Finally, we show in the table below that the mayors'
+in Table 4 (page 24). Finally, we show in the table below that the mayors'
 parties are not driving our results. We have ommitted the table from the
@@
 our results might be conditional on the contextual characteristics of our
-study. We have rewritten two paragraphs in the Discussion (page 29) to highligh
-the implication of our results. We write: "\textit{Our findings have
+study. We have rewritten two paragraphs in the Discussion (page 25) to highligh
+the implication of our results. We write: ``\textit{Our findings have
 implications that extend well beyond Brazil. A general form of our argument is
@@
 despite having strong executives and large coalitions
-\citep{pereira2012surprising}.}".
+\citep{pereira2012surprising}.}''
 
-In the next paragraph (page 29), we indicate some of the limitations of our
+In the next paragraph (page 26), we indicate some of the limitations of our
 findings and encourage scholars to conduct further research on the topic. We
-write: "\textit{This paper opens several questions for future analysis. [...]
+write: ``\textit{This paper opens several questions for future analysis. [...]
 Third, scholars might want to investigate whether our findings remain valid
@@
 These questions are crucial for institution design and welfare in developing
-democracies.}"
+democracies.}''
 

### 2022-05-28 article/article.Rmd
final touches

@@
 proposal, which consists of investments in public goods provision, rents for
-personal gains, and a vector of side-transfers for councilors. If mayors fail
+personal gains, and a vector of side transfers for councilors. If mayors fail
 to secure majoritarian support from councilors, a reversal stage occurs, in
 which the decision leaves the mayor's office and councilors propose the public
-investments. In this bargaining process, costs come from the side-transfers
+investments. In this bargaining process, costs come from the side transfers
 required to secure a majority among councilors. We show that in a model without
@@
 thousand inhabitants away from the cutoffs. While all municipalities mention
-public goods in their legislation, those with larger city councils have 15
+public goods in their legislation, those with larger city councils had 15
 percent more proposals about public service delivery.
@@
 of multilateral bargaining started with \citet{baron1989bargaining}, and
-scholars have recently analysed how endogenous recognition power, the size of
+scholars have recently analyzed how endogenous recognition power, the size of
 the required majority, and partisanship impact these results
@@
 calvert2005legislative, choate2019partisan}. Here we include the mayor's first
-move and political partisanship to Baron and Ferejohn's
+move advantage and political partisanship to Baron and Ferejohn
 (\citeyear{baron1989bargaining}) and investigate the often-overlooked effect of
@@
 Finally, this paper also contributes to the literature on the causes and effects of
-legislature sizes. While most papers on legislature size analyse the trade-off
+legislature sizes. While most papers on legislature size analyze the trade-off
 between representation and efficiency \citep{frederick2008people,
@@
 \citep{allenrepresentation, gerring2020population}. On the other hand, better
-representation is often countered by the decline in efficiency in larger
+representation is often countered by the decline in efficiency in bigger
 legislatures \citep{Weingastetal1981}. In large councils, it is harder for
@@
 The city council votes the mayor's proposal and the proposal is implemented if
-most councilors accept it. Otherwise, a reversal policy takes place. Reversal
-policy in this context means that the mayor's proposal failed to secure the
-majority of council votes. The decision process then leaves the mayor's office
-and is transferred to the council. The types of reversal policies are crucial
-for our argument, as they change the relative strength of the council when
-legislators bargain with the mayor. Here we investigate two types of reversal
-policies: A baseline reversal with no parties and a hybrid mechanism with
-partisan and non-partisan concerns. The differences between these two
-mechanisms are that the non-partisan councilors only care about rents, while
-partisan councilors care about both rents and policy.
+councilors accept it. Otherwise, a reversal policy takes place. Reversal policy
+in this context means that the mayor's proposal failed to secure the majority
+of council votes. The decision process then leaves the mayor's office and is
+transferred to the council. The types of reversal policies are crucial for our
+argument, as they change the relative strength of the council when legislators
+bargain with the mayor. Here we investigate two types of reversal policies: A
+baseline reversal with no parties and a hybrid mechanism with partisan and
+non-partisan concerns. The differences between these two mechanisms are that
+the non-partisan councilors only care about rents, while partisan councilors
+care about both rents and policy.
 
@@
 minimum number of members that must be convinced to implement the policy, is
-equal to half of the selectorate ($N/2$). City councilors are motivated by
-policy concerns $p$ and transfers received from the mayor or the councilor
-nominated as the proposer \textbf{x}. We leave the definition of these
-transfers open, as this allows us to analyze how mayors combine transfers with
-other incentives to pressure city councilors. Examples of transfers are
-granting electoral favors, funding clientelistic brokers, spending in areas in
-which the councilor has political or personal interests, or providing portfolio
-(municipal offices) and public jobs within the bureaucracy. The use
-of transfers to influence the councilors' choices generate a bargaining cost of
-$C_G$. Bargaining costs vary according to the reversal mechanism and the size
-of the legislature.
-
-Finally, after learning the bargaining costs, the mayor provides a level of
+equal to half of the selectorate. City councilors are motivated by policy
+concerns $p$ and transfers \textbf{x} received from the mayor or the councilor
+nominated as the proposer. We leave the definition of these transfers open, as
+this allows us to analyze how mayors combine transfers with other incentives to
+pressure city councilors. Examples of transfers are granting electoral favors,
+funding clientelistic brokers, spending in areas in which the councilor has
+political or personal interests, or providing portfolio (municipal offices) and
+public jobs within the bureaucracy. The use of transfers to influence the
+councilors' choices generate a bargaining cost of $C_G$. Bargaining costs vary
+according to the reversal mechanism and the size of the legislature.
+
+Finally, after learning the bargaining costs, the mayor offers a level of
 public goods provision $g$ and pockets rents $r$. Public goods provision helps
 the mayor to get reelected. Rents are for the mayor's direct consumption and do
-not contribute to her electoral success. This makes the mayor's expected utility a
-sum of the gains from rents and the benefits from reelection. Both the
-utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are
-concave functions, meaning that more rents or public goods increase the utility
-at a decreasing rate. The probability of reelection is multiplied by the
-benefit from holding office $B_M > 0$. This benefit captures the tangible and
+not contribute to her electoral success. This makes the mayor's expected
+utility a sum of the gains from rents and the benefits from reelection ($B_M$).
+Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$
+are concave functions, meaning that more rents or public goods increase the
+utility at a decreasing rate. The probability of reelection is multiplied by
+the benefit from holding office. This benefit captures the tangible and
 intangible gains that the mayor receives from holding the public office. We
@@
 
-We now consider a situation that combines both partisan and non-partisan
+We then consider a situation that combines both partisan and non-partisan
 legislature concerns. Each councilor has a party affiliation. Party
 affiliations are mutually exclusive, and if a city councilor is aligned with
-the mayor's party, then she belongs to the government coalition $G \subset \{1,
+the mayor's party, then he belongs to the government coalition $G \subset \{1,
 2, \cdots, N \}$. Otherwise, the city councilor belongs to the opposition $O =
@@
 councilor's utility depends on the party affiliation of the councilor. If
-councilors reject the mayor's proposal, no public goods are provided ($p=0$).
-Moreover, in equilibrium, we assume that city councilors would prefer to
-receive transfers instead of providing public goods.
-
-The solution concept we use in this model is the subgame perfect Nash
-equilibrium. This game requires that the strategies follow a Nash equilibrium
-in each subgame. We find the solution using backward induction. Since the model
-may have infinitely repeated proposals, any strategy can be shown to be a Nash
-equilibrium. Thus, a natural assumption is to extend the equilibrium concept to
-require the equilibrium to be stationary. A stationary subgame perfect
-equilibrium requires that, at each given point of the game, if a politician
-accepts an offer at time $k+1$, she should take the same offer at time $k$.
-Stationarity gives us a method to find a proposal that would be accepted at any
-stage of the game. Hence, we can characterize a sequence of offers for each
-point $k$ in time. For the mayor, the optimal offer is at $k=0$, representing a
-no delay in policy implementation. We assume that players have no dominated
-strategies, even when there is insufficient support for the policy.
+councilors reject the mayor's proposal, there are no partisan alignment
+benefits ($p=0$). Moreover, in equilibrium, we assume that city councilors
+would prefer to receive transfers instead of providing public goods.
+
+The solution concept we use in this model is the stationary subgame perfect
+Nash equilibrium. This solution concept requires that the strategies follow a
+Nash equilibrium in each subgame. Since the model may have infinitely repeated
+proposals, any strategy can be shown to be a Nash equilibrium. Thus, we solve
+for a stationary equilibrium. A stationary subgame perfect equilibrium requires
+that, at each given point of the game, if a politician accepts an offer at time
+$k+1$, he should take the same offer at time $k$. Stationarity gives us a
+method to find a proposal that would be accepted at any stage of the game.
+Hence, we can characterize a sequence of offers for each point $k$ in time. For
+the mayor, the optimal offer is at $k=0$, representing a no delay in policy
+implementation. We assume that councilors play no dominated strategies, even
+when there is insufficient support for the policy.
 
@@
 
-The optimal level of public goods provision equates the marginal gains accrued
-from rents with the marginal benefits from reelection.
-
 \begin{proposition}\label{prop1}
@@
 intuition involves finding what happens to the mayor's marginal utility when we
-increase both $g$ and $N$. As $N$ increases discretely on a complete lattice,
-we use monotone comparative statics to derive the conditions for increasing
-differences \citep{ashworth2006monotone}. Increasing differences mean that
-higher $N$ leads to higher equilibrium $g$.
+increase both $g$ and $N$. As $N$ increases discretely, we use monotone
+comparative statics to derive the conditions for increasing differences
+\citep{ashworth2006monotone}. Increasing differences mean that higher $N$ leads
+to higher equilibrium $g$.
 
@@
 \[
-x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left[ 1 - \dfrac{1}{N} \right]\left[\dfrac{1}{2} x_i \right]
+x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left[ 1 - \dfrac{1}{N} \right]\dfrac{x_i}{2}  
 \]
@@
 We place the offer on the left-hand side. There are two components on the
-right-hand side. The first is the amount that the councilor $i$ gets when she
-is the proposer. It is equal to the chance that she is recognized as the
-proposer times the budget in the next round minus the offers she makes to
-convince half of the councilors. The second part represents the gains if the
-councilor rejects the current offer but still gets an offer in the following
-round. It is equal to the chance that she is not recognized as the proposer
-times the chance that she receives a transfer times the transfer amount. Note
-that the offer the councilor makes as the proposer is the same as the offer she
-wants to receive. This is because city councilors are exchangeable. The
-solution is symmetric for all councilors receiving an offer (this means that,
-without loss of generality, we could have dropped the $i$ in the solution).
-After some algebra, the offer $x_i$ must be greater than or equal to:
+right-hand side. The first is the amount that councilor $i$ gets when he is the
+proposer. It is the chance that he is recognized as the proposer times the
+budget in the next round minus the offers he makes to convince half of the
+councilors. The second part represents the gains if the councilor rejects the
+current offer but still gets an offer in the following round. It is equal to
+the chance that he is not recognized as the proposer times the chance that he
+receives a transfer times the transfer's amount. Note that the offer the
+councilor makes as the proposer is the same as the offer he wants to receive.
+This is because city councilors are exchangeable. The solution is symmetric for
+all councilors receiving an offer (this means that, without loss of generality,
+we could have dropped $i$ in the solution). After some algebra, the offer $x_i$
+must be greater than or equal to:
 
@@
 
-The proposer always offers the minimum required to get the proposal approved.
-In this case, the offer at any given stage $k$ is going to be equal to
+The proposer always offers the minimum required to get the offer approved.
+In this case, the proposal at any given stage $k$ is going to be equal to
 $\underline{x}(k, N)$.
 
-Proceeding backwards, at the mayor's proposal stage $k=0$ the mayor is going to
+Proceeding backwards, at the mayor's proposal stage $k=0$ she is going to
 offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the
@@
 
-An opposition politician, on the other hand, favors the mayor's offer if, and
-only if:
+An opposition politician, in contrast, favors the mayor's offer if, and only
+if:
 
@@
 the bargaining costs depend on what the mayor offers for councilors in her
-coalition versus what she provides to members of the opposition. As the ex-ante
-chance of an opposition member being elected is equal to $1-\gamma$, after
-taking the weighted averages these costs become:
+coalition versus what she provides to members of the opposition. As the chance
+of electing a government member is equal to $\gamma$, after taking the weighted
+averages, these costs become:
 
@@
 policy $p$ and the size of the legislature $N$. This means that intensive
-partisanship and larger legislatures make it easier to satisfy the electoral
+partisanship and larger legislatures make it easier to satisfy this electoral
 threshold.
@@
 First, they should discuss and vote on legislation put forward by the mayors or
-by their peers. Second, they oversee the public budget and sanction mayors who
+their peers. Second, they oversee the public budget and sanction mayors who
 do not comply with fiscal legislation. Councilors and mayors also provide an
@@
 
-\newpage
-
 Table \ref{validitycheck} displays the results of the validity checks. We

### 2022-05-28 memorandum/memo.Rmd
final touches

@@
 Below we discuss in more detail these changes and the several others we have
-made to the manuscript in response to comments from the Editors and Reviewers.
-We thank the Editors again for the opportunity to revise the manuscript, and
-the Reviewers for their extremely helpful comments.
+made to the manuscript in response to comments from the Editors, the Reviewers,
+and the Editorial Office. We thank the Editors again for the opportunity to
+revise the manuscript, and the Reviewers for their extremely helpful comments.
 
@@
 We thank Reviewer 1 for the opportunity to clarify why we have selected these
-two sets of variables. We included an explanation for our decision on pages
-14-15: "\textit{Our focus is on the impact of legislature size on education and
-health care, which are the two most important public services the municipal
-government should provide to citizens. According to the Brazilian Constitution,
+two sets of variables. We included an explanation for our decision on page 14:
+"\textit{Our focus is on the impact of legislature size on education and health
+care, which are the two most important public services the municipal government
+should provide to citizens. According to the Brazilian Constitution,
 municipalities must spend 25\% of their budget on education and 15\% on health
@@
 consistency of our empirical results. In Section A.5 of the Appendix, we use
-simulations to show that the inclusion of covariates enhances the consistency of
-our RDD estimates. The simulations indicate that the controls improve
+simulations to show that the inclusion of covariates enhances the consistency
+of our RDD estimates. The simulations indicate that the controls improve
 consistency even if we assume different distributions for the running variables
@@
 demonstrates that the covariates improve consistency in both the main estimates
-and the placebo ones. Table \ref{validitycheck} (page 17, reproduced below) shows that without
-controls, we would overestimate the treatment effects (finding an increase of
-1.63 legislators instead of an increase of exactly one legislator), and
-underestimate the placebo treatment effects (finding a significant decrease of
-0.31 legislators where there was supposed to be no effects in legislature size).
-This substantial improvement is attributed to the addition of control variables,
-which make the subpopulations in each threshold more comparable across all the
-thresholds. Thus, we avoid spurious comparisons between cases on the left
-(right) of one threshold and those on the right (left) of a different threshold.
+and the placebo ones. Table \ref{validitycheck} (page 17, reproduced below)
+shows that without controls, we would overestimate the treatment effects
+(finding an increase of 1.63 legislators instead of an increase of exactly one
+legislator), and underestimate the placebo treatment effects (finding a
+significant decrease of 0.31 legislators where there was supposed to be no
+effects in legislature size). This substantial improvement is attributed to the
+addition of control variables, which make the subpopulations in each threshold
+more comparable across all the thresholds. Thus, we avoid spurious comparisons
+between cases on the left (right) of one threshold and those on the right
+(left) of a different threshold.
 
@@
 To reflect these pieces of information, we have rewritten paragraph five in
-Section 5 of the manuscript (pages 16-17). It now reads:
+Section 5 of the manuscript (page 16). It now reads:
 

### 2022-05-28 article/article.Rmd
pesky typos fixed

@@
 politics to explain how city council size impacts local public goods provision.
-We incorporate partisanship and mayoral first-move advantage to a
-\citet{baron1989bargaining} bargaining model. Mayors make the initial policy
-proposal, which consists of investments in public goods provision, rents for
-personal gains, and a vector of side transfers for councilors. If mayors fail
-to secure majoritarian support from councilors, a reversal stage occurs, in
-which the decision leaves the mayor's office and councilors propose the public
-investments. In this bargaining process, costs come from the side transfers
-required to secure a majority among councilors. We show that in a model without
-partisan concerns, bargaining costs always increase with larger city councils,
-which in turn lower public goods provision and rents. However, partisanship
-decreases bargaining costs when the chances of electing government-aligned
-councilors are sufficiently high. Lower bargaining costs release funds for
-mayors to invest in public goods. In this case, a larger city council may add
-more members to the government coalition, thus reducing the mayor's bargaining
-costs and increasing the equilibrium public goods provision.
+We incorporate partisanship and mayoral first-mover advantage to
+Baron and Ferejohn's (\citeyear{baron1989bargaining}) bargaining
+model. Mayors make the initial policy proposal, which consists of investments
+in public goods provision, rents for personal gains, and a vector of side
+transfers for councilors. If mayors fail to secure majoritarian support from
+councilors, a reversal stage occurs, in which the decision leaves the mayor's
+office and councilors propose the public investments. In this bargaining
+process, costs come from the side transfers required to secure a majority among
+councilors. We show that in a model without partisan concerns, bargaining costs
+always increase with larger city councils, which in turn lower public goods
+provision and rents. However, partisanship decreases bargaining costs when the
+chances of electing government-aligned councilors are sufficiently high. Lower
+bargaining costs release funds for mayors to invest in public goods. In this
+case, a larger city council may add more members to the government coalition,
+thus reducing the mayor's bargaining costs and increasing the equilibrium
+public goods provision.
 
@@
 \citep{agranov2020persistence, baranski2020determinants,
-calvert2005legislative, choate2019partisan}. Here we include the mayor's first
-move advantage and political partisanship to Baron and Ferejohn
-(\citeyear{baron1989bargaining}) and investigate the often-overlooked effect of
-legislature size on bargaining equilibrium strategies.
+calvert2005legislative, choate2019partisan}. Here we include the mayor's
+first-mover advantage and political partisanship to Baron and Ferejohn's
+(\citeyear{baron1989bargaining}) model and investigate the often-overlooked
+effect of legislature size on bargaining equilibrium strategies.
 

### 2022-05-28 memorandum/memo.Rmd
fix spacing memo

@@
 representation and facilitate the electoral success of ethnic and political
-minorities\citep{allenrepresentation, gerring2020population}}.''
+minorities \citep{allenrepresentation, gerring2020population}}.''
 

### 2022-07-02 appendix/appendix.Rmd
add author info, socarxiv links

@@
 author: 
-date: \today
+  - Umberto Mignozzetti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
+date: May 28, 2022
 fontfamily: libertine
@@
 ```
+
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+
+[^gabriel]: Associate Professor, Department of Public Policy and International Relations, State University of São Paulo, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
 

### 2022-07-02 article/article.Rmd
add author info, socarxiv links

@@
 author: 
-date: \today
+  - Umberto Mignozzetti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
+date: May 28, 2022
+thanks: We would like to thank Victor Araujo, Eric Arias, Mark Bennister, Taylor Boas, Natalia Bueno, Nick Cowen, Andrea Freitas, Saad Gulzar, Shoaib Jillani, James Mahon, Lucas Mingardi, Lucas Novaes, Ingrid Oliveira, Catarina Roman, Nelson Ruiz, David Skarbek, Mike Slaven, Denis Stukal, the AJPS Editorial Team, and three anonymous reviewers for their valuable comments.
+We also thank the participants of seminars and conferences at the CEPESP-FGV, CUNY, INSPER, IPSA, IR-FGV, LACEA, LASA, Lincoln, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.
+All remaining errors are the sole responsibility of the authors.
+The authors thank FAPESP for their financial support, grant number 2017/07290-5.
+Replication materials are available at <https://github.com/umbertomig/legislature-size-welfare>.
 abstract: "How does legislature size impact public service provision?

### 2022-07-02 article/article.Rmd
small edits

@@
 date: May 28, 2022
-thanks: We would like to thank Victor Araujo, Eric Arias, Mark Bennister, Taylor Boas, Natalia Bueno, Nick Cowen, Andrea Freitas, Saad Gulzar, Shoaib Jillani, James Mahon, Lucas Mingardi, Lucas Novaes, Ingrid Oliveira, Catarina Roman, Nelson Ruiz, David Skarbek, Mike Slaven, Denis Stukal, the AJPS Editorial Team, and three anonymous reviewers for their valuable comments.
+thanks: We would like to thank Victor Araujo, Eric Arias, Mark Bennister, Taylor Boas, Natalia Bueno, Nick Cowen, Andrea Freitas, Saad Gulzar, Shoaib Jillani, Fernando Limongi, James Mahon, Lucas Mingardi, Lucas Novaes, Ingrid Oliveira, Nelson Ruiz, David Skarbek, Mike Slaven, Denis Stukal, the AJPS Editorial Team, and three anonymous reviewers for their valuable comments.
 We also thank the participants of seminars and conferences at the CEPESP-FGV, CUNY, INSPER, IPSA, IR-FGV, LACEA, LASA, Lincoln, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.
-All remaining errors are the sole responsibility of the authors.
-The authors thank FAPESP for their financial support, grant number 2017/07290-5.
+We gratefully acknolwedge funding from the São Paulo Research Foundation (FAPESP 2017/07290-5).
 Replication materials are available at <https://github.com/umbertomig/legislature-size-welfare>.

### 2022-08-26 appendix/appendix.Rmd
small updates

--- 2022-05-17 appendix/appendix.Rmd
@@
 author: 
-date: \today
+  - Umberto Mignozzetti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
+date: August 26, 2022
 fontfamily: libertine
@@
 ```
+
+[^umberto]: Assistant Teaching Professor, Department of Political Science and Computational Social Sciences Program, University of California, San Diego, SSB 393, 2997 Thurgood Marshall Ln, La Jolla, CA 92037, United States of America, <umbertomig@ucsd.edu>, <http://umbertomig.com>.
+Corresponding author.
+
+[^gabriel]: Associate Professor, Department of Public Policy and International Relations, São Paulo State University, Av.
+Eufrásia Monteiro Petráglia 900, Franca, SP 14409-160, Brazil, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, Brayford Pool, Lincoln, LN6 7TS, United Kingdom, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
 
@@
 \item \textbf{Number of Seats 2004}: Number of city councilors in 2004 according to the Electoral Court (source: TSE).
-\item \textbf{Infant Mortality 2005--2008}: Number of children who died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS)
-\item \textbf{Postneonatal Mortality 2005--2008}: Number of children alive for at least 28 days who died before reaching one year of age, divided by the total number of children who lived for 28 days, multiplied by 1,000 (source: DataSUS)
+\item \textbf{Infant Mortality 2005--2008}: Number of children who died before reaching one year of age, divided by the number of children born alive, multiplied by 1,000 (source: DataSUS).
+\item \textbf{Postneonatal Mortality 2005--2008}: Number of children alive for at least 28 days who died before reaching one year of age, divided by the total number of children who lived for 28 days, multiplied by 1,000 (source: DataSUS).
 \item \textbf{Enrollment Elementary School 2005--2008}: Number of children enrolled in elementary schools, averaged by classroom size (K--4) (source: INEP).
@@
 INEP reweights the estimators to avoid school and classroom specific distortions (source: INEP, years: 2005, 2007).
-\item \textbf{Size of Mayoral Pre-Electoral Coalition 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE)
-\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of bureaucrats of the direct administration who were appointed to jobs in the municipality (source: IBGE, years: 2005, 2006, and 2008)
-\item \textbf{Number of Females Elected 2004}: Number of females elected to the city council (source: TSE)
+\item \textbf{Size of Mayoral Pre-Electoral Coalition 2004}: Number of elected councilors in the mayoral pre-electoral coalition (source: TSE).
+\item \textbf{Number of Appointed Bureaucrats 2005--2008}: Number of municipal bureaucrats of the direct administration who were appointed to jobs (source: IBGE, years: 2005, 2006, and 2008).
+\item \textbf{Number of Career Bureaucrats 2005--2008}: Number of municipal bureaucrats of the direct administration hired via admission tests (source: IBGE, years: 2005, 2006, and 2008).
+\item \textbf{Number of Councilor Assistants 2005}: Number of city councilor assistants (source: InterLegis).
+\item \textbf{Number of Females Elected 2004}: Number of females elected to the city council (source: TSE).
 \item \textbf{Number of Non-Whites Elected 2004}: Number of non-whites elected to the city council.
 We collect these data for municipalities less than 10,000 inhabitants away from the cutoffs (source: own compilation based on the TSE candidate pictures).
-\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the size of the city council (source: TSE)
-\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis)
+\item \textbf{Competition per Seat 2004}: Number of people running for city councilor divided by the size of the city council (source: TSE).
+\item \textbf{Proportion Approved Legislation 2005}: Number of approved legislation in 2005 divided by the number of proposed legislation (source: InterLegis).
 \end{itemize}
@@
 GDP Census 2000 & 5,474 & 0.13 & 0.46 & 0.00 & 13.57 \\ 
-Proportion of Poverty Census 2000 & 5,474 & 46.58 & 22.82 & 2.89 & 93.02 \\
+Proportion of Poverty Census 2000 & 32,845 & 46.58 & 22.82 & 2.89 & 93.02 \\ 
 Number of Seats 2004 & 5,527 & 9.22 & 0.94 & 9 & 21 \\
 & \multicolumn{5}{c}{\textbf{Health Care Outcomes}} \\ \cline{2-6}
-Infant Mortality 2005-2008 & 13,328 & 20.64 & 13.45 & 1.28 & 209.30 \\
+Infant Mortality 2005-2008 & 13,329 & 20.64 & 13.45 & 1.28 & 209.30 \\ 
 Postneonatal Mortality 2005-2008 & 6,113 & 9.29 & 8.64 & 0.59 & 200.00 \\
@@
 Enrollment Elementary School 2005-2008 & 10,842 & 20.62 & 5.32 & 1.00 & 57.80 \\ 
-Quality of Elementary School 2005-2008 & 9,266 & 3.73 & 0.94 & 0.70 & 8.10 \\
+Quality of Elementary School Index 2005-2008 & 9,267 & 3.73 & 0.94 & 0.70 & 8.10 \\
 & \multicolumn{5}{c}{\textbf{Bargaining, Coalition, and Public Employment}} \\ \cline{2-6}
-Mayoral Pre-electoral coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0.00 & 17.00 \\
-Number of Appointed Bureaucrats 2005-2008 & 16,563 & 67.77 & 126.68 & 0 & 2,894 \\
+Mayoral Pre-electoral Coalition Size 2004 & 5,522 & 4.86 & 1.71 & 0 & 17 \\ 
+Number of Appointed Bureaucrats 2005-2008 & 16,564 & 67.78 & 126.68 & 0 & 2,894 \\ 
+Num. Career Bureaucrats & 16,558 & 436.13 & 698.17 & 0 & 11,633 \\ 
+Num. Councilor Assistants & 5,523 & 4.63 & 8.55 & 0 & 213 \\
 & \multicolumn{5}{c}{\textbf{Representation and Competition}} \\ \cline{2-6}
@@
 Competition per Seat 2004 & 5,527 & 6.27 & 3.82 & 1.00 & 25.83 \\ 
-Proportion Approved Legislation 2005 & 3,693 & 0.83 & 0.28 & 0.00 & 1.00 \\
+Proportion Approved Legislation 2005 & 3,694 & 0.83 & 0.28 & 0.00 & 1.00 \\
 & \multicolumn{5}{c}{\textbf{Legislation Approved Data}} \\ \cline{2-6}
@@
 Legislation -- Oversight & 346,553 & 0.03 & 0.18 & 0 & 1 \\ 
+Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\ 
 Legislation -- Education and Health & 346,553 & 0.11 & 0.31 & 0 & 1 \\
-Legislation -- Others & 346,553 & 0.17 & 0.38 & 0 & 1 \\
 & \multicolumn{5}{c}{\textbf{Survey -- Strategy to Consolidate Coalition Support}} \\ \cline{2-6}
@@
  & \multicolumn{1}{c}{\small{Num. Female}} &
- \multicolumn{1}{c}{\small{Num. Non-white}} &
+ \multicolumn{1}{c}{\small{Num. Non-White}} &
   \multicolumn{1}{c}{\small{Candidates}} &
@@
   & (0.27) &  & (0.48) & (0.06) \\ 
- N Left & 4620 &  & 4621 & 2990 \\
+ N Left & 4620 &  & 4621 & 2991 \\ 
 N Right & 906 &  & 906 & 703 \\ 
@@
 Eff N Right & 298 &  & 347 & 229 \\ 
-BW Loc Poly & 4.874 &  & 6.104 & 5.583 \\
-BW Bias & 8.789 &  & 10.312 & 8.89 \\
+BW Loc Poly & 4.874 &  & 6.104 & 5.585 \\ 
+BW Bias & 8.789 &  & 10.312 & 8.893 \\
 \midrule
@@
  \multicolumn{1}{c}{\small{Bureaucrats}} &  & \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.13 & -0.58 & & \\
-  & (0.33) & (17.14)  & & \\
- N Left & 4618 & 13854  & & \\
-N Right & 904 & 2709  & & \\
-Eff N Left & 654 & 1345  & & \\
-Eff N Right & 394 & 915  & & \\
-BW Loc Poly & 6.813 & 5.127  & & \\
-BW Bias & 10.501 & 8.194  & & \\
+ LATE & 0.13 & -0.58 & 92.83 & -2.16 \\ 
+  & (0.33) & (17.15) & (63.66) & (1.80) \\ 
+ N Left & 4618 & 13855 & 13850 & 4618 \\ 
+N Right & 904 & 2709 & 2708 & 905 \\ 
+Eff N Left & 654 & 1345 & 2268 & 598 \\ 
+Eff N Right & 394 & 915 & 1277 & 364 \\ 
+BW Loc Poly & 6.813 & 5.126 & 7.672 & 6.323 \\ 
+BW Bias & 10.501 & 8.194 & 13.251 & 11.031 \\
 \bottomrule
@@
 
-## Mayor's Characteristics, Revenues, and Transfers from the Central Government
+## Mayors' Characteristics, Revenues, and Transfers from the Central Government
 
@@
   \hline \\[-1.8ex]
-  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\
+  LATE & 0.07 & -0.06 & -0.10 & 0.06 \\ 
   & (0.08) & (0.13) & (0.10) & (0.14) \\ 
@@
 N Right & 335 & 335 & 343 & 343 \\ 
-  Eff N Left & 299 & 226 & 192 & 231 \\
-  Eff N Right & 184 & 154 & 141 & 159 \\
-  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\
-  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\
+Eff N Left & 300 & 232 & 195 & 233 \\ 
+Eff N Right & 184 & 155 & 145 & 159 \\ 
+BW Loc Poly & 11.772 & 9.832 & 8.611 & 9.681 \\ 
+BW Bias & 17.081 & 15.8 & 13.399 & 14.758 \\
   \hline \\[-1.8ex]
@@
   \hline \\[-1.8ex]
-  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\
+  LATE & 0.03 & -0.02 & 0.17$^{*}$ & 0.06 \\ 
   & (0.04) & (0.03) & (0.10) & (0.04) \\ 
@@
 N Right & 1029 & 1029 & 1028 & 998 \\ 
-  Eff N Left & 804 & 258 & 349 & 626 \\
-  Eff N Right & 516 & 273 & 333 & 442 \\
-  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\
-  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\
+Eff N Left & 858 & 282 & 409 & 735 \\ 
+Eff N Right & 540 & 294 & 357 & 481 \\ 
+BW Loc Poly & 11.254 & 4.922 & 6.496 & 10.248 \\ 
+BW Bias & 16.599 & 8.382 & 11.603 & 15.583 \\
   \hline \\[-1.8ex]
@@
 \centering
-\caption{Accuracy of SVM Classifier (tested in 20\% of the data)}
+\caption{Accuracy of SVM Classifier (Tested in 20\% of the Data)}
 \label{accurClassif}
@@
 \centering
-\caption{Proportions for each bin used in the weighting process}
+\caption{Proportions for Each Bin Used in the Weighting Process}
 \label{tabweight}

### 2022-08-26 article/article.Rmd
small updates

--- 2022-05-28 article/article.Rmd
@@
 author: 
-date: \today
+  - Umberto Mignozzetti[^umberto]
+  - Gabriel Cepaluni[^gabriel]
+  - Danilo Freire[^danilo]
+date: August 26, 2022
+thanks: "We would like to thank Victor Araujo, Eric Arias, Mark Bennister, Taylor Boas, Natalia Bueno, Nick Cowen, Dominik Duell, Andrea Freitas, Saad Gulzar, Cathy Hafer, Daniel Hidalgo, Fernando Limongi, James Mahon, Lucas Novaes, Adam Przeworski, Catarina Roman, Howard Rosenthal, Nelson Ruiz, Renard Sexton, David Skarbek, Mike Slaven, Denis Stukal, the AJPS Editorial Team, and three anonymous reviewers for their valuable comments.
+We also thank the participants of seminars and conferences at the CEPESP-FGV, CUNY, INSPER, IPSA, LACEA, LASA, Lincoln, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.
+The data and materials required to verify the computational reproducibility of the results, procedures and analyses in this article are available at <https://github.com/umbertomig/legislature-size-welfare>.
+We gratefully acknolwedge funding from the São Paulo Research Foundation (FAPESP 2017/07290-5)."
 abstract: "How does legislature size impact public service provision?
@@
 This paper has implications for the design of representative institutions."
-abstractspacing: double
+abstractspacing: onehalf
 keywords: legislature size; legislative bargaining; local public goods provision; regression discontinuity design; Brazil
@@
 
+[^umberto]: Assistant Teaching Professor, Department of Political Science and Computational Social Sciences Program, University of California, San Diego, SSB 393, 2997 Thurgood Marshall Ln, La Jolla, CA 92037, United States of America, <umbertomig@ucsd.edu>, <http://umbertomig.com>.
+Corresponding author.
+
+[^gabriel]: Associate Professor, Department of Public Policy and International Relations, São Paulo State University, Av.
+Eufrásia Monteiro Petráglia 900, Franca, SP 14409-160, Brazil, <gabi.cepal@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, Brayford Pool, Lincoln, LN6 7TS, United Kingdom, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+
 \newpage
@@
     \hdashline \\[-1.8ex]
- N Left & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{4621} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{906} \\ 
-Eff N Left & \multicolumn{1}{c}{199} & \multicolumn{1}{c}{638} & \multicolumn{1}{c}{49} & \multicolumn{1}{c}{886} \\ 
-Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{385} & \multicolumn{1}{c}{51} & \multicolumn{1}{c}{477} \\ 
-BW Loc Poly & 8.717 & 6.700 & 3.008 & 8.629 \\ 
-BW Bias & 13.620 & 12.114 & 5.008 & 13.466 \\ 
+ N Left & 5184 & 4621 & 5184 & 4621 \\ 
+N Right & 343 & 906 & 343 & 906 \\ 
+Eff N Left & 201 & 645 & 51 & 935 \\ 
+Eff N Right & 145 & 388 & 55 & 493 \\ 
+BW Loc Poly & 8.783 & 6.741 & 3.194 & 8.978 \\ 
+BW Bias & 13.638 & 12.199 & 5.321 & 13.943 \\[1.0ex] 
 \midrule 
@@
    \multicolumn{1}{c}{\small{2000 Census}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.17 & -2057.60 & 0.06 & -9.72 \\ 
-  & (0.67) & (1926.33) & (0.18) & (6.27) \\ 
+LATE & 0.17 & -2055.17 & 0.06 & -9.71 \\ 
+  & (0.67) & (1920.89) & (0.18) & (6.27) \\ 
   \hdashline \\[-1.8ex]
- N Left & \multicolumn{1}{c}{5178} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} & \multicolumn{1}{c}{5131} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{343} \\ 
-Eff N Left & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{219} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{194} \\ 
-Eff N Right & \multicolumn{1}{c}{147} & \multicolumn{1}{c}{157} & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{142} \\ 
-BW Loc Poly & 8.970 & 9.368 & 8.739 & 8.530 \\ 
-BW Bias & 13.860 & 15.029 & 14.752 & 13.035 \\ 
+ N Left & 5178 & 5131 & 5131 & 5131 \\ 
+N Right & 343 & 343 & 343 & 343 \\ 
+Eff N Left & 211 & 224 & 205 & 195 \\ 
+Eff N Right & 148 & 157 & 146 & 145 \\ 
+BW Loc Poly & 9.018 & 9.464 & 8.871 & 8.591 \\ 
+BW Bias & 13.835 & 15.079 & 14.82 & 13.05 \\[1.0ex] 
 \bottomrule
@@
  \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
- LATE & 0.91$^{*}$ & 104.49$^{*}$ & 71.57 & 2.09 \\ 
-  & (0.50) & (61.53) & (218.12) & (4.37) \\ 
+LATE & 0.91$^{*}$ & 104.48$^{*}$ & 73.02 & 2.08 \\ 
+  & (0.50) & (61.51) & (216.64) & (4.40) \\ 
 \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{5179} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
-Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
-Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
-BW Loc Poly & 10.025 & 6.242 & 7.695 & 5.134 \\ 
-BW Bias & 15.889 & 10.243 & 11.780 & 8.902 \\ 
+N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1028} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
+Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & \multicolumn{1}{c}{540} & \multicolumn{1}{c}{100} \\ 
+Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{400} & \multicolumn{1}{c}{101} \\
+BW Loc Poly & 10.025 & 6.245 & 8.256 & 5.226 \\ 
+BW Bias & 15.889 & 10.249 & 11.769 & 8.959 \\[1.0ex] 
 \bottomrule
@@
   \multicolumn{1}{c}{\small{Quality}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
-LATE & -2.01$^{**}$ & -0.90$^{*}$ & 2.52$^{***}$ & -0.03 \\ 
+LATE & -2.01$^{**}$ & -0.90$^{*}$ & 2.52$^{***}$ & -0.02 \\ 
   & (0.79) & (0.48) & (0.80) & (0.13) \\ 
 \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{8597} \\ 
-N Right & \multicolumn{1}{c}{1029} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{669} \\ 
-Eff N Left & \multicolumn{1}{c}{501} & \multicolumn{1}{c}{324} & \multicolumn{1}{c}{206} & \multicolumn{1}{c}{409} \\ 
-Eff N Right & \multicolumn{1}{c}{381} & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{291} \\ 
-BW Loc Poly & 7.527 & 7.564 & 5.425 & 9.05 \\ 
-BW Bias & 11.95 & 11.01 & 10.58 & 15.107 \\ [1.0ex] 
+ N Left & 12299 & 5441 & 10156 & 8597 \\ 
+N Right & 1030 & 672 & 686 & 670 \\ 
+Eff N Left & 495 & 324 & 206 & 411 \\ 
+Eff N Right & 378 & 244 & 208 & 291 \\ 
+BW Loc Poly & 7.494 & 7.564 & 5.425 & 9.08 \\ 
+BW Bias & 11.908 & 11.01 & 10.58 & 15.144 \\ [1.0ex] 
 \bottomrule
@@
  & \multicolumn{1}{c}{\small{Num. Female}} & 
- \multicolumn{1}{c}{\small{Num. Non-white}} &
+ \multicolumn{1}{c}{\small{Num. Non-White}} &
   \multicolumn{1}{c}{\small{Candidates}} & 
   \multicolumn{1}{c}{\small{Prop. Laws}} \\ 
-   & \multicolumn{1}{c}{\small{councillors}} & 
- \multicolumn{1}{c}{\small{councillors}} &
+   & \multicolumn{1}{c}{\small{Councillors}} & 
+ \multicolumn{1}{c}{\small{Councillors}} &
   \multicolumn{1}{c}{\small{Per Seat}} & 
@@
   \hdashline \\[-1.8ex] 
- N Left & \multicolumn{1}{c}{5183} & \multicolumn{1}{c}{239} & \multicolumn{1}{c}{5184} & \multicolumn{1}{c}{3424} \\ 
-N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{158} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{269} \\ 
-Eff N Left & \multicolumn{1}{c}{195} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{179} & \multicolumn{1}{c}{227} \\ 
-Eff N Right & \multicolumn{1}{c}{145} & \multicolumn{1}{c}{47} & \multicolumn{1}{c}{132} & \multicolumn{1}{c}{141} \\ 
-BW Loc Poly & 8.623 & 2.958 & 8.144 & 10.976 \\ 
-BW Bias & 13.565 & 4.922 & 12.018 & 16.708 \\[1.0ex] 
+ N Left & 5183 & 239 & 5184 & 3424 \\ 
+N Right & 343 & 158 & 343 & 270 \\ 
+Eff N Left & 195 & 47 & 179 & 227 \\ 
+Eff N Right & 145 & 47 & 132 & 142 \\ 
+BW Loc Poly & 8.623 & 2.958 & 8.144 & 11.088 \\ 
+BW Bias & 13.565 & 4.922 & 12.018 & 16.908 \\ [1.0ex] 
 \bottomrule

### 2022-08-26 article/article.Rmd
small edits

@@
 date: August 26, 2022
-thanks: "We would like to thank Victor Araujo, Eric Arias, Mark Bennister, Taylor Boas, Natalia Bueno, Nick Cowen, Dominik Duell, Andrea Freitas, Saad Gulzar, Cathy Hafer, Daniel Hidalgo, Fernando Limongi, James Mahon, Lucas Novaes, Adam Przeworski, Catarina Roman, Howard Rosenthal, Nelson Ruiz, Renard Sexton, David Skarbek, Mike Slaven, Denis Stukal, the AJPS Editorial Team, and three anonymous reviewers for their valuable comments.
+thanks: "We would like to thank Victor Araujo, Eric Arias, Mark Bennister, Taylor Boas, Natalia Bueno, Nick Cowen, Dominik Duell, Andrea Freitas, Saad Gulzar, Cathy Hafer, Daniel Hidalgo, Fernando Limongi, James Mahon, Lucas Novaes, Adam Przeworski, Howard Rosenthal, Nelson Ruiz, Renard Sexton, David Skarbek, Mike Slaven, Denis Stukal, the AJPS Editorial Team, and three anonymous reviewers for their valuable comments.
 We also thank the participants of seminars and conferences at the CEPESP-FGV, CUNY, INSPER, IPSA, LACEA, LASA, Lincoln, MPSA, Notre Dame, NYU, PUC Chile, SPSA, and Uppsala.

### 2022-11-30 appendix/appendix.Rmd
Changes appendix to comply with AJPS editorial policies

@@
 \appendix
-\addtocounter{section}{1}
 
@@
 
-## A Model of Legislature Size and Service Provision (Proofs)
+# A Model of Legislature Size and Service Provision (Proofs)
 
@@
 
-## Variable Sources and Descriptive Statistics
+# Variable Sources and Descriptive Statistics
 \label{appsources}
@@
 
-### Outcomes Aggregated at the Municipal Level
+## Outcomes Aggregated at the Municipal Level
 
@@
 
-### Legislation Dataset
+## Legislation Dataset
 
@@
 
-### Online 2016 Former City Councilors Survey
+## Online 2016 Former City Councilors Survey
 
@@
 
-## Threshold Manipulation, Sorting, and Pre-Treatment Consistency
+# Threshold Manipulation, Sorting, and Pre-Treatment Consistency
 
@@
 
-## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
+# Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
 \label{appidentif}
@@
 
-## Identification Strategy in Regression Discontinuity Designs with Multiple Thresholds
+# Identification Strategy in Regression Discontinuity Designs with Multiple Thresholds
 \label{ISMT}
@@
 
-## Placebo Regressions for the Political Mechanism
+# Placebo Regressions for the Political Mechanism
 \label{placmechmain}
@@
 
-## Sensitivity Analysis of Bandwidth Selection
+# Sensitivity Analysis of Bandwidth Selection
 \label{sensffapp}
@@
 
-## Sensitivity Analysis of State Characteristics
+# Sensitivity Analysis of State Characteristics
 \label{sensstate}
@@
 
-## Sensitivity Analysis of Model Functional Form
+# Sensitivity Analysis of Model Functional Form
 \label{sensfuncform}
@@
 
-## Sensitivity Analysis of Covariates
+# Sensitivity Analysis of Covariates
 \label{senstcovapp}
@@
 
-## Sensitivity Analysis of Additional Cutoffs
+# Sensitivity Analysis of Additional Cutoffs
 
@@
 
-## Mayors' Characteristics, Revenues, and Transfers from the Central Government
+# Mayors' Characteristics, Revenues, and Transfers from the Central Government
 
@@
 
-### Mayors' Characteristics
+## Mayors' Characteristics
 
@@
 
-### Revenues and Transfers
+## Revenues and Transfers
 
@@
 
-## Legislation Dataset
+# Legislation Dataset
 
@@
 
-## City Councilors Survey
+# City Councilors Survey
 \label{appsurv}

### 2023-08-26 appendix/appendix.Rmd
change table seven appendix

@@
   - Danilo Freire[^danilo]
-date: August 26, 2022
+date: ""
 fontfamily: libertine
@@
 
-Table \ref{accurClassif} shows the classification accuracy for each of the variables that we have hand-coded. In all models, we set cost to 10 to avoid overfitting.
-
-\begin{table}[htb!]
-\centering
-\caption{Accuracy of SVM Classifier (Tested in 20\% of the Data)}
-\label{accurClassif}
-\begin{tabular}{lc}
-\hline
-\textbf{Variable}            & \textbf{Accuracy}  \\
-\hline
-Local Public Goods           & 93.8               \\
-Oversight                    & 94.9               \\
-Education and Health Care    & 92.5               \\
-Others                       & 93.5               \\
-\hline
-\end{tabular}
-\end{table}
-
 After we classified all the bills, we added the frequency of each category to the main paper.
